### 2019-12-10 manuscript/manuscript.tex
Add manuscript and references

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

% Define title, authors, affiliations and DOI
% ===========================================
\newcommand{\Title}{A better strategy for interpolating gravity and magnetic data}
\newcommand{\Author}{
    S.R. Soler,
    L. Uieda
}
\newcommand{\AuthorAffil}{
    {\large
        S.R. Soler$^{1,2}$,
        L. Uieda$^{3}$
    }
    \\[0.4cm]
    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
    {\small $^{3}$University of Liverpool} \\

}
\newcommand{\DOI}{doi:\href{https://doi.org/xxx.xxx/xxxxxx}{10.1093/xxx.xxx/xxxxxx}}
\newcommand{\DOILink}{\href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}}

% Configure header and hypersetup
% ===============================
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author{}, 2019. \DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    \today
}
\maketitle

\begin{abstract}
    My abstract
    \\[0.5cm]
    \textbf{Keywords:}
    My keywords
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Potential field data, like gravity and magnetics, are useful for geophysics exploration.
The potential field data can be obtained from ground, airborne or satellite
measurements.
On ground surveys the data is often gathered on scattered points or following irregular
paths.
On airborne surveys the data is gathered on flight paths, producing a large number of
data points concentrated along almost straight lines.
To improve visualization of the data for interpretation and to prepare the data for
processing through different methods (RTP, upward continuation, Euler deconvolution,
etc), the data needs to be interpolated on a regular grid of data points.

There are several methods for interpolating 2D data like minimum curvature, biharmonic
Splines or Kriging.
These all-purpose methods show a few problems when applied to potential field data.
(i) They don't take into account the height of the observation points. Potential field
data has a strong dependency on measurement height.
(ii) The predicted grid data is not necessary an Harmonic function.
(iii) They don't usually take into account the anisotropy of the observation points in
ground and airborne surveys.

One of the most widely used methods for interpolating gravity and magnetic data is the
equivalent sources technique (also known as equivalent layer, radial basis functions or
Green's functions interpolation).
It consists in estimating a source distribution that produces the same field as the one
measured and using this estimate to predict new values.
\citet{dampney1969} was the first to introduce the equivalent source technique.

The EQL can be used for interpolation of potential field data \citep{cordell1992,
cooper2000}.
It has been also used for applying a reduction to the pole to magnetic data
\citep{guspi2009, silva1986, emilia1973, nakatsuka2006} or an upward continuation
(cite).

The most widely used source distribution is a set of point sources.
The potential field of point sources is easy to compute.
How to locate these point masses?
Existing approaches:
(i) one point source beneath each observation point at a constant depth (cite),
(ii) one point source beneath each observation point at a depth proportional to the
distance to its nearest data points (cite),
(iii) a regular grid of point sources (missing citations).

We want to find out which distribution of sources produces the best interpolations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The equivalent sources technique}

Mathematical background of the EQL\@.
How it can be understood in terms of Green's functions problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Source layouts}

Describe the proposed source layouts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Comparison of source layouts}

Describe forward model made out of prisms, ground and airborne survey (plus noise), the
target grid, how do we score each interpolation.
Describe the Harmonica implementation of the EQL.

Show results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgements}

We are indebted to the developers and maintainers of the open-source software without
which this work would not have been possible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}

### 2019-12-13 manuscript/manuscript.tex
Add more structure to manuscript

@@
 \usepackage[utf8]{inputenc}
+\usepackage{amssymb}
 \usepackage{amsmath}
@@
 
-\section{Source layouts}
+\section{Source distributions}
 
-Describe the proposed source layouts.
+Describe the proposed source distributions as combination of layouts and depths
+strategies.
+
+\begin{table*}
+    \begin{minipage}{80mm}
+        \caption{
+            Source distributions as combinations of source layouts and depth
+            strategies.
+        }
+        \label{tab:source-distributions}
+        \begin{tabular}{lccc}
+            & Source bellow data & Block-reduced data & Grid sources \\ \hline
+            Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            Relative depth          & $\checkmark$ & $\checkmark$ & $\times$     \\
+            Variable relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
+        \end{tabular}
+    \end{minipage}
+\end{table*}
 
@@
 
-\section{Comparison of source layouts}
+\section{Comparison of source distributions}
 
-Describe forward model made out of prisms, ground and airborne survey (plus noise), the
-target grid, how do we score each interpolation.
+\subsection{Synthetic Model}
+
+Describe forward model made out of prisms.
+Show prisms model?
+
+\subsection{Synthetic Surveys}
+
+Describe the ground and airborne survey (plus noise).
+Show survey values.
+
+\subsection{Comparisons}
+
+Describe the target grid. Show target grid figure.
+Describe the parameters used for each source distribution, how do we score each interpolation.
 Describe the Harmonica implementation of the EQL.

### 2019-12-18 manuscript/manuscript.tex
Rename block-reduced data for block-median sources

@@
         \begin{tabular}{lccc}
-            & Source bellow data & Block-reduced data & Grid sources \\ \hline
+            & Source bellow data & Block-median sources & Grid sources \\ \hline
             Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
@@
 
+\section{Discussion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusions}

### 2019-12-19 manuscript/manuscript.tex
Advances on manuscript

@@
 On ground surveys the data is often gathered on scattered points or following irregular
-paths.
+paths, usually at the topographic surface.
+The data points have different heights.
 On airborne surveys the data is gathered on flight paths, producing a large number of
 data points concentrated along almost straight lines.
+The height of measurement could change because of the vertical movement of the airship.
 To improve visualization of the data for interpretation and to prepare the data for
@@
 The potential field of point sources is easy to compute.
+\citet{barnes2011} make use of prisms.
 How to locate these point masses?
@@
 distance to its nearest data points (cite),
-(iii) a regular grid of point sources (missing citations).
+(iii) a regular grid of sources \citep{barnes2011}.
 
@@
 strategies.
+
+The choice of a source distribution is not trivial and plays an important role on the
+accuracy of the predictions.
+
+The most widely used source distributions are: a regular grid of point sources and
+one point source beneath each observation point.
+
+The \emph{regular grid} creates an homogeneous distribution of point sources bellow the
+surveyed region.
+It could create too many sources on areas without data and very few ones on
+areas with a high number of observation points, leading to an underfitting of the
+observed data.
+This could be solved by reducing the grid spacing and therefore increasing the number of
+point sources, heavily increasing the computational load of the interpolation process.
+
+The \emph{source beneath data} layout adds sources where they are more needed.
+If the survey is composed by a large number of data points clustered on paths
+(like an airborne survey), putting one source beneath each observation point will create
+an anisotropic source distribution: there will be several sources distributed along
+a privileged direction.
+This could introduce aliases on the predictions and increase the computational load for
+fitting the predictor.
+
+We propose a new source distribution that could simultaneously solve the problems of the
+preceding ones: the \emph{block-median sources}.
+It consist in dividing the region in blocks of equal size, computing the median location
+of the observation points that fall inside each block, and putting one point source
+bellow this block-median coordinate.
+It creates one point source beneath each populated block, solving the problem of the
+\emph{grid sources} layout, but also reducing the number of point sources in comparison
+with the \emph{source beneath data} layout.
+
+The depth of the point sources can be chosen following different criteria.
+The most simple option is to locate all point sources at the same depth, which we will
+call \emph{constant depth} in the future.
+It could introduce some artifacts, like
 

### 2019-12-19 manuscript/manuscript.tex
Continue writing manuscript

@@
 The depth of the point sources can be chosen following different criteria.
+Deep sources generate low frequencies, while shallow ones generate high frequencies
+(cite).
 The most simple option is to locate all point sources at the same depth, which we will
 call \emph{constant depth} in the future.
-It could introduce some artifacts, like
+If the measurement where taken at significantly different altitudes, the elevated
+computation points will be more distant to the sources than the lower ones.
+This may create problems on reproducing high frequencies on the elevated points.
+
+One possible solution is to locate each source bellow its corresponding observation
+point or block-median point at a constant \emph{relative depth} from it.
+The sources won't be all at the same depth, but they will all be at the same distance
+from their corresponding observation point or block-median point.
+It worth mention that this approach could not be applied to \emph{grid sources}.
+
+In case our survey presents heavily clustered data points, we may want to reduce the
+depth of the sources bellow that region in order to reproduce the high frequencies
+measured by these clustered observation points.
+We can propose a \emph{variable relative depth} approach that locates each point source
+to a depth proportional to the mean distance to its $k$ nearest source neighbours
+\citep{cordell1992, guspi2004, guspi2009}.
+We propose to add a static shift to the computed depth in order to prevent very shallow
+sources in case the mean distance to the $k$ nearest neighbours is too small.
+In summary, the depth of the sources can be set as follows:
+
+\begin{equation}
+    \textrm{depth} =
+        \textrm{depth_factor} \textrm{mean_distance} + \textrm{static_shift}
+\end{equation}
+
+\noindent where the $\textrm{depth_factor}$ and the $\textrm{static_shift}$ are
+parameters and the $\textrm{mean_distance}$ is the mean distance to the $k$ nearest
+source neighbours.
+
+The combination of the three source layouts with the three strategies to define the
+depth of the sources define seven different source distributions
+(see Table~\ref{tab:source-distributions}).
+The \emph{grid sources} is only compatible with the \emph{constant depth} scheme.
 

### 2019-12-23 manuscript/manuscript.tex
Continue writing manuscript

@@
 How it can be understood in terms of Green's functions problem.
+EQL implementation on Harmonica.
 
@@
 
-Describe the proposed source distributions as combination of layouts and depths
-strategies.
+% Describe the proposed source distributions as combination of layouts and depths
+% strategies.
 
@@
 This could be solved by reducing the grid spacing and therefore increasing the number of
-point sources, heavily increasing the computational load of the interpolation process.
+point sources and the computational load of the interpolation process.
 
@@
 
+Compare the accuracy of the predictions made by each source distribution.
+Need an objective way to compare them.
+Propose a synthetic gravity model made out of prisms of different sizes and density
+contrasts.
+Create a regular grid of observation points where the gravitational effect of the
+synthetic model will be computed.
+Call it the \emph{target grid}.
+Generate synthetic surveys above the same synthetic model and compute the gravitational
+effect of the model on each survey.
+Use each source distribution to predict values based on the ones obtained on each survey
+onto the same grid points of the \emph{target grid}.
+Score each interpolation by comparing the predicted values with the \emph{target grid}.
+Finally compare the accuracy of the predictions made by each source distribution.
+
 \subsection{Synthetic Model}
@@
 
-Describe the ground and airborne survey (plus noise).
-Show survey values.
+Create synthetic surveys to produce observation points.
+In order to compare each source layout under very different set of observation points we
+create a ground and an airborne synthetic surveys.
+We selected a portion of the Southern Africa Gravity Data obtained by Dr. R.J. Kleywegt
+et al.\ and made available through the NOAA website
+(\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}) for creating a synthetic
+ground survey.
+We selected a portion of the Great Britain Aeromagnetic Survey acquired by Hunting
+Geology and Geophysics Ltd and Canadian Aeroservices Ltd between 1955 and 1965 and made
+available by the
+\href{
+    https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html
+    }{
+    British Geological Survey (BGS)
+}, for creating a synthetic airborne survey.
+
+The gravitation effect of the synthetic model has been computed on both surveys and
+added Gaussian noise (standard deviation of 1mGal) to simulate acquisition errors.
 
@@
 
-Describe the target grid. Show target grid figure.
-Describe the parameters used for each source distribution, how do we score each interpolation.
-Describe the Harmonica implementation of the EQL.
+%Describe the target grid. Show target grid figure.
+%Describe the parameters used for each source distribution, how do we score each interpolation.
+%Describe the Harmonica implementation of the EQL.
+%Show results.
 
-Show results.
+Compute the gravitational effect of the synthetic model on a regular grid of points
+located at the same height.
+This will be called our \emph{target grid}.
+We will use it to compute the accuracy of the predictions made by each source
+distribution.
+
+Take a source distribution, fit the source coefficients and then use them to predict
+data on the grid points where the \emph{target grid} is defined.
+Define prediction error as the difference between the predicted values and the
+\emph{target grid}.
+
+Each source distribution has parameters that need to be specified before fitting its
+coefficients.
+For example, the \emph{grid of sources} needs the depth at which the sources will be
+located.
+The damping parameter used on the fitting process must also be specified beforehand.
+These parameters play an important role on the accuracy of the prediction.
+We compute several predictions made by the same source distribution, but with different
+values for its parameters.
+Then we score each interpolation by computing the R$^2$ between each prediction and the
+target grid.
+We keep the best prediction, i.e.\ the one that has the highest R$^2$ score.
 

### 2020-01-14 manuscript/manuscript.tex
Shrink manuscript to 80 chars per line

@@
 % ===========================================
-\newcommand{\Title}{A better strategy for interpolating gravity and magnetic data}
+\newcommand{\Title}{
+    A better strategy for interpolating gravity and magnetic data
+}
 \newcommand{\Author}{
@@
 }
-\newcommand{\DOI}{doi:\href{https://doi.org/xxx.xxx/xxxxxx}{10.1093/xxx.xxx/xxxxxx}}
-\newcommand{\DOILink}{\href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}}
+\newcommand{\DOI}{
+    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{10.1093/xxx.xxx/xxxxxx}
+}
+\newcommand{\DOILink}{
+    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
+}
 
@@
 
-Potential field data, like gravity and magnetics, are useful for geophysics exploration.
+Potential field data, like gravity and magnetics, are useful for geophysics
+exploration.
 The potential field data can be obtained from ground, airborne or satellite
 measurements.
-On ground surveys the data is often gathered on scattered points or following irregular
-paths, usually at the topographic surface.
+On ground surveys the data is often gathered on scattered points or following
+irregular paths, usually at the topographic surface.
 The data points have different heights.
-On airborne surveys the data is gathered on flight paths, producing a large number of
-data points concentrated along almost straight lines.
-The height of measurement could change because of the vertical movement of the airship.
-To improve visualization of the data for interpretation and to prepare the data for
-processing through different methods (RTP, upward continuation, Euler deconvolution,
-etc), the data needs to be interpolated on a regular grid of data points.
+On airborne surveys the data is gathered on flight paths, producing a large
+number of data points concentrated along almost straight lines.
+The height of measurement could change because of the vertical movement of the
+airship.
+To improve visualization of the data for interpretation and to prepare the data
+for processing through different methods (RTP, upward continuation, Euler
+deconvolution, etc), the data needs to be interpolated on a regular grid of
+data points.
 
-There are several methods for interpolating 2D data like minimum curvature, biharmonic
-Splines or Kriging.
-These all-purpose methods show a few problems when applied to potential field data.
-(i) They don't take into account the height of the observation points. Potential field
-data has a strong dependency on measurement height.
+There are several methods for interpolating 2D data like minimum curvature,
+biharmonic Splines or Kriging.
+These all-purpose methods show a few problems when applied to potential field
+data.
+(i) They don't take into account the height of the observation points.
+Potential field data has a strong dependency on measurement height.
 (ii) The predicted grid data is not necessary an Harmonic function.
-(iii) They don't usually take into account the anisotropy of the observation points in
-ground and airborne surveys.
+(iii) They don't usually take into account the anisotropy of the observation
+points in ground and airborne surveys.
 
-One of the most widely used methods for interpolating gravity and magnetic data is the
-equivalent sources technique (also known as equivalent layer, radial basis functions or
-Green's functions interpolation).
-It consists in estimating a source distribution that produces the same field as the one
-measured and using this estimate to predict new values.
+One of the most widely used methods for interpolating gravity and magnetic data
+is the equivalent sources technique (also known as equivalent layer, radial
+basis functions or Green's functions interpolation).
+It consists in estimating a source distribution that produces the same field as
+the one measured and using this estimate to predict new values.
 \citet{dampney1969} was the first to introduce the equivalent source technique.
 
-The EQL can be used for interpolation of potential field data \citep{cordell1992,
-cooper2000}.
+The EQL can be used for interpolation of potential field data
+\citep{cordell1992, cooper2000}.
 It has been also used for applying a reduction to the pole to magnetic data
-\citep{guspi2009, silva1986, emilia1973, nakatsuka2006} or an upward continuation
-(cite).
+\citep{guspi2009, silva1986, emilia1973, nakatsuka2006} or an upward
+continuation (cite).
 
@@
 (i) one point source beneath each observation point at a constant depth (cite),
-(ii) one point source beneath each observation point at a depth proportional to the
-distance to its nearest data points (cite),
+(ii) one point source beneath each observation point at a depth proportional to
+the distance to its nearest data points (cite),
 (iii) a regular grid of sources \citep{barnes2011}.
 
-We want to find out which distribution of sources produces the best interpolations.
+We want to find out which distribution of sources produces the best
+interpolations.
 
@@
 
-% Describe the proposed source distributions as combination of layouts and depths
-% strategies.
+% Describe the proposed source distributions as combination of layouts and
+% depths strategies.
 
-The choice of a source distribution is not trivial and plays an important role on the
-accuracy of the predictions.
+The choice of a source distribution is not trivial and plays an important role
+on the accuracy of the predictions.
 
-The most widely used source distributions are: a regular grid of point sources and
-one point source beneath each observation point.
+The most widely used source distributions are: a regular grid of point sources
+and one point source beneath each observation point.
 
-The \emph{regular grid} creates an homogeneous distribution of point sources bellow the
-surveyed region.
+The \emph{regular grid} creates an homogeneous distribution of point sources
+bellow the surveyed region.
 It could create too many sources on areas without data and very few ones on
-areas with a high number of observation points, leading to an underfitting of the
-observed data.
-This could be solved by reducing the grid spacing and therefore increasing the number of
-point sources and the computational load of the interpolation process.
+areas with a high number of observation points, leading to an underfitting of
+the observed data.
+This could be solved by reducing the grid spacing and therefore increasing the
+number of point sources and the computational load of the interpolation
+process.
 
@@
 If the survey is composed by a large number of data points clustered on paths
-(like an airborne survey), putting one source beneath each observation point will create
-an anisotropic source distribution: there will be several sources distributed along
-a privileged direction.
-This could introduce aliases on the predictions and increase the computational load for
-fitting the predictor.
+(like an airborne survey), putting one source beneath each observation point
+will create an anisotropic source distribution: there will be several sources
+distributed along a privileged direction.
+This could introduce aliases on the predictions and increase the computational
+load for fitting the predictor.
 
-We propose a new source distribution that could simultaneously solve the problems of the
-preceding ones: the \emph{block-median sources}.
-It consist in dividing the region in blocks of equal size, computing the median location
-of the observation points that fall inside each block, and putting one point source
-bellow this block-median coordinate.
-It creates one point source beneath each populated block, solving the problem of the
-\emph{grid sources} layout, but also reducing the number of point sources in comparison
-with the \emph{source beneath data} layout.
+We propose a new source distribution that could simultaneously solve the
+problems of the preceding ones: the \emph{block-median sources}.
+It consist in dividing the region in blocks of equal size, computing the median
+location of the observation points that fall inside each block, and putting one
+point source bellow this block-median coordinate.
+It creates one point source beneath each populated block, solving the problem
+of the \emph{grid sources} layout, but also reducing the number of point
+sources in comparison with the \emph{source beneath data} layout.
 
 The depth of the point sources can be chosen following different criteria.
-Deep sources generate low frequencies, while shallow ones generate high frequencies
-(cite).
-The most simple option is to locate all point sources at the same depth, which we will
-call \emph{constant depth} in the future.
-If the measurement where taken at significantly different altitudes, the elevated
-computation points will be more distant to the sources than the lower ones.
-This may create problems on reproducing high frequencies on the elevated points.
+Deep sources generate low frequencies, while shallow ones generate high
+frequencies (cite).
+The most simple option is to locate all point sources at the same depth, which
+we will call \emph{constant depth} in the future.
+If the measurement where taken at significantly different altitudes, the
+elevated computation points will be more distant to the sources than the lower
+ones.
+This may create problems on reproducing high frequencies on the elevated
+points.
 
-One possible solution is to locate each source bellow its corresponding observation
-point or block-median point at a constant \emph{relative depth} from it.
-The sources won't be all at the same depth, but they will all be at the same distance
-from their corresponding observation point or block-median point.
-It worth mention that this approach could not be applied to \emph{grid sources}.
+One possible solution is to locate each source bellow its corresponding
+observation point or block-median point at a constant \emph{relative depth}
+from it.
+The sources won't be all at the same depth, but they will all be at the same
+distance from their corresponding observation point or block-median point.
+It worth mention that this approach could not be applied to \emph{grid
+sources}.
 
-In case our survey presents heavily clustered data points, we may want to reduce the
-depth of the sources bellow that region in order to reproduce the high frequencies
-measured by these clustered observation points.
-We can propose a \emph{variable relative depth} approach that locates each point source
-to a depth proportional to the mean distance to its $k$ nearest source neighbours
-\citep{cordell1992, guspi2004, guspi2009}.
-We propose to add a static shift to the computed depth in order to prevent very shallow
-sources in case the mean distance to the $k$ nearest neighbours is too small.
+In case our survey presents heavily clustered data points, we may want to
+reduce the depth of the sources bellow that region in order to reproduce the
+high frequencies measured by these clustered observation points.
+We can propose a \emph{variable relative depth} approach that locates each
+point source to a depth proportional to the mean distance to its $k$ nearest
+source neighbours \citep{cordell1992, guspi2004, guspi2009}.
+We propose to add a static shift to the computed depth in order to prevent very
+shallow sources in case the mean distance to the $k$ nearest neighbours is too
+small.
 In summary, the depth of the sources can be set as follows:
@@
 \noindent where the $\textrm{depth_factor}$ and the $\textrm{static_shift}$ are
-parameters and the $\textrm{mean_distance}$ is the mean distance to the $k$ nearest
-source neighbours.
+parameters and the $\textrm{mean_distance}$ is the mean distance to the $k$
+nearest source neighbours.
 
-The combination of the three source layouts with the three strategies to define the
-depth of the sources define seven different source distributions
-(see Table~\ref{tab:source-distributions}).
-The \emph{grid sources} is only compatible with the \emph{constant depth} scheme.
+The combination of the three source layouts with the three strategies to define
+the depth of the sources define seven different source distributions (see
+Table~\ref{tab:source-distributions}).
+The \emph{grid sources} is only compatible with the \emph{constant depth}
+scheme.
 
@@
 Need an objective way to compare them.
-Propose a synthetic gravity model made out of prisms of different sizes and density
-contrasts.
-Create a regular grid of observation points where the gravitational effect of the
-synthetic model will be computed.
+Propose a synthetic gravity model made out of prisms of different sizes and
+density contrasts.
+Create a regular grid of observation points where the gravitational effect of
+the synthetic model will be computed.
 Call it the \emph{target grid}.
-Generate synthetic surveys above the same synthetic model and compute the gravitational
-effect of the model on each survey.
-Use each source distribution to predict values based on the ones obtained on each survey
-onto the same grid points of the \emph{target grid}.
-Score each interpolation by comparing the predicted values with the \emph{target grid}.
-Finally compare the accuracy of the predictions made by each source distribution.
+Generate synthetic surveys above the same synthetic model and compute the
+gravitational effect of the model on each survey.
+Use each source distribution to predict values based on the ones obtained on
+each survey onto the same grid points of the \emph{target grid}.
+Score each interpolation by comparing the predicted values with the
+\emph{target grid}.
+Finally compare the accuracy of the predictions made by each source
+distribution.
 
@@
 Create synthetic surveys to produce observation points.
-In order to compare each source layout under very different set of observation points we
-create a ground and an airborne synthetic surveys.
-We selected a portion of the Southern Africa Gravity Data obtained by Dr. R.J. Kleywegt
-et al.\ and made available through the NOAA website
-(\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}) for creating a synthetic
-ground survey.
-We selected a portion of the Great Britain Aeromagnetic Survey acquired by Hunting
-Geology and Geophysics Ltd and Canadian Aeroservices Ltd between 1955 and 1965 and made
-available by the
+In order to compare each source layout under very different set of observation
+points we create a ground and an airborne synthetic surveys.
+We selected a portion of the Southern Africa Gravity Data obtained by Dr. R.J.
+Kleywegt et al.\ and made available through the NOAA website
+(\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}) for creating
+a synthetic ground survey.
+We selected a portion of the Great Britain Aeromagnetic Survey acquired by
+Hunting Geology and Geophysics Ltd and Canadian Aeroservices Ltd between 1955
+and 1965 and made available by the
 \href{
@@
     British Geological Survey (BGS)
-}, for creating a synthetic airborne survey.
+}
+, for creating a synthetic airborne survey.
 
-The gravitation effect of the synthetic model has been computed on both surveys and
-added Gaussian noise (standard deviation of 1mGal) to simulate acquisition errors.
+The gravitation effect of the synthetic model has been computed on both surveys
+and added Gaussian noise (standard deviation of 1mGal) to simulate acquisition
+errors.
 
@@
 %Describe the target grid. Show target grid figure.
-%Describe the parameters used for each source distribution, how do we score each interpolation.
+%Describe the parameters used for each source distribution, how do we score
+%each interpolation.
 %Describe the Harmonica implementation of the EQL.
@@
 
-Compute the gravitational effect of the synthetic model on a regular grid of points
-located at the same height.
+Compute the gravitational effect of the synthetic model on a regular grid of
+points located at the same height.
 This will be called our \emph{target grid}.
@@
 
-Take a source distribution, fit the source coefficients and then use them to predict
-data on the grid points where the \emph{target grid} is defined.
+Take a source distribution, fit the source coefficients and then use them to
+predict data on the grid points where the \emph{target grid} is defined.
 Define prediction error as the difference between the predicted values and the
@@
 
-Each source distribution has parameters that need to be specified before fitting its
-coefficients.
-For example, the \emph{grid of sources} needs the depth at which the sources will be
-located.
-The damping parameter used on the fitting process must also be specified beforehand.
+Each source distribution has parameters that need to be specified before
+fitting its coefficients.
+For example, the \emph{grid of sources} needs the depth at which the sources
+will be located.
+The damping parameter used on the fitting process must also be specified
+beforehand.
 These parameters play an important role on the accuracy of the prediction.
-We compute several predictions made by the same source distribution, but with different
-values for its parameters.
-Then we score each interpolation by computing the R$^2$ between each prediction and the
-target grid.
+We compute several predictions made by the same source distribution, but with
+different values for its parameters.
+Then we score each interpolation by computing the R$^2$ between each prediction
+and the target grid.
 We keep the best prediction, i.e.\ the one that has the highest R$^2$ score.
@@
 
-We are indebted to the developers and maintainers of the open-source software without
-which this work would not have been possible.
+We are indebted to the developers and maintainers of the open-source software
+without which this work would not have been possible.
 

### 2020-01-15 manuscript/manuscript.tex
Start writing the equivalent sources technique section

@@
 
+The Green's equivalent layer theorem states that any harmonic potential field
+generated by any three dimensional physical-property distribution can by
+reproduced by a continuous two dimensional surface distribution.
+This introduces an ambiguity on the distribution that generates
+a potential field: multiple physical-property distributions can generate the
+same potential field.
+This represents an obstacle for determining the true shape and
+physical-property distribution that generates the measured potential field.
+Nevertheless this ambiguity can also be exploited for developing preprocessing
+techniques like interpolating potential field data.
+
+Approximating the continuous distribution by a finite and discrete density
+distribution is the basis of the \emph{equivalent sources technique}
+\citep{dampney1969}.
+The most common approach is to make use of a set of point masses (the
+\emph{equivalent sources}) located beneath the observation points.
+
+Lets consider a set of gravity acceleration measurements $g_z$ on points
+$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$ and a set of point sources with mass
+$\{m_1, \ldots, m_M\}$ located on points
+$\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$.
+The point sources must generate the same gravity field as the one measured:
+
+\begin{equation}
+    \mathbf{g}(\mathbf{p}) = \mathbf{A} \mathbf{m},
+    \label{eq:linear-problem-g}
+\end{equation}
+
+\noindent where $\mathbf{g}(\mathbf{p})$ is the vector containing the measured
+field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
+masses of the point sources and $\mathbf{A}$ the \emph{Jacobian matrix}, whose
+elements can be obtained as:
+
+\begin{equation}
+    a_{ij} = G \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|^2},
+    \quad \forall \,\, i = 1, \ldots, N
+    \quad \forall \,\, j = 1, \ldots, M.
+\end{equation}
+
+By solving equation~\ref{eq:linear-problem-g} we can obtain the values of
+$\mathbf{m}$ that better reproduce the measured field.
+This source distribution along with the fitted masses can be used to predict
+gravity values on any point where the potential field has not been measured.
+
+Worth noting that solving equation~\ref{eq:linear-problem-g} is equivalent to
+an inversion and thus solving an ill-posed problem by nature due to the
+non-uniqueness and the instability of the possible solutions.
+Therefore is usually needed to add regularization functions in order to obtain
+stable solutions \citep{oliveira2013}.
+Moreover there's no limitation on the amount of point sources.
+The number of sources can either be equal, less or more than the number of
+observation points, leading to well, under or overdetermined linear problem,
+respectively.
+
+Add other possible applications to the EQL like RTP or upward continuation.
+
+\subsection{Generalization of equivalent sources}
+
+By definition, any harmonic field $V$ must satisfy the Laplace's equation:
+
+\begin{equation}
+    \nabla^2 V = 0.
+\end{equation}
+
+The fundamental solution $\psi$ \citep[p.~210]{vladimirov1979} of the harmonic
+field $V$ must satisfy:
+
+\begin{equation}
+    \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
+        - 4\pi \delta(\mathbf{p}, \mathbf{q})
+\end{equation}
+
+\noindent where $\delta(\mathbf{p}, \mathbf{q})$ is the Dirac's delta function
+and $\nabla_\mathbf{p}$ symbolize the Nabla operator applied on the
+coordinates $\mathbf{p}$.
+
+Assuming that $\psi$ tends to zero when approaching to infinity as boundary
+condition, the fundamental solution of any harmonic field can be obtained as
+follows \citep{blakely1995}:
+
+\begin{equation}
+    \psi(\mathbf{p}, \mathbf{q})
+    =
+    \int
+    \frac{\delta(\mathbf{p}, \mathbf{q})}{|\mathbf{p} - \mathbf{q}|}
+    \textrm{d}v
+    =
+    \frac{1}{|\mathbf{p} - \mathbf{q}|}
+    =
+    \frac{1}{r}.
+\end{equation}
+
+This shows that the Green's function associated with any harmonic field is
+equal to one over the Cartesian distance between the evaluation and the source
+points.
+
 Mathematical background of the EQL\@.
@@
     \textrm{depth} =
-        \textrm{depth_factor} \textrm{mean_distance} + \textrm{static_shift}
+        \textrm{depth factor} \cdot \textrm{mean distance}
+        + \textrm{static shift}
 \end{equation}
 
-\noindent where the $\textrm{depth_factor}$ and the $\textrm{static_shift}$ are
-parameters and the $\textrm{mean_distance}$ is the mean distance to the $k$
+\noindent where the \emph{depth factor} and the \emph{static shift} are
+parameters and the \emph{mean distance} is the mean distance to the $k$
 nearest source neighbours.

### 2020-01-21 manuscript/manuscript.tex
Continue writing EQL technique

@@
 \newcommand{\DOI}{
-    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{10.1093/xxx.xxx/xxxxxx}
+    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
 }
@@
 This represents an obstacle for determining the true shape and
-physical-property distribution that generates the measured potential field.
+physical-property distribution that generates any measured potential field.
 Nevertheless this ambiguity can also be exploited for developing preprocessing
@@
 \citep{dampney1969}.
-The most common approach is to make use of a set of point masses (the
+The most common approach is to make use of a set of point sources (the
 \emph{equivalent sources}) located beneath the observation points.
@@
     \mathbf{g}(\mathbf{p}) = \mathbf{A} \mathbf{m},
-    \label{eq:linear-problem-g}
 \end{equation}
@@
 field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
-masses of the point sources and $\mathbf{A}$ the \emph{Jacobian matrix}, whose
+masses of the point sources and $\mathbf{A}$ a matrix whose
 elements can be obtained as:
@@
     a_{ij} = G \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|^2},
-    \quad \forall \,\, i = 1, \ldots, N
-    \quad \forall \,\, j = 1, \ldots, M.
 \end{equation}
@@
 
-Worth noting that solving equation~\ref{eq:linear-problem-g} is equivalent to
-an inversion and thus solving an ill-posed problem by nature due to the
-non-uniqueness and the instability of the possible solutions.
-Therefore is usually needed to add regularization functions in order to obtain
-stable solutions \citep{oliveira2013}.
-Moreover there's no limitation on the amount of point sources.
-The number of sources can either be equal, less or more than the number of
-observation points, leading to well, under or overdetermined linear problem,
-respectively.
+\subsection{Generalization of equivalent sources}
 
-Add other possible applications to the EQL like RTP or upward continuation.
-
-\subsection{Generalization of equivalent sources}
+It's possible to generalize the equivalent sources technique to any harmonic
+field through a Green's function problem, regardless the nature of the field.
 
@@
     =
-    \frac{1}{|\mathbf{p} - \mathbf{q}|}
-    =
-    \frac{1}{r}.
+    \frac{1}{|\mathbf{p} - \mathbf{q}|}.
 \end{equation}
@@
 This shows that the Green's function associated with any harmonic field is
-equal to one over the Cartesian distance between the evaluation and the source
-points.
+equal to the inverse of the Cartesian distance between the evaluation and the
+source points.
+Thus any harmonic field $V$ can be expressed as \citep[p.~37]{blakely1995}:
 
-Mathematical background of the EQL\@.
-How it can be understood in terms of Green's functions problem.
+\begin{equation}
+    V(\mathbf{p})
+    =
+    \int \psi(\mathbf{p}, \mathbf{q}) \rho(\mathbf{q}) d\mathbf{q}
+    =
+    \int \frac{\rho(\mathbf{q})}{|\mathbf{p} - \mathbf{q}|}  d\mathbf{q},
+\end{equation}
+
+\noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
+physical-property evaluated on the point $\mathbf{q}$. This density
+distribution can be approximated by a finite and discrete set of point sources
+located on $\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$:
+
+\begin{equation}
+    \rho(\mathbf{q}) =
+        \sum\limits_{j=1}^{M} c_j \delta(\mathbf{q} - \mathbf{q_j}),
+\end{equation}
+
+\noindent where $c_j$ is a coefficient related to the point source located on
+$\mathbf{q}_j$, with the same units as the physical-property.
+Then the harmonic field $V$ can be approximated by:
+
+\begin{equation}
+    V(\mathbf{p})
+    \simeq
+    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
+\end{equation}
+
+In case we have measured the value of the harmonic field on points
+$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$, we can adjust the values of the $c$
+coefficients so they satisfy:
+
+\begin{equation}
+    V(\mathbf{p}_i)
+    =
+    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p}_i - \mathbf{q}_j|}
+    \quad \forall i=1,\ldots,N.
+\end{equation}
+
+This system of linear equations can be written in an more algebraic way:
+
+\begin{equation}
+    V(\mathbf{p}) = \mathbf{A} \mathbf{c}
+    \label{eq:linear-problem}
+\end{equation}
+
+\noindent where $V(\mathbf{p}$) is a vertical vector containing the measured
+values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
+containing the $c$ coefficients and $\mathbf{A}$ is the \emph{Jacobian matrix},
+whose elements are defined as the Green's function evaluated on each pair of
+points $\mathbf{p}$ and $\mathbf{q}$:
+
+\begin{equation}
+    a_{ij}
+    =
+    \psi(\mathbf{p}_i, \mathbf{q}_j)
+    =
+    \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|}
+\end{equation}
+
+Worth noting that solving equation~\ref{eq:linear-problem} is equivalent to
+an inversion and thus solving an ill-posed problem by nature due to the
+non-uniqueness and the instability of the possible solutions.
+Therefore is usually needed to add regularization functions in order to obtain
+stable solutions \citep{oliveira2013}.
+Moreover there's no limitation on the amount of point sources.
+The number of sources can either be equal, less or more than the number of
+observation points, leading to well, under or overdetermined linear problem,
+respectively.
+
+Add other possible applications to the EQL like RTP or upward continuation.
+
 EQL implementation on Harmonica.

### 2020-01-21 manuscript/manuscript.tex
Change g vector to g_z

@@
 \begin{equation}
-    \mathbf{g}(\mathbf{p}) = \mathbf{A} \mathbf{m},
+    g_z(\mathbf{p}) = \mathbf{A} \mathbf{m},
+    \label{eq:linear-problem-g}
 \end{equation}
 
-\noindent where $\mathbf{g}(\mathbf{p})$ is the vector containing the measured
+\noindent where $g_z(\mathbf{p})$ is the vector containing the measured
 field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
 masses of the point sources and $\mathbf{A}$ a matrix whose
-elements can be obtained as:
+elements can be obtained as the vertical component of the gravitational
+acceleration measured on $\mathbf{p}$ due to the point mass on $\mathbf{q}$:
 
 \begin{equation}
-    a_{ij} = G \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|^2},
+    a_{ij} = G \frac{(z_i - z_j)}{|\mathbf{p}_i - \mathbf{q}_j|^3},
 \end{equation}
+
+\noindent where $z_i$ and $z_j$ are the vertical components of the
+$\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
 

### 2020-01-23 manuscript/manuscript.tex
Continue writing manuscript

@@
 
+A classical approach for applying the equivalent sources technique would be to
+propose a set of point sources that generate the same harmonic field that has
+been measured.
+This requires
 Lets consider a set of gravity acceleration measurements $g_z$ on points
@@
 \noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
-physical-property evaluated on the point $\mathbf{q}$. This density
-distribution can be approximated by a finite and discrete set of point sources
-located on $\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$:
+physical-property evaluated on the point $\mathbf{q}$. Following
+\citet{dampney1969}, this density distribution can be approximated by a finite
+and discrete set of point sources located on $\{\mathbf{q}_1, \ldots,
+\mathbf{q}_M\}$:
 
@@
     V(\mathbf{p})
-    \simeq
+    =
     \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
+    \label{eq:eql-field}
 \end{equation}
@@
 
-Worth noting that solving equation~\ref{eq:linear-problem} is equivalent to
-an inversion and thus solving an ill-posed problem by nature due to the
-non-uniqueness and the instability of the possible solutions.
+By solving equation~\ref{eq:linear-problem} we can obtain the values of
+$\mathbf{c}$ that better reproduce the measured field.
+Then they can be used to predict the value of the harmonic field on any other
+point where no measurement has been taken by evaluating
+equation~\ref{eq:eql-field}.
+
+Worth noting that solving equations~\ref{eq:linear-problem-g}
+and~\ref{eq:linear-problem} is equivalent to performing an inversion and thus
+solving an ill-posed problem by nature due to the non-uniqueness and the
+instability of the possible solutions.
 Therefore is usually needed to add regularization functions in order to obtain
@@
 
-Add other possible applications to the EQL like RTP or upward continuation.
+% Add other possible applications to the EQL like RTP or upward continuation.
 
-EQL implementation on Harmonica.
+% EQL implementation on Harmonica.
 

### 2020-01-23 manuscript/manuscript.tex
Describe EQL implementation in Harmonica

@@
 
+\subsection{Equivalent sources implementation}
+
+The subsequent comparisons between strategies for interpolating data through
+equivalent sources are carried out by the equivalent sources implementation in
+Harmonica \citep{harmonica}.
+
+It solves equation~\ref{eq:linear-problem} by a least-squares fit, with
+the option of adding a zeroth-order Tikhonov \citep{tikhonov} regularization
+through a dimensionless \emph{damping} parameter.
+This is achieved by scaling the Jacobian matrix so each column has unit
+variance.
+
+Define a diagonal matrix $S$, whose elements corresponds to the standard
+deviation of each column of the Jacobian matrix $\mathbf{A}$:
+
+\begin{equation}
+    \mathbf{S} =
+    \begin{bmatrix}
+        \sigma_1 & \cdots &0 \\
+        \vdots & \ddots & \vdots \\
+        0 & \cdots & \sigma_M
+    \end{bmatrix}.
+\end{equation}
+
+Equation~\ref{eq:linear-problem} can be written as:
+
+\begin{equation}
+    V(\mathbf{p})
+    =
+    \mathbf{A} \mathbf{S}^{-1} \mathbf{S} \mathbf{c}
+    =
+    \left[
+        \mathbf{A} \mathbf{S}^{-1}
+    \right]
+    \left[
+        \mathbf{S} \mathbf{c}
+    \right]
+    =
+    \mathbf{A}' \mathbf{c}'
+\end{equation}
+
+\noindent where $\mathbf{A}'$ the scaled Jacobian matrix and $\mathbf{c}'$ is
+a vector containing scaled coefficients.
+
+Now we can define the misfit function as the sum between the data misift and
+the Tikhonov regularization function:
+
+\begin{equation}
+    \phi(\mathbf{c'}) =
+        \left\lVert V(\mathbf{p}) - \mathbf{A}'\mathbf{c}' \right\rVert ^ 2
+        + \lambda \left\lVert \mathbf{c}' \right\rVert ^2,
+    \label{eq:misfit}
+\end{equation}
+
+\noindent where $\lambda$ is a dimensionless damping parameter.
+
+After solving the least squares problem, we obtain the set of scaled
+coefficients $\mathbf{c}'$ that minimizes equation~\ref{eq:misfit}.
+We can get the corresponding coefficients $\mathbf{c}$ by rescaling
+$\mathbf{c}'$:
+
+\begin{equation}
+    \mathbf{c} = \mathbf{S}^{-1} \mathbf{c}'.
+\end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-02-05 manuscript/manuscript.tex
Add depth-types figure to manuscript
Delete old line

@@
 been measured.
-This requires
 Lets consider a set of gravity acceleration measurements $g_z$ on points
@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
+    \caption{Cartoon illustrating the different depth types.}
+    \label{fig:depth-types}
+\end{figure*}
+
 The combination of the three source layouts with the three strategies to define

### 2020-02-05 manuscript/manuscript.tex
Redefine symbols for scaled matrix and coefs vector

@@
     =
-    \mathbf{A}' \mathbf{c}'
+    \mathbf{A_s} \mathbf{c_s}
 \end{equation}
 
-\noindent where $\mathbf{A}'$ the scaled Jacobian matrix and $\mathbf{c}'$ is
+\noindent where $\mathbf{A_s}$ the scaled Jacobian matrix and $\mathbf{c_s}$ is
 a vector containing scaled coefficients.
@@
     \phi(\mathbf{c'}) =
-        \left\lVert V(\mathbf{p}) - \mathbf{A}'\mathbf{c}' \right\rVert ^ 2
-        + \lambda \left\lVert \mathbf{c}' \right\rVert ^2,
+        \left\lVert V(\mathbf{p}) - \mathbf{A_s}\mathbf{c_s} \right\rVert ^ 2
+        + \lambda \left\lVert \mathbf{c_s} \right\rVert ^2,
     \label{eq:misfit}
@@
 After solving the least squares problem, we obtain the set of scaled
-coefficients $\mathbf{c}'$ that minimizes equation~\ref{eq:misfit}.
+coefficients $\mathbf{c_s}$ that minimizes equation~\ref{eq:misfit}.
 We can get the corresponding coefficients $\mathbf{c}$ by rescaling
-$\mathbf{c}'$:
+$\mathbf{c_s}$:
 
 \begin{equation}
-    \mathbf{c} = \mathbf{S}^{-1} \mathbf{c}'.
+    \mathbf{c} = \mathbf{S}^{-1} \mathbf{c_s}.
 \end{equation}

### 2020-02-05 manuscript/manuscript.tex
Improve caption of depth type figure

@@
     \includegraphics[width=\linewidth]{figs/depth_types.pdf}
-    \caption{Cartoon illustrating the different depth types.}
+    \caption{
+        Depth types for locating point sources. We put one source beneath each
+        observation point (station) using: (a)~a \emph{constant depth} where all sources
+        are located at the same depth, (b)~a \emph{relative depth} where all sources are
+        located at the same vertical distance from its corresponding observation point,
+        and (c)~a \emph{variable relative depth} where the depth of the sources is
+        proportional to the average distance to its neighbour sources. Notice how the
+        clustered sources on (c) are relatively shallower than the other ones.
+    }
     \label{fig:depth-types}

### 2020-02-10 manuscript/manuscript.tex
Improve description of variable depth

@@
 we will call \emph{constant depth} in the future.
-If the measurement where taken at significantly different altitudes, the
+If the measurement were taken at significantly different altitudes, the
 elevated computation points will be more distant to the sources than the lower
@@
 The sources won't be all at the same depth, but they will all be at the same
-distance from their corresponding observation point or block-median point.
+distance from their corresponding observation point (or block-median point).
 It worth mention that this approach could not be applied to \emph{grid
@@
 high frequencies measured by these clustered observation points.
-We can propose a \emph{variable relative depth} approach that locates each
-point source to a depth proportional to the mean distance to its $k$ nearest
-source neighbours \citep{cordell1992, guspi2004, guspi2009}.
-We propose to add a static shift to the computed depth in order to prevent very
-shallow sources in case the mean distance to the $k$ nearest neighbours is too
-small.
-In summary, the depth of the sources can be set as follows:
+We can propose a \emph{variable depth} approach: it locates each point source
+according to the \emph{relative depth} approach and then add a term
+proportional to the mean distance to its $k$ nearest neighbour sources.
+So, the depth of the sources can be computed as follows:
 
 \begin{equation}
+    \begin{split}
         \textrm{depth} =
-        \textrm{depth factor} \cdot \textrm{mean distance}
-        + \textrm{static shift}
+           &\textrm{data point height} - \textrm{relative depth} \\
+           &- \textrm{depth factor} \cdot \textrm{mean distance}
+    \end{split}
 \end{equation}
 
-\noindent where the \emph{depth factor} and the \emph{static shift} are
-parameters and the \emph{mean distance} is the mean distance to the $k$
-nearest source neighbours.
+\noindent where \emph{data point height} is the elevation of the corresponding
+observation (or block-median) point to the source, \emph{depth factor} and
+\emph{relative depth} are parameters and \emph{mean distance} is the mean
+distance to the $k$ nearest source neighbours.
+
+Similar approaches for setting sources at depths that depend
+on the distance to their nearest neighbours were already proposed by
+\citet{cordell1992, guspi2004, guspi2009}.
 

### 2020-02-11 manuscript/manuscript.tex
Add block-median sources figure to manuscript

@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
+    \caption{
+        Block-median sources. Given a set of observation points (a) we divide
+        the survey region on blocks of equal size (b) and compute the median
+        location of the observation points that fall inside each block.
+        A source point is located beneath each block-median coordinate (c).
+    }
+    \label{fig:depth-types}
+\end{figure*}
+
 The depth of the point sources can be chosen following different criteria.

### 2020-02-12 manuscript/manuscript.tex
Add extra lines to figure caption
Improve Green's function section

@@
 
-The fundamental solution $\psi$ \citep[p.~210]{vladimirov1979} of the harmonic
-field $V$ must satisfy:
+Considering as boundary condition that $V$ is equal to zero at infinity, then
+its fundamental solution $\psi$ (also known as Green's function or radial basis
+function) must satisfy \citep[p.~210]{vladimirov1979}:
 
@@
     \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
-        - 4\pi \delta(\mathbf{p}, \mathbf{q})
+        - 4\pi \delta(\mathbf{p}, \mathbf{q}),
 \end{equation}
@@
 \noindent where $\delta(\mathbf{p}, \mathbf{q})$ is the Dirac's delta function
-and $\nabla_\mathbf{p}$ symbolize the Nabla operator applied on the
-coordinates $\mathbf{p}$.
+and $\nabla_\mathbf{p}$ symbolize the Nabla operator applied on the coordinates
+$\mathbf{p}$.
 
-Assuming that $\psi$ tends to zero when approaching to infinity as boundary
-condition, the fundamental solution of any harmonic field can be obtained as
-follows \citep{blakely1995}:
+The fundamental solution of any harmonic field can be obtained as follows
+\citep{blakely1995}:
 
@@
 This shows that the Green's function associated with any harmonic field is
-equal to the inverse of the Cartesian distance between the evaluation and the
+equal to the inverse of the Euclidean distance between the evaluation and the
 source points.
@@
         A source point is located beneath each block-median coordinate (c).
+        The number of point sources could be less or equal to the number of
+        observation points.
+        No source is located beneath unpopulated blocks.
     }

### 2020-02-13 manuscript/manuscript.tex
Fix typo
Editing Source distributions section

@@
 
-Now we can define the misfit function as the sum between the data misift and
+Now we can define the misfit function as the sum between the data misfit and
 the Tikhonov regularization function:
@@
 
-The choice of a source distribution is not trivial and plays an important role
-on the accuracy of the predictions.
+How to choose how many sources will be used and where to locate them are not
+trivial decisions and play an important role on the accuracy of the predictions
+and the computational resources needed to fit the sources' coefficients.
+
+The chosen distribution of sources should be reproduce the
+measured data on the survey points and simultaneously be able to make accurate
+predictions of the measured harmonic field on non observed locations.
+
+A high number of sources scattered on the survey region is capable of
+reproducing the observed data. Nevertheless, too many sources will make the
+Jacobian matrix too large. This could introduce computational problems: like
+the inability of storing the matrix on memory or increasing the computational
+time needed to fit the sources' coefficients.
+On the other hand, using very few sources will undoubtedly reduce the memory
+needs and lower the computational time when fitting the sources' coefficients.
+Nevertheless, it could be incapable of making accurate predictions and even
+reproducing the measured data if the number of sources is too low.
 

### 2020-02-14 manuscript/manuscript.tex
Improve EQL implementation and add references

@@
 \usepackage{fancyhdr}
+
+% Define inverse symbol with shorter minus
+\newcommand{\inv}{^{\text{-}1}}
 
@@
 \begin{equation}
-    V(\mathbf{p}) = \mathbf{A} \mathbf{c}
+    \mathbf{d} = \mathbf{A} \mathbf{c}
     \label{eq:linear-problem}
@@
 
-\noindent where $V(\mathbf{p}$) is a vertical vector containing the measured
+\noindent where $\mathbf{d}$ is a vertical vector containing the measured
 values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
@@
 
-It solves equation~\ref{eq:linear-problem} by a least-squares fit, with
-the option of adding a zeroth-order Tikhonov \citep{tikhonov} regularization
-through a dimensionless \emph{damping} parameter.
-This is achieved by scaling the Jacobian matrix so each column has unit
-variance.
+It solves equation~\ref{eq:linear-problem} through least squares with
+a zeroth-order Tikhonov \citep{tikhonov1977} regularization in order to
+stabilize the solution.
+It consists in minimizing the misfit function:
 
-Define a diagonal matrix $S$, whose elements corresponds to the standard
-deviation of each column of the Jacobian matrix $\mathbf{A}$:
+\begin{equation}
+    \phi(\mathbf{c}) =
+        \left\lVert
+            \mathbf{d} - \mathbf{A}\mathbf{c}
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
+    \label{eq:misfit-unscaled}
+\end{equation}
+
+\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
+and $\lambda_d$ is a \emph{damping} parameter that has the same dimension as
+the Jacobian matrix elements.
+
+In order to simplify the choice of this parameter we scale the Jacobian matrix
+so each column has unit variance.
+We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
+standard deviation of each column of the Jacobian matrix $\mathbf{A}$:
 
@@
         0 & \cdots & \sigma_M
-    \end{bmatrix}.
+    \end{bmatrix}
+    ,
 \end{equation}
 
-Equation~\ref{eq:linear-problem} can be written as:
+\noindent so equation~\ref{eq:linear-problem} can be written as:
 
 \begin{equation}
-    V(\mathbf{p})
+    \mathbf{d}
     =
-    \mathbf{A} \mathbf{S}^{-1} \mathbf{S} \mathbf{c}
+    \mathbf{A} \mathbf{S}\inv \mathbf{S} \mathbf{c}
     =
     \left[
-        \mathbf{A} \mathbf{S}^{-1}
+        \mathbf{A} \mathbf{S}\inv
     \right]
@@
     =
-    \mathbf{A_s} \mathbf{c_s}
+    \hat{\mathbf{A}} \hat{\mathbf{c}}
 \end{equation}
 
-\noindent where $\mathbf{A_s}$ the scaled Jacobian matrix and $\mathbf{c_s}$ is
-a vector containing scaled coefficients.
+\noindent where $\hat{\mathbf{A}}$ is the scaled Jacobian matrix and
+$\hat{\mathbf{c}}$ is a vector containing scaled coefficients.
 
-Now we can define the misfit function as the sum between the data misfit and
-the Tikhonov regularization function:
+The misfit function defined on equation~\ref{eq:misfit-unscaled} can be then
+rewritten as follows:
 
 \begin{equation}
-    \phi(\mathbf{c'}) =
-        \left\lVert V(\mathbf{p}) - \mathbf{A_s}\mathbf{c_s} \right\rVert ^ 2
-        + \lambda \left\lVert \mathbf{c_s} \right\rVert ^2,
+    \phi(\hat{\mathbf{c}}) =
+        \left\lVert \mathbf{d}
+        - \hat{\mathbf{A}}\hat{\mathbf{c}} \right\rVert ^ 2
+        + \lambda \left\lVert \hat{\mathbf{c}} \right\rVert ^2,
     \label{eq:misfit}
@@
 
-\noindent where $\lambda$ is a dimensionless damping parameter.
+\noindent where now $\lambda$ is a \emph{dimensionless} damping parameter.
 
-After solving the least squares problem, we obtain the set of scaled
-coefficients $\mathbf{c_s}$ that minimizes equation~\ref{eq:misfit}.
-We can get the corresponding coefficients $\mathbf{c}$ by rescaling
-$\mathbf{c_s}$:
+Misfit function from equation~\ref{eq:misfit} is solved through least squares.
+If the number of observation points is equal or larger to the number of
+sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
+well- or over-determined, respectively. Therefore, the scaled coefficients that
+minimize the misfit function can be obtained through \citep{menke1989}:
 
 \begin{equation}
-    \mathbf{c} = \mathbf{S}^{-1} \mathbf{c_s}.
+    \hat{\mathbf{c}}_\text{est} =
+        \left[
+            \hat{\mathbf{A}}^\text{T} \hat{\mathbf{A}}
+            + \lambda^2 \mathbf{I}
+        \right]\inv
+        \hat{\mathbf{A}}^\text{T}
+        \mathbf{d}.
+\end{equation}
+
+On the other hand, if there are more sources than observation points, the
+problem is under-determined and the scaled coefficients can be obtained as
+\citep{menke1989}:
+
+\begin{equation}
+    \hat{\mathbf{c}}_\text{est} =
+    \hat{\mathbf{A}}^\text{T}
+        \left[
+            \hat{\mathbf{A}} \hat{\mathbf{A}}^\text{T}
+            + \lambda^2 \mathbf{I}
+        \right]\inv
+        \mathbf{d}.
+\end{equation}
+
+Once the scaled coefficients are obtained, the sources coefficients
+$\mathbf{c}_\text{est}$ can be obtained by rescaling
+$\hat{\mathbf{c}}_\text{est}$:
+
+\begin{equation}
+    \mathbf{c}_\text{est} = \mathbf{S}\inv \hat{\mathbf{c}}_\text{est}.
 \end{equation}

### 2020-02-17 manuscript/manuscript.tex
Improve some text

@@
 \noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
-and $\lambda_d$ is a \emph{damping} parameter that has the same dimension as
-the Jacobian matrix elements.
+and $\lambda_d$ is a \emph{damping} parameter with the same units as the
+Jacobian matrix elements.
 
@@
 
-Misfit function from equation~\ref{eq:misfit} is solved through least squares.
+Misfit function from equation~\ref{eq:misfit} is minimized through Cholesky
+decomposition.
 If the number of observation points is equal or larger to the number of
@@
 
-Once the scaled coefficients are obtained, the sources coefficients
+Once the scaled coefficients are obtained, the sources' coefficients
 $\mathbf{c}_\text{est}$ can be obtained by rescaling

### 2020-02-17 manuscript/manuscript.tex
Fix some writing

@@
 
-How to choose how many sources will be used and where to locate them are not
-trivial decisions and play an important role on the accuracy of the predictions
-and the computational resources needed to fit the sources' coefficients.
+How to choose how many sources to use and where to locate them are not
+trivial decisions which play an important role on the accuracy of the
+predictions and the computational resources needed to fit the sources'
+coefficients.
 
-The chosen distribution of sources should be reproduce the
-measured data on the survey points and simultaneously be able to make accurate
+The chosen distribution of sources should reproduce the measured data on the
+survey points and simultaneously be able to make accurate
 predictions of the measured harmonic field on non observed locations.

### 2020-02-17 manuscript/manuscript.tex
Rename block-median to block averaged

@@
 We propose a new source distribution that could simultaneously solve the
-problems of the preceding ones: the \emph{block-median sources}.
+problems of the preceding ones: the \emph{block averaged sources}.
 It consist in dividing the region in blocks of equal size, computing the median
 location of the observation points that fall inside each block, and putting one
-point source bellow this block-median coordinate.
-It creates one point source beneath each populated block, solving the problem
+point source bellow this block averaged coordinate
+(fig.~\ref{fig:block-median-sources}).
+It creates one source beneath each populated block, solving the problem
 of the \emph{grid sources} layout, but also reducing the number of point
@@
     \caption{
-        Block-median sources. Given a set of observation points (a) we divide
+        Block averaged sources. Given a set of observation points (a) we divide
         the survey region on blocks of equal size (b) and compute the median
         location of the observation points that fall inside each block.
-        A source point is located beneath each block-median coordinate (c).
+        A source point is located beneath each block averaged coordinate (c).
         The number of point sources could be less or equal to the number of
@@
     }
-    \label{fig:depth-types}
+    \label{fig:block-median-sources}
 \end{figure*}
@@
 One possible solution is to locate each source bellow its corresponding
-observation point or block-median point at a constant \emph{relative depth}
+observation point or block averaged point at a constant \emph{relative depth}
 from it.
 The sources won't be all at the same depth, but they will all be at the same
-distance from their corresponding observation point (or block-median point).
+distance from their corresponding observation point (or block averaged point).
 It worth mention that this approach could not be applied to \emph{grid
@@
 \noindent where \emph{data point height} is the elevation of the corresponding
-observation (or block-median) point to the source, \emph{depth factor} and
+observation (or block averaged) point to the source, \emph{depth factor} and
 \emph{relative depth} are parameters and \emph{mean distance} is the mean
@@
     \begin{tabular}{lccc}
-        & Source bellow data & Block-median sources & Grid sources \\ \hline
+        & Source bellow data & Block averaged sources & Grid sources \\ \hline
         Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\

### 2020-02-17 manuscript/manuscript.tex
Add description of surveys

@@
 reproducing the observed data. Nevertheless, too many sources will make the
-Jacobian matrix too large. This could introduce computational problems: like
-the inability of storing the matrix on memory or increasing the computational
+Jacobian matrix too large, what could introduce computational problems like
+the inability of storing the matrix on memory or a high computational
 time needed to fit the sources' coefficients.
@@
 needs and lower the computational time when fitting the sources' coefficients.
-Nevertheless, it could be incapable of making accurate predictions and even
+Nevertheless, it could be incapable of making accurate predictions or even
 reproducing the measured data if the number of sources is too low.
+
+The choice of the source distribution could also depend on the characteristic
+of the survey and how the observation points are distributed on the region.
+
+A ground survey usually consists in observation points located along irregular
+paths plus some possible scattered points. The survey region is usually
+heterogeneously covered, leaving areas without any observation.
+
+On the other hand, an airborne survey consists in observation points located
+along almost straight flight lines. The measurements are usually taken at
+a high frequency, so the observation points along the flight lines are very
+close to each other. This creates an anisotropy on the observation points:
+there are much more observation points along the flight lines directions.
+Airborne surveys homogeneously cover the survey region.
 

### 2020-02-17 manuscript/manuscript.tex
Minor text improvement

@@
 
-The chosen distribution of sources should reproduce the measured data on the
-survey points and simultaneously be able to make accurate
-predictions of the measured harmonic field on non observed locations.
+The chosen distribution of sources should simultaneously reproduce the measured
+data on the survey points and be able to make accurate predictions of the
+measured harmonic field on non observed locations.
 

### 2020-02-17 manuscript/manuscript.tex
Improve source distributions text

@@
 How to choose how many sources to use and where to locate them are not
-trivial decisions which play an important role on the accuracy of the
+trivial decisions that play an important role on the accuracy of the
 predictions and the computational resources needed to fit the sources'
@@
 
-A high number of sources scattered on the survey region is capable of
-reproducing the observed data. Nevertheless, too many sources will make the
-Jacobian matrix too large, what could introduce computational problems like
-the inability of storing the matrix on memory or a high computational
-time needed to fit the sources' coefficients.
+A high number of sources homogeneously distributed on the survey region are
+capable of reproducing the observed data. Nevertheless, too many sources will
+make the Jacobian matrix too large, what could introduce computational problems
+like the inability of storing the matrix on memory or a high computational time
+needed to fit the sources' coefficients.
 On the other hand, using very few sources will undoubtedly reduce the memory
@@
 of the survey and how the observation points are distributed on the region.
-
 A ground survey usually consists in observation points located along irregular
-paths plus some possible scattered points. The survey region is usually
-heterogeneously covered, leaving areas without any observation.
-
+paths plus some possible scattered points.
+The survey region is usually heterogeneously covered, leaving areas without any
+observation.
 On the other hand, an airborne survey consists in observation points located
@@
 a high frequency, so the observation points along the flight lines are very
-close to each other. This creates an anisotropy on the observation points:
-there are much more observation points along the flight lines directions.
-Airborne surveys homogeneously cover the survey region.
+close to each other.
+This creates an anisotropy on the observation points: there are much more
+observation points along the flight lines directions.
 
@@
 bellow the surveyed region.
-It could create too many sources on areas without data and very few ones on
-areas with a high number of observation points, leading to an underfitting of
-the observed data.
-This could be solved by reducing the grid spacing and therefore increasing the
-number of point sources and the computational load of the interpolation
-process.
+The distance between sources is controlled by the grid spacing parameter.
+Keeping the boundaries of the grid constant, reducing the spacing increases the
+number of sources.
 
-The \emph{source beneath data} layout adds sources where they are more needed.
-If the survey is composed by a large number of data points clustered on paths
-(like an airborne survey), putting one source beneath each observation point
-will create an anisotropic source distribution: there will be several sources
-distributed along a privileged direction.
-This could introduce aliases on the predictions and increase the computational
-load for fitting the predictor.
+The \emph{source beneath data} layout locates one source bellow each
+observation point, therefore the number of sources will be equal to the number
+of data points.
 
-We propose a new source distribution that could simultaneously solve the
-problems of the preceding ones: the \emph{block averaged sources}.
-It consist in dividing the region in blocks of equal size, computing the median
-location of the observation points that fall inside each block, and putting one
-point source bellow this block averaged coordinate
-(fig.~\ref{fig:block-median-sources}).
-It creates one source beneath each populated block, solving the problem
-of the \emph{grid sources} layout, but also reducing the number of point
-sources in comparison with the \emph{source beneath data} layout.
+When working with ground surveys, the \emph{regular grid} needs the grid
+spacing to be sufficiently small so observed values can be accurately
+reproduced by the source distribution.
+This will create too many sources on areas where no observation has been
+carried out.
+In contrast, the \emph{source beneath data} layout is more likely to accurately
+fit the observed data with much less sources, reducing the computational load
+to fit the equivalent sources' coefficients.
+
+When working with airborne surveys, the \emph{source beneath data} may
+generate an anisotropic distribution of sources by locating too many sources
+along the flight paths.
+It could lead to unwanted aliases on the predicted values.
+In contrast, the \emph{regular grid} won't generate aliases by homogeneously
+locating sources.
+
+We propose a new source distribution that could simultaneously reduce the
+computational load and remove the drawbacks of the preceding ones: the
+\emph{block averaged sources}.
+It consist in:
+
+\begin{enumerate}
+    \item Dividing the region in blocks of equal size. The size of the blocks
+        is controlled by a \emph{spacing} parameter.
+        (see Fig.~\ref{fig:block-median-sources}(a)-(b)).
+    \item Computing the median location of the observation points that fall
+        inside each block. Blocks without any observation point are ignored.
+    \item Locating one point source bellow each block averaged coordinate.
+        (see Fig.~\ref{fig:block-median-sources}(c)).
+\end{enumerate}
+
+The number of sources created by this new distribution will be less or equal to
+the ones created by the \emph{source beneath data} and the \emph{regular
+grid} with the same spacing.
+Moreover, the sources are only located beneath populated blocks, so sources
+will be concentrated on regions where data has been gathered and no anisotropic
+distribution of sources will be generated.
 
@@
     \caption{
-        Block averaged sources. Given a set of observation points (a) we divide
-        the survey region on blocks of equal size (b) and compute the median
+        Block averaged sources. (a) Given a set of observation points (b) we divide
+        the survey region on blocks of equal size and compute the median
         location of the observation points that fall inside each block.
-        A source point is located beneath each block averaged coordinate (c).
+        (c) A source point is located beneath each block averaged coordinate.
         The number of point sources could be less or equal to the number of
@@
 frequencies (cite).
-The most simple option is to locate all point sources at the same depth, which
-we will call \emph{constant depth} in the future.
+The simplest option is to locate all sources at the same depth, which we will
+call \emph{constant depth} in the future (see Fig.~\ref{fig:depth-types}(a)).
 If the measurement were taken at significantly different altitudes, the
@@
 One possible solution is to locate each source bellow its corresponding
-observation point or block averaged point at a constant \emph{relative depth}
+observation (or block averaged) point at a constant \emph{relative depth}
 from it.
+The depth of each source can be computed as the height of its corresponding
+observation (or block averaged) point minus a depth parameter that assumes the
+same value for all sources (see Fig.~\ref{fig:depth-types}(b)).
 The sources won't be all at the same depth, but they will all be at the same
-distance from their corresponding observation point (or block averaged point).
-It worth mention that this approach could not be applied to \emph{grid
-sources}.
+distance from their corresponding observation (or block averaged) point.
 
-In case our survey presents heavily clustered data points, we may want to
-reduce the depth of the sources bellow that region in order to reproduce the
+In case our survey presents heavily clustered data points on some areas, we may
+want the sources bellow that region to be shallower in order to reproduce the
 high frequencies measured by these clustered observation points.
 We can propose a \emph{variable depth} approach: it locates each point source
-according to the \emph{relative depth} approach and then add a term
-proportional to the mean distance to its $k$ nearest neighbour sources.
+according to the \emph{relative depth} and then subtracts a term proportional
+to the mean distance to its $k$ nearest neighbour sources
+(see Fig.~\ref{fig:depth-types}(c)).
 So, the depth of the sources can be computed as follows:
@@
 distance to the $k$ nearest source neighbours.
+This term will be smaller in case of clustered sources, making them shallower
+than scattered and distant sources.
 
@@
 
+Worth mention that the two last approaches (the \emph{relative depth} and the
+\emph{variable depth}) could not be applied to \emph{grid sources}.
+
 \begin{figure*}
@@
         Depth types for locating point sources. We put one source beneath each
-        observation point (station) using: (a)~a \emph{constant depth} where all sources
-        are located at the same depth, (b)~a \emph{relative depth} where all sources are
-        located at the same vertical distance from its corresponding observation point,
-        and (c)~a \emph{variable relative depth} where the depth of the sources is
-        proportional to the average distance to its neighbour sources. Notice how the
-        clustered sources on (c) are relatively shallower than the other ones.
+        observation point (station) using: (a)~a \emph{constant depth} where
+        all sources are located at the same depth, (b)~a \emph{relative depth}
+        where all sources are located at the same vertical distance from its
+        corresponding observation point, and (c)~a \emph{variable relative
+        depth} where the depth of the sources is proportional to the average
+        distance to its neighbour sources. Notice how the clustered sources on
+        (c) are relatively shallower than the other ones.
     }

### 2020-02-18 manuscript/manuscript.tex
Start improving source distributions comparison

@@
 
-Compare the accuracy of the predictions made by each source distribution.
-Need an objective way to compare them.
-Propose a synthetic gravity model made out of prisms of different sizes and
-density contrasts.
-Create a regular grid of observation points where the gravitational effect of
-the synthetic model will be computed.
-Call it the \emph{target grid}.
-Generate synthetic surveys above the same synthetic model and compute the
-gravitational effect of the model on each survey.
-Use each source distribution to predict values based on the ones obtained on
-each survey onto the same grid points of the \emph{target grid}.
-Score each interpolation by comparing the predicted values with the
-\emph{target grid}.
-Finally compare the accuracy of the predictions made by each source
-distribution.
+%Compare the accuracy of the predictions made by each source distribution.
+%Need an objective way to compare them.
+%Propose a synthetic gravity model made out of prisms of different sizes and
+%density contrasts.
+%Create a regular grid of observation points where the gravitational effect of
+%the synthetic model will be computed.
+%Call it the \emph{target grid}.
+%Generate synthetic surveys above the same synthetic model and compute the
+%gravitational effect of the model on each survey.
+%Use each source distribution to predict values based on the ones obtained on
+%each survey onto the same grid points of the \emph{target grid}.
+%Score each interpolation by comparing the predicted values with the
+%\emph{target grid}.
+%Finally compare the accuracy of the predictions made by each source
+%distribution.
+
+Our goal is to to compare the performance of all source distributions from
+Table~\ref{tab:source-distributions} when predicting harmonic field data using
+the equivalent layer technique.
+To do so we have created a synthetic model made out of prisms of different
+shape and density contrasts.
+The gravitational effect of this synthetic model have been computed on two
+different set of observation points that we will call \emph{synthetic surveys}:
+a ground and an airborne survey.
+Its effect have also been computed on a regular grid at a constant height which
+we will use as the \emph{target} values of the harmonic field.
+Then the data from each synthetic survey is interpolated on the same grid
+points as the \emph{target} grid using each source
+distribution with different sets of parameters.
+Each prediction is then scored against the \emph{target} grid and keep the one
+that achieves the highest score.
+We can then quantitatively compare how accurate is each source distribution at
+predicting unobserved data on each synthetic survey and quantify the
+computational load needed to do it.
 
@@
 
-Describe forward model made out of prisms.
-Show prisms model?
+%Describe forward model made out of prisms.
+%Show prisms model?
+
+The synthetic model is made out of \textbf{number} number of prisms distributed
+on a region of 100km$\times$100km between 10km deep and surface level.
 

### 2020-02-18 manuscript/manuscript.tex
Start writing Synthetic Model section

@@
 \usepackage{graphicx}
+\usepackage{siunitx}
 \usepackage[round]{natbib}
@@
 The synthetic model is made out of \textbf{number} number of prisms distributed
-on a region of 100km$\times$100km between 10km deep and surface level.
+on a region of \SI{100}{\km}$\times$\SI{100}{\km} between \SI{10}{\km} deep and
+the zero height plane.
+Density of prisms range from \SI{-900}{\kg\per\cubic\m} and
+\SI{500}{\kg\per\cubic\m}.
+We created deep big and thin shallow prisms for creating gravity anomalies with
+long and short wavelengths, respectively.
+
+The gravitational effect of the synthetic model has been computed on a regular
+grid of 56$\times$57 points with a spacing of \SI{2}{\km} located
+\SI{2000}{\m} above the zero height plane (Fig.~\ref{fig:target-grid}).
+We will refer to this grid as the \emph{target} grid in the future.
+
+\begin{figure*}
+    %\includegraphics[width=\linewidth]{}
+    \caption{
+        Target grid. Gravitational effect of synthetic model on a regular grid
+        composed of 56$\times$57 points with a spacing of \SI{2}{\km} located
+        \SI{2000}{\m} above the zero height plane.
+    }
+    \label{fig:target-grid}
+\end{figure*}
 

### 2020-02-18 manuscript/manuscript.tex
Specify number of prisms on synthetic model

@@
 
-The synthetic model is made out of \textbf{number} number of prisms distributed
-on a region of \SI{100}{\km}$\times$\SI{100}{\km} between \SI{10}{\km} deep and
-the zero height plane.
+The synthetic model is made out of 64 prisms distributed on a region of
+\SI{100}{\km}$\times$\SI{100}{\km} between \SI{10}{\km} deep and the zero
+height plane.
 Density of prisms range from \SI{-900}{\kg\per\cubic\m} and

### 2020-02-18 manuscript/manuscript.tex
Make target grid figure on single column
Replace variable depth on table and fig caption

@@
         where all sources are located at the same vertical distance from its
-        corresponding observation point, and (c)~a \emph{variable relative
-        depth} where the depth of the sources is proportional to the average
-        distance to its neighbour sources. Notice how the clustered sources on
-        (c) are relatively shallower than the other ones.
+        corresponding observation point, and (c)~a \emph{variable depth} where
+        the depth of the sources is proportional to the average distance to its
+        neighbour sources. Notice how the clustered sources on (c) are
+        relatively shallower than the other ones.
     }
@@
         Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
-        Variable relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
+        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
     \end{tabular}
@@
 
-\begin{figure*}
+\begin{figure}
     %\includegraphics[width=\linewidth]{}
@@
     \label{fig:target-grid}
-\end{figure*}
+\end{figure}
 

### 2020-02-18 manuscript/manuscript.tex
Improve figure captions

@@
     \caption{
-        Block averaged sources. (a) Given a set of observation points (b) we divide
-        the survey region on blocks of equal size and compute the median
-        location of the observation points that fall inside each block.
-        (c) A source point is located beneath each block averaged coordinate.
+        Block averaged sources.
+        (a)~Given a set of observation points
+        (b)~we divide the survey region on blocks of equal size and compute the
+            median location of the observation points that fall inside each
+            block.
+        (c)~A source point is located beneath each block averaged coordinate.
             The number of point sources could be less or equal to the number of
-        observation points.
-        No source is located beneath unpopulated blocks.
+            observation points. No source is located beneath unpopulated
+            blocks.
     }
@@
         Depth types for locating point sources. We put one source beneath each
-        observation point (station) using: (a)~a \emph{constant depth} where
-        all sources are located at the same depth, (b)~a \emph{relative depth}
-        where all sources are located at the same vertical distance from its
-        corresponding observation point, and (c)~a \emph{variable depth} where
-        the depth of the sources is proportional to the average distance to its
-        neighbour sources. Notice how the clustered sources on (c) are
-        relatively shallower than the other ones.
+        observation point (station) using:
+        (a)~a \emph{constant depth} where all sources are located at the same
+           depth,
+        (b)~a \emph{relative depth} where all sources are located at the same
+           vertical distance from its corresponding observation point, and
+        (c)~a \emph{variable depth} where the depth of the sources is
+           proportional to the average distance to its neighbour sources.
+           Notice how the clustered sources on (c) are relatively shallower
+           than the
+           other ones.
     }

### 2020-02-18 manuscript/manuscript.tex
Write description of synthetic model and surveys

@@
 \usepackage{fancyhdr}
+
+% Define special units
+\DeclareSIUnit\mgal{\milli Gal}
 
@@
 shape and density contrasts.
-The gravitational effect of this synthetic model have been computed on two
-different set of observation points that we will call \emph{synthetic surveys}:
-a ground and an airborne survey.
-Its effect have also been computed on a regular grid at a constant height which
-we will use as the \emph{target} values of the harmonic field.
-Then the data from each synthetic survey is interpolated on the same grid
-points as the \emph{target} grid using each source
-distribution with different sets of parameters.
-Each prediction is then scored against the \emph{target} grid and keep the one
-that achieves the highest score.
+The gravitational effect of this synthetic model have been computed on
+a regular grid (\emph{target} grid) at a constant height and on two different
+set of observation points that we will call \emph{synthetic surveys}: a ground
+and an airborne survey.
+The data from each synthetic survey is interpolated on the points of the
+\emph{target} grid.
+The interpolations are carried out using each source distribution and combining
+different parameter values for each distribution.
+Each prediction is then scored against the \emph{target} grid.
 We can then quantitatively compare how accurate is each source distribution at
@@
 The synthetic model is made out of 64 prisms distributed on a region of
-\SI{100}{\km}$\times$\SI{100}{\km} between \SI{10}{\km} deep and the zero
+\SI{89}{\km}$\times$\SI{88}{\km} between \SI{10}{\km} deep and the zero
 height plane.
-Density of prisms range from \SI{-900}{\kg\per\cubic\m} and
+Density contrast of prisms range from \SI{-900}{\kg\per\cubic\m} and
 \SI{500}{\kg\per\cubic\m}.
@@
 
-The gravitational effect of the synthetic model has been computed on a regular
-grid of 56$\times$57 points with a spacing of \SI{2}{\km} located
-\SI{2000}{\m} above the zero height plane (Fig.~\ref{fig:target-grid}).
+The vertical component of the gravity acceleration generated by the synthetic
+model has been computed on a regular grid of 56$\times$57 points with a spacing
+of \SI{2}{\km} located \SI{2000}{\m} above the zero height plane
+(Fig.~\ref{fig:target-grid}).
 We will refer to this grid as the \emph{target} grid in the future.
@@
 
-Create synthetic surveys to produce observation points.
-In order to compare each source layout under very different set of observation
-points we create a ground and an airborne synthetic surveys.
-We selected a portion of the Southern Africa Gravity Data obtained by Dr. R.J.
-Kleywegt et al.\ and made available through the NOAA website
-(\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}) for creating
-a synthetic ground survey.
-We selected a portion of the Great Britain Aeromagnetic Survey acquired by
-Hunting Geology and Geophysics Ltd and Canadian Aeroservices Ltd between 1955
-and 1965 and made available by the
-\href{
-    https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html
-    }{
+In order to compare the predictive capabilities of each source distribution
+under on different surveys, we created a ground and an airborne \emph{synthetic
+surveys}.
+For creating the synthetic ground survey we selected a portion of the Southern
+Africa Gravity Data available through the
+\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
+For the airborne survey we used a portion of the Great Britain Aeromagnetic
+Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
+Ltd between 1955 and 1965 and made available by the
+\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
 British Geological Survey (BGS)
+}.
+
+On both cases we selected only a portion of the survey and rescaled it to span
+on an area of \SI{111}{\km}$\times$\SI{111}{\km}.
+The ground survey is composed by 963 observation points distributed at heights
+ranging between \SI{0}{\m} and \SI{2052}{\m}
+(Fig.~\ref{fig:synthetic-ground-survey}(a)).
+While the airborne survey has 5673 points at heights between \SI{359}{\m} and
+\SI{1255}{\m}.
+(Fig.~\ref{fig:synthetic-ground-survey}(a)).
+
+The vertical component of the gravity acceleration generated by the synthetic
+model has been computed on both surveys.
+Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
+to the effect of the synthetic model to simulate acquisition errors.
+(Figs.~\ref{fig:synthetic-ground-survey}(b)
+and~\ref{fig:synthetic-airborne-survey}(b)).
+
+\begin{figure}
+    %\includegraphics[width=\linewidth]{}
+    \caption{
+        Synthetic ground survey.
+        (a)~Location of observation points.
+        (b)~Vertical component of gravity acceleration generated by the
+            synthetic model plus Gaussian noise on the airborne survey
+            observation points.
     }
-, for creating a synthetic airborne survey.
+    \label{fig:synthetic-ground-survey}
+\end{figure}
 
-The gravitation effect of the synthetic model has been computed on both surveys
-and added Gaussian noise (standard deviation of 1mGal) to simulate acquisition
-errors.
+\begin{figure}
+    %\includegraphics[width=\linewidth]{}
+    \caption{
+        Synthetic airborne survey.
+        (a)~Location of observation points.
+        (b)~Vertical component of gravity acceleration generated by the
+            synthetic model plus Gaussian noise on the airborne survey
+            observation points.
+        Based upon the Great Britain aeromagnetic data, with the permission of
+        the British Geological Survey.
+    }
+    \label{fig:synthetic-airborne-survey}
+\end{figure}
 
@@
 
-%Describe the target grid. Show target grid figure.
 %Describe the parameters used for each source distribution, how do we score
 %each interpolation.
-%Describe the Harmonica implementation of the EQL.
 %Show results.
@@
 
+The synthetic airborne survey was based upon the Great Britain aeromagnetic
+data, reproduced with the permission of the British Geological Survey
+$\textcopyright$UKRI\@.
+All rights Reserved.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-02-18 manuscript/manuscript.tex
Remove unwanted dot

@@
 Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
-to the effect of the synthetic model to simulate acquisition errors.
+to the effect of the synthetic model to simulate acquisition errors
 (Figs.~\ref{fig:synthetic-ground-survey}(b)

### 2020-02-21 manuscript/manuscript.tex
Change case on acknowledgements
Remove minipage from tabular
Add manuscript (#19)
Start writing manuscript. Add BiBTeX references file. Add and/or improve
notebooks for creating schematic figures of source distributions and depth
types.

@@
 \begin{table*}
-\begin{minipage}{80mm}
+    \centering
     \caption{
@@
     \end{tabular}
-\end{minipage}
 \end{table*}
@@
 
-%Describe the parameters used for each source distribution, how do we score
-%each interpolation.
-%Show results.
+Each source distribution from Table~\ref{tab:source-distributions} needs
+certain parameters in order to build the set of point sources.
+The prediction capabilities of the source distribution depends on the choice of
+these parameters.
+For example, locating the sources beneath the data points at constant depth
+needs the definition of the \emph{depth} parameter.
+If the sources are set too close to the data points, the source distribution
+it's very likely to overfit the data: the measured field will be recovered, but
+the predictions on unobserved locations will be very inaccurate.
+Another parameter that plays an important role on the predictive capabilities
+of the sources is the damping parameter.
+On real world scenarios, choosing the values of the parameters is a challenging
+task: it's not easy to determine the accuracy of the predictions without
+knowing the true value of the field on unobserved locations.
+This problem can be solved through cross-validation.
+When working with a synthetic model, the situation is different: we can compute
+the true values of harmonic field generated by the synthetic model on any
+point.
+Therefore, interpolating the observed data on the same points of the
+\emph{target} grid and then scoring the prediction against the true values of
+the \emph{target} grid constitutes an objective way to measure the predictive
+accuracy of the source distribution.
 
-Compute the gravitational effect of the synthetic model on a regular grid of
-points located at the same height.
-This will be called our \emph{target grid}.
-We will use it to compute the accuracy of the predictions made by each source
-distribution.
-
-Take a source distribution, fit the source coefficients and then use them to
-predict data on the grid points where the \emph{target grid} is defined.
-Define prediction error as the difference between the predicted values and the
-\emph{target grid}.
-
-Each source distribution has parameters that need to be specified before
-fitting its coefficients.
-For example, the \emph{grid of sources} needs the depth at which the sources
-will be located.
-The damping parameter used on the fitting process must also be specified
-beforehand.
-These parameters play an important role on the accuracy of the prediction.
-We compute several predictions made by the same source distribution, but with
-different values for its parameters.
-Then we score each interpolation by computing the R$^2$ between each prediction
-and the target grid.
-We keep the best prediction, i.e.\ the one that has the highest R$^2$ score.
+For each source distribution we proposed different values for each parameter
+(including the damping) and combined them into several parameters sets.
+For each parameter set we build the sources and fit their coefficients through
+least-squares.
+Then the sources are used to predict the field on the same points of the
+\emph{target} grid and finally we compute the coefficient of determination
+(R$^2$ score) between the prediction and the true values of the \emph{target}
+grid.
+We can therefore obtain the \emph{best prediction} generated by each source
+distribution as the one that achieves the highest score.
 
@@
 $\textcopyright$UKRI\@.
-All rights Reserved.
+All rights reserved.
 

### 2020-02-21 notebooks/block-median-schematics.py

@@ -1,0 +1,142 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:light
+#     text_representation:
+#       extension: .py
+#       format_name: light
+#       format_version: '1.5'
+#       jupytext_version: 1.3.2
+#   kernelspec:
+#     display_name: Python [conda env:eql_source_layouts]
+#     language: python
+#     name: conda-env-eql_source_layouts-py
+# ---
+
+# # Schematic figure of block-median sources
+
+# Import packages
+
+# +
+import os
+import numpy as np
+import verde as vd
+import matplotlib.pyplot as plt
+
+from eql_source_layouts import block_median_sources
+
+# -
+
+# Define parameters
+
+# +
+region = (-50e3, 50e3, -50e3, 50e3)
+
+n_data = 30
+spacing = 25000
+seed = 1234
+height = 1000
+depth = 100
+# -
+
+# Create random observation points
+
+coordinates = vd.scatter_points(
+    region, size=n_data, random_state=seed, extra_coords=height
+)
+
+# Create block-median sources
+
+points = block_median_sources(
+    coordinates, constant_depth=depth, spacing=spacing, depth_type="constant_depth"
+)
+
+# Create grid lines
+
+# +
+grid_nodes = vd.grid_coordinates(vd.get_region(coordinates), spacing=spacing)
+
+grid_lines = (np.unique(grid_nodes[0]), np.unique(grid_nodes[1]))
+for nodes in grid_lines:
+    nodes.sort()
+# -
+
+# Plot figure
+
+# +
+# Load matplotlib configuration
+plt.style.use(os.path.join("..", "matplotlib.rc"))
+
+# Boundaries of the grid
+xmin, xmax, ymin, ymax = vd.get_region(coordinates)
+
+# Define styles and axes labels
+grid_style = dict(color="grey", linewidth=1, linestyle="--")
+scatter_style = dict(s=12)
+labels = "a b c".split()
+
+# Initialize figure and axes
+width = 6.66
+height = width / 3 * 1.1
+fig, axes = plt.subplots(
+    ncols=3, nrows=1, sharey=True, sharex=True, figsize=(width, height)
+)
+
+# Plot coordinates
+ax = axes[0]
+coords_scatter = ax.scatter(
+    *coordinates[:2], label="observation points", **scatter_style
+)
+
+# Plot coordinates and grid
+ax = axes[1]
[…]

### 2020-02-21 notebooks/depth-types-schematics.py

@@ -13,6 +13,10 @@
 #     name: conda-env-eql_source_layouts-py
 # ---
 
+# # Schematic figure of depth types
+
+# Import packages
+
 # +
 from IPython.display import display
 import os
@@ -24,10 +28,16 @@ from eql_source_layouts.layouts import source_bellow_data
 
 # -
 
+# Read a synthetic 1d survey
+
 survey = pd.read_csv(os.path.join("..", "data", "survey_1d.csv"))
 display(survey)
 
+# ## Create source distributions
+
 points = {}
+
+# Source beneath data with constant depth
 
 # +
 depth_type = "constant_depth"
@@ -37,6 +47,9 @@ points[depth_type] = source_bellow_data(coordinates, depth_type=depth_type, dept
 plt.scatter(coordinates[0], coordinates[2])
 plt.scatter(points[depth_type][0], points[depth_type][2])
 plt.show()
+# -
+
+# Source beneath data with relative depth
 
 # +
 depth_type = "relative_depth"
@@ -46,6 +59,9 @@ points[depth_type] = source_bellow_data(coordinates, depth_type=depth_type, dept
 plt.scatter(coordinates[0], coordinates[2])
 plt.scatter(points[depth_type][0], points[depth_type][2])
 plt.show()
+# -
+
+# Source beneath data with variable depth
 
 # +
 depth_type = "variable_depth"
@@ -58,13 +74,20 @@ plt.scatter(coordinates[0], coordinates[2])
 plt.scatter(points[depth_type][0], points[depth_type][2])
 plt.show()
 # +
+# Load matplotlib configuration
 plt.style.use(os.path.join("..", "matplotlib.rc"))
-fig, axes = plt.subplots(ncols=3, nrows=1, sharey=True, figsize=(6.66, 2), dpi=300)
+
+# Initialize figure and axes
+width = 6.66
+height = 1.5
+fig, axes = plt.subplots(ncols=3, nrows=1, sharey=True, figsize=(width, height))
+
+# Define styles and axes labels and titles
 size = 8
-
 titles = ["Constant Depth", "Relative Depth", "Variable Depth"]
-labels = "(a) (b) (c)".split()
+labels = "a b c".split()
 
+# Plot
 for i, (ax, depth_type, title, label) in enumerate(zip(axes, points, titles, labels)):
     ax.scatter(coordinates[0], coordinates[2], s=size, label="stations", marker="^")
[…]

### 2020-02-21 notebooks/01-synthetic-surveys.py
Create target grid figure

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.3
+#       jupytext_version: 1.3.2
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -178,3 +178,32 @@ target = grid_to_dataarray(target, grid, attrs={"height": target_grid_height})
 # Save target grid to disk for future usage
 
 target.to_netcdf(os.path.join(results_dir, "target.nc"))
+
+# +
+# Load matplotlib configuration
+plt.style.use(os.path.join("..", "matplotlib.rc"))
+
+width = 3.33
+figsize = (width, width * 0.85)
+fig, ax = plt.subplots(figsize=figsize)
+
+tmp = target.plot.pcolormesh(
+    ax=ax, add_colorbar=False, cmap="viridis", center=False, rasterized=True
+)
+ax.set_aspect("equal")
+ax.ticklabel_format(axis="both", style="sci", scilimits=(0, 0))
+# ax.xaxis.set_label_position('top')
+# ax.xaxis.tick_top()
+ax.set_xlabel(ax.get_xlabel() + " [m]")
+ax.set_ylabel(ax.get_ylabel() + " [m]")
+clb = plt.colorbar(tmp, ax=ax, shrink=1, orientation="vertical", pad=0.03, aspect=30)
+clb.set_label("mGal", labelpad=-15, y=1.05, rotation=0)
+
+plt.tight_layout()
+plt.savefig(
+    os.path.join("..", "manuscript", "figs", "target-grid.pdf"),
+    bbox_inches="tight",
+    dpi=300,
+)
+plt.show()
+# -

### 2020-02-21 notebooks/01-synthetic-surveys.py
Add survey figures

@@ -121,6 +121,54 @@ survey[field] = hm.prism_gravity(
 ) + np.random.normal(scale=noise_std, size=survey.easting.size)
 display(survey)
 
+# +
+# Load matplotlib configuration
+plt.style.use(os.path.join("..", "matplotlib.rc"))
+
+# Define useful parameters
+width = 3.33
+figsize = (width, width * 1.5)
+cbar_shrink = 0.9
+size = 2
+
+# Initialize figure and axes
+fig, (ax1, ax2) = plt.subplots(ncols=1, nrows=2, sharex=True, figsize=figsize)
+
+# Plot survey points
+tmp = ax1.scatter(
+    survey.easting, survey.northing, c=survey.height, cmap="cividis", s=size
+)
+clb = plt.colorbar(
+    tmp, ax=ax1, shrink=cbar_shrink, orientation="vertical", pad=0.03, aspect=30
+)
+clb.set_label("m", labelpad=-15, y=1.05, rotation=0)
+
+# Plot measured values
+tmp = ax2.scatter(survey.easting, survey.northing, c=survey.g_z, cmap="viridis", s=size)
+clb = plt.colorbar(
+    tmp, ax=ax2, shrink=cbar_shrink, orientation="vertical", pad=0.03, aspect=30
+)
+clb.set_label("mGal", labelpad=-15, y=1.05, rotation=0)
+
+ax2.set_xlabel("easting [m]")
+ax1.tick_params(
+    axis="x", which="both", bottom=False, top=False, labelbottom=False,
+)
+
+for ax in (ax1, ax2):
+    ax.set_aspect("equal")
+    ax.ticklabel_format(axis="both", style="sci", scilimits=(0, 0))
+    ax.set_ylabel("northing [m]")
+
+plt.tight_layout(h_pad=0)
+plt.savefig(
+    os.path.join("..", "manuscript", "figs", "ground-survey.pdf"),
+    bbox_inches="tight",
+    dpi=300,
+)
+plt.show()
+# -
+
 # Save ground survey for future usage
 
 survey.to_csv(os.path.join(ground_results_dir, "survey.csv"), index=False)
@@ -155,6 +203,54 @@ survey[field] = hm.prism_gravity(
     coordinates, model["prisms"], model["densities"], field=field
 ) + np.random.normal(scale=noise_std, size=survey.easting.size)
 display(survey)
+
+# +
+# Load matplotlib configuration
[…]

### 2020-02-21 manuscript/manuscript.tex
Create target grid figure
Add survey figures
Add LaTeX variables file for synthetic model and surveys
Add single file created by the 01-synthetic-surveys.py notebook where
all quantities related to synthetic model and surveys live.
Import them into the manuscript.

@@
 \newcommand{\inv}{^{\text{-}1}}
+
+% Import files with parameter values generated by notebooks
+\input{synthetic_model_surveys.tex}
 
@@
 
-The synthetic model is made out of 64 prisms distributed on a region of
-\SI{89}{\km}$\times$\SI{88}{\km} between \SI{10}{\km} deep and the zero
+The synthetic model is made out of \NPrisms prisms distributed on a region of
+\ModelEasting$\times$\ModelNorthing between \ModelDepth deep and the zero
 height plane.
-Density contrast of prisms range from \SI{-900}{\kg\per\cubic\m} and
-\SI{500}{\kg\per\cubic\m}.
+Density contrast of prisms range from \ModelMinDensity and \ModelMaxDensity.
 We created deep big and thin shallow prisms for creating gravity anomalies with
@@
 The vertical component of the gravity acceleration generated by the synthetic
-model has been computed on a regular grid of 56$\times$57 points with a spacing
-of \SI{2}{\km} located \SI{2000}{\m} above the zero height plane
+model has been computed on a regular grid of
+\TargetEastingSize$\times$\TargetNorthingSize points with a spacing of
+\TargetSpacing located \TargetHeight above the zero height plane
 (Fig.~\ref{fig:target-grid}).
@@
 \begin{figure}
-    %\includegraphics[width=\linewidth]{}
+    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
     \caption{
         Target grid. Gravitational effect of synthetic model on a regular grid
-        composed of 56$\times$57 points with a spacing of \SI{2}{\km} located
-        \SI{2000}{\m} above the zero height plane.
+        composed of \TargetEastingSize$\times$\TargetNorthingSize points with
+        a spacing of \TargetSpacing located \TargetHeight above the zero height
+        plane.
     }
@@
 On both cases we selected only a portion of the survey and rescaled it to span
-on an area of \SI{111}{\km}$\times$\SI{111}{\km}.
-The ground survey is composed by 963 observation points distributed at heights
-ranging between \SI{0}{\m} and \SI{2052}{\m}
+on an area of \SurveyEasting$\times$\SurveyNorthing.
+The ground survey is composed by \GroundSurveyPoints observation points distributed at heights
+ranging between \GroundSurveyMinHeight and \GroundSurveyMaxHeight
 (Fig.~\ref{fig:synthetic-ground-survey}(a)).
-While the airborne survey has 5673 points at heights between \SI{359}{\m} and
-\SI{1255}{\m}.
+While the airborne survey has \AirborneSurveyPoints points at heights between
+\AirborneSurveyMinHeight and \AirborneSurveyMaxHeight.
 (Fig.~\ref{fig:synthetic-ground-survey}(a)).
@@
 model has been computed on both surveys.
-Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
+Some Gaussian noise (with standard deviation of \SurveyNoise) has been added
 to the effect of the synthetic model to simulate acquisition errors
@@
 \begin{figure}
-    %\includegraphics[width=\linewidth]{}
+    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
     \caption{
         Synthetic ground survey.
-        (a)~Location of observation points.
+        (a)~Location of observation points. Altitude given in meters above the
+            zero height plane.
         (b)~Vertical component of gravity acceleration generated by the
@@
 \begin{figure}
-    %\includegraphics[width=\linewidth]{}
+    \includegraphics[width=\linewidth]{figs/airborne-survey.pdf}
     \caption{
         Synthetic airborne survey.
-        (a)~Location of observation points.
+        (a)~Location of observation points. Altitude given in meters above the
+            zero height plane.
         (b)~Vertical component of gravity acceleration generated by the

### 2020-02-26 notebooks/02-grid-ground-data.py
Gridding nb generate LaTeX tables with params

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.2
+#       jupytext_version: 1.3.3
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -30,6 +30,7 @@ from eql_source_layouts import (
     plot_prediction,
     get_best_prediction,
     predictions_to_datasets,
+    latex_parameters_table,
 )
 
 # -
@@ -76,9 +77,7 @@ k_values = [1, 5, 10, 15]
 block_spacings = [1_000, 2_000, 3_000, 4_000]
 # -
 
-# ### Define set of parameters for each source distribution
-#
-# Lets create combinations of parameter values for each source distribution
+# ## Create dictionary with the parameter values for each source distribution
 
 # +
 parameters = {layout: {} for layout in layouts}
@@ -86,17 +85,24 @@ parameters = {layout: {} for layout in layouts}
 # Source bellow data
 layout = "source_bellow_data"
 depth_type = "constant_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
+    depth_type=depth_type, damping=dampings, depth=depths.tolist()
+)
+
+# Source bellow data
+layout = "source_bellow_data"
+depth_type = "constant_depth"
+parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths
 )
 
 depth_type = "relative_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths
 )
 
 depth_type = "variable_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
     depth_type=depth_type,
     damping=dampings,
     depth_factor=depth_factors,
@@ -107,17 +113,17 @@ parameters[layout][depth_type] = combine_parameters(
 # Block-median sources
 layout = "block_median_sources"
 depth_type = "constant_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths, spacing=block_spacings,
 )
 
 depth_type = "relative_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
[…]

### 2020-02-26 notebooks/03-grid-airborne-data.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.2
+#       jupytext_version: 1.3.3
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -36,6 +36,7 @@ from eql_source_layouts import (
     plot_prediction,
     get_best_prediction,
     predictions_to_datasets,
+    latex_parameters_table,
 )
 
 # -
@@ -81,9 +82,7 @@ k_values = [1, 5, 10, 15]
 block_spacings = [1_000, 2_000, 3_000, 4_000]
 # -
 
-# ### Define set of parameters for each source distribution
-#
-# Lets create combinations of parameter values for each source distribution
+# ## Create dictionary with the parameter values for each source distribution
 
 # +
 parameters = {layout: {} for layout in layouts}
@@ -91,17 +90,17 @@ parameters = {layout: {} for layout in layouts}
 # Source bellow data
 layout = "source_bellow_data"
 depth_type = "constant_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths
 )
 
 depth_type = "relative_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths
 )
 
 depth_type = "variable_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
     depth_type=depth_type,
     damping=dampings,
     depth_factor=depth_factors,
@@ -112,17 +111,17 @@ parameters[layout][depth_type] = combine_parameters(
 # Block-median sources
 layout = "block_median_sources"
 depth_type = "constant_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths, spacing=block_spacings,
 )
 
 depth_type = "relative_depth"
-parameters[layout][depth_type] = combine_parameters(
+parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths, spacing=block_spacings,
 )
 
 depth_type = "variable_depth"
-parameters[layout][depth_type] = combine_parameters(
[…]

### 2020-02-26 manuscript/manuscript.tex
Replace airborne for ground on fig caption
Include parameter tables on manuscript

@@
 \usepackage{fancyhdr}
+\usepackage{multirow}
 
@@
         (b)~Vertical component of gravity acceleration generated by the
-            synthetic model plus Gaussian noise on the airborne survey
+            synthetic model plus Gaussian noise on the ground survey
             observation points.
@@
 
+\appendix
+
+\section{Source distributions parameters}
+
+\begin{table*}
+    \centering
+    \caption{
+        Parameters used with each source distribution when gridding the
+        synthetic ground survey. Depths and spacings are given in km.
+    }
+    \label{tab:parameters-ground-survey}
+    \input{parameters_ground_survey.tex}
+\end{table*}
+
+\begin{table*}
+    \centering
+    \caption{
+        Parameters used with each source distribution when gridding the
+        synthetic airborne survey. Depths and spacings are given in km.
+    }
+    \label{tab:parameters-airborne-survey}
+    \input{parameters_airborne_survey.tex}
+\end{table*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliographystyle{plainnat}

### 2020-02-28 eql_source_layouts/__init__.py
Save parameters as LaTeX variables
Instead of programmatically creating the LaTeX tables for parameters,
list of parameters values are stored as LaTeX values and then the tables
are created manually, filling each cell with these variables.

@@ -4,7 +4,7 @@ from ._version import get_versions
 from .layouts import source_bellow_data, block_median_sources, grid_sources
 from .synthetic_model import synthetic_model
 from .plot import plot_prediction
-from .latex_variables import latex_variables, latex_parameters_table
+from .latex_variables import latex_variables, latex_parameters
 from .utils import (
     combine_parameters,
     get_best_prediction,

### 2020-02-28 eql_source_layouts/latex_variables.py

@@ -21,79 +21,32 @@ def latex_variables(variable, number, unit=None, fmt=None):
     return tex_line
 
 
-def latex_parameters_table(parameters):
+def latex_parameters(parameters, survey):
     """
-    Create a LaTeX table for source distributions parameters
+    Create list of parameters for each source distribution as LaTeX variables
     """
-    # Initialize tabular
-    tabular_tex = []
-    tabular_tex.append(
-        r"\begin{{tabular}}{{{table_layout}}}".format(
-            table_layout=" ".join(["c"] * (len(parameters.keys()) + 2))
-        )
-    )
-    # Create table titles
-    column_titles = list(p.replace("_", " ").title() for p in parameters)
-    tabular_tex.append("& & " + " & ".join(column_titles) + r" \\")
-    tabular_tex.append(r"\hline")
-
-    # Append values for each depth type
-    for depth_type in get_depth_types(parameters):
-        # Get parameters names that involve this depth type
-        params_names = get_parameters_names(parameters, depth_type)
-        tabular_tex.append(
-            r"\multirow{{{n_params}}}{{*}}{{\parbox{{0.05\linewidth}}".format(
-                n_params=len(params_names)
-            )
-            + r"{{\centering {depth_type}}}}}".format(
-                depth_type=depth_type.replace("_", " ").title()
-            )
-        )
-        # Fill rows with parameter names and values for each source layout
-        for param in params_names:
-            line = r"    & {parameter_name} ".format(
-                parameter_name=param.replace("_", " ").title()
-            )
-            for layout in parameters:
-                if depth_type in parameters[layout]:
-                    if param in parameters[layout][depth_type]:
-                        values = format_parameters(
-                            parameters[layout][depth_type][param], param
-                        )
-                        line += "& {} ".format(values)
-                    else:
-                        line += "& - "
-            line += r"\\"
-            tabular_tex.append(line)
-        tabular_tex.append(r"\hline")
-    tabular_tex.append(r"\end{tabular}")
-    tabular_tex = "\n".join(tabular_tex)
-    return tabular_tex
-
-
-def get_depth_types(parameters):
-    """
-    Return a list with available depth types without repetition
-    """
-    depth_types = []
+    tex_variables = []
     for layout in parameters:
         for depth_type in parameters[layout]:
-            if depth_type not in depth_types:
-                depth_types.append(depth_type)
-    return depth_types
+            for parameter in parameters[layout][depth_type]:
+                if parameter != "depth_type":
[…]

### 2020-02-28 notebooks/02-grid-ground-data.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.3
+#       jupytext_version: 1.3.2
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -30,7 +30,7 @@ from eql_source_layouts import (
     plot_prediction,
     get_best_prediction,
     predictions_to_datasets,
-    latex_parameters_table,
+    latex_parameters,
 )
 
 # -
@@ -144,10 +144,10 @@ parameters[layout][depth_type] = dict(
 )
 # -
 
-# ### Create LaTeX table with parameters values
+# ### Save parameters to LaTeX variables file
 
 with open(os.path.join("..", "manuscript", "parameters_ground_survey.tex"), "w") as f:
-    f.write(latex_parameters_table(parameters))
+    f.write("\n".join(latex_parameters(parameters, "ground")))
 
 # ### Combine parameter values for each source distribution
 #

### 2020-02-28 notebooks/03-grid-airborne-data.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.3
+#       jupytext_version: 1.3.2
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -36,7 +36,7 @@ from eql_source_layouts import (
     plot_prediction,
     get_best_prediction,
     predictions_to_datasets,
-    latex_parameters_table,
+    latex_parameters,
 )
 
 # -
@@ -142,10 +142,10 @@ parameters[layout][depth_type] = dict(
 )
 # -
 
-# ### Create LaTeX table with parameters values
+# ### Save parameters to LaTeX variables file
 
 with open(os.path.join("..", "manuscript", "parameters_airborne_survey.tex"), "w") as f:
-    f.write(latex_parameters_table(parameters))
+    f.write("\n".join(latex_parameters(parameters, "airborne")))
 
 # ### Combine parameter values for each source distribution
 #

### 2020-02-28 manuscript/manuscript.tex
Save parameters as LaTeX variables
Instead of programmatically creating the LaTeX tables for parameters,
list of parameters values are stored as LaTeX values and then the tables
are created manually, filling each cell with these variables.
Add curly braces after LaTeX variables
Without the braces, LaTeX does not compile spaces after the variables.

@@
 \input{synthetic_model_surveys.tex}
+\input{parameters_ground_survey.tex}
+\input{parameters_airborne_survey.tex}
 
@@
 
-The synthetic model is made out of \NPrisms prisms distributed on a region of
-\ModelEasting$\times$\ModelNorthing between \ModelDepth deep and the zero
+The synthetic model is made out of \NPrisms{} prisms distributed on a region of
+\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
 height plane.
-Density contrast of prisms range from \ModelMinDensity and \ModelMaxDensity.
+Density contrast of prisms range from \ModelMinDensity{} and
+\ModelMaxDensity{}.
 We created deep big and thin shallow prisms for creating gravity anomalies with
@@
 model has been computed on a regular grid of
-\TargetEastingSize$\times$\TargetNorthingSize points with a spacing of
-\TargetSpacing located \TargetHeight above the zero height plane
+\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
+\TargetSpacing{} located \TargetHeight{} above the zero height plane
 (Fig.~\ref{fig:target-grid}).
@@
         Target grid. Gravitational effect of synthetic model on a regular grid
-        composed of \TargetEastingSize$\times$\TargetNorthingSize points with
-        a spacing of \TargetSpacing located \TargetHeight above the zero height
-        plane.
+        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
+        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
+        zero height plane.
     }
@@
 On both cases we selected only a portion of the survey and rescaled it to span
-on an area of \SurveyEasting$\times$\SurveyNorthing.
-The ground survey is composed by \GroundSurveyPoints observation points distributed at heights
-ranging between \GroundSurveyMinHeight and \GroundSurveyMaxHeight
-(Fig.~\ref{fig:synthetic-ground-survey}(a)).
-While the airborne survey has \AirborneSurveyPoints points at heights between
-\AirborneSurveyMinHeight and \AirborneSurveyMaxHeight.
+on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
+The ground survey is composed by \GroundSurveyPoints{} observation points
+distributed at heights ranging between \GroundSurveyMinHeight{} and
+\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
+While the airborne survey has \AirborneSurveyPoints{} points at heights between
+\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
 (Fig.~\ref{fig:synthetic-ground-survey}(a)).
@@
 model has been computed on both surveys.
-Some Gaussian noise (with standard deviation of \SurveyNoise) has been added
+Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
 to the effect of the synthetic model to simulate acquisition errors
@@
     \label{tab:parameters-ground-survey}
-    \input{parameters_ground_survey.tex}
+    \begin{tabular}{l c c c}
+        & \textbf{Sources bellow data} & \textbf{Block median sources}
+        & \textbf{Grid sources} \\
+
+        \textbf{Constant depth} & & & \\
+        \hline
+        Depth & \GroundSourceBellowDataConstantDepthDepth
+              & \GroundBlockMedianSourcesConstantDepthDepth
+              & \GroundGridSourcesConstantDepthDepth \\
+        Spacing & -
+                & \GroundBlockMedianSourcesConstantDepthSpacing
+                & \GroundGridSourcesConstantDepthSpacing \\
+        Pad & -
+            & -
+            & \GroundGridSourcesConstantDepthPad \\
+
+        & & & \\
+        \textbf{Relative depth} & & & \\
+        \cline{1-3}
+        Depth & \GroundSourceBellowDataRelativeDepthDepth
+              & \GroundBlockMedianSourcesRelativeDepthDepth
+              & \\
+        Spacing & -
+                & \GroundBlockMedianSourcesRelativeDepthSpacing
+                & \\
+
+        & & & \\
+        \textbf{Variable depth} & & & \\
+        \cline{1-3}
+        Depth & \GroundSourceBellowDataVariableDepthDepth
+              & \GroundBlockMedianSourcesVariableDepthDepth
+              & \\
+        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
+                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
+                     & \\
+        K nearest & \GroundSourceBellowDataVariableDepthKNearest
+                  & \GroundBlockMedianSourcesVariableDepthKNearest
+                  & \\
+        Spacing & -
+                & \GroundBlockMedianSourcesVariableDepthSpacing
+                & \\
+    \end{tabular}
 \end{table*}
@@
     \label{tab:parameters-airborne-survey}
-    \input{parameters_airborne_survey.tex}
+    \begin{tabular}{l c c c}
+        & \textbf{Sources bellow data} & \textbf{Block median sources}
+        & \textbf{Grid sources} \\
+
+        \textbf{Constant depth} & & & \\
+        \hline
+        Depth & \AirborneSourceBellowDataConstantDepthDepth
+              & \AirborneBlockMedianSourcesConstantDepthDepth
+              & \AirborneGridSourcesConstantDepthDepth \\
+        Spacing & -
+                & \AirborneBlockMedianSourcesConstantDepthSpacing
+                & \AirborneGridSourcesConstantDepthSpacing \\
+        Pad & -
+            & -
+            & \AirborneGridSourcesConstantDepthPad \\
+
+        & & & \\
+        \textbf{Relative depth} & & & \\
+        \cline{1-3}
+        Depth & \AirborneSourceBellowDataRelativeDepthDepth
+              & \AirborneBlockMedianSourcesRelativeDepthDepth
+              & \\
+        Spacing & -
+                & \AirborneBlockMedianSourcesRelativeDepthSpacing
+                & \\
+
+        & & & \\
+        \textbf{Variable depth} & & & \\
+        \cline{1-3}
+        Depth & \AirborneSourceBellowDataVariableDepthDepth
+              & \AirborneBlockMedianSourcesVariableDepthDepth
+              & \\
+        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
+                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
+                     & \\
+        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
+                  & \AirborneBlockMedianSourcesVariableDepthKNearest
+                  & \\
+        Spacing & -
+                & \AirborneBlockMedianSourcesVariableDepthSpacing
+                & \\
+    \end{tabular}
 \end{table*}

### 2020-03-02 manuscript/manuscript.tex
Define parameters units on tables

@@
         Parameters used with each source distribution when gridding the
-        synthetic ground survey. Depths and spacings are given in km.
+        synthetic ground survey.
     }
@@
         \hline
-        Depth & \GroundSourceBellowDataConstantDepthDepth
+        Depth (km) & \GroundSourceBellowDataConstantDepthDepth
                    & \GroundBlockMedianSourcesConstantDepthDepth
                    & \GroundGridSourcesConstantDepthDepth \\
-        Spacing & -
+        Spacing (km) & -
                      & \GroundBlockMedianSourcesConstantDepthSpacing
@@
         \cline{1-3}
-        Depth & \GroundSourceBellowDataRelativeDepthDepth
+        Depth (km) & \GroundSourceBellowDataRelativeDepthDepth
                    & \GroundBlockMedianSourcesRelativeDepthDepth
                    & \\
-        Spacing & -
+        Spacing (km) & -
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
@@
         \cline{1-3}
-        Depth & \GroundSourceBellowDataVariableDepthDepth
+        Depth (km) & \GroundSourceBellowDataVariableDepthDepth
                    & \GroundBlockMedianSourcesVariableDepthDepth
@@
                   & \\
-        Spacing & -
+        Spacing (km) & -
                      & \GroundBlockMedianSourcesVariableDepthSpacing
@@
         Parameters used with each source distribution when gridding the
-        synthetic airborne survey. Depths and spacings are given in km.
+        synthetic airborne survey.
     }
@@
         \hline
-        Depth & \AirborneSourceBellowDataConstantDepthDepth
+        Depth (km) & \AirborneSourceBellowDataConstantDepthDepth
                    & \AirborneBlockMedianSourcesConstantDepthDepth
                    & \AirborneGridSourcesConstantDepthDepth \\
-        Spacing & -
+        Spacing (km) & -
                      & \AirborneBlockMedianSourcesConstantDepthSpacing
@@
         \cline{1-3}
-        Depth & \AirborneSourceBellowDataRelativeDepthDepth
+        Depth (km) & \AirborneSourceBellowDataRelativeDepthDepth
                    & \AirborneBlockMedianSourcesRelativeDepthDepth
                    & \\
-        Spacing & -
+        Spacing (km) & -
                      & \AirborneBlockMedianSourcesRelativeDepthSpacing
@@
         \cline{1-3}
-        Depth & \AirborneSourceBellowDataVariableDepthDepth
+        Depth (km) & \AirborneSourceBellowDataVariableDepthDepth
                    & \AirborneBlockMedianSourcesVariableDepthDepth
@@
                   & \\
-        Spacing & -
+        Spacing (km) & -
                      & \AirborneBlockMedianSourcesVariableDepthSpacing

### 2020-03-02 manuscript/manuscript.tex
Add best prediction parameters tables

@@
 \input{parameters_airborne_survey.tex}
+\input{best_parameters_ground_survey.tex}
+\input{best_parameters_airborne_survey.tex}
 
@@
 
+\begin{table*}
+    \centering
+    \caption{
+        Combination of parameters that produce the best prediction when
+        gridding the synthetic ground survey with each source distribution.
+        The score of each best prediction is also shown.
+    }
+    \label{tab:parameters-ground-survey}
+    \begin{tabular}{l c c c}
+        & \textbf{Sources bellow data} & \textbf{Block median sources}
+        & \textbf{Grid sources} \\
+
+        \textbf{Constant depth} & & & \\
+        \hline
+        Depth (m) & \BestGroundSourceBellowDataConstantDepthDepth
+                   & \BestGroundBlockMedianSourcesConstantDepthDepth
+                   & \BestGroundGridSourcesConstantDepthDepth \\
+        Spacing (m) & -
+                     & \BestGroundBlockMedianSourcesConstantDepthSpacing
+                     & \BestGroundGridSourcesConstantDepthSpacing \\
+        Pad & -
+            & -
+            & \BestGroundGridSourcesConstantDepthPad \\
+        Damping & \BestGroundSourceBellowDataConstantDepthDamping
+                & \BestGroundBlockMedianSourcesConstantDepthDamping
+                & \BestGroundGridSourcesConstantDepthDamping \\
+        \textbf{R$^2$ score}
+                & \textbf{\BestGroundSourceBellowDataConstantDepthScore}
+                & \textbf{\BestGroundBlockMedianSourcesConstantDepthScore}
+                & \textbf{\BestGroundGridSourcesConstantDepthScore} \\
+
+        & & & \\
+        \textbf{Relative depth} & & & \\
+        \cline{1-3}
+        Depth (m) & \BestGroundSourceBellowDataRelativeDepthDepth
+                   & \BestGroundBlockMedianSourcesRelativeDepthDepth
+                   & \\
+        Spacing (m) & -
+                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
+                & \\
+        Damping & \BestGroundSourceBellowDataRelativeDepthDamping
+                & \BestGroundBlockMedianSourcesRelativeDepthDamping
+                & \\
+        \textbf{R$^2$ score}
+                & \textbf{\BestGroundSourceBellowDataRelativeDepthScore}
+                & \textbf{\BestGroundBlockMedianSourcesRelativeDepthScore}
+                & \\
+
+        & & & \\
+        \textbf{Variable depth} & & & \\
+        \cline{1-3}
+        Depth (m) & \BestGroundSourceBellowDataVariableDepthDepth
+                   & \BestGroundBlockMedianSourcesVariableDepthDepth
+                   & \\
+        Depth factor & \BestGroundSourceBellowDataVariableDepthDepthFactor
+                     & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
+                     & \\
+        K nearest & \BestGroundSourceBellowDataVariableDepthKNearest
+                  & \BestGroundBlockMedianSourcesVariableDepthKNearest
+                  & \\
+        Spacing (m) & -
+                     & \BestGroundBlockMedianSourcesVariableDepthSpacing
+                     & \\
+        Damping & \BestGroundSourceBellowDataVariableDepthDamping
+                & \BestGroundBlockMedianSourcesVariableDepthDamping
+                &  \\
+        \textbf{R$^2$ score}
+                & \textbf{\BestGroundSourceBellowDataVariableDepthScore}
+                & \textbf{\BestGroundBlockMedianSourcesVariableDepthScore}
+                & \\
+    \end{tabular}
+\end{table*}
+
+\begin{table*}
+    \centering
+    \caption{
+        Combination of parameters that produce the best prediction when
+        gridding the synthetic airborne survey with each source distribution.
+        The score of each best prediction is also shown.
+    }
+    \label{tab:parameters-ground-survey}
+    \begin{tabular}{l c c c}
+        & \textbf{Sources bellow data} & \textbf{Block median sources}
+        & \textbf{Grid sources} \\
+
+        \textbf{Constant depth} & & & \\
+        \hline
+        Depth (m) & \BestAirborneSourceBellowDataConstantDepthDepth
+                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
+                   & \BestAirborneGridSourcesConstantDepthDepth \\
+        Spacing (m) & -
+                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
+                     & \BestAirborneGridSourcesConstantDepthSpacing \\
+        Pad & -
+            & -
+            & \BestAirborneGridSourcesConstantDepthPad \\
+        Damping & \BestAirborneSourceBellowDataConstantDepthDamping
+                & \BestAirborneBlockMedianSourcesConstantDepthDamping
+                & \BestAirborneGridSourcesConstantDepthDamping \\
+        R$^2$ score & \BestAirborneSourceBellowDataConstantDepthScore
+                    & \BestAirborneBlockMedianSourcesConstantDepthScore
+                    & \BestAirborneGridSourcesConstantDepthScore \\
+        \textbf{R$^2$ score}
+                & \textbf{\BestAirborneSourceBellowDataConstantDepthScore}
+                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
+                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\
+
+        & & & \\
+        \textbf{Relative depth} & & & \\
+        \cline{1-3}
+        Depth (m) & \BestAirborneSourceBellowDataRelativeDepthDepth
+                   & \BestAirborneBlockMedianSourcesRelativeDepthDepth
+                   & \\
+        Spacing (m) & -
+                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
+                & \\
+        Damping & \BestAirborneSourceBellowDataRelativeDepthDamping
+                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
+                & \\
+        \textbf{R$^2$ score}
+                & \textbf{\BestAirborneSourceBellowDataRelativeDepthScore}
+                & \textbf{\BestAirborneBlockMedianSourcesRelativeDepthScore}
+                & \\
+
+        & & & \\
+        \textbf{Variable depth} & & & \\
+        \cline{1-3}
+        Depth (m) & \BestAirborneSourceBellowDataVariableDepthDepth
+                   & \BestAirborneBlockMedianSourcesVariableDepthDepth
+                   & \\
+        Depth factor & \BestAirborneSourceBellowDataVariableDepthDepthFactor
+                     & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
+                     & \\
+        K nearest & \BestAirborneSourceBellowDataVariableDepthKNearest
+                  & \BestAirborneBlockMedianSourcesVariableDepthKNearest
+                  & \\
+        Spacing (m) & -
+                     & \BestAirborneBlockMedianSourcesVariableDepthSpacing
+                     & \\
+        Damping & \BestAirborneSourceBellowDataVariableDepthDamping
+                & \BestAirborneBlockMedianSourcesVariableDepthDamping
+                &  \\
+        \textbf{R$^2$ score}
+                & \textbf{\BestAirborneSourceBellowDataVariableDepthScore}
+                & \textbf{\BestAirborneBlockMedianSourcesVariableDepthScore}
+                & \\
+    \end{tabular}
+\end{table*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-02 notebooks/02-grid-ground-data.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.2
+#       jupytext_version: 1.3.3
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -31,6 +31,7 @@ from eql_source_layouts import (
     get_best_prediction,
     predictions_to_datasets,
     latex_parameters,
+    latex_variables,
 )
 
 # -
@@ -322,3 +323,38 @@ cbar_ax = fig.add_axes([0.15, 0.05, 0.7, 0.02])
 fig.colorbar(tmp, cax=cbar_ax, orientation="horizontal", label=field_units)
 
 plt.show()
+# -
+
+# ## Save best predictions parameters
+#
+# Save best predictions parameters as LaTeX variables
+
+# +
+tex_variables = []
+for dataset in best_predictions:
+    for depth_type in dataset:
+        parameters = dataset[depth_type].attrs
+        layout = parameters["layout"]
+        for parameter, value in parameters.items():
+            if parameter in ("depth_type", "layout", "height"):
+                continue
+            fmt = ""
+            variable_name = (
+                "_".join(["best", "ground", layout, depth_type, parameter])
+                .replace("_", " ")
+                .title()
+                .replace(" ", "")
+            )
+            if parameter in ("spacing", "depth"):
+                fmt = ".1f"
+            if parameter == "score":
+                fmt = ".3f"
+            if value == 0:
+                fmt = ".0f"
+            tex_variables.append(latex_variables(variable_name, value, fmt=fmt))
+
+
+with open(
+    os.path.join("..", "manuscript", "best_parameters_ground_survey.tex"), "w"
+) as f:
+    f.write("\n".join(tex_variables,))

### 2020-03-02 notebooks/03-grid-airborne-data.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.2
+#       jupytext_version: 1.3.3
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -37,6 +37,7 @@ from eql_source_layouts import (
     get_best_prediction,
     predictions_to_datasets,
     latex_parameters,
+    latex_variables,
 )
 
 # -
@@ -324,3 +325,39 @@ cbar_ax = fig.add_axes([0.15, 0.05, 0.7, 0.02])
 fig.colorbar(tmp, cax=cbar_ax, orientation="horizontal", label=field_units)
 
 plt.show()
+# -
+
+# ## Save best predictions parameters
+#
+# Save best predictions parameters as LaTeX variables
+
+# +
+tex_variables = []
+for dataset in best_predictions:
+    for depth_type in dataset:
+        parameters = dataset[depth_type].attrs
+        layout = parameters["layout"]
+        for parameter, value in parameters.items():
+            if parameter in ("depth_type", "layout", "height"):
+                continue
+            fmt = ""
+            variable_name = (
+                "_".join(["best", "airborne", layout, depth_type, parameter])
+                .replace("_", " ")
+                .title()
+                .replace(" ", "")
+            )
+            if parameter in ("spacing", "depth"):
+                fmt = ".1f"
+            if parameter == "score":
+                fmt = ".3f"
+            if value == 0:
+                fmt = ".0f"
+            tex_variables.append(latex_variables(variable_name, value, fmt=fmt))
+
+
+with open(
+    os.path.join("..", "manuscript", "best_parameters_airborne_survey.tex"), "w"
+) as f:
+    f.write("\n".join(tex_variables,))
+# -

### 2020-03-02 eql_source_layouts/latex_variables.py
Fix wrong format on variable depths
When specifying depths on variable depth distributions the last
significant digit was being omitted.

@@ -58,7 +58,7 @@ def format_parameters(parameters_list, parameter_name):
     if parameter_name in ("spacing", "depth"):
         parameters_list = np.array(parameters_list) * 1e-3
         if min(parameters_list) < 1:  # asign formats if min value is lower than 1 km
-            fmt = ".1f"
+            fmt = ".2f"
         else:
             fmt = ".0f"
     # Create a string of parameters separated by commas

### 2020-03-02 manuscript/manuscript.tex
Add gridding differences figures to manuscript

--- 2020-02-28 manuscript/manuscript.tex
@@
 \usepackage{fancyhdr}
-\usepackage{multirow}
 
@@
 \newcommand{\inv}{^{\text{-}1}}
-
-% Import files with parameter values generated by notebooks
-\input{synthetic_model_surveys.tex}
-\input{parameters_ground_survey.tex}
-\input{parameters_airborne_survey.tex}
 
@@
 
-The synthetic model is made out of \NPrisms{} prisms distributed on a region of
-\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
+The synthetic model is made out of 64 prisms distributed on a region of
+\SI{89}{\km}$\times$\SI{88}{\km} between \SI{10}{\km} deep and the zero
 height plane.
-Density contrast of prisms range from \ModelMinDensity{} and
-\ModelMaxDensity{}.
+Density contrast of prisms range from \SI{-900}{\kg\per\cubic\m} and
+\SI{500}{\kg\per\cubic\m}.
 We created deep big and thin shallow prisms for creating gravity anomalies with
@@
 The vertical component of the gravity acceleration generated by the synthetic
-model has been computed on a regular grid of
-\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
-\TargetSpacing{} located \TargetHeight{} above the zero height plane
+model has been computed on a regular grid of 56$\times$57 points with a spacing
+of \SI{2}{\km} located \SI{2000}{\m} above the zero height plane
 (Fig.~\ref{fig:target-grid}).
@@
         Target grid. Gravitational effect of synthetic model on a regular grid
-        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
-        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
-        zero height plane.
+        composed of 56$\times$57 points with a spacing of \SI{2}{\km} located
+        \SI{2000}{\m} above the zero height plane.
     }
@@
 On both cases we selected only a portion of the survey and rescaled it to span
-on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
-The ground survey is composed by \GroundSurveyPoints{} observation points
-distributed at heights ranging between \GroundSurveyMinHeight{} and
-\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
-While the airborne survey has \AirborneSurveyPoints{} points at heights between
-\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
+on an area of \SI{111}{\km}$\times$\SI{111}{\km}.
+The ground survey is composed by 963 observation points distributed at heights
+ranging between \SI{0}{\m} and \SI{2052}{\m}
+(Fig.~\ref{fig:synthetic-ground-survey}(a)).
+While the airborne survey has 5673 points at heights between \SI{359}{\m} and
+\SI{1255}{\m}.
 (Fig.~\ref{fig:synthetic-ground-survey}(a)).
@@
 model has been computed on both surveys.
-Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
+Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
 to the effect of the synthetic model to simulate acquisition errors
@@
         (b)~Vertical component of gravity acceleration generated by the
-            synthetic model plus Gaussian noise on the ground survey
+            synthetic model plus Gaussian noise on the airborne survey
             observation points.
@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
+    \caption{
+        Differences between gravitational effects measured on the target grid
+        and the ones produced by the best prediction made by each source
+        distribution based on the synthetic ground survey.
+    }
+    \label{fig:ground-survey-differences}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
+    \caption{
+        Differences between gravitational effects measured on the target grid
+        and the ones produced by the best prediction made by each source
+        distribution based on the synthetic airborne survey.
+    }
+    \label{fig:airborne-survey-differences}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\appendix
-
-\section{Source distributions parameters}
-
-\begin{table*}
-    \centering
-    \caption{
-        Parameters used with each source distribution when gridding the
-        synthetic ground survey. Depths and spacings are given in km.
-    }
-    \label{tab:parameters-ground-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources bellow data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
-        \hline
-        Depth & \GroundSourceBellowDataConstantDepthDepth
-              & \GroundBlockMedianSourcesConstantDepthDepth
-              & \GroundGridSourcesConstantDepthDepth \\
-        Spacing & -
-                & \GroundBlockMedianSourcesConstantDepthSpacing
-                & \GroundGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \GroundGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth & \GroundSourceBellowDataRelativeDepthDepth
-              & \GroundBlockMedianSourcesRelativeDepthDepth
-              & \\
-        Spacing & -
-                & \GroundBlockMedianSourcesRelativeDepthSpacing
-                & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth & \GroundSourceBellowDataVariableDepthDepth
-              & \GroundBlockMedianSourcesVariableDepthDepth
-              & \\
-        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
-                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \GroundSourceBellowDataVariableDepthKNearest
-                  & \GroundBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing & -
-                & \GroundBlockMedianSourcesVariableDepthSpacing
-                & \\
-    \end{tabular}
-\end{table*}
-
-\begin{table*}
-    \centering
-    \caption{
-        Parameters used with each source distribution when gridding the
-        synthetic airborne survey. Depths and spacings are given in km.
-    }
-    \label{tab:parameters-airborne-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources bellow data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
-        \hline
-        Depth & \AirborneSourceBellowDataConstantDepthDepth
-              & \AirborneBlockMedianSourcesConstantDepthDepth
-              & \AirborneGridSourcesConstantDepthDepth \\
-        Spacing & -
-                & \AirborneBlockMedianSourcesConstantDepthSpacing
-                & \AirborneGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \AirborneGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth & \AirborneSourceBellowDataRelativeDepthDepth
-              & \AirborneBlockMedianSourcesRelativeDepthDepth
-              & \\
-        Spacing & -
-                & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth & \AirborneSourceBellowDataVariableDepthDepth
-              & \AirborneBlockMedianSourcesVariableDepthDepth
-              & \\
-        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
-                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
-                  & \AirborneBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing & -
-                & \AirborneBlockMedianSourcesVariableDepthSpacing
-                & \\
-    \end{tabular}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \bibliographystyle{plainnat}

### 2020-03-03 manuscript/manuscript.tex
Add nb for creating source layouts schematic figure

@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
+    \caption{
+        Source layouts.
+        (a) Set of synthetic observation points that resemble a ground survey.
+        (b) Location of sources obtained through the \emph{sources beneath
+            data} layout.
+        (c) Location of sources obtained through the \emph{block averaged
+            sources} layout.
+        (d) Location of sources obtained through the \emph{grid sources}
+            layout.
+    }
+    \label{fig:source-layouts-schematics}
+\end{figure*}
+
 The depth of the point sources can be chosen following different criteria.
@@
 
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
-    \caption{
-        Differences between gravitational effects measured on the target grid
-        and the ones produced by the best prediction made by each source
-        distribution based on the synthetic ground survey.
-    }
-    \label{fig:ground-survey-differences}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
-    \caption{
-        Differences between gravitational effects measured on the target grid
-        and the ones produced by the best prediction made by each source
-        distribution based on the synthetic airborne survey.
-    }
-    \label{fig:airborne-survey-differences}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-03 notebooks/source-layouts-schematics.py

@@ -1,0 +1,137 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:light
+#     text_representation:
+#       extension: .py
+#       format_name: light
+#       format_version: '1.5'
+#       jupytext_version: 1.3.3
+#   kernelspec:
+#     display_name: Python [conda env:eql_source_layouts]
+#     language: python
+#     name: conda-env-eql_source_layouts-py
+# ---
+
+# +
+from IPython.display import display
+import os
+import pyproj
+import numpy as np
+import pandas as pd
+import verde as vd
+import harmonica as hm
+import matplotlib.pyplot as plt
+
+import eql_source_layouts
+from eql_source_layouts import latex_variables, format_variable_name
+
+# -
+
+# ## Define parameters for building the source distributions
+
+# Define results directory to read synthetic ground survey
+ground_results_dir = os.path.join("..", "results", "ground_survey")
+
+# ## Read synthetic ground survey
+#
+
+# Get coordinates of observation points from a synthetic ground survey
+
+survey = pd.read_csv(os.path.join(ground_results_dir, "survey.csv"))
+
+inside = np.logical_and(
+    np.logical_and(survey.easting > 0e3, survey.easting < 40e3,),
+    np.logical_and(survey.northing > -60e3, survey.northing < -20e3,),
+)
+survey = survey.loc[inside]
+
+survey
+
+fig, ax = plt.subplots(figsize=(6, 6))
+tmp = ax.scatter(survey.easting, survey.northing)
+ax.set_aspect("equal")
+ax.set_title("Height of ground survey points")
+plt.show()
+
+coordinates = (survey.easting, survey.northing, survey.height)
+
+# ### Generate the source distributions
+
+# +
+layouts = ["source_bellow_data", "block_median_sources", "grid_sources"]
+depth_type = "constant_depth"
+
+parameters = {}
+
+layout = "source_bellow_data"
+parameters[layout] = dict(depth_type=depth_type, depth=500,)
+
+layout = "block_median_sources"
+parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=4000,)
+
+layout = "grid_sources"
+parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=4000,)
+# -
+
+source_distributions = {}
+for layout in parameters:
+    source_distributions[layout] = getattr(eql_source_layouts, layout)(
[…]

### 2020-03-03 manuscript/manuscript.tex

--- 2020-03-02 manuscript/manuscript.tex
@@
     \label{fig:block-median-sources}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
+    \caption{
+        Source layouts.
+        (a) Set of synthetic observation points that resemble a ground survey.
+        (b) Location of sources obtained through the \emph{sources beneath
+            data} layout.
+        (c) Location of sources obtained through the \emph{block averaged
+            sources} layout.
+        (d) Location of sources obtained through the \emph{grid sources}
+            layout.
+    }
+    \label{fig:source-layouts-schematics}
 \end{figure*}

### 2020-03-03 notebooks/source-layouts-schematics.py
Save number of sources as LaTeX variables

@@ -41,7 +41,7 @@ ground_results_dir = os.path.join("..", "results", "ground_survey")
 survey = pd.read_csv(os.path.join(ground_results_dir, "survey.csv"))
 
 inside = np.logical_and(
-    np.logical_and(survey.easting > 0e3, survey.easting < 40e3,),
+    np.logical_and(survey.easting > 0, survey.easting < 40e3,),
     np.logical_and(survey.northing > -60e3, survey.northing < -20e3,),
 )
 survey = survey.loc[inside]
@@ -59,6 +59,9 @@ coordinates = (survey.easting, survey.northing, survey.height)
 # ### Generate the source distributions
 
 # +
+block_spacing = 4000
+grid_spacing = 4000
+
 layouts = ["source_bellow_data", "block_median_sources", "grid_sources"]
 depth_type = "constant_depth"
 
@@ -68,10 +71,10 @@ layout = "source_bellow_data"
 parameters[layout] = dict(depth_type=depth_type, depth=500,)
 
 layout = "block_median_sources"
-parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=4000,)
+parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=block_spacing)
 
 layout = "grid_sources"
-parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=4000,)
+parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=grid_spacing)
 # -
 
 source_distributions = {}
@@ -124,14 +127,19 @@ plt.show()
 # ## Save number of observation points and sources to LaTeX variables
 
 # +
-tex_lines = [
-    latex_variables("SourceLayoutsSchematicsObservations", survey.easting.size),
-]
+tex_lines = []
 
+tex_lines.append(
+    latex_variables("SourceLayoutsSchematicsObservations", survey.easting.size),
+)
 for layout in layouts:
     tex_lines.append(
         latex_variables(
             "SourceLayoutsSchematics{}".format(format_variable_name(layout)),
-            source_distributions[layout][0].size
+            source_distributions[layout][0].size,
         )
     )
+# -
+
+with open(os.path.join("..", "manuscript", "source_layouts_schematics.tex"), "w") as f:
+    f.write("\n".join(tex_lines))

### 2020-03-03 manuscript/manuscript.tex
Specify number of sources on manuscript

@@
 \input{best_parameters_airborne_survey.tex}
+\input{source_layouts_schematics.tex}
 
@@
         Source layouts.
-        (a) Set of synthetic observation points that resemble a ground survey.
-        (b) Location of sources obtained through the \emph{sources beneath
-            data} layout.
-        (c) Location of sources obtained through the \emph{block averaged
-            sources} layout.
-        (d) Location of sources obtained through the \emph{grid sources}
-            layout.
+        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
+            points that resemble a ground survey.
+        (b) Location of the \SourceLayoutsSchematicsSourceBellowData{} sources
+            obtained through the \emph{sources beneath data} layout.
+        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
+            sources obtained through the \emph{block averaged sources} layout.
+        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
+            obtained through the \emph{grid sources} layout.
     }

### 2020-03-03 manuscript/manuscript.tex
Standardize source bellow data layout name
Replace "beneath" for "bellow" when naming the layout.

--- 2020-03-03 manuscript/manuscript.tex
@@
 
-The \emph{source beneath data} layout locates one source bellow each
+The \emph{source bellow data} layout locates one source bellow each
 observation point, therefore the number of sources will be equal to the number
@@
 carried out.
-In contrast, the \emph{source beneath data} layout is more likely to accurately
+In contrast, the \emph{source bellow data} layout is more likely to accurately
 fit the observed data with much less sources, reducing the computational load
@@
 
-When working with airborne surveys, the \emph{source beneath data} may
+When working with airborne surveys, the \emph{source bellow data} may
 generate an anisotropic distribution of sources by locating too many sources
@@
 The number of sources created by this new distribution will be less or equal to
-the ones created by the \emph{source beneath data} and the \emph{regular
+the ones created by the \emph{source bellow data} and the \emph{regular
 grid} with the same spacing.
@@
     \label{fig:block-median-sources}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
-    \caption{
-        Source layouts.
-        (a) Set of synthetic observation points that resemble a ground survey.
-        (b) Location of sources obtained through the \emph{sources beneath
-            data} layout.
-        (c) Location of sources obtained through the \emph{block averaged
-            sources} layout.
-        (d) Location of sources obtained through the \emph{grid sources}
-            layout.
-    }
-    \label{fig:source-layouts-schematics}
 \end{figure*}

### 2020-03-03 notebooks/source-distributions.py

@@ -22,7 +22,7 @@
 # a combination of a source layout and a depth type.
 # Lets define three layouts of point sources:
 #
-# 1. **Source beneath data**: One source point beneath each data point
+# 1. **Source bellow data**: One source point beneath each data point
 # 2. **Block averaged sources**: Split the region in blocks of equal size, compute the
 #    median coordinate of the data points per block, and put one point source beneath
 #    this block-median coordinate.
@@ -44,7 +44,7 @@
 #
 # |    | Constant depth | Relative depth | Variable depth |
 # | -- |----------------|----------------|----------------|
-# | **Source beneath data** | ✅ | ✅ | ✅ |
+# | **Source bellow data** | ✅ | ✅ | ✅ |
 # | **Block averaged sources** | ✅ | ✅ | ✅ |
 # | **Grid of sources** | ✅ | ❌ | ❌ |
 #
@@ -92,7 +92,7 @@ spacing = 4000
 # =====================================================
 parameters = {layout: {} for layout in layouts}
 
-# ... for source beneath data layout
+# ... for source bellow data layout
 layout = "source_bellow_data"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = {

### 2020-03-03 manuscript/manuscript.tex
Reformat ground survey parameter table
Replace full list of parameters for ranges when possible.
Change table design to better fit paper width and visualization.

--- 2020-03-03 manuscript/manuscript.tex
@@
 \usepackage{multirow}
+\usepackage{booktabs}
 
@@
     \label{tab:parameters-ground-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources bellow data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
+    \begin{tabular}{c | l l c c}
+        \multicolumn{1}{c}{\textbf{Source layout}}
+            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
+            & \multicolumn{1}{c}{\textbf{Values}}
+            & \multicolumn{1}{c}{\textbf{Interval}} \\
         \hline
-        Depth (km) & \GroundSourceBellowDataConstantDepthDepth
+
+        \multirow{5}{*}{Source Bellow Data}
+            & Constant Depth
+                & Depth (km)
+                & \GroundSourceBellowDataConstantDepthDepth
+                & \GroundSourceBellowDataConstantDepthDepthInterval \\
+            \cline{2-5}
+            & Relative Depth
+                & Depth (km)
+                & \GroundSourceBellowDataRelativeDepthDepth
+                & \GroundSourceBellowDataRelativeDepthDepthInterval \\
+            \cline{2-5}
+            & \multirow{3}{*}{Variable Depth}
+                & Depth (km)
+                & \GroundSourceBellowDataVariableDepthDepth
+                & \GroundSourceBellowDataVariableDepthDepthInterval \\
+            &
+                & Depth factor
+                & \GroundSourceBellowDataVariableDepthDepthFactor
+                & \GroundSourceBellowDataVariableDepthDepthFactorInterval \\
+            &
+                & K nearest
+                & \GroundSourceBellowDataVariableDepthKNearest
+                & \GroundSourceBellowDataVariableDepthKNearestInterval \\
+        \hline
+
+        \multirow{8}{*}{Block median sources}
+            & \multirow{2}{*}{Constant Depth}
+                & Depth (km)
                 & \GroundBlockMedianSourcesConstantDepthDepth
-                   & \GroundGridSourcesConstantDepthDepth \\
-        Spacing (km) & -
+                & \GroundBlockMedianSourcesConstantDepthDepthInterval \\
+            &
+                & Spacing (km)
                 & \GroundBlockMedianSourcesConstantDepthSpacing
-                     & \GroundGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \GroundGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \GroundSourceBellowDataRelativeDepthDepth
+                & \GroundBlockMedianSourcesConstantDepthSpacingInterval \\
+            \cline{2-5}
+            & \multirow{2}{*}{Relative Depth}
+                & Depth (km)
                 & \GroundBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (km) & -
+                & \GroundBlockMedianSourcesRelativeDepthDepthInterval \\
+            &
+                & Spacing (km)
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
-                & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \GroundSourceBellowDataVariableDepthDepth
+                & \GroundBlockMedianSourcesRelativeDepthSpacingInterval \\
+            \cline{2-5}
+            & \multirow{4}{*}{Variable Depth}
+                & Depth (km)
                 & \GroundBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
+                & \GroundBlockMedianSourcesVariableDepthDepthInterval \\
+            &
+                & Depth factor
                 & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \GroundSourceBellowDataVariableDepthKNearest
+                & \GroundBlockMedianSourcesVariableDepthDepthFactorInterval \\
+            &
+                & K nearest
                 & \GroundBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (km) & -
+                & \GroundBlockMedianSourcesVariableDepthKNearestInterval \\
+            &
+                & Spacing (km)
                 & \GroundBlockMedianSourcesVariableDepthSpacing
-                     & \\
+                & \GroundBlockMedianSourcesVariableDepthSpacingInterval \\
+        \hline
+
+        \multirow{3}{*}{Grid Sources}
+            & \multirow{3}{*}{Constant Depth}
+                & Depth (km)
+                    & \GroundGridSourcesConstantDepthDepth
+                    & \GroundGridSourcesConstantDepthDepthInterval \\
+            &
+                & Spacing (km)
+                    & \GroundGridSourcesConstantDepthSpacing
+                    & \GroundGridSourcesConstantDepthSpacingInterval \\
+            &
+                & Pad
+                    & \GroundGridSourcesConstantDepthPad
+                    & \GroundGridSourcesConstantDepthPadInterval \\
     \end{tabular}

### 2020-03-03 notebooks/02-grid-ground-data.py
Fix max value of block spacing

@@ -75,7 +75,7 @@ depth_factors = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
 variable_depths = np.arange(0, 1500, 200)
 k_values = [1, 5, 10, 15]
 # Define block spacing for block median sources
-block_spacings = np.arange(1e3, 5e4, 1e3)
+block_spacings = np.arange(1e3, 5e3, 1e3)
 # -
 
 # ## Create dictionary with the parameter values for each source distribution

### 2020-03-03 manuscript/manuscript.tex
Add damping to table
Improve how damping values are shown. Instead of showing a full list or
a range, using dots between first two values and last.

--- 2020-03-03 manuscript/manuscript.tex
@@
 \input{best_parameters_airborne_survey.tex}
-\input{source_layouts_schematics.tex}
 
@@
 \section{Introduction}
+
+\num{1e3}
 
@@
     \label{fig:block-median-sources}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
-    \caption{
-        Source layouts.
-        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
-            points that resemble a ground survey.
-        (b) Location of the \SourceLayoutsSchematicsSourceBellowData{} sources
-            obtained through the \emph{sources beneath data} layout.
-        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
-            sources obtained through the \emph{block averaged sources} layout.
-        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
-            obtained through the \emph{grid sources} layout.
-    }
-    \label{fig:source-layouts-schematics}
 \end{figure*}
@@
     \label{tab:parameters-ground-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources bellow data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
+    \begin{tabular}{c | l l c c}
+        \multicolumn{1}{c}{\textbf{Source layout}}
+            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
+            & \multicolumn{1}{c}{\textbf{Values}}
+            & \multicolumn{1}{c}{\textbf{Interval}} \\
         \hline
-        Depth (km) & \GroundSourceBellowDataConstantDepthDepth
+
+        \multirow{8}{*}{Source Bellow Data}
+            & \multirow{2}{*}{Constant Depth}
+                & Depth (km)
+                & \GroundSourceBellowDataConstantDepthDepth
+                & \GroundSourceBellowDataConstantDepthDepthInterval \\
+            &
+                & Damping
+                & \GroundSourceBellowDataConstantDepthDamping
+                & \GroundSourceBellowDataConstantDepthDampingInterval \\
+            \cline{2-5}
+            & \multirow{2}{*}{Relative Depth}
+                & Depth (km)
+                & \GroundSourceBellowDataRelativeDepthDepth
+                & \GroundSourceBellowDataRelativeDepthDepthInterval \\
+            &
+                & Damping
+                & \GroundSourceBellowDataRelativeDepthDamping
+                & \GroundSourceBellowDataRelativeDepthDampingInterval \\
+            \cline{2-5}
+            & \multirow{4}{*}{Variable Depth}
+                & Depth (km)
+                & \GroundSourceBellowDataVariableDepthDepth
+                & \GroundSourceBellowDataVariableDepthDepthInterval \\
+            &
+                & Depth factor
+                & \GroundSourceBellowDataVariableDepthDepthFactor
+                & \GroundSourceBellowDataVariableDepthDepthFactorInterval \\
+            &
+                & K nearest
+                & \GroundSourceBellowDataVariableDepthKNearest
+                & \GroundSourceBellowDataVariableDepthKNearestInterval \\
+            &
+                & Damping
+                & \GroundSourceBellowDataVariableDepthDamping
+                & \GroundSourceBellowDataVariableDepthDampingInterval \\
+        \hline
+
+        \multirow{11}{*}{Block median sources}
+            & \multirow{3}{*}{Constant Depth}
+                & Depth (km)
                 & \GroundBlockMedianSourcesConstantDepthDepth
-                   & \GroundGridSourcesConstantDepthDepth \\
-        Spacing (km) & -
+                & \GroundBlockMedianSourcesConstantDepthDepthInterval \\
+            &
+                & Spacing (km)
                 & \GroundBlockMedianSourcesConstantDepthSpacing
-                     & \GroundGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \GroundGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \GroundSourceBellowDataRelativeDepthDepth
+                & \GroundBlockMedianSourcesConstantDepthSpacingInterval \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesConstantDepthDamping
+                & \GroundBlockMedianSourcesConstantDepthDampingInterval \\
+            \cline{2-5}
+            & \multirow{3}{*}{Relative Depth}
+                & Depth (km)
                 & \GroundBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (km) & -
+                & \GroundBlockMedianSourcesRelativeDepthDepthInterval \\
+            &
+                & Spacing (km)
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
-                & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \GroundSourceBellowDataVariableDepthDepth
+                & \GroundBlockMedianSourcesRelativeDepthSpacingInterval \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesRelativeDepthDamping
+                & \GroundBlockMedianSourcesRelativeDepthDampingInterval \\
+            \cline{2-5}
+            & \multirow{5}{*}{Variable Depth}
+                & Depth (km)
                 & \GroundBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
+                & \GroundBlockMedianSourcesVariableDepthDepthInterval \\
+            &
+                & Depth factor
                 & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \GroundSourceBellowDataVariableDepthKNearest
+                & \GroundBlockMedianSourcesVariableDepthDepthFactorInterval \\
+            &
+                & K nearest
                 & \GroundBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (km) & -
+                & \GroundBlockMedianSourcesVariableDepthKNearestInterval \\
+            &
+                & Spacing (km)
                 & \GroundBlockMedianSourcesVariableDepthSpacing
-                     & \\
+                & \GroundBlockMedianSourcesVariableDepthSpacingInterval \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesVariableDepthDamping
+                & \GroundBlockMedianSourcesVariableDepthDampingInterval \\
+        \hline
+
+        \multirow{4}{*}{Grid Sources}
+            & \multirow{4}{*}{Constant Depth}
+                & Depth (km)
+                    & \GroundGridSourcesConstantDepthDepth
+                    & \GroundGridSourcesConstantDepthDepthInterval \\
+            &
+                & Spacing (km)
+                    & \GroundGridSourcesConstantDepthSpacing
+                    & \GroundGridSourcesConstantDepthSpacingInterval \\
+            &
+                & Pad
+                    & \GroundGridSourcesConstantDepthPad
+                    & \GroundGridSourcesConstantDepthPadInterval \\
+            &
+                & Damping
+                    & \GroundGridSourcesConstantDepthDamping
+                    & \GroundGridSourcesConstantDepthDampingInterval \\
     \end{tabular}

### 2020-03-03 eql_source_layouts/latex_variables.py

@@ -115,13 +115,12 @@ def _format_damping(parameters):
     """
     Create range of values for damping parameters
     """
-    fmt = ".0f"
     parameters = np.log10(parameters)
     differences = parameters[1:] - parameters[:-1]
     interval = differences[1] - differences[0]
     assert np.allclose(differences[0], differences)
-    values = r"\numrange{{10$^{min:>{fmt}}$}}{{10$^{max:>{fmt}}$}}".format(
-        min=parameters.min(), max=parameters.max(), fmt=fmt
+    values = r"\num{{e{:.0f}}}, \num{{e{:.0f}}},$\dots$, \num{{e{:.0f}}}".format(
+        parameters[0], parameters[1], parameters[-1]
     )
-    interval = r"\num{{10$^{interval:>{fmt}}$}}".format(interval=interval, fmt=fmt)
+    interval = "-"
     return values, interval

### 2020-03-03 eql_source_layouts/latex_variables.py
Make blank intervals if values are passed as list

@@ -107,7 +107,7 @@ def _create_numlist(parameters):
         values.append("{v:>{fmt}}".format(v=value, fmt=fmt))
     values = ";".join(values)
     values = r"\numlist{{{values}}}".format(values=values)
-    interval = "-"
+    interval = ""
     return values, interval
 
 
@@ -122,5 +122,5 @@ def _format_damping(parameters):
     values = r"\num{{e{:.0f}}}, \num{{e{:.0f}}},$\dots$, \num{{e{:.0f}}}".format(
         parameters[0], parameters[1], parameters[-1]
     )
-    interval = "-"
+    interval = ""
     return values, interval

### 2020-03-04 manuscript/manuscript.tex
Change ranges on airborne nb and update parameters table
Change parameters on gridding airborne survey notebook to ranges when
possible. Update parameters table on manuscript.

@@
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources bellow data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
+    \begin{tabular}{c | l l c c}
+        \multicolumn{1}{c}{\textbf{Source layout}}
+            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
+            & \multicolumn{1}{c}{\textbf{Values}}
+            & \multicolumn{1}{c}{\textbf{Interval}} \\
         \hline
-        Depth (km) & \AirborneSourceBellowDataConstantDepthDepth
+
+        \multirow{8}{*}{Source Bellow Data}
+            & \multirow{2}{*}{Constant Depth}
+                & Depth (km)
+                & \AirborneSourceBellowDataConstantDepthDepth
+                & \AirborneSourceBellowDataConstantDepthDepthInterval \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataConstantDepthDamping
+                & \AirborneSourceBellowDataConstantDepthDampingInterval \\
+            \cline{2-5}
+            & \multirow{2}{*}{Relative Depth}
+                & Depth (km)
+                & \AirborneSourceBellowDataRelativeDepthDepth
+                & \AirborneSourceBellowDataRelativeDepthDepthInterval \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataRelativeDepthDamping
+                & \AirborneSourceBellowDataRelativeDepthDampingInterval \\
+            \cline{2-5}
+            & \multirow{4}{*}{Variable Depth}
+                & Depth (km)
+                & \AirborneSourceBellowDataVariableDepthDepth
+                & \AirborneSourceBellowDataVariableDepthDepthInterval \\
+            &
+                & Depth factor
+                & \AirborneSourceBellowDataVariableDepthDepthFactor
+                & \AirborneSourceBellowDataVariableDepthDepthFactorInterval \\
+            &
+                & K nearest
+                & \AirborneSourceBellowDataVariableDepthKNearest
+                & \AirborneSourceBellowDataVariableDepthKNearestInterval \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataVariableDepthDamping
+                & \AirborneSourceBellowDataVariableDepthDampingInterval \\
+        \hline
+
+        \multirow{11}{*}{Block median sources}
+            & \multirow{3}{*}{Constant Depth}
+                & Depth (km)
                 & \AirborneBlockMedianSourcesConstantDepthDepth
-                   & \AirborneGridSourcesConstantDepthDepth \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesConstantDepthDepthInterval \\
+            &
+                & Spacing (km)
                 & \AirborneBlockMedianSourcesConstantDepthSpacing
-                     & \AirborneGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \AirborneGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \AirborneSourceBellowDataRelativeDepthDepth
+                & \AirborneBlockMedianSourcesConstantDepthSpacingInterval \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesConstantDepthDamping
+                & \AirborneBlockMedianSourcesConstantDepthDampingInterval \\
+            \cline{2-5}
+            & \multirow{3}{*}{Relative Depth}
+                & Depth (km)
                 & \AirborneBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesRelativeDepthDepthInterval \\
+            &
+                & Spacing (km)
                 & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                     & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \AirborneSourceBellowDataVariableDepthDepth
+                & \AirborneBlockMedianSourcesRelativeDepthSpacingInterval \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesRelativeDepthDamping
+                & \AirborneBlockMedianSourcesRelativeDepthDampingInterval \\
+            \cline{2-5}
+            & \multirow{5}{*}{Variable Depth}
+                & Depth (km)
                 & \AirborneBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
+                & \AirborneBlockMedianSourcesVariableDepthDepthInterval \\
+            &
+                & Depth factor
                 & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
+                & \AirborneBlockMedianSourcesVariableDepthDepthFactorInterval \\
+            &
+                & K nearest
                 & \AirborneBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesVariableDepthKNearestInterval \\
+            &
+                & Spacing (km)
                 & \AirborneBlockMedianSourcesVariableDepthSpacing
-                     & \\
+                & \AirborneBlockMedianSourcesVariableDepthSpacingInterval \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesVariableDepthDamping
+                & \AirborneBlockMedianSourcesVariableDepthDampingInterval \\
+        \hline
+
+        \multirow{4}{*}{Grid Sources}
+            & \multirow{4}{*}{Constant Depth}
+                & Depth (km)
+                    & \AirborneGridSourcesConstantDepthDepth
+                    & \AirborneGridSourcesConstantDepthDepthInterval \\
+            &
+                & Spacing (km)
+                    & \AirborneGridSourcesConstantDepthSpacing
+                    & \AirborneGridSourcesConstantDepthSpacingInterval \\
+            &
+                & Pad
+                    & \AirborneGridSourcesConstantDepthPad
+                    & \AirborneGridSourcesConstantDepthPadInterval \\
+            &
+                & Damping
+                    & \AirborneGridSourcesConstantDepthDamping
+                    & \AirborneGridSourcesConstantDepthDampingInterval \\
     \end{tabular}

### 2020-03-04 notebooks/03-grid-airborne-data.py

@@ -65,7 +65,7 @@ field_units = "mGal"
 # Define a list of source layouts
 layouts = ["source_bellow_data", "block_median_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
-dampings = [None, 1e-4, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2]
+dampings = np.logspace(-4, 2, 7)
 # Define depht values
 depths = np.arange(1e3, 18e3, 2e3)
 # Define parameters for the grid sources:
@@ -73,14 +73,14 @@ depths = np.arange(1e3, 18e3, 2e3)
 grid_sources_spacings = [1e3, 2e3, 3e3]
 grid_sources_depths = np.arange(3e3, 15e3, 2e3)
 grid_sources_paddings = [0, 0.1, 0.2]
-grid_sources_dampings = [1e1, 1e2, 1e3, 1e4]
+grid_sources_dampings = np.logspace(1, 4, 4)
 # Define parameters for variable relative depth layouts:
 #    depth factor, depth shift and k_values
 depth_factors = [1, 2, 3, 4, 5, 6]
 variable_depths = np.arange(50, 1500, 200)
 k_values = [1, 5, 10, 15]
 # Define block spacing for block median sources
-block_spacings = [1_000, 2_000, 3_000, 4_000]
+block_spacings = np.arange(1e3, 5e3, 1e3)
 # -
 
 # ## Create dictionary with the parameter values for each source distribution
@@ -361,3 +361,5 @@ with open(
 ) as f:
     f.write("\n".join(tex_variables,))
 # -
+
+

### 2020-03-04 manuscript/manuscript.tex
Rename interval for increment

--- 2020-03-03 manuscript/manuscript.tex
@@
             & \multicolumn{1}{c}{\textbf{Values}}
-            & \multicolumn{1}{c}{\textbf{Interval}} \\
+            & \multicolumn{1}{c}{\textbf{Increment}} \\
         \hline
 
-        \multirow{5}{*}{Source Bellow Data}
-            & Constant Depth
+        \multirow{8}{*}{Source Bellow Data}
+            & \multirow{2}{*}{Constant Depth}
                 & Depth (km)
                 & \GroundSourceBellowDataConstantDepthDepth
-                & \GroundSourceBellowDataConstantDepthDepthInterval \\
+                & \GroundSourceBellowDataConstantDepthDepthIncrement \\
+            &
+                & Damping
+                & \GroundSourceBellowDataConstantDepthDamping
+                & \GroundSourceBellowDataConstantDepthDampingIncrement \\
             \cline{2-5}
-            & Relative Depth
+            & \multirow{2}{*}{Relative Depth}
                 & Depth (km)
                 & \GroundSourceBellowDataRelativeDepthDepth
-                & \GroundSourceBellowDataRelativeDepthDepthInterval \\
+                & \GroundSourceBellowDataRelativeDepthDepthIncrement \\
+            &
+                & Damping
+                & \GroundSourceBellowDataRelativeDepthDamping
+                & \GroundSourceBellowDataRelativeDepthDampingIncrement \\
             \cline{2-5}
-            & \multirow{3}{*}{Variable Depth}
+            & \multirow{4}{*}{Variable Depth}
                 & Depth (km)
                 & \GroundSourceBellowDataVariableDepthDepth
-                & \GroundSourceBellowDataVariableDepthDepthInterval \\
+                & \GroundSourceBellowDataVariableDepthDepthIncrement \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthDepthFactor
-                & \GroundSourceBellowDataVariableDepthDepthFactorInterval \\
+                & \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthKNearest
-                & \GroundSourceBellowDataVariableDepthKNearestInterval \\
+                & \GroundSourceBellowDataVariableDepthKNearestIncrement \\
+            &
+                & Damping
+                & \GroundSourceBellowDataVariableDepthDamping
+                & \GroundSourceBellowDataVariableDepthDampingIncrement \\
         \hline
 
-        \multirow{8}{*}{Block median sources}
-            & \multirow{2}{*}{Constant Depth}
+        \multirow{11}{*}{Block median sources}
+            & \multirow{3}{*}{Constant Depth}
                 & Depth (km)
                 & \GroundBlockMedianSourcesConstantDepthDepth
-                & \GroundBlockMedianSourcesConstantDepthDepthInterval \\
+                & \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesConstantDepthSpacing
-                & \GroundBlockMedianSourcesConstantDepthSpacingInterval \\
+                & \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesConstantDepthDamping
+                & \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
             \cline{2-5}
-            & \multirow{2}{*}{Relative Depth}
+            & \multirow{3}{*}{Relative Depth}
                 & Depth (km)
                 & \GroundBlockMedianSourcesRelativeDepthDepth
-                & \GroundBlockMedianSourcesRelativeDepthDepthInterval \\
+                & \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
-                & \GroundBlockMedianSourcesRelativeDepthSpacingInterval \\
+                & \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesRelativeDepthDamping
+                & \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
             \cline{2-5}
-            & \multirow{4}{*}{Variable Depth}
+            & \multirow{5}{*}{Variable Depth}
                 & Depth (km)
                 & \GroundBlockMedianSourcesVariableDepthDepth
-                & \GroundBlockMedianSourcesVariableDepthDepthInterval \\
+                & \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                & \GroundBlockMedianSourcesVariableDepthDepthFactorInterval \\
+                & \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthKNearest
-                & \GroundBlockMedianSourcesVariableDepthKNearestInterval \\
+                & \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthSpacing
-                & \GroundBlockMedianSourcesVariableDepthSpacingInterval \\
+                & \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesVariableDepthDamping
+                & \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
         \hline
 
-        \multirow{3}{*}{Grid Sources}
-            & \multirow{3}{*}{Constant Depth}
+        \multirow{4}{*}{Grid Sources}
+            & \multirow{4}{*}{Constant Depth}
                 & Depth (km)
                     & \GroundGridSourcesConstantDepthDepth
-                    & \GroundGridSourcesConstantDepthDepthInterval \\
+                    & \GroundGridSourcesConstantDepthDepthIncrement \\
             &
@@
                     & \GroundGridSourcesConstantDepthSpacing
-                    & \GroundGridSourcesConstantDepthSpacingInterval \\
+                    & \GroundGridSourcesConstantDepthSpacingIncrement \\
             &
@@
                     & \GroundGridSourcesConstantDepthPad
-                    & \GroundGridSourcesConstantDepthPadInterval \\
+                    & \GroundGridSourcesConstantDepthPadIncrement \\
+            &
+                & Damping
+                    & \GroundGridSourcesConstantDepthDamping
+                    & \GroundGridSourcesConstantDepthDampingIncrement \\
     \end{tabular}
@@
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources bellow data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
+    \begin{tabular}{c | l l c c}
+        \multicolumn{1}{c}{\textbf{Source layout}}
+            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
+            & \multicolumn{1}{c}{\textbf{Values}}
+            & \multicolumn{1}{c}{\textbf{Increment}} \\
         \hline
-        Depth (km) & \AirborneSourceBellowDataConstantDepthDepth
+
+        \multirow{8}{*}{Source Bellow Data}
+            & \multirow{2}{*}{Constant Depth}
+                & Depth (km)
+                & \AirborneSourceBellowDataConstantDepthDepth
+                & \AirborneSourceBellowDataConstantDepthDepthIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataConstantDepthDamping
+                & \AirborneSourceBellowDataConstantDepthDampingIncrement \\
+            \cline{2-5}
+            & \multirow{2}{*}{Relative Depth}
+                & Depth (km)
+                & \AirborneSourceBellowDataRelativeDepthDepth
+                & \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataRelativeDepthDamping
+                & \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
+            \cline{2-5}
+            & \multirow{4}{*}{Variable Depth}
+                & Depth (km)
+                & \AirborneSourceBellowDataVariableDepthDepth
+                & \AirborneSourceBellowDataVariableDepthDepthIncrement \\
+            &
+                & Depth factor
+                & \AirborneSourceBellowDataVariableDepthDepthFactor
+                & \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
+            &
+                & K nearest
+                & \AirborneSourceBellowDataVariableDepthKNearest
+                & \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataVariableDepthDamping
+                & \AirborneSourceBellowDataVariableDepthDampingIncrement \\
+        \hline
+
+        \multirow{11}{*}{Block median sources}
+            & \multirow{3}{*}{Constant Depth}
+                & Depth (km)
                 & \AirborneBlockMedianSourcesConstantDepthDepth
-                   & \AirborneGridSourcesConstantDepthDepth \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
+            &
+                & Spacing (km)
                 & \AirborneBlockMedianSourcesConstantDepthSpacing
-                     & \AirborneGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \AirborneGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \AirborneSourceBellowDataRelativeDepthDepth
+                & \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesConstantDepthDamping
+                & \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
+            \cline{2-5}
+            & \multirow{3}{*}{Relative Depth}
+                & Depth (km)
                 & \AirborneBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
+            &
+                & Spacing (km)
                 & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                     & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \AirborneSourceBellowDataVariableDepthDepth
+                & \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesRelativeDepthDamping
+                & \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
+            \cline{2-5}
+            & \multirow{5}{*}{Variable Depth}
+                & Depth (km)
                 & \AirborneBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
+                & \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
+            &
+                & Depth factor
                 & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
+                & \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
+            &
+                & K nearest
                 & \AirborneBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
+            &
+                & Spacing (km)
                 & \AirborneBlockMedianSourcesVariableDepthSpacing
-                     & \\
+                & \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesVariableDepthDamping
+                & \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
+        \hline
+
+        \multirow{4}{*}{Grid Sources}
+            & \multirow{4}{*}{Constant Depth}
+                & Depth (km)
+                    & \AirborneGridSourcesConstantDepthDepth
+                    & \AirborneGridSourcesConstantDepthDepthIncrement \\
+            &
+                & Spacing (km)
+                    & \AirborneGridSourcesConstantDepthSpacing
+                    & \AirborneGridSourcesConstantDepthSpacingIncrement \\
+            &
+                & Pad
+                    & \AirborneGridSourcesConstantDepthPad
+                    & \AirborneGridSourcesConstantDepthPadIncrement \\
+            &
+                & Damping
+                    & \AirborneGridSourcesConstantDepthDamping
+                    & \AirborneGridSourcesConstantDepthDampingIncrement \\
     \end{tabular}

### 2020-03-04 eql_source_layouts/latex_variables.py

@@ -30,7 +30,7 @@ def latex_parameters(parameters, survey):
         for depth_type in parameters[layout]:
             for parameter in parameters[layout][depth_type]:
                 if parameter != "depth_type":
-                    values, interval = format_parameters(
+                    values, increment = format_parameters(
                         parameters[layout][depth_type][parameter], parameter
                     )
                     variable_name = format_variable_name(
@@ -38,7 +38,7 @@ def latex_parameters(parameters, survey):
                     )
                     tex_variables.append(latex_variables(variable_name, values))
                     tex_variables.append(
-                        latex_variables(variable_name + "Interval", interval)
+                        latex_variables(variable_name + "Increment", increment)
                     )
     return tex_variables
 
@@ -69,17 +69,17 @@ def format_parameters(parameters, parameter_name):
     # Check if parameters are given in ranges
     differences = parameters[1:] - parameters[:-1]
     if np.allclose(differences, differences[0]):
-        values, interval = _create_numrange(parameters)
+        values, increment = _create_numrange(parameters)
     else:
-        values, interval = _create_numlist(parameters)
-    return values, interval
+        values, increment = _create_numlist(parameters)
+    return values, increment
 
 
 def _create_numrange(parameters):
     """
     Create range of values using LaTeX numrange
     """
-    interval = parameters[1] - parameters[0]
+    increment = parameters[1] - parameters[0]
     # Set format
     if parameters.min() < 1:
         fmt = ".1f"
@@ -88,8 +88,8 @@ def _create_numrange(parameters):
     values = r"\numrange{{{min:>{fmt}}}}{{{max:>{fmt}}}}".format(
         min=parameters.min(), max=parameters.max(), fmt=fmt
     )
-    interval = r"\num{{{interval:>{fmt}}}}".format(interval=interval, fmt=fmt)
-    return values, interval
+    increment = r"\num{{{increment:>{fmt}}}}".format(increment=increment, fmt=fmt)
+    return values, increment
 
 
 def _create_numlist(parameters):
@@ -107,8 +107,8 @@ def _create_numlist(parameters):
         values.append("{v:>{fmt}}".format(v=value, fmt=fmt))
     values = ";".join(values)
     values = r"\numlist{{{values}}}".format(values=values)
-    interval = ""
-    return values, interval
+    increment = ""
+    return values, increment
 
 
 def _format_damping(parameters):
[…]

### 2020-03-04 manuscript/manuscript.tex
Depths and spacing are presented in meters

--- 2020-03-03 manuscript/manuscript.tex
@@
             & \multicolumn{1}{c}{\textbf{Values}}
-            & \multicolumn{1}{c}{\textbf{Interval}} \\
+            & \multicolumn{1}{c}{\textbf{Increment}} \\
         \hline
@@
             & \multirow{2}{*}{Constant Depth}
-                & Depth (km)
+                & Depth (m)
                 & \GroundSourceBellowDataConstantDepthDepth
-                & \GroundSourceBellowDataConstantDepthDepthInterval \\
+                & \GroundSourceBellowDataConstantDepthDepthIncrement \\
             &
@@
                 & \GroundSourceBellowDataConstantDepthDamping
-                & \GroundSourceBellowDataConstantDepthDampingInterval \\
+                & \GroundSourceBellowDataConstantDepthDampingIncrement \\
             \cline{2-5}
             & \multirow{2}{*}{Relative Depth}
-                & Depth (km)
+                & Depth (m)
                 & \GroundSourceBellowDataRelativeDepthDepth
-                & \GroundSourceBellowDataRelativeDepthDepthInterval \\
+                & \GroundSourceBellowDataRelativeDepthDepthIncrement \\
             &
@@
                 & \GroundSourceBellowDataRelativeDepthDamping
-                & \GroundSourceBellowDataRelativeDepthDampingInterval \\
+                & \GroundSourceBellowDataRelativeDepthDampingIncrement \\
             \cline{2-5}
             & \multirow{4}{*}{Variable Depth}
-                & Depth (km)
+                & Depth (m)
                 & \GroundSourceBellowDataVariableDepthDepth
-                & \GroundSourceBellowDataVariableDepthDepthInterval \\
+                & \GroundSourceBellowDataVariableDepthDepthIncrement \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthKNearest
-                & \GroundSourceBellowDataVariableDepthKNearestInterval \\
+                & \GroundSourceBellowDataVariableDepthKNearestIncrement \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthDamping
-                & \GroundSourceBellowDataVariableDepthDampingInterval \\
+                & \GroundSourceBellowDataVariableDepthDampingIncrement \\
         \hline
@@
             & \multirow{3}{*}{Constant Depth}
-                & Depth (km)
+                & Depth (m)
                 & \GroundBlockMedianSourcesConstantDepthDepth
-                & \GroundBlockMedianSourcesConstantDepthDepthInterval \\
-            &
-                & Spacing (km)
+                & \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
+            &
+                & Spacing (m)
                 & \GroundBlockMedianSourcesConstantDepthSpacing
-                & \GroundBlockMedianSourcesConstantDepthSpacingInterval \\
+                & \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesConstantDepthDamping
-                & \GroundBlockMedianSourcesConstantDepthDampingInterval \\
+                & \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
             \cline{2-5}
             & \multirow{3}{*}{Relative Depth}
-                & Depth (km)
+                & Depth (m)
                 & \GroundBlockMedianSourcesRelativeDepthDepth
-                & \GroundBlockMedianSourcesRelativeDepthDepthInterval \\
-            &
-                & Spacing (km)
+                & \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
+            &
+                & Spacing (m)
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
-                & \GroundBlockMedianSourcesRelativeDepthSpacingInterval \\
+                & \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesRelativeDepthDamping
-                & \GroundBlockMedianSourcesRelativeDepthDampingInterval \\
+                & \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
             \cline{2-5}
             & \multirow{5}{*}{Variable Depth}
-                & Depth (km)
+                & Depth (m)
                 & \GroundBlockMedianSourcesVariableDepthDepth
-                & \GroundBlockMedianSourcesVariableDepthDepthInterval \\
+                & \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthKNearest
-                & \GroundBlockMedianSourcesVariableDepthKNearestInterval \\
-            &
-                & Spacing (km)
+                & \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
+            &
+                & Spacing (m)
                 & \GroundBlockMedianSourcesVariableDepthSpacing
-                & \GroundBlockMedianSourcesVariableDepthSpacingInterval \\
+                & \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthDamping
-                & \GroundBlockMedianSourcesVariableDepthDampingInterval \\
+                & \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
         \hline
@@
             & \multirow{4}{*}{Constant Depth}
-                & Depth (km)
+                & Depth (m)
                     & \GroundGridSourcesConstantDepthDepth
-                    & \GroundGridSourcesConstantDepthDepthInterval \\
-            &
-                & Spacing (km)
+                    & \GroundGridSourcesConstantDepthDepthIncrement \\
+            &
+                & Spacing (m)
                     & \GroundGridSourcesConstantDepthSpacing
-                    & \GroundGridSourcesConstantDepthSpacingInterval \\
+                    & \GroundGridSourcesConstantDepthSpacingIncrement \\
             &
@@
                     & \GroundGridSourcesConstantDepthPad
-                    & \GroundGridSourcesConstantDepthPadInterval \\
+                    & \GroundGridSourcesConstantDepthPadIncrement \\
             &
@@
                     & \GroundGridSourcesConstantDepthDamping
-                    & \GroundGridSourcesConstantDepthDampingInterval \\
+                    & \GroundGridSourcesConstantDepthDampingIncrement \\
     \end{tabular}
@@
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources bellow data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
+    \begin{tabular}{c | l l c c}
+        \multicolumn{1}{c}{\textbf{Source layout}}
+            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
+            & \multicolumn{1}{c}{\textbf{Values}}
+            & \multicolumn{1}{c}{\textbf{Increment}} \\
         \hline
-        Depth (km) & \AirborneSourceBellowDataConstantDepthDepth
+
+        \multirow{8}{*}{Source Bellow Data}
+            & \multirow{2}{*}{Constant Depth}
+                & Depth (m)
+                & \AirborneSourceBellowDataConstantDepthDepth
+                & \AirborneSourceBellowDataConstantDepthDepthIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataConstantDepthDamping
+                & \AirborneSourceBellowDataConstantDepthDampingIncrement \\
+            \cline{2-5}
+            & \multirow{2}{*}{Relative Depth}
+                & Depth (m)
+                & \AirborneSourceBellowDataRelativeDepthDepth
+                & \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataRelativeDepthDamping
+                & \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
+            \cline{2-5}
+            & \multirow{4}{*}{Variable Depth}
+                & Depth (m)
+                & \AirborneSourceBellowDataVariableDepthDepth
+                & \AirborneSourceBellowDataVariableDepthDepthIncrement \\
+            &
+                & Depth factor
+                & \AirborneSourceBellowDataVariableDepthDepthFactor
+                & \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
+            &
+                & K nearest
+                & \AirborneSourceBellowDataVariableDepthKNearest
+                & \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataVariableDepthDamping
+                & \AirborneSourceBellowDataVariableDepthDampingIncrement \\
+        \hline
+
+        \multirow{11}{*}{Block median sources}
+            & \multirow{3}{*}{Constant Depth}
+                & Depth (m)
                 & \AirborneBlockMedianSourcesConstantDepthDepth
-                   & \AirborneGridSourcesConstantDepthDepth \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
+            &
+                & Spacing (m)
                 & \AirborneBlockMedianSourcesConstantDepthSpacing
-                     & \AirborneGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \AirborneGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \AirborneSourceBellowDataRelativeDepthDepth
+                & \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesConstantDepthDamping
+                & \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
+            \cline{2-5}
+            & \multirow{3}{*}{Relative Depth}
+                & Depth (m)
                 & \AirborneBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
+            &
+                & Spacing (m)
                 & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                     & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \AirborneSourceBellowDataVariableDepthDepth
+                & \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesRelativeDepthDamping
+                & \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
+            \cline{2-5}
+            & \multirow{5}{*}{Variable Depth}
+                & Depth (m)
                 & \AirborneBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
+                & \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
+            &
+                & Depth factor
                 & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
+                & \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
+            &
+                & K nearest
                 & \AirborneBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (km) & -
+                & \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
+            &
+                & Spacing (m)
                 & \AirborneBlockMedianSourcesVariableDepthSpacing
-                     & \\
+                & \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesVariableDepthDamping
+                & \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
+        \hline
+
+        \multirow{4}{*}{Grid Sources}
+            & \multirow{4}{*}{Constant Depth}
+                & Depth (m)
+                    & \AirborneGridSourcesConstantDepthDepth
+                    & \AirborneGridSourcesConstantDepthDepthIncrement \\
+            &
+                & Spacing (m)
+                    & \AirborneGridSourcesConstantDepthSpacing
+                    & \AirborneGridSourcesConstantDepthSpacingIncrement \\
+            &
+                & Pad
+                    & \AirborneGridSourcesConstantDepthPad
+                    & \AirborneGridSourcesConstantDepthPadIncrement \\
+            &
+                & Damping
+                    & \AirborneGridSourcesConstantDepthDamping
+                    & \AirborneGridSourcesConstantDepthDampingIncrement \\
     \end{tabular}

### 2020-03-04 eql_source_layouts/latex_variables.py

@@ -62,10 +62,6 @@ def format_parameters(parameters, parameter_name):
     if parameter_name == "damping":
         return _format_damping(parameters)
 
-    # Convert depths and spacings to km
-    if parameter_name in ("depth", "spacing"):
-        parameters *= 1e-3
-
     # Check if parameters are given in ranges
     differences = parameters[1:] - parameters[:-1]
     if np.allclose(differences, differences[0]):

### 2020-03-04 notebooks/03-grid-airborne-data.py

@@ -361,5 +361,3 @@ with open(
 ) as f:
     f.write("\n".join(tex_variables,))
 # -
-
-

### 2020-03-04 eql_source_layouts/latex_variables.py
Create numranges only if number of parameters > 4

@@ -62,9 +62,9 @@ def format_parameters(parameters, parameter_name):
     if parameter_name == "damping":
         return _format_damping(parameters)
 
-    # Check if parameters are given in ranges
+    # Check if parameters are given in ranges and create numrages if # parameter > 4
     differences = parameters[1:] - parameters[:-1]
-    if np.allclose(differences, differences[0]):
+    if np.allclose(differences, differences[0]) and len(parameters) > 4:
         values, increment = _create_numrange(parameters)
     else:
         values, increment = _create_numlist(parameters)

### 2020-03-04 notebooks/03-grid-airborne-data.py

@@ -360,4 +360,3 @@ with open(
     os.path.join("..", "manuscript", "best_parameters_airborne_survey.tex"), "w"
 ) as f:
     f.write("\n".join(tex_variables,))
-# -

### 2020-03-04 eql_source_layouts/latex_variables.py
Specify fmt of min and max numranges separately
Also standardize the way the fmt is created.

@@ -77,15 +77,32 @@ def _create_numrange(parameters):
     """
     increment = parameters[1] - parameters[0]
     # Set format
-    if parameters.min() < 1:
-        fmt = ".1f"
-    else:
-        fmt = ".0f"
-    values = r"\numrange{{{min:>{fmt}}}}{{{max:>{fmt}}}}".format(
-        min=parameters.min(), max=parameters.max(), fmt=fmt
+    params_min_max = []
+    for value in (parameters.min(), parameters.max()):
+        fmt = _determine_fmt(value)
+        params_min_max.append("{v:>{fmt}}".format(v=value, fmt=fmt))
+    values = r"\numrange{{{min}}}{{{max}}}".format(
+        min=params_min_max[0], max=params_min_max[1]
     )
+    fmt = _determine_fmt(increment)
     increment = r"\num{{{increment:>{fmt}}}}".format(increment=increment, fmt=fmt)
     return values, increment
+
+
+def _determine_fmt(value, decimal_digits=1):
+    """
+    Determine the proper format for float numbers
+
+    We assume that value is > 0.
+    """
+    if value == 0:
+        fmt = ".0f"
+    else:
+        if value < 1:
+            fmt = ".{:d}f".format(decimal_digits)
+        else:
+            fmt = ".0f"
+    return fmt
 
 
 def _create_numlist(parameters):
@@ -94,12 +111,7 @@ def _create_numlist(parameters):
     """
     values = []
     for value in parameters:
-        if value == 0:
-            fmt = ".0f"
-        if value < 1:
-            fmt = ".1f"
-        else:
-            fmt = ".0f"
+        fmt = _determine_fmt(value)
         values.append("{v:>{fmt}}".format(v=value, fmt=fmt))
     values = ";".join(values)
     values = r"\numlist{{{values}}}".format(values=values)

### 2020-03-05 manuscript/manuscript.tex
Remove repeated line of R2 score on table
Remove vertical lines from tables

@@
                 & \BestAirborneGridSourcesConstantDepthDamping \\
-        R$^2$ score & \BestAirborneSourceBellowDataConstantDepthScore
-                    & \BestAirborneBlockMedianSourcesConstantDepthScore
-                    & \BestAirborneGridSourcesConstantDepthScore \\
         \textbf{R$^2$ score}
@@
     \label{tab:parameters-ground-survey}
-    \begin{tabular}{c | l l c c}
-        \multicolumn{1}{c}{\textbf{Source layout}}
-            & \multicolumn{1}{c}{\textbf{Depth type}}
-            & \multicolumn{1}{c}{\textbf{Parameters}}
-            & \multicolumn{1}{c}{\textbf{Values}}
-            & \multicolumn{1}{c}{\textbf{Increment}} \\
+    \begin{tabular}{c l l c c}
+        \textbf{Source layout}
+            & \textbf{Depth type}
+            & \textbf{Parameters}
+            & \textbf{Values}
+            & \textbf{Increment} \\
         \hline
@@
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{c | l l c c}
-        \multicolumn{1}{c}{\textbf{Source layout}}
-            & \multicolumn{1}{c}{\textbf{Depth type}}
-            & \multicolumn{1}{c}{\textbf{Parameters}}
-            & \multicolumn{1}{c}{\textbf{Values}}
-            & \multicolumn{1}{c}{\textbf{Increment}} \\
+    \begin{tabular}{c l l c c}
+        \textbf{Source layout}
+            & \textbf{Depth type}
+            & \textbf{Parameters}
+            & \textbf{Values}
+            & \textbf{Increment} \\
         \hline

### 2020-03-05 manuscript/manuscript.tex
Replace hlines and clines for rules
Replace first hline of the table for a toprule, the clines for cmidrules
and hlines on the body of the table for midrules.

@@
             & \textbf{Increment} \\
-        \hline
+        \toprule
 
@@
                 & \GroundSourceBellowDataConstantDepthDampingIncrement \\
-            \cline{2-5}
+            \cmidrule{2-5}
             & \multirow{2}{*}{Relative Depth}
@@
                 & \GroundSourceBellowDataRelativeDepthDampingIncrement \\
-            \cline{2-5}
+            \cmidrule{2-5}
             & \multirow{4}{*}{Variable Depth}
@@
                 & \GroundSourceBellowDataVariableDepthDampingIncrement \\
-        \hline
+        \midrule
 
@@
                 & \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
-            \cline{2-5}
+            \cmidrule{2-5}
             & \multirow{3}{*}{Relative Depth}
@@
                 & \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
-            \cline{2-5}
+            \cmidrule{2-5}
             & \multirow{5}{*}{Variable Depth}
@@
                 & \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
-        \hline
+        \midrule
 
@@
                 & \AirborneSourceBellowDataConstantDepthDampingIncrement \\
-            \cline{2-5}
+            \cmidrule{2-5}
             & \multirow{2}{*}{Relative Depth}
@@
                 & \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
-            \cline{2-5}
+            \cmidrule{2-5}
             & \multirow{4}{*}{Variable Depth}
@@
                 & \AirborneSourceBellowDataVariableDepthDampingIncrement \\
-        \hline
+        \midrule
 
@@
                 & \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
-            \cline{2-5}
+            \cmidrule{2-5}
             & \multirow{3}{*}{Relative Depth}
@@
                 & \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
-            \cline{2-5}
+            \cmidrule{2-5}
             & \multirow{5}{*}{Variable Depth}
@@
                 & \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
-        \hline
+        \midrule
 

### 2020-03-05 manuscript/manuscript.tex
Remove increment column and include step in values
Ditch the whole Increment columns from parameter tables and include the
increment (step size) into the Values column. Now increment variables
has the following hardcoded text: ", step size " before the actual
numeric interval. This allows to programmatically add steps into the
table without the need to to edit the LaTeX table.

--- 2020-03-05 manuscript/manuscript.tex
@@
     \label{tab:parameters-ground-survey}
-    \begin{tabular}{c l l c c}
+    \begin{tabular}{c l l c}
         \textbf{Source layout}
@@
             & \textbf{Parameters}
-            & \textbf{Values}
-            & \textbf{Increment} \\
-        \hline
+            & \textbf{Values} \\
+        \toprule
 
@@
                 & \GroundSourceBellowDataConstantDepthDepth
-                & \GroundSourceBellowDataConstantDepthDepthIncrement \\
+                  \GroundSourceBellowDataConstantDepthDepthIncrement \\
             &
@@
                 & \GroundSourceBellowDataConstantDepthDamping
-                & \GroundSourceBellowDataConstantDepthDampingIncrement \\
-            \cline{2-5}
+                  \GroundSourceBellowDataConstantDepthDampingIncrement \\
+            \cmidrule{2-4}
             & \multirow{2}{*}{Relative Depth}
@@
                 & \GroundSourceBellowDataRelativeDepthDepth
-                & \GroundSourceBellowDataRelativeDepthDepthIncrement \\
+                  \GroundSourceBellowDataRelativeDepthDepthIncrement \\
             &
@@
                 & \GroundSourceBellowDataRelativeDepthDamping
-                & \GroundSourceBellowDataRelativeDepthDampingIncrement \\
-            \cline{2-5}
+                  \GroundSourceBellowDataRelativeDepthDampingIncrement \\
+            \cmidrule{2-4}
             & \multirow{4}{*}{Variable Depth}
@@
                 & \GroundSourceBellowDataVariableDepthDepth
-                & \GroundSourceBellowDataVariableDepthDepthIncrement \\
+                  \GroundSourceBellowDataVariableDepthDepthIncrement \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthDepthFactor
-                & \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
+                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthKNearest
-                & \GroundSourceBellowDataVariableDepthKNearestIncrement \\
+                  \GroundSourceBellowDataVariableDepthKNearestIncrement \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthDamping
-                & \GroundSourceBellowDataVariableDepthDampingIncrement \\
-        \hline
+                  \GroundSourceBellowDataVariableDepthDampingIncrement \\
+        \midrule
 
@@
                 & \GroundBlockMedianSourcesConstantDepthDepth
-                & \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
+                  \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesConstantDepthSpacing
-                & \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
+                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesConstantDepthDamping
-                & \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
-            \cline{2-5}
+                  \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
+            \cmidrule{2-4}
             & \multirow{3}{*}{Relative Depth}
@@
                 & \GroundBlockMedianSourcesRelativeDepthDepth
-                & \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
+                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
-                & \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
+                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesRelativeDepthDamping
-                & \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
-            \cline{2-5}
+                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
+            \cmidrule{2-4}
             & \multirow{5}{*}{Variable Depth}
@@
                 & \GroundBlockMedianSourcesVariableDepthDepth
-                & \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                & \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthKNearest
-                & \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthSpacing
-                & \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthDamping
-                & \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
-        \hline
+                  \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
+        \midrule
 
@@
                     & \GroundGridSourcesConstantDepthDepth
-                    & \GroundGridSourcesConstantDepthDepthIncrement \\
+                      \GroundGridSourcesConstantDepthDepthIncrement \\
             &
@@
                     & \GroundGridSourcesConstantDepthSpacing
-                    & \GroundGridSourcesConstantDepthSpacingIncrement \\
+                      \GroundGridSourcesConstantDepthSpacingIncrement \\
             &
@@
                     & \GroundGridSourcesConstantDepthPad
-                    & \GroundGridSourcesConstantDepthPadIncrement \\
+                     \GroundGridSourcesConstantDepthPadIncrement \\
             &
@@
                     & \GroundGridSourcesConstantDepthDamping
-                    & \GroundGridSourcesConstantDepthDampingIncrement \\
+                      \GroundGridSourcesConstantDepthDampingIncrement \\
     \end{tabular}
@@
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{c l l c c}
+    \begin{tabular}{c l l c}
         \textbf{Source layout}
@@
                 & \AirborneSourceBellowDataConstantDepthDepth
-                & \AirborneSourceBellowDataConstantDepthDepthIncrement \\
+                  \AirborneSourceBellowDataConstantDepthDepthIncrement \\
             &
@@
                 & \AirborneSourceBellowDataConstantDepthDamping
-                & \AirborneSourceBellowDataConstantDepthDampingIncrement \\
-            \cline{2-5}
+                  \AirborneSourceBellowDataConstantDepthDampingIncrement \\
+            \cmidrule{2-4}
             & \multirow{2}{*}{Relative Depth}
@@
                 & \AirborneSourceBellowDataRelativeDepthDepth
-                & \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
+                  \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
             &
@@
                 & \AirborneSourceBellowDataRelativeDepthDamping
-                & \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
-            \cline{2-5}
+                  \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
+            \cmidrule{2-4}
             & \multirow{4}{*}{Variable Depth}
@@
                 & \AirborneSourceBellowDataVariableDepthDepth
-                & \AirborneSourceBellowDataVariableDepthDepthIncrement \\
+                  \AirborneSourceBellowDataVariableDepthDepthIncrement \\
             &
@@
                 & \AirborneSourceBellowDataVariableDepthDepthFactor
-                & \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
+                  \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
             &
@@
                 & \AirborneSourceBellowDataVariableDepthKNearest
-                & \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
+                  \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
             &
@@
                 & \AirborneSourceBellowDataVariableDepthDamping
-                & \AirborneSourceBellowDataVariableDepthDampingIncrement \\
-        \hline
+                  \AirborneSourceBellowDataVariableDepthDampingIncrement \\
+        \midrule
 
@@
                 & \AirborneBlockMedianSourcesConstantDepthDepth
-                & \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
+                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
             &
@@
                 & \AirborneBlockMedianSourcesConstantDepthSpacing
-                & \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
+                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
             &
@@
                 & \AirborneBlockMedianSourcesConstantDepthDamping
-                & \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
-            \cline{2-5}
+                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
+            \cmidrule{2-4}
             & \multirow{3}{*}{Relative Depth}
@@
                 & \AirborneBlockMedianSourcesRelativeDepthDepth
-                & \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
+                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
             &
@@
                 & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                & \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
+                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
             &
@@
                 & \AirborneBlockMedianSourcesRelativeDepthDamping
-                & \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
-            \cline{2-5}
+                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
+            \cmidrule{2-4}
             & \multirow{5}{*}{Variable Depth}
@@
                 & \AirborneBlockMedianSourcesVariableDepthDepth
-                & \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
             &
@@
                 & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                & \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
             &
@@
                 & \AirborneBlockMedianSourcesVariableDepthKNearest
-                & \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
             &
@@
                 & \AirborneBlockMedianSourcesVariableDepthSpacing
-                & \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
             &
@@
                 & \AirborneBlockMedianSourcesVariableDepthDamping
-                & \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
-        \hline
+                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
+        \midrule
 
@@
                     & \AirborneGridSourcesConstantDepthDepth
-                    & \AirborneGridSourcesConstantDepthDepthIncrement \\
+                      \AirborneGridSourcesConstantDepthDepthIncrement \\
             &
@@
                     & \AirborneGridSourcesConstantDepthSpacing
-                    & \AirborneGridSourcesConstantDepthSpacingIncrement \\
+                      \AirborneGridSourcesConstantDepthSpacingIncrement \\
             &
@@
                     & \AirborneGridSourcesConstantDepthPad
-                    & \AirborneGridSourcesConstantDepthPadIncrement \\
+                      \AirborneGridSourcesConstantDepthPadIncrement \\
             &
@@
                     & \AirborneGridSourcesConstantDepthDamping
-                    & \AirborneGridSourcesConstantDepthDampingIncrement \\
+                      \AirborneGridSourcesConstantDepthDampingIncrement \\
     \end{tabular}

### 2020-03-05 eql_source_layouts/latex_variables.py

@@ -85,7 +85,9 @@ def _create_numrange(parameters):
         min=params_min_max[0], max=params_min_max[1]
     )
     fmt = _determine_fmt(increment)
-    increment = r"\num{{{increment:>{fmt}}}}".format(increment=increment, fmt=fmt)
+    increment = r", step size \num{{{increment:>{fmt}}}}".format(
+        increment=increment, fmt=fmt
+    )
     return values, increment
 
 

### 2020-03-05 manuscript/manuscript.tex
Center all column titles
Draft to include best parameters and score on table
Trying if it's possible to include best parameters and best score into
parameters table.

@@
     \label{tab:parameters-ground-survey}
-    \begin{tabular}{c l l c}
+    \begin{tabular}{c l l c c c}
         \textbf{Source layout}
-            & \textbf{Depth type}
-            & \textbf{Parameters}
-            & \textbf{Values} \\
+            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
+            & \textbf{Values}
+            & \textbf{Best}
+            & \textbf{R$^2$ score} \\
         \toprule
@@
                 & \GroundSourceBellowDataConstantDepthDepth
-                  \GroundSourceBellowDataConstantDepthDepthIncrement \\
+                  \GroundSourceBellowDataConstantDepthDepthIncrement
+                & \BestGroundSourceBellowDataConstantDepthDepth
+                & \multirow{2}{*}{
+                    \BestGroundSourceBellowDataConstantDepthScore
+                  } \\
             &
@@
                 & \GroundSourceBellowDataConstantDepthDamping
-                  \GroundSourceBellowDataConstantDepthDampingIncrement \\
-            \cmidrule{2-4}
+                  \GroundSourceBellowDataConstantDepthDampingIncrement
+                & \BestGroundSourceBellowDataConstantDepthDamping
+                & \\
+            \cmidrule{2-6}
             & \multirow{2}{*}{Relative Depth}
@@
                 & \GroundSourceBellowDataRelativeDepthDepth
-                  \GroundSourceBellowDataRelativeDepthDepthIncrement \\
+                  \GroundSourceBellowDataRelativeDepthDepthIncrement
+                & \BestGroundSourceBellowDataRelativeDepthDepth
+                & \multirow{2}{*}{
+                    \BestGroundSourceBellowDataRelativeDepthScore
+                  } \\
             &
@@
                 & \GroundSourceBellowDataRelativeDepthDamping
-                  \GroundSourceBellowDataRelativeDepthDampingIncrement \\
-            \cmidrule{2-4}
+                  \GroundSourceBellowDataRelativeDepthDampingIncrement
+                & \BestGroundSourceBellowDataRelativeDepthDamping
+                & \\
+            \cmidrule{2-6}
             & \multirow{4}{*}{Variable Depth}
@@
                 & \GroundSourceBellowDataVariableDepthDepth
-                  \GroundSourceBellowDataVariableDepthDepthIncrement \\
+                  \GroundSourceBellowDataVariableDepthDepthIncrement
+                & \BestGroundSourceBellowDataVariableDepthDepth
+                & \multirow{4}{*}{
+                    \BestGroundSourceBellowDataVariableDepthScore
+                  } \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthDepthFactor
-                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
+                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement
+                & \BestGroundSourceBellowDataVariableDepthDepthFactor
+                & \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthKNearest
-                  \GroundSourceBellowDataVariableDepthKNearestIncrement \\
+                  \GroundSourceBellowDataVariableDepthKNearestIncrement
+                & \BestGroundSourceBellowDataVariableDepthKNearest
+                & \\
             &
@@
                 & \GroundSourceBellowDataVariableDepthDamping
-                  \GroundSourceBellowDataVariableDepthDampingIncrement \\
+                  \GroundSourceBellowDataVariableDepthDampingIncrement
+                & \BestGroundSourceBellowDataVariableDepthDamping
+                & \\
         \midrule
@@
                 & \GroundBlockMedianSourcesConstantDepthDepth
-                  \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
+                  \GroundBlockMedianSourcesConstantDepthDepthIncrement
+                & \BestGroundBlockMedianSourcesConstantDepthDepth
+                & \multirow{3}{*}{
+                    \textbf{\BestGroundBlockMedianSourcesConstantDepthScore}
+                  } \\
             &
@@
                 & \GroundBlockMedianSourcesConstantDepthSpacing
-                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
+                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement
+                & \BestGroundBlockMedianSourcesConstantDepthSpacing
+                & \\
             &
@@
                 & \GroundBlockMedianSourcesConstantDepthDamping
-                  \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
-            \cmidrule{2-4}
+                  \GroundBlockMedianSourcesConstantDepthDampingIncrement
+                & \BestGroundBlockMedianSourcesConstantDepthDamping
+                & \\
+            \cmidrule{2-6}
             & \multirow{3}{*}{Relative Depth}
@@
                 & \GroundBlockMedianSourcesRelativeDepthDepth
-                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
+                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement
+                & \BestGroundBlockMedianSourcesRelativeDepthDepth
+                & \multirow{3}{*}{
+                    \BestGroundBlockMedianSourcesRelativeDepthScore
+                  } \\
             &
@@
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
-                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
+                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement
+                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
+                & \\
             &
@@
                 & \GroundBlockMedianSourcesRelativeDepthDamping
-                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
-            \cmidrule{2-4}
+                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement
+                & \BestGroundBlockMedianSourcesRelativeDepthDamping
+                & \\
+            \cmidrule{2-6}
             & \multirow{5}{*}{Variable Depth}
@@
                 & \GroundBlockMedianSourcesVariableDepthDepth
-                  \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthDepthIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthDepth
+                & \multirow{5}{*}{
+                    \BestGroundBlockMedianSourcesVariableDepthScore
+                  } \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
+                & \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthKNearest
-                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthKNearest
+                & \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthSpacing
-                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthSpacing
+                & \\
             &
@@
                 & \GroundBlockMedianSourcesVariableDepthDamping
-                  \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
+                  \GroundBlockMedianSourcesVariableDepthDampingIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthDamping
+                & \\
         \midrule
@@
                 & \GroundGridSourcesConstantDepthDepth
-                      \GroundGridSourcesConstantDepthDepthIncrement \\
+                  \GroundGridSourcesConstantDepthDepthIncrement
+                & \BestGroundGridSourcesConstantDepthDepth
+                & \multirow{4}{*}{
+                    \BestGroundGridSourcesConstantDepthScore
+                  } \\
             &
@@
                 & \GroundGridSourcesConstantDepthSpacing
-                      \GroundGridSourcesConstantDepthSpacingIncrement \\
+                  \GroundGridSourcesConstantDepthSpacingIncrement
+                & \BestGroundGridSourcesConstantDepthSpacing
+                & \\
             &
@@
                 & \GroundGridSourcesConstantDepthPad
-                     \GroundGridSourcesConstantDepthPadIncrement \\
+                  \GroundGridSourcesConstantDepthPadIncrement
+                & \BestGroundGridSourcesConstantDepthPad
+                & \\
             &
@@
                 & \GroundGridSourcesConstantDepthDamping
-                      \GroundGridSourcesConstantDepthDampingIncrement \\
+                  \GroundGridSourcesConstantDepthDampingIncrement
+                & \BestGroundGridSourcesConstantDepthDamping
+                & \\
     \end{tabular}
@@
         \textbf{Source layout}
-            & \textbf{Depth type}
-            & \textbf{Parameters}
+            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
             & \textbf{Values} \\

### 2020-03-05 manuscript/manuscript.tex
Center the whole Depth Types column

@@
     \label{tab:parameters-ground-survey}
-    \begin{tabular}{c l l c c c}
+    \begin{tabular}{c c l c c c}
         \textbf{Source layout}
-            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \textbf{Depth type}
             & \multicolumn{1}{c}{\textbf{Parameters}}
@@
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{c l l c}
+    \begin{tabular}{c c l c}
         \textbf{Source layout}
-            & \multicolumn{1}{c}{\textbf{Depth type}}
+            & \textbf{Depth type}
             & \multicolumn{1}{c}{\textbf{Parameters}}

### 2020-03-05 eql_source_layouts/__init__.py
Add latex_best_parameters function
The new function formats best parameters into LaTeX variables.

@@ -4,7 +4,12 @@ from ._version import get_versions
 from .layouts import source_bellow_data, block_median_sources, grid_sources
 from .synthetic_model import synthetic_model
 from .plot import plot_prediction
-from .latex_variables import latex_variables, latex_parameters, format_variable_name
+from .latex_variables import (
+    latex_variables,
+    latex_parameters,
+    format_variable_name,
+    latex_best_parameters,
+)
 from .utils import (
     combine_parameters,
     get_best_prediction,

### 2020-03-05 eql_source_layouts/latex_variables.py

@@ -21,6 +21,28 @@ def latex_variables(variable, number, unit=None, fmt=None):
     return tex_line
 
 
+def latex_best_parameters(best_parameters, survey, layout, depth_type):
+    """
+    Create LaTeX variables for best parameters
+    """
+    tex_lines = []
+    for parameter, value in best_parameters.items():
+        if parameter in ("depth_type", "layout", "height"):
+            continue
+        variable_name = format_variable_name(
+            "_".join(["best", survey, layout, depth_type, parameter])
+        )
+        if parameter == "damping":
+            value = r"\num{{e{:.0f}}}".format(np.log10(value))
+            fmt = None
+        elif parameter == "score":
+            fmt = ".3f"
+        else:
+            fmt = _determine_fmt(value)
+        tex_lines.append(latex_variables(variable_name, value, fmt=fmt))
+    return tex_lines
+
+
 def latex_parameters(parameters, survey):
     """
     Create list or ranges of parameters for each source distribution as LaTeX variables

### 2020-03-05 notebooks/02-grid-ground-data.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.3
+#       jupytext_version: 1.3.4
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -32,6 +32,7 @@ from eql_source_layouts import (
     predictions_to_datasets,
     latex_parameters,
     latex_variables,
+    latex_best_parameters,
 )
 
 # -
@@ -329,32 +330,17 @@ plt.show()
 #
 # Save best predictions parameters as LaTeX variables
 
-# +
-tex_variables = []
+tex_lines = []
 for dataset in best_predictions:
     for depth_type in dataset:
         parameters = dataset[depth_type].attrs
         layout = parameters["layout"]
-        for parameter, value in parameters.items():
-            if parameter in ("depth_type", "layout", "height"):
-                continue
-            fmt = ""
-            variable_name = (
-                "_".join(["best", "ground", layout, depth_type, parameter])
-                .replace("_", " ")
-                .title()
-                .replace(" ", "")
-            )
-            if parameter in ("spacing", "depth"):
-                fmt = ".1f"
-            if parameter == "score":
-                fmt = ".3f"
-            if value == 0:
-                fmt = ".0f"
-            tex_variables.append(latex_variables(variable_name, value, fmt=fmt))
+        tex_lines.extend(
+            latex_best_parameters(parameters, "ground", layout, depth_type)
+        )
 
 
 with open(
     os.path.join("..", "manuscript", "best_parameters_ground_survey.tex"), "w"
 ) as f:
-    f.write("\n".join(tex_variables,))
+    f.write("\n".join(tex_lines,))

### 2020-03-05 notebooks/03-grid-airborne-data.py
Use latex_best_parameters on airborne nb

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.3
+#       jupytext_version: 1.3.4
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -37,7 +37,7 @@ from eql_source_layouts import (
     get_best_prediction,
     predictions_to_datasets,
     latex_parameters,
-    latex_variables,
+    latex_best_parameters,
 )
 
 # -
@@ -331,32 +331,17 @@ plt.show()
 #
 # Save best predictions parameters as LaTeX variables
 
-# +
-tex_variables = []
+tex_lines = []
 for dataset in best_predictions:
     for depth_type in dataset:
         parameters = dataset[depth_type].attrs
         layout = parameters["layout"]
-        for parameter, value in parameters.items():
-            if parameter in ("depth_type", "layout", "height"):
-                continue
-            fmt = ""
-            variable_name = (
-                "_".join(["best", "airborne", layout, depth_type, parameter])
-                .replace("_", " ")
-                .title()
-                .replace(" ", "")
-            )
-            if parameter in ("spacing", "depth"):
-                fmt = ".1f"
-            if parameter == "score":
-                fmt = ".3f"
-            if value == 0:
-                fmt = ".0f"
-            tex_variables.append(latex_variables(variable_name, value, fmt=fmt))
+        tex_lines.extend(
+            latex_best_parameters(parameters, "airborne", layout, depth_type)
+        )
 
 
 with open(
     os.path.join("..", "manuscript", "best_parameters_airborne_survey.tex"), "w"
 ) as f:
-    f.write("\n".join(tex_variables,))
+    f.write("\n".join(tex_lines,))

### 2020-03-09 manuscript/manuscript.tex
Remove forgotten textbf on table
Replace bellow for below

--- 2020-03-05 manuscript/manuscript.tex
@@
 \usepackage{multirow}
-\usepackage{booktabs}
 
@@
 \section{Introduction}
-
-\num{1e3}
 
@@
 The \emph{regular grid} creates an homogeneous distribution of point sources
-bellow the surveyed region.
+below the surveyed region.
 The distance between sources is controlled by the grid spacing parameter.
@@
 
-The \emph{source beneath data} layout locates one source bellow each
+The \emph{source below data} layout locates one source below each
 observation point, therefore the number of sources will be equal to the number
@@
 carried out.
-In contrast, the \emph{source beneath data} layout is more likely to accurately
+In contrast, the \emph{source below data} layout is more likely to accurately
 fit the observed data with much less sources, reducing the computational load
@@
 
-When working with airborne surveys, the \emph{source beneath data} may
+When working with airborne surveys, the \emph{source below data} may
 generate an anisotropic distribution of sources by locating too many sources
@@
         inside each block. Blocks without any observation point are ignored.
-    \item Locating one point source bellow each block averaged coordinate.
+    \item Locating one point source below each block averaged coordinate.
         (see Fig.~\ref{fig:block-median-sources}(c)).
@@
 The number of sources created by this new distribution will be less or equal to
-the ones created by the \emph{source beneath data} and the \emph{regular
+the ones created by the \emph{source below data} and the \emph{regular
 grid} with the same spacing.
@@
 
-One possible solution is to locate each source bellow its corresponding
+One possible solution is to locate each source below its corresponding
 observation (or block averaged) point at a constant \emph{relative depth}
@@
 In case our survey presents heavily clustered data points on some areas, we may
-want the sources bellow that region to be shallower in order to reproduce the
+want the sources below that region to be shallower in order to reproduce the
 high frequencies measured by these clustered observation points.
@@
     \begin{tabular}{lccc}
-        & Source bellow data & Block averaged sources & Grid sources \\ \hline
+        & Source below data & Block averaged sources & Grid sources \\ \hline
         Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
@@
     \begin{tabular}{l c c c}
-        & \textbf{Sources bellow data} & \textbf{Block median sources}
+        & \textbf{Sources below data} & \textbf{Block median sources}
         & \textbf{Grid sources} \\
@@
         \hline
-        Depth (m) & \BestGroundSourceBellowDataConstantDepthDepth
+        Depth (m) & \BestGroundSourceBelowDataConstantDepthDepth
                    & \BestGroundBlockMedianSourcesConstantDepthDepth
@@
             & \BestGroundGridSourcesConstantDepthPad \\
-        Damping & \BestGroundSourceBellowDataConstantDepthDamping
+        Damping & \BestGroundSourceBelowDataConstantDepthDamping
                 & \BestGroundBlockMedianSourcesConstantDepthDamping
@@
         \textbf{R$^2$ score}
-                & \textbf{\BestGroundSourceBellowDataConstantDepthScore}
+                & \textbf{\BestGroundSourceBelowDataConstantDepthScore}
                 & \textbf{\BestGroundBlockMedianSourcesConstantDepthScore}
@@
         \cline{1-3}
-        Depth (m) & \BestGroundSourceBellowDataRelativeDepthDepth
+        Depth (m) & \BestGroundSourceBelowDataRelativeDepthDepth
                    & \BestGroundBlockMedianSourcesRelativeDepthDepth
@@
                 & \\
-        Damping & \BestGroundSourceBellowDataRelativeDepthDamping
+        Damping & \BestGroundSourceBelowDataRelativeDepthDamping
                 & \BestGroundBlockMedianSourcesRelativeDepthDamping
@@
         \textbf{R$^2$ score}
-                & \textbf{\BestGroundSourceBellowDataRelativeDepthScore}
+                & \textbf{\BestGroundSourceBelowDataRelativeDepthScore}
                 & \textbf{\BestGroundBlockMedianSourcesRelativeDepthScore}
@@
         \cline{1-3}
-        Depth (m) & \BestGroundSourceBellowDataVariableDepthDepth
+        Depth (m) & \BestGroundSourceBelowDataVariableDepthDepth
                    & \BestGroundBlockMedianSourcesVariableDepthDepth
                    & \\
-        Depth factor & \BestGroundSourceBellowDataVariableDepthDepthFactor
+        Depth factor & \BestGroundSourceBelowDataVariableDepthDepthFactor
                      & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
                      & \\
-        K nearest & \BestGroundSourceBellowDataVariableDepthKNearest
+        K nearest & \BestGroundSourceBelowDataVariableDepthKNearest
                   & \BestGroundBlockMedianSourcesVariableDepthKNearest
@@
                      & \\
-        Damping & \BestGroundSourceBellowDataVariableDepthDamping
+        Damping & \BestGroundSourceBelowDataVariableDepthDamping
                 & \BestGroundBlockMedianSourcesVariableDepthDamping
@@
         \textbf{R$^2$ score}
-                & \textbf{\BestGroundSourceBellowDataVariableDepthScore}
+                & \textbf{\BestGroundSourceBelowDataVariableDepthScore}
                 & \textbf{\BestGroundBlockMedianSourcesVariableDepthScore}
@@
         \hline
-        Depth (m) & \BestAirborneSourceBellowDataConstantDepthDepth
+        Depth (m) & \BestAirborneSourceBelowDataConstantDepthDepth
                    & \BestAirborneBlockMedianSourcesConstantDepthDepth
@@
             & \BestAirborneGridSourcesConstantDepthPad \\
-        Damping & \BestAirborneSourceBellowDataConstantDepthDamping
+        Damping & \BestAirborneSourceBelowDataConstantDepthDamping
                 & \BestAirborneBlockMedianSourcesConstantDepthDamping
                 & \BestAirborneGridSourcesConstantDepthDamping \\
+        R$^2$ score & \BestAirborneSourceBelowDataConstantDepthScore
+                    & \BestAirborneBlockMedianSourcesConstantDepthScore
+                    & \BestAirborneGridSourcesConstantDepthScore \\
         \textbf{R$^2$ score}
-                & \textbf{\BestAirborneSourceBellowDataConstantDepthScore}
+                & \textbf{\BestAirborneSourceBelowDataConstantDepthScore}
                 & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
@@
         \cline{1-3}
-        Depth (m) & \BestAirborneSourceBellowDataRelativeDepthDepth
+        Depth (m) & \BestAirborneSourceBelowDataRelativeDepthDepth
                    & \BestAirborneBlockMedianSourcesRelativeDepthDepth
@@
                 & \\
-        Damping & \BestAirborneSourceBellowDataRelativeDepthDamping
+        Damping & \BestAirborneSourceBelowDataRelativeDepthDamping
                 & \BestAirborneBlockMedianSourcesRelativeDepthDamping
@@
         \textbf{R$^2$ score}
-                & \textbf{\BestAirborneSourceBellowDataRelativeDepthScore}
+                & \textbf{\BestAirborneSourceBelowDataRelativeDepthScore}
                 & \textbf{\BestAirborneBlockMedianSourcesRelativeDepthScore}
@@
         \cline{1-3}
-        Depth (m) & \BestAirborneSourceBellowDataVariableDepthDepth
+        Depth (m) & \BestAirborneSourceBelowDataVariableDepthDepth
                    & \BestAirborneBlockMedianSourcesVariableDepthDepth
                    & \\
-        Depth factor & \BestAirborneSourceBellowDataVariableDepthDepthFactor
+        Depth factor & \BestAirborneSourceBelowDataVariableDepthDepthFactor
                      & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
                      & \\
-        K nearest & \BestAirborneSourceBellowDataVariableDepthKNearest
+        K nearest & \BestAirborneSourceBelowDataVariableDepthKNearest
                   & \BestAirborneBlockMedianSourcesVariableDepthKNearest
@@
                      & \\
-        Damping & \BestAirborneSourceBellowDataVariableDepthDamping
+        Damping & \BestAirborneSourceBelowDataVariableDepthDamping
                 & \BestAirborneBlockMedianSourcesVariableDepthDamping
@@
         \textbf{R$^2$ score}
-                & \textbf{\BestAirborneSourceBellowDataVariableDepthScore}
+                & \textbf{\BestAirborneSourceBelowDataVariableDepthScore}
                 & \textbf{\BestAirborneBlockMedianSourcesVariableDepthScore}
@@
     \label{tab:parameters-ground-survey}
-    \begin{tabular}{c l l c}
-        \textbf{Source layout}
-            & \textbf{Depth type}
-            & \textbf{Parameters}
-            & \textbf{Values} \\
-        \toprule
-
-        \multirow{8}{*}{Source Bellow Data}
-            & \multirow{2}{*}{Constant Depth}
-                & Depth (m)
-                & \GroundSourceBellowDataConstantDepthDepth
-                  \GroundSourceBellowDataConstantDepthDepthIncrement \\
-            &
-                & Damping
-                & \GroundSourceBellowDataConstantDepthDamping
-                  \GroundSourceBellowDataConstantDepthDampingIncrement \\
-            \cmidrule{2-4}
-            & \multirow{2}{*}{Relative Depth}
-                & Depth (m)
-                & \GroundSourceBellowDataRelativeDepthDepth
-                  \GroundSourceBellowDataRelativeDepthDepthIncrement \\
-            &
-                & Damping
-                & \GroundSourceBellowDataRelativeDepthDamping
-                  \GroundSourceBellowDataRelativeDepthDampingIncrement \\
-            \cmidrule{2-4}
-            & \multirow{4}{*}{Variable Depth}
-                & Depth (m)
-                & \GroundSourceBellowDataVariableDepthDepth
-                  \GroundSourceBellowDataVariableDepthDepthIncrement \\
-            &
-                & Depth factor
-                & \GroundSourceBellowDataVariableDepthDepthFactor
-                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
-            &
-                & K nearest
-                & \GroundSourceBellowDataVariableDepthKNearest
-                  \GroundSourceBellowDataVariableDepthKNearestIncrement \\
-            &
-                & Damping
-                & \GroundSourceBellowDataVariableDepthDamping
-                  \GroundSourceBellowDataVariableDepthDampingIncrement \\
-        \midrule
-
-        \multirow{11}{*}{Block median sources}
-            & \multirow{3}{*}{Constant Depth}
-                & Depth (m)
+    \begin{tabular}{l c c c}
+        & \textbf{Sources below data} & \textbf{Block median sources}
+        & \textbf{Grid sources} \\
+
+        \textbf{Constant depth} & & & \\
+        \hline
+        Depth (km) & \GroundSourceBelowDataConstantDepthDepth
                    & \GroundBlockMedianSourcesConstantDepthDepth
-                  \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
-            &
-                & Spacing (m)
+                   & \GroundGridSourcesConstantDepthDepth \\
+        Spacing (km) & -
                      & \GroundBlockMedianSourcesConstantDepthSpacing
-                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
-            &
-                & Damping
-                & \GroundBlockMedianSourcesConstantDepthDamping
-                  \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
-            \cmidrule{2-4}
-            & \multirow{3}{*}{Relative Depth}
-                & Depth (m)
+                     & \GroundGridSourcesConstantDepthSpacing \\
+        Pad & -
+            & -
+            & \GroundGridSourcesConstantDepthPad \\
+
+        & & & \\
+        \textbf{Relative depth} & & & \\
+        \cline{1-3}
+        Depth (km) & \GroundSourceBelowDataRelativeDepthDepth
                    & \GroundBlockMedianSourcesRelativeDepthDepth
-                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
-            &
-                & Spacing (m)
+                   & \\
+        Spacing (km) & -
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
-                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
-            &
-                & Damping
-                & \GroundBlockMedianSourcesRelativeDepthDamping
-                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
-            \cmidrule{2-4}
-            & \multirow{5}{*}{Variable Depth}
-                & Depth (m)
+                & \\
+
+        & & & \\
+        \textbf{Variable depth} & & & \\
+        \cline{1-3}
+        Depth (km) & \GroundSourceBelowDataVariableDepthDepth
                    & \GroundBlockMedianSourcesVariableDepthDepth
-                  \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
-            &
-                & Depth factor
+                   & \\
+        Depth factor & \GroundSourceBelowDataVariableDepthDepthFactor
                      & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
-            &
-                & K nearest
+                     & \\
+        K nearest & \GroundSourceBelowDataVariableDepthKNearest
                   & \GroundBlockMedianSourcesVariableDepthKNearest
-                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
-            &
-                & Spacing (m)
+                  & \\
+        Spacing (km) & -
                      & \GroundBlockMedianSourcesVariableDepthSpacing
-                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
-            &
-                & Damping
-                & \GroundBlockMedianSourcesVariableDepthDamping
-                  \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
-        \midrule
-
-        \multirow{4}{*}{Grid Sources}
-            & \multirow{4}{*}{Constant Depth}
-                & Depth (m)
-                    & \GroundGridSourcesConstantDepthDepth
-                      \GroundGridSourcesConstantDepthDepthIncrement \\
-            &
-                & Spacing (m)
-                    & \GroundGridSourcesConstantDepthSpacing
-                      \GroundGridSourcesConstantDepthSpacingIncrement \\
-            &
-                & Pad
-                    & \GroundGridSourcesConstantDepthPad
-                     \GroundGridSourcesConstantDepthPadIncrement \\
-            &
-                & Damping
-                    & \GroundGridSourcesConstantDepthDamping
-                      \GroundGridSourcesConstantDepthDampingIncrement \\
+                     & \\
     \end{tabular}
@@
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{c l l c}
-        \textbf{Source layout}
-            & \textbf{Depth type}
-            & \textbf{Parameters}
-            & \textbf{Values} \\
-        \toprule
-
-        \multirow{8}{*}{Source Bellow Data}
-            & \multirow{2}{*}{Constant Depth}
-                & Depth (m)
-                & \AirborneSourceBellowDataConstantDepthDepth
-                  \AirborneSourceBellowDataConstantDepthDepthIncrement \\
-            &
-                & Damping
-                & \AirborneSourceBellowDataConstantDepthDamping
-                  \AirborneSourceBellowDataConstantDepthDampingIncrement \\
-            \cmidrule{2-4}
-            & \multirow{2}{*}{Relative Depth}
-                & Depth (m)
-                & \AirborneSourceBellowDataRelativeDepthDepth
-                  \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
-            &
-                & Damping
-                & \AirborneSourceBellowDataRelativeDepthDamping
-                  \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
-            \cmidrule{2-4}
-            & \multirow{4}{*}{Variable Depth}
-                & Depth (m)
-                & \AirborneSourceBellowDataVariableDepthDepth
-                  \AirborneSourceBellowDataVariableDepthDepthIncrement \\
-            &
-                & Depth factor
-                & \AirborneSourceBellowDataVariableDepthDepthFactor
-                  \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
-            &
-                & K nearest
-                & \AirborneSourceBellowDataVariableDepthKNearest
-                  \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
-            &
-                & Damping
-                & \AirborneSourceBellowDataVariableDepthDamping
-                  \AirborneSourceBellowDataVariableDepthDampingIncrement \\
-        \midrule
-
-        \multirow{11}{*}{Block median sources}
-            & \multirow{3}{*}{Constant Depth}
-                & Depth (m)
+    \begin{tabular}{l c c c}
+        & \textbf{Sources below data} & \textbf{Block median sources}
+        & \textbf{Grid sources} \\
+
+        \textbf{Constant depth} & & & \\
+        \hline
+        Depth (km) & \AirborneSourceBelowDataConstantDepthDepth
                    & \AirborneBlockMedianSourcesConstantDepthDepth
-                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
-            &
-                & Spacing (m)
+                   & \AirborneGridSourcesConstantDepthDepth \\
+        Spacing (km) & -
                      & \AirborneBlockMedianSourcesConstantDepthSpacing
-                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
-            &
-                & Damping
-                & \AirborneBlockMedianSourcesConstantDepthDamping
-                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
-            \cmidrule{2-4}
-            & \multirow{3}{*}{Relative Depth}
-                & Depth (m)
+                     & \AirborneGridSourcesConstantDepthSpacing \\
+        Pad & -
+            & -
+            & \AirborneGridSourcesConstantDepthPad \\
+
+        & & & \\
+        \textbf{Relative depth} & & & \\
+        \cline{1-3}
+        Depth (km) & \AirborneSourceBelowDataRelativeDepthDepth
                    & \AirborneBlockMedianSourcesRelativeDepthDepth
-                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
-            &
-                & Spacing (m)
+                   & \\
+        Spacing (km) & -
                      & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
-            &
-                & Damping
-                & \AirborneBlockMedianSourcesRelativeDepthDamping
-                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
-            \cmidrule{2-4}
-            & \multirow{5}{*}{Variable Depth}
-                & Depth (m)
+                     & \\
+
+        & & & \\
+        \textbf{Variable depth} & & & \\
+        \cline{1-3}
+        Depth (km) & \AirborneSourceBelowDataVariableDepthDepth
                    & \AirborneBlockMedianSourcesVariableDepthDepth
-                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
-            &
-                & Depth factor
+                   & \\
+        Depth factor & \AirborneSourceBelowDataVariableDepthDepthFactor
                      & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
-            &
-                & K nearest
+                     & \\
+        K nearest & \AirborneSourceBelowDataVariableDepthKNearest
                   & \AirborneBlockMedianSourcesVariableDepthKNearest
-                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
-            &
-                & Spacing (m)
+                  & \\
+        Spacing (km) & -
                      & \AirborneBlockMedianSourcesVariableDepthSpacing
-                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
-            &
-                & Damping
-                & \AirborneBlockMedianSourcesVariableDepthDamping
-                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
-        \midrule
-
-        \multirow{4}{*}{Grid Sources}
-            & \multirow{4}{*}{Constant Depth}
-                & Depth (m)
-                    & \AirborneGridSourcesConstantDepthDepth
-                      \AirborneGridSourcesConstantDepthDepthIncrement \\
-            &
-                & Spacing (m)
-                    & \AirborneGridSourcesConstantDepthSpacing
-                      \AirborneGridSourcesConstantDepthSpacingIncrement \\
-            &
-                & Pad
-                    & \AirborneGridSourcesConstantDepthPad
-                      \AirborneGridSourcesConstantDepthPadIncrement \\
-            &
-                & Damping
-                    & \AirborneGridSourcesConstantDepthDamping
-                      \AirborneGridSourcesConstantDepthDampingIncrement \\
+                     & \\
     \end{tabular}

### 2020-03-09 notebooks/02-grid-ground-data.py

@@ -58,7 +58,7 @@ field_units = "mGal"
 # Define set of interpolation parameters
 # ======================================
 # Define a list of source layouts
-layouts = ["source_bellow_data", "block_median_sources", "grid_sources"]
+layouts = ["source_below_data", "block_median_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
 dampings = [None, 1e-4, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2]
 # Define depht values
@@ -83,15 +83,15 @@ block_spacings = [1_000, 2_000, 3_000, 4_000]
 # +
 parameters = {layout: {} for layout in layouts}
 
-# Source bellow data
-layout = "source_bellow_data"
+# Source below data
+layout = "source_below_data"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths.tolist()
 )
 
-# Source bellow data
-layout = "source_bellow_data"
+# Source below data
+layout = "source_below_data"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths

### 2020-03-09 notebooks/03-grid-airborne-data.py

@@ -63,7 +63,7 @@ field_units = "mGal"
 # Define set of interpolation parameters
 # ======================================
 # Define a list of source layouts
-layouts = ["source_bellow_data", "block_median_sources", "grid_sources"]
+layouts = ["source_below_data", "block_median_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
 dampings = [None, 1e-4, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2]
 # Define depht values
@@ -88,8 +88,8 @@ block_spacings = [1_000, 2_000, 3_000, 4_000]
 # +
 parameters = {layout: {} for layout in layouts}
 
-# Source bellow data
-layout = "source_bellow_data"
+# Source below data
+layout = "source_below_data"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths

### 2020-03-09 notebooks/depth-types-schematics.py

@@ -24,7 +24,7 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 
-from eql_source_layouts.layouts import source_bellow_data
+from eql_source_layouts.layouts import source_below_data
 
 # -
 
@@ -37,36 +37,36 @@ display(survey)
 
 points = {}
 
-# Source bellow data with constant depth
+# Source below data with constant depth
 
 # +
 depth_type = "constant_depth"
 coordinates = (survey.easting, np.zeros_like(survey.easting), survey.height)
-points[depth_type] = source_bellow_data(coordinates, depth_type=depth_type, depth=150)
+points[depth_type] = source_below_data(coordinates, depth_type=depth_type, depth=150)
 
 plt.scatter(coordinates[0], coordinates[2])
 plt.scatter(points[depth_type][0], points[depth_type][2])
 plt.show()
 # -
 
-# Source bellow data with relative depth
+# Source below data with relative depth
 
 # +
 depth_type = "relative_depth"
 coordinates = (survey.easting, np.zeros_like(survey.easting), survey.height)
-points[depth_type] = source_bellow_data(coordinates, depth_type=depth_type, depth=150)
+points[depth_type] = source_below_data(coordinates, depth_type=depth_type, depth=150)
 
 plt.scatter(coordinates[0], coordinates[2])
 plt.scatter(points[depth_type][0], points[depth_type][2])
 plt.show()
 # -
 
-# Source bellow data with variable depth
+# Source below data with variable depth
 
 # +
 depth_type = "variable_depth"
 coordinates = (survey.easting, np.zeros_like(survey.easting), survey.height)
-points[depth_type] = source_bellow_data(
+points[depth_type] = source_below_data(
     coordinates, depth_type=depth_type, depth_factor=1, depth=100, k_nearest=3
 )
 

### 2020-03-09 notebooks/source-distributions.py

@@ -22,7 +22,7 @@
 # a combination of a source layout and a depth type.
 # Lets define three layouts of point sources:
 #
-# 1. **Source bellow data**: One source point beneath each data point
+# 1. **Source below data**: One source point beneath each data point
 # 2. **Block averaged sources**: Split the region in blocks of equal size, compute the
 #    median coordinate of the data points per block, and put one point source beneath
 #    this block-median coordinate.
@@ -44,7 +44,7 @@
 #
 # |    | Constant depth | Relative depth | Variable depth |
 # | -- |----------------|----------------|----------------|
-# | **Source bellow data** | ✅ | ✅ | ✅ |
+# | **Source below data** | ✅ | ✅ | ✅ |
 # | **Block averaged sources** | ✅ | ✅ | ✅ |
 # | **Grid of sources** | ✅ | ❌ | ❌ |
 #
@@ -76,7 +76,7 @@ ground_results_dir = os.path.join("..", "results", "ground_survey")
 airborne_results_dir = os.path.join("..", "results", "airborne_survey")
 
 # Define dictionaries where the source distributions will be stored
-layouts = ["source_bellow_data", "block_median_sources", "grid_sources"]
+layouts = ["source_below_data", "block_median_sources", "grid_sources"]
 source_distributions = {layout: {} for layout in layouts}
 
 # Define a region for the synthetic survey
@@ -92,8 +92,8 @@ spacing = 4000
 # =====================================================
 parameters = {layout: {} for layout in layouts}
 
-# ... for source bellow data layout
-layout = "source_bellow_data"
+# ... for source below data layout
+layout = "source_below_data"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = {
     "depth_type": depth_type,

### 2020-03-10 notebooks/03-grid-airborne-data.py
Rerun all notebooks

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.3
+#       jupytext_version: 1.3.5
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -235,9 +235,7 @@ for layout in scores:
         )
 # -
 
-# ## 5. Plot best predictions
-
-# Read best predictions from saved files
+# ### Read best predictions from saved files
 
 best_predictions = []
 for layout in layouts:
@@ -247,7 +245,7 @@ for layout in layouts:
         )
     )
 
-# Plot best predictions
+# ## Plot best predictions
 
 for dataset in best_predictions:
     for depth_type in dataset:
@@ -260,7 +258,7 @@ for dataset in best_predictions:
         plot_prediction(prediction, target, units=field_units)
 
 
-# ## 6. Plot and compare all best predictions
+# ## Plot and compare all best predictions
 
 # +
 # We will use the same boundary value for each plot in order to
@@ -360,4 +358,3 @@ with open(
     os.path.join("..", "manuscript", "best_parameters_airborne_survey.tex"), "w"
 ) as f:
     f.write("\n".join(tex_variables,))
-# -

### 2020-03-10 notebooks/source-distributions.py

@@ -7,7 +7,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.2
+#       jupytext_version: 1.3.5
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python

### 2020-03-10 eql_source_layouts/tests/test_layouts.py
Standarize source layouts names (#34)
Replace "beneath" for "below" when naming the layout.

@@ -10,7 +10,7 @@ from ..layouts import (
     constant_depth,
     relative_depth,
     variable_depth,
-    source_bellow_data,
+    source_below_data,
     block_median_sources,
     grid_sources,
 )
@@ -73,7 +73,7 @@ def test_variable_depth(coordinates):
     assert not np.allclose(coordinates[2] - depth, points[2])
     # Check if depths are not all equal
     assert not np.allclose(points[2][0], points[2])
-    # Check if all masses are bellow relative depth
+    # Check if all masses are below relative depth
     assert np.all(points[2] < coordinates[2] - depth)
     # Set depth_factor equal to zero and check if relative depth is recovered
     points = variable_depth(
@@ -107,11 +107,11 @@ def test_variable_depth_analytical(coordinates):
 # Source distributions
 # --------------------
 
-# Sources bellow data
+# Sources below data
 # -------------------
-def test_source_bellow_data(coordinates):
+def test_source_below_data(coordinates):
     """
-    Check if source_bellow_data puts sources beneath data points
+    Check if source_below_data puts sources beneath data points
     """
     depth = 100
     depth_factor = 1
@@ -122,22 +122,22 @@ def test_source_bellow_data(coordinates):
         "variable_depth": {"depth_factor": depth_factor, "k_nearest": k_nearest},
     }
     for depth_type, params in parameters.items():
-        points = source_bellow_data(
+        points = source_below_data(
             coordinates, depth_type=depth_type, depth=depth, **params
         )
         npt.assert_allclose(points[0], coordinates[0])
         npt.assert_allclose(points[1], coordinates[1])
 
 
-def test_source_bellow_data_kwargs(coordinates):
+def test_source_below_data_kwargs(coordinates):
     """
-    Check if extra kwargs on source_bellow_data are ignored
+    Check if extra kwargs on source_below_data are ignored
     """
     depth_type = "constant_depth"
     depth = 100
     npt.assert_allclose(
-        source_bellow_data(coordinates, depth_type=depth_type, depth=depth,),
-        source_bellow_data(
+        source_below_data(coordinates, depth_type=depth_type, depth=depth,),
+        source_below_data(
             coordinates, depth_type=depth_type, depth=depth, blabla=3.1415
         ),
     )
@@ -243,6 +243,6 @@ def test_invalid_depth_type(coordinates):
     """
     depth_type = "not a valid depth_type"
     with pytest.raises(ValueError):
[…]

### 2020-03-10 manuscript/manuscript.tex

@@
     \label{fig:block-median-sources}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
+    \caption{
+        Source layouts.
+        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
+            points that resemble a ground survey.
+        (b) Location of the \SourceLayoutsSchematicsSourceBellowData{} sources
+            obtained through the \emph{sources beneath data} layout.
+        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
+            sources obtained through the \emph{block averaged sources} layout.
+        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
+            obtained through the \emph{grid sources} layout.
+    }
+    \label{fig:source-layouts-schematics}
 \end{figure*}

### 2020-03-10 manuscript/manuscript.tex
Create figures of gridding results for both surveys (#32)
Create figures containing the differences between the target grid and the best
predictions made by each source distribution for each synthetic survey.

--- 2020-03-09 manuscript/manuscript.tex
@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
+    \caption{
+        Differences between gravitational effects measured on the target grid
+        and the ones produced by the best prediction made by each source
+        distribution based on the synthetic ground survey.
+    }
+    \label{fig:ground-survey-differences}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
+    \caption{
+        Differences between gravitational effects measured on the target grid
+        and the ones produced by the best prediction made by each source
+        distribution based on the synthetic airborne survey.
+    }
+    \label{fig:airborne-survey-differences}
+\end{figure*}
+
 \begin{table*}

### 2020-03-10 manuscript/manuscript.tex
Replace Bellow for Below on LaTeX variable name

@@
             points that resemble a ground survey.
-        (b) Location of the \SourceLayoutsSchematicsSourceBellowData{} sources
+        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
             obtained through the \emph{sources beneath data} layout.
@@
                 & \BestAirborneGridSourcesConstantDepthDamping \\
-        R$^2$ score & \BestAirborneSourceBelowDataConstantDepthScore
-                    & \BestAirborneBlockMedianSourcesConstantDepthScore
-                    & \BestAirborneGridSourcesConstantDepthScore \\
         \textbf{R$^2$ score}
@@
     \label{tab:parameters-ground-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources below data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
-        \hline
-        Depth (km) & \GroundSourceBelowDataConstantDepthDepth
+    \begin{tabular}{c c l c c c}
+        \textbf{Source layout}
+            & \textbf{Depth type}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
+            & \textbf{Values}
+            & \textbf{Best}
+            & \textbf{R$^2$ score} \\
+        \toprule
+
+        \multirow{8}{*}{Source Bellow Data}
+            & \multirow{2}{*}{Constant Depth}
+                & Depth (m)
+                & \GroundSourceBellowDataConstantDepthDepth
+                  \GroundSourceBellowDataConstantDepthDepthIncrement
+                & \BestGroundSourceBellowDataConstantDepthDepth
+                & \multirow{2}{*}{
+                    \BestGroundSourceBellowDataConstantDepthScore
+                  } \\
+            &
+                & Damping
+                & \GroundSourceBellowDataConstantDepthDamping
+                  \GroundSourceBellowDataConstantDepthDampingIncrement
+                & \BestGroundSourceBellowDataConstantDepthDamping
+                & \\
+            \cmidrule{2-6}
+            & \multirow{2}{*}{Relative Depth}
+                & Depth (m)
+                & \GroundSourceBellowDataRelativeDepthDepth
+                  \GroundSourceBellowDataRelativeDepthDepthIncrement
+                & \BestGroundSourceBellowDataRelativeDepthDepth
+                & \multirow{2}{*}{
+                    \BestGroundSourceBellowDataRelativeDepthScore
+                  } \\
+            &
+                & Damping
+                & \GroundSourceBellowDataRelativeDepthDamping
+                  \GroundSourceBellowDataRelativeDepthDampingIncrement
+                & \BestGroundSourceBellowDataRelativeDepthDamping
+                & \\
+            \cmidrule{2-6}
+            & \multirow{4}{*}{Variable Depth}
+                & Depth (m)
+                & \GroundSourceBellowDataVariableDepthDepth
+                  \GroundSourceBellowDataVariableDepthDepthIncrement
+                & \BestGroundSourceBellowDataVariableDepthDepth
+                & \multirow{4}{*}{
+                    \BestGroundSourceBellowDataVariableDepthScore
+                  } \\
+            &
+                & Depth factor
+                & \GroundSourceBellowDataVariableDepthDepthFactor
+                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement
+                & \BestGroundSourceBellowDataVariableDepthDepthFactor
+                & \\
+            &
+                & K nearest
+                & \GroundSourceBellowDataVariableDepthKNearest
+                  \GroundSourceBellowDataVariableDepthKNearestIncrement
+                & \BestGroundSourceBellowDataVariableDepthKNearest
+                & \\
+            &
+                & Damping
+                & \GroundSourceBellowDataVariableDepthDamping
+                  \GroundSourceBellowDataVariableDepthDampingIncrement
+                & \BestGroundSourceBellowDataVariableDepthDamping
+                & \\
+        \midrule
+
+        \multirow{11}{*}{Block median sources}
+            & \multirow{3}{*}{Constant Depth}
+                & Depth (m)
                 & \GroundBlockMedianSourcesConstantDepthDepth
-                   & \GroundGridSourcesConstantDepthDepth \\
-        Spacing (km) & -
+                  \GroundBlockMedianSourcesConstantDepthDepthIncrement
+                & \BestGroundBlockMedianSourcesConstantDepthDepth
+                & \multirow{3}{*}{
+                    \BestGroundBlockMedianSourcesConstantDepthScore
+                  } \\
+            &
+                & Spacing (m)
                 & \GroundBlockMedianSourcesConstantDepthSpacing
-                     & \GroundGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \GroundGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \GroundSourceBelowDataRelativeDepthDepth
+                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement
+                & \BestGroundBlockMedianSourcesConstantDepthSpacing
+                & \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesConstantDepthDamping
+                  \GroundBlockMedianSourcesConstantDepthDampingIncrement
+                & \BestGroundBlockMedianSourcesConstantDepthDamping
+                & \\
+            \cmidrule{2-6}
+            & \multirow{3}{*}{Relative Depth}
+                & Depth (m)
                 & \GroundBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (km) & -
+                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement
+                & \BestGroundBlockMedianSourcesRelativeDepthDepth
+                & \multirow{3}{*}{
+                    \BestGroundBlockMedianSourcesRelativeDepthScore
+                  } \\
+            &
+                & Spacing (m)
                 & \GroundBlockMedianSourcesRelativeDepthSpacing
-                & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \GroundSourceBelowDataVariableDepthDepth
+                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement
+                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
+                & \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesRelativeDepthDamping
+                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement
+                & \BestGroundBlockMedianSourcesRelativeDepthDamping
+                & \\
+            \cmidrule{2-6}
+            & \multirow{5}{*}{Variable Depth}
+                & Depth (m)
                 & \GroundBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \GroundSourceBelowDataVariableDepthDepthFactor
+                  \GroundBlockMedianSourcesVariableDepthDepthIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthDepth
+                & \multirow{5}{*}{
+                    \BestGroundBlockMedianSourcesVariableDepthScore
+                  } \\
+            &
+                & Depth factor
                 & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \GroundSourceBelowDataVariableDepthKNearest
+                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
+                & \\
+            &
+                & K nearest
                 & \GroundBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (km) & -
+                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthKNearest
+                & \\
+            &
+                & Spacing (m)
                 & \GroundBlockMedianSourcesVariableDepthSpacing
+                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthSpacing
+                & \\
+            &
+                & Damping
+                & \GroundBlockMedianSourcesVariableDepthDamping
+                  \GroundBlockMedianSourcesVariableDepthDampingIncrement
+                & \BestGroundBlockMedianSourcesVariableDepthDamping
+                & \\
+        \midrule
+
+        \multirow{4}{*}{Grid Sources}
+            & \multirow{4}{*}{Constant Depth}
+                & Depth (m)
+                & \GroundGridSourcesConstantDepthDepth
+                  \GroundGridSourcesConstantDepthDepthIncrement
+                & \BestGroundGridSourcesConstantDepthDepth
+                & \multirow{4}{*}{
+                    \BestGroundGridSourcesConstantDepthScore
+                  } \\
+            &
+                & Spacing (m)
+                & \GroundGridSourcesConstantDepthSpacing
+                  \GroundGridSourcesConstantDepthSpacingIncrement
+                & \BestGroundGridSourcesConstantDepthSpacing
+                & \\
+            &
+                & Pad
+                & \GroundGridSourcesConstantDepthPad
+                  \GroundGridSourcesConstantDepthPadIncrement
+                & \BestGroundGridSourcesConstantDepthPad
+                & \\
+            &
+                & Damping
+                & \GroundGridSourcesConstantDepthDamping
+                  \GroundGridSourcesConstantDepthDampingIncrement
+                & \BestGroundGridSourcesConstantDepthDamping
                 & \\
@@
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources below data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
-        \hline
-        Depth (km) & \AirborneSourceBelowDataConstantDepthDepth
+    \begin{tabular}{c c l c}
+        \textbf{Source layout}
+            & \textbf{Depth type}
+            & \multicolumn{1}{c}{\textbf{Parameters}}
+            & \textbf{Values} \\
+        \toprule
+
+        \multirow{8}{*}{Source Bellow Data}
+            & \multirow{2}{*}{Constant Depth}
+                & Depth (m)
+                & \AirborneSourceBellowDataConstantDepthDepth
+                  \AirborneSourceBellowDataConstantDepthDepthIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataConstantDepthDamping
+                  \AirborneSourceBellowDataConstantDepthDampingIncrement \\
+            \cmidrule{2-4}
+            & \multirow{2}{*}{Relative Depth}
+                & Depth (m)
+                & \AirborneSourceBellowDataRelativeDepthDepth
+                  \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataRelativeDepthDamping
+                  \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
+            \cmidrule{2-4}
+            & \multirow{4}{*}{Variable Depth}
+                & Depth (m)
+                & \AirborneSourceBellowDataVariableDepthDepth
+                  \AirborneSourceBellowDataVariableDepthDepthIncrement \\
+            &
+                & Depth factor
+                & \AirborneSourceBellowDataVariableDepthDepthFactor
+                  \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
+            &
+                & K nearest
+                & \AirborneSourceBellowDataVariableDepthKNearest
+                  \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
+            &
+                & Damping
+                & \AirborneSourceBellowDataVariableDepthDamping
+                  \AirborneSourceBellowDataVariableDepthDampingIncrement \\
+        \midrule
+
+        \multirow{11}{*}{Block median sources}
+            & \multirow{3}{*}{Constant Depth}
+                & Depth (m)
                 & \AirborneBlockMedianSourcesConstantDepthDepth
-                   & \AirborneGridSourcesConstantDepthDepth \\
-        Spacing (km) & -
+                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
+            &
+                & Spacing (m)
                 & \AirborneBlockMedianSourcesConstantDepthSpacing
-                     & \AirborneGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \AirborneGridSourcesConstantDepthPad \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \AirborneSourceBelowDataRelativeDepthDepth
+                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesConstantDepthDamping
+                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
+            \cmidrule{2-4}
+            & \multirow{3}{*}{Relative Depth}
+                & Depth (m)
                 & \AirborneBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (km) & -
+                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
+            &
+                & Spacing (m)
                 & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                     & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (km) & \AirborneSourceBelowDataVariableDepthDepth
+                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesRelativeDepthDamping
+                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
+            \cmidrule{2-4}
+            & \multirow{5}{*}{Variable Depth}
+                & Depth (m)
                 & \AirborneBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \AirborneSourceBelowDataVariableDepthDepthFactor
+                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
+            &
+                & Depth factor
                 & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \AirborneSourceBelowDataVariableDepthKNearest
+                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
+            &
+                & K nearest
                 & \AirborneBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (km) & -
+                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
+            &
+                & Spacing (m)
                 & \AirborneBlockMedianSourcesVariableDepthSpacing
-                     & \\
+                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
+            &
+                & Damping
+                & \AirborneBlockMedianSourcesVariableDepthDamping
+                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
+        \midrule
+
+        \multirow{4}{*}{Grid Sources}
+            & \multirow{4}{*}{Constant Depth}
+                & Depth (m)
+                    & \AirborneGridSourcesConstantDepthDepth
+                      \AirborneGridSourcesConstantDepthDepthIncrement \\
+            &
+                & Spacing (m)
+                    & \AirborneGridSourcesConstantDepthSpacing
+                      \AirborneGridSourcesConstantDepthSpacingIncrement \\
+            &
+                & Pad
+                    & \AirborneGridSourcesConstantDepthPad
+                      \AirborneGridSourcesConstantDepthPadIncrement \\
+            &
+                & Damping
+                    & \AirborneGridSourcesConstantDepthDamping
+                      \AirborneGridSourcesConstantDepthDampingIncrement \\
     \end{tabular}

### 2020-03-10 manuscript/manuscript.tex
Replace Bellow for Below on LaTeX variables

@@
 
-        \multirow{8}{*}{Source Bellow Data}
+        \multirow{8}{*}{Source Below Data}
             & \multirow{2}{*}{Constant Depth}
                 & Depth (m)
-                & \GroundSourceBellowDataConstantDepthDepth
-                  \GroundSourceBellowDataConstantDepthDepthIncrement
-                & \BestGroundSourceBellowDataConstantDepthDepth
+                & \GroundSourceBelowDataConstantDepthDepth
+                  \GroundSourceBelowDataConstantDepthDepthIncrement
+                & \BestGroundSourceBelowDataConstantDepthDepth
                 & \multirow{2}{*}{
-                    \BestGroundSourceBellowDataConstantDepthScore
+                    \BestGroundSourceBelowDataConstantDepthScore
                   } \\
@@
                 & Damping
-                & \GroundSourceBellowDataConstantDepthDamping
-                  \GroundSourceBellowDataConstantDepthDampingIncrement
-                & \BestGroundSourceBellowDataConstantDepthDamping
+                & \GroundSourceBelowDataConstantDepthDamping
+                  \GroundSourceBelowDataConstantDepthDampingIncrement
+                & \BestGroundSourceBelowDataConstantDepthDamping
                 & \\
@@
                 & Depth (m)
-                & \GroundSourceBellowDataRelativeDepthDepth
-                  \GroundSourceBellowDataRelativeDepthDepthIncrement
-                & \BestGroundSourceBellowDataRelativeDepthDepth
+                & \GroundSourceBelowDataRelativeDepthDepth
+                  \GroundSourceBelowDataRelativeDepthDepthIncrement
+                & \BestGroundSourceBelowDataRelativeDepthDepth
                 & \multirow{2}{*}{
-                    \BestGroundSourceBellowDataRelativeDepthScore
+                    \BestGroundSourceBelowDataRelativeDepthScore
                   } \\
@@
                 & Damping
-                & \GroundSourceBellowDataRelativeDepthDamping
-                  \GroundSourceBellowDataRelativeDepthDampingIncrement
-                & \BestGroundSourceBellowDataRelativeDepthDamping
+                & \GroundSourceBelowDataRelativeDepthDamping
+                  \GroundSourceBelowDataRelativeDepthDampingIncrement
+                & \BestGroundSourceBelowDataRelativeDepthDamping
                 & \\
@@
                 & Depth (m)
-                & \GroundSourceBellowDataVariableDepthDepth
-                  \GroundSourceBellowDataVariableDepthDepthIncrement
-                & \BestGroundSourceBellowDataVariableDepthDepth
+                & \GroundSourceBelowDataVariableDepthDepth
+                  \GroundSourceBelowDataVariableDepthDepthIncrement
+                & \BestGroundSourceBelowDataVariableDepthDepth
                 & \multirow{4}{*}{
-                    \BestGroundSourceBellowDataVariableDepthScore
+                    \BestGroundSourceBelowDataVariableDepthScore
                   } \\
@@
                 & Depth factor
-                & \GroundSourceBellowDataVariableDepthDepthFactor
-                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement
-                & \BestGroundSourceBellowDataVariableDepthDepthFactor
+                & \GroundSourceBelowDataVariableDepthDepthFactor
+                  \GroundSourceBelowDataVariableDepthDepthFactorIncrement
+                & \BestGroundSourceBelowDataVariableDepthDepthFactor
                 & \\
@@
                 & K nearest
-                & \GroundSourceBellowDataVariableDepthKNearest
-                  \GroundSourceBellowDataVariableDepthKNearestIncrement
-                & \BestGroundSourceBellowDataVariableDepthKNearest
+                & \GroundSourceBelowDataVariableDepthKNearest
+                  \GroundSourceBelowDataVariableDepthKNearestIncrement
+                & \BestGroundSourceBelowDataVariableDepthKNearest
                 & \\
@@
                 & Damping
-                & \GroundSourceBellowDataVariableDepthDamping
-                  \GroundSourceBellowDataVariableDepthDampingIncrement
-                & \BestGroundSourceBellowDataVariableDepthDamping
+                & \GroundSourceBelowDataVariableDepthDamping
+                  \GroundSourceBelowDataVariableDepthDampingIncrement
+                & \BestGroundSourceBelowDataVariableDepthDamping
                 & \\
@@
 
-        \multirow{8}{*}{Source Bellow Data}
+        \multirow{8}{*}{Source Below Data}
             & \multirow{2}{*}{Constant Depth}
                 & Depth (m)
-                & \AirborneSourceBellowDataConstantDepthDepth
-                  \AirborneSourceBellowDataConstantDepthDepthIncrement \\
+                & \AirborneSourceBelowDataConstantDepthDepth
+                  \AirborneSourceBelowDataConstantDepthDepthIncrement \\
             &
                 & Damping
-                & \AirborneSourceBellowDataConstantDepthDamping
-                  \AirborneSourceBellowDataConstantDepthDampingIncrement \\
+                & \AirborneSourceBelowDataConstantDepthDamping
+                  \AirborneSourceBelowDataConstantDepthDampingIncrement \\
             \cmidrule{2-4}
@@
                 & Depth (m)
-                & \AirborneSourceBellowDataRelativeDepthDepth
-                  \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
+                & \AirborneSourceBelowDataRelativeDepthDepth
+                  \AirborneSourceBelowDataRelativeDepthDepthIncrement \\
             &
                 & Damping
-                & \AirborneSourceBellowDataRelativeDepthDamping
-                  \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
+                & \AirborneSourceBelowDataRelativeDepthDamping
+                  \AirborneSourceBelowDataRelativeDepthDampingIncrement \\
             \cmidrule{2-4}
@@
                 & Depth (m)
-                & \AirborneSourceBellowDataVariableDepthDepth
-                  \AirborneSourceBellowDataVariableDepthDepthIncrement \\
+                & \AirborneSourceBelowDataVariableDepthDepth
+                  \AirborneSourceBelowDataVariableDepthDepthIncrement \\
             &
                 & Depth factor
-                & \AirborneSourceBellowDataVariableDepthDepthFactor
-                  \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
+                & \AirborneSourceBelowDataVariableDepthDepthFactor
+                  \AirborneSourceBelowDataVariableDepthDepthFactorIncrement \\
             &
                 & K nearest
-                & \AirborneSourceBellowDataVariableDepthKNearest
-                  \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
+                & \AirborneSourceBelowDataVariableDepthKNearest
+                  \AirborneSourceBelowDataVariableDepthKNearestIncrement \\
             &
                 & Damping
-                & \AirborneSourceBellowDataVariableDepthDamping
-                  \AirborneSourceBellowDataVariableDepthDampingIncrement \\
+                & \AirborneSourceBelowDataVariableDepthDamping
+                  \AirborneSourceBelowDataVariableDepthDampingIncrement \\
         \midrule

### 2020-03-10 manuscript/manuscript.tex
Add citation to Harmonica v0.1.0 (#36)
Add BibTeX entry for Harmonica v0.1.0 and cite it on manuscript.

--- 2020-03-10 manuscript/manuscript.tex
@@
 equivalent sources are carried out by the equivalent sources implementation in
-Harmonica \citep{harmonica}.
+Harmonica (v0.1.0) \citep{uieda2020}.
 

### 2020-03-10 eql_source_layouts/latex_variables.py
Show dampings as a numlist if # <= 4

@@ -151,7 +151,12 @@ def _format_damping(parameters):
     differences = parameters[1:] - parameters[:-1]
     increment = differences[1] - differences[0]
     assert np.allclose(differences[0], differences)
-    values = [r"\num{{e{:.0f}}}".format(p) for p in parameters]
-    values = r"{}, {},$\dots$, {}".format(values[0], values[1], values[-1])
+    values = ["e{:.0f}".format(p) for p in parameters]
+    if len(values) > 4:
+        values = [r"\num{{{v}}}".format(v=v) for v in values]
+        values = r"{}, {},$\dots$, {}".format(values[0], values[1], values[-1])
+    else:
+        values = ";".join(values)
+        values = r"\numlist{{{values}}}".format(values=values)
     increment = ""
     return values, increment

### 2020-03-10 notebooks/03-grid-airborne-data.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.5
+#       jupytext_version: 1.3.4
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python

### 2020-03-12 manuscript/manuscript.tex
Define parameters as ranges and improve parameters table (#35)
Define gridding parameters as ranges when possible. Rewrite functions to
convert parameters to LaTeX variables using \numlist and \numrange. Change
parameters table design, showing values as ranges when possible. Include
damping parameters on table. Merge best predictions parameters and R2 scores
into the parameters tables.

@@
 
-\begin{table*}
-    \centering
-    \caption{
-        Combination of parameters that produce the best prediction when
-        gridding the synthetic ground survey with each source distribution.
-        The score of each best prediction is also shown.
-    }
-    \label{tab:parameters-ground-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources below data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
-        \hline
-        Depth (m) & \BestGroundSourceBelowDataConstantDepthDepth
-                   & \BestGroundBlockMedianSourcesConstantDepthDepth
-                   & \BestGroundGridSourcesConstantDepthDepth \\
-        Spacing (m) & -
-                     & \BestGroundBlockMedianSourcesConstantDepthSpacing
-                     & \BestGroundGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \BestGroundGridSourcesConstantDepthPad \\
-        Damping & \BestGroundSourceBelowDataConstantDepthDamping
-                & \BestGroundBlockMedianSourcesConstantDepthDamping
-                & \BestGroundGridSourcesConstantDepthDamping \\
-        \textbf{R$^2$ score}
-                & \textbf{\BestGroundSourceBelowDataConstantDepthScore}
-                & \textbf{\BestGroundBlockMedianSourcesConstantDepthScore}
-                & \textbf{\BestGroundGridSourcesConstantDepthScore} \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (m) & \BestGroundSourceBelowDataRelativeDepthDepth
-                   & \BestGroundBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (m) & -
-                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
-                & \\
-        Damping & \BestGroundSourceBelowDataRelativeDepthDamping
-                & \BestGroundBlockMedianSourcesRelativeDepthDamping
-                & \\
-        \textbf{R$^2$ score}
-                & \textbf{\BestGroundSourceBelowDataRelativeDepthScore}
-                & \textbf{\BestGroundBlockMedianSourcesRelativeDepthScore}
-                & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (m) & \BestGroundSourceBelowDataVariableDepthDepth
-                   & \BestGroundBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \BestGroundSourceBelowDataVariableDepthDepthFactor
-                     & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \BestGroundSourceBelowDataVariableDepthKNearest
-                  & \BestGroundBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (m) & -
-                     & \BestGroundBlockMedianSourcesVariableDepthSpacing
-                     & \\
-        Damping & \BestGroundSourceBelowDataVariableDepthDamping
-                & \BestGroundBlockMedianSourcesVariableDepthDamping
-                &  \\
-        \textbf{R$^2$ score}
-                & \textbf{\BestGroundSourceBelowDataVariableDepthScore}
-                & \textbf{\BestGroundBlockMedianSourcesVariableDepthScore}
-                & \\
-    \end{tabular}
-\end{table*}
-
-\begin{table*}
-    \centering
-    \caption{
-        Combination of parameters that produce the best prediction when
-        gridding the synthetic airborne survey with each source distribution.
-        The score of each best prediction is also shown.
-    }
-    \label{tab:parameters-ground-survey}
-    \begin{tabular}{l c c c}
-        & \textbf{Sources below data} & \textbf{Block median sources}
-        & \textbf{Grid sources} \\
-
-        \textbf{Constant depth} & & & \\
-        \hline
-        Depth (m) & \BestAirborneSourceBelowDataConstantDepthDepth
-                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
-                   & \BestAirborneGridSourcesConstantDepthDepth \\
-        Spacing (m) & -
-                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
-                     & \BestAirborneGridSourcesConstantDepthSpacing \\
-        Pad & -
-            & -
-            & \BestAirborneGridSourcesConstantDepthPad \\
-        Damping & \BestAirborneSourceBelowDataConstantDepthDamping
-                & \BestAirborneBlockMedianSourcesConstantDepthDamping
-                & \BestAirborneGridSourcesConstantDepthDamping \\
-        \textbf{R$^2$ score}
-                & \textbf{\BestAirborneSourceBelowDataConstantDepthScore}
-                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
-                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\
-
-        & & & \\
-        \textbf{Relative depth} & & & \\
-        \cline{1-3}
-        Depth (m) & \BestAirborneSourceBelowDataRelativeDepthDepth
-                   & \BestAirborneBlockMedianSourcesRelativeDepthDepth
-                   & \\
-        Spacing (m) & -
-                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
-                & \\
-        Damping & \BestAirborneSourceBelowDataRelativeDepthDamping
-                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
-                & \\
-        \textbf{R$^2$ score}
-                & \textbf{\BestAirborneSourceBelowDataRelativeDepthScore}
-                & \textbf{\BestAirborneBlockMedianSourcesRelativeDepthScore}
-                & \\
-
-        & & & \\
-        \textbf{Variable depth} & & & \\
-        \cline{1-3}
-        Depth (m) & \BestAirborneSourceBelowDataVariableDepthDepth
-                   & \BestAirborneBlockMedianSourcesVariableDepthDepth
-                   & \\
-        Depth factor & \BestAirborneSourceBelowDataVariableDepthDepthFactor
-                     & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
-                     & \\
-        K nearest & \BestAirborneSourceBelowDataVariableDepthKNearest
-                  & \BestAirborneBlockMedianSourcesVariableDepthKNearest
-                  & \\
-        Spacing (m) & -
-                     & \BestAirborneBlockMedianSourcesVariableDepthSpacing
-                     & \\
-        Damping & \BestAirborneSourceBelowDataVariableDepthDamping
-                & \BestAirborneBlockMedianSourcesVariableDepthDamping
-                &  \\
-        \textbf{R$^2$ score}
-                & \textbf{\BestAirborneSourceBelowDataVariableDepthScore}
-                & \textbf{\BestAirborneBlockMedianSourcesVariableDepthScore}
-                & \\
-    \end{tabular}
-\end{table*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         Parameters used with each source distribution when gridding the
-        synthetic ground survey.
+        synthetic ground survey. The table also contains the set of parameters
+        that generates the best prediction for each source distribution and its
+        corresponding R$^2$ score.
     }
@@
         Parameters used with each source distribution when gridding the
-        synthetic airborne survey.
+        synthetic airborne survey. The table also contains the set of
+        parameters that generates the best prediction for each source
+        distribution and its corresponding R$^2$ score.
     }
     \label{tab:parameters-airborne-survey}
-    \begin{tabular}{c c l c}
+    \begin{tabular}{c c l c c c}
         \textbf{Source layout}
@@
             & \multicolumn{1}{c}{\textbf{Parameters}}
-            & \textbf{Values} \\
+            & \textbf{Values}
+            & \textbf{Best}
+            & \textbf{R$^2$ score} \\
         \toprule
@@
                 & \AirborneSourceBelowDataConstantDepthDepth
-                  \AirborneSourceBelowDataConstantDepthDepthIncrement \\
+                  \AirborneSourceBelowDataConstantDepthDepthIncrement
+                & \BestAirborneSourceBelowDataConstantDepthDepth
+                & \multirow{2}{*}{
+                    \BestAirborneSourceBelowDataConstantDepthScore
+                  } \\
             &
@@
                 & \AirborneSourceBelowDataConstantDepthDamping
-                  \AirborneSourceBelowDataConstantDepthDampingIncrement \\
-            \cmidrule{2-4}
+                  \AirborneSourceBelowDataConstantDepthDampingIncrement
+                & \BestAirborneSourceBelowDataConstantDepthDamping
+                & \\
+            \cmidrule{2-6}
             & \multirow{2}{*}{Relative Depth}
@@
                 & \AirborneSourceBelowDataRelativeDepthDepth
-                  \AirborneSourceBelowDataRelativeDepthDepthIncrement \\
+                  \AirborneSourceBelowDataRelativeDepthDepthIncrement
+                & \BestAirborneSourceBelowDataRelativeDepthDepth
+                & \multirow{2}{*}{
+                    \BestAirborneSourceBelowDataRelativeDepthScore
+                  } \\
             &
@@
                 & \AirborneSourceBelowDataRelativeDepthDamping
-                  \AirborneSourceBelowDataRelativeDepthDampingIncrement \\
-            \cmidrule{2-4}
+                  \AirborneSourceBelowDataRelativeDepthDampingIncrement
+                & \BestAirborneSourceBelowDataRelativeDepthDamping
+                & \\
+            \cmidrule{2-6}
             & \multirow{4}{*}{Variable Depth}
@@
                 & \AirborneSourceBelowDataVariableDepthDepth
-                  \AirborneSourceBelowDataVariableDepthDepthIncrement \\
+                  \AirborneSourceBelowDataVariableDepthDepthIncrement
+                & \BestAirborneSourceBelowDataVariableDepthDepth
+                & \multirow{4}{*}{
+                    \BestAirborneSourceBelowDataVariableDepthScore
+                  } \\
             &
@@
                 & \AirborneSourceBelowDataVariableDepthDepthFactor
-                  \AirborneSourceBelowDataVariableDepthDepthFactorIncrement \\
+                  \AirborneSourceBelowDataVariableDepthDepthFactorIncrement
+                & \BestAirborneSourceBelowDataVariableDepthDepthFactor
+                & \\
             &
@@
                 & \AirborneSourceBelowDataVariableDepthKNearest
-                  \AirborneSourceBelowDataVariableDepthKNearestIncrement \\
+                  \AirborneSourceBelowDataVariableDepthKNearestIncrement
+                & \BestAirborneSourceBelowDataVariableDepthKNearest
+                & \\
             &
@@
                 & \AirborneSourceBelowDataVariableDepthDamping
-                  \AirborneSourceBelowDataVariableDepthDampingIncrement \\
+                  \AirborneSourceBelowDataVariableDepthDampingIncrement
+                & \BestAirborneSourceBelowDataVariableDepthDamping
+                & \\
         \midrule
@@
                 & \AirborneBlockMedianSourcesConstantDepthDepth
-                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
+                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement
+                & \BestAirborneBlockMedianSourcesConstantDepthDepth
+                & \multirow{3}{*}{
+                    \BestAirborneBlockMedianSourcesConstantDepthScore
+                  } \\
             &
@@
                 & \AirborneBlockMedianSourcesConstantDepthSpacing
-                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
+                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement
+                & \BestAirborneBlockMedianSourcesConstantDepthSpacing
+                & \\
             &
@@
                 & \AirborneBlockMedianSourcesConstantDepthDamping
-                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
-            \cmidrule{2-4}
+                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement
+                & \BestAirborneBlockMedianSourcesConstantDepthDamping
+                & \\
+            \cmidrule{2-6}
             & \multirow{3}{*}{Relative Depth}
@@
                 & \AirborneBlockMedianSourcesRelativeDepthDepth
-                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
+                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement
+                & \BestAirborneBlockMedianSourcesRelativeDepthDepth
+                & \multirow{3}{*}{
+                    \BestAirborneBlockMedianSourcesRelativeDepthScore
+                  } \\
             &
@@
                 & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
+                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement
+                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
+                & \\
             &
@@
                 & \AirborneBlockMedianSourcesRelativeDepthDamping
-                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
-            \cmidrule{2-4}
+                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement
+                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
+                & \\
+            \cmidrule{2-6}
             & \multirow{5}{*}{Variable Depth}
@@
                 & \AirborneBlockMedianSourcesVariableDepthDepth
-                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement
+                & \BestAirborneBlockMedianSourcesVariableDepthDepth
+                & \multirow{5}{*}{
+                    \BestAirborneBlockMedianSourcesVariableDepthScore
+                  } \\
             &
@@
                 & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement
+                & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
+                & \\
             &
@@
                 & \AirborneBlockMedianSourcesVariableDepthKNearest
-                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement
+                & \BestAirborneBlockMedianSourcesVariableDepthKNearest
+                & \\
             &
@@
                 & \AirborneBlockMedianSourcesVariableDepthSpacing
-                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement
+                & \BestAirborneBlockMedianSourcesVariableDepthSpacing
+                & \\
             &
@@
                 & \AirborneBlockMedianSourcesVariableDepthDamping
-                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
+                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement
+                & \BestAirborneBlockMedianSourcesVariableDepthDamping
+                & \\
         \midrule
@@
                 & \AirborneGridSourcesConstantDepthDepth
-                      \AirborneGridSourcesConstantDepthDepthIncrement \\
+                  \AirborneGridSourcesConstantDepthDepthIncrement
+                & \BestAirborneGridSourcesConstantDepthDepth
+                & \multirow{4}{*}{
+                    \BestAirborneGridSourcesConstantDepthScore
+                  } \\
             &
@@
                 & \AirborneGridSourcesConstantDepthSpacing
-                      \AirborneGridSourcesConstantDepthSpacingIncrement \\
+                  \AirborneGridSourcesConstantDepthSpacingIncrement
+                & \BestAirborneGridSourcesConstantDepthSpacing
+                & \\
             &
@@
                 & \AirborneGridSourcesConstantDepthPad
-                      \AirborneGridSourcesConstantDepthPadIncrement \\
+                  \AirborneGridSourcesConstantDepthPadIncrement
+                & \BestAirborneGridSourcesConstantDepthPad
+                & \\
             &
@@
                 & \AirborneGridSourcesConstantDepthDamping
-                      \AirborneGridSourcesConstantDepthDampingIncrement \\
+                  \AirborneGridSourcesConstantDepthDampingIncrement
+                & \BestAirborneGridSourcesConstantDepthDamping
+                & \\
     \end{tabular}

### 2020-03-12 eql_source_layouts/__init__.py

@@ -4,7 +4,12 @@ from ._version import get_versions
 from .layouts import source_below_data, block_median_sources, grid_sources
 from .synthetic_model import synthetic_model
 from .plot import plot_prediction
-from .latex_variables import latex_variables, latex_parameters, format_variable_name
+from .latex_variables import (
+    latex_variables,
+    latex_parameters,
+    format_variable_name,
+    latex_best_parameters,
+)
 from .utils import (
     combine_parameters,
     get_best_prediction,

### 2020-03-12 eql_source_layouts/latex_variables.py

@@ -21,22 +21,47 @@ def latex_variables(variable, number, unit=None, fmt=None):
     return tex_line
 
 
+def latex_best_parameters(best_parameters, survey, layout, depth_type):
+    """
+    Create LaTeX variables for best parameters
+    """
+    tex_lines = []
+    for parameter, value in best_parameters.items():
+        if parameter in ("depth_type", "layout", "height"):
+            continue
+        variable_name = format_variable_name(
+            "_".join(["best", survey, layout, depth_type, parameter])
+        )
+        if parameter == "damping":
+            value = r"\num{{e{:.0f}}}".format(np.log10(value))
+            fmt = None
+        elif parameter == "score":
+            fmt = ".3f"
+        else:
+            fmt = _determine_fmt(value)
+        tex_lines.append(latex_variables(variable_name, value, fmt=fmt))
+    return tex_lines
+
+
 def latex_parameters(parameters, survey):
     """
-    Create list of parameters for each source distribution as LaTeX variables
+    Create list or ranges of parameters for each source distribution as LaTeX variables
     """
     tex_variables = []
     for layout in parameters:
         for depth_type in parameters[layout]:
             for parameter in parameters[layout][depth_type]:
                 if parameter != "depth_type":
-                    values = format_parameters(
+                    values, increment = format_parameters(
                         parameters[layout][depth_type][parameter], parameter
                     )
                     variable_name = format_variable_name(
                         "_".join([survey, layout, depth_type, parameter])
                     )
                     tex_variables.append(latex_variables(variable_name, values))
+                    tex_variables.append(
+                        latex_variables(variable_name + "Increment", increment)
+                    )
     return tex_variables
 
 
@@ -49,26 +74,89 @@ def format_variable_name(name):
     return name.replace("_", " ").title().replace(" ", "")
 
 
-def format_parameters(parameters_list, parameter_name):
+def format_parameters(parameters, parameter_name):
     """
-    Format a list of parameters to appear on the table
+    Format a list or range of parameters to appear on the table
     """
-    fmt = ""
-    # Convert spacings and depths from m to km and configure string format
-    if parameter_name in ("spacing", "depth"):
-        parameters_list = np.array(parameters_list) * 1e-3
[…]

### 2020-03-12 notebooks/02-grid-ground-data.py

@@ -31,7 +31,7 @@ from eql_source_layouts import (
     get_best_prediction,
     predictions_to_datasets,
     latex_parameters,
-    latex_variables,
+    latex_best_parameters,
 )
 
 # -
@@ -60,22 +60,22 @@ field_units = "mGal"
 # Define a list of source layouts
 layouts = ["source_below_data", "block_median_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
-dampings = [None, 1e-4, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2]
+dampings = np.logspace(-4, 2, 7)
 # Define depht values
 depths = np.arange(1e3, 18e3, 2e3)
 # Define parameters for the grid sources:
 #    spacing, depth, padding and damping
-grid_sources_spacings = [1e3, 2e3, 3e3, 4e3]
+grid_sources_spacings = np.arange(1e3, 5e3, 1e3)
 grid_sources_depths = np.arange(3e3, 15e3, 2e3)
 grid_sources_paddings = [0, 0.1]
-grid_sources_dampings = [1e1, 1e2, 1e3, 1e4]
+grid_sources_dampings = np.logspace(1, 4, 4)
 # Define parameters for variable relative depth layouts:
 #    depth_factor, depth and k_nearest
 depth_factors = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
 variable_depths = np.arange(0, 1500, 200)
 k_values = [1, 5, 10, 15]
 # Define block spacing for block median sources
-block_spacings = [1_000, 2_000, 3_000, 4_000]
+block_spacings = np.arange(1e3, 5e3, 1e3)
 # -
 
 # ## Create dictionary with the parameter values for each source distribution
@@ -357,32 +357,17 @@ plt.show()
 #
 # Save best predictions parameters as LaTeX variables
 
-# +
-tex_variables = []
+tex_lines = []
 for dataset in best_predictions:
     for depth_type in dataset:
         parameters = dataset[depth_type].attrs
         layout = parameters["layout"]
-        for parameter, value in parameters.items():
-            if parameter in ("depth_type", "layout", "height"):
-                continue
-            fmt = ""
-            variable_name = (
-                "_".join(["best", "ground", layout, depth_type, parameter])
-                .replace("_", " ")
-                .title()
-                .replace(" ", "")
-            )
-            if parameter in ("spacing", "depth"):
-                fmt = ".1f"
-            if parameter == "score":
[…]

### 2020-03-12 notebooks/03-grid-airborne-data.py

@@ -37,7 +37,7 @@ from eql_source_layouts import (
     get_best_prediction,
     predictions_to_datasets,
     latex_parameters,
-    latex_variables,
+    latex_best_parameters,
 )
 
 # -
@@ -65,7 +65,7 @@ field_units = "mGal"
 # Define a list of source layouts
 layouts = ["source_below_data", "block_median_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
-dampings = [None, 1e-4, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2]
+dampings = np.logspace(-4, 2, 7)
 # Define depht values
 depths = np.arange(1e3, 18e3, 2e3)
 # Define parameters for the grid sources:
@@ -73,14 +73,14 @@ depths = np.arange(1e3, 18e3, 2e3)
 grid_sources_spacings = [1e3, 2e3, 3e3]
 grid_sources_depths = np.arange(3e3, 15e3, 2e3)
 grid_sources_paddings = [0, 0.1, 0.2]
-grid_sources_dampings = [1e1, 1e2, 1e3, 1e4]
+grid_sources_dampings = np.logspace(1, 4, 4)
 # Define parameters for variable relative depth layouts:
 #    depth factor, depth shift and k_values
 depth_factors = [1, 2, 3, 4, 5, 6]
 variable_depths = np.arange(50, 1500, 200)
 k_values = [1, 5, 10, 15]
 # Define block spacing for block median sources
-block_spacings = [1_000, 2_000, 3_000, 4_000]
+block_spacings = np.arange(1e3, 5e3, 1e3)
 # -
 
 # ## Create dictionary with the parameter values for each source distribution
@@ -357,32 +357,17 @@ plt.show()
 #
 # Save best predictions parameters as LaTeX variables
 
-# +
-tex_variables = []
+tex_lines = []
 for dataset in best_predictions:
     for depth_type in dataset:
         parameters = dataset[depth_type].attrs
         layout = parameters["layout"]
-        for parameter, value in parameters.items():
-            if parameter in ("depth_type", "layout", "height"):
-                continue
-            fmt = ""
-            variable_name = (
-                "_".join(["best", "airborne", layout, depth_type, parameter])
-                .replace("_", " ")
-                .title()
-                .replace(" ", "")
-            )
-            if parameter in ("spacing", "depth"):
-                fmt = ".1f"
-            if parameter == "score":
-                fmt = ".3f"
[…]

### 2020-03-16 manuscript/manuscript.tex
Add flowchart and description of sources comparison

@@
 Another parameter that plays an important role on the predictive capabilities
-of the sources is the damping parameter.
+of the sources is the \emph{damping}.
+
 On real world scenarios, choosing the values of the parameters is a challenging
@@
 
+In order to compare the predictive capabilities of each source distribution we
+perform a parameter search to obtain the best prediction that can be achieved
+by each one of them.
 For each source distribution we proposed different values for each parameter
-(including the damping) and combined them into several parameters sets.
-For each parameter set we build the sources and fit their coefficients through
-least-squares.
-Then the sources are used to predict the field on the same points of the
-\emph{target} grid and finally we compute the coefficient of determination
-(R$^2$ score) between the prediction and the true values of the \emph{target}
-grid.
-We can therefore obtain the \emph{best prediction} generated by each source
-distribution as the one that achieves the highest score.
+(see Tables~\ref{tab:parameters-ground-survey}
+and~\ref{tab:parameters-airborne-survey}).
+These parameters values are combined obtaining several \emph{set of
+parameters}.
+We use each set of parameters to create the sources, fit their coefficients
+through least-squares and predict the field on the same points of the
+\emph{target} grid.
+We then \emph{score} the prediction by computing the coefficient of
+determination (R$^2$ score) between the prediction and the true values of the
+\emph{target} grid.
+Finally, we obtain the \emph{best prediction} for each source distribution as
+the one that achieves the highest score.
+See Figure~\ref{fig:flowchart} for a graphical illustration of this process.
+This process is carried out on both ground and airborne synthetic surveys.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/flowchart.pdf}
+    \caption{
+        Flowchart for comparing the performance of the source distributions.
+        For each source distribution we propose different values for its
+        parameters (see Tables~\ref{tab:parameters-ground-survey}
+        and~\ref{tab:parameters-airborne-survey}).
+        These values are then combined to obtain several set of parameters
+        which are iteratively submitted to the process illustrated on this
+        figure.
+        Finally we obtain the best prediction generated by each source
+        distribution as the one that achieves the best score.
+    }
+    \label{fig:flowchart}
+\end{figure}
+
+Tables~\ref{tab:parameters-ground-survey}
+and~\ref{tab:parameters-airborne-survey} also show the parameter combination
+that produces the best prediction for each source distribution and its
+corresponding R$^2$ score, for both ground and synthetic surveys, respectively.
+Figures~ \ref{fig:ground-survey-differences}
+and~\ref{fig:airborne-survey-differences} show the differences between the
+target grid and the best prediction achieved by each source distribution, for
+both ground and synthetic surveys, respectively.
 

### 2020-03-16 manuscript/manuscript.tex
Start writing Discussion

@@
 
+Figures~ \ref{fig:ground-survey-differences}
+and~\ref{fig:airborne-survey-differences} show that all source distributions
+produce accurate predictions, both for the ground and airborne survey.
+The R$^2$ scores don't show significant difference, so we can only conclude
+that all the source distributions are able to produce comparable predictions.
+Nevertheless, the \emph{block averaged sources} make use of less sources to
+produce this predictions, what would reduce the computational load needed to
+fit the sources coefficients and finally compute the actual prediction.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-16 manuscript/manuscript.tex
Replace block median for block averaged

@@
         is controlled by a \emph{spacing} parameter.
-        (see Fig.~\ref{fig:block-median-sources}(a)-(b)).
+        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
     \item Computing the median location of the observation points that fall
@@
     \item Locating one point source below each block averaged coordinate.
-        (see Fig.~\ref{fig:block-median-sources}(c)).
+        (see Fig.~\ref{fig:block-averaged-sources}(c)).
 \end{enumerate}
@@
 \begin{figure*}
-    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
+    \includegraphics[width=\linewidth]{figs/block-averaged-sources-schematics.pdf}
     \caption{
@@
     }
-    \label{fig:block-median-sources}
+    \label{fig:block-averaged-sources}
 \end{figure*}
@@
             obtained through the \emph{sources beneath data} layout.
-        (c) Location of the \SourceLayoutsSchematicsBlockMedianSources{}
+        (c) Location of the \SourceLayoutsSchematicsBlockaveragedSources{}
             sources obtained through the \emph{block averaged sources} layout.
@@
 corresponding R$^2$ score, for both ground and synthetic surveys, respectively.
-Figures~ \ref{fig:ground-survey-differences}
+Figures~\ref{fig:ground-survey-differences}
 and~\ref{fig:airborne-survey-differences} show the differences between the
@@
 
-Figures~ \ref{fig:ground-survey-differences}
+Figures~\ref{fig:ground-survey-differences}
 and~\ref{fig:airborne-survey-differences} show that all source distributions
@@
 
-        \multirow{11}{*}{Block median sources}
+        \multirow{11}{*}{Block averaged sources}
             & \multirow{3}{*}{Constant Depth}
                 & Depth (m)
-                & \GroundBlockMedianSourcesConstantDepthDepth
-                  \GroundBlockMedianSourcesConstantDepthDepthIncrement
-                & \BestGroundBlockMedianSourcesConstantDepthDepth
+                & \GroundBlockAveragedSourcesConstantDepthDepth
+                  \GroundBlockAveragedSourcesConstantDepthDepthIncrement
+                & \BestGroundBlockAveragedSourcesConstantDepthDepth
                 & \multirow{3}{*}{
-                    \BestGroundBlockMedianSourcesConstantDepthScore
+                    \BestGroundBlockAveragedSourcesConstantDepthScore
                   } \\
@@
                 & Spacing (m)
-                & \GroundBlockMedianSourcesConstantDepthSpacing
-                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement
-                & \BestGroundBlockMedianSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockMedianSourcesConstantDepthDamping
-                  \GroundBlockMedianSourcesConstantDepthDampingIncrement
-                & \BestGroundBlockMedianSourcesConstantDepthDamping
+                & \GroundBlockAveragedSourcesConstantDepthSpacing
+                  \GroundBlockAveragedSourcesConstantDepthSpacingIncrement
+                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
+                & \\
+            &
+                & Damping
+                & \GroundBlockAveragedSourcesConstantDepthDamping
+                  \GroundBlockAveragedSourcesConstantDepthDampingIncrement
+                & \BestGroundBlockAveragedSourcesConstantDepthDamping
                 & \\
@@
                 & Depth (m)
-                & \GroundBlockMedianSourcesRelativeDepthDepth
-                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement
-                & \BestGroundBlockMedianSourcesRelativeDepthDepth
+                & \GroundBlockAveragedSourcesRelativeDepthDepth
+                  \GroundBlockAveragedSourcesRelativeDepthDepthIncrement
+                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
                 & \multirow{3}{*}{
-                    \BestGroundBlockMedianSourcesRelativeDepthScore
+                    \BestGroundBlockAveragedSourcesRelativeDepthScore
                   } \\
@@
                 & Spacing (m)
-                & \GroundBlockMedianSourcesRelativeDepthSpacing
-                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement
-                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockMedianSourcesRelativeDepthDamping
-                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement
-                & \BestGroundBlockMedianSourcesRelativeDepthDamping
+                & \GroundBlockAveragedSourcesRelativeDepthSpacing
+                  \GroundBlockAveragedSourcesRelativeDepthSpacingIncrement
+                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
+                & \\
+            &
+                & Damping
+                & \GroundBlockAveragedSourcesRelativeDepthDamping
+                  \GroundBlockAveragedSourcesRelativeDepthDampingIncrement
+                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
                 & \\
@@
                 & Depth (m)
-                & \GroundBlockMedianSourcesVariableDepthDepth
-                  \GroundBlockMedianSourcesVariableDepthDepthIncrement
-                & \BestGroundBlockMedianSourcesVariableDepthDepth
+                & \GroundBlockAveragedSourcesVariableDepthDepth
+                  \GroundBlockAveragedSourcesVariableDepthDepthIncrement
+                & \BestGroundBlockAveragedSourcesVariableDepthDepth
                 & \multirow{5}{*}{
-                    \BestGroundBlockMedianSourcesVariableDepthScore
+                    \BestGroundBlockAveragedSourcesVariableDepthScore
                   } \\
@@
                 & Depth factor
-                & \GroundBlockMedianSourcesVariableDepthDepthFactor
-                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement
-                & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
+                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
+                  \GroundBlockAveragedSourcesVariableDepthDepthFactorIncrement
+                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
                 & \\
@@
                 & K nearest
-                & \GroundBlockMedianSourcesVariableDepthKNearest
-                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement
-                & \BestGroundBlockMedianSourcesVariableDepthKNearest
+                & \GroundBlockAveragedSourcesVariableDepthKNearest
+                  \GroundBlockAveragedSourcesVariableDepthKNearestIncrement
+                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
                 & \\
@@
                 & Spacing (m)
-                & \GroundBlockMedianSourcesVariableDepthSpacing
-                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement
-                & \BestGroundBlockMedianSourcesVariableDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockMedianSourcesVariableDepthDamping
-                  \GroundBlockMedianSourcesVariableDepthDampingIncrement
-                & \BestGroundBlockMedianSourcesVariableDepthDamping
+                & \GroundBlockAveragedSourcesVariableDepthSpacing
+                  \GroundBlockAveragedSourcesVariableDepthSpacingIncrement
+                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
+                & \\
+            &
+                & Damping
+                & \GroundBlockAveragedSourcesVariableDepthDamping
+                  \GroundBlockAveragedSourcesVariableDepthDampingIncrement
+                & \BestGroundBlockAveragedSourcesVariableDepthDamping
                 & \\
@@
 
-        \multirow{11}{*}{Block median sources}
+        \multirow{11}{*}{Block averaged sources}
             & \multirow{3}{*}{Constant Depth}
                 & Depth (m)
-                & \AirborneBlockMedianSourcesConstantDepthDepth
-                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement
-                & \BestAirborneBlockMedianSourcesConstantDepthDepth
+                & \AirborneBlockAveragedSourcesConstantDepthDepth
+                  \AirborneBlockAveragedSourcesConstantDepthDepthIncrement
+                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
                 & \multirow{3}{*}{
-                    \BestAirborneBlockMedianSourcesConstantDepthScore
+                    \BestAirborneBlockAveragedSourcesConstantDepthScore
                   } \\
@@
                 & Spacing (m)
-                & \AirborneBlockMedianSourcesConstantDepthSpacing
-                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement
-                & \BestAirborneBlockMedianSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockMedianSourcesConstantDepthDamping
-                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement
-                & \BestAirborneBlockMedianSourcesConstantDepthDamping
+                & \AirborneBlockAveragedSourcesConstantDepthSpacing
+                  \AirborneBlockAveragedSourcesConstantDepthSpacingIncrement
+                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
+                & \\
+            &
+                & Damping
+                & \AirborneBlockAveragedSourcesConstantDepthDamping
+                  \AirborneBlockAveragedSourcesConstantDepthDampingIncrement
+                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
                 & \\
@@
                 & Depth (m)
-                & \AirborneBlockMedianSourcesRelativeDepthDepth
-                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement
-                & \BestAirborneBlockMedianSourcesRelativeDepthDepth
+                & \AirborneBlockAveragedSourcesRelativeDepthDepth
+                  \AirborneBlockAveragedSourcesRelativeDepthDepthIncrement
+                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
                 & \multirow{3}{*}{
-                    \BestAirborneBlockMedianSourcesRelativeDepthScore
+                    \BestAirborneBlockAveragedSourcesRelativeDepthScore
                   } \\
@@
                 & Spacing (m)
-                & \AirborneBlockMedianSourcesRelativeDepthSpacing
-                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement
-                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockMedianSourcesRelativeDepthDamping
-                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement
-                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
+                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
+                  \AirborneBlockAveragedSourcesRelativeDepthSpacingIncrement
+                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
+                & \\
+            &
+                & Damping
+                & \AirborneBlockAveragedSourcesRelativeDepthDamping
+                  \AirborneBlockAveragedSourcesRelativeDepthDampingIncrement
+                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
                 & \\
@@
                 & Depth (m)
-                & \AirborneBlockMedianSourcesVariableDepthDepth
-                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement
-                & \BestAirborneBlockMedianSourcesVariableDepthDepth
+                & \AirborneBlockAveragedSourcesVariableDepthDepth
+                  \AirborneBlockAveragedSourcesVariableDepthDepthIncrement
+                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
                 & \multirow{5}{*}{
-                    \BestAirborneBlockMedianSourcesVariableDepthScore
+                    \BestAirborneBlockAveragedSourcesVariableDepthScore
                   } \\
@@
                 & Depth factor
-                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
-                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement
-                & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
+                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
+                  \AirborneBlockAveragedSourcesVariableDepthDepthFactorIncrement
+                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
                 & \\
@@
                 & K nearest
-                & \AirborneBlockMedianSourcesVariableDepthKNearest
-                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement
-                & \BestAirborneBlockMedianSourcesVariableDepthKNearest
+                & \AirborneBlockAveragedSourcesVariableDepthKNearest
+                  \AirborneBlockAveragedSourcesVariableDepthKNearestIncrement
+                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
                 & \\
@@
                 & Spacing (m)
-                & \AirborneBlockMedianSourcesVariableDepthSpacing
-                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement
-                & \BestAirborneBlockMedianSourcesVariableDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockMedianSourcesVariableDepthDamping
-                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement
-                & \BestAirborneBlockMedianSourcesVariableDepthDamping
+                & \AirborneBlockAveragedSourcesVariableDepthSpacing
+                  \AirborneBlockAveragedSourcesVariableDepthSpacingIncrement
+                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
+                & \\
+            &
+                & Damping
+                & \AirborneBlockAveragedSourcesVariableDepthDamping
+                  \AirborneBlockAveragedSourcesVariableDepthDampingIncrement
+                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
                 & \\

### 2020-03-16 notebooks/02-grid-ground-data.py

@@ -58,7 +58,7 @@ field_units = "mGal"
 # Define set of interpolation parameters
 # ======================================
 # Define a list of source layouts
-layouts = ["source_below_data", "block_median_sources", "grid_sources"]
+layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
 dampings = np.logspace(-4, 2, 7)
 # Define depht values
@@ -74,7 +74,7 @@ grid_sources_dampings = np.logspace(1, 4, 4)
 depth_factors = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
 variable_depths = np.arange(0, 1500, 200)
 k_values = [1, 5, 10, 15]
-# Define block spacing for block median sources
+# Define block spacing for block averaged sources
 block_spacings = np.arange(1e3, 5e3, 1e3)
 # -
 
@@ -111,8 +111,8 @@ parameters[layout][depth_type] = dict(
     k_nearest=k_values,
 )
 
-# Block-median sources
-layout = "block_median_sources"
+# Block-averaged sources
+layout = "block_averaged_sources"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths, spacing=block_spacings,

### 2020-03-16 notebooks/03-grid-airborne-data.py

@@ -63,7 +63,7 @@ field_units = "mGal"
 # Define set of interpolation parameters
 # ======================================
 # Define a list of source layouts
-layouts = ["source_below_data", "block_median_sources", "grid_sources"]
+layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
 dampings = np.logspace(-4, 2, 7)
 # Define depht values
@@ -79,7 +79,7 @@ grid_sources_dampings = np.logspace(1, 4, 4)
 depth_factors = [1, 2, 3, 4, 5, 6]
 variable_depths = np.arange(50, 1500, 200)
 k_values = [1, 5, 10, 15]
-# Define block spacing for block median sources
+# Define block spacing for block averaged sources
 block_spacings = np.arange(1e3, 5e3, 1e3)
 # -
 
@@ -109,8 +109,8 @@ parameters[layout][depth_type] = dict(
     k_nearest=k_values,
 )
 
-# Block-median sources
-layout = "block_median_sources"
+# Block-averaged sources
+layout = "block_averaged_sources"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths, spacing=block_spacings,

### 2020-03-16 notebooks/block-averaged-schematics.py

@@ -6,14 +6,14 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.5
+#       jupytext_version: 1.3.4
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
 #     name: conda-env-eql_source_layouts-py
 # ---
 
-# # Schematic figure of block-median sources
+# # Schematic figure of block-averaged sources
 
 # Import packages
 
@@ -23,7 +23,7 @@ import numpy as np
 import verde as vd
 import matplotlib.pyplot as plt
 
-from eql_source_layouts import block_median_sources
+from eql_source_layouts import block_averaged_sources
 
 # -
 
@@ -45,9 +45,9 @@ coordinates = vd.scatter_points(
     region, size=n_data, random_state=seed, extra_coords=height
 )
 
-# Create block-median sources
+# Create block-averaged sources
 
-points = block_median_sources(
+points = block_averaged_sources(
     coordinates, depth=depth, spacing=spacing, depth_type="constant_depth"
 )
 
@@ -96,14 +96,14 @@ for y in grid_lines[1]:
     ax.plot((xmin, xmax), (y, y), **grid_style)
 ax.scatter(*coordinates[:2], **scatter_style)
 
-# Plot block-median sources and grid
+# Plot block-averaged sources and grid
 ax = axes[2]
 for x in grid_lines[0]:
     ax.plot((x, x), (ymin, ymax), **grid_style)
 for y in grid_lines[1]:
     ax.plot((xmin, xmax), (y, y), **grid_style)
 sources_scatter = ax.scatter(
-    *points[:2], color="C1", label="block-median sources", **scatter_style
+    *points[:2], color="C1", label="block-averaged sources", **scatter_style
 )
 
 # Configure axes
@@ -136,7 +136,6 @@ for ax, label in zip(axes, labels):
 
 plt.tight_layout(w_pad=0)
 plt.savefig(
-    os.path.join("..", "manuscript", "figs", "block-median-sources-schematics.pdf")
+    os.path.join("..", "manuscript", "figs", "block-averaged-sources-schematics.pdf")
 )
 plt.show()
-# -

### 2020-03-16 notebooks/source-distributions.py

@@ -7,7 +7,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.5
+#       jupytext_version: 1.3.4
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -24,8 +24,8 @@
 #
 # 1. **Source below data**: One source point beneath each data point
 # 2. **Block averaged sources**: Split the region in blocks of equal size, compute the
-#    median coordinate of the data points per block, and put one point source beneath
-#    this block-median coordinate.
+#    averaged coordinate of the data points per block, and put one point source beneath
+#    this block-averaged coordinate.
 # 3. **Grid of sources**: A regular grid of source points
 #
 # And the depth types, i.e. how deep do we put the point sources:
@@ -35,7 +35,7 @@
 # 2. **Relative depth**: Each source is located at a constant distance beneath its
 #    corresponding observation (or block averaged) point.
 # 3. **Variable depth**: Locate each source according to the Relative dpeth approach
-#    and then modify this depth by removing a term that depends on the median distance
+#    and then modify this depth by removing a term that depends on the averaged distance
 #    to the k nearest source points.
 #
 # The first two layouts can be setted with any of these three types of depth, although
@@ -76,7 +76,7 @@ ground_results_dir = os.path.join("..", "results", "ground_survey")
 airborne_results_dir = os.path.join("..", "results", "airborne_survey")
 
 # Define dictionaries where the source distributions will be stored
-layouts = ["source_below_data", "block_median_sources", "grid_sources"]
+layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 source_distributions = {layout: {} for layout in layouts}
 
 # Define a region for the synthetic survey
@@ -85,7 +85,7 @@ region_degrees = [-0.5, 0.5, -0.5, 0.5]  # given in degrees
 # Set a depth of 2km
 depth = 2000
 
-# Define a block size of 2km for block-median layouts
+# Define a block size of 2km for block-averaged layouts
 spacing = 4000
 
 # Define set of parameters for each source distribution
@@ -112,8 +112,8 @@ parameters[layout][depth_type] = {
     "k_nearest": 15,
 }
 
-# ... for block-median sources layout
-layout = "block_median_sources"
+# ... for block-averaged sources layout
+layout = "block_averaged_sources"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = {
     "depth_type": depth_type,

### 2020-03-16 notebooks/source-layouts-schematics.py

@@ -62,7 +62,7 @@ coordinates = (survey.easting, survey.northing, survey.height)
 block_spacing = 4000
 grid_spacing = 4000
 
-layouts = ["source_below_data", "block_median_sources", "grid_sources"]
+layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 depth_type = "constant_depth"
 
 parameters = {}
@@ -70,7 +70,7 @@ parameters = {}
 layout = "source_below_data"
 parameters[layout] = dict(depth_type=depth_type, depth=500,)
 
-layout = "block_median_sources"
+layout = "block_averaged_sources"
 parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=block_spacing)
 
 layout = "grid_sources"
@@ -129,7 +129,7 @@ for ax, layout in zip(axes[1:], layouts):
     ax.scatter(*source_distributions[layout][:2], s=size, c="C1")
     ax.set_title(layout.replace("_", " ").title())
 
-# Add blocks boundaries to Block Median Sources plot
+# Add blocks boundaries to Block Averaged Sources plot
 ax = axes[2]
 grid_style = dict(color="grey", linewidth=0.3, linestyle="--")
 xmin, xmax, ymin, ymax = region[:]

### 2020-03-16 notebooks/02-grid-ground-data.py
Rerun all notebooks

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.4
+#       jupytext_version: 1.3.5
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python

### 2020-03-16 notebooks/source-distributions.py

@@ -7,7 +7,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.4
+#       jupytext_version: 1.3.5
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python

### 2020-03-17 notebooks/source-layouts-schematics.py
Rerun source-layouts-schematics.py

@@ -165,3 +165,5 @@ for layout in layouts:
 
 with open(os.path.join("..", "manuscript", "source_layouts_schematics.tex"), "w") as f:
     f.write("\n".join(tex_lines))
+
+

### 2020-03-17 eql_source_layouts/__init__.py
Rename block median sources for block averaged sources (#37)
Standarize the source layout name to block_averaged_sources.

@@ -1,7 +1,7 @@
 # pylint: disable=missing-docstring
 # Import functions/classes to make the public API
 from ._version import get_versions
-from .layouts import source_below_data, block_median_sources, grid_sources
+from .layouts import source_below_data, block_averaged_sources, grid_sources
 from .synthetic_model import synthetic_model
 from .plot import plot_prediction
 from .latex_variables import (

### 2020-03-17 eql_source_layouts/layouts.py

@@ -2,7 +2,13 @@
 Create different layouts of point sources
 """
 import numpy as np
-from verde import median_distance, BlockReduce, get_region, pad_region, grid_coordinates
+from verde import (
+    median_distance,
+    BlockReduce,
+    get_region,
+    pad_region,
+    grid_coordinates,
+)
 
 
 DEPTH_TYPES = ["constant_depth", "relative_depth", "variable_depth"]
@@ -42,7 +48,7 @@ def source_below_data(coordinates, depth_type, **kwargs):
 
     The *variable depth* locates the sources in the same way the _relative depth_ does
     but also adds a term that can be computed as the product of the ``depth_factor`` and
-    the median distance between the ``k_nearest`` nearest neighbor sources.
+    the averaged distance between the ``k_nearest`` nearest neighbor sources.
 
     The depth type can be chosen through the ``depth_type`` argument, while the
     ``depth``, ``depth_factor`` and ``k_nearest`` arguments can be passed as ``kwargs``.
@@ -69,25 +75,25 @@ def source_below_data(coordinates, depth_type, **kwargs):
     return points
 
 
-def block_median_sources(coordinates, spacing, depth_type, **kwargs):
+def block_averaged_sources(coordinates, spacing, depth_type, **kwargs):
     """
-    Put one point source beneath the block-median observation points
+    Put one point source beneath the block-averaged observation points
 
     The depth of the point sources can be set according to the following methods:
     *constant*, *relative* or *variable* depth.
 
     The *constant depth* locates all sources at the same depth. It can be computed as
-    the difference between the minimum elevation of block-median coordinates and the
+    the difference between the minimum elevation of block-averaged coordinates and the
     ``depth`` argument.
 
     The *relative depth* locates all sources at a constant _relative_ ``depth`` beneath
-    its corresponding block-median point. Each source point will be located at the same
-    distance from its corresponding block-median point. Sources points will _copy_ the
-    elevations of the block-median coordinates at a ``depth`` below.
+    its corresponding block-averaged point. Each source point will be located at the
+    same distance from its corresponding block-averaged point. Sources points will
+    _copy_ the elevations of the block-averaged coordinates at a ``depth`` below.
 
     The *variable depth* locates the sources in the same way the _relative depth_ does
     but also adds a term that can be computed as the product of the ``depth_factor`` and
-    the median distance between the ``k_nearest`` nearest neighbor sources.
+    the averaged distance between the ``k_nearest`` nearest neighbor sources.
[…]

### 2020-03-17 eql_source_layouts/tests/test_layouts.py

@@ -11,7 +11,7 @@ from ..layouts import (
     relative_depth,
     variable_depth,
     source_below_data,
-    block_median_sources,
+    block_averaged_sources,
     grid_sources,
 )
 
@@ -143,11 +143,11 @@ def test_source_below_data_kwargs(coordinates):
     )
 
 
-# Block median sources
-# --------------------
-def test_block_median_sources(coordinates):
+# Block averaged sources
+# ----------------------
+def test_block_averaged_sources(coordinates):
     """
-    Check if block_median_sources block average coordinates
+    Check if block_averaged_sources block average coordinates
     """
     spacing = 4000
     depth = 100
@@ -159,7 +159,7 @@ def test_block_median_sources(coordinates):
         "variable_depth": {"depth_factor": depth_factor, "k_nearest": k_nearest},
     }
     for depth_type, params in parameters.items():
-        points = block_median_sources(
+        points = block_averaged_sources(
             coordinates, depth_type=depth_type, spacing=spacing, depth=depth, **params
         )
         # Check if there's one source per block
@@ -172,18 +172,18 @@ def test_block_median_sources(coordinates):
         npt.assert_allclose(points[1], block_coords[1][labels], atol=spacing / 2)
 
 
-def test_block_median_sources_kwargs(coordinates):
+def test_block_averaged_sources_kwargs(coordinates):
     """
-    Check if extra kwargs on block_median_sources are ignored
+    Check if extra kwargs on block_averaged_sources are ignored
     """
     depth_type = "constant_depth"
     depth = 100
     spacing = 4000
     npt.assert_allclose(
-        block_median_sources(
+        block_averaged_sources(
             coordinates, depth_type=depth_type, depth=depth, spacing=spacing,
         ),
-        block_median_sources(
+        block_averaged_sources(
             coordinates,
             depth_type=depth_type,
             depth=depth,
@@ -245,4 +245,4 @@ def test_invalid_depth_type(coordinates):
     with pytest.raises(ValueError):
         source_below_data(coordinates, depth_type=depth_type)
     with pytest.raises(ValueError):
-        block_median_sources(coordinates, depth_type=depth_type, spacing=4000)
+        block_averaged_sources(coordinates, depth_type=depth_type, spacing=4000)

### 2020-03-17 notebooks/02-grid-ground-data.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.4
+#       jupytext_version: 1.3.5
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -58,7 +58,7 @@ field_units = "mGal"
 # Define set of interpolation parameters
 # ======================================
 # Define a list of source layouts
-layouts = ["source_below_data", "block_median_sources", "grid_sources"]
+layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
 dampings = np.logspace(-4, 2, 7)
 # Define depht values
@@ -74,7 +74,7 @@ grid_sources_dampings = np.logspace(1, 4, 4)
 depth_factors = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
 variable_depths = np.arange(0, 1500, 200)
 k_values = [1, 5, 10, 15]
-# Define block spacing for block median sources
+# Define block spacing for block averaged sources
 block_spacings = np.arange(1e3, 5e3, 1e3)
 # -
 
@@ -111,8 +111,8 @@ parameters[layout][depth_type] = dict(
     k_nearest=k_values,
 )
 
-# Block-median sources
-layout = "block_median_sources"
+# Block-averaged sources
+layout = "block_averaged_sources"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = dict(
     depth_type=depth_type, damping=dampings, depth=depths, spacing=block_spacings,

### 2020-03-17 notebooks/block-averaged-schematics.py

@@ -13,7 +13,7 @@
 #     name: conda-env-eql_source_layouts-py
 # ---
 
-# # Schematic figure of block-median sources
+# # Schematic figure of block-averaged sources
 
 # Import packages
 
@@ -23,7 +23,7 @@ import numpy as np
 import verde as vd
 import matplotlib.pyplot as plt
 
-from eql_source_layouts import block_median_sources
+from eql_source_layouts import block_averaged_sources
 
 # -
 
@@ -45,9 +45,9 @@ coordinates = vd.scatter_points(
     region, size=n_data, random_state=seed, extra_coords=height
 )
 
-# Create block-median sources
+# Create block-averaged sources
 
-points = block_median_sources(
+points = block_averaged_sources(
     coordinates, depth=depth, spacing=spacing, depth_type="constant_depth"
 )
 
@@ -96,14 +96,14 @@ for y in grid_lines[1]:
     ax.plot((xmin, xmax), (y, y), **grid_style)
 ax.scatter(*coordinates[:2], **scatter_style)
 
-# Plot block-median sources and grid
+# Plot block-averaged sources and grid
 ax = axes[2]
 for x in grid_lines[0]:
     ax.plot((x, x), (ymin, ymax), **grid_style)
 for y in grid_lines[1]:
     ax.plot((xmin, xmax), (y, y), **grid_style)
 sources_scatter = ax.scatter(
-    *points[:2], color="C1", label="block-median sources", **scatter_style
+    *points[:2], color="C1", label="block-averaged sources", **scatter_style
 )
 
 # Configure axes
@@ -136,7 +136,6 @@ for ax, label in zip(axes, labels):
 
 plt.tight_layout(w_pad=0)
 plt.savefig(
-    os.path.join("..", "manuscript", "figs", "block-median-sources-schematics.pdf")
+    os.path.join("..", "manuscript", "figs", "block-averaged-sources-schematics.pdf")
 )
 plt.show()
-# -

### 2020-03-23 manuscript/manuscript.tex
Rename block median sources for block averaged sources (#37)
Standarize the source layout name to block_averaged_sources.
Improve manuscript

@@
 
+Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
+observation points that simulates a ground survey, and the possible location of
+sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
+averaged sources} and (d) the \emph{grid sources} layouts.
+
 \begin{figure*}
@@
         (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
-            obtained through the \emph{sources beneath data} layout.
-        (c) Location of the \SourceLayoutsSchematicsBlockaveragedSources{}
+            obtained through the \emph{sources below data} layout.
+        (c) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
             sources obtained through the \emph{block averaged sources} layout.
@@
 \noindent where \emph{data point height} is the elevation of the corresponding
-observation (or block averaged) point to the source, \emph{depth factor} and
-\emph{relative depth} are parameters and \emph{mean distance} is the mean
-distance to the $k$ nearest source neighbours.
-This term will be smaller in case of clustered sources, making them shallower
-than scattered and distant sources.
+observation (or block averaged) point, \emph{mean distance} is the mean
+distance to the $k$ nearest source neighbours, \emph{depth factor} and
+\emph{relative depth} are parameters.
+The addition of this new term will make clustered sources to be shallower than
+scattered and distant sources.
 
@@
 \citet{cordell1992, guspi2004, guspi2009}.
-
-Worth mention that the two last approaches (the \emph{relative depth} and the
-\emph{variable depth}) could not be applied to \emph{grid sources}.
 
@@
 The data from each synthetic survey is interpolated on the points of the
-\emph{target} grid.
-The interpolations are carried out using each source distribution and combining
-different parameter values for each distribution.
-Each prediction is then scored against the \emph{target} grid.
+\emph{target} grid and then scored against the \emph{target} grid.
 We can then quantitatively compare how accurate is each source distribution at
@@
 
-        \multirow{11}{*}{Block averaged sources}
+        \multirow{11}{*}{Block Averaged Sources}
             & \multirow{3}{*}{Constant Depth}

### 2020-03-26 manuscript/manuscript.tex
Remove rubbish line from manuscript
Improve manuscript

@@
 The fundamental solution of any harmonic field can be obtained as follows
-\citep{blakely1995}:
+\citep[p.~37]{blakely1995}:
 
@@
 Therefore is usually needed to add regularization functions in order to obtain
-stable solutions \citep{oliveira2013}.
-Moreover there's no limitation on the amount of point sources.
-The number of sources can either be equal, less or more than the number of
-observation points, leading to well, under or overdetermined linear problem,
-respectively.
+stable solutions
+(\citealp[p.~52]{menke1989}; \citealp{cooper2000}; \citealp{oliveira2013}).
+Worth noting that the number of sources can either be equal, greater or lower
+than the number of observation points, leading to well, under or overdetermined
+linear problem, respectively.
 
 % Add other possible applications to the EQL like RTP or upward continuation.
-
-% EQL implementation on Harmonica.
 
@@
 distribution of sources will be generated.
+
+% Worth noting that the \emph{source below data} generates a number of sources
+% equal to the data points, obtaining a well determined linear problem.
+% The \emph{block averaged sources} layouts can generate a number of point
+% sources equal or lower than the number of data points, well or
+% overdetermined.
+% The \emph{grid sources} is the only layout that can generate either a well,
+% over or under determined problem.
 

### 2020-03-26 notebooks/03-grid-airborne-data.py
Remove pad parameter from gridding nbs and run them

@@ -69,10 +69,9 @@ dampings = np.logspace(-4, 2, 7)
 # Define depht values
 depths = np.arange(1e3, 18e3, 2e3)
 # Define parameters for the grid sources:
-#    spacing, depth, padding and damping
+#    spacing, depth and damping
 grid_sources_spacings = [1e3, 2e3, 3e3]
 grid_sources_depths = np.arange(3e3, 15e3, 2e3)
-grid_sources_paddings = [0, 0.1, 0.2]
 grid_sources_dampings = np.logspace(1, 4, 4)
 # Define parameters for variable relative depth layouts:
 #    depth factor, depth shift and k_values
@@ -138,7 +137,6 @@ parameters[layout][depth_type] = dict(
     depth_type=depth_type,
     damping=grid_sources_dampings,
     depth=grid_sources_depths,
-    pad=grid_sources_paddings,
     spacing=grid_sources_spacings,
 )
 # -

### 2020-04-07 manuscript/manuscript.tex
Remove pad rows on parameter tables
Started reviewing the introduction
Got through the first two paragraphs. Minor re-wording and added a
reference to the method in GMT's `surface` module.

@@
 
-Potential field data, like gravity and magnetics, are useful for geophysics
-exploration.
-The potential field data can be obtained from ground, airborne or satellite
-measurements.
-On ground surveys the data is often gathered on scattered points or following
-irregular paths, usually at the topographic surface.
-The data points have different heights.
-On airborne surveys the data is gathered on flight paths, producing a large
-number of data points concentrated along almost straight lines.
-The height of measurement could change because of the vertical movement of the
-airship.
-To improve visualization of the data for interpretation and to prepare the data
-for processing through different methods (RTP, upward continuation, Euler
-deconvolution, etc), the data needs to be interpolated on a regular grid of
-data points.
-
-There are several methods for interpolating 2D data like minimum curvature,
-biharmonic Splines or Kriging.
-These all-purpose methods show a few problems when applied to potential field
-data.
-(i) They don't take into account the height of the observation points.
-Potential field data has a strong dependency on measurement height.
-(ii) The predicted grid data is not necessary an Harmonic function.
-(iii) They don't usually take into account the anisotropy of the observation
-points in ground and airborne surveys.
+Measurements of anomalies in potential fields, like gravity disturbances and
+total-field magnetic anomalies, are widely used in geophysical exploration for
+their relatively low cost of acquisition.
+These data can be surveyed using ground, airborne, shipborne, or satellite
+systems.
+In ground surveys, the data are often gathered following
+irregular paths or networks along the surface of the terrain, leading to highly
+variable elevations in mountainous regions.
+On airborne surveys, the data are gathered along flight lines, producing a
+large number of measurements concentrated along almost straight lines.
+In surveys that drape the topography, the height of measurement could change
+dramatically because of the vertical movement of the aircraft.
+Processing of the data often involves interpolation onto a regular grid at
+constant height, both to improve visualization for interpretation purposes as
+well as to prepare the data for further processing and modelling (e.g.,
+reduction-to-the-pole, derivative calculations, upward continuation, Euler
+deconvolution),
+
+Several methods exist in the literature for interpolation in two dimensions,
+for example continuous curvature splines in tension \citep{smith1990},
+biharmonic (thin-plate) splines \citep{sandwell1987}, and kriging.
+These general-purpose methods have limitations when it comes to interpolating
+potential field data:
+(i) they are not able to take into account the variable height of the
+observation points;
+(ii) the interpolating functions are not necessarily harmonic functions, which
+is the underlying assumption behind many processing techniques
+(e.g., upward continuation and vertical derivatives).
 

### 2020-04-07 manuscript/manuscript.tex
Finish introduction with a motivation paragraph
Added some more references for strategies for accelerating the EQL
processing. Need to add text about them all.

@@
         S.R. Soler$^{1,2}$,
-        L. Uieda$^{3}$
+        Leonardo Uieda$^{3}$
     }
@@
     {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
-    {\small $^{3}$University of Liverpool} \\
+    {\small $^{3}$Department of Earth, Ocean and Ecological Sciences, School of Environmental Sciences, University of Liverpool, UK} \\
 
@@
 reduction-to-the-pole, derivative calculations, upward continuation, Euler
-deconvolution),
+deconvolution).
 
@@
 (i) they are not able to take into account the variable height of the
-observation points;
+observation points and
 (ii) the interpolating functions are not necessarily harmonic functions, which
@@
 
-One of the most widely used methods for interpolating gravity and magnetic data
-is the equivalent sources technique (also known as equivalent layer, radial
-basis functions or Green's functions interpolation).
-It consists in estimating a source distribution that produces the same field as
-the one measured and using this estimate to predict new values.
-\citet{dampney1969} was the first to introduce the equivalent source technique.
-
-The EQL can be used for interpolation of potential field data
-\citep{cordell1992, cooper2000}.
-It has been also used for applying a reduction to the pole to magnetic data
-\citep{guspi2009, silva1986, emilia1973, nakatsuka2006} or an upward
-continuation (cite).
-
-The most widely used source distribution is a set of point sources.
-The potential field of point sources is easy to compute.
-\citet{barnes2011} make use of prisms.
-How to locate these point masses?
-Existing approaches:
-(i) one point source beneath each observation point at a constant depth (cite),
-(ii) one point source beneath each observation point at a depth proportional to
-the distance to its nearest data points (cite),
-(iii) a regular grid of sources \citep{barnes2011}.
-
-We want to find out which distribution of sources produces the best
-interpolations.
+A widely used method for interpolating gravity and magnetic data
+is the equivalent source technique (also known as equivalent layer, radial
+basis functions, or Green's functions interpolation), first introduced by
+\citet{dampney1969}.
+It consists in fitting a model of point sources to the data and using this
+model to predict new data values.
+Besides interpolation, equivalent sources have been used for
+reduction-to-the-pole of magnetic data
+\citep{guspi2009, silva1986, emilia1973, nakatsuka2006}, upward
+continuation (CITATION NEEDED), and merging datasets (CITATION NEEDED).
+
+Many variants of the equivalent source technique have been proposed.
+The key factors that vary between them are: (i) the type of source, (ii)
+the location of the sources, and (iii) the solution strategy.
+The type of source is most commonly a point mass (for gravity) or dipole (for
+magnetics) (CITATION NEEDED).
+However, an inverse distance function $1/r$ (CITATION NEEDED),
+right-rectangular prisms (CITATION NEEDED:
+one by the simpeg group and one for magnetic data integration),
+and tesseroids \citep{bouman2016} have also been used successfully.
+The sources are often distributed on a regular grid at a constant depth (e.g.,
+CITATION NEEDED) or placed beneath each data point (e.g., CITATION NEEDED).
+The model is usually estimated through damped least-squares, which imposes a
+heavy computational load when the number of data points is large (e.g.,
+airborne and satellite surveys).
+Other solution strategies have been proposed to attempt to reduce this load and
+make the use of equivalent sources feasible.
+\citet{mendonca1994} blablabla.
+\citet{leao1989} blablabla.
+\citet{li2010} blablabla.
+\citet{barnes2011} blablabla.
+\citet{oliveira2013} blablabla.
+\citet{siqueira2017} blablabla.
+\citet{jirigalatu2019} blablabla.
+Many other techniques have been proposed, more so than could be included here.
+
+In the present study, we will evaluate the impact of different source
+distributions, both horizontally and vertically, on the performance of
+equivalent source interpolation.
+Vertically, the sources can be located: (i) at a constant depth, (ii) at a
+depth proportional to the height of observations, and (iii) at a depth
+proportional to the median distance to adjacent data points.
+The horizontal source distribution strategies are: (i) regular grid, (ii)
+beneath data point, (iii) on the median location of data points inside spatial
+blocks. The latter is a novel method while the others have been used in some
+form in the past.
 

### 2020-04-08 manuscript/manuscript.tex
Apply suggestions by Santiago
Co-Authored-By: Santiago Soler <santiago.r.soler@gmail.com>

@@
     {\large
-        S.R. Soler$^{1,2}$,
+        Santiago R. Soler$^{1,2}$,
         Leonardo Uieda$^{3}$
@@
 large number of measurements concentrated along almost straight lines.
-In surveys that drape the topography, the height of measurement could change
-dramatically because of the vertical movement of the aircraft.
+Measurement height can also change because of the vertical movement of the aircraft.
 Processing of the data often involves interpolation onto a regular grid at
@@
 for example continuous curvature splines in tension \citep{smith1990},
-biharmonic (thin-plate) splines \citep{sandwell1987}, and kriging.
+biharmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
 These general-purpose methods have limitations when it comes to interpolating
@@
 \citet{dampney1969}.
-It consists in fitting a model of point sources to the data and using this
+It consists in fitting a model of elementary sources to the data and using this
 model to predict new data values.
@@
 However, an inverse distance function $1/r$ (CITATION NEEDED),
-right-rectangular prisms (CITATION NEEDED:
+right-rectangular prisms \citep{barnes2011} (CITATION NEEDED:
 one by the simpeg group and one for magnetic data integration),
 and tesseroids \citep{bouman2016} have also been used successfully.
-The sources are often distributed on a regular grid at a constant depth (e.g.,
-CITATION NEEDED) or placed beneath each data point (e.g., CITATION NEEDED).
+The sources are often distributed on a regular grid at a constant depth
+\citep[e.g.,~]{barnes2011,oliveira2013}
+(e.g., CITATION NEEDED) or placed beneath each data point (e.g., CITATION NEEDED).
 The model is usually estimated through damped least-squares, which imposes a

### 2020-04-08 manuscript/manuscript.tex
Better description of relative depths

@@
 Vertically, the sources can be located: (i) at a constant depth, (ii) at a
-depth proportional to the height of observations, and (iii) at a depth
+depth relative to the height of observations, and (iii) at a depth
 proportional to the median distance to adjacent data points.

### 2020-07-24 manuscript/manuscript.tex
Finish introduction

@@
 \usepackage{siunitx}
-\usepackage[round]{natbib}
+\usepackage[round,authoryear,sort]{natbib}
 \usepackage{url}
@@
 systems.
-In ground surveys, the data are often gathered following
-irregular paths or networks along the surface of the terrain, leading to highly
-variable elevations in mountainous regions.
+In ground surveys, the data are often gathered following irregular paths or
+networks along the surface of the terrain, leading to highly variable
+elevations in mountainous regions.
 On airborne surveys, the data are gathered along flight lines, producing a
 large number of measurements concentrated along almost straight lines.
-Measurement height can also change because of the vertical movement of the aircraft.
+Measurement height can also change because of the vertical movement of the
+aircraft.
 Processing of the data often involves interpolation onto a regular grid at
@@
 for example continuous curvature splines in tension \citep{smith1990},
-biharmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
+bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
 These general-purpose methods have limitations when it comes to interpolating
@@
 reduction-to-the-pole of magnetic data
-\citep{guspi2009, silva1986, emilia1973, nakatsuka2006}, upward
-continuation (CITATION NEEDED), and merging datasets (CITATION NEEDED).
-
-Many variants of the equivalent source technique have been proposed.
+\citep{silva1986, nakatsuka2006, guspi2009}, upward
+continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
+data \citep{barnes2011}, modelling the lithospheric magnetic field
+\citep{kother2015}, recovering the magnetic induction vector from
+total-field magnetic anomalies \citep{li2020}, and more.
+
+Many variants of the equivalent source technique have been proposed, often
+attempting to obtain faster or more accurate solutions.
 The key factors that vary between them are: (i) the type of source, (ii)
@@
 The type of source is most commonly a point mass (for gravity) or dipole (for
-magnetics) (CITATION NEEDED).
-However, an inverse distance function $1/r$ (CITATION NEEDED),
-right-rectangular prisms \citep{barnes2011} (CITATION NEEDED:
-one by the simpeg group and one for magnetic data integration),
+magnetics) \citep[e.g.,~]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
+However, an inverse distance function $1/r$ \citep{cordell1992},
+right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019, li2020},
 and tesseroids \citep{bouman2016} have also been used successfully.
 The sources are often distributed on a regular grid at a constant depth
-\citep[e.g.,~]{barnes2011,oliveira2013}
-(e.g., CITATION NEEDED) or placed beneath each data point (e.g., CITATION NEEDED).
+\citep[e.g.,~]{leao1989, barnes2011, oliveira2013}
+or placed beneath each data point \citep[e.g.,~]{cordell1992, siqueira2017}.
 The model is usually estimated through damped least-squares, which imposes a
@@
 airborne and satellite surveys).
-Other solution strategies have been proposed to attempt to reduce this load and
-make the use of equivalent sources feasible.
-\citet{mendonca1994} blablabla.
-\citet{leao1989} blablabla.
-\citet{li2010} blablabla.
-\citet{barnes2011} blablabla.
-\citet{oliveira2013} blablabla.
-\citet{siqueira2017} blablabla.
-\citet{jirigalatu2019} blablabla.
-Many other techniques have been proposed, more so than could be included here.
-
-In the present study, we will evaluate the impact of different source
-distributions, both horizontally and vertically, on the performance of
-equivalent source interpolation.
-Vertically, the sources can be located: (i) at a constant depth, (ii) at a
-depth relative to the height of observations, and (iii) at a depth
-proportional to the median distance to adjacent data points.
-The horizontal source distribution strategies are: (i) regular grid, (ii)
-beneath data point, (iii) on the median location of data points inside spatial
-blocks. The latter is a novel method while the others have been used in some
-form in the past.
+To reduce the computational load, \citet{mendonca1994} built the solution
+iteratively by incorporating one data point at a time using the ``equivalent
+data concept''.
+\citet{leao1989} processed the input data using a moving window, only fitting the
+data inside the window and predicting observations at the center of the window.
+\citet{li2010} and \citet{barnes2011} apply different operations to generate a
+sparse representation of the sensitive matrix (respectively, wavelet
+compression and quadtree discretization), which significantly improves the
+speed of the least-squares solution.
+\citet{oliveira2013} parametrized the equivalent layer as a piecewise bivariate
+polynomial function, reducing the number of parameters in the solution.
+\citet{siqueira2017} developed an iterative solution in which the sensitivity
+matrix is transformed into a diagonal matrix with constant terms through the
+``excess mass criterion''.
+\citet{jirigalatu2019} applied the Guass-FFT method to speed up the forward
+modelling operations and solved the least-squares problem using steepest
+descent to avoid calculating the Hessian matrix and solving linear systems.
+Most existing methods solve under-determined problems, requiring a much larger
+number of equivalent sources than the number of data points.
+Furthermore, many of the optimizations proposed are also complex to implement
+in a computer program, limiting their wider adoption.
+
+In the present study,
+we propose a simple method for reducing the number of equivalent sources.
+The survey area is divided into horizontal blocks and one source is assigned
+to each block at the median horizontal location of the data points.
+For airborne surveys, which are oversampled along tracks, this can greatly
+reduce the size of the inverse problem while retaining the quality of
+interpolation.
+We experiment with the existing strategies of assigning sources at
+a uniform depth, a depth relative to the data height, or a depth proportional
+to the median distance to adjacent data points.
+Through tests on synthetic data, we show that non-uniform depths perform better
+at interpolation and that our method is able to achieve the same accuracy as a
+traditional equivalent layer while using a fraction of the number of sources.
 
@@
 physical-property distribution that generates any measured potential field.
-Nevertheless this ambiguity can also be exploited for developing preprocessing
+Nevertheless this ambiguity can also be exploited for developing pre-processing
 techniques like interpolating potential field data.
@@
 If the sources are set too close to the data points, the source distribution
-it's very likely to overfit the data: the measured field will be recovered, but
+it's very likely to over-fit the data: the measured field will be recovered, but
 the predictions on unobserved locations will be very inaccurate.
@@
             &
-                & Pad
-                & \GroundGridSourcesConstantDepthPad
-                  \GroundGridSourcesConstantDepthPadIncrement
-                & \BestGroundGridSourcesConstantDepthPad
-                & \\
-            &
                 & Damping
@@
             &
-                & Pad
-                & \AirborneGridSourcesConstantDepthPad
-                  \AirborneGridSourcesConstantDepthPadIncrement
-                & \BestAirborneGridSourcesConstantDepthPad
-                & \\
-            &
                 & Damping
@@
 
-\bibliographystyle{plainnat}
+\bibliographystyle{humannat}
 \bibliography{references}

### 2020-07-24 manuscript/manuscript.tex
Fix typo

@@
 ``excess mass criterion''.
-\citet{jirigalatu2019} applied the Guass-FFT method to speed up the forward
+\citet{jirigalatu2019} applied the Gauss-FFT method to speed up the forward
 modelling operations and solved the least-squares problem using steepest

### 2020-07-28 manuscript/manuscript.tex
Rephrase the part about the 1/r functions

@@
 The type of source is most commonly a point mass (for gravity) or dipole (for
-magnetics) \citep[e.g.,~]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
-However, an inverse distance function $1/r$ \citep{cordell1992},
+magnetics) \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
+However,
+point sources with a simple inverse distance function instead of gravity or
+magnetic fields \citep{cordell1992},
 right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019, li2020},
-and tesseroids \citep{bouman2016} have also been used successfully.
+and tesseroids \citep{bouman2016}
+have also been used successfully.
 The sources are often distributed on a regular grid at a constant depth
-\citep[e.g.,~]{leao1989, barnes2011, oliveira2013}
-or placed beneath each data point \citep[e.g.,~]{cordell1992, siqueira2017}.
+\citep[e.g.,~][]{leao1989, barnes2011, oliveira2013}
+or placed beneath each data point \citep[e.g.,~][]{cordell1992, siqueira2017}.
 The model is usually estimated through damped least-squares, which imposes a

### 2020-08-27 manuscript/manuscript.tex

@@
 the location of the sources, and (iii) the solution strategy.
-The type of source is most commonly a point mass (for gravity) or dipole (for
-magnetics) \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
-However,
-point sources with a simple inverse distance function instead of gravity or
-magnetic fields \citep{cordell1992},
-right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019, li2020},
-and tesseroids \citep{bouman2016}
-have also been used successfully.
+The type of source is most commonly a point mass for gravity or dipole for
+magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
+However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
+li2020} and tesseroids \citep{bouman2016} have also been used successfully.
+In fact, even point sources with a simple inverse distance function, instead of
+actual gravity or magnetic fields, can be used as
+equivalent sources \citep{cordell1992}.
 The sources are often distributed on a regular grid at a constant depth

### 2020-10-05 notebooks/01-synthetic-surveys.py
Simplify generation of latex variables
Computing notebooks only export variables to JSON files.
Add a new notebook that reads all JSON files and creates LaTeX variables
stored in .tex files. This notebooks handles units and format
conversions.
Simplify functions to create latex variables. Write some general purpouse
functions inside .py files and add some specific functions for
parameters into this new notebook.
Don't save `parameters_and_scores` pandas.DataFrame.

@@ -20,6 +20,7 @@
 # +
 from IPython.display import display
 from pathlib import Path
+import json
 import pyproj
 import numpy as np
 import xarray as xr
@@ -66,12 +67,6 @@ target_grid_spacing = 2e3
 target_grid_height = 2000
 # -
 
-# **Initialize latex_lines list**
-#
-# On this list we will store all the variables we want to mention on the LaTeX manuscript.
-
-latex_lines = []
-
 # ## Synthetic model made out of prisms
 
 # Project region coordinates to get synthetic model boundaries
@@ -97,36 +92,18 @@ ax.set_xlim(region[:2])
 ax.set_ylim(region[2:4])
 plt.show()
 
-# **Save model related quantities to LaTeX file**
+# **Save model related quantities on dictionary**
 
-# +
-assert model_region[5] == 0
+np.min(model["densities"])
 
-latex_lines.extend(
-    [
-        latex_variables("NPrisms", len(model["densities"])),
-        latex_variables(
-            "ModelEasting",
-            (model_region[1] - model_region[0]) * 1e-3,
-            r"\km",
-            fmt=".0f",
-        ),
-        latex_variables(
-            "ModelNorthing",
-            (model_region[1] - model_region[0]) * 1e-3,
-            r"\km",
-            fmt=".0f",
-        ),
-        latex_variables("ModelDepth", abs(model_region[4]) * 1e-3, r"\km", fmt=".0f"),
-        latex_variables(
-            "ModelMinDensity", np.min(model["densities"]), r"\kg\per\cubic\m", fmt=".0f"
-        ),
-        latex_variables(
-            "ModelMaxDensity", np.max(model["densities"]), r"kg\per\cubic\m", fmt=".0f"
-        ),
-    ]
-)
-# -
+variables = {
+    "n_prisms": len(model["densities"]),
+    "model_easting": (model_region[1] - model_region[0]),
+    "model_northing": (model_region[1] - model_region[0]),
+    "model_depth": abs(model_region[4]),
+    "model_min_density": np.min(model["densities"]),
+    "model_max_density": np.max(model["densities"]),
+}
 
 # ## Synthetic ground survey
 
@@ -187,20 +164,12 @@ survey.to_csv(ground_results_dir / "survey.csv", index=False)
 
 # Save ground survey quantities to LaTeX file
 
-latex_lines.extend(
-    [
-        latex_variables(
[…]

### 2020-10-05 notebooks/02-grid-ground-data.py

@@ -19,6 +19,7 @@
 
 # +
 from pathlib import Path
+import json
 import numpy as np
 import pandas as pd
 import xarray as xr
@@ -30,8 +31,6 @@ from source_layouts import (
     plot_prediction,
     get_best_prediction,
     predictions_to_datasets,
-    latex_parameters,
-    latex_best_parameters,
 )
 
 # -
@@ -60,21 +59,21 @@ field_units = "mGal"
 # Define a list of source layouts
 layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
-dampings = np.logspace(-4, 2, 7)
+dampings = np.logspace(-4, 2, 7).tolist()
 # Define depht values
-depths = np.arange(1e3, 18e3, 2e3)
+depths = np.arange(1e3, 18e3, 2e3).tolist()
 # Define parameters for the grid sources:
 #    spacing, depth and damping
-grid_sources_spacings = np.arange(1e3, 5e3, 1e3)
-grid_sources_depths = np.arange(3e3, 15e3, 2e3)
-grid_sources_dampings = np.logspace(1, 4, 4)
+grid_sources_spacings = np.arange(1e3, 5e3, 1e3).tolist()
+grid_sources_depths = np.arange(3e3, 15e3, 2e3).tolist()
+grid_sources_dampings = np.logspace(1, 4, 4).tolist()
 # Define parameters for variable relative depth layouts:
 #    depth_factor, depth and k_nearest
 depth_factors = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
-variable_depths = np.arange(0, 1500, 200)
+variable_depths = np.arange(0, 1500, 200).tolist()
 k_values = [1, 5, 10, 15]
 # Define block spacing for block averaged sources
-block_spacings = np.arange(1e3, 5e3, 1e3)
+block_spacings = np.arange(1e3, 5e3, 1e3).tolist()
 # -
 
 # ## Create dictionary with the parameter values for each source distribution
@@ -86,7 +85,7 @@ parameters = {layout: {} for layout in layouts}
 layout = "source_below_data"
 depth_type = "constant_depth"
 parameters[layout][depth_type] = dict(
-    depth_type=depth_type, damping=dampings, depth=depths.tolist()
+    depth_type=depth_type, damping=dampings, depth=depths
 )
 
 # Source below data
[…]

### 2020-10-05 notebooks/03-grid-airborne-data.py

@@ -19,6 +19,7 @@
 
 # +
 from pathlib import Path
+import json
 import numpy as np
 import pandas as pd
 import xarray as xr
@@ -30,8 +31,6 @@ from source_layouts import (
     plot_prediction,
     get_best_prediction,
     predictions_to_datasets,
-    latex_parameters,
-    latex_best_parameters,
 )
 
 # -
@@ -59,21 +58,21 @@ field_units = "mGal"
 # Define a list of source layouts
 layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
-dampings = np.logspace(-4, 2, 7)
+dampings = np.logspace(-4, 2, 7).tolist()
 # Define depht values
-depths = np.arange(1e3, 18e3, 2e3)
+depths = np.arange(1e3, 18e3, 2e3).tolist()
 # Define parameters for the grid sources:
 #    spacing, depth and damping
 grid_sources_spacings = [1e3, 2e3, 3e3]
-grid_sources_depths = np.arange(3e3, 15e3, 2e3)
-grid_sources_dampings = np.logspace(1, 4, 4)
+grid_sources_depths = np.arange(3e3, 15e3, 2e3).tolist()
+grid_sources_dampings = np.logspace(1, 4, 4).tolist()
 # Define parameters for variable relative depth layouts:
 #    depth factor, depth shift and k_values
 depth_factors = [1, 2, 3, 4, 5, 6]
-variable_depths = np.arange(50, 1500, 200)
+variable_depths = np.arange(50, 1500, 200).tolist()
 k_values = [1, 5, 10, 15]
 # Define block spacing for block averaged sources
-block_spacings = np.arange(1e3, 5e3, 1e3)
+block_spacings = np.arange(1e3, 5e3, 1e3).tolist()
 # -
 
 # ## Create dictionary with the parameter values for each source distribution
@@ -141,10 +140,11 @@ parameters[layout][depth_type] = dict(
 )
 # -
 
-# ### Save parameters to LaTeX variables file
+# ### Dump parameters to a JSON file
 
-with open(Path("..") / "manuscript" / "parameters_airborne_survey.tex", "w") as f:
-    f.write("\n".join(latex_parameters(parameters, "airborne")))
+json_file = results_dir / "parameters-airborne-survey.json"
+with open(json_file, "w") as f:
+    json.dump(parameters, f)
 
[…]

### 2020-10-05 notebooks/source-layouts-schematics.py

@@ -15,6 +15,7 @@
 
 # +
 from IPython.display import display  # noqa: F401  # ignore used but not imported
+import json
 from pathlib import Path
 import numpy as np
 import pandas as pd
@@ -29,7 +30,8 @@ from source_layouts import latex_variables, format_variable_name
 # ## Define parameters for building the source distributions
 
 # Define results directory to read synthetic ground survey
-ground_results_dir = Path("..") / "results" / "ground_survey"
+results_dir = Path("..") / "results"
+ground_results_dir = results_dir / "ground_survey"
 
 # ## Read synthetic ground survey
 #
@@ -161,22 +163,17 @@ plt.savefig(
 plt.show()
 # -
 
-# ## Save number of observation points and sources to LaTeX variables
+# ## Dump number of observation points and sources to JSON file
 
 # +
-tex_lines = []
-
-tex_lines.append(
-    latex_variables("SourceLayoutsSchematicsObservations", survey.easting.size),
-)
+variables = {
+    "source_layouts_schematics_observations": survey.easting.size,
+}
 for layout in layouts:
-    tex_lines.append(
-        latex_variables(
-            "SourceLayoutsSchematics{}".format(format_variable_name(layout)),
-            source_distributions[layout][0].size,
-        )
-    )
-# -
+    variables["source_layouts_schematics_{}".format(layout)] = source_distributions[
+        layout
+    ][0].size
 
-with open(Path("..") / "manuscript" / "source_layouts_schematics.tex", "w") as f:
-    f.write("\n".join(tex_lines))
+json_file = results_dir / "source-layouts-schematics.json"
+with open(json_file, "w") as f:
+    json.dump(variables, f)

### 2020-10-05 notebooks/source_layouts/__init__.py

@@ -4,10 +4,10 @@ from .layouts import source_below_data, block_averaged_sources, grid_sources
 from .synthetic_model import synthetic_model
 from .plot import plot_prediction
 from .latex_variables import (
-    latex_variables,
-    latex_parameters,
+    create_latex_variable,
+    create_loglist,
+    list_to_latex,
     format_variable_name,
-    latex_best_parameters,
 )
 from .utils import (
     combine_parameters,

### 2020-10-05 notebooks/source_layouts/latex_variables.py

@@ -4,65 +4,32 @@ Function to define LaTeX variables
 import numpy as np
 
 
-def latex_variables(variable, number, unit=None, fmt=None):
+def create_latex_variable(variable_name, value, unit=None, fmt="5g"):
     """
     Create string to define a new LaTeX variable
     """
+    variable_name = format_variable_name(variable_name)
     if fmt is not None:
-        number = "{number:>{fmt}}".format(number=number, fmt=fmt)
+        value = value_to_string(value, fmt)
     if unit:
-        tex_line = r"\newcommand{{\{variable}}}{{\SI{{{number}}}{{{unit}}}}}".format(
-            variable=variable, number=number, unit=unit
+        unit = format_unit(unit)
+        tex_string = (
+            r"\newcommand{{\{variable_name}}}{{\SI{{{value}}}{{{unit}}}}}".format(
+                variable_name=variable_name, value=value, unit=unit
+            )
         )
     else:
-        tex_line = r"\newcommand{{\{variable}}}{{{number}}}".format(
-            variable=variable, number=number
+        tex_string = r"\newcommand{{\{variable_name}}}{{{value}}}".format(
+            variable_name=variable_name, value=value
         )
-    return tex_line
+    return tex_string
 
 
-def latex_best_parameters(best_parameters, survey, layout, depth_type):
+def value_to_string(value, fmt):
     """
-    Create LaTeX variables for best parameters
+    Convert numerical value to string with a specific format
     """
-    tex_lines = []
-    for parameter, value in best_parameters.items():
-        if parameter in ("depth_type", "layout", "height", "metadata"):
-            continue
-        variable_name = format_variable_name(
-            "_".join(["best", survey, layout, depth_type, parameter])
-        )
-        if parameter == "damping":
-            value = r"\num{{e{:.0f}}}".format(np.log10(value))
-            fmt = None
-        elif parameter == "score":
-            fmt = ".3f"
-        else:
-            fmt = _determine_fmt(value)
-        tex_lines.append(latex_variables(variable_name, value, fmt=fmt))
-    return tex_lines
-
-
-def latex_parameters(parameters, survey):
-    """
-    Create list or ranges of parameters for each source distribution as LaTeX variables
-    """
-    tex_variables = []
-    for layout in parameters:
-        for depth_type in parameters[layout]:
-            for parameter in parameters[layout][depth_type]:
-                if parameter != "depth_type":
[…]

### 2020-10-08 manuscript/manuscript.tex
Refactor the repository to make it simpler (#55)
Ditch the eql_source_layouts package: remove MANIFEST.in, setup.py and
versioneer. Move all code inside the notebooks folder. All additional code
lives inside notebooks/source_layouts, including its test functions. Replace
os.path for pathlib. Add a new run target in the Makefile. Save
variables into JSON files and create a notebook to convert them all to LaTeX
variables. Prevent saving & loading the datasets in the same notebook. Remove
setup.cfg, move flake8 configuration to .flake8 and don't ignore F401
anymore. Add flake8-bugbear as a depend

@@
 % Import files with parameter values generated by notebooks
-\input{synthetic_model_surveys.tex}
-\input{parameters_ground_survey.tex}
-\input{parameters_airborne_survey.tex}
-\input{best_parameters_ground_survey.tex}
-\input{best_parameters_airborne_survey.tex}
-\input{source_layouts_schematics.tex}
+\newcommand{\Gal}{Gal}
+\input{synthetic-surveys.tex}
+\input{parameters-ground-survey.tex}
+\input{parameters-airborne-survey.tex}
+\input{best-parameters-ground-survey.tex}
+\input{best-parameters-airborne-survey.tex}
+\input{source-layouts-schematics.tex}
 
@@
     {\small $^{3}$Department of Earth, Ocean and Ecological Sciences, School of Environmental Sciences, University of Liverpool, UK} \\
-
 }
@@
                 & \GroundSourceBelowDataConstantDepthDepth
-                  \GroundSourceBelowDataConstantDepthDepthIncrement
                 & \BestGroundSourceBelowDataConstantDepthDepth
@@
                 & \GroundSourceBelowDataConstantDepthDamping
-                  \GroundSourceBelowDataConstantDepthDampingIncrement
                 & \BestGroundSourceBelowDataConstantDepthDamping
@@
                 & \GroundSourceBelowDataRelativeDepthDepth
-                  \GroundSourceBelowDataRelativeDepthDepthIncrement
                 & \BestGroundSourceBelowDataRelativeDepthDepth
@@
                 & \GroundSourceBelowDataRelativeDepthDamping
-                  \GroundSourceBelowDataRelativeDepthDampingIncrement
                 & \BestGroundSourceBelowDataRelativeDepthDamping
@@
                 & \GroundSourceBelowDataVariableDepthDepth
-                  \GroundSourceBelowDataVariableDepthDepthIncrement
                 & \BestGroundSourceBelowDataVariableDepthDepth
@@
                 & \GroundSourceBelowDataVariableDepthDepthFactor
-                  \GroundSourceBelowDataVariableDepthDepthFactorIncrement
                 & \BestGroundSourceBelowDataVariableDepthDepthFactor
@@
                 & \GroundSourceBelowDataVariableDepthKNearest
-                  \GroundSourceBelowDataVariableDepthKNearestIncrement
                 & \BestGroundSourceBelowDataVariableDepthKNearest
@@
                 & \GroundSourceBelowDataVariableDepthDamping
-                  \GroundSourceBelowDataVariableDepthDampingIncrement
                 & \BestGroundSourceBelowDataVariableDepthDamping
@@
                 & \GroundBlockAveragedSourcesConstantDepthDepth
-                  \GroundBlockAveragedSourcesConstantDepthDepthIncrement
                 & \BestGroundBlockAveragedSourcesConstantDepthDepth
@@
                 & \GroundBlockAveragedSourcesConstantDepthSpacing
-                  \GroundBlockAveragedSourcesConstantDepthSpacingIncrement
                 & \BestGroundBlockAveragedSourcesConstantDepthSpacing
@@
                 & \GroundBlockAveragedSourcesConstantDepthDamping
-                  \GroundBlockAveragedSourcesConstantDepthDampingIncrement
                 & \BestGroundBlockAveragedSourcesConstantDepthDamping
@@
                 & \GroundBlockAveragedSourcesRelativeDepthDepth
-                  \GroundBlockAveragedSourcesRelativeDepthDepthIncrement
                 & \BestGroundBlockAveragedSourcesRelativeDepthDepth
@@
                 & \GroundBlockAveragedSourcesRelativeDepthSpacing
-                  \GroundBlockAveragedSourcesRelativeDepthSpacingIncrement
                 & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
@@
                 & \GroundBlockAveragedSourcesRelativeDepthDamping
-                  \GroundBlockAveragedSourcesRelativeDepthDampingIncrement
                 & \BestGroundBlockAveragedSourcesRelativeDepthDamping
@@
                 & \GroundBlockAveragedSourcesVariableDepthDepth
-                  \GroundBlockAveragedSourcesVariableDepthDepthIncrement
                 & \BestGroundBlockAveragedSourcesVariableDepthDepth
@@
                 & \GroundBlockAveragedSourcesVariableDepthDepthFactor
-                  \GroundBlockAveragedSourcesVariableDepthDepthFactorIncrement
                 & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
@@
                 & \GroundBlockAveragedSourcesVariableDepthKNearest
-                  \GroundBlockAveragedSourcesVariableDepthKNearestIncrement
                 & \BestGroundBlockAveragedSourcesVariableDepthKNearest
@@
                 & \GroundBlockAveragedSourcesVariableDepthSpacing
-                  \GroundBlockAveragedSourcesVariableDepthSpacingIncrement
                 & \BestGroundBlockAveragedSourcesVariableDepthSpacing
@@
                 & \GroundBlockAveragedSourcesVariableDepthDamping
-                  \GroundBlockAveragedSourcesVariableDepthDampingIncrement
                 & \BestGroundBlockAveragedSourcesVariableDepthDamping
@@
                 & \GroundGridSourcesConstantDepthDepth
-                  \GroundGridSourcesConstantDepthDepthIncrement
                 & \BestGroundGridSourcesConstantDepthDepth
@@
                 & \GroundGridSourcesConstantDepthSpacing
-                  \GroundGridSourcesConstantDepthSpacingIncrement
                 & \BestGroundGridSourcesConstantDepthSpacing
@@
                 & \GroundGridSourcesConstantDepthDamping
-                  \GroundGridSourcesConstantDepthDampingIncrement
                 & \BestGroundGridSourcesConstantDepthDamping
@@
                 & \AirborneSourceBelowDataConstantDepthDepth
-                  \AirborneSourceBelowDataConstantDepthDepthIncrement
                 & \BestAirborneSourceBelowDataConstantDepthDepth
@@
                 & \AirborneSourceBelowDataConstantDepthDamping
-                  \AirborneSourceBelowDataConstantDepthDampingIncrement
                 & \BestAirborneSourceBelowDataConstantDepthDamping
@@
                 & \AirborneSourceBelowDataRelativeDepthDepth
-                  \AirborneSourceBelowDataRelativeDepthDepthIncrement
                 & \BestAirborneSourceBelowDataRelativeDepthDepth
@@
                 & \AirborneSourceBelowDataRelativeDepthDamping
-                  \AirborneSourceBelowDataRelativeDepthDampingIncrement
                 & \BestAirborneSourceBelowDataRelativeDepthDamping
@@
                 & \AirborneSourceBelowDataVariableDepthDepth
-                  \AirborneSourceBelowDataVariableDepthDepthIncrement
                 & \BestAirborneSourceBelowDataVariableDepthDepth
@@
                 & \AirborneSourceBelowDataVariableDepthDepthFactor
-                  \AirborneSourceBelowDataVariableDepthDepthFactorIncrement
                 & \BestAirborneSourceBelowDataVariableDepthDepthFactor
@@
                 & \AirborneSourceBelowDataVariableDepthKNearest
-                  \AirborneSourceBelowDataVariableDepthKNearestIncrement
                 & \BestAirborneSourceBelowDataVariableDepthKNearest
@@
                 & \AirborneSourceBelowDataVariableDepthDamping
-                  \AirborneSourceBelowDataVariableDepthDampingIncrement
                 & \BestAirborneSourceBelowDataVariableDepthDamping
@@
                 & \AirborneBlockAveragedSourcesConstantDepthDepth
-                  \AirborneBlockAveragedSourcesConstantDepthDepthIncrement
                 & \BestAirborneBlockAveragedSourcesConstantDepthDepth
@@
                 & \AirborneBlockAveragedSourcesConstantDepthSpacing
-                  \AirborneBlockAveragedSourcesConstantDepthSpacingIncrement
                 & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
@@
                 & \AirborneBlockAveragedSourcesConstantDepthDamping
-                  \AirborneBlockAveragedSourcesConstantDepthDampingIncrement
                 & \BestAirborneBlockAveragedSourcesConstantDepthDamping
@@
                 & \AirborneBlockAveragedSourcesRelativeDepthDepth
-                  \AirborneBlockAveragedSourcesRelativeDepthDepthIncrement
                 & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
@@
                 & \AirborneBlockAveragedSourcesRelativeDepthSpacing
-                  \AirborneBlockAveragedSourcesRelativeDepthSpacingIncrement
                 & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
@@
                 & \AirborneBlockAveragedSourcesRelativeDepthDamping
-                  \AirborneBlockAveragedSourcesRelativeDepthDampingIncrement
                 & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
@@
                 & \AirborneBlockAveragedSourcesVariableDepthDepth
-                  \AirborneBlockAveragedSourcesVariableDepthDepthIncrement
                 & \BestAirborneBlockAveragedSourcesVariableDepthDepth
@@
                 & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
-                  \AirborneBlockAveragedSourcesVariableDepthDepthFactorIncrement
                 & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
@@
                 & \AirborneBlockAveragedSourcesVariableDepthKNearest
-                  \AirborneBlockAveragedSourcesVariableDepthKNearestIncrement
                 & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
@@
                 & \AirborneBlockAveragedSourcesVariableDepthSpacing
-                  \AirborneBlockAveragedSourcesVariableDepthSpacingIncrement
                 & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
@@
                 & \AirborneBlockAveragedSourcesVariableDepthDamping
-                  \AirborneBlockAveragedSourcesVariableDepthDampingIncrement
                 & \BestAirborneBlockAveragedSourcesVariableDepthDamping
@@
                 & \AirborneGridSourcesConstantDepthDepth
-                  \AirborneGridSourcesConstantDepthDepthIncrement
                 & \BestAirborneGridSourcesConstantDepthDepth
@@
                 & \AirborneGridSourcesConstantDepthSpacing
-                  \AirborneGridSourcesConstantDepthSpacingIncrement
                 & \BestAirborneGridSourcesConstantDepthSpacing
@@
                 & \AirborneGridSourcesConstantDepthDamping
-                  \AirborneGridSourcesConstantDepthDampingIncrement
                 & \BestAirborneGridSourcesConstantDepthDamping

### 2020-10-08 notebooks/01-synthetic-surveys.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.5.0
+#       jupytext_version: 1.6.0
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -19,7 +19,8 @@
 
 # +
 from IPython.display import display
-import os
+from pathlib import Path
+import json
 import pyproj
 import numpy as np
 import xarray as xr
@@ -28,9 +29,8 @@ import harmonica as hm
 import matplotlib.pyplot as plt
 from matplotlib.collections import PatchCollection
 
-from eql_source_layouts import (
+from source_layouts import (
     synthetic_model,
-    latex_variables,
 )
 
 # -
@@ -39,9 +39,9 @@ from eql_source_layouts import (
 
 # +
 # Define results directories
-results_dir = os.path.join("..", "results")
-ground_results_dir = os.path.join(results_dir, "ground_survey")
-airborne_results_dir = os.path.join(results_dir, "airborne_survey")
+results_dir = Path("..") / "results"
+ground_results_dir = results_dir / "ground_survey"
+airborne_results_dir = results_dir / "airborne_survey"
 
 # Define a survey region of 1 x 1 degrees (~ 100km x 100km)
 region_degrees = (-0.5, 0.5, -0.5, 0.5)
@@ -65,12 +65,6 @@ np.random.seed(12345)
 target_grid_spacing = 2e3
 target_grid_height = 2000
 # -
-
-# **Initialize latex_lines list**
-#
-# On this list we will store all the variables we want to mention on the LaTeX manuscript.
-
-latex_lines = []
 
 # ## Synthetic model made out of prisms
 
@@ -97,36 +91,18 @@ ax.set_xlim(region[:2])
 ax.set_ylim(region[2:4])
 plt.show()
 
-# **Save model related quantities to LaTeX file**
+# **Save model related quantities on dictionary**
 
-# +
-assert model_region[5] == 0
+np.min(model["densities"])
 
-latex_lines.extend(
-    [
-        latex_variables("NPrisms", len(model["densities"])),
-        latex_variables(
-            "ModelEasting",
-            (model_region[1] - model_region[0]) * 1e-3,
-            r"\km",
-            fmt=".0f",
-        ),
-        latex_variables(
-            "ModelNorthing",
-            (model_region[1] - model_region[0]) * 1e-3,
[…]

### 2020-10-08 notebooks/02-source-layouts-schematics.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.4
+#       jupytext_version: 1.6.0
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -14,31 +14,30 @@
 # ---
 
 # +
-from IPython.display import display
-import os
-import pyproj
+from IPython.display import display  # noqa: F401  # ignore used but not imported
+import json
+from pathlib import Path
 import numpy as np
 import pandas as pd
 import verde as vd
-import harmonica as hm
 import matplotlib.pyplot as plt
 
-import eql_source_layouts
-from eql_source_layouts import latex_variables, format_variable_name
+import source_layouts
 
 # -
 
 # ## Define parameters for building the source distributions
 
 # Define results directory to read synthetic ground survey
-ground_results_dir = os.path.join("..", "results", "ground_survey")
+results_dir = Path("..") / "results"
+ground_results_dir = results_dir / "ground_survey"
 
 # ## Read synthetic ground survey
 #
 
 # Get coordinates of observation points from a synthetic ground survey
 
-survey = pd.read_csv(os.path.join(ground_results_dir, "survey.csv"))
+survey = pd.read_csv(ground_results_dir / "survey.csv")
 
 inside = np.logical_and(
     np.logical_and(
@@ -88,7 +87,7 @@ parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=grid_spacing
 
 source_distributions = {}
 for layout in parameters:
-    source_distributions[layout] = getattr(eql_source_layouts, layout)(
+    source_distributions[layout] = getattr(source_layouts, layout)(
         coordinates, **parameters[layout]
     )
 
@@ -107,7 +106,7 @@ for nodes in grid_lines:
 
 # +
 # Load matplotlib configuration
-plt.style.use(os.path.join("..", "matplotlib.rc"))
+plt.style.use(Path("..") / "matplotlib.rc")
 
 fig, axes = plt.subplots(nrows=1, ncols=4, sharey=True, figsize=(6.66, 1.65), dpi=300)
 size = 3
@@ -158,27 +157,22 @@ for y in grid_lines[1]:
 
 plt.tight_layout(w_pad=0)
 plt.savefig(
-    os.path.join("..", "manuscript", "figs", "source-layouts-schematics.pdf"), dpi=300
[…]

### 2020-10-08 notebooks/03-source-distributions.py

@@ -7,7 +7,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.5
+#       jupytext_version: 1.6.0
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -56,15 +56,14 @@
 
 # +
 from IPython.display import display
-import os
+from pathlib import Path
 import pyproj
 import numpy as np
 import pandas as pd
 import verde as vd
-import harmonica as hm
 import matplotlib.pyplot as plt
 
-import eql_source_layouts
+import source_layouts
 
 # -
 
@@ -72,8 +71,8 @@ import eql_source_layouts
 
 # +
 # Define results directory to read synthetic ground survey
-ground_results_dir = os.path.join("..", "results", "ground_survey")
-airborne_results_dir = os.path.join("..", "results", "airborne_survey")
+ground_results_dir = Path("..") / "results" / "ground_survey"
+airborne_results_dir = Path("..") / "results" / "airborne_survey"
 
 # Define dictionaries where the source distributions will be stored
 layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
@@ -149,7 +148,7 @@ parameters[layout][depth_type] = {
 
 # Get coordinates of observation points from a synthetic ground survey
 
-survey = pd.read_csv(os.path.join(ground_results_dir, "survey.csv"))
+survey = pd.read_csv(ground_results_dir / "survey.csv")
 
 # Plot the survey points
 
@@ -169,7 +168,7 @@ region = vd.get_region(coordinates)
 
 for layout in parameters:
     for depth_type in parameters[layout]:
-        source_distributions[layout][depth_type] = getattr(eql_source_layouts, layout)(
+        source_distributions[layout][depth_type] = getattr(source_layouts, layout)(
             coordinates, **parameters[layout][depth_type]
         )
 
@@ -234,7 +233,7 @@ plt.show()
 
 # Get coordinates of observation points from a synthetic airborne survey
 
-survey = pd.read_csv(os.path.join(airborne_results_dir, "survey.csv"))
+survey = pd.read_csv(airborne_results_dir / "survey.csv")
 
 # Project survey points into Cartesian coordinates
 
@@ -272,7 +271,7 @@ region = vd.get_region(coordinates)
 
 for layout in parameters:
     for depth_type in parameters[layout]:
[…]

### 2020-10-08 notebooks/04-depth-types-schematics.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.5
+#       jupytext_version: 1.6.0
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -19,18 +19,18 @@
 
 # +
 from IPython.display import display
-import os
+from pathlib import Path
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 
-from eql_source_layouts.layouts import source_below_data
+from source_layouts import source_below_data
 
 # -
 
 # Read a synthetic 1d survey
 
-survey = pd.read_csv(os.path.join("..", "data", "survey_1d.csv"))
+survey = pd.read_csv(Path("..") / "data" / "survey_1d.csv")
 display(survey)
 
 # ## Create source distributions
@@ -75,7 +75,7 @@ plt.scatter(points[depth_type][0], points[depth_type][2])
 plt.show()
 # +
 # Load matplotlib configuration
-plt.style.use(os.path.join("..", "matplotlib.rc"))
+plt.style.use(Path("..") / "matplotlib.rc")
 
 # Initialize figure and axes
 width = 6.66
@@ -88,7 +88,7 @@ titles = ["Constant Depth", "Relative Depth", "Variable Depth"]
 labels = "a b c".split()
 
 # Plot
-for i, (ax, depth_type, title, label) in enumerate(zip(axes, points, titles, labels)):
+for ax, depth_type, title, label in zip(axes, points, titles, labels):
     ax.scatter(coordinates[0], coordinates[2], s=size, label="stations", marker="^")
     ax.scatter(points[depth_type][0], points[depth_type][2], s=size, label="sources")
     ax.axhline(y=0, color="grey", linestyle="--", linewidth=0.5)
@@ -119,5 +119,5 @@ axes[0].legend(loc=(0.6, 0.32), borderpad=0.2, labelspacing=0.3)
 axes[0].set_ylim(-200, 130)
 
 plt.tight_layout(w_pad=0)
-plt.savefig(os.path.join("..", "manuscript", "figs", "depth_types.pdf"))
+plt.savefig(Path("..") / "manuscript" / "figs" / "depth_types.pdf")
 plt.show()

### 2020-10-08 notebooks/05-block-averaged-schematics.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.3.5
+#       jupytext_version: 1.6.0
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -18,12 +18,12 @@
 # Import packages
 
 # +
-import os
+from pathlib import Path
 import numpy as np
 import verde as vd
 import matplotlib.pyplot as plt
 
-from eql_source_layouts import block_averaged_sources
+from source_layouts import block_averaged_sources
 
 # -
 
@@ -65,7 +65,7 @@ for nodes in grid_lines:
 
 # +
 # Load matplotlib configuration
-plt.style.use(os.path.join("..", "matplotlib.rc"))
+plt.style.use(Path("..") / "matplotlib.rc")
 
 # Boundaries of the grid
 xmin, xmax, ymin, ymax = vd.get_region(coordinates)
@@ -144,6 +144,6 @@ for ax, label in zip(axes, labels):
 
 plt.tight_layout(w_pad=0)
 plt.savefig(
-    os.path.join("..", "manuscript", "figs", "block-averaged-sources-schematics.pdf")
+    Path("..") / "manuscript" / "figs" / "block-averaged-sources-schematics.pdf"
 )
 plt.show()

### 2020-10-08 notebooks/06-grid-ground-data.py

@@ -6,32 +6,31 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.5.0
+#       jupytext_version: 1.6.0
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
 #     name: conda-env-eql_source_layouts-py
 # ---
 
-# # Grid airborne survey data using different source distributions
+# # Grid ground survey data using different source distributions
 
 # **Import useful packages**
 
 # +
-import os
+from pathlib import Path
+import json
 import numpy as np
 import pandas as pd
 import xarray as xr
 import verde as vd
 import matplotlib.pyplot as plt
 
-from eql_source_layouts import (
+from source_layouts import (
     combine_parameters,
     plot_prediction,
     get_best_prediction,
     predictions_to_datasets,
-    latex_parameters,
-    latex_best_parameters,
 )
 
 # -
@@ -40,15 +39,16 @@ from eql_source_layouts import (
 #
 # Let's define all the parameters that will be used on this notebook in the following
 # cells. These control the results that will be obtain on the rest of the notebook. If
-# you want to change something (like the interpolation parameters), you can just do it here.
+# you want to change something (like the interpolation parameters), you can just do it
+# here.
 #
 # We will avoid hardcoding parameters outside of these few cells in order to facilitate
 # reproducibility and keep things more organized.
 
 # +
 # Define results directory
-results_dir = os.path.join("..", "results")
-airborne_results_dir = os.path.join(results_dir, "airborne_survey")
+results_dir = Path("..") / "results"
+ground_results_dir = results_dir / "ground_survey"
 
 # Define which field will be meassured
 field = "g_z"
@@ -59,27 +59,34 @@ field_units = "mGal"
 # Define a list of source layouts
 layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
-dampings = np.logspace(-4, 2, 7)
+dampings = np.logspace(-4, 2, 7).tolist()
 # Define depht values
-depths = np.arange(1e3, 18e3, 2e3)
+depths = np.arange(1e3, 18e3, 2e3).tolist()
 # Define parameters for the grid sources:
 #    spacing, depth and damping
[…]

### 2020-10-08 notebooks/07-grid-airborne-data.py

@@ -6,32 +6,31 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.5.0
+#       jupytext_version: 1.6.0
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
 #     name: conda-env-eql_source_layouts-py
 # ---
 
-# # Grid ground survey data using different source distributions
+# # Grid airborne survey data using different source distributions
 
 # **Import useful packages**
 
 # +
-import os
+from pathlib import Path
+import json
 import numpy as np
 import pandas as pd
 import xarray as xr
 import verde as vd
 import matplotlib.pyplot as plt
 
-from eql_source_layouts import (
+from source_layouts import (
     combine_parameters,
     plot_prediction,
     get_best_prediction,
     predictions_to_datasets,
-    latex_parameters,
-    latex_best_parameters,
 )
 
 # -
@@ -40,16 +39,15 @@ from eql_source_layouts import (
 #
 # Let's define all the parameters that will be used on this notebook in the following
 # cells. These control the results that will be obtain on the rest of the notebook. If
-# you want to change something (like the interpolation parameters), you can just do it
-# here.
+# you want to change something (like the interpolation parameters), you can just do it here.
 #
 # We will avoid hardcoding parameters outside of these few cells in order to facilitate
 # reproducibility and keep things more organized.
 
 # +
 # Define results directory
-results_dir = os.path.join("..", "results")
-ground_results_dir = os.path.join(results_dir, "ground_survey")
+results_dir = Path("..") / "results"
+airborne_results_dir = results_dir / "airborne_survey"
 
 # Define which field will be meassured
 field = "g_z"
@@ -60,34 +58,27 @@ field_units = "mGal"
 # Define a list of source layouts
 layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
 # Define dampings used on every fitting of the gridder
-dampings = np.logspace(-4, 2, 7)
+dampings = np.logspace(-4, 2, 7).tolist()
 # Define depht values
-depths = np.arange(1e3, 18e3, 2e3)
+depths = np.arange(1e3, 18e3, 2e3).tolist()
 # Define parameters for the grid sources:
 #    spacing, depth and damping
[…]

### 2020-10-08 notebooks/99-figures.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.5.0
+#       jupytext_version: 1.6.0
 #   kernelspec:
 #     display_name: Python [conda env:eql_source_layouts]
 #     language: python
@@ -15,8 +15,7 @@
 
 # # Generate manuscript figures
 
-import os
-import numpy as np
+from pathlib import Path
 import xarray as xr
 import pandas as pd
 import verde as vd
@@ -24,17 +23,17 @@ import matplotlib.pyplot as plt
 
 # ## Load matplotlib configuration
 
-plt.style.use(os.path.join("..", "matplotlib.rc"))
+plt.style.use(Path("..") / "matplotlib.rc")
 
 # ## Define results directory
 
-results_dir = os.path.join("..", "results")
-ground_results_dir = os.path.join(results_dir, "ground_survey")
-airborne_results_dir = os.path.join(results_dir, "airborne_survey")
+results_dir = Path("..") / "results"
+ground_results_dir = results_dir / "ground_survey"
+airborne_results_dir = results_dir / "airborne_survey"
 
 # ## Ground survey
 
-survey = pd.read_csv(os.path.join(ground_results_dir, "survey.csv"))
+survey = pd.read_csv(ground_results_dir / "survey.csv")
 
 # +
 # Define useful parameters
@@ -103,7 +102,7 @@ ax2.set_title("Observed gravity acceleration", pad=3)
 
 plt.tight_layout(h_pad=0.2)
 plt.savefig(
-    os.path.join("..", "manuscript", "figs", "ground-survey.pdf"),
+    Path("..") / "manuscript" / "figs" / "ground-survey.pdf",
     bbox_inches="tight",
     dpi=300,
 )
@@ -111,7 +110,7 @@ plt.savefig(
 
 # ## Airborne survey
 
-survey = pd.read_csv(os.path.join(airborne_results_dir, "survey.csv"))
+survey = pd.read_csv(airborne_results_dir / "survey.csv")
 
 # +
 # Define useful parameters
@@ -168,7 +167,7 @@ ax2.set_title("Observed gravity acceleration", pad=3)
 
 plt.tight_layout(h_pad=0.2)
 plt.savefig(
-    os.path.join("..", "manuscript", "figs", "airborne-survey.pdf"),
+    Path("..") / "manuscript" / "figs" / "airborne-survey.pdf",
[…]

### 2020-10-08 notebooks/source_layouts/__init__.py

@@ -1,14 +1,13 @@
 # pylint: disable=missing-docstring
 # Import functions/classes to make the public API
-from ._version import get_versions
 from .layouts import source_below_data, block_averaged_sources, grid_sources
 from .synthetic_model import synthetic_model
 from .plot import plot_prediction
 from .latex_variables import (
-    latex_variables,
-    latex_parameters,
+    create_latex_variable,
+    create_loglist,
+    list_to_latex,
     format_variable_name,
-    latex_best_parameters,
 )
 from .utils import (
     combine_parameters,
@@ -17,7 +16,3 @@ from .utils import (
     predictions_to_datasets,
 )
 from .eql_iterative import EQLIterative
-
-# Get the version number through versioneer
-__version__ = get_versions()["version"]
-del get_versions

### 2020-10-08 notebooks/source_layouts/latex_variables.py

@@ -1,0 +1,106 @@
+"""
+Function to define LaTeX variables
+"""
+import numpy as np
+
+
+def create_latex_variable(variable_name, value, unit=None, fmt="5g"):
+    """
+    Create string to define a new LaTeX variable
+    """
+    variable_name = format_variable_name(variable_name)
+    if fmt is not None:
+        value = value_to_string(value, fmt)
+    if unit:
+        unit = format_unit(unit)
+        tex_string = (
+            r"\newcommand{{\{variable_name}}}{{\SI{{{value}}}{{{unit}}}}}".format(
+                variable_name=variable_name, value=value, unit=unit
+            )
+        )
+    else:
+        tex_string = r"\newcommand{{\{variable_name}}}{{{value}}}".format(
+            variable_name=variable_name, value=value
+        )
+    return tex_string
+
+
+def value_to_string(value, fmt):
+    """
+    Convert numerical value to string with a specific format
+    """
+    return "{value:>{fmt}}".format(value=value, fmt=fmt).strip()
+
+
+def format_variable_name(name):
+    """
+    Format Python variable name to LaTeX variable name
+
+    Remove underscores and case the first letter of each word.
+    """
+    return name.replace("_", " ").title().replace(" ", "")
+
+
+def format_unit(unit):
+    """
+    Format unit string to work well with SIunits LaTeX packcage
+    """
+    return " ".join(["\\" + u for u in unit.strip().split()])
+
+
+def list_to_latex(values, max_list_items=4, fmt="5g"):
+    """
+    Generate a numrange or numlist from a list of values
+    """
+    # Convert list to np.array
+    values = np.array(values)
+    # Sort values
+    values.sort()
+    # Check if we must create a numrange or numlist
+    diffs = values[1:] - values[:-1]
+    if np.allclose(diffs, diffs[0]) and values.size > max_list_items:
+        return create_numrange(values, fmt)
+    else:
+        return create_numlist(values, fmt)
+
+
+def create_numrange(values, fmt):
+    """
+    Create a numrange out of a list of values
+
+    Intended to represent a linspace.
+    """
+    increment = value_to_string(values[1] - values[0], fmt=fmt)
+    vmin = value_to_string(values.min(), fmt=fmt)
+    vmax = value_to_string(values.max(), fmt=fmt)
+    numrange = r"\numrange{{{min}}}{{{max}}}".format(min=vmin, max=vmax)
[…]

### 2020-10-08 notebooks/source_layouts/synthetic_model.py

@@ -80,6 +80,10 @@ def synthetic_model(region):
     prisms += dike["prisms"]
     densities += dike["densities"]
 
+    # Convert prisms and densities to numpy arrays
+    prisms = np.array(prisms, dtype="float64")
+    densities = np.array(densities, dtype="float64")
+
     # Scale prisms to the passed region
     prisms = _scale_model(prisms, region)
     # Create a collection of Rectangle from the prisms

### 2020-10-08 notebooks/source_layouts/test_eql_iterative.py

@@ -7,8 +7,8 @@ import verde as vd
 import harmonica as hm
 from sklearn.metrics import mean_squared_error
 
-from ..eql_iterative import EQLIterative
-from .. import block_averaged_sources
+from .eql_iterative import EQLIterative
+from .layouts import block_averaged_sources
 
 
 def test_eql_iterative_single_window():

### 2020-10-08 notebooks/source_layouts/test_layouts.py

@@ -6,7 +6,7 @@ import numpy as np
 import numpy.testing as npt
 import verde as vd
 
-from ..layouts import (
+from .layouts import (
     constant_depth,
     relative_depth,
     variable_depth,

### 2020-10-29 manuscript/manuscript.tex
Start explaining iterative method on manuscript

@@
 \subsection{Equivalent sources implementation}
+\label{sec:eql-implementation}
 
@@
 
+\section{Iteratively fitting source coefficients}
+
+Reducing the number of sources helps, but it's not enough if we want to grid
+a very large dataset.
+Even if we can reduce the number of sources by one order of magnitude, having
+too many data points would still increase the size of the Jacobian matrix until
+the point of not being able to store it in memory.
+This problem was already faced by other authors.
+
+Here we propose an iterative algorithm for fitting the source coefficients
+using a gradient boosting \citep{friedman2002} strategy and overlapping moving
+windows.
+
+Following equation \ref{eq:linear-problem} lets assume we have $N$ measurements
+of a harmonic field on observations points $\{\mathbf{p}_i\}_{i=1}^{N}$ stored in
+the vector $\mathbf{d} = (d_1, d_2, \ldots, d_N)^T$. We have defined a set of
+$M$ point sources located on $\{\mathbf{q}_j\}_{j=1}^{M}$, whose coefficients
+$\mathbf{c} = (c_1, c_2, \ldots, c_M)^T$ must be fitted so they can minimize
+the misfit function defined on \ref{eq:misfit-unscaled}.
+
+By defining a set of $K$ overlapping windows we can simplify the linear problem:
+
+\begin{equation}
+    \mathbf{d}
+    = \mathbf{A} \mathbf{c}
+    = \mathbf{A} \left( \sum_{k=1}^K \mathbf{c}_k \right)
+    = \sum_{k=1}^K \mathbf{A} \mathbf{c}_k,
+\end{equation}
+
+\noindent where $\mathbf{c}_k$ are vectors full of zeros except those $m_k$
+elements corresponding to the sources $\mathbf{q}_j$ that fall inside the
+window $k$.
+
+By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
+independently and iteratively by defining a residue vector $\mathbf{r}_k$ that
+it's initialized with the observed data and updated on each iteration:
+
+\begin{equation}
+    \mathbf{r}_0 = \mathbf{d},
+\end{equation}
+
+\begin{equation}
+    \mathbf{r}_k = \mathbf{r}_{k-1} - \mathbf{A}\mathbf{c}_k.
+    \label{eq:residue}
+\end{equation}
+
+\noindent On each iteration the $\mathbf{c}_k$ vectors can be fitted so they
+minimize the misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \mathbf{d} - \mathbf{A}\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+Because the $\mathbf{c}_k$ vector has only $m_k$ non-zero elements, the linear
+system can be greatly simplified:
+
+\begin{equation}
+    \begin{split}
+        \mathbf{A}\mathbf{c}_k = &
+        \overbrace{
+            \begin{bmatrix}
+                a_{11} & a_{12} & a_{13} & \cdots & a_{1M} \\
+                a_{21} & a_{22} & a_{23} & \cdots & a_{2M} \\
+                a_{31} & a_{32} & a_{33} & \cdots & a_{3M} \\
+                \vdots  & \vdots  & \vdots  & \cdots & \vdots \\
+                a_{N1} & a_{N2} & a_{N3} & \cdots & a_{NM}
+            \end{bmatrix}
+        }^\text{$N \times M$ elements}
+        \cdot
+        \overbrace{
+            \begin{bmatrix}
+                0 \\
+                {c_k}_2 \\
+                0 \\
+                \vdots  \\
+                {c_k}_M \\
+            \end{bmatrix}
+        }^\text{$M$ elements}
+        = \\ = &
+        \underbrace{
+            \begin{bmatrix}
+                a_{12} & \cdots & a_{1M} \\
+                a_{22} & \cdots & a_{2M} \\
+                a_{32} & \cdots & a_{3M} \\
+                \vdots  & \cdots & \vdots \\
+                a_{N2} & \cdots & a_{NM}
+            \end{bmatrix}
+        }_\text{$N \times m_k$ elements}
+        \cdot
+        \underbrace{
+            \begin{bmatrix}
+                {c_k}_2 \\
+                \vdots  \\
+                {c_k}_M \\
+            \end{bmatrix}
+        }_\text{$m_k$ elements}
+        = \tilde{\mathbf{A}} \tilde{\mathbf{c}}_k
+        .
+    \end{split}
+\end{equation}
+
+By removing the columns of the $\mathbf{A}$ matrix that are not needed in the
+$k$-th iteration we greatly reduce the memory consumption to solve the linear
+problem. Nevertheless, if the number of observation points ($N$) is too large,
+the $\tilde{\mathbf{A}}$ matrix might be large enough for the available memory.
+
+One more simplification can be carried out by ignoring the effect of the $m_k$
+sources on the observation points that fall outside the $k$ window. This means
+that the coefficients $\mathbf{c}_k$ will be fitted only taking into account
+the data values on the $n_k$ observation points that fall inside the same
+$k$-th window.
+This allows to reduce the $\tilde{\mathbf{A}}$ matrix to a $\mathbf{B}$ matrix
+with $n_k \times m_k$ elements:
+
+\begin{equation}
+    \mathbf{B} \tilde{\mathbf{c}}_k
+    =
+    \underbrace{
+        \begin{bmatrix}
+            a_{32} & \cdots & a_{3M} \\
+            \vdots  & \cdots & \vdots \\
+            a_{N2} & \cdots & a_{NM}
+        \end{bmatrix}
+    }_\text{$n_k \times m_k$ elements}
+    \cdot
+    \underbrace{
+        \begin{bmatrix}
+            {c_k}_2 \\
+            \vdots  \\
+            {c_k}_M \\
+        \end{bmatrix}
+    }_\text{$m_k$ elements}
+    .
+\end{equation}
+
+These two simplifications help to greatly reduce the size of the linear
+problem, reducing it to:
+
+\begin{equation}
+    \mathbf{d}_k = \mathbf{B} \tilde{\mathbf{c}}_k,
+\end{equation}
+
+\noindent where $\mathbf{d}_k$ is a vector containing only the measured data
+values corresponding to the observation points that fall inside the $k$-th
+window.
+This linear problem can be solved using the same method described on Section
+\ref{sec:eql-implementation}, obtaining values for the $\mathbf{c}_k$
+coefficients and updating the residual through equation \ref{eq:residue}, i.e.
+taking into account the effect of the fitted coefficients on every observation
+point.
+Worth noting that for updating the residue there's no need of computing the
+entire Jacobian matrix.
+
+After passing through every $K$ window, the residue $r_K$ should be
+sufficiently small obtaining a set of source coefficients as the sum of the
+$\mathbf{c}_k$ vectors:
+
+\begin{equation}
+    \mathbf{c} = \sum_{k=1}^K \mathbf{c}_k
+\end{equation}
+
+Shuffle the windows.
+
+First we define a set of equivalent sources following one of the
+source distributions described on the previous sections, e.g. the block-reduced
+sources at variable depth. Secondly we define a set of overlapping moving
+windows that cover the entire area of the data. Then we start the iterative
+process: on each iteration we choose one window and select every data points
+and sources that fall inside it, compute the Jacobian elements corresponding to
+these subsets of data points and sources, fit the coefficients of the chosen
+sources and finally remove the effect of these sources from the entire data,
+obtaining a \emph{residue}. On the following iterations the same process is
+carried out, but now the coefficients are fitted using the residue instead of
+the original data.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Discussion}

### 2020-11-03 manuscript/manuscript.tex

@@
 \emph{target} grid.
-We then \emph{score} the prediction by computing the coefficient of
-determination (R$^2$ score) between the prediction and the true values of the
-\emph{target} grid.
+We then \emph{score} the prediction by computing the root mean square (RMS)
+between the prediction and the true values of the \emph{target} grid.
 Finally, we obtain the \emph{best prediction} for each source distribution as
-the one that achieves the highest score.
+the one that achieves the lowest RMS.
 See Figure~\ref{fig:flowchart} for a graphical illustration of this process.
@@
 that produces the best prediction for each source distribution and its
-corresponding R$^2$ score, for both ground and synthetic surveys, respectively.
+corresponding RMS score, for both ground and synthetic surveys, respectively.
 Figures~\ref{fig:ground-survey-differences}
@@
 produce accurate predictions, both for the ground and airborne survey.
-The R$^2$ scores don't show significant difference, so we can only conclude
+The RMS scores don't show significant difference, so we can only conclude
 that all the source distributions are able to produce comparable predictions.
@@
         that generates the best prediction for each source distribution and its
-        corresponding R$^2$ score.
+        corresponding RMS score (in mGal).
     }
@@
             & \textbf{Best}
-            & \textbf{R$^2$ score} \\
+            & \textbf{RMS (mGal)} \\
         \toprule
@@
                 & \multirow{2}{*}{
-                    \BestGroundSourceBelowDataConstantDepthScore
+                    \BestGroundSourceBelowDataConstantDepthRms
                   } \\
@@
                 & \multirow{2}{*}{
-                    \BestGroundSourceBelowDataRelativeDepthScore
+                    \BestGroundSourceBelowDataRelativeDepthRms
                   } \\
@@
                 & \multirow{4}{*}{
-                    \BestGroundSourceBelowDataVariableDepthScore
+                    \BestGroundSourceBelowDataVariableDepthRms
                   } \\
@@
                 & \multirow{3}{*}{
-                    \BestGroundBlockAveragedSourcesConstantDepthScore
+                    \BestGroundBlockAveragedSourcesConstantDepthRms
                   } \\
@@
                 & \multirow{3}{*}{
-                    \BestGroundBlockAveragedSourcesRelativeDepthScore
+                    \BestGroundBlockAveragedSourcesRelativeDepthRms
                   } \\
@@
                 & \multirow{5}{*}{
-                    \BestGroundBlockAveragedSourcesVariableDepthScore
+                    \BestGroundBlockAveragedSourcesVariableDepthRms
                   } \\
@@
                 & \multirow{4}{*}{
-                    \BestGroundGridSourcesConstantDepthScore
+                    \BestGroundGridSourcesConstantDepthRms
                   } \\
@@
         parameters that generates the best prediction for each source
-        distribution and its corresponding R$^2$ score.
+        distribution and its corresponding RMS score (in mGal).
     }
@@
                 & \multirow{2}{*}{
-                    \BestAirborneSourceBelowDataConstantDepthScore
+                    \BestAirborneSourceBelowDataConstantDepthRms
                   } \\
@@
                 & \multirow{2}{*}{
-                    \BestAirborneSourceBelowDataRelativeDepthScore
+                    \BestAirborneSourceBelowDataRelativeDepthRms
                   } \\
@@
                 & \multirow{4}{*}{
-                    \BestAirborneSourceBelowDataVariableDepthScore
+                    \BestAirborneSourceBelowDataVariableDepthRms
                   } \\
@@
                 & \multirow{3}{*}{
-                    \BestAirborneBlockAveragedSourcesConstantDepthScore
+                    \BestAirborneBlockAveragedSourcesConstantDepthRms
                   } \\
@@
                 & \multirow{3}{*}{
-                    \BestAirborneBlockAveragedSourcesRelativeDepthScore
+                    \BestAirborneBlockAveragedSourcesRelativeDepthRms
                   } \\
@@
                 & \multirow{5}{*}{
-                    \BestAirborneBlockAveragedSourcesVariableDepthScore
+                    \BestAirborneBlockAveragedSourcesVariableDepthRms
                   } \\
@@
                 & \multirow{4}{*}{
-                    \BestAirborneGridSourcesConstantDepthScore
+                    \BestAirborneGridSourcesConstantDepthRms
                   } \\

### 2020-11-03 manuscript/manuscript.tex
Move new section after "Source distributions"
Improve math and move section as a subsection of EQL technique

@@
 
+\subsection{Gradient boosted equivalent sources}
+
+Reducing the number of sources helps, but it's not enough if we want to grid
+a very large dataset.
+Even if we can reduce the number of sources by one order of magnitude, having
+too many data points would still increase the size of the Jacobian matrix until
+the point of not being able to store it in memory.
+This problem was already faced by other authors.
+
+Here we propose an iterative algorithm for fitting the source coefficients
+using a gradient boosting \citep{friedman2002} strategy and overlapping moving
+windows.
+
+Lets assume we have $N$ measurements of a harmonic field on observations points
+$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
+\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
+$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
+coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
+different sets of equivalent sources: we define $K$ overlapping windows of
+equal size that cover the whole observation area, and then we create one set of
+equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
+sources that fall inside the $k$-th window.
+The observed data should be equal to the superposition of the
+effect of every set of equivalent sources:
+
+\begin{equation}
+    \mathbf{d} = \sum_{k=1}^K \mathbf{A}_k \mathbf{c}_k,
+\end{equation}
+
+\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
+set of equivalent sources and $\mathbf{A}_k$ is the Jacobian matrix between
+those sources and every data point.
+
+By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
+iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
+with the observed data) is used to fit the $\mathbf{c}_k$
+coefficients and then updated by removing the effect of the same sources, as
+follows:
+
+\begin{equation}
+    \mathbf{r}_0 = \mathbf{d},
+\end{equation}
+
+\begin{equation}
+    \mathbf{r}_k = \mathbf{r}_{k-1} - \mathbf{A}_k\mathbf{c}_k.
+    \label{eq:residue}
+\end{equation}
+
+\noindent On each iteration the $\mathbf{c}_k$ vectors can be fitted so they
+minimize following misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \mathbf{r}_{k-1} - \mathbf{A}_k\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+\noindent following the same method described on Section
+\ref{sec:eql-implementation}.
+Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
+adjusting the size of the overlapping windows can help in reducing the computer
+memory needed to fit the source coefficients and ultimately to interpolate the
+observed data.
+
+Nevertheless, in case our observed data is too large that even the
+$\mathbf{A}_k$ matrices cannot be stored into memory, we can apply one more
+simplification on the fitting process: ignore the effect of any observation
+point outside the $k$-th window while fitting the sources that fall under the
+same window.
+
+Assuming that there are $N_k$ observation points that fall under the $k$-th
+window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
+misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
+only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
+observation points that fall under the $k$-th window, and
+$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between the observation points
+and sources that fall under the same window.
+Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
+elements, the computer memory needed for fitting the $\mathbf{c}_k$
+coefficients is greatly reduced.
+
+Once the $\mathbf{c}_k$ coefficients are fitted, equation \ref{eq:residue} is
+applied to update the residue, i.e. the effect of the sources belonging to the
+$k$-th window is computed on every observation point. Worth noting that while
+calculating the effect of the sources we don't need to pre-compute the entire
+Jacobian matrix: the effect of the sources on each observation point can be
+carried by a simple addition of terms, computing each Jacobian element at once
+when needed.
+
+Because the number of windows is fixed before starting the iteration process,
+its number of steps are also fixed to $K$. Moreover, the windows are randomly
+shuffled before starting the process to prevent that any particular
+sets of equivalent sources are prioritized over the rest.
+
+After all $\mathbf{c}_k$ coefficients vectors are fitted, we can predict the
+effect of every equivalent source on any point as follows:
+
+\begin{equation}
+    V(\mathbf{p}) =
+    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
+    \frac{{c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
+\end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Iteratively fitting source coefficients}
-
-Reducing the number of sources helps, but it's not enough if we want to grid
-a very large dataset.
-Even if we can reduce the number of sources by one order of magnitude, having
-too many data points would still increase the size of the Jacobian matrix until
-the point of not being able to store it in memory.
-This problem was already faced by other authors.
-
-Here we propose an iterative algorithm for fitting the source coefficients
-using a gradient boosting \citep{friedman2002} strategy and overlapping moving
-windows.
-
-Following equation \ref{eq:linear-problem} lets assume we have $N$ measurements
-of a harmonic field on observations points $\{\mathbf{p}_i\}_{i=1}^{N}$ stored in
-the vector $\mathbf{d} = (d_1, d_2, \ldots, d_N)^T$. We have defined a set of
-$M$ point sources located on $\{\mathbf{q}_j\}_{j=1}^{M}$, whose coefficients
-$\mathbf{c} = (c_1, c_2, \ldots, c_M)^T$ must be fitted so they can minimize
-the misfit function defined on \ref{eq:misfit-unscaled}.
-
-By defining a set of $K$ overlapping windows we can simplify the linear problem:
-
-\begin{equation}
-    \mathbf{d}
-    = \mathbf{A} \mathbf{c}
-    = \mathbf{A} \left( \sum_{k=1}^K \mathbf{c}_k \right)
-    = \sum_{k=1}^K \mathbf{A} \mathbf{c}_k,
-\end{equation}
-
-\noindent where $\mathbf{c}_k$ are vectors full of zeros except those $m_k$
-elements corresponding to the sources $\mathbf{q}_j$ that fall inside the
-window $k$.
-
-By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
-independently and iteratively by defining a residue vector $\mathbf{r}_k$ that
-it's initialized with the observed data and updated on each iteration:
-
-\begin{equation}
-    \mathbf{r}_0 = \mathbf{d},
-\end{equation}
-
-\begin{equation}
-    \mathbf{r}_k = \mathbf{r}_{k-1} - \mathbf{A}\mathbf{c}_k.
-    \label{eq:residue}
-\end{equation}
-
-\noindent On each iteration the $\mathbf{c}_k$ vectors can be fitted so they
-minimize the misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \mathbf{d} - \mathbf{A}\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-Because the $\mathbf{c}_k$ vector has only $m_k$ non-zero elements, the linear
-system can be greatly simplified:
-
-\begin{equation}
-    \begin{split}
-        \mathbf{A}\mathbf{c}_k = &
-        \overbrace{
-            \begin{bmatrix}
-                a_{11} & a_{12} & a_{13} & \cdots & a_{1M} \\
-                a_{21} & a_{22} & a_{23} & \cdots & a_{2M} \\
-                a_{31} & a_{32} & a_{33} & \cdots & a_{3M} \\
-                \vdots  & \vdots  & \vdots  & \cdots & \vdots \\
-                a_{N1} & a_{N2} & a_{N3} & \cdots & a_{NM}
-            \end{bmatrix}
-        }^\text{$N \times M$ elements}
-        \cdot
-        \overbrace{
-            \begin{bmatrix}
-                0 \\
-                {c_k}_2 \\
-                0 \\
-                \vdots  \\
-                {c_k}_M \\
-            \end{bmatrix}
-        }^\text{$M$ elements}
-        = \\ = &
-        \underbrace{
-            \begin{bmatrix}
-                a_{12} & \cdots & a_{1M} \\
-                a_{22} & \cdots & a_{2M} \\
-                a_{32} & \cdots & a_{3M} \\
-                \vdots  & \cdots & \vdots \\
-                a_{N2} & \cdots & a_{NM}
-            \end{bmatrix}
-        }_\text{$N \times m_k$ elements}
-        \cdot
-        \underbrace{
-            \begin{bmatrix}
-                {c_k}_2 \\
-                \vdots  \\
-                {c_k}_M \\
-            \end{bmatrix}
-        }_\text{$m_k$ elements}
-        = \tilde{\mathbf{A}} \tilde{\mathbf{c}}_k
-        .
-    \end{split}
-\end{equation}
-
-By removing the columns of the $\mathbf{A}$ matrix that are not needed in the
-$k$-th iteration we greatly reduce the memory consumption to solve the linear
-problem. Nevertheless, if the number of observation points ($N$) is too large,
-the $\tilde{\mathbf{A}}$ matrix might be large enough for the available memory.
-
-One more simplification can be carried out by ignoring the effect of the $m_k$
-sources on the observation points that fall outside the $k$ window. This means
-that the coefficients $\mathbf{c}_k$ will be fitted only taking into account
-the data values on the $n_k$ observation points that fall inside the same
-$k$-th window.
-This allows to reduce the $\tilde{\mathbf{A}}$ matrix to a $\mathbf{B}$ matrix
-with $n_k \times m_k$ elements:
-
-\begin{equation}
-    \mathbf{B} \tilde{\mathbf{c}}_k
-    =
-    \underbrace{
-        \begin{bmatrix}
-            a_{32} & \cdots & a_{3M} \\
-            \vdots  & \cdots & \vdots \\
-            a_{N2} & \cdots & a_{NM}
-        \end{bmatrix}
-    }_\text{$n_k \times m_k$ elements}
-    \cdot
-    \underbrace{
-        \begin{bmatrix}
-            {c_k}_2 \\
-            \vdots  \\
-            {c_k}_M \\
-        \end{bmatrix}
-    }_\text{$m_k$ elements}
-    .
-\end{equation}
-
-These two simplifications help to greatly reduce the size of the linear
-problem, reducing it to:
-
-\begin{equation}
-    \mathbf{d}_k = \mathbf{B} \tilde{\mathbf{c}}_k,
-\end{equation}
-
-\noindent where $\mathbf{d}_k$ is a vector containing only the measured data
-values corresponding to the observation points that fall inside the $k$-th
-window.
-This linear problem can be solved using the same method described on Section
-\ref{sec:eql-implementation}, obtaining values for the $\mathbf{c}_k$
-coefficients and updating the residual through equation \ref{eq:residue}, i.e.
-taking into account the effect of the fitted coefficients on every observation
-point.
-Worth noting that for updating the residue there's no need of computing the
-entire Jacobian matrix.
-
-After passing through every $K$ window, the residue $r_K$ should be
-sufficiently small obtaining a set of source coefficients as the sum of the
-$\mathbf{c}_k$ vectors:
-
-\begin{equation}
-    \mathbf{c} = \sum_{k=1}^K \mathbf{c}_k
-\end{equation}
-
-Shuffle the windows.
-
-First we define a set of equivalent sources following one of the
-source distributions described on the previous sections, e.g. the block-reduced
-sources at variable depth. Secondly we define a set of overlapping moving
-windows that cover the entire area of the data. Then we start the iterative
-process: on each iteration we choose one window and select every data points
-and sources that fall inside it, compute the Jacobian elements corresponding to
-these subsets of data points and sources, fit the coefficients of the chosen
-sources and finally remove the effect of these sources from the entire data,
-obtaining a \emph{residue}. On the following iterations the same process is
-carried out, but now the coefficients are fitted using the residue instead of
-the original data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Discussion}

### 2020-11-09 manuscript/manuscript.tex

@@
 \subsection{Equivalent sources implementation}
-\label{sec:eql-implementation}
 
@@
     \mathbf{c}_\text{est} = \mathbf{S}\inv \hat{\mathbf{c}}_\text{est}.
-\end{equation}
-
-\subsection{Gradient boosted equivalent sources}
-
-Reducing the number of sources helps, but it's not enough if we want to grid
-a very large dataset.
-Even if we can reduce the number of sources by one order of magnitude, having
-too many data points would still increase the size of the Jacobian matrix until
-the point of not being able to store it in memory.
-This problem was already faced by other authors.
-
-Here we propose an iterative algorithm for fitting the source coefficients
-using a gradient boosting \citep{friedman2002} strategy and overlapping moving
-windows.
-
-Lets assume we have $N$ measurements of a harmonic field on observations points
-$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
-\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
-$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
-coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
-different sets of equivalent sources: we define $K$ overlapping windows of
-equal size that cover the whole observation area, and then we create one set of
-equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
-sources that fall inside the $k$-th window.
-The observed data should be equal to the superposition of the
-effect of every set of equivalent sources:
-
-\begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \mathbf{A}_k \mathbf{c}_k,
-\end{equation}
-
-\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
-set of equivalent sources and $\mathbf{A}_k$ is the Jacobian matrix between
-those sources and every data point.
-
-By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
-iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
-with the observed data) is used to fit the $\mathbf{c}_k$
-coefficients and then updated by removing the effect of the same sources, as
-follows:
-
-\begin{equation}
-    \mathbf{r}_0 = \mathbf{d},
-\end{equation}
-
-\begin{equation}
-    \mathbf{r}_k = \mathbf{r}_{k-1} - \mathbf{A}_k\mathbf{c}_k.
-    \label{eq:residue}
-\end{equation}
-
-\noindent On each iteration the $\mathbf{c}_k$ vectors can be fitted so they
-minimize following misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \mathbf{r}_{k-1} - \mathbf{A}_k\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-\noindent following the same method described on Section
-\ref{sec:eql-implementation}.
-Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
-adjusting the size of the overlapping windows can help in reducing the computer
-memory needed to fit the source coefficients and ultimately to interpolate the
-observed data.
-
-Nevertheless, in case our observed data is too large that even the
-$\mathbf{A}_k$ matrices cannot be stored into memory, we can apply one more
-simplification on the fitting process: ignore the effect of any observation
-point outside the $k$-th window while fitting the sources that fall under the
-same window.
-
-Assuming that there are $N_k$ observation points that fall under the $k$-th
-window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
-misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
-only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
-observation points that fall under the $k$-th window, and
-$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between the observation points
-and sources that fall under the same window.
-Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
-elements, the computer memory needed for fitting the $\mathbf{c}_k$
-coefficients is greatly reduced.
-
-Once the $\mathbf{c}_k$ coefficients are fitted, equation \ref{eq:residue} is
-applied to update the residue, i.e. the effect of the sources belonging to the
-$k$-th window is computed on every observation point. Worth noting that while
-calculating the effect of the sources we don't need to pre-compute the entire
-Jacobian matrix: the effect of the sources on each observation point can be
-carried by a simple addition of terms, computing each Jacobian element at once
-when needed.
-
-Because the number of windows is fixed before starting the iteration process,
-its number of steps are also fixed to $K$. Moreover, the windows are randomly
-shuffled before starting the process to prevent that any particular
-sets of equivalent sources are prioritized over the rest.
-
-After all $\mathbf{c}_k$ coefficients vectors are fitted, we can predict the
-effect of every equivalent source on any point as follows:
-
-\begin{equation}
-    V(\mathbf{p}) =
-    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
-    \frac{{c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
 \end{equation}

### 2020-11-10 manuscript/manuscript.tex
Improve manuscript

@@
 
-\subsection{Generalization of equivalent sources}
+\subsection{Generalized equivalent sources}
 
@@
 
-Worth noting that solving equations~\ref{eq:linear-problem-g}
-and~\ref{eq:linear-problem} is equivalent to performing an inversion and thus
-solving an ill-posed problem by nature due to the non-uniqueness and the
-instability of the possible solutions.
+\subsection{Fitting source coefficients}
+\label{sec:eql-inversion}
+
+Solving equations~\ref{eq:linear-problem-g} and~\ref{eq:linear-problem} is
+equivalent to performing an inversion and thus solving an ill-posed problem by
+nature due to the non-uniqueness and the instability of the possible solutions.
 Therefore is usually needed to add regularization functions in order to obtain
@@
 (\citealp[p.~52]{menke1989}; \citealp{cooper2000}; \citealp{oliveira2013}).
-Worth noting that the number of sources can either be equal, greater or lower
-than the number of observation points, leading to well, under or overdetermined
-linear problem, respectively.
-
-% Add other possible applications to the EQL like RTP or upward continuation.
-
-\subsection{Equivalent sources implementation}
-
-The subsequent comparisons between strategies for interpolating data through
-equivalent sources are carried out by the equivalent sources implementation in
-Harmonica (v0.1.0) \citep{uieda2020}.
-
-It solves equation~\ref{eq:linear-problem} through least squares with
-a zeroth-order Tikhonov \citep{tikhonov1977} regularization in order to
-stabilize the solution.
-It consists in minimizing the misfit function:
+
+We can obtain the values of the source coefficients $\mathbf{c}$ that better
+reproduce the measured field by minimizing an objective or misfit function
+$\phi(\mathbf{c})$ through a least squares method:
 
@@
 Jacobian matrix elements.
-
-In order to simplify the choice of this parameter we scale the Jacobian matrix
-so each column has unit variance.
+The second term of the equation applies a zeroth-order Tikhonov
+\citep{tikhonov1977} regularization to stabilize the solution.
+
+In order to simplify the choice of the \emph{damping} parameter we scale the
+Jacobian matrix so each column has unit variance.
 We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
@@
 \begin{equation}
-    \hat{\mathbf{c}}_\text{est} =
+    \hat{\mathbf{c}} =
         \left[
@@
 \begin{equation}
-    \hat{\mathbf{c}}_\text{est} =
+    \hat{\mathbf{c}} =
     \hat{\mathbf{A}}^\text{T}
@@
 Once the scaled coefficients are obtained, the sources' coefficients
-$\mathbf{c}_\text{est}$ can be obtained by rescaling
-$\hat{\mathbf{c}}_\text{est}$:
-
-\begin{equation}
-    \mathbf{c}_\text{est} = \mathbf{S}\inv \hat{\mathbf{c}}_\text{est}.
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Source distributions}
-
-% Describe the proposed source distributions as combination of layouts and
-% depths strategies.
+$\mathbf{c}$ can be obtained by rescaling
+$\hat{\mathbf{c}}$:
+
+\begin{equation}
+    \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{c}}.
+\end{equation}
+
+\subsection{Source distributions}
 
@@
 distribution of sources will be generated.
-
-% Worth noting that the \emph{source below data} generates a number of sources
-% equal to the data points, obtaining a well determined linear problem.
-% The \emph{block averaged sources} layouts can generate a number of point
-% sources equal or lower than the number of data points, well or
-% overdetermined.
-% The \emph{grid sources} is the only layout that can generate either a well,
-% over or under determined problem.
 
@@
 The \emph{grid sources} is only compatible with the \emph{constant depth}
-scheme.
+scheme if no further information is provided.
 
@@
 \end{table*}
+
+\subsection{Gradient boosted equivalent sources}
+
+Reducing the number of sources might help to lower the amount of computer
+memory needed to fit their coefficients, although it may be not enough for
+a very large set of observation points.
+Even if we can greatly reduce the number of sources, having too many data
+points would still produce a Jacobian matrix large enough that cannot fit in
+memory.
+This problem was already faced by other authors (CITE PEOPLE).
+Here we propose an iterative algorithm for fitting the source coefficients
+using a gradient boosting \citep{friedman2001, friedman2002} strategy.
+
+Lets assume we have $N$ measurements of a harmonic field on observations points
+$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
+\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
+$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
+coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
+different sets of equivalent sources: we define $K$ overlapping windows of
+equal size that cover the whole observation area, and then we create one set of
+equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
+sources that fall inside the $k$-th window.
+The observed data should be equal to the superposition of the
+effect of every set of equivalent sources:
+
+\begin{equation}
+    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k,
+\end{equation}
+
+\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
+set of equivalent sources; $\mathbf{A}_k$ is the Jacobian matrix between
+those sources and every data point; and each $\alpha_k$ is a constant called
+\emph{step-size parameter}.
+
+By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
+iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
+with the observed data) is used to fit the $\mathbf{c}_k$
+coefficients and $\alpha_k$ step-size parameter, and then updated by removing
+the effect of the same sources, as follows:
+
+\begin{equation}
+    \mathbf{r}_0 = \mathbf{d},
+\end{equation}
+
+\begin{equation}
+    \mathbf{r}_k = \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k.
+    \label{eq:residue}
+\end{equation}
+
+\noindent On each iteration the $\mathbf{c}_k$ vector and the $\alpha_k$
+parameter can be fitted so they minimize the misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+\noindent following the same method described on Section
+\ref{sec:eql-inversion}.
+Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
+adjusting the size of the overlapping windows can help in reducing the computer
+memory needed to fit the source coefficients and ultimately to interpolate the
+observed data.
+Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
+matrices large enough that they cannot be stored in memory, we can apply one
+more simplification on the fitting process: ignore the effect of the sources on
+the $k$-th window on any observation point that falls outside it.
+
+Assuming that there are $N_k$ observation points that fall under the $k$-th
+window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
+misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
+only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
+observation points that fall under the $k$-th window; and
+$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between the observation points
+and sources that fall under the same window.
+Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
+elements, the computer memory needed for fitting the $\mathbf{c}_k$
+coefficients is greatly reduced.
+
+Once the $\mathbf{c}_k$ coefficients are fitted following the same method
+described on Section \ref{sec:eql-inversion}, , we need to obtain the value
+of the step-size parameter $\alpha_k$.
+This can be achieved by minimizing the norm of the difference between the
+previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th set of
+equivalent sources on every observation point:
+
+\begin{equation}
+    \alpha_k = \underset{\alpha}{\mathrm{argmin}}
+    \left(
+        \left\lVert
+            \mathbf{r}_{k-1} - \alpha \mathbf{A}_k \mathbf{c}_k
+        \right\rVert ^ 2
+    \right),
+\end{equation}
+
+\noindent which leads to:
+
+\begin{equation}
+    \alpha_k = \frac{
+        \mathbf{r}_{k-1}^T \mathbf{A}_k \mathbf{c}_k
+    }{
+        \left(\mathbf{A}_k \mathbf{c}_k\right)^T \mathbf{A}_k \mathbf{c}_k
+    }.
+\end{equation}
+
+This step will improve the convergence of the iterative algorithm and also will
+introduce at some extent the effect of the $k$-th sources on every data point,
+which was neglected on the fitting of the $\mathbf{c}_k$ coefficients.
+
+Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
+fitted, equation \ref{eq:residue} is applied to update the residue: compute the
+effect of the sources belonging to the $k$-th window on every observation
+point. Worth noting that when calculating the effect of any number of sources
+we don't need to pre-compute the entire Jacobian matrix: we can compute the
+effect of the sources on each observation point by a simple addition of terms,
+what means computing each Jacobian element at once when needed.
+
+Because the number of windows is fixed before starting the iteration process,
+its number of steps are also fixed to $K$. Moreover, the windows are randomly
+shuffled before starting the process to prevent the prioritization of clustered
+sets of equivalent sources.
+
+After all $\alpha_k$ parameters and $\mathbf{c}_k$ coefficients vectors are
+fitted, we can predict the effect of every equivalent source on any point as
+follows:
+
+\begin{equation}
+    V(\mathbf{p}) =
+    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
+    \frac{\alpha_k {c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
+\end{equation}
 
@@
 
-Our goal is to to compare the performance of all source distributions from
-Table~\ref{tab:source-distributions} when predicting harmonic field data using
-the equivalent layer technique.
+Our first goal is to to compare the performance of all source distributions
+from Table~\ref{tab:source-distributions} when predicting harmonic field data
+using the equivalent layer technique.
 To do so we have created a synthetic model made out of prisms of different

### 2020-11-10 manuscript/manuscript.tex
Specify gravity constant

@@
 
-\noindent where $z_i$ and $z_j$ are the vertical components of the
-$\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
+\noindent where
+$G = \SI{6.674e-11}{\cubic\meter\per\kilogram\per\second\squared}$ is the
+universal gravitational constant, $z_i$ and $z_j$ are the vertical components
+of the $\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
 

### 2020-11-10 manuscript/manuscript.tex
Minor improvements to manuscript

@@
 adjusting the size of the overlapping windows can help in reducing the computer
-memory needed to fit the source coefficients and ultimately to interpolate the
-observed data.
+memory needed to fit the source coefficients.
 Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
 matrices large enough that they cannot be stored in memory, we can apply one
-more simplification on the fitting process: ignore the effect of the sources on
-the $k$-th window on any observation point that falls outside it.
+more simplification on the fitting process: ignore the effect of the $k$-th
+sources on any observation point that falls outside the $k$-th window.
 
@@
 observation points that fall under the $k$-th window; and
-$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between the observation points
-and sources that fall under the same window.
+$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
+and the $k$-th sources.
 Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
@@
 Once the $\mathbf{c}_k$ coefficients are fitted following the same method
-described on Section \ref{sec:eql-inversion}, , we need to obtain the value
+described on Section \ref{sec:eql-inversion}, we need to obtain the value
 of the step-size parameter $\alpha_k$.
 This can be achieved by minimizing the norm of the difference between the
-previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th set of
-equivalent sources on every observation point:
+previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
+every observation point:
 
@@
 point. Worth noting that when calculating the effect of any number of sources
-we don't need to pre-compute the entire Jacobian matrix: we can compute the
+we don't need to pre-compute the entire Jacobian matrix: we can calculate the
 effect of the sources on each observation point by a simple addition of terms,

### 2020-11-18 manuscript/manuscript.tex
Continue edit manuscript

@@
 \newcommand{\Title}{
-    A better strategy for interpolating gravity and magnetic data
+    Gradient boosted equivalent sources
 }
@@
 in a computer program, limiting their wider adoption.
-
 In the present study,
-we propose a simple method for reducing the number of equivalent sources.
-The survey area is divided into horizontal blocks and one source is assigned
+we propose a two-way method for reducing the computational load needed to apply
+the equivalent sources technique: first by reducing the number of equivalent
+sources through a \emph{block-averaging} strategy and then simplifying the
+fitting process through a \emph{gradient boosting} algorithm.
+The first strategy consists in
+dividing the survey area into horizontal blocks and assign one source
 to each block at the median horizontal location of the data points.
@@
 interpolation.
-We experiment with the existing strategies of assigning sources at
-a uniform depth, a depth relative to the data height, or a depth proportional
-to the median distance to adjacent data points.
-Through tests on synthetic data, we show that non-uniform depths perform better
-at interpolation and that our method is able to achieve the same accuracy as a
-traditional equivalent layer while using a fraction of the number of sources.
+The second algorithm simplifies the process of fitting a very large number of
+equivalent sources by defining sets of fewer sources, whose coefficients are
+fitted iteratively while minimizing a given residue.
+Through tests on synthetic data, we show that: (i) the \emph{block-averaged}
+sources achieve the same accuracy as a traditional equivalent layer while using
+a fraction of the number of sources, and (ii) the \emph{gradient boosting}
+algorithm greatly reduces the computational memory required to fit very large
+datasets without scarifying predictions' accuracy.
+Finally these methods are used to interpolate a 1.7 million gravity data
+measurements around Australia onto a regular grid.
 
@@
 memory.
-This problem was already faced by other authors (CITE PEOPLE).
+This problem was already faced by other authors
+\citep{
+    mendonca1994,
+    leao1989,
+    li2010,
+    barnes2011,
+    oliveira2013,
+    siqueira2017,
+    jirigalatu2019
+}.
+The iterative method proposed by \citet{siqueira2017} needs equivalent sources
+to be located beneath each observation point, so it cannot take advantage of
+the block-averaged sources.
+\citet{leao1989} perform the fitting simultaneously with the prediction, what
+prevents us to use already fitted equivalent sources to make future
+predictions. Besides the method is limited to interpolations on regular grids.
+\citet{mendonca1994}
+\citet{li2010}
+\citet{barnes2011}
+\citet{jirigalatu2019}
+
 Here we propose an iterative algorithm for fitting the source coefficients
-using a gradient boosting \citep{friedman2001, friedman2002} strategy.
+using a gradient boosting \citep{friedman2001, friedman2002} strategy:
+(i) define a collection of overlapping windows of equal size that cover the
+survey area,
+(ii) define one set of equivalent sources per window,
+(iii) iteratively fit the coefficients of each set of sources.
+Once every set of sources is fitted, we can predict the value of the field on
+any observation point as the effect of every set of equivalent sources.
 
@@
 
-%Compare the accuracy of the predictions made by each source distribution.
-%Need an objective way to compare them.
-%Propose a synthetic gravity model made out of prisms of different sizes and
-%density contrasts.
-%Create a regular grid of observation points where the gravitational effect of
-%the synthetic model will be computed.
-%Call it the \emph{target grid}.
-%Generate synthetic surveys above the same synthetic model and compute the
-%gravitational effect of the model on each survey.
-%Use each source distribution to predict values based on the ones obtained on
-%each survey onto the same grid points of the \emph{target grid}.
-%Score each interpolation by comparing the predicted values with the
-%\emph{target grid}.
-%Finally compare the accuracy of the predictions made by each source
-%distribution.
-
 Our first goal is to to compare the performance of all source distributions
 from Table~\ref{tab:source-distributions} when predicting harmonic field data
-using the equivalent layer technique.
+using the equivalent sources technique.
 To do so we have created a synthetic model made out of prisms of different
@@
 The data from each synthetic survey is interpolated on the points of the
-\emph{target} grid and then scored against the \emph{target} grid.
+\emph{target} grid and then scored against its values.
 We can then quantitatively compare how accurate is each source distribution at
@@
 \ModelMaxDensity{}.
-We created deep big and thin shallow prisms for creating gravity anomalies with
+We built deep big and thin shallow prisms for creating gravity anomalies with
 long and short wavelengths, respectively.
@@
 \TargetSpacing{} located \TargetHeight{} above the zero height plane
-(Fig.~\ref{fig:target-grid}).
+(Fig.~\ref{fig:target-grid}), using \citet{nagy2000} and \citet{nagy2002}.
 We will refer to this grid as the \emph{target} grid in the future.

### 2020-11-26 manuscript/manuscript.tex
Add gradient boosting method to manuscript (#58)
Add description and mathematical background of gradient boosting method applied to equivalent sources.
Improve introduction to mention the new addition to the paper.
Fix minor issues, add a few more references, minor impovements.
Start adding boosting results to manuscript

@@
 This problem was already faced by other authors
-\citep{
-    mendonca1994,
-    leao1989,
-    li2010,
-    barnes2011,
-    oliveira2013,
-    siqueira2017,
-    jirigalatu2019
-}.
+\citep{mendonca1994, leao1989, li2010, barnes2011, oliveira2013, siqueira2017,
+jirigalatu2019}.
 The iterative method proposed by \citet{siqueira2017} needs equivalent sources
@@
 predictions. Besides the method is limited to interpolations on regular grids.
+% Add more discussion on why we won't apply any of the following methods
 \citet{mendonca1994}
@@
 the one that achieves the lowest RMS.
-See Figure~\ref{fig:flowchart} for a graphical illustration of this process.
 This process is carried out on both ground and airborne synthetic surveys.
+See Figure~\ref{fig:flowchart} for a graphical illustration of it.
 
@@
 that produces the best prediction for each source distribution and its
-corresponding RMS score, for both ground and synthetic surveys, respectively.
+corresponding RMS score, for both ground and airborne synthetic surveys,
+respectively.
 Figures~\ref{fig:ground-survey-differences}
@@
 target grid and the best prediction achieved by each source distribution, for
-both ground and synthetic surveys, respectively.
+both ground and airborne synthetic surveys, respectively.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
+\subsection{Discussion}
 
@@
 fit the sources coefficients and finally compute the actual prediction.
+
+The RMS doesn't seem to depend on the choice of the depth strategy used to
+locate the equivalent sources.
+At first glance, the choice of a depth strategy doesn't seem to impact the
+computational needs.
+Nevertheless, when trying to find the set of parameters that produce the most
+accurate predictions through a method like cross-validation, we need to fit the
+source coefficients one time per every possible combination of parameters.
+A depth strategy like the \emph{variable depth} needs a higher number of
+parameters (depth, depth factor, K nearest) than \emph{constant depth} or
+\emph{relative depth} (which takes only a depth parameter).
+The addition of these new parameters makes the search of the best set more
+computationally expensive: more parameters means increasing the dimensions of
+the parameters space and thus increasing the number of possible combinations.
+Therefore we would be more prone to choose a \emph{constant depth} or
+a \emph{relative depth} when dealing with very large datasets in order to save
+some computation time.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Performance of gradient boosted equivalent sources}
+
+Our second goal is to assess the accuracy of the predictions achieved by the
+gradient boosting algorithm while registering its performance by comparison
+with the more classical approach described on Section~\ref{sec:eql-inversion}.
+
+We applied the gradient boosted equivalent sources to interpolate the synthetic
+airborne survey on the same points of the target grid.
+We selected several window sizes to assess how accuracy and performance depend
+on that variable.
+For each window size we gridded the synthetic data with different sets of
+parameters. Then we compared each prediction to the target grid in order to get
+the best prediction for each window size.
+On every interpolation, block-averaged sources with relative depth are used
+with a spacing of PUT-BLOCK-SPACING-HERE.
 

### 2020-11-30 manuscript/manuscript.tex

@@
 
-\section{Performance of gradient boosted equivalent sources}
-
-Our second goal is to assess the accuracy of the predictions achieved by the
-gradient boosting algorithm while registering its performance by comparison
-with the more classical approach described on Section~\ref{sec:eql-inversion}.
-
-We applied the gradient boosted equivalent sources to interpolate the synthetic
-airborne survey on the same points of the target grid.
-We selected several window sizes to assess how accuracy and performance depend
-on that variable.
-For each window size we gridded the synthetic data with different sets of
-parameters. Then we compared each prediction to the target grid in order to get
-the best prediction for each window size.
-On every interpolation, block-averaged sources with relative depth are used
-with a spacing of PUT-BLOCK-SPACING-HERE.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusions}

### 2020-11-30 manuscript/manuscript.tex
Continue writing manuscript

--- 2020-11-26 manuscript/manuscript.tex
@@
 gradient boosting algorithm while registering its performance by comparison
-with the more classical approach described on Section~\ref{sec:eql-inversion}.
+with the non-boosted equivalent sources.
 
@@
 On every interpolation, block-averaged sources with relative depth are used
-with a spacing of PUT-BLOCK-SPACING-HERE.
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}, and an
+overlap of 50\% between adjacent windows.
+
+Using the best set of parameters for each window size, we registered the
+achieved RMS against the values of the target grid and the time needed to fit
+the sources coefficients.
+
+Compare RMS with the one achieved by the best prediction carried out by the
+non-boosted equivalent sources with block-averaged sources (see
+Table~\ref{tab:parameters-airborne-survey}).
+Calculated the fitting time relative to the time needed by non-boosted
+equivalent sources.
+
+\subsection{Overlapping}
+
+Another factor that plays an important role on the accuracy of the predictions
+and impacts the computation time needed to fit the source coefficients is the
+amount of overlap between adjacent windows.
+The previous choice of 50\% showed to be sufficiently good to achieve
+acceptable accuracy, although a deeper study should be carried out to assess
+how the amount of overlap impacts both accuracy and fitting time.
+
+We interpolated the synthetic airborne survey using the gradient boosted
+equivalent sources on the same points of the target grid.
+The interpolations were carried out using different amount of overlap, from
+0\% to 0.95\% with a step size of 0.05\%.
+For each overlap, we gridded the synthetic data with different sets of
+parameters, fixing the window size to INSERT-WINDOW-SIZE and using
+block-averaged sources with relative depth and a spacing of
+\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}.
+We registered the RMS achieved by the best prediction for each overlap and the
+computation time needed to fit the source coefficients.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Gridding Australia gravity data}
 

### 2020-11-30 manuscript/manuscript.tex
Continue writing manuscript

@@
 
+\subsection{Window size}
+
+One factor that plays an important role on the gradient boosted equivalent
+layers is the size of the overlapping windows used to create each set of
+equivalent sources.
+Smaller windows will reduce the amount of computer memory needed to fit the
+source coefficients: smaller windows will reduce the size of Jacobian matrices
+$\tilde{\mathbf{A}_k}$.
+Nevertheless, the usage of smaller windows may produce less accurate
+predictions: the equivalent sources cannot achieve the global minimum of the
+misfit $\varphi(\mathbf{c})$ of equation~\ref{eq:misfit-unscaled}.
+Moreover, the size of the overlapping windows might also impact on the
+computation time needed to fit the source coefficients: smaller windows will
+generate simpler least-square problems which are easier to solve, but they will
+also create more iterations.
+
+We want to assess how the size of the overlapping windows impacts both the
+accuracy of the predictions and the computation time needed to fit the source
+coefficients in comparison with the performance of the non-boosted equivalent
+sources.
+
 We applied the gradient boosted equivalent sources to interpolate the synthetic

### 2020-11-30 notebooks/06-grid-ground-data.py
Rerun all notebooks with dev version of Verde

@@ -67,7 +67,7 @@ depths = np.arange(1e3, 18e3, 2e3)
 # Define parameters for the grid sources:
 #    spacing, depth and damping
 grid_sources_spacings = np.arange(1e3, 5e3, 1e3)
-grid_sources_depths = np.arange(3e3, 15e3, 2e3)
+grid_sources_depths = np.arange(1e3, 11e3, 2e3)
 grid_sources_dampings = np.logspace(1, 4, 4)
 # Define parameters for variable relative depth layouts:
 #    depth_factor, depth and k_nearest

### 2020-12-09 manuscript/manuscript.tex
Shorten and summarize basic EQL theory in methods
I was a bit unsure about the explanations for the theory behind the
equivalent layer that we were presenting. It felt a bit too short with
some important parts missing about the upward continuation equation and
Green's identities. But at the same time it was feeling too long for a
paper (considering we already have to explain the gradient boosting
scheme). So I figured it might be good to cheat and start from the
Cordell 1992 and skip the deductions of why we can use 1/r. That's been
done in books and we have the citation for Cordell so we don'

--- 2020-11-30 manuscript/manuscript.tex
@@
 \documentclass[twocolumn]{article}
-\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
+%\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
 \setlength{\columnsep}{2\columnsep}
@@
 in a computer program, limiting their wider adoption.
+
 In the present study,
@@
 
-\section{The equivalent sources technique}
-
-The Green's equivalent layer theorem states that any harmonic potential field
-generated by any three dimensional physical-property distribution can by
-reproduced by a continuous two dimensional surface distribution.
-This introduces an ambiguity on the distribution that generates
-a potential field: multiple physical-property distributions can generate the
-same potential field.
-This represents an obstacle for determining the true shape and
-physical-property distribution that generates any measured potential field.
-Nevertheless this ambiguity can also be exploited for developing pre-processing
-techniques like interpolating potential field data.
-
-Approximating the continuous distribution by a finite and discrete density
-distribution is the basis of the \emph{equivalent sources technique}
-\citep{dampney1969}.
-The most common approach is to make use of a set of point sources (the
-\emph{equivalent sources}) located beneath the observation points.
-
-A classical approach for applying the equivalent sources technique would be to
-propose a set of point sources that generate the same harmonic field that has
-been measured.
-Lets consider a set of gravity acceleration measurements $g_z$ on points
-$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$ and a set of point sources with mass
-$\{m_1, \ldots, m_M\}$ located on points
-$\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$.
-The point sources must generate the same gravity field as the one measured:
-
-\begin{equation}
-    g_z(\mathbf{p}) = \mathbf{A} \mathbf{m},
-    \label{eq:linear-problem-g}
-\end{equation}
-
-\noindent where $g_z(\mathbf{p})$ is the vector containing the measured
-field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
-masses of the point sources and $\mathbf{A}$ a matrix whose
-elements can be obtained as the vertical component of the gravitational
-acceleration measured on $\mathbf{p}$ due to the point mass on $\mathbf{q}$:
-
-\begin{equation}
-    a_{ij} = G \frac{(z_i - z_j)}{|\mathbf{p}_i - \mathbf{q}_j|^3},
-\end{equation}
-
-\noindent where
-$G = \SI{6.674e-11}{\cubic\meter\per\kilogram\per\second\squared}$ is the
-universal gravitational constant, $z_i$ and $z_j$ are the vertical components
-of the $\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
-
-By solving equation~\ref{eq:linear-problem-g} we can obtain the values of
-$\mathbf{m}$ that better reproduce the measured field.
-This source distribution along with the fitted masses can be used to predict
-gravity values on any point where the potential field has not been measured.
-
-\subsection{Generalized equivalent sources}
-
-It's possible to generalize the equivalent sources technique to any harmonic
-field through a Green's function problem, regardless the nature of the field.
-
-By definition, any harmonic field $V$ must satisfy the Laplace's equation:
-
-\begin{equation}
-    \nabla^2 V = 0.
-\end{equation}
-
-Considering as boundary condition that $V$ is equal to zero at infinity, then
-its fundamental solution $\psi$ (also known as Green's function or radial basis
-function) must satisfy \citep[p.~210]{vladimirov1979}:
-
-\begin{equation}
-    \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
-        - 4\pi \delta(\mathbf{p}, \mathbf{q}),
-\end{equation}
-
-\noindent where $\delta(\mathbf{p}, \mathbf{q})$ is the Dirac's delta function
-and $\nabla_\mathbf{p}$ symbolize the Nabla operator applied on the coordinates
-$\mathbf{p}$.
-
-The fundamental solution of any harmonic field can be obtained as follows
-\citep[p.~37]{blakely1995}:
-
-\begin{equation}
-    \psi(\mathbf{p}, \mathbf{q})
+\section{Methodology}
+
+\subsection{The equivalent sources technique}
+
+Here, we will follow the ``generalized equivalent sources'' of
+\citet{cordell1992} and assume that any harmonic function $d(\mathbf{p})$ can
+be approximated by a sum of $M$ discrete point source effects
+
+\begin{equation}
+    d(\mathbf{p})
     =
-    \int
-    \frac{\delta(\mathbf{p}, \mathbf{q})}{|\mathbf{p} - \mathbf{q}|}
-    \textrm{d}v
+    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p} - \mathbf{q}_j
+    \right\rVert} \ ,
+    \label{eq:eql-forward}
+\end{equation}
+
+\noindent in which
+$\mathbf{p}$ and $\mathbf{q}_j$ are position vectors in a 3D Cartesian space,
+$c_j$ is a scalar coefficient related to the point source located at
+$\mathbf{q}_j$,
+and $\lVert \cdot \rVert$ is the vector norm.
+
+In case we have measured the value of the harmonic field on $N$ points
+$\{\mathbf{p}_1\ \mathbf{p}_2\ \ldots\ \mathbf{p}_N\}$,
+we can write a set of $N$ equations of the form
+
+\begin{equation}
+    d_i
     =
-    \frac{1}{|\mathbf{p} - \mathbf{q}|}.
-\end{equation}
-
-This shows that the Green's function associated with any harmonic field is
-equal to the inverse of the Euclidean distance between the evaluation and the
-source points.
-Thus any harmonic field $V$ can be expressed as \citep[p.~37]{blakely1995}:
-
-\begin{equation}
-    V(\mathbf{p})
-    =
-    \int \psi(\mathbf{p}, \mathbf{q}) \rho(\mathbf{q}) d\mathbf{q}
-    =
-    \int \frac{\rho(\mathbf{q})}{|\mathbf{p} - \mathbf{q}|}  d\mathbf{q},
-\end{equation}
-
-\noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
-physical-property evaluated on the point $\mathbf{q}$. Following
-\citet{dampney1969}, this density distribution can be approximated by a finite
-and discrete set of point sources located on $\{\mathbf{q}_1, \ldots,
-\mathbf{q}_M\}$:
-
-\begin{equation}
-    \rho(\mathbf{q}) =
-        \sum\limits_{j=1}^{M} c_j \delta(\mathbf{q} - \mathbf{q_j}),
-\end{equation}
-
-\noindent where $c_j$ is a coefficient related to the point source located on
-$\mathbf{q}_j$, with the same units as the physical-property.
-Then the harmonic field $V$ can be approximated by:
-
-\begin{equation}
-    V(\mathbf{p})
-    =
-    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
-    \label{eq:eql-field}
-\end{equation}
-
-In case we have measured the value of the harmonic field on points
-$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$, we can adjust the values of the $c$
-coefficients so they satisfy:
-
-\begin{equation}
-    V(\mathbf{p}_i)
-    =
-    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p}_i - \mathbf{q}_j|}
-    \quad \forall i=1,\ldots,N.
-\end{equation}
-
-This system of linear equations can be written in an more algebraic way:
-
-\begin{equation}
-    \mathbf{d} = \mathbf{A} \mathbf{c}
+    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p}_i - \mathbf{q}_j
+    \right\rVert}
+    \quad \forall i=1,2,\ldots,N
+    \ ,
+\end{equation}
+
+\noindent which can also be expressed as the following matrix equation
+
+\begin{equation}
+    \mathbf{d} = \mathbf{A} \mathbf{c} \ ,
     \label{eq:linear-problem}
@@
 
-\noindent where $\mathbf{d}$ is a vertical vector containing the measured
-values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
-containing the $c$ coefficients and $\mathbf{A}$ is the \emph{Jacobian matrix},
-whose elements are defined as the Green's function evaluated on each pair of
-points $\mathbf{p}$ and $\mathbf{q}$:
-
-\begin{equation}
-    a_{ij}
-    =
-    \psi(\mathbf{p}_i, \mathbf{q}_j)
-    =
-    \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|}
-\end{equation}
-
-By solving equation~\ref{eq:linear-problem} we can obtain the values of
-$\mathbf{c}$ that better reproduce the measured field.
-Then they can be used to predict the value of the harmonic field on any other
-point where no measurement has been taken by evaluating
-equation~\ref{eq:eql-field}.
+\noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
+values of the field $d_i$ on the observation points $\mathbf{p}_i$,
+$\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,
+and $\mathbf{A}$ is the $N \times M$ Jacobian matrix,
+whose elements are
+
+\begin{equation}
+    a_{ij} = \frac{1}{\left\lVert\mathbf{p}_i - \mathbf{q}_j\right\rVert}
+\end{equation}
+
+For a given set of $N$ observed field values $\mathbf{d}^o$,
+we can find a least-squares solution to
+equation~\ref{eq:linear-problem} and obtain the values of
+$\mathbf{c}$ that best fit the observations.
+These values can, in turn, be used to predict the value of the harmonic field
+at any other point outside of the sources by evaluating
+equation~\ref{eq:eql-forward}.
+Griding and upward continuation can thus be achieved by predicting values on
+points that fall on a regular grid or at different heights.
 

### 2020-12-09 manuscript/manuscript.tex
Start a revision of the inversion section
Make some tweaks to the notation, including using B and m instead of Â
and ĉ since ^ is often used to denote an estimate. Removed some of the
^2 from the lambdas in the least-squares solutions. Removed the part
about Cholesky decomposition because that is used to solve the linear
system, not minimize the goal function (and not always, it depends on
what sklearn does). Added an ^o to the data in the equations to
distinguish between predicted and observed data.

--- 2020-11-30 manuscript/manuscript.tex
@@
 
-\subsection{Fitting source coefficients}
+\subsection{Damped least-squares solution}
 \label{sec:eql-inversion}
 
-Solving equations~\ref{eq:linear-problem-g} and~\ref{eq:linear-problem} is
-equivalent to performing an inversion and thus solving an ill-posed problem by
-nature due to the non-uniqueness and the instability of the possible solutions.
-Therefore is usually needed to add regularization functions in order to obtain
-stable solutions
-(\citealp[p.~52]{menke1989}; \citealp{cooper2000}; \citealp{oliveira2013}).
-
-We can obtain the values of the source coefficients $\mathbf{c}$ that better
-reproduce the measured field by minimizing an objective or misfit function
-$\phi(\mathbf{c})$ through a least squares method:
+We can obtain the values of the source coefficients $\mathbf{c}$ that best
+fit the observed field values $\mathbf{d}^o$ by minimizing the goal function
 
@@
         \left\lVert
-            \mathbf{d} - \mathbf{A}\mathbf{c}
+            \mathbf{d}^o - \mathbf{A}\mathbf{c}
         \right\rVert ^ 2
@@
 
-\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
-and $\lambda_d$ is a \emph{damping} parameter with the same units as the
+\noindent where $\left\lVert \cdot \right\rVert$ symbolizes the L$_2$ norm and
+$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
 Jacobian matrix elements.
-The second term of the equation applies a zeroth-order Tikhonov
-\citep{tikhonov1977} regularization to stabilize the solution.
-
-In order to simplify the choice of the \emph{damping} parameter we scale the
-Jacobian matrix so each column has unit variance.
+The second term on the right-hand side of the equation is a zeroth-order
+Tikhonov regularization \citep{tikhonov1977} (also known as a damping
+regularization or ridge regression) that is used to stabilize the solution.
+
+The range of acceptable values for the damping parameter $\lambda_d$ will
+depend on the values of the Jacobian matrix $\mathbf{A}$ and the coefficients.
+Consequently, this range will vary (often dramatically) between datasets,
+making it difficult to choose an appropriate value for $\lambda_d$ in practice.
+
+To solve this issue, we first scale the Jacobian matrix so that its elements
+are unitless and each column has unit variance.
 We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
-standard deviation of each column of the Jacobian matrix $\mathbf{A}$:
+standard deviation of each column of $\mathbf{A}$:
 
@@
     \end{bmatrix}
-    ,
-\end{equation}
-
-\noindent so equation~\ref{eq:linear-problem} can be written as:
+    .
+\end{equation}
+
+We then write the forward problem in equation~\ref{eq:linear-problem} as
 
@@
     =
-    \hat{\mathbf{A}} \hat{\mathbf{c}}
-\end{equation}
-
-\noindent where $\hat{\mathbf{A}}$ is the scaled Jacobian matrix and
-$\hat{\mathbf{c}}$ is a vector containing scaled coefficients.
-
-The misfit function defined on equation~\ref{eq:misfit-unscaled} can be then
-rewritten as follows:
-
-\begin{equation}
-    \phi(\hat{\mathbf{c}}) =
-        \left\lVert \mathbf{d}
-        - \hat{\mathbf{A}}\hat{\mathbf{c}} \right\rVert ^ 2
-        + \lambda \left\lVert \hat{\mathbf{c}} \right\rVert ^2,
+    \mathbf{B} \mathbf{m}
+\end{equation}
+
+\noindent where $\mathbf{B}$ is the scaled and unitless Jacobian matrix and
+$\mathbf{m}$ is a vector containing scaled coefficients with the same units as
+the data.
+
+The misfit function defined on equation~\ref{eq:misfit-unscaled} can be
+rewritten as
+
+\begin{equation}
+    \phi(\mathbf{m}) =
+        \left\lVert \mathbf{d}^o
+        - \mathbf{B}\mathbf{m} \right\rVert ^ 2
+        + \lambda \left\lVert \mathbf{m} \right\rVert ^2,
     \label{eq:misfit}
@@
 
-\noindent where now $\lambda$ is a \emph{dimensionless} damping parameter.
-
-Misfit function from equation~\ref{eq:misfit} is minimized through Cholesky
-decomposition.
+\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
+regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
+$\mathbf{c}$.
+
 If the number of observation points is equal or larger to the number of
@@
 \begin{equation}
-    \hat{\mathbf{c}} =
+    \hat{\mathbf{m}} =
         \left[
-            \hat{\mathbf{A}}^\text{T} \hat{\mathbf{A}}
-            + \lambda^2 \mathbf{I}
+            \mathbf{B}^\text{T} \mathbf{B}
+            + \lambda \mathbf{I}
         \right]\inv
-        \hat{\mathbf{A}}^\text{T}
-        \mathbf{d}.
+        \mathbf{B}^\text{T}
+        \mathbf{d}^o.
 \end{equation}
@@
 \begin{equation}
-    \hat{\mathbf{c}} =
-    \hat{\mathbf{A}}^\text{T}
+    \hat{\mathbf{m}} =
+    \mathbf{B}^\text{T}
         \left[
-            \hat{\mathbf{A}} \hat{\mathbf{A}}^\text{T}
-            + \lambda^2 \mathbf{I}
+            \mathbf{B} \mathbf{B}^\text{T}
+            + \lambda \mathbf{I}
         \right]\inv
-        \mathbf{d}.
-\end{equation}
-
-Once the scaled coefficients are obtained, the sources' coefficients
-$\mathbf{c}$ can be obtained by rescaling
-$\hat{\mathbf{c}}$:
-
-\begin{equation}
-    \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{c}}.
+        \mathbf{d}^o.
+\end{equation}
+
+Once the scaled coefficients are obtained, the coefficients
+$\mathbf{c}$ can be obtained by
+
+\begin{equation}
+    \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{m}}.
 \end{equation}
@@
 
-\section{Performance of gradient boosted equivalent sources}
-
-Our second goal is to assess the accuracy of the predictions achieved by the
-gradient boosting algorithm while registering its performance by comparison
-with the non-boosted equivalent sources.
-
-We applied the gradient boosted equivalent sources to interpolate the synthetic
-airborne survey on the same points of the target grid.
-We selected several window sizes to assess how accuracy and performance depend
-on that variable.
-For each window size we gridded the synthetic data with different sets of
-parameters. Then we compared each prediction to the target grid in order to get
-the best prediction for each window size.
-On every interpolation, block-averaged sources with relative depth are used
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}, and an
-overlap of 50\% between adjacent windows.
-
-Using the best set of parameters for each window size, we registered the
-achieved RMS against the values of the target grid and the time needed to fit
-the sources coefficients.
-
-Compare RMS with the one achieved by the best prediction carried out by the
-non-boosted equivalent sources with block-averaged sources (see
-Table~\ref{tab:parameters-airborne-survey}).
-Calculated the fitting time relative to the time needed by non-boosted
-equivalent sources.
-
-\subsection{Overlapping}
-
-Another factor that plays an important role on the accuracy of the predictions
-and impacts the computation time needed to fit the source coefficients is the
-amount of overlap between adjacent windows.
-The previous choice of 50\% showed to be sufficiently good to achieve
-acceptable accuracy, although a deeper study should be carried out to assess
-how the amount of overlap impacts both accuracy and fitting time.
-
-We interpolated the synthetic airborne survey using the gradient boosted
-equivalent sources on the same points of the target grid.
-The interpolations were carried out using different amount of overlap, from
-0\% to 0.95\% with a step size of 0.05\%.
-For each overlap, we gridded the synthetic data with different sets of
-parameters, fixing the window size to INSERT-WINDOW-SIZE and using
-block-averaged sources with relative depth and a spacing of
-\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}.
-We registered the RMS achieved by the best prediction for each overlap and the
-computation time needed to fit the source coefficients.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Gridding Australia gravity data}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusions}

### 2020-12-09 manuscript/manuscript.tex
Make a tiny change to trigger the actions build

--- 2020-11-30 manuscript/manuscript.tex
@@
     \fontsize{9pt}{12pt}\selectfont
-    \Author{}, 2019. \DOI{}
+    \Author{}, 2020. \DOI{}
 }
@@
 
-\section{Performance of gradient boosted equivalent sources}
-
-Our second goal is to assess the accuracy of the predictions achieved by the
-gradient boosting algorithm while registering its performance by comparison
-with the non-boosted equivalent sources.
-
-\subsection{Window size}
-
-One factor that plays an important role on the gradient boosted equivalent
-layers is the size of the overlapping windows used to create each set of
-equivalent sources.
-Smaller windows will reduce the amount of computer memory needed to fit the
-source coefficients: smaller windows will reduce the size of Jacobian matrices
-$\tilde{\mathbf{A}_k}$.
-Nevertheless, the usage of smaller windows may produce less accurate
-predictions: the equivalent sources cannot achieve the global minimum of the
-misfit $\varphi(\mathbf{c})$ of equation~\ref{eq:misfit-unscaled}.
-Moreover, the size of the overlapping windows might also impact on the
-computation time needed to fit the source coefficients: smaller windows will
-generate simpler least-square problems which are easier to solve, but they will
-also create more iterations.
-
-We want to assess how the size of the overlapping windows impacts both the
-accuracy of the predictions and the computation time needed to fit the source
-coefficients in comparison with the performance of the non-boosted equivalent
-sources.
-
-We applied the gradient boosted equivalent sources to interpolate the synthetic
-airborne survey on the same points of the target grid.
-We selected several window sizes to assess how accuracy and performance depend
-on that variable.
-For each window size we gridded the synthetic data with different sets of
-parameters. Then we compared each prediction to the target grid in order to get
-the best prediction for each window size.
-On every interpolation, block-averaged sources with relative depth are used
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}, and an
-overlap of 50\% between adjacent windows.
-
-Using the best set of parameters for each window size, we registered the
-achieved RMS against the values of the target grid and the time needed to fit
-the sources coefficients.
-
-Compare RMS with the one achieved by the best prediction carried out by the
-non-boosted equivalent sources with block-averaged sources (see
-Table~\ref{tab:parameters-airborne-survey}).
-Calculated the fitting time relative to the time needed by non-boosted
-equivalent sources.
-
-\subsection{Overlapping}
-
-Another factor that plays an important role on the accuracy of the predictions
-and impacts the computation time needed to fit the source coefficients is the
-amount of overlap between adjacent windows.
-The previous choice of 50\% showed to be sufficiently good to achieve
-acceptable accuracy, although a deeper study should be carried out to assess
-how the amount of overlap impacts both accuracy and fitting time.
-
-We interpolated the synthetic airborne survey using the gradient boosted
-equivalent sources on the same points of the target grid.
-The interpolations were carried out using different amount of overlap, from
-0\% to 0.95\% with a step size of 0.05\%.
-For each overlap, we gridded the synthetic data with different sets of
-parameters, fixing the window size to INSERT-WINDOW-SIZE and using
-block-averaged sources with relative depth and a spacing of
-\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}.
-We registered the RMS achieved by the best prediction for each overlap and the
-computation time needed to fit the source coefficients.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Gridding Australia gravity data}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusions}

### 2020-12-09 manuscript/manuscript.tex
Minor change to trigger a build
Add data weights to the equations

--- 2020-12-09 manuscript/manuscript.tex
@@
 \newcommand{\inv}{^{\text{-}1}}
+\newcommand{\trans}{^{\text{T}}}
 
@@
     \phi(\mathbf{c}) =
-        \left\lVert
-            \mathbf{d}^o - \mathbf{A}\mathbf{c}
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
+    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]\trans
+    \mathbf{W}
+    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]
+    + \lambda_d\ \mathbf{c}\trans\mathbf{c}
+    \ ,
     \label{eq:misfit-unscaled}
@@
 
-\noindent where $\left\lVert \cdot \right\rVert$ symbolizes the L$_2$ norm and
+\noindent where
+$\mathbf{W}$ is a $N \times N$ matrix of data weights and
 $\lambda_d$ is a positive \emph{damping} parameter with the same units as the
@@
 
-The misfit function defined on equation~\ref{eq:misfit-unscaled} can be
+The goal function defined on equation~\ref{eq:misfit-unscaled} can be
 rewritten as
@@
     \phi(\mathbf{m}) =
-        \left\lVert \mathbf{d}^o
-        - \mathbf{B}\mathbf{m} \right\rVert ^ 2
-        + \lambda \left\lVert \mathbf{m} \right\rVert ^2,
+    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]\trans
+    \mathbf{W}
+    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]
+    + \lambda\ \mathbf{m}\trans\mathbf{m}
+    \ ,
     \label{eq:misfit}
@@
     \left[
-            \mathbf{B}^\text{T} \mathbf{B}
-            + \lambda \mathbf{I}
+      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
     \right]\inv
-        \mathbf{B}^\text{T}
-        \mathbf{d}^o.
-\end{equation}
-
-On the other hand, if there are more sources than observation points, the
-problem is under-determined and the scaled coefficients can be obtained as
-\citep{menke1989}:
-
-\begin{equation}
-    \hat{\mathbf{m}} =
-    \mathbf{B}^\text{T}
-        \left[
-            \mathbf{B} \mathbf{B}^\text{T}
-            + \lambda \mathbf{I}
-        \right]\inv
+    \mathbf{B}\trans\mathbf{W}
     \mathbf{d}^o.
@@
 $\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
-\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
+\ldots, d_N)\trans$. We have defined a set of $M$ point sources located on
 $\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
@@
     \alpha_k = \frac{
-        \mathbf{r}_{k-1}^T \mathbf{A}_k \mathbf{c}_k
+        \mathbf{r}_{k-1}\trans \mathbf{A}_k \mathbf{c}_k
     }{
-        \left(\mathbf{A}_k \mathbf{c}_k\right)^T \mathbf{A}_k \mathbf{c}_k
+        \left(\mathbf{A}_k \mathbf{c}_k\right)\trans \mathbf{A}_k \mathbf{c}_k
     }.

### 2020-12-09 manuscript/manuscript.tex
Revise the least squares solution section
Removed the underdetermined solution because in practice we don't really
use it. Even for grid sources, our code runs the overdetermined version.
Also left the system instead of using the inverse because that is also
what we do in practice (and I hate having to always say that in practice
we don't calculate inverses).

@@
 are unitless and each column has unit variance.
-We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
-standard deviation of each column of $\mathbf{A}$:
+We define a diagonal matrix $\mathbf{S}$
 
@@
     \begin{bmatrix}
-        \sigma_1 & \cdots &0 \\
-        \vdots & \ddots & \vdots \\
-        0 & \cdots & \sigma_M
-    \end{bmatrix}
-    .
-\end{equation}
-
+      \sigma_1 & 0 & \cdots &0 \\
+      0 & \sigma_2 & \cdots &0 \\
+      \vdots & \vdots & \ddots & \vdots \\
+      0  & 0 & \cdots & \sigma_M
+    \end{bmatrix}_{M \times M}
+    ,
+\end{equation}
+
+\noindent in which $\sigma_j$ is the standard deviation of the $j$-th column of
+$\mathbf{A}$.
 We then write the forward problem in equation~\ref{eq:linear-problem} as
@@
 
-The goal function defined on equation~\ref{eq:misfit-unscaled} can be
+The goal function defined in equation~\ref{eq:misfit-unscaled} can be
 rewritten as
@@
 
-If the number of observation points is equal or larger to the number of
-sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
-well- or over-determined, respectively. Therefore, the scaled coefficients that
-minimize the misfit function can be obtained through \citep{menke1989}:
-
-\begin{equation}
-    \hat{\mathbf{m}} =
+The vector of scaled coefficients $\hat{\mathbf{m}}$ that minimizes the goal
+function can be found by solving the \emph{normal equation system}
+\citep{menke1989}
+
+\begin{equation}
     \left[
       \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
-    \right]\inv
+    \right]
+    \hat{\mathbf{m}} =
     \mathbf{B}\trans\mathbf{W}
@@
 
-Once the scaled coefficients are obtained, the coefficients
-$\mathbf{c}$ can be obtained by
-
-\begin{equation}
-    \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{m}}.
-\end{equation}
+Once the scaled coefficients are obtained, the estimated unscaled coefficients
+$\hat{\mathbf{c}}$ can be calculated by removing the scaling factor
+
+\begin{equation}
+    \hat{\mathbf{c}} = \mathbf{S}\inv \hat{\mathbf{m}} \ .
+\end{equation}
+
+\noindent The forward modeling operations used to perform predictions
+(e.g., for interpolation and upward continuation) are left unchanged by
+using vector $\hat{\mathbf{c}}$ instead of $\hat{\mathbf{m}}$.
 

### 2020-12-09 manuscript/manuscript.tex
Move justification of gradient boosting to intro

--- 2020-12-09 manuscript/manuscript.tex
@@
     \fontsize{9pt}{12pt}\selectfont
-    \Author{}, 2020. \DOI{}
+    \Author{}, 2019. \DOI{}
 }
@@
 descent to avoid calculating the Hessian matrix and solving linear systems.
-Most existing methods solve under-determined problems, requiring a much larger
-number of equivalent sources than the number of data points.
+
+Many of the existing methods solve under-determined problems, requiring a much
+larger number of equivalent sources than the number of data points.
+Some achieve greater efficiency by restricting their applications
+specific data types \citep{siqueira2017},
+interpolating only on regular grids \citep{leao1989},
+or requiring already gridded data (CITE PINGA NEW PAPER),
+to name a few.
 Furthermore, many of the optimizations proposed are also complex to implement
 in a computer program, limiting their wider adoption.
+
 In the present study,
-we propose a two-way method for reducing the computational load needed to apply
-the equivalent sources technique: first by reducing the number of equivalent
-sources through a \emph{block-averaging} strategy and then simplifying the
-fitting process through a \emph{gradient boosting} algorithm.
-The first strategy consists in
-dividing the survey area into horizontal blocks and assign one source
-to each block at the median horizontal location of the data points.
-For airborne surveys, which are oversampled along tracks, this can greatly
-reduce the size of the inverse problem while retaining the quality of
-interpolation.
-The second algorithm simplifies the process of fitting a very large number of
-equivalent sources by defining sets of fewer sources, whose coefficients are
-fitted iteratively while minimizing a given residue.
+we propose a two strategies for reducing the computational load of
+the equivalent sources technique:
+
+\begin{enumerate}
+    \item Reduce the number of equivalent sources for oversampled surveys
+      through a \emph{block-averaging} strategy while maintaining the quality
+      of the solution.
+    \item Fit the equivalent source model iteratively along overlapping windows
+      using a \emph{gradient boosting} algorithm \citep{friedman2001}.
+\end{enumerate}
+
+The first strategy consists in dividing the survey area into horizontal blocks
+and assign one source to each block, located at the median horizontal location
+of the data points. For airborne, shipborne, and satellite surveys, which are
+oversampled along tracks, this can greatly reduce the size of the inverse
+problem while retaining the same quality of interpolation.
+
+The gradient boosting algorithm allows us to fit the equivalent source model
+iteratively by operating on individual overlapping windows.
+Thus, our method solves several much smaller least-squares problems instead of
+a large one.
+This has some similarities with the strategy used by \citet{leao1989} but
+without the requirement for sources and predictions to be on regular grids.
+
 Through tests on synthetic data, we show that: (i) the \emph{block-averaged}
-sources achieve the same accuracy as a traditional equivalent layer while using
-a fraction of the number of sources, and (ii) the \emph{gradient boosting}
-algorithm greatly reduces the computational memory required to fit very large
-datasets without scarifying predictions' accuracy.
-Finally these methods are used to interpolate a 1.7 million gravity data
-measurements around Australia onto a regular grid.
+sources are able to achieve the same accuracy as other traditional equivalent
+source layouts while using a fraction of the number of sources, and (ii) the
+\emph{gradient boosting} algorithm greatly reduces the computational memory
+required to fit very large datasets without sacrificing prediction accuracy.
+Finally, a combination of both strategies are used to process a collection of
+around 1.7 million ground gravity data measurements from Australia.
 
@@
     \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{c}}.
+\end{equation}
+
+\subsection{Gradient boosting}
+
+Here we propose an iterative algorithm for fitting the source coefficients
+using a gradient boosting \citep{friedman2001, friedman2002} strategy:
+(i) define a collection of overlapping windows of equal size that cover the
+survey area,
+(ii) define one set of equivalent sources per window,
+(iii) iteratively fit the coefficients of each set of sources.
+Once every set of sources is fitted, we can predict the value of the field on
+any observation point as the effect of every set of equivalent sources.
+
+Lets assume we have $N$ measurements of a harmonic field on observations points
+$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
+\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
+$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
+coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
+different sets of equivalent sources: we define $K$ overlapping windows of
+equal size that cover the whole observation area, and then we create one set of
+equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
+sources that fall inside the $k$-th window.
+The observed data should be equal to the superposition of the
+effect of every set of equivalent sources:
+
+\begin{equation}
+    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k,
+\end{equation}
+
+\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
+set of equivalent sources; $\mathbf{A}_k$ is the Jacobian matrix between
+those sources and every data point; and each $\alpha_k$ is a constant called
+\emph{step-size parameter}.
+
+By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
+iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
+with the observed data) is used to fit the $\mathbf{c}_k$
+coefficients and $\alpha_k$ step-size parameter, and then updated by removing
+the effect of the same sources, as follows:
+
+\begin{equation}
+    \mathbf{r}_0 = \mathbf{d},
+\end{equation}
+
+\begin{equation}
+    \mathbf{r}_k = \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k.
+    \label{eq:residue}
+\end{equation}
+
+\noindent On each iteration the $\mathbf{c}_k$ vector and the $\alpha_k$
+parameter can be fitted so they minimize the misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+\noindent following the same method described on Section
+\ref{sec:eql-inversion}.
+Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
+adjusting the size of the overlapping windows can help in reducing the computer
+memory needed to fit the source coefficients.
+Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
+matrices large enough that they cannot be stored in memory, we can apply one
+more simplification on the fitting process: ignore the effect of the $k$-th
+sources on any observation point that falls outside the $k$-th window.
+
+Assuming that there are $N_k$ observation points that fall under the $k$-th
+window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
+misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
+only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
+observation points that fall under the $k$-th window; and
+$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
+and the $k$-th sources.
+Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
+elements, the computer memory needed for fitting the $\mathbf{c}_k$
+coefficients is greatly reduced.
+
+Once the $\mathbf{c}_k$ coefficients are fitted following the same method
+described on Section \ref{sec:eql-inversion}, we need to obtain the value
+of the step-size parameter $\alpha_k$.
+This can be achieved by minimizing the norm of the difference between the
+previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
+every observation point:
+
+\begin{equation}
+    \alpha_k = \underset{\alpha}{\mathrm{argmin}}
+    \left(
+        \left\lVert
+            \mathbf{r}_{k-1} - \alpha \mathbf{A}_k \mathbf{c}_k
+        \right\rVert ^ 2
+    \right),
+\end{equation}
+
+\noindent which leads to:
+
+\begin{equation}
+    \alpha_k = \frac{
+        \mathbf{r}_{k-1}^T \mathbf{A}_k \mathbf{c}_k
+    }{
+        \left(\mathbf{A}_k \mathbf{c}_k\right)^T \mathbf{A}_k \mathbf{c}_k
+    }.
+\end{equation}
+
+This step will improve the convergence of the iterative algorithm and also will
+introduce at some extent the effect of the $k$-th sources on every data point,
+which was neglected on the fitting of the $\mathbf{c}_k$ coefficients.
+
+Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
+fitted, equation \ref{eq:residue} is applied to update the residue: compute the
+effect of the sources belonging to the $k$-th window on every observation
+point. Worth noting that when calculating the effect of any number of sources
+we don't need to pre-compute the entire Jacobian matrix: we can calculate the
+effect of the sources on each observation point by a simple addition of terms,
+what means computing each Jacobian element at once when needed.
+
+Because the number of windows is fixed before starting the iteration process,
+its number of steps are also fixed to $K$. Moreover, the windows are randomly
+shuffled before starting the process to prevent the prioritization of clustered
+sets of equivalent sources.
+
+After all $\alpha_k$ parameters and $\mathbf{c}_k$ coefficients vectors are
+fitted, we can predict the effect of every equivalent source on any point as
+follows:
+
+\begin{equation}
+    V(\mathbf{p}) =
+    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
+    \frac{\alpha_k {c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
 \end{equation}
@@
 \end{table*}
-
-\subsection{Gradient boosted equivalent sources}
-
-Reducing the number of sources might help to lower the amount of computer
-memory needed to fit their coefficients, although it may be not enough for
-a very large set of observation points.
-Even if we can greatly reduce the number of sources, having too many data
-points would still produce a Jacobian matrix large enough that cannot fit in
-memory.
-This problem was already faced by other authors
-\citep{mendonca1994, leao1989, li2010, barnes2011, oliveira2013, siqueira2017,
-jirigalatu2019}.
-The iterative method proposed by \citet{siqueira2017} needs equivalent sources
-to be located beneath each observation point, so it cannot take advantage of
-the block-averaged sources.
-\citet{leao1989} perform the fitting simultaneously with the prediction, what
-prevents us to use already fitted equivalent sources to make future
-predictions. Besides the method is limited to interpolations on regular grids.
-% Add more discussion on why we won't apply any of the following methods
-\citet{mendonca1994}
-\citet{li2010}
-\citet{barnes2011}
-\citet{jirigalatu2019}
-
-Here we propose an iterative algorithm for fitting the source coefficients
-using a gradient boosting \citep{friedman2001, friedman2002} strategy:
-(i) define a collection of overlapping windows of equal size that cover the
-survey area,
-(ii) define one set of equivalent sources per window,
-(iii) iteratively fit the coefficients of each set of sources.
-Once every set of sources is fitted, we can predict the value of the field on
-any observation point as the effect of every set of equivalent sources.
-
-Lets assume we have $N$ measurements of a harmonic field on observations points
-$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
-\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
-$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
-coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
-different sets of equivalent sources: we define $K$ overlapping windows of
-equal size that cover the whole observation area, and then we create one set of
-equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
-sources that fall inside the $k$-th window.
-The observed data should be equal to the superposition of the
-effect of every set of equivalent sources:
-
-\begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k,
-\end{equation}
-
-\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
-set of equivalent sources; $\mathbf{A}_k$ is the Jacobian matrix between
-those sources and every data point; and each $\alpha_k$ is a constant called
-\emph{step-size parameter}.
-
-By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
-iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
-with the observed data) is used to fit the $\mathbf{c}_k$
-coefficients and $\alpha_k$ step-size parameter, and then updated by removing
-the effect of the same sources, as follows:
-
-\begin{equation}
-    \mathbf{r}_0 = \mathbf{d},
-\end{equation}
-
-\begin{equation}
-    \mathbf{r}_k = \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k.
-    \label{eq:residue}
-\end{equation}
-
-\noindent On each iteration the $\mathbf{c}_k$ vector and the $\alpha_k$
-parameter can be fitted so they minimize the misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-\noindent following the same method described on Section
-\ref{sec:eql-inversion}.
-Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
-adjusting the size of the overlapping windows can help in reducing the computer
-memory needed to fit the source coefficients.
-Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
-matrices large enough that they cannot be stored in memory, we can apply one
-more simplification on the fitting process: ignore the effect of the $k$-th
-sources on any observation point that falls outside the $k$-th window.
-
-Assuming that there are $N_k$ observation points that fall under the $k$-th
-window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
-misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
-only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
-observation points that fall under the $k$-th window; and
-$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
-and the $k$-th sources.
-Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
-elements, the computer memory needed for fitting the $\mathbf{c}_k$
-coefficients is greatly reduced.
-
-Once the $\mathbf{c}_k$ coefficients are fitted following the same method
-described on Section \ref{sec:eql-inversion}, we need to obtain the value
-of the step-size parameter $\alpha_k$.
-This can be achieved by minimizing the norm of the difference between the
-previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
-every observation point:
-
-\begin{equation}
-    \alpha_k = \underset{\alpha}{\mathrm{argmin}}
-    \left(
-        \left\lVert
-            \mathbf{r}_{k-1} - \alpha \mathbf{A}_k \mathbf{c}_k
-        \right\rVert ^ 2
-    \right),
-\end{equation}
-
-\noindent which leads to:
-
-\begin{equation}
-    \alpha_k = \frac{
-        \mathbf{r}_{k-1}^T \mathbf{A}_k \mathbf{c}_k
-    }{
-        \left(\mathbf{A}_k \mathbf{c}_k\right)^T \mathbf{A}_k \mathbf{c}_k
-    }.
-\end{equation}
-
-This step will improve the convergence of the iterative algorithm and also will
-introduce at some extent the effect of the $k$-th sources on every data point,
-which was neglected on the fitting of the $\mathbf{c}_k$ coefficients.
-
-Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
-fitted, equation \ref{eq:residue} is applied to update the residue: compute the
-effect of the sources belonging to the $k$-th window on every observation
-point. Worth noting that when calculating the effect of any number of sources
-we don't need to pre-compute the entire Jacobian matrix: we can calculate the
-effect of the sources on each observation point by a simple addition of terms,
-what means computing each Jacobian element at once when needed.
-
-Because the number of windows is fixed before starting the iteration process,
-its number of steps are also fixed to $K$. Moreover, the windows are randomly
-shuffled before starting the process to prevent the prioritization of clustered
-sets of equivalent sources.
-
-After all $\alpha_k$ parameters and $\mathbf{c}_k$ coefficients vectors are
-fitted, we can predict the effect of every equivalent source on any point as
-follows:
-
-\begin{equation}
-    V(\mathbf{p}) =
-    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
-    \frac{\alpha_k {c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
-\end{equation}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-12-10 manuscript/manuscript.tex
Write gradient boosting as an algorithm

@@
 \usepackage{amsmath}
+\usepackage[longend,linesnumbered]{algorithm2e}
 \usepackage{graphicx}
@@
 \usepackage{booktabs}
+\usepackage{setspace}
 
@@
 
-Here we propose an iterative algorithm for fitting the source coefficients
-using a gradient boosting \citep{friedman2001, friedman2002} strategy:
-(i) define a collection of overlapping windows of equal size that cover the
-survey area,
-(ii) define one set of equivalent sources per window,
-(iii) iteratively fit the coefficients of each set of sources.
-Once every set of sources is fitted, we can predict the value of the field on
-any observation point as the effect of every set of equivalent sources.
-
-Lets assume we have $N$ measurements of a harmonic field on observations points
-$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
-\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
-$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
-coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
-different sets of equivalent sources: we define $K$ overlapping windows of
-equal size that cover the whole observation area, and then we create one set of
-equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
-sources that fall inside the $k$-th window.
-The observed data should be equal to the superposition of the
-effect of every set of equivalent sources:
-
-\begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k,
-\end{equation}
-
-\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
-set of equivalent sources; $\mathbf{A}_k$ is the Jacobian matrix between
-those sources and every data point; and each $\alpha_k$ is a constant called
-\emph{step-size parameter}.
+Gradient boosting was first introduced by \citet{friedman2001, friedman2002} as
+a method for fitting additive parametric models of the form
+
+\begin{equation}
+  d = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
+\end{equation}
+
+\noindent where $\alpha_k$ is a scalar coefficient called the \emph{step-size}
+and $f$ is a function of the parameter vector $\mathbf{c}_k$.
+For linear regression problems, these additive models can be written as the
+matrix equation
+
+\begin{equation}
+    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k \ .
+    \label{eq:gb-linear-model}
+\end{equation}
+
+We can transform our equivalent source problem in
+equation~\ref{eq:linear-problem} into an additive model by
+(1) defining a set of $K$ overlapping windows of equal size that cover the
+survey area and (2) defining separate sets of equivalent sources, one per
+window. Then, the coefficients $\mathbf{c}_k$ relate to the equivalent sources
+of the $k$-th window and $\mathbf{A}_k$ is the Jacobian matrix between
+those sources and every data point.
+Thus, the predicted data are a superposition of the
+effects of the $K$ sets of equivalent sources.
+
+The gradient boosting algorithm for finding the damped least-squares solutions
+for the $K$ parameters vectors $\mathbf{c}_k$ in
+equation~\ref{eq:gb-linear-model} can be modified from \citep{friedman2001}
+
+\begin{algorithm}[!h]
+  \DontPrintSemicolon
+  \setstretch{1.5}
+  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
+  \For{ $k = 1$ \KwTo $K$ }{
+    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$ \;
+    $
+     \hat{\mathbf{m}}_k = \left[\mathbf{B}_k\trans \mathbf{W}_k \mathbf{B}_k +
+     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \mathbf{W}_k
+     \mathbf{r}_{k-1}
+    $ \;
+    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$ \;
+    $
+      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
+      \left(
+        \left\lVert
+          \mathbf{r}_{k - 1} - \alpha \mathbf{A}_k \hat{\mathbf{c}}_k
+        \right\rVert ^ 2
+      \right)
+    $ \;
+    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
+  }
+  \BlankLine
+  \setstretch{1}
+  \caption{Gradient boosting solution for damped least-squares regression.}
+\end{algorithm}
+
+The algorithm above works by fitting each component of the additive model, one
+at a time, to the residuals of the previous component.
 
@@
     \alpha_k = \frac{
-        \mathbf{r}_{k-1}^T \mathbf{A}_k \mathbf{c}_k
+      \mathbf{r}_{k-1}\trans \mathbf{A}_k \hat{\mathbf{c}}_k
     }{
-        \left(\mathbf{A}_k \mathbf{c}_k\right)^T \mathbf{A}_k \mathbf{c}_k
+      \hat{\mathbf{c}}_k\trans\mathbf{A}_k\trans \mathbf{A}_k \hat{\mathbf{c}}_k
     }.

### 2020-12-10 manuscript/manuscript.tex
Finish the boosting description

@@
 
-The gradient boosting algorithm for finding the damped least-squares solutions
-for the $K$ parameters vectors $\mathbf{c}_k$ in
-equation~\ref{eq:gb-linear-model} can be modified from \citep{friedman2001}
+The gradient boosting algorithm above works by fitting each component of the
+additive model, one at a time, to the residuals of the previous component.
+\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
+optimization in the so-called ``function space'', with $\alpha_k$ corresponding
+to step sizes in steepest descent.
+We can modify the gradient boosting algorithm of \citet{friedman2001} to
+find the damped least-squares solutions for the $K$ parameters vectors
+$\mathbf{c}_k$ and step sizes $\alpha_k$ in equation~\ref{eq:gb-linear-model}:
 
@@
   \For{ $k = 1$ \KwTo $K$ }{
+
+    \nllabel{alg:scale}
     $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$ \;
+
+    \nllabel{alg:fit}
     $
@@
     $ \;
+
+    \nllabel{alg:unscale}
     $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$ \;
+
+    \nllabel{alg:stepsize}
     $
@@
     $ \;
+
+    \nllabel{alg:residual}
     $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
@@
 
-The algorithm above works by fitting each component of the additive model, one
-at a time, to the residuals of the previous component.
-
-By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
-iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
-with the observed data) is used to fit the $\mathbf{c}_k$
-coefficients and $\alpha_k$ step-size parameter, and then updated by removing
-the effect of the same sources, as follows:
-
-\begin{equation}
-    \mathbf{r}_0 = \mathbf{d},
-\end{equation}
-
-\begin{equation}
-    \mathbf{r}_k = \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k.
-    \label{eq:residue}
-\end{equation}
-
-\noindent On each iteration the $\mathbf{c}_k$ vector and the $\alpha_k$
-parameter can be fitted so they minimize the misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-\noindent following the same method described on Section
-\ref{sec:eql-inversion}.
-Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
-adjusting the size of the overlapping windows can help in reducing the computer
-memory needed to fit the source coefficients.
-Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
-matrices large enough that they cannot be stored in memory, we can apply one
-more simplification on the fitting process: ignore the effect of the $k$-th
-sources on any observation point that falls outside the $k$-th window.
-
-Assuming that there are $N_k$ observation points that fall under the $k$-th
-window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
-misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
-only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
-observation points that fall under the $k$-th window; and
-$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
-and the $k$-th sources.
-Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
-elements, the computer memory needed for fitting the $\mathbf{c}_k$
-coefficients is greatly reduced.
-
-Once the $\mathbf{c}_k$ coefficients are fitted following the same method
-described on Section \ref{sec:eql-inversion}, we need to obtain the value
-of the step-size parameter $\alpha_k$.
-This can be achieved by minimizing the norm of the difference between the
-previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
-every observation point:
-
-\begin{equation}
-    \alpha_k = \underset{\alpha}{\mathrm{argmin}}
-    \left(
-        \left\lVert
-            \mathbf{r}_{k-1} - \alpha \mathbf{A}_k \mathbf{c}_k
-        \right\rVert ^ 2
-    \right),
-\end{equation}
-
-\noindent which leads to:
+\citet{friedman2002} suggests that introducing randomness into the fitting
+process can improve convergence of the solution. To achieve this, we randomize
+the order in which the $K$ windows are used in the gradient boosting algorithm.
+
+The $\mathbf{A}_k$ matrices have only $N \times M_k$ elements, which can be
+considerably smaller than the $N \times M$ elements of $\mathbf{A}$.
+Therefore, the gradient boosting method allows us to fit
+equivalent sources models that would produce Jacobian matrices that are larger
+than the available computer memory.
+Furthermore, we can increase or decrease the size of the overlapping windows as
+needed depending on the number of sources in the model and the available
+computer memory.
+
+We can improve the efficiency of the algorithm further by using only data
+points that fall within the $k$-th window for fitting the sources
+(steps \ref{alg:scale} and \ref{alg:fit}),
+while using all available data when calculating the step size and residuals
+(steps \ref{alg:stepsize} and \ref{alg:residual}).
+By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
+elements.
+The forward modeling operations performed in steps \ref{alg:stepsize} and
+\ref{alg:residual} can be done by a summation
+(TODO: ADD EQUATION)
+instead of a matrix-vector product, which allows us to avoid storing the larger
+$N \times M_k$ Jacobian.
+The influence of distance sources on the solution is maintained by using the
+entire set of data points when updating the residuals vector.
+
+The step size parameter functions as scaling factor that prevents the algorithm
+from worsening the fit to data points outside of the current window.
+As such, it improves the converge of the solution and ensures that the
+overall misfit decreases with iteration.
+The step size that minimizes the misfit function in step \ref{alg:stepsize} of
+the algorithm is
 
@@
 
-This step will improve the convergence of the iterative algorithm and also will
-introduce at some extent the effect of the $k$-th sources on every data point,
-which was neglected on the fitting of the $\mathbf{c}_k$ coefficients.
-
-Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
-fitted, equation \ref{eq:residue} is applied to update the residue: compute the
-effect of the sources belonging to the $k$-th window on every observation
-point. Worth noting that when calculating the effect of any number of sources
-we don't need to pre-compute the entire Jacobian matrix: we can calculate the
-effect of the sources on each observation point by a simple addition of terms,
-what means computing each Jacobian element at once when needed.
-
-Because the number of windows is fixed before starting the iteration process,
-its number of steps are also fixed to $K$. Moreover, the windows are randomly
-shuffled before starting the process to prevent the prioritization of clustered
-sets of equivalent sources.
-
-After all $\alpha_k$ parameters and $\mathbf{c}_k$ coefficients vectors are
-fitted, we can predict the effect of every equivalent source on any point as
-follows:
-
-\begin{equation}
-    V(\mathbf{p}) =
-    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
-    \frac{\alpha_k {c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
-\end{equation}
+After all $\alpha_k$ step sizes and $\hat{\mathbf{c}}_k$ coefficients vectors
+are estimated, we can predict the effect of the additive equivalent source
+model on any point through the summation
+
+\begin{equation}
+    d(\mathbf{p}) =
+    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
+    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
+    \ .
+\end{equation}
+
+SOMETHING ABOUT THE VON FRESE 88 PAPER (BOOTSTRAP INVERSION) AND HOW THIS IS
+DIFFERENT.
 

### 2020-12-10 manuscript/manuscript.tex
Include section comparing with boostrap inversion

@@
 
-SOMETHING ABOUT THE VON FRESE 88 PAPER (BOOTSTRAP INVERSION) AND HOW THIS IS
-DIFFERENT.
+Our gradient boosting algorithm for overlapping windows is similar to the
+``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
+fits portions of an equivalent source model to the data residuals.
+The key differences are:
+(1) the sources in the overlapping portions of the windows are fit more than
+once, allowing the algorithm to self-correct for poor solutions to any given
+window;
+(2) using only data points within the window when fitting the data enables the
+use of larger datasets;
+(3) experience shows that the step size parameter improves the convergence of
+the solution, particularly when using only the data inside the windows for
+fitting.
 

### 2020-12-10 manuscript/manuscript.tex
Minor tweaks to the text

@@
 (TODO: ADD EQUATION)
-instead of a matrix-vector product, which allows us to avoid storing the larger
-$N \times M_k$ Jacobian.
+instead of a matrix-vector product, which allows us to avoid computing and
+storing the larger $N \times M_k$ Jacobian at any point.
 The influence of distance sources on the solution is maintained by using the

### 2020-12-10 manuscript/manuscript.tex
Add note that the comparison might better for discussion
Divide the section in horizontal and depth
Reviewed the horizontal location part. Mostly some wording changes and
made some lists in the text into bullet points for easier reading.

--- 2020-12-10 manuscript/manuscript.tex
@@
 \usepackage{amsmath}
-\usepackage[longend,linesnumbered]{algorithm2e}
 \usepackage{graphicx}
@@
 \usepackage{booktabs}
-\usepackage{setspace}
 
@@
 descent to avoid calculating the Hessian matrix and solving linear systems.
-
-Many of the existing methods solve under-determined problems, requiring a much
-larger number of equivalent sources than the number of data points.
-Some achieve greater efficiency by restricting their applications
-specific data types \citep{siqueira2017},
-interpolating only on regular grids \citep{leao1989},
-or requiring already gridded data (CITE PINGA NEW PAPER),
-to name a few.
+Most existing methods solve under-determined problems, requiring a much larger
+number of equivalent sources than the number of data points.
 Furthermore, many of the optimizations proposed are also complex to implement
 in a computer program, limiting their wider adoption.
-
 In the present study,
-we propose a two strategies for reducing the computational load of
-the equivalent sources technique:
-
-\begin{enumerate}
-    \item Reduce the number of equivalent sources for oversampled surveys
-      through a \emph{block-averaging} strategy while maintaining the quality
-      of the solution.
-    \item Fit the equivalent source model iteratively along overlapping windows
-      using a \emph{gradient boosting} algorithm \citep{friedman2001}.
-\end{enumerate}
-
-The first strategy consists in dividing the survey area into horizontal blocks
-and assign one source to each block, located at the median horizontal location
-of the data points. For airborne, shipborne, and satellite surveys, which are
-oversampled along tracks, this can greatly reduce the size of the inverse
-problem while retaining the same quality of interpolation.
-
-The gradient boosting algorithm allows us to fit the equivalent source model
-iteratively by operating on individual overlapping windows.
-Thus, our method solves several much smaller least-squares problems instead of
-a large one.
-This has some similarities with the strategy used by \citet{leao1989} but
-without the requirement for sources and predictions to be on regular grids.
-
+we propose a two-way method for reducing the computational load needed to apply
+the equivalent sources technique: first by reducing the number of equivalent
+sources through a \emph{block-averaging} strategy and then simplifying the
+fitting process through a \emph{gradient boosting} algorithm.
+The first strategy consists in
+dividing the survey area into horizontal blocks and assign one source
+to each block at the median horizontal location of the data points.
+For airborne surveys, which are oversampled along tracks, this can greatly
+reduce the size of the inverse problem while retaining the quality of
+interpolation.
+The second algorithm simplifies the process of fitting a very large number of
+equivalent sources by defining sets of fewer sources, whose coefficients are
+fitted iteratively while minimizing a given residue.
 Through tests on synthetic data, we show that: (i) the \emph{block-averaged}
-sources are able to achieve the same accuracy as other traditional equivalent
-source layouts while using a fraction of the number of sources, and (ii) the
-\emph{gradient boosting} algorithm greatly reduces the computational memory
-required to fit very large datasets without sacrificing prediction accuracy.
-Finally, a combination of both strategies are used to process a collection of
-around 1.7 million ground gravity data measurements from Australia.
+sources achieve the same accuracy as a traditional equivalent layer while using
+a fraction of the number of sources, and (ii) the \emph{gradient boosting}
+algorithm greatly reduces the computational memory required to fit very large
+datasets without scarifying predictions' accuracy.
+Finally these methods are used to interpolate a 1.7 million gravity data
+measurements around Australia onto a regular grid.
 
@@
 
-\subsection{Gradient boosting}
-
-Gradient boosting was first introduced by \citet{friedman2001, friedman2002} as
-a method for fitting additive parametric models of the form
-
-\begin{equation}
-  d = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
-\end{equation}
-
-\noindent where $\alpha_k$ is a scalar coefficient called the \emph{step-size}
-and $f$ is a function of the parameter vector $\mathbf{c}_k$.
-For linear regression problems, these additive models can be written as the
-matrix equation
-
-\begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k \ .
-    \label{eq:gb-linear-model}
-\end{equation}
-
-We can transform our equivalent source problem in
-equation~\ref{eq:linear-problem} into an additive model by
-(1) defining a set of $K$ overlapping windows of equal size that cover the
-survey area and (2) defining separate sets of equivalent sources, one per
-window. Then, the coefficients $\mathbf{c}_k$ relate to the equivalent sources
-of the $k$-th window and $\mathbf{A}_k$ is the Jacobian matrix between
-those sources and every data point.
-Thus, the predicted data are a superposition of the
-effects of the $K$ sets of equivalent sources.
-
-The gradient boosting algorithm above works by fitting each component of the
-additive model, one at a time, to the residuals of the previous component.
-\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
-optimization in the so-called ``function space'', with $\alpha_k$ corresponding
-to step sizes in steepest descent.
-We can modify the gradient boosting algorithm of \citet{friedman2001} to
-find the damped least-squares solutions for the $K$ parameters vectors
-$\mathbf{c}_k$ and step sizes $\alpha_k$ in equation~\ref{eq:gb-linear-model}:
-
-\begin{algorithm}[!h]
-  \DontPrintSemicolon
-  \setstretch{1.5}
-  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
-  \For{ $k = 1$ \KwTo $K$ }{
-
-    \nllabel{alg:scale}
-    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$ \;
-
-    \nllabel{alg:fit}
-    $
-     \hat{\mathbf{m}}_k = \left[\mathbf{B}_k\trans \mathbf{W}_k \mathbf{B}_k +
-     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \mathbf{W}_k
-     \mathbf{r}_{k-1}
-    $ \;
-
-    \nllabel{alg:unscale}
-    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$ \;
-
-    \nllabel{alg:stepsize}
-    $
-      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
-      \left(
-        \left\lVert
-          \mathbf{r}_{k - 1} - \alpha \mathbf{A}_k \hat{\mathbf{c}}_k
-        \right\rVert ^ 2
-      \right)
-    $ \;
-
-    \nllabel{alg:residual}
-    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
-  }
-  \BlankLine
-  \setstretch{1}
-  \caption{Gradient boosting solution for damped least-squares regression.}
-\end{algorithm}
-
-\citet{friedman2002} suggests that introducing randomness into the fitting
-process can improve convergence of the solution. To achieve this, we randomize
-the order in which the $K$ windows are used in the gradient boosting algorithm.
-
-The $\mathbf{A}_k$ matrices have only $N \times M_k$ elements, which can be
-considerably smaller than the $N \times M$ elements of $\mathbf{A}$.
-Therefore, the gradient boosting method allows us to fit
-equivalent sources models that would produce Jacobian matrices that are larger
-than the available computer memory.
-Furthermore, we can increase or decrease the size of the overlapping windows as
-needed depending on the number of sources in the model and the available
-computer memory.
-
-We can improve the efficiency of the algorithm further by using only data
-points that fall within the $k$-th window for fitting the sources
-(steps \ref{alg:scale} and \ref{alg:fit}),
-while using all available data when calculating the step size and residuals
-(steps \ref{alg:stepsize} and \ref{alg:residual}).
-By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
-elements.
-The forward modeling operations performed in steps \ref{alg:stepsize} and
-\ref{alg:residual} can be done by a summation
-(TODO: ADD EQUATION)
-instead of a matrix-vector product, which allows us to avoid storing the larger
-$N \times M_k$ Jacobian.
-The influence of distance sources on the solution is maintained by using the
-entire set of data points when updating the residuals vector.
-
-The step size parameter functions as scaling factor that prevents the algorithm
-from worsening the fit to data points outside of the current window.
-As such, it improves the converge of the solution and ensures that the
-overall misfit decreases with iteration.
-The step size that minimizes the misfit function in step \ref{alg:stepsize} of
-the algorithm is
-
-\begin{equation}
-    \alpha_k = \frac{
-      \mathbf{r}_{k-1}\trans \mathbf{A}_k \hat{\mathbf{c}}_k
-    }{
-      \hat{\mathbf{c}}_k\trans\mathbf{A}_k\trans \mathbf{A}_k \hat{\mathbf{c}}_k
-    }.
-\end{equation}
-
-After all $\alpha_k$ step sizes and $\hat{\mathbf{c}}_k$ coefficients vectors
-are estimated, we can predict the effect of the additive equivalent source
-model on any point through the summation
-
-\begin{equation}
-    d(\mathbf{p}) =
-    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
-    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
-    \ .
-\end{equation}
-
-SOMETHING ABOUT THE VON FRESE 88 PAPER (BOOTSTRAP INVERSION) AND HOW THIS IS
-DIFFERENT.
-
-\subsection{Source distributions}
-
-How to choose how many sources to use and where to locate them are not
-trivial decisions that play an important role on the accuracy of the
-predictions and the computational resources needed to fit the sources'
-coefficients.
-
-The chosen distribution of sources should simultaneously reproduce the measured
-data on the survey points and be able to make accurate predictions of the
-measured harmonic field on non observed locations.
-
-A high number of sources homogeneously distributed on the survey region are
-capable of reproducing the observed data. Nevertheless, too many sources will
-make the Jacobian matrix too large, what could introduce computational problems
-like the inability of storing the matrix on memory or a high computational time
-needed to fit the sources' coefficients.
-On the other hand, using very few sources will undoubtedly reduce the memory
-needs and lower the computational time when fitting the sources' coefficients.
-Nevertheless, it could be incapable of making accurate predictions or even
-reproducing the measured data if the number of sources is too low.
-
-The choice of the source distribution could also depend on the characteristic
-of the survey and how the observation points are distributed on the region.
-A ground survey usually consists in observation points located along irregular
-paths plus some possible scattered points.
-The survey region is usually heterogeneously covered, leaving areas without any
-observation.
-On the other hand, an airborne survey consists in observation points located
-along almost straight flight lines. The measurements are usually taken at
-a high frequency, so the observation points along the flight lines are very
-close to each other.
-This creates an anisotropy on the observation points: there are much more
-observation points along the flight lines directions.
-
-The most widely used source distributions are: a regular grid of point sources
-and one point source beneath each observation point.
-
-The \emph{regular grid} creates an homogeneous distribution of point sources
-below the surveyed region.
-The distance between sources is controlled by the grid spacing parameter.
-Keeping the boundaries of the grid constant, reducing the spacing increases the
-number of sources.
-
-The \emph{source below data} layout locates one source below each
-observation point, therefore the number of sources will be equal to the number
-of data points.
-
-When working with ground surveys, the \emph{regular grid} needs the grid
-spacing to be sufficiently small so observed values can be accurately
-reproduced by the source distribution.
-This will create too many sources on areas where no observation has been
-carried out.
-In contrast, the \emph{source below data} layout is more likely to accurately
-fit the observed data with much less sources, reducing the computational load
-to fit the equivalent sources' coefficients.
-
-When working with airborne surveys, the \emph{source below data} may
-generate an anisotropic distribution of sources by locating too many sources
-along the flight paths.
-It could lead to unwanted aliases on the predicted values.
-In contrast, the \emph{regular grid} won't generate aliases by homogeneously
-locating sources.
-
-We propose a new source distribution that could simultaneously reduce the
-computational load and remove the drawbacks of the preceding ones: the
-\emph{block averaged sources}.
-It consist in:
-
+\subsection{Location of sources}
+
+The ideal number of sources and their locations, both horizontally and
+vertically, has been debated since the inception of the equivalent source
+technique with \citet{dampney1969}.
+The choices made regarding these parameters can play an important role on the
+accuracy of the predictions and the computational resources needed to estimate
+the coefficients.
+An ideal distribution of sources should simultaneously be able to reproduce the
+measured data on the survey points and also be able to make accurate
+predictions on non-observed locations.
+
+A large number of sources evenly distributed along the survey region are
+capable of reproducing the observed data. Nevertheless, the computational load
+can be prohibitive and such underdetermined problems are prone to overfiting
+the data, leading to poor performance when making predictions. On the other
+hand, using very few sources will undoubtedly reduce the computational
+requirements but the equivalent source model could be incapable of reproducing
+the measured data, leading to inaccurate predictions.
+
+Particular survey characteristics also play a role in the choice of source
+distribution.
+In a ground survey, observation points are usually located along irregular
+paths as well as some possible scattered points.
+The coverage of the survey region is usually uneven, often leaving large areas
+without any observation.
+On the other hand, observations from airborne surveys are located along almost
+straight flight lines.
+Measurements are usually taken at
+a high temporal frequency, leading to the observation points along the flight
+lines that are several times closer than the flight line spacing.
+This creates an anisotropy in the sampling, which can cause aliasing artifacts
+in gridded products.
+
+\subsubsection{Horizontal layout}
+
+The most widely used layouts of equivalent sources are:
+
+\begin{itemize}
+  \item
+    \emph{Regular grid}: a homogeneous distribution of point sources below the
+    survey region at a constant depth. A padding region is often added to help
+    reduce edge effect. In practice, often leads to underdetermined problems
+    ($N<M$).
+  \item
+    \emph{Sources below data}: one equivalent source is placed below each
+    observation point at a given depth (often dependent on the distance to
+    neighboring data points). Therefore, the number of sources is be equal to
+    the number of observations ($N=M$).
+\end{itemize}
+
+For ground surveys, the \emph{regular-grid} layout needs a sufficiently
+small grid spacing to be able to fit the observed data.
+This creates an unnecessarily large number of sources in areas where no
+observations exist.
+In contrast, the \emph{sources-below-data} layout is more likely to accurately
+fit the observed data with many fewer sources, reducing the computational load.
+
+For airborne surveys, the \emph{source-below-data} layout may
+place an undesirably large number of sources along the flight paths.
+This could lead to aliasing effects on the predicted values, such as the
+stripes parallel to flight lines that are often observed when griding airborne
+magnetic data.
+In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
+distributing sources and using a continuous source layer (e.g.,
+right-rectangular prisms or tesseroids).
+
+We propose a new source layout that could simultaneously reduce the
+computational load and remove some of the drawbacks of the regular-grid and
+source-below-data layouts:
+
+\begin{itemize}
+  \item
+    \emph{Block-averaged sources}: point sources are placed in the average
+    position of data points that fall within specified spatial blocks
+    (Fig.~\ref{fig:block-averaged-sources}). In
+    short, this is done by:
     \begin{enumerate}
-    \item Dividing the region in blocks of equal size. The size of the blocks
-        is controlled by a \emph{spacing} parameter.
-        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
-    \item Computing the median location of the observation points that fall
+        \item Dividing the survey region in blocks of equal size
+            (Fig.~\ref{fig:block-averaged-sources}a-b).
+        \item Computing the median position of the observation points that fall
           inside each block. Blocks without any observation point are ignored.
-    \item Locating one point source below each block averaged coordinate.
-        (see Fig.~\ref{fig:block-averaged-sources}(c)).
+        \item Assign one point source to the computed median position, shifted
+          to a specified depth (Fig.~\ref{fig:block-averaged-sources}c).
     \end{enumerate}
-
-The number of sources created by this new distribution will be less or equal to
-the ones created by the \emph{source below data} and the \emph{regular
-grid} with the same spacing.
-Moreover, the sources are only located beneath populated blocks, so sources
-will be concentrated on regions where data has been gathered and no anisotropic
-distribution of sources will be generated.
+\end{itemize}
+
+The number of sources created by this new layout will be less than or equal to
+(if the blocks contain a single data point)
+the number of observations.
+The overdetermined problems that arise from this layout have a lower
+computational load and are less prone to overfiting since the complexity of the
+model is lower.
+Moreover, the block averaging process can balance the spacing between sources
+along a flight line and between adjacent lines.
+
+Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
+observation points that simulates a ground survey, and the possible location of
+sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
+averaged sources} and (d) the \emph{grid sources} layouts.
 
@@
 
-Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
-observation points that simulates a ground survey, and the possible location of
-sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
-averaged sources} and (d) the \emph{grid sources} layouts.
-
 \begin{figure*}
@@
 \end{figure*}
+
+\subsubsection{Depth of sources}
 
@@
 \end{table*}
+
+\subsection{Gradient boosted equivalent sources}
+
+Reducing the number of sources might help to lower the amount of computer
+memory needed to fit their coefficients, although it may be not enough for
+a very large set of observation points.
+Even if we can greatly reduce the number of sources, having too many data
+points would still produce a Jacobian matrix large enough that cannot fit in
+memory.
+This problem was already faced by other authors
+\citep{mendonca1994, leao1989, li2010, barnes2011, oliveira2013, siqueira2017,
+jirigalatu2019}.
+The iterative method proposed by \citet{siqueira2017} needs equivalent sources
+to be located beneath each observation point, so it cannot take advantage of
+the block-averaged sources.
+\citet{leao1989} perform the fitting simultaneously with the prediction, what
+prevents us to use already fitted equivalent sources to make future
+predictions. Besides the method is limited to interpolations on regular grids.
+% Add more discussion on why we won't apply any of the following methods
+\citet{mendonca1994}
+\citet{li2010}
+\citet{barnes2011}
+\citet{jirigalatu2019}
+
+Here we propose an iterative algorithm for fitting the source coefficients
+using a gradient boosting \citep{friedman2001, friedman2002} strategy:
+(i) define a collection of overlapping windows of equal size that cover the
+survey area,
+(ii) define one set of equivalent sources per window,
+(iii) iteratively fit the coefficients of each set of sources.
+Once every set of sources is fitted, we can predict the value of the field on
+any observation point as the effect of every set of equivalent sources.
+
+Lets assume we have $N$ measurements of a harmonic field on observations points
+$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
+\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
+$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
+coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
+different sets of equivalent sources: we define $K$ overlapping windows of
+equal size that cover the whole observation area, and then we create one set of
+equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
+sources that fall inside the $k$-th window.
+The observed data should be equal to the superposition of the
+effect of every set of equivalent sources:
+
+\begin{equation}
+    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k,
+\end{equation}
+
+\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
+set of equivalent sources; $\mathbf{A}_k$ is the Jacobian matrix between
+those sources and every data point; and each $\alpha_k$ is a constant called
+\emph{step-size parameter}.
+
+By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
+iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
+with the observed data) is used to fit the $\mathbf{c}_k$
+coefficients and $\alpha_k$ step-size parameter, and then updated by removing
+the effect of the same sources, as follows:
+
+\begin{equation}
+    \mathbf{r}_0 = \mathbf{d},
+\end{equation}
+
+\begin{equation}
+    \mathbf{r}_k = \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k.
+    \label{eq:residue}
+\end{equation}
+
+\noindent On each iteration the $\mathbf{c}_k$ vector and the $\alpha_k$
+parameter can be fitted so they minimize the misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+\noindent following the same method described on Section
+\ref{sec:eql-inversion}.
+Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
+adjusting the size of the overlapping windows can help in reducing the computer
+memory needed to fit the source coefficients.
+Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
+matrices large enough that they cannot be stored in memory, we can apply one
+more simplification on the fitting process: ignore the effect of the $k$-th
+sources on any observation point that falls outside the $k$-th window.
+
+Assuming that there are $N_k$ observation points that fall under the $k$-th
+window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
+misfit function:
+
+\begin{equation}
+    \phi(\mathbf{c}_k) =
+        \left\lVert
+            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
+\end{equation}
+
+\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
+only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
+observation points that fall under the $k$-th window; and
+$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
+and the $k$-th sources.
+Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
+elements, the computer memory needed for fitting the $\mathbf{c}_k$
+coefficients is greatly reduced.
+
+Once the $\mathbf{c}_k$ coefficients are fitted following the same method
+described on Section \ref{sec:eql-inversion}, we need to obtain the value
+of the step-size parameter $\alpha_k$.
+This can be achieved by minimizing the norm of the difference between the
+previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
+every observation point:
+
+\begin{equation}
+    \alpha_k = \underset{\alpha}{\mathrm{argmin}}
+    \left(
+        \left\lVert
+            \mathbf{r}_{k-1} - \alpha \mathbf{A}_k \mathbf{c}_k
+        \right\rVert ^ 2
+    \right),
+\end{equation}
+
+\noindent which leads to:
+
+\begin{equation}
+    \alpha_k = \frac{
+        \mathbf{r}_{k-1}^T \mathbf{A}_k \mathbf{c}_k
+    }{
+        \left(\mathbf{A}_k \mathbf{c}_k\right)^T \mathbf{A}_k \mathbf{c}_k
+    }.
+\end{equation}
+
+This step will improve the convergence of the iterative algorithm and also will
+introduce at some extent the effect of the $k$-th sources on every data point,
+which was neglected on the fitting of the $\mathbf{c}_k$ coefficients.
+
+Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
+fitted, equation \ref{eq:residue} is applied to update the residue: compute the
+effect of the sources belonging to the $k$-th window on every observation
+point. Worth noting that when calculating the effect of any number of sources
+we don't need to pre-compute the entire Jacobian matrix: we can calculate the
+effect of the sources on each observation point by a simple addition of terms,
+what means computing each Jacobian element at once when needed.
+
+Because the number of windows is fixed before starting the iteration process,
+its number of steps are also fixed to $K$. Moreover, the windows are randomly
+shuffled before starting the process to prevent the prioritization of clustered
+sets of equivalent sources.
+
+After all $\alpha_k$ parameters and $\mathbf{c}_k$ coefficients vectors are
+fitted, we can predict the effect of every equivalent source on any point as
+follows:
+
+\begin{equation}
+    V(\mathbf{p}) =
+    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
+    \frac{\alpha_k {c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
+\end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-12-15 manuscript/manuscript.tex
Apply comments from Santiago
Made slight changes to the suggestions

Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
 \newcommand{\inv}{^{\text{-}1}}
-\newcommand{\trans}{^{\text{T}}}
 
@@
 
-\section{The equivalent sources technique}
-
-The Green's equivalent layer theorem states that any harmonic potential field
-generated by any three dimensional physical-property distribution can by
-reproduced by a continuous two dimensional surface distribution.
-This introduces an ambiguity on the distribution that generates
-a potential field: multiple physical-property distributions can generate the
-same potential field.
-This represents an obstacle for determining the true shape and
-physical-property distribution that generates any measured potential field.
-Nevertheless this ambiguity can also be exploited for developing pre-processing
-techniques like interpolating potential field data.
-
-Approximating the continuous distribution by a finite and discrete density
-distribution is the basis of the \emph{equivalent sources technique}
-\citep{dampney1969}.
-The most common approach is to make use of a set of point sources (the
-\emph{equivalent sources}) located beneath the observation points.
-
-A classical approach for applying the equivalent sources technique would be to
-propose a set of point sources that generate the same harmonic field that has
-been measured.
-Lets consider a set of gravity acceleration measurements $g_z$ on points
-$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$ and a set of point sources with mass
-$\{m_1, \ldots, m_M\}$ located on points
-$\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$.
-The point sources must generate the same gravity field as the one measured:
-
-\begin{equation}
-    g_z(\mathbf{p}) = \mathbf{A} \mathbf{m},
-    \label{eq:linear-problem-g}
-\end{equation}
-
-\noindent where $g_z(\mathbf{p})$ is the vector containing the measured
-field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
-masses of the point sources and $\mathbf{A}$ a matrix whose
-elements can be obtained as the vertical component of the gravitational
-acceleration measured on $\mathbf{p}$ due to the point mass on $\mathbf{q}$:
-
-\begin{equation}
-    a_{ij} = G \frac{(z_i - z_j)}{|\mathbf{p}_i - \mathbf{q}_j|^3},
-\end{equation}
-
-\noindent where
-$G = \SI{6.674e-11}{\cubic\meter\per\kilogram\per\second\squared}$ is the
-universal gravitational constant, $z_i$ and $z_j$ are the vertical components
-of the $\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
-
-By solving equation~\ref{eq:linear-problem-g} we can obtain the values of
-$\mathbf{m}$ that better reproduce the measured field.
-This source distribution along with the fitted masses can be used to predict
-gravity values on any point where the potential field has not been measured.
-
-\subsection{Generalized equivalent sources}
-
-It's possible to generalize the equivalent sources technique to any harmonic
-field through a Green's function problem, regardless the nature of the field.
-
-By definition, any harmonic field $V$ must satisfy the Laplace's equation:
-
-\begin{equation}
-    \nabla^2 V = 0.
-\end{equation}
-
-Considering as boundary condition that $V$ is equal to zero at infinity, then
-its fundamental solution $\psi$ (also known as Green's function or radial basis
-function) must satisfy \citep[p.~210]{vladimirov1979}:
-
-\begin{equation}
-    \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
-        - 4\pi \delta(\mathbf{p}, \mathbf{q}),
-\end{equation}
-
-\noindent where $\delta(\mathbf{p}, \mathbf{q})$ is the Dirac's delta function
-and $\nabla_\mathbf{p}$ symbolize the Nabla operator applied on the coordinates
-$\mathbf{p}$.
-
-The fundamental solution of any harmonic field can be obtained as follows
-\citep[p.~37]{blakely1995}:
-
-\begin{equation}
-    \psi(\mathbf{p}, \mathbf{q})
+\section{Methodology}
+
+\subsection{The equivalent sources technique}
+
+Here, we will follow the ``generalized equivalent sources'' of
+\citet{cordell1992} and assume that any harmonic function $d(\mathbf{p})$ can
+be approximated by a sum of $M$ discrete point source effects
+
+\begin{equation}
+    d(\mathbf{p})
     =
-    \int
-    \frac{\delta(\mathbf{p}, \mathbf{q})}{|\mathbf{p} - \mathbf{q}|}
-    \textrm{d}v
+    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p} - \mathbf{q}_j
+    \right\rVert} \ ,
+    \label{eq:eql-forward}
+\end{equation}
+
+\noindent in which
+$\mathbf{p}$ and $\mathbf{q}_j$ are position vectors in a 3D Cartesian space,
+$c_j$ is a scalar coefficient related to the point source located at
+$\mathbf{q}_j$,
+and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.
+
+In case we have measured the value of the harmonic field on $N$ points
+$\{\mathbf{p}_1\ \mathbf{p}_2\ \ldots\ \mathbf{p}_N\}$,
+we can write a set of $N$ equations of the form
+
+\begin{equation}
+    d_i
     =
-    \frac{1}{|\mathbf{p} - \mathbf{q}|}.
-\end{equation}
-
-This shows that the Green's function associated with any harmonic field is
-equal to the inverse of the Euclidean distance between the evaluation and the
-source points.
-Thus any harmonic field $V$ can be expressed as \citep[p.~37]{blakely1995}:
-
-\begin{equation}
-    V(\mathbf{p})
-    =
-    \int \psi(\mathbf{p}, \mathbf{q}) \rho(\mathbf{q}) d\mathbf{q}
-    =
-    \int \frac{\rho(\mathbf{q})}{|\mathbf{p} - \mathbf{q}|}  d\mathbf{q},
-\end{equation}
-
-\noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
-physical-property evaluated on the point $\mathbf{q}$. Following
-\citet{dampney1969}, this density distribution can be approximated by a finite
-and discrete set of point sources located on $\{\mathbf{q}_1, \ldots,
-\mathbf{q}_M\}$:
-
-\begin{equation}
-    \rho(\mathbf{q}) =
-        \sum\limits_{j=1}^{M} c_j \delta(\mathbf{q} - \mathbf{q_j}),
-\end{equation}
-
-\noindent where $c_j$ is a coefficient related to the point source located on
-$\mathbf{q}_j$, with the same units as the physical-property.
-Then the harmonic field $V$ can be approximated by:
-
-\begin{equation}
-    V(\mathbf{p})
-    =
-    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
-    \label{eq:eql-field}
-\end{equation}
-
-In case we have measured the value of the harmonic field on points
-$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$, we can adjust the values of the $c$
-coefficients so they satisfy:
-
-\begin{equation}
-    V(\mathbf{p}_i)
-    =
-    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p}_i - \mathbf{q}_j|}
-    \quad \forall i=1,\ldots,N.
-\end{equation}
-
-This system of linear equations can be written in an more algebraic way:
-
-\begin{equation}
-    \mathbf{d} = \mathbf{A} \mathbf{c}
+    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p}_i - \mathbf{q}_j
+    \right\rVert}
+    \quad \forall i=1,2,\ldots,N
+    \ ,
+\end{equation}
+
+\noindent where $d_i$ is the value of the potential field at the observation point $\mathbf{p}_i$.
+These equations can also be expressed as
+
+\begin{equation}
+    \mathbf{d} = \mathbf{A} \mathbf{c} \ ,
     \label{eq:linear-problem}
@@
 
-\noindent where $\mathbf{d}$ is a vertical vector containing the measured
-values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
-containing the $c$ coefficients and $\mathbf{A}$ is the \emph{Jacobian matrix},
-whose elements are defined as the Green's function evaluated on each pair of
-points $\mathbf{p}$ and $\mathbf{q}$:
-
-\begin{equation}
-    a_{ij}
-    =
-    \psi(\mathbf{p}_i, \mathbf{q}_j)
-    =
-    \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|}
-\end{equation}
-
-By solving equation~\ref{eq:linear-problem} we can obtain the values of
-$\mathbf{c}$ that better reproduce the measured field.
-Then they can be used to predict the value of the harmonic field on any other
-point where no measurement has been taken by evaluating
-equation~\ref{eq:eql-field}.
+\noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
+values of the observed field at the observation points ${\mathbf{p}_i}_{i=1}^N$,
+$\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,
+and $\mathbf{A}$ is the $N \times M$ Jacobian matrix,
+whose elements are
+
+\begin{equation}
+    a_{ij} = \frac{1}{\left\lVert\mathbf{p}_i - \mathbf{q}_j\right\rVert}
+\end{equation}
+
+For a given set of $N$ observed field values $\mathbf{d}^o$,
+we can find a least-squares solution to
+equation~\ref{eq:linear-problem} and obtain the values of
+$\mathbf{c}$ that best fit the observations.
+These values can, in turn, be used to predict the value of the harmonic field
+at any other point outside of the sources by evaluating
+equation~\ref{eq:eql-forward}.
+Gridding and upward continuation can thus be achieved by predicting values on
+points that fall on a regular grid or at different heights.
 
@@
 
-\subsection{Location of sources}
-
-The ideal number of sources and their locations, both horizontally and
-vertically, has been debated since the inception of the equivalent source
-technique with \citet{dampney1969}.
-The choices made regarding these parameters can play an important role on the
-accuracy of the predictions and the computational resources needed to estimate
-the coefficients.
-An ideal distribution of sources should simultaneously be able to reproduce the
-measured data on the survey points and also be able to make accurate
-predictions on non-observed locations.
-
-A large number of sources evenly distributed along the survey region are
-capable of reproducing the observed data. Nevertheless, the computational load
-can be prohibitive and such underdetermined problems are prone to overfiting
-the data, leading to poor performance when making predictions. On the other
-hand, using very few sources will undoubtedly reduce the computational
-requirements but the equivalent source model could be incapable of reproducing
-the measured data, leading to inaccurate predictions.
-
-Particular survey characteristics also play a role in the choice of source
-distribution.
-In a ground survey, observation points are usually located along irregular
-paths as well as some possible scattered points.
-The coverage of the survey region is usually uneven, often leaving large areas
-without any observation.
-On the other hand, observations from airborne surveys are located along almost
-straight flight lines.
-Measurements are usually taken at
-a high temporal frequency, leading to the observation points along the flight
-lines that are several times closer than the flight line spacing.
-This creates an anisotropy in the sampling, which can cause aliasing artifacts
-in gridded products.
-
-\subsubsection{Horizontal layout}
-
-The most widely used layouts of equivalent sources are:
-
-\begin{itemize}
-  \item
-    \emph{Regular grid}: a homogeneous distribution of point sources below the
-    survey region at a constant depth. A padding region is often added to help
-    reduce edge effect. In practice, often leads to underdetermined problems
-    ($N<M$).
-  \item
-    \emph{Sources below data}: one equivalent source is placed below each
-    observation point at a given depth (often dependent on the distance to
-    neighboring data points). Therefore, the number of sources is be equal to
-    the number of observations ($N=M$).
-\end{itemize}
-
-For ground surveys, the \emph{regular-grid} layout needs a sufficiently
-small grid spacing to be able to fit the observed data.
-This creates an unnecessarily large number of sources in areas where no
-observations exist.
-In contrast, the \emph{sources-below-data} layout is more likely to accurately
-fit the observed data with many fewer sources, reducing the computational load.
-
-For airborne surveys, the \emph{source-below-data} layout may
-place an undesirably large number of sources along the flight paths.
-This could lead to aliasing effects on the predicted values, such as the
-stripes parallel to flight lines that are often observed when griding airborne
-magnetic data.
-In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
-distributing sources and using a continuous source layer (e.g.,
-right-rectangular prisms or tesseroids).
-
-We propose a new source layout that could simultaneously reduce the
-computational load and remove some of the drawbacks of the regular-grid and
-source-below-data layouts:
-
-\begin{itemize}
-  \item
-    \emph{Block-averaged sources}: point sources are placed in the average
-    position of data points that fall within specified spatial blocks
-    (Fig.~\ref{fig:block-averaged-sources}). In
-    short, this is done by:
+\subsection{Source distributions}
+
+How to choose how many sources to use and where to locate them are not
+trivial decisions that play an important role on the accuracy of the
+predictions and the computational resources needed to fit the sources'
+coefficients.
+
+The chosen distribution of sources should simultaneously reproduce the measured
+data on the survey points and be able to make accurate predictions of the
+measured harmonic field on non observed locations.
+
+A high number of sources homogeneously distributed on the survey region are
+capable of reproducing the observed data. Nevertheless, too many sources will
+make the Jacobian matrix too large, what could introduce computational problems
+like the inability of storing the matrix on memory or a high computational time
+needed to fit the sources' coefficients.
+On the other hand, using very few sources will undoubtedly reduce the memory
+needs and lower the computational time when fitting the sources' coefficients.
+Nevertheless, it could be incapable of making accurate predictions or even
+reproducing the measured data if the number of sources is too low.
+
+The choice of the source distribution could also depend on the characteristic
+of the survey and how the observation points are distributed on the region.
+A ground survey usually consists in observation points located along irregular
+paths plus some possible scattered points.
+The survey region is usually heterogeneously covered, leaving areas without any
+observation.
+On the other hand, an airborne survey consists in observation points located
+along almost straight flight lines. The measurements are usually taken at
+a high frequency, so the observation points along the flight lines are very
+close to each other.
+This creates an anisotropy on the observation points: there are much more
+observation points along the flight lines directions.
+
+The most widely used source distributions are: a regular grid of point sources
+and one point source beneath each observation point.
+
+The \emph{regular grid} creates an homogeneous distribution of point sources
+below the surveyed region.
+The distance between sources is controlled by the grid spacing parameter.
+Keeping the boundaries of the grid constant, reducing the spacing increases the
+number of sources.
+
+The \emph{source below data} layout locates one source below each
+observation point, therefore the number of sources will be equal to the number
+of data points.
+
+When working with ground surveys, the \emph{regular grid} needs the grid
+spacing to be sufficiently small so observed values can be accurately
+reproduced by the source distribution.
+This will create too many sources on areas where no observation has been
+carried out.
+In contrast, the \emph{source below data} layout is more likely to accurately
+fit the observed data with much less sources, reducing the computational load
+to fit the equivalent sources' coefficients.
+
+When working with airborne surveys, the \emph{source below data} may
+generate an anisotropic distribution of sources by locating too many sources
+along the flight paths.
+It could lead to unwanted aliases on the predicted values.
+In contrast, the \emph{regular grid} won't generate aliases by homogeneously
+locating sources.
+
+We propose a new source distribution that could simultaneously reduce the
+computational load and remove the drawbacks of the preceding ones: the
+\emph{block averaged sources}.
+It consist in:
+
 \begin{enumerate}
-        \item Dividing the survey region in blocks of equal size
-            (Fig.~\ref{fig:block-averaged-sources}a-b).
-        \item Computing the median position of the observation points that fall
+    \item Dividing the region in blocks of equal size. The size of the blocks
+        is controlled by a \emph{spacing} parameter.
+        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
+    \item Computing the median location of the observation points that fall
         inside each block. Blocks without any observation point are ignored.
-        \item Assign one point source to the computed median position, shifted
-          to a specified depth (Fig.~\ref{fig:block-averaged-sources}c).
+    \item Locating one point source below each block averaged coordinate.
+        (see Fig.~\ref{fig:block-averaged-sources}(c)).
 \end{enumerate}
-\end{itemize}
-
-The number of sources created by this new layout will be less than or equal to
-(if the blocks contain a single data point)
-the number of observations.
-The overdetermined problems that arise from this layout have a lower
-computational load and are less prone to overfiting since the complexity of the
-model is lower.
-Moreover, the block averaging process can balance the spacing between sources
-along a flight line and between adjacent lines.
-
-Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
-observation points that simulates a ground survey, and the possible location of
-sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
-averaged sources} and (d) the \emph{grid sources} layouts.
+
+The number of sources created by this new distribution will be less or equal to
+the ones created by the \emph{source below data} and the \emph{regular
+grid} with the same spacing.
+Moreover, the sources are only located beneath populated blocks, so sources
+will be concentrated on regions where data has been gathered and no anisotropic
+distribution of sources will be generated.
 
@@
 \end{figure*}
-
-\subsubsection{Depth of sources}
 

### 2020-12-15 manuscript/manuscript.tex
Don't include definition of observation points a second time

@@
 \noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
-values of the observed field at the observation points ${\mathbf{p}_i}_{i=1}^N$,
+values of the observed field at the observation points,
 $\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,

### 2020-12-15 manuscript/manuscript.tex
Apply suggestions from code review
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
 \documentclass[twocolumn]{article}
-%\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
+\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
 \setlength{\columnsep}{2\columnsep}
@@
 in a computer program, limiting their wider adoption.
-
 In the present study,
@@
 
-\section{Methodology}
-
-\subsection{The equivalent sources technique}
-
-Here, we will follow the ``generalized equivalent sources'' of
-\citet{cordell1992} and assume that any harmonic function $d(\mathbf{p})$ can
-be approximated by a sum of $M$ discrete point source effects
-
-\begin{equation}
-    d(\mathbf{p})
+\section{The equivalent sources technique}
+
+The Green's equivalent layer theorem states that any harmonic potential field
+generated by any three dimensional physical-property distribution can by
+reproduced by a continuous two dimensional surface distribution.
+This introduces an ambiguity on the distribution that generates
+a potential field: multiple physical-property distributions can generate the
+same potential field.
+This represents an obstacle for determining the true shape and
+physical-property distribution that generates any measured potential field.
+Nevertheless this ambiguity can also be exploited for developing pre-processing
+techniques like interpolating potential field data.
+
+Approximating the continuous distribution by a finite and discrete density
+distribution is the basis of the \emph{equivalent sources technique}
+\citep{dampney1969}.
+The most common approach is to make use of a set of point sources (the
+\emph{equivalent sources}) located beneath the observation points.
+
+A classical approach for applying the equivalent sources technique would be to
+propose a set of point sources that generate the same harmonic field that has
+been measured.
+Lets consider a set of gravity acceleration measurements $g_z$ on points
+$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$ and a set of point sources with mass
+$\{m_1, \ldots, m_M\}$ located on points
+$\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$.
+The point sources must generate the same gravity field as the one measured:
+
+\begin{equation}
+    g_z(\mathbf{p}) = \mathbf{A} \mathbf{m},
+    \label{eq:linear-problem-g}
+\end{equation}
+
+\noindent where $g_z(\mathbf{p})$ is the vector containing the measured
+field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
+masses of the point sources and $\mathbf{A}$ a matrix whose
+elements can be obtained as the vertical component of the gravitational
+acceleration measured on $\mathbf{p}$ due to the point mass on $\mathbf{q}$:
+
+\begin{equation}
+    a_{ij} = G \frac{(z_i - z_j)}{|\mathbf{p}_i - \mathbf{q}_j|^3},
+\end{equation}
+
+\noindent where
+$G = \SI{6.674e-11}{\cubic\meter\per\kilogram\per\second\squared}$ is the
+universal gravitational constant, $z_i$ and $z_j$ are the vertical components
+of the $\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
+
+By solving equation~\ref{eq:linear-problem-g} we can obtain the values of
+$\mathbf{m}$ that better reproduce the measured field.
+This source distribution along with the fitted masses can be used to predict
+gravity values on any point where the potential field has not been measured.
+
+\subsection{Generalized equivalent sources}
+
+It's possible to generalize the equivalent sources technique to any harmonic
+field through a Green's function problem, regardless the nature of the field.
+
+By definition, any harmonic field $V$ must satisfy the Laplace's equation:
+
+\begin{equation}
+    \nabla^2 V = 0.
+\end{equation}
+
+Considering as boundary condition that $V$ is equal to zero at infinity, then
+its fundamental solution $\psi$ (also known as Green's function or radial basis
+function) must satisfy \citep[p.~210]{vladimirov1979}:
+
+\begin{equation}
+    \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
+        - 4\pi \delta(\mathbf{p}, \mathbf{q}),
+\end{equation}
+
+\noindent where $\delta(\mathbf{p}, \mathbf{q})$ is the Dirac's delta function
+and $\nabla_\mathbf{p}$ symbolize the Nabla operator applied on the coordinates
+$\mathbf{p}$.
+
+The fundamental solution of any harmonic field can be obtained as follows
+\citep[p.~37]{blakely1995}:
+
+\begin{equation}
+    \psi(\mathbf{p}, \mathbf{q})
     =
-    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p} - \mathbf{q}_j
-    \right\rVert} \ ,
-    \label{eq:eql-forward}
-\end{equation}
-
-\noindent in which
-$\mathbf{p}$ and $\mathbf{q}_j$ are position vectors in a 3D Cartesian space,
-$c_j$ is a scalar coefficient related to the point source located at
-$\mathbf{q}_j$,
-and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.
-
-In case we have measured the value of the harmonic field on $N$ points
-$\{\mathbf{p}_1\ \mathbf{p}_2\ \ldots\ \mathbf{p}_N\}$,
-we can write a set of $N$ equations of the form
-
-\begin{equation}
-    d_i
+    \int
+    \frac{\delta(\mathbf{p}, \mathbf{q})}{|\mathbf{p} - \mathbf{q}|}
+    \textrm{d}v
     =
-    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p}_i - \mathbf{q}_j
-    \right\rVert}
-    \quad \forall i=1,2,\ldots,N
+    \frac{1}{|\mathbf{p} - \mathbf{q}|}.
+\end{equation}
+
+This shows that the Green's function associated with any harmonic field is
+equal to the inverse of the Euclidean distance between the evaluation and the
+source points.
+Thus any harmonic field $V$ can be expressed as \citep[p.~37]{blakely1995}:
+
+\begin{equation}
+    V(\mathbf{p})
+    =
+    \int \psi(\mathbf{p}, \mathbf{q}) \rho(\mathbf{q}) d\mathbf{q}
+    =
+    \int \frac{\rho(\mathbf{q})}{|\mathbf{p} - \mathbf{q}|}  d\mathbf{q},
+\end{equation}
+
+\noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
+physical-property evaluated on the point $\mathbf{q}$. Following
+\citet{dampney1969}, this density distribution can be approximated by a finite
+and discrete set of point sources located on $\{\mathbf{q}_1, \ldots,
+\mathbf{q}_M\}$:
+
+\begin{equation}
+    \rho(\mathbf{q}) =
+        \sum\limits_{j=1}^{M} c_j \delta(\mathbf{q} - \mathbf{q_j}),
+\end{equation}
+
+\noindent where $c_j$ is a coefficient related to the point source located on
+$\mathbf{q}_j$, with the same units as the physical-property.
+Then the harmonic field $V$ can be approximated by:
+
+\begin{equation}
+    V(\mathbf{p})
+    =
+    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
+    \label{eq:eql-field}
+\end{equation}
+
+In case we have measured the value of the harmonic field on points
+$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$, we can adjust the values of the $c$
+coefficients so they satisfy:
+
+\begin{equation}
+    V(\mathbf{p}_i)
+    =
+    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p}_i - \mathbf{q}_j|}
+    \quad \forall i=1,\ldots,N.
+\end{equation}
+
+This system of linear equations can be written in an more algebraic way:
+
+\begin{equation}
+    \mathbf{d} = \mathbf{A} \mathbf{c}
+    \label{eq:linear-problem}
+\end{equation}
+
+\noindent where $\mathbf{d}$ is a vertical vector containing the measured
+values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
+containing the $c$ coefficients and $\mathbf{A}$ is the \emph{Jacobian matrix},
+whose elements are defined as the Green's function evaluated on each pair of
+points $\mathbf{p}$ and $\mathbf{q}$:
+
+\begin{equation}
+    a_{ij}
+    =
+    \psi(\mathbf{p}_i, \mathbf{q}_j)
+    =
+    \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|}
+\end{equation}
+
+By solving equation~\ref{eq:linear-problem} we can obtain the values of
+$\mathbf{c}$ that better reproduce the measured field.
+Then they can be used to predict the value of the harmonic field on any other
+point where no measurement has been taken by evaluating
+equation~\ref{eq:eql-field}.
+
+\subsection{Damped least-squares solution}
+\label{sec:eql-inversion}
+
+We can obtain the values of the source coefficients $\mathbf{c}$ that best
+fit the observed field values $\mathbf{d}^o$ by minimizing the goal function
+
+\begin{equation}
+    \phi(\mathbf{c}) =
+    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]\trans
+    \mathbf{W}
+    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]
+    + \lambda_d\ \mathbf{c}\trans\mathbf{c}
     \ ,
-\end{equation}
-
-\noindent where $d_i$ is the value of the potential field at the observation point $\mathbf{p}_i$.
-These equations can also be expressed as
-
-\begin{equation}
-    \mathbf{d} = \mathbf{A} \mathbf{c} \ ,
-    \label{eq:linear-problem}
-\end{equation}
-
-\noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
-values of the observed field at the observation points,
-$\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,
-and $\mathbf{A}$ is the $N \times M$ Jacobian matrix,
-whose elements are
-
-\begin{equation}
-    a_{ij} = \frac{1}{\left\lVert\mathbf{p}_i - \mathbf{q}_j\right\rVert}
-\end{equation}
-
-For a given set of $N$ observed field values $\mathbf{d}^o$,
-we can find a least-squares solution to
-equation~\ref{eq:linear-problem} and obtain the values of
-$\mathbf{c}$ that best fit the observations.
-These values can, in turn, be used to predict the value of the harmonic field
-at any other point outside of the sources by evaluating
-equation~\ref{eq:eql-forward}.
-Gridding and upward continuation can thus be achieved by predicting values on
-points that fall on a regular grid or at different heights.
-
-\subsection{Fitting source coefficients}
-\label{sec:eql-inversion}
-
-Solving equations~\ref{eq:linear-problem-g} and~\ref{eq:linear-problem} is
-equivalent to performing an inversion and thus solving an ill-posed problem by
-nature due to the non-uniqueness and the instability of the possible solutions.
-Therefore is usually needed to add regularization functions in order to obtain
-stable solutions
-(\citealp[p.~52]{menke1989}; \citealp{cooper2000}; \citealp{oliveira2013}).
-
-We can obtain the values of the source coefficients $\mathbf{c}$ that better
-reproduce the measured field by minimizing an objective or misfit function
-$\phi(\mathbf{c})$ through a least squares method:
-
-\begin{equation}
-    \phi(\mathbf{c}) =
-        \left\lVert
-            \mathbf{d} - \mathbf{A}\mathbf{c}
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
     \label{eq:misfit-unscaled}
@@
 
-\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
-and $\lambda_d$ is a \emph{damping} parameter with the same units as the
+\noindent where
+$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
+$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
 Jacobian matrix elements.
-The second term of the equation applies a zeroth-order Tikhonov
-\citep{tikhonov1977} regularization to stabilize the solution.
-
-In order to simplify the choice of the \emph{damping} parameter we scale the
-Jacobian matrix so each column has unit variance.
-We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
-standard deviation of each column of the Jacobian matrix $\mathbf{A}$:
+The second term on the right-hand side of the equation is a zeroth-order
+Tikhonov regularization \citep{tikhonov1977} (also known as a damping
+regularization or ridge regression) that is used to stabilize the solution.
+
+The range of acceptable values for the damping parameter $\lambda_d$ will
+depend on the values of the Jacobian matrix $\mathbf{A}$ and the coefficients.
+Consequently, this range will vary (often dramatically) between datasets,
+making it difficult to choose an appropriate value for $\lambda_d$ in practice.
+
+To solve this issue, we first scale the Jacobian matrix so that its elements
+are unitless and each column has unit variance.
+We define a diagonal matrix $\mathbf{S}$
 
@@
     \begin{bmatrix}
-        \sigma_1 & \cdots &0 \\
-        \vdots & \ddots & \vdots \\
-        0 & \cdots & \sigma_M
-    \end{bmatrix}
+      \sigma_1 & 0 & \cdots &0 \\
+      0 & \sigma_2 & \cdots &0 \\
+      \vdots & \vdots & \ddots & \vdots \\
+      0  & 0 & \cdots & \sigma_M
+    \end{bmatrix}_{M \times M}
     ,
@@
 
-\noindent so equation~\ref{eq:linear-problem} can be written as:
+\noindent in which $\sigma_j$ is the standard deviation of the $j$-th column of
+$\mathbf{A}$.
+We then write the forward problem in equation~\ref{eq:linear-problem} as
 
@@
     =
-    \hat{\mathbf{A}} \hat{\mathbf{c}}
-\end{equation}
-
-\noindent where $\hat{\mathbf{A}}$ is the scaled Jacobian matrix and
-$\hat{\mathbf{c}}$ is a vector containing scaled coefficients.
-
-The misfit function defined on equation~\ref{eq:misfit-unscaled} can be then
-rewritten as follows:
-
-\begin{equation}
-    \phi(\hat{\mathbf{c}}) =
-        \left\lVert \mathbf{d}
-        - \hat{\mathbf{A}}\hat{\mathbf{c}} \right\rVert ^ 2
-        + \lambda \left\lVert \hat{\mathbf{c}} \right\rVert ^2,
+    \mathbf{B} \mathbf{m}
+\end{equation}
+
+\noindent where $\mathbf{B}$ is the scaled and unitless Jacobian matrix and
+$\mathbf{m}$ is a vector containing scaled coefficients with the same units as
+the data.
+
+The goal function defined in equation~\ref{eq:misfit-unscaled} can be
+rewritten as
+
+\begin{equation}
+    \phi(\mathbf{m}) =
+    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]\trans
+    \mathbf{W}
+    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]
+    + \lambda\ \mathbf{m}\trans\mathbf{m}
+    \ ,
     \label{eq:misfit}
@@
 
-\noindent where now $\lambda$ is a \emph{dimensionless} damping parameter.
-
-Misfit function from equation~\ref{eq:misfit} is minimized through Cholesky
-decomposition.
-If the number of observation points is equal or larger to the number of
-sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
-well- or over-determined, respectively. Therefore, the scaled coefficients that
-minimize the misfit function can be obtained through \citep{menke1989}:
-
-\begin{equation}
-    \hat{\mathbf{c}} =
+\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
+regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
+$\mathbf{c}$.
+
+The vector of scaled coefficients $\hat{\mathbf{m}}$ that minimizes the goal
+function can be found by solving the \emph{normal equation system}
+\citep{menke1989}
+
+\begin{equation}
     \left[
-            \hat{\mathbf{A}}^\text{T} \hat{\mathbf{A}}
-            + \lambda^2 \mathbf{I}
-        \right]\inv
-        \hat{\mathbf{A}}^\text{T}
-        \mathbf{d}.
-\end{equation}
-
-On the other hand, if there are more sources than observation points, the
-problem is under-determined and the scaled coefficients can be obtained as
-\citep{menke1989}:
-
-\begin{equation}
-    \hat{\mathbf{c}} =
-    \hat{\mathbf{A}}^\text{T}
-        \left[
-            \hat{\mathbf{A}} \hat{\mathbf{A}}^\text{T}
-            + \lambda^2 \mathbf{I}
-        \right]\inv
-        \mathbf{d}.
-\end{equation}
-
-Once the scaled coefficients are obtained, the sources' coefficients
-$\mathbf{c}$ can be obtained by rescaling
-$\hat{\mathbf{c}}$:
-
-\begin{equation}
-    \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{c}}.
-\end{equation}
+      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
+    \right]
+    \hat{\mathbf{m}} =
+    \mathbf{B}\trans\mathbf{W}
+    \mathbf{d}^o.
+\end{equation}
+
+Once the scaled coefficients are obtained, the estimated unscaled coefficients
+$\hat{\mathbf{c}}$ can be calculated by removing the scaling factor
+
+\begin{equation}
+    \hat{\mathbf{c}} = \mathbf{S}\inv \hat{\mathbf{m}} \ .
+\end{equation}
+
+\noindent The forward modeling operations used to perform predictions
+(e.g., for interpolation and upward continuation) are left unchanged by
+using vector $\hat{\mathbf{c}}$ instead of $\hat{\mathbf{m}}$.
 

### 2020-12-15 manuscript/manuscript.tex

--- 2020-12-15 manuscript/manuscript.tex
@@
     \phi(\mathbf{c}) =
-        \left\lVert
-            \mathbf{d} - \mathbf{A}\mathbf{c}
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
+    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]\trans
+    \mathbf{W}
+    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]
+    + \lambda_d\ \mathbf{c}\trans\mathbf{c}
+    \ ,
     \label{eq:misfit-unscaled}

### 2020-12-15 manuscript/manuscript.tex
Apply Santiago's comments about defining some parameters
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

--- 2020-12-15 manuscript/manuscript.tex
@@
 
-\subsection{Damped least-squares solution}
+\subsection{Fitting source coefficients}
 \label{sec:eql-inversion}
 
-We can obtain the values of the source coefficients $\mathbf{c}$ that best
-fit the observed field values $\mathbf{d}^o$ by minimizing the goal function
+Solving equations~\ref{eq:linear-problem-g} and~\ref{eq:linear-problem} is
+equivalent to performing an inversion and thus solving an ill-posed problem by
+nature due to the non-uniqueness and the instability of the possible solutions.
+Therefore is usually needed to add regularization functions in order to obtain
+stable solutions
+(\citealp[p.~52]{menke1989}; \citealp{cooper2000}; \citealp{oliveira2013}).
+
+We can obtain the values of the source coefficients $\mathbf{c}$ that better
+reproduce the measured field by minimizing an objective or misfit function
+$\phi(\mathbf{c})$ through a least squares method:
 
@@
     \phi(\mathbf{c}) =
-    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]\trans
-    \mathbf{W}
-    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]
-    + \lambda_d\ \mathbf{c}\trans\mathbf{c}
-    \ ,
+        \left\lVert
+            \mathbf{d} - \mathbf{A}\mathbf{c}
+        \right\rVert ^ 2
+        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
     \label{eq:misfit-unscaled}
@@
 
-\noindent where
-$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
-$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
+\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
+and $\lambda_d$ is a \emph{damping} parameter with the same units as the
 Jacobian matrix elements.
-The second term on the right-hand side of the equation is a zeroth-order
-Tikhonov regularization \citep{tikhonov1977} (also known as a damping
-regularization or ridge regression) that is used to stabilize the solution.
-
-The range of acceptable values for the damping parameter $\lambda_d$ will
-depend on the values of the Jacobian matrix $\mathbf{A}$ and the coefficients.
-Consequently, this range will vary (often dramatically) between datasets,
-making it difficult to choose an appropriate value for $\lambda_d$ in practice.
-
-To solve this issue, we first scale the Jacobian matrix so that its elements
-are unitless and each column has unit variance.
-We define a diagonal matrix $\mathbf{S}$
+The second term of the equation applies a zeroth-order Tikhonov
+\citep{tikhonov1977} regularization to stabilize the solution.
+
+In order to simplify the choice of the \emph{damping} parameter we scale the
+Jacobian matrix so each column has unit variance.
+We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
+standard deviation of each column of the Jacobian matrix $\mathbf{A}$:
 
@@
     \begin{bmatrix}
-      \sigma_1 & 0 & \cdots &0 \\
-      0 & \sigma_2 & \cdots &0 \\
-      \vdots & \vdots & \ddots & \vdots \\
-      0  & 0 & \cdots & \sigma_M
-    \end{bmatrix}_{M \times M}
+        \sigma_1 & \cdots &0 \\
+        \vdots & \ddots & \vdots \\
+        0 & \cdots & \sigma_M
+    \end{bmatrix}
     ,
@@
 
-\noindent in which $\sigma_j$ is the standard deviation of the $j$-th column of
-$\mathbf{A}$.
-We then write the forward problem in equation~\ref{eq:linear-problem} as
+\noindent so equation~\ref{eq:linear-problem} can be written as:
 
@@
     =
-    \mathbf{B} \mathbf{m}
-\end{equation}
-
-\noindent where $\mathbf{B}$ is the scaled and unitless Jacobian matrix and
-$\mathbf{m}$ is a vector containing scaled coefficients with the same units as
-the data.
-
-The goal function defined in equation~\ref{eq:misfit-unscaled} can be
-rewritten as
-
-\begin{equation}
-    \phi(\mathbf{m}) =
-    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]\trans
-    \mathbf{W}
-    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]
-    + \lambda\ \mathbf{m}\trans\mathbf{m}
-    \ ,
+    \hat{\mathbf{A}} \hat{\mathbf{c}}
+\end{equation}
+
+\noindent where $\hat{\mathbf{A}}$ is the scaled Jacobian matrix and
+$\hat{\mathbf{c}}$ is a vector containing scaled coefficients.
+
+The misfit function defined on equation~\ref{eq:misfit-unscaled} can be then
+rewritten as follows:
+
+\begin{equation}
+    \phi(\hat{\mathbf{c}}) =
+        \left\lVert \mathbf{d}
+        - \hat{\mathbf{A}}\hat{\mathbf{c}} \right\rVert ^ 2
+        + \lambda \left\lVert \hat{\mathbf{c}} \right\rVert ^2,
     \label{eq:misfit}
@@
 
-\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
-regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
-$\mathbf{c}$.
-
-The vector of scaled coefficients $\hat{\mathbf{m}}$ that minimizes the goal
-function can be found by solving the \emph{normal equation system}
-\citep{menke1989}
-
-\begin{equation}
+\noindent where now $\lambda$ is a \emph{dimensionless} damping parameter.
+
+Misfit function from equation~\ref{eq:misfit} is minimized through Cholesky
+decomposition.
+If the number of observation points is equal or larger to the number of
+sources, then the linear problem defined on equation~\ref{eq:linear-problem} is
+well- or over-determined, respectively. Therefore, the scaled coefficients that
+minimize the misfit function can be obtained through \citep{menke1989}:
+
+\begin{equation}
+    \hat{\mathbf{c}} =
         \left[
-      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
-    \right]
-    \hat{\mathbf{m}} =
-    \mathbf{B}\trans\mathbf{W}
-    \mathbf{d}^o.
-\end{equation}
-
-Once the scaled coefficients are obtained, the estimated unscaled coefficients
-$\hat{\mathbf{c}}$ can be calculated by removing the scaling factor
-
-\begin{equation}
-    \hat{\mathbf{c}} = \mathbf{S}\inv \hat{\mathbf{m}} \ .
-\end{equation}
-
-\noindent The forward modeling operations used to perform predictions
-(e.g., for interpolation and upward continuation) are left unchanged by
-using vector $\hat{\mathbf{c}}$ instead of $\hat{\mathbf{m}}$.
+            \hat{\mathbf{A}}^\text{T} \hat{\mathbf{A}}
+            + \lambda^2 \mathbf{I}
+        \right]\inv
+        \hat{\mathbf{A}}^\text{T}
+        \mathbf{d}.
+\end{equation}
+
+On the other hand, if there are more sources than observation points, the
+problem is under-determined and the scaled coefficients can be obtained as
+\citep{menke1989}:
+
+\begin{equation}
+    \hat{\mathbf{c}} =
+    \hat{\mathbf{A}}^\text{T}
+        \left[
+            \hat{\mathbf{A}} \hat{\mathbf{A}}^\text{T}
+            + \lambda^2 \mathbf{I}
+        \right]\inv
+        \mathbf{d}.
+\end{equation}
+
+Once the scaled coefficients are obtained, the sources' coefficients
+$\mathbf{c}$ can be obtained by rescaling
+$\hat{\mathbf{c}}$:
+
+\begin{equation}
+    \mathbf{c} = \mathbf{S}\inv \hat{\mathbf{c}}.
+\end{equation}
+
+\subsection{Gradient boosting}
+
+Gradient boosting was first introduced by \citet{friedman2001, friedman2002} as
+a method for fitting additive parametric models of the form
+
+\begin{equation}
+  d = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
+\end{equation}
+
+\noindent where $\alpha_k$ is a scalar coefficient called the \emph{step-size}
+and $f$ is a function of the parameter vector $\mathbf{c}_k$.
+For linear regression problems, these additive models can be written as the
+matrix equation
+
+\begin{equation}
+    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k \ .
+    \label{eq:gb-linear-model}
+\end{equation}
+
+We can transform our equivalent source problem in
+equation~\ref{eq:linear-problem} into an additive model by
+(1) defining a set of $K$ overlapping windows of equal size that cover the
+survey area and (2) defining one set of equivalent sources per
+window. Then, the coefficients $\mathbf{c}_k$ relate to the equivalent sources
+of the $k$-th window and $\mathbf{A}_k$ is the Jacobian matrix between
+those sources and every data point.
+Thus, the predicted data are a superposition of the
+effects of the $K$ sets of equivalent sources.
+
+The gradient boosting algorithm above works by fitting each component of the
+additive model, one at a time, to the residuals of the previous component.
+\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
+optimization in the so-called ``function space'', with $\alpha_k$ corresponding
+to step sizes in steepest descent.
+We can modify the gradient boosting algorithm of \citet{friedman2001} to
+find the damped least-squares solutions for the $K$ parameters vectors
+$\mathbf{c}_k$ and step sizes $\alpha_k$ in equation~\ref{eq:gb-linear-model}:
+
+\begin{algorithm}[!h]
+  \DontPrintSemicolon
+  \setstretch{1.5}
+  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
+  \For{ $k = 1$ \KwTo $K$ }{
+
+    \nllabel{alg:scale}
+    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$ \;
+
+    \nllabel{alg:fit}
+    $
+     \hat{\mathbf{m}}_k = \left[\mathbf{B}_k\trans \mathbf{W}_k \mathbf{B}_k +
+     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \mathbf{W}_k
+     \mathbf{r}_{k-1}
+    $ \;
+
+    \nllabel{alg:unscale}
+    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$ \;
+
+    \nllabel{alg:stepsize}
+    $
+      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
+      \left(
+        \left\lVert
+          \mathbf{r}_{k - 1} - \alpha \mathbf{A}_k \hat{\mathbf{c}}_k
+        \right\rVert ^ 2
+      \right)
+    $ \;
+
+    \nllabel{alg:residual}
+    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
+  }
+  \BlankLine
+  \setstretch{1}
+  \caption{Gradient boosting solution for damped least-squares regression.}
+\end{algorithm}
+
+\citet{friedman2002} suggests that introducing randomness into the fitting
+process can improve convergence of the solution. To achieve this, we randomize
+the order in which the $K$ windows are used in the gradient boosting algorithm.
+
+The $\mathbf{A}_k$ matrices have only $N \times M_k$ elements
+(where $M_k$ is the number sources on the $k-$th window), which can be
+considerably smaller than the $N \times M$ elements of $\mathbf{A}$.
+Therefore, the gradient boosting method allows us to fit
+equivalent sources models that would produce Jacobian matrices that are larger
+than the available computer memory.
+Furthermore, we can increase or decrease the size of the overlapping windows as
+needed depending on the number of sources in the model and the available
+computer memory.
+
+We can improve the efficiency of the algorithm further by using only the $N_k$ data
+points that fall within the $k$-th window for fitting the sources
+(steps \ref{alg:scale} and \ref{alg:fit}),
+while using all available data when calculating the step size and residuals
+(steps \ref{alg:stepsize} and \ref{alg:residual}).
+By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
+elements.
+The forward modeling operations performed in steps \ref{alg:stepsize} and
+\ref{alg:residual} can be done by a summation
+(TODO: ADD EQUATION)
+instead of a matrix-vector product, which allows us to avoid computing and
+storing the larger $N \times M_k$ Jacobian at any point.
+The influence of distance sources on the solution is maintained by using the
+entire set of data points when updating the residuals vector.
+
+The step size parameter functions as scaling factor that prevents the algorithm
+from worsening the fit to data points outside of the current window.
+As such, it improves the converge of the solution and ensures that the
+overall misfit decreases with iteration.
+The step size that minimizes the misfit function in step \ref{alg:stepsize} of
+the algorithm is
+
+\begin{equation}
+    \alpha_k = \frac{
+      \mathbf{r}_{k-1}\trans \mathbf{A}_k \hat{\mathbf{c}}_k
+    }{
+      \hat{\mathbf{c}}_k\trans\mathbf{A}_k\trans \mathbf{A}_k \hat{\mathbf{c}}_k
+    }.
+\end{equation}
+
+After all $\alpha_k$ step sizes and $\hat{\mathbf{c}}_k$ coefficients vectors
+are estimated, we can predict the effect of the additive equivalent source
+model on any point through the summation
+
+\begin{equation}
+    d(\mathbf{p}) =
+    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
+    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
+    \ .
+\end{equation}
+
+NOTE: This paragraph might be better in the Discussion section.
+
+Our gradient boosting algorithm for overlapping windows is similar to the
+``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
+fits portions of an equivalent source model to the data residuals.
+The key differences are:
+(1) the sources in the overlapping portions of the windows are fit more than
+once, allowing the algorithm to self-correct for poor solutions to any given
+window;
+(2) using only data points within the window when fitting the data enables the
+use of larger datasets;
+(3) experience shows that the step size parameter improves the convergence of
+the solution, particularly when using only the data inside the windows for
+fitting.
 
@@
 \end{table*}
-
-\subsection{Gradient boosted equivalent sources}
-
-Reducing the number of sources might help to lower the amount of computer
-memory needed to fit their coefficients, although it may be not enough for
-a very large set of observation points.
-Even if we can greatly reduce the number of sources, having too many data
-points would still produce a Jacobian matrix large enough that cannot fit in
-memory.
-This problem was already faced by other authors
-\citep{mendonca1994, leao1989, li2010, barnes2011, oliveira2013, siqueira2017,
-jirigalatu2019}.
-The iterative method proposed by \citet{siqueira2017} needs equivalent sources
-to be located beneath each observation point, so it cannot take advantage of
-the block-averaged sources.
-\citet{leao1989} perform the fitting simultaneously with the prediction, what
-prevents us to use already fitted equivalent sources to make future
-predictions. Besides the method is limited to interpolations on regular grids.
-% Add more discussion on why we won't apply any of the following methods
-\citet{mendonca1994}
-\citet{li2010}
-\citet{barnes2011}
-\citet{jirigalatu2019}
-
-Here we propose an iterative algorithm for fitting the source coefficients
-using a gradient boosting \citep{friedman2001, friedman2002} strategy:
-(i) define a collection of overlapping windows of equal size that cover the
-survey area,
-(ii) define one set of equivalent sources per window,
-(iii) iteratively fit the coefficients of each set of sources.
-Once every set of sources is fitted, we can predict the value of the field on
-any observation point as the effect of every set of equivalent sources.
-
-Lets assume we have $N$ measurements of a harmonic field on observations points
-$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
-\ldots, d_N)\trans$. We have defined a set of $M$ point sources located on
-$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
-coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
-different sets of equivalent sources: we define $K$ overlapping windows of
-equal size that cover the whole observation area, and then we create one set of
-equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
-sources that fall inside the $k$-th window.
-The observed data should be equal to the superposition of the
-effect of every set of equivalent sources:
-
-\begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k,
-\end{equation}
-
-\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
-set of equivalent sources; $\mathbf{A}_k$ is the Jacobian matrix between
-those sources and every data point; and each $\alpha_k$ is a constant called
-\emph{step-size parameter}.
-
-By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
-iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
-with the observed data) is used to fit the $\mathbf{c}_k$
-coefficients and $\alpha_k$ step-size parameter, and then updated by removing
-the effect of the same sources, as follows:
-
-\begin{equation}
-    \mathbf{r}_0 = \mathbf{d},
-\end{equation}
-
-\begin{equation}
-    \mathbf{r}_k = \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k.
-    \label{eq:residue}
-\end{equation}
-
-\noindent On each iteration the $\mathbf{c}_k$ vector and the $\alpha_k$
-parameter can be fitted so they minimize the misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \mathbf{r}_{k-1} - \alpha_k \mathbf{A}_k\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-\noindent following the same method described on Section
-\ref{sec:eql-inversion}.
-Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
-adjusting the size of the overlapping windows can help in reducing the computer
-memory needed to fit the source coefficients.
-Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
-matrices large enough that they cannot be stored in memory, we can apply one
-more simplification on the fitting process: ignore the effect of the $k$-th
-sources on any observation point that falls outside the $k$-th window.
-
-Assuming that there are $N_k$ observation points that fall under the $k$-th
-window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
-misfit function:
-
-\begin{equation}
-    \phi(\mathbf{c}_k) =
-        \left\lVert
-            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
-\end{equation}
-
-\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
-only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
-observation points that fall under the $k$-th window; and
-$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
-and the $k$-th sources.
-Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
-elements, the computer memory needed for fitting the $\mathbf{c}_k$
-coefficients is greatly reduced.
-
-Once the $\mathbf{c}_k$ coefficients are fitted following the same method
-described on Section \ref{sec:eql-inversion}, we need to obtain the value
-of the step-size parameter $\alpha_k$.
-This can be achieved by minimizing the norm of the difference between the
-previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
-every observation point:
-
-\begin{equation}
-    \alpha_k = \underset{\alpha}{\mathrm{argmin}}
-    \left(
-        \left\lVert
-            \mathbf{r}_{k-1} - \alpha \mathbf{A}_k \mathbf{c}_k
-        \right\rVert ^ 2
-    \right),
-\end{equation}
-
-\noindent which leads to:
-
-\begin{equation}
-    \alpha_k = \frac{
-        \mathbf{r}_{k-1}\trans \mathbf{A}_k \mathbf{c}_k
-    }{
-        \left(\mathbf{A}_k \mathbf{c}_k\right)\trans \mathbf{A}_k \mathbf{c}_k
-    }.
-\end{equation}
-
-This step will improve the convergence of the iterative algorithm and also will
-introduce at some extent the effect of the $k$-th sources on every data point,
-which was neglected on the fitting of the $\mathbf{c}_k$ coefficients.
-
-Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
-fitted, equation \ref{eq:residue} is applied to update the residue: compute the
-effect of the sources belonging to the $k$-th window on every observation
-point. Worth noting that when calculating the effect of any number of sources
-we don't need to pre-compute the entire Jacobian matrix: we can calculate the
-effect of the sources on each observation point by a simple addition of terms,
-what means computing each Jacobian element at once when needed.
-
-Because the number of windows is fixed before starting the iteration process,
-its number of steps are also fixed to $K$. Moreover, the windows are randomly
-shuffled before starting the process to prevent the prioritization of clustered
-sets of equivalent sources.
-
-After all $\alpha_k$ parameters and $\mathbf{c}_k$ coefficients vectors are
-fitted, we can predict the effect of every equivalent source on any point as
-follows:
-
-\begin{equation}
-    V(\mathbf{p}) =
-    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
-    \frac{\alpha_k {c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
-\end{equation}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-12-15 manuscript/manuscript.tex

@@
 
-\section{The equivalent sources technique}
-
-The Green's equivalent layer theorem states that any harmonic potential field
-generated by any three dimensional physical-property distribution can by
-reproduced by a continuous two dimensional surface distribution.
-This introduces an ambiguity on the distribution that generates
-a potential field: multiple physical-property distributions can generate the
-same potential field.
-This represents an obstacle for determining the true shape and
-physical-property distribution that generates any measured potential field.
-Nevertheless this ambiguity can also be exploited for developing pre-processing
-techniques like interpolating potential field data.
-
-Approximating the continuous distribution by a finite and discrete density
-distribution is the basis of the \emph{equivalent sources technique}
-\citep{dampney1969}.
-The most common approach is to make use of a set of point sources (the
-\emph{equivalent sources}) located beneath the observation points.
-
-A classical approach for applying the equivalent sources technique would be to
-propose a set of point sources that generate the same harmonic field that has
-been measured.
-Lets consider a set of gravity acceleration measurements $g_z$ on points
-$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$ and a set of point sources with mass
-$\{m_1, \ldots, m_M\}$ located on points
-$\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$.
-The point sources must generate the same gravity field as the one measured:
-
-\begin{equation}
-    g_z(\mathbf{p}) = \mathbf{A} \mathbf{m},
-    \label{eq:linear-problem-g}
-\end{equation}
-
-\noindent where $g_z(\mathbf{p})$ is the vector containing the measured
-field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
-masses of the point sources and $\mathbf{A}$ a matrix whose
-elements can be obtained as the vertical component of the gravitational
-acceleration measured on $\mathbf{p}$ due to the point mass on $\mathbf{q}$:
-
-\begin{equation}
-    a_{ij} = G \frac{(z_i - z_j)}{|\mathbf{p}_i - \mathbf{q}_j|^3},
+\section{Methodology}
+
+\subsection{The equivalent sources technique}
+
+Here, we will follow the ``generalized equivalent sources'' of
+\citet{cordell1992} and assume that any harmonic function $d(\mathbf{p})$ can
+be approximated by a sum of $M$ discrete point source effects
+
+\begin{equation}
+    d(\mathbf{p})
+    =
+    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p} - \mathbf{q}_j
+    \right\rVert} \ ,
+    \label{eq:eql-forward}
+\end{equation}
+
+\noindent in which
+$\mathbf{p}$ and $\mathbf{q}_j$ are position vectors in a 3D Cartesian space,
+$c_j$ is a scalar coefficient related to the point source located at
+$\mathbf{q}_j$,
+and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.
+
+In case we have measured the value of the harmonic field on $N$ points
+$\{\mathbf{p}_1\ \mathbf{p}_2\ \ldots\ \mathbf{p}_N\}$,
+we can write a set of $N$ equations of the form
+
+\begin{equation}
+    d_i
+    =
+    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p}_i - \mathbf{q}_j
+    \right\rVert}
+    \quad \forall i=1,2,\ldots,N
+    \ ,
+\end{equation}
+
+\noindent where $d_i$ is the value of the potential field at the observation point $\mathbf{p}_i$.
+These equations can also be expressed as
+
+\begin{equation}
+    \mathbf{d} = \mathbf{A} \mathbf{c} \ ,
+    \label{eq:linear-problem}
+\end{equation}
+
+\noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
+values of the observed field at the observation points,
+$\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,
+and $\mathbf{A}$ is the $N \times M$ Jacobian matrix,
+whose elements are
+
+\begin{equation}
+    a_{ij} = \frac{1}{\left\lVert\mathbf{p}_i - \mathbf{q}_j\right\rVert}
+\end{equation}
+
+For a given set of $N$ observed field values $\mathbf{d}^o$,
+we can find a least-squares solution to
+equation~\ref{eq:linear-problem} and obtain the values of
+$\mathbf{c}$ that best fit the observations.
+These values can, in turn, be used to predict the value of the harmonic field
+at any other point outside of the sources by evaluating
+equation~\ref{eq:eql-forward}.
+Gridding and upward continuation can thus be achieved by predicting values on
+points that fall on a regular grid or at different heights.
+
+\subsection{Damped least-squares solution}
+\label{sec:eql-inversion}
+
+We can obtain the values of the source coefficients $\mathbf{c}$ that best
+fit the observed field values $\mathbf{d}^o$ by minimizing the goal function
+
+\begin{equation}
+    \phi(\mathbf{c}) =
+    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]\trans
+    \mathbf{W}
+    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]
+    + \lambda_d\ \mathbf{c}\trans\mathbf{c}
+    \ ,
+    \label{eq:misfit-unscaled}
 \end{equation}
@@
 \noindent where
-$G = \SI{6.674e-11}{\cubic\meter\per\kilogram\per\second\squared}$ is the
-universal gravitational constant, $z_i$ and $z_j$ are the vertical components
-of the $\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
-
-By solving equation~\ref{eq:linear-problem-g} we can obtain the values of
-$\mathbf{m}$ that better reproduce the measured field.
-This source distribution along with the fitted masses can be used to predict
-gravity values on any point where the potential field has not been measured.
-
-\subsection{Generalized equivalent sources}
-
-It's possible to generalize the equivalent sources technique to any harmonic
-field through a Green's function problem, regardless the nature of the field.
-
-By definition, any harmonic field $V$ must satisfy the Laplace's equation:
-
-\begin{equation}
-    \nabla^2 V = 0.
-\end{equation}
-
-Considering as boundary condition that $V$ is equal to zero at infinity, then
-its fundamental solution $\psi$ (also known as Green's function or radial basis
-function) must satisfy \citep[p.~210]{vladimirov1979}:
-
-\begin{equation}
-    \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
-        - 4\pi \delta(\mathbf{p}, \mathbf{q}),
-\end{equation}
-
-\noindent where $\delta(\mathbf{p}, \mathbf{q})$ is the Dirac's delta function
-and $\nabla_\mathbf{p}$ symbolize the Nabla operator applied on the coordinates
-$\mathbf{p}$.
-
-The fundamental solution of any harmonic field can be obtained as follows
-\citep[p.~37]{blakely1995}:
-
-\begin{equation}
-    \psi(\mathbf{p}, \mathbf{q})
-    =
-    \int
-    \frac{\delta(\mathbf{p}, \mathbf{q})}{|\mathbf{p} - \mathbf{q}|}
-    \textrm{d}v
-    =
-    \frac{1}{|\mathbf{p} - \mathbf{q}|}.
-\end{equation}
-
-This shows that the Green's function associated with any harmonic field is
-equal to the inverse of the Euclidean distance between the evaluation and the
-source points.
-Thus any harmonic field $V$ can be expressed as \citep[p.~37]{blakely1995}:
-
-\begin{equation}
-    V(\mathbf{p})
-    =
-    \int \psi(\mathbf{p}, \mathbf{q}) \rho(\mathbf{q}) d\mathbf{q}
-    =
-    \int \frac{\rho(\mathbf{q})}{|\mathbf{p} - \mathbf{q}|}  d\mathbf{q},
-\end{equation}
-
-\noindent where $\rho(\mathbf{q})$ is the density distribution of a certain
-physical-property evaluated on the point $\mathbf{q}$. Following
-\citet{dampney1969}, this density distribution can be approximated by a finite
-and discrete set of point sources located on $\{\mathbf{q}_1, \ldots,
-\mathbf{q}_M\}$:
-
-\begin{equation}
-    \rho(\mathbf{q}) =
-        \sum\limits_{j=1}^{M} c_j \delta(\mathbf{q} - \mathbf{q_j}),
-\end{equation}
-
-\noindent where $c_j$ is a coefficient related to the point source located on
-$\mathbf{q}_j$, with the same units as the physical-property.
-Then the harmonic field $V$ can be approximated by:
-
-\begin{equation}
-    V(\mathbf{p})
-    =
-    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p} - \mathbf{q}_j|}.
-    \label{eq:eql-field}
-\end{equation}
-
-In case we have measured the value of the harmonic field on points
-$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$, we can adjust the values of the $c$
-coefficients so they satisfy:
-
-\begin{equation}
-    V(\mathbf{p}_i)
-    =
-    \sum\limits_{j=1}^{M} \frac{c_j}{|\mathbf{p}_i - \mathbf{q}_j|}
-    \quad \forall i=1,\ldots,N.
-\end{equation}
-
-This system of linear equations can be written in an more algebraic way:
-
-\begin{equation}
-    \mathbf{d} = \mathbf{A} \mathbf{c}
-    \label{eq:linear-problem}
-\end{equation}
-
-\noindent where $\mathbf{d}$ is a vertical vector containing the measured
-values of $V$ on the observation points, $\mathbf{c}$ a vertical vector
-containing the $c$ coefficients and $\mathbf{A}$ is the \emph{Jacobian matrix},
-whose elements are defined as the Green's function evaluated on each pair of
-points $\mathbf{p}$ and $\mathbf{q}$:
-
-\begin{equation}
-    a_{ij}
-    =
-    \psi(\mathbf{p}_i, \mathbf{q}_j)
-    =
-    \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|}
-\end{equation}
-
-By solving equation~\ref{eq:linear-problem} we can obtain the values of
-$\mathbf{c}$ that better reproduce the measured field.
-Then they can be used to predict the value of the harmonic field on any other
-point where no measurement has been taken by evaluating
-equation~\ref{eq:eql-field}.
-
-\subsection{Fitting source coefficients}
-\label{sec:eql-inversion}
-
-Solving equations~\ref{eq:linear-problem-g} and~\ref{eq:linear-problem} is
-equivalent to performing an inversion and thus solving an ill-posed problem by
-nature due to the non-uniqueness and the instability of the possible solutions.
-Therefore is usually needed to add regularization functions in order to obtain
-stable solutions
-(\citealp[p.~52]{menke1989}; \citealp{cooper2000}; \citealp{oliveira2013}).
-
-We can obtain the values of the source coefficients $\mathbf{c}$ that better
-reproduce the measured field by minimizing an objective or misfit function
-$\phi(\mathbf{c})$ through a least squares method:
-
-\begin{equation}
-    \phi(\mathbf{c}) =
-        \left\lVert
-            \mathbf{d} - \mathbf{A}\mathbf{c}
-        \right\rVert ^ 2
-        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
-    \label{eq:misfit-unscaled}
-\end{equation}
-
-\noindent where $\left\lVert \cdot \right\rVert ^ 2$ symbolizes the L$_2$ norm
-and $\lambda_d$ is a \emph{damping} parameter with the same units as the
+$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
+$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
 Jacobian matrix elements.
-The second term of the equation applies a zeroth-order Tikhonov
-\citep{tikhonov1977} regularization to stabilize the solution.
-
-In order to simplify the choice of the \emph{damping} parameter we scale the
-Jacobian matrix so each column has unit variance.
-We define a diagonal matrix $\mathbf{S}$, whose elements corresponds to the
-standard deviation of each column of the Jacobian matrix $\mathbf{A}$:
+The second term on the right-hand side of the equation is a zeroth-order
+Tikhonov regularization \citep{tikhonov1977} (also known as a damping
+regularization or ridge regression) that is used to stabilize the solution.
+
+The range of acceptable values for the damping parameter $\lambda_d$ will
+depend on the values of the Jacobian matrix $\mathbf{A}$ and the coefficients.
+Consequently, this range will vary (often dramatically) between datasets,
+making it difficult to choose an appropriate value for $\lambda_d$ in practice.
+
+To solve this issue, we first scale the Jacobian matrix so that its elements
+are unitless and each column has unit variance.
+We define a diagonal matrix $\mathbf{S}$
 

### 2020-12-15 manuscript/manuscript.tex
Add reference to forward modelling sum equation

@@
     \ ,
+    \label{eq:forward-sum}
 \end{equation}
@@
 \ref{alg:residual} can be done by a summation
-(TODO: ADD EQUATION)
+(equation~\ref{eq:forward-sum})
 instead of a matrix-vector product, which allows us to avoid computing and

### 2020-12-16 manuscript/manuscript.tex
Make a list of steps to setup windows and layers

@@
 We can transform our equivalent source problem in
-equation~\ref{eq:linear-problem} into an additive model by
-(1) defining a set of $K$ overlapping windows of equal size that cover the
-survey area and (2) defining one set of equivalent sources per
-window. Then, the coefficients $\mathbf{c}_k$ relate to the equivalent sources
-of the $k$-th window and $\mathbf{A}_k$ is the Jacobian matrix between
-those sources and every data point.
-Thus, the predicted data are a superposition of the
-effects of the $K$ sets of equivalent sources.
-
-The gradient boosting algorithm above works by fitting each component of the
+equation~\ref{eq:linear-problem} into an additive model by following these
+steps:
+
+\begin{enumerate}
+  \item Define a set of $M$ equivalent sources distributed throughout the
+    survey area (see section \ref{sec:source-distribution} for details).
+  \item Define a set of $K$ overlapping windows of equal size that cover the
+    survey area.
+  \item Create $K$ separate sets of equivalent sources, one for each window, by
+    taking from the original set of $M$ sources the ones that fall within the
+    respective windows. Since the windows overlap, the total number of sources
+    from all sets will be greater than $M$.
+  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
+    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
+    matrix between those sources and every data point of the survey.
+  \item Model the predicted data as a superposition of the effects of the $K$
+    separate sets of equivalent sources.
+\end{enumerate}
+
+The gradient boosting algorithm works by fitting each component of the
 additive model, one at a time, to the residuals of the previous component.
@@
 to step sizes in steepest descent.
-We can modify the gradient boosting algorithm of \citet{friedman2001} to
-find the damped least-squares solutions for the $K$ parameters vectors
-$\mathbf{c}_k$ and step sizes $\alpha_k$ in equation~\ref{eq:gb-linear-model}:
+The adaptation of the gradient boosting method to find the damped least-squares
+solutions for the $K$ parameters vectors $\mathbf{c}_k$ and step sizes
+$\alpha_k$ in equation~\ref{eq:gb-linear-model} is presented in
+Algorithm~\ref{alg:gradient_boosting}.
 
@@
   \caption{Gradient boosting solution for damped least-squares regression.}
+  \label{alg:gradient_boosting}
 \end{algorithm}
 
-\citet{friedman2002} suggests that introducing randomness into the fitting
-process can improve convergence of the solution. To achieve this, we randomize
+To improve the convergence of the algorithm, \citet{friedman2002} suggests that
+introducing randomness into the fitting process. We achieve this by randomizing
 the order in which the $K$ windows are used in the gradient boosting algorithm.
@@
 \subsection{Source distributions}
+\label{sec:source-distribution}
 

### 2020-12-16 manuscript/manuscript.tex
Reorganize the parts about the step size
It was a bit out of order at the end of the section. So I moved the
equation to the algorithm and the discussion of what it does to the part
about fitting only inside windows.

@@
   \DontPrintSemicolon
-  \setstretch{1.5}
+  \setstretch{1.75}
   define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
@@
 
+    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$
     \nllabel{alg:scale}
-    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$ \;
-
-    \nllabel{alg:fit}
+    \;
+
     $
@@
      \mathbf{r}_{k-1}
-    $ \;
-
+    $
+    \nllabel{alg:fit}
+    \;
+
+    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$
     \nllabel{alg:unscale}
-    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$ \;
-
-    \nllabel{alg:stepsize}
+    \;
+
+    $\mathbf{d}_k = \mathbf{A}_k \hat{\mathbf{c}}_k$
+    \nllabel{alg:predicted}
+    \;
+
     $
@@
         \left\lVert
-          \mathbf{r}_{k - 1} - \alpha \mathbf{A}_k \hat{\mathbf{c}}_k
+          \mathbf{r}_{k - 1} - \alpha \mathbf{d}_k
         \right\rVert ^ 2
       \right)
-    $ \;
-
+      = \dfrac{
+        \mathbf{r}_{k-1}\trans \mathbf{d}_k
+      }{
+        \mathbf{d}_k\trans \mathbf{d}_k
+      }
+    $
+    \nllabel{alg:stepsize}
+    \;
+
+    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
     \nllabel{alg:residual}
-    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{A}_k \hat{\mathbf{c}}_k$ \;
+    \;
   }
@@
 \end{algorithm}
+
+After all $\alpha_k$ step sizes and $\mathbf{c}_k$ coefficients vectors
+are estimated, we can predict the effect of the additive equivalent source
+model on any point through the summation
+
+\begin{equation}
+    d(\mathbf{p}) =
+    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
+    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
+    \ .
+\end{equation}
 
@@
 while using all available data when calculating the step size and residuals
-(steps \ref{alg:stepsize} and \ref{alg:residual}).
+(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}).
 By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
@@
 The influence of distance sources on the solution is maintained by using the
-entire set of data points when updating the residuals vector.
-
-The step size parameter functions as scaling factor that prevents the algorithm
-from worsening the fit to data points outside of the current window.
+entire set of data points when calculating
+the step size $\alpha_k$ and updating the residuals vector.
+In this case, the step size prevents the algorithm from worsening the fit to
+data points that fall outside of the current window.
 As such, it improves the converge of the solution and ensures that the
 overall misfit decreases with iteration.
-The step size that minimizes the misfit function in step \ref{alg:stepsize} of
-the algorithm is
-
-\begin{equation}
-    \alpha_k = \frac{
-      \mathbf{r}_{k-1}\trans \mathbf{A}_k \hat{\mathbf{c}}_k
-    }{
-      \hat{\mathbf{c}}_k\trans\mathbf{A}_k\trans \mathbf{A}_k \hat{\mathbf{c}}_k
-    }.
-\end{equation}
-
-After all $\alpha_k$ step sizes and $\hat{\mathbf{c}}_k$ coefficients vectors
-are estimated, we can predict the effect of the additive equivalent source
-model on any point through the summation
-
-\begin{equation}
-    d(\mathbf{p}) =
-    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
-    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
-    \ .
-\end{equation}
-
-NOTE: This paragraph might be better in the Discussion section.
+
+\textbf{NOTE: This paragraph might be better in the Discussion section.}
 

### 2020-12-16 manuscript/manuscript.tex
Minor tweaks to section about forward modeling by sum

@@
 elements.
-The forward modeling operations performed in steps \ref{alg:stepsize} and
-\ref{alg:residual} can be done by a summation
-(equation~\ref{eq:forward-sum})
+The forward modeling operation performed in step \ref{alg:predicted} can be
+done by a summation (equation~\ref{eq:forward-sum})
 instead of a matrix-vector product, which allows us to avoid computing and

### 2020-12-16 manuscript/manuscript.tex
Apply suggestions by Santiago
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
     survey area.
-  \item Create $K$ separate sets of equivalent sources, one for each window, by
-    taking from the original set of $M$ sources the ones that fall within the
-    respective windows. Since the windows overlap, the total number of sources
+  \item Create $K$ separate sets of equivalent sources, one for each window.
+    Each set will be formed by the portion of the original $M$ sources that fall inside
+    the respective window.
+    Since the windows overlap, the total number of sources
     from all sets will be greater than $M$.
@@
     \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
-    \ .
+    \ ,
 \end{equation}
+
+\noindent where ${c_k}_j$ is the $j$-th element of the $\mathbf{c}_k$ vector.
 
@@
 data points that fall outside of the current window.
-As such, it improves the converge of the solution and ensures that the
+As such, it improves the convergence of the solution and ensures that the
 overall misfit decreases with iteration.

### 2020-12-17 manuscript/manuscript.tex

@@
 \usepackage{amsmath}
-\usepackage[longend,linesnumbered]{algorithm2e}
+\usepackage[longend,linesnumbered,ruled]{algorithm2e}
 \usepackage{graphicx}
@@
   \DontPrintSemicolon
-  \setstretch{1.75}
+  \setstretch{1.5}
   define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
   \For{ $k = 1$ \KwTo $K$ }{
+
+    calculate $N \times M_k$ Jacobian matrix $\mathbf{A}_k$
+    \;
 
@@
 points that fall within the $k$-th window for fitting the sources
-(steps \ref{alg:scale} and \ref{alg:fit}),
+(steps \ref{alg:scale} and \ref{alg:fit} of
+algorithm~\ref{alg:gradient_boosting}),
 while using all available data when calculating the step size and residuals
-(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}).
-By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
-elements.
+(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}
+of algorithm~\ref{alg:gradient_boosting}).
+By doing so, we can reduce the size of the Jacobian matrix further to $N_k
+\times M_k$ elements.
 The forward modeling operation performed in step \ref{alg:predicted} can be
@@
 storing the larger $N \times M_k$ Jacobian at any point.
+Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
+the final \textit{gradient boosted equivalent source algorithm}.
+
+\begin{algorithm}[!h]
+  \DontPrintSemicolon
+  \setstretch{1.5}
+  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
+  \For{ $k = 1$ \KwTo $K$ }{
+
+    select weights $\tilde{\mathbf{W}}_k$ and residuals
+    $\tilde{\mathbf{r}}_{k - 1}$ for data points inside the $k$-th window only
+    \;
+
+    calculate $N_k \times M_k$ Jacobian matrix $\tilde{\mathbf{A}}_k$
+    with data points and sources inside the $k$-th window only
+    \;
+
+    $\mathbf{B}_k = \tilde{\mathbf{A}}_k \mathbf{S}_k\inv$
+    \;
+
+    $
+     \hat{\mathbf{m}}_k = \left[
+     \mathbf{B}_k\trans \tilde{\mathbf{W}}_k \mathbf{B}_k +
+     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \tilde{\mathbf{W}}_k
+     \tilde{\mathbf{r}}_{k-1}
+    $
+    \;
+
+    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$
+    \;
+
+    $
+    \mathbf{d}_k \Rightarrow
+    {d_k}_i
+    =
+    \sum\limits_{j=1}^{M_k} \dfrac{{c_k}_j}{\left\lVert \mathbf{p}_i -
+        {\mathbf{q}_k}_j
+    \right\rVert}
+    \ \forall i=1\ \text{to}\ N
+    $
+    \;
+
+    $
+      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
+      \left(
+        \left\lVert
+          \mathbf{r}_{k - 1} - \alpha \mathbf{d}_k
+        \right\rVert ^ 2
+      \right)
+      = \dfrac{
+        \mathbf{r}_{k-1}\trans \mathbf{d}_k
+      }{
+        \mathbf{d}_k\trans \mathbf{d}_k
+      }
+    $
+    \;
+
+    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
+    \;
+  }
+  \BlankLine
+  \setstretch{1}
+  \caption{ Gradient boosted equivalent source algorithm. }
+  \label{alg:gradient_boosting_window}
+\end{algorithm}
+
 The influence of distance sources on the solution is maintained by using the

### 2020-12-21 manuscript/manuscript.tex

@@
 
+\section{Performance of gradient boosted equivalent sources}
+
+Our second goal is to assess the accuracy of the predictions achieved by the
+gradient boosting algorithm while registering its performance by comparison
+with the non-boosted equivalent sources.
+
+\subsection{Window size}
+
+One factor that plays an important role on the gradient boosted equivalent
+layers is the size of the overlapping windows used to create each set of
+equivalent sources.
+Smaller windows will reduce the amount of computer memory needed to fit the
+source coefficients: smaller windows will reduce the size of Jacobian matrices
+$\tilde{\mathbf{A}_k}$.
+Nevertheless, the usage of smaller windows may produce less accurate
+predictions: the equivalent sources cannot achieve the global minimum of the
+misfit $\varphi(\mathbf{c})$ of equation~\ref{eq:misfit-unscaled}.
+Moreover, the size of the overlapping windows might also impact on the
+computation time needed to fit the source coefficients: smaller windows will
+generate simpler least-square problems which are easier to solve, but they will
+also create more iterations.
+
+We want to assess how the size of the overlapping windows impacts both the
+accuracy of the predictions and the computation time needed to fit the source
+coefficients in comparison with the performance of the non-boosted equivalent
+sources.
+
+We applied the gradient boosted equivalent sources to interpolate the synthetic
+airborne survey on the same points of the target grid.
+We selected several window sizes to assess how accuracy and performance depend
+on that variable.
+For each window size we gridded the synthetic data with different sets of
+parameters. Then we compared each prediction to the target grid in order to get
+the best prediction for each window size.
+On every interpolation, block-averaged sources with relative depth are used
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}, and an
+overlap of 50\% between adjacent windows.
+
+Using the best set of parameters for each window size, we registered the
+achieved RMS against the values of the target grid and the time needed to fit
+the sources coefficients.
+
+Compare RMS with the one achieved by the best prediction carried out by the
+non-boosted equivalent sources with block-averaged sources (see
+Table~\ref{tab:parameters-airborne-survey}).
+Calculated the fitting time relative to the time needed by non-boosted
+equivalent sources.
+
+\subsection{Overlapping}
+
+Another factor that plays an important role on the accuracy of the predictions
+and impacts the computation time needed to fit the source coefficients is the
+amount of overlap between adjacent windows.
+The previous choice of 50\% showed to be sufficiently good to achieve
+acceptable accuracy, although a deeper study should be carried out to assess
+how the amount of overlap impacts both accuracy and fitting time.
+
+We interpolated the synthetic airborne survey using the gradient boosted
+equivalent sources on the same points of the target grid.
+The interpolations were carried out using different amount of overlap, from
+0\% to 0.95\% with a step size of 0.05\%.
+For each overlap, we gridded the synthetic data with different sets of
+parameters, fixing the window size to INSERT-WINDOW-SIZE and using
+block-averaged sources with relative depth and a spacing of
+\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}.
+We registered the RMS achieved by the best prediction for each overlap and the
+computation time needed to fit the source coefficients.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Gridding Australia gravity data}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusions}

### 2020-12-23 notebooks/08-eql-boost-synthetic.py
Advance on results for gradient boosting (#82)
Add notebooks for assessing the performance of gradient boosted equivalent sources against window size and overlapping.
Start adding gradient boosting results to manuscript.

@@ -73,9 +73,8 @@ region = (
 
 # ## Grid data with EQLHarmonicBoost
 #
-#
-# ### Use a window size of 20km
-#
+# Let's grid the airborne survey with the gradient boosted equivalent sources using a window size of 20km and block-averaged sources with relative depth.
+
 # Define gridding parameters
 
 depth_type = "relative_depth"
@@ -156,96 +155,12 @@ plt.show()
 
 # Plot misfit through the iterations
 
-plt.plot(eql.errors_)
+plt.plot(eql.errors_, ".-")
 plt.xlabel("Iterations")
-plt.ylabel("RMS of the residue")
+plt.ylabel("RMS of the residue [mGal]")
+plt.grid()
 plt.show()
 
 # Save grid
 
 grid.to_netcdf(eql_boost_results_dir / "airborne_grid_boost_20km.nc")
-
-# ### Use a window size of 50km
-
-dampings = np.logspace(-4, 3, 8)
-depths = [100, 500, 1e3, 2e3, 5e3, 10e3]
-window_size = 50e3
-
-# Combine parameters values
-
-parameters = combine_parameters(
-    **dict(
-        depth_type=depth_type,
-        depth=depths,
-        damping=dampings,
-        spacing=block_spacing,
-        window_size=window_size,
-        random_state=random_state,
-    )
-)
-
-# Dump parameters to a JSON file
-
-json_file = eql_boost_results_dir / "parameters-50km.json"
-save_to_json(parameters, json_file)
-
-# Grid and score the prediction with each set of parameters
-
-rms = []
-for params in parameters:
-    points = block_averaged_sources(coordinates, **params)
-    eql = EQLHarmonicBoost(
-        points=points,
-        damping=params["damping"],
-        window_size=params["window_size"],
-        random_state=params["random_state"],
-    )
-    eql.fit(coordinates, getattr(survey, field).values)
-    grid = eql.grid(upward=target.height, region=region, shape=target.shape).scalars
-    rms.append(np.sqrt(mean_squared_error(grid.values, target.values)))
-
-# Get maximum score and the corresponding set of parameters
-
-# +
-best_rms = np.min(rms)
-best_params = parameters[np.argmin(rms)]
-
-print("Best RMS score: {}".format(best_rms))
-print("Best parameters: {}".format(best_params))
-# -
-
-# Obtain grid with the best set of parameters
-
[…]

### 2020-12-23 notebooks/10-eql-boost-overlapping.py

@@ -1,0 +1,362 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:light
+#     text_representation:
+#       extension: .py
+#       format_name: light
+#       format_version: '1.5'
+#       jupytext_version: 1.7.1
+#   kernelspec:
+#     display_name: Python [conda env:eql-gradient-boosted]
+#     language: python
+#     name: conda-env-eql-gradient-boosted-py
+# ---
+
+# # Compare performance of EQLHarmonicBoost with different overlapping
+
+# **Import useful packages**
+
+# +
+from pathlib import Path
+import time
+import numpy as np
+import pandas as pd
+import xarray as xr
+import harmonica as hm
+import matplotlib.pyplot as plt
+from sklearn.metrics import mean_squared_error
+
+from boost_and_layouts import (
+    block_averaged_sources,
+    combine_parameters,
+    EQLHarmonicBoost,
+    save_to_json,
+)
+
+# -
+
+# **Define results directory**
+
+results_dir = Path("..") / "results"
+airborne_results_dir = results_dir / "airborne_survey"
+eql_boost_results_dir = results_dir / "eql-boost"
+
+# **Define which field will be meassured**
+
+field = "g_z"
+field_units = "mGal"
+
+# ## Read synthetic airborne survey and target grid
+
+# Read airborne survey
+
+survey = pd.read_csv(airborne_results_dir / "survey.csv")
+survey
+
+# Read target grid
+
+target = xr.open_dataarray(results_dir / "target.nc")
+target
+
+# Define coordiantes tuple with the location of the survey points
+
+coordinates = (survey.easting.values, survey.northing.values, survey.height.values)
+
+# Get region of the target grid
+
+region = (
+    target.easting.min().values,
+    target.easting.max().values,
+    target.northing.min().values,
+    target.northing.max().values,
+)
+
+# # Grid data with EQLHarmonic for reference on performance
+#
+# Use the best of parameters for block-averaged sources with relative depth, which was obtained on a previous notebook.
+
+depth_type = "relative_depth"
+block_spacing = 2e3
+damping = 1e-3
+depth = 9e3
+
+# Grid the data using `hm.EQLHarmonic` and track time of the fitting process
+
+# +
+points = block_averaged_sources(
+    coordinates, depth_type=depth_type, spacing=block_spacing, depth=depth
+)
[…]

### 2020-12-23 manuscript/manuscript.tex

--- 2020-12-17 manuscript/manuscript.tex
@@
 \input{source-layouts-schematics.tex}
+\input{boost-overlapping.tex}
 
@@
 
+\section{Performance of gradient boosted equivalent sources}
+
+Our second goal is to assess the accuracy of the predictions achieved by the
+gradient boosting algorithm while registering its performance by comparison
+with the non-boosted equivalent sources.
+
+\subsection{Window size}
+\label{sec:window-size}
+
+One factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the size of the overlapping windows used to create
+each set of equivalent sources.
+The size of the windows controls the size of the Jacobian matrices
+$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
+Thus, using smaller windows will reduce the amount of computer memory needed to
+fit the source coefficients.
+Nevertheless, smaller windows may produce less accurate predictions because
+their inability to achieve the global minimum of the misfit from
+equation~\ref{eq:misfit-unscaled}.
+Besides, the window size might also impact on the computation time needed to
+fit the source coefficients: smaller windows will generate simpler least-square
+problems which are easier to solve, but they will also create more iterations.
+
+We want to assess how the size of the overlapping windows impacts both the
+accuracy of the predictions and the computation time needed to fit the source
+coefficients in comparison with the performance of the non-boosted equivalent
+sources.
+
+We applied the gradient boosted equivalent sources to interpolate the synthetic
+airborne survey on the same points of the target grid.
+We selected several window sizes to assess how accuracy and performance depend
+on that variable.
+For each window size we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
+of 50\%, and with different values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each window size and the damping value used to
+obtain it.
+
+Using the best set of parameters for each window size, we registered the
+achieved RMS against the values of the target grid and the time needed to fit
+the sources coefficients.
+In order to avoid any errors introduced by the way windows are shuffled, the
+RMS for each window size was obtained as the mean RMS achieved by using
+different random seeds.
+
+\subsection{Overlapping}
+
+Another factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the amount of overlap between adjacent windows.
+The previous choice of 50\% showed to be sufficiently good to achieve
+acceptable accuracy, although a deeper study should be carried out to assess
+how the amount of overlap impacts both accuracy and fitting time.
+
+We interpolated the synthetic airborne survey using the gradient boosted
+equivalent sources on the same points of the target grid.
+The interpolations were carried out using different amount of overlap, from
+0\% to 0.95\% with a step size of 0.05\%.
+For each overlap we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
+a window size of \BoostOverlappingWindowSize, and with different
+values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each overlap and the damping value used to
+obtain it.
+
+Using the best set of parameters for each overlap, we registered the achieved
+RMS against the values of the target grid and the time needed to fit the
+sources coefficients.
+The RMS was obtained as the mean RMS achieved by using different random seeds
+as we did on~\ref{sec:window-size}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Gridding Australia gravity data}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusions}
@@
             & \textbf{Best}
-            & \textbf{RMS (mGal)} \\
+            & \textbf{RMS} \\
         \toprule
@@
         \multirow{8}{*}{Source Below Data}
-            & \multirow{2}{*}{Constant Depth}
+            & \multirow{2}{*}{Constant}
                 & Depth (m)
@@
             \cmidrule{2-6}
-            & \multirow{2}{*}{Relative Depth}
+            & \multirow{2}{*}{Relative}
                 & Depth (m)
@@
             \cmidrule{2-6}
-            & \multirow{4}{*}{Variable Depth}
+            & \multirow{4}{*}{Variable}
                 & Depth (m)
@@
         \multirow{11}{*}{Block Averaged Sources}
-            & \multirow{3}{*}{Constant Depth}
+            & \multirow{3}{*}{Constant}
                 & Depth (m)
@@
             \cmidrule{2-6}
-            & \multirow{3}{*}{Relative Depth}
+            & \multirow{3}{*}{Relative}
                 & Depth (m)
@@
             \cmidrule{2-6}
-            & \multirow{5}{*}{Variable Depth}
+            & \multirow{5}{*}{Variable}
                 & Depth (m)
@@
         \multirow{4}{*}{Grid Sources}
-            & \multirow{4}{*}{Constant Depth}
+            & \multirow{4}{*}{Constant}
                 & Depth (m)

### 2021-01-06 manuscript/manuscript.tex

@@
 
-\subsection{Source distributions}
+\subsection{Location of sources}
 \label{sec:source-distribution}
 
-How to choose how many sources to use and where to locate them are not
-trivial decisions that play an important role on the accuracy of the
-predictions and the computational resources needed to fit the sources'
-coefficients.
-
-The chosen distribution of sources should simultaneously reproduce the measured
-data on the survey points and be able to make accurate predictions of the
-measured harmonic field on non observed locations.
-
-A high number of sources homogeneously distributed on the survey region are
-capable of reproducing the observed data. Nevertheless, too many sources will
-make the Jacobian matrix too large, what could introduce computational problems
-like the inability of storing the matrix on memory or a high computational time
-needed to fit the sources' coefficients.
-On the other hand, using very few sources will undoubtedly reduce the memory
-needs and lower the computational time when fitting the sources' coefficients.
-Nevertheless, it could be incapable of making accurate predictions or even
-reproducing the measured data if the number of sources is too low.
-
-The choice of the source distribution could also depend on the characteristic
-of the survey and how the observation points are distributed on the region.
-A ground survey usually consists in observation points located along irregular
-paths plus some possible scattered points.
-The survey region is usually heterogeneously covered, leaving areas without any
-observation.
-On the other hand, an airborne survey consists in observation points located
-along almost straight flight lines. The measurements are usually taken at
-a high frequency, so the observation points along the flight lines are very
-close to each other.
-This creates an anisotropy on the observation points: there are much more
-observation points along the flight lines directions.
-
-The most widely used source distributions are: a regular grid of point sources
-and one point source beneath each observation point.
-
-The \emph{regular grid} creates an homogeneous distribution of point sources
-below the surveyed region.
-The distance between sources is controlled by the grid spacing parameter.
-Keeping the boundaries of the grid constant, reducing the spacing increases the
-number of sources.
-
-The \emph{source below data} layout locates one source below each
-observation point, therefore the number of sources will be equal to the number
-of data points.
-
-When working with ground surveys, the \emph{regular grid} needs the grid
-spacing to be sufficiently small so observed values can be accurately
-reproduced by the source distribution.
-This will create too many sources on areas where no observation has been
-carried out.
-In contrast, the \emph{source below data} layout is more likely to accurately
-fit the observed data with much less sources, reducing the computational load
-to fit the equivalent sources' coefficients.
-
-When working with airborne surveys, the \emph{source below data} may
-generate an anisotropic distribution of sources by locating too many sources
-along the flight paths.
-It could lead to unwanted aliases on the predicted values.
-In contrast, the \emph{regular grid} won't generate aliases by homogeneously
-locating sources.
-
-We propose a new source distribution that could simultaneously reduce the
-computational load and remove the drawbacks of the preceding ones: the
-\emph{block averaged sources}.
-It consist in:
-
+The ideal number of sources and their locations, both horizontally and
+vertically, has been debated since the inception of the equivalent source
+technique with \citet{dampney1969}.
+The choices made regarding these parameters can play an important role on the
+accuracy of the predictions and the computational resources needed to estimate
+the coefficients.
+An ideal distribution of sources should simultaneously be able to reproduce the
+measured data on the survey points and also be able to make accurate
+predictions on non-observed locations.
+
+A large number of sources evenly distributed along the survey region are
+capable of reproducing the observed data. Nevertheless, the computational load
+can be prohibitive and such underdetermined problems are prone to overfiting
+the data, leading to poor performance when making predictions. On the other
+hand, using very few sources will undoubtedly reduce the computational
+requirements but the equivalent source model could be incapable of reproducing
+the measured data, leading to inaccurate predictions.
+
+Particular survey characteristics also play a role in the choice of source
+distribution.
+In a ground survey, observation points are usually located along irregular
+paths as well as some possible scattered points.
+The coverage of the survey region is usually uneven, often leaving large areas
+without any observation.
+On the other hand, observations from airborne surveys are located along almost
+straight flight lines.
+Measurements are usually taken at
+a high temporal frequency, leading to the observation points along the flight
+lines that are several times closer than the flight line spacing.
+This creates an anisotropy in the sampling, which can cause aliasing artifacts
+in gridded products.
+
+\subsubsection{Horizontal layout}
+
+The most widely used layouts of equivalent sources are:
+
+\begin{itemize}
+  \item
+    \emph{Regular grid}: a homogeneous distribution of point sources below the
+    survey region at a constant depth. A padding region is often added to help
+    reduce edge effect. In practice, often leads to underdetermined problems
+    ($N<M$).
+  \item
+    \emph{Sources below data}: one equivalent source is placed below each
+    observation point at a given depth (often dependent on the distance to
+    neighboring data points). Therefore, the number of sources is be equal to
+    the number of observations ($N=M$).
+\end{itemize}
+
+For ground surveys, the \emph{regular-grid} layout needs a sufficiently
+small grid spacing to be able to fit the observed data.
+This creates an unnecessarily large number of sources in areas where no
+observations exist.
+In contrast, the \emph{sources-below-data} layout is more likely to accurately
+fit the observed data with many fewer sources, reducing the computational load.
+
+For airborne surveys, the \emph{source-below-data} layout may
+place an undesirably large number of sources along the flight paths.
+This could lead to aliasing effects on the predicted values, such as the
+stripes parallel to flight lines that are often observed when griding airborne
+magnetic data.
+In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
+distributing sources and using a continuous source layer (e.g.,
+right-rectangular prisms or tesseroids).
+
+We propose a new source layout that could simultaneously reduce the
+computational load and remove some of the drawbacks of the regular-grid and
+source-below-data layouts:
+
+\begin{itemize}
+  \item
+    \emph{Block-averaged sources}: point sources are placed in the average
+    position of data points that fall within specified spatial blocks
+    (Fig.~\ref{fig:block-averaged-sources}). In
+    short, this is done by:
     \begin{enumerate}
-    \item Dividing the region in blocks of equal size. The size of the blocks
-        is controlled by a \emph{spacing} parameter.
-        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
-    \item Computing the median location of the observation points that fall
+        \item Dividing the survey region in blocks of equal size
+            (Fig.~\ref{fig:block-averaged-sources}a-b).
+        \item Computing the median position of the observation points that fall
           inside each block. Blocks without any observation point are ignored.
-    \item Locating one point source below each block averaged coordinate.
-        (see Fig.~\ref{fig:block-averaged-sources}(c)).
+        \item Assign one point source to the computed median position, shifted
+          to a specified depth (Fig.~\ref{fig:block-averaged-sources}c).
     \end{enumerate}
-
-The number of sources created by this new distribution will be less or equal to
-the ones created by the \emph{source below data} and the \emph{regular
-grid} with the same spacing.
-Moreover, the sources are only located beneath populated blocks, so sources
-will be concentrated on regions where data has been gathered and no anisotropic
-distribution of sources will be generated.
+\end{itemize}
+
+The number of sources created by this new layout will be less than or equal to
+(if the blocks contain a single data point)
+the number of observations.
+The overdetermined problems that arise from this layout have a lower
+computational load and are less prone to overfiting since the complexity of the
+model is lower.
+Moreover, the block averaging process can balance the spacing between sources
+along a flight line and between adjacent lines.
+
+Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
+observation points that simulates a ground survey, and the possible location of
+sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
+averaged sources} and (d) the \emph{grid sources} layouts.
 

### 2021-01-06 manuscript/manuscript.tex
Mention that source layouts is discussed later

@@
 and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.
+The horizontal and vertical distribution of sources is discussed in section~\ref{sec:source_distribution}.
 
@@
 \subsection{Damped least-squares solution}
-\label{sec:eql-inversion}
+\label{sec:eql_inversion}
 
@@
   \item Define a set of $M$ equivalent sources distributed throughout the
-    survey area (see section \ref{sec:source-distribution} for details).
+    survey area (see section \ref{sec:source_distribution} for details).
   \item Define a set of $K$ overlapping windows of equal size that cover the
@@
 \subsection{Location of sources}
-\label{sec:source-distribution}
+\label{sec:source_distribution}
 
@@
 \subsection{Window size}
-\label{sec:window-size}
+\label{sec:window_size}
 
@@
 The RMS was obtained as the mean RMS achieved by using different random seeds
-as we did on~\ref{sec:window-size}.
+as we did on~\ref{sec:window_size}.
 

### 2021-01-06 manuscript/manuscript.tex
Explain how scaling limits the range of damping
Specify that in practice we find it's constrained to some values.

@@
 $\mathbf{c}$.
+In practice, we find that suitable $\lambda$ values fall between $10^{-8}$ and
+$10^{-1}$, irrespective of the dataset, and that results are mostly sensitive
+to order-of-magnitude changes in $\lambda$.
 
@@
 
-To improve the convergence of the algorithm, \citet{friedman2002} suggests that
+To improve the convergence of the algorithm, \citet{friedman2002} suggests
 introducing randomness into the fitting process. We achieve this by randomizing

### 2021-01-06 manuscript/manuscript.tex
Standardize use of "Equivalent sources" and "gradient-boosted"

@@
 \newcommand{\Title}{
-    Gradient boosted equivalent sources
+    Gradient-boosted equivalent sources
 }
@@
 A widely used method for interpolating gravity and magnetic data
-is the equivalent source technique (also known as equivalent layer, radial
+is the equivalent sources technique (also known as equivalent layer, radial
 basis functions, or Green's functions interpolation), first introduced by
@@
 
-Many variants of the equivalent source technique have been proposed, often
+Many variants of the equivalent sources technique have been proposed, often
 attempting to obtain faster or more accurate solutions.
@@
 Therefore, the gradient boosting method allows us to fit
-equivalent sources models that would produce Jacobian matrices that are larger
+equivalent source models that would produce Jacobian matrices that are larger
 than the available computer memory.
@@
 Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
-the final \textit{gradient boosted equivalent source algorithm}.
+the final \textit{gradient-boosted equivalent source algorithm}.
 
@@
   \setstretch{1}
-  \caption{ Gradient boosted equivalent source algorithm. }
+  \caption{Gradient-boosted equivalent source algorithm.}
   \label{alg:gradient_boosting_window}
@@
 
-\section{Performance of gradient boosted equivalent sources}
+\section{Performance of gradient-boosted equivalent sources}
 

### 2021-01-06 manuscript/manuscript.tex
Review text for horizontal positioning of sources

@@
 The ideal number of sources and their locations, both horizontally and
-vertically, has been debated since the inception of the equivalent source
+vertically, has been debated since the inception of the equivalent sources
 technique with \citet{dampney1969}.
@@
 accuracy of the predictions and the computational resources needed to estimate
-the coefficients.
+the source coefficients.
 An ideal distribution of sources should simultaneously be able to reproduce the
-measured data on the survey points and also be able to make accurate
-predictions on non-observed locations.
-
-A large number of sources evenly distributed along the survey region are
-capable of reproducing the observed data. Nevertheless, the computational load
-can be prohibitive and such underdetermined problems are prone to overfiting
-the data, leading to poor performance when making predictions. On the other
-hand, using very few sources will undoubtedly reduce the computational
-requirements but the equivalent source model could be incapable of reproducing
-the measured data, leading to inaccurate predictions.
-
-Particular survey characteristics also play a role in the choice of source
-distribution.
-In a ground survey, observation points are usually located along irregular
-paths as well as some possible scattered points.
-The coverage of the survey region is usually uneven, often leaving large areas
-without any observation.
+measured data on the survey points, make accurate predictions on non-surveyed
+locations, and minimize the required computational resources.
+
+A large number of evenly distributed sources along the survey region are
+capable of reproducing the observed data.
+Nevertheless, the computational load can be prohibitive and such
+underdetermined problems are prone to overfiting the data, leading to poor
+predictive power when interpolating and extrapolating.
+On the other hand, using few sources will reduce the computational requirements
+but the model may be incapable of reproducing the full spectral content of the
+measured data.
+
+Particular survey characteristics also play a role in the choice of equivalent
+source distribution.
+In a ground survey, observations are usually located along irregular paths and
+scattered points.
+The coverage of the survey region is often uneven, leaving large areas without
+any observation.
 On the other hand, observations from airborne surveys are located along almost
-straight flight lines.
-Measurements are usually taken at
-a high temporal frequency, leading to the observation points along the flight
-lines that are several times closer than the flight line spacing.
-This creates an anisotropy in the sampling, which can cause aliasing artifacts
-in gridded products.
-
-\subsubsection{Horizontal layout}
-
-The most widely used layouts of equivalent sources are:
-
-\begin{itemize}
+straight and closely spaced flight lines.
+Measurements are usually taken at a high temporal frequency, leading to the
+observation points along the flight lines that are several times closer to each
+other than the flight line spacing.
+This creates a bias in the sampling, which can cause aliasing artifacts in
+gridded products.
+
+\subsubsection{Horizontal source layouts}
+
+The most widely used layouts for distributing equivalent sources horizontally
+are:
+
+\begin{enumerate}
   \item
@@
     survey region at a constant depth. A padding region is often added to help
-    reduce edge effect. In practice, often leads to underdetermined problems
-    ($N<M$).
+    reduce edge effects. In practice, it often leads to underdetermined problems
+    since a large number of sources is required ($N<M$).
   \item
-    \emph{Sources below data}: one equivalent source is placed below each
+    \emph{Sources below data points}: one equivalent source is placed below each
     observation point at a given depth (often dependent on the distance to
@@
     the number of observations ($N=M$).
-\end{itemize}
+\end{enumerate}
 
@@
 fit the observed data with many fewer sources, reducing the computational load.
-
-For airborne surveys, the \emph{source-below-data} layout may
+But when applied to airborne surveys, the \emph{source-below-data} layout may
 place an undesirably large number of sources along the flight paths.
@@
 
-We propose a new source layout that could simultaneously reduce the
-computational load and remove some of the drawbacks of the regular-grid and
-source-below-data layouts:
-
-\begin{itemize}
-  \item
-    \emph{Block-averaged sources}: point sources are placed in the average
+We propose a new way of distributing equivalent sources horizontally that could
+simultaneously reduce the computational load and mitigate some of the drawbacks
+of existing layouts.
+In the \emph{block-averaged sources} layout,
+point sources are placed in the average
 position of data points that fall within specified spatial blocks
-    (Fig.~\ref{fig:block-averaged-sources}). In
-    short, this is done by:
+(Fig.~\ref{fig:block-averaged-sources}).
+This is done by:
+
 \begin{enumerate}
-        \item Dividing the survey region in blocks of equal size
-            (Fig.~\ref{fig:block-averaged-sources}a-b).
-        \item Computing the median position of the observation points that fall
-          inside each block. Blocks without any observation point are ignored.
-        \item Assign one point source to the computed median position, shifted
-          to a specified depth (Fig.~\ref{fig:block-averaged-sources}c).
+    \item Dividing the survey region into rectangular blocks of equal size.
+    \item Computing the median horizontal position of the observation points
+      that fall inside each block. Blocks without any observation point are
+      omitted.
+    \item Assign one point source to the median horizontal position calculated
+      in step 1.
 \end{enumerate}
-\end{itemize}
-
-The number of sources created by this new layout will be less than or equal to
-(if the blocks contain a single data point)
-the number of observations.
-The overdetermined problems that arise from this layout have a lower
-computational load and are less prone to overfiting since the complexity of the
-model is lower.
+
+The number of sources created by this new layout will be less than the number
+of observations if the block size is chosen appropriately (i.e., making sure
+that blocks are large enough to contain more than a single data point).
+The overdetermined problem that arises from this layout has a lower
+computational load and is less prone to overfiting the data since the model
+complexity is lower.
 Moreover, the block averaging process can balance the spacing between sources
-along a flight line and between adjacent lines.
+along a flight line and between adjacent lines, helping to reduce aliasing
+effects in generated grids.
 

### 2021-01-06 notebooks/02-source-layouts-schematics.py
Tweaks to the source layout sketch figure
Removed the axis to make it cleaner. Increased the number of sources in
the grid to make it more realistic (underdetermined) and decrease the
block-averaged sources spacing as well.

@@ -23,7 +23,6 @@ import matplotlib.pyplot as plt
 
 import boost_and_layouts
 from boost_and_layouts import save_to_json
-
 # -
 
 # ## Define parameters for building the source distributions
@@ -64,10 +63,10 @@ coordinates = (survey.easting, survey.northing, survey.height)
 # ### Generate the source distributions
 
 # +
-block_spacing = 4000
-grid_spacing = 4000
+block_spacing = 3000
+grid_spacing = 2000
 
-layouts = ["source_below_data", "block_averaged_sources", "grid_sources"]
+layouts = ["source_below_data", "grid_sources", "block_averaged_sources"]
 depth_type = "constant_depth"
 
 parameters = {}
@@ -78,11 +77,11 @@ parameters[layout] = dict(
     depth=500,
 )
 
-layout = "block_averaged_sources"
-parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=block_spacing)
-
 layout = "grid_sources"
 parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=grid_spacing)
+
+layout = "block_averaged_sources"
+parameters[layout] = dict(depth_type=depth_type, depth=500, spacing=block_spacing)
 # -
 
 source_distributions = {}
@@ -108,32 +107,25 @@ for nodes in grid_lines:
 # Load matplotlib configuration
 plt.style.use(Path(".") / "matplotlib.rc")
 
-fig, axes = plt.subplots(nrows=1, ncols=4, sharey=True, figsize=(6.66, 1.65), dpi=300)
+titles = {
+    "source_below_data": "Sources below data", 
+    "block_averaged_sources": "Block-averaged sources", 
+    "grid_sources": "Regular grid"
+}
+
+fig, axes = plt.subplots(nrows=1, ncols=4, sharey=True, figsize=(7, 1.7), dpi=300)
 size = 3
 labels = "a b c d".split()
 
 for ax, label in zip(axes, labels):
     ax.set_aspect("equal")
-    ax.tick_params(
-        axis="y",
-        which="both",
-        left=False,
-        right=False,
-        labelleft=False,
-    )
-    ax.tick_params(
-        axis="x",
-        which="both",
-        bottom=False,
-        top=False,
-        labelbottom=False,
-    )
     ax.annotate(
         label,
-        xy=(0.05, 0.9),
+        xy=(0.02, 0.95),
[…]

### 2021-01-06 manuscript/manuscript.tex
Use only the source layouts figure
The figure with just the block average sketch wasn't necessary since the
one with all layouts has all the same information (the blocks and the
median position inside them).

@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
+    \caption{
+        Sketch of different horizontal layouts for equivalent source models.
+        Blue points represent the locations of observations and orange points
+        represent the locations of equivalent sources according to different
+        layout strategies.
+        (a) Set of \SourceLayoutsSchematicsObservations{} observation points
+        that simulate a ground survey.
+        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
+        obtained through the \emph{sources-below-data} layout.
+        (c) Location of the \SourceLayoutsSchematicsGridSources{} sources
+        obtained through the \emph{regular-grid} layout.
+        (d) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
+        sources obtained through the \emph{block-averaged sources} layout.
+    }
+    \label{fig:source_layouts}
+\end{figure*}
+
 The most widely used layouts for distributing equivalent sources horizontally
@@
   \item
+    \emph{Sources below data points}: one equivalent source is placed at the
+    horizontal location of each data point (Fig.~\ref{fig:source_layouts}b).
+    Therefore, the number of sources is be equal to the number of observations
+    ($N=M$).
+  \item
     \emph{Regular grid}: a homogeneous distribution of point sources below the
-    survey region at a constant depth. A padding region is often added to help
-    reduce edge effects. In practice, it often leads to underdetermined problems
-    since a large number of sources is required ($N<M$).
-  \item
-    \emph{Sources below data points}: one equivalent source is placed below each
-    observation point at a given depth (often dependent on the distance to
-    neighboring data points). Therefore, the number of sources is be equal to
-    the number of observations ($N=M$).
+    survey region (Fig.~\ref{fig:source_layouts}c). A padding region is often
+    added to help reduce edge effects. In practice, it often leads to
+    underdetermined problems since a large number of sources is required
+    ($N<M$).
 \end{enumerate}
@@
 fit the observed data with many fewer sources, reducing the computational load.
-But when applied to airborne surveys, the \emph{source-below-data} layout may
+But when applied to airborne surveys, the \emph{sources-below-data} layout may
 place an undesirably large number of sources along the flight paths.
@@
 position of data points that fall within specified spatial blocks
-(Fig.~\ref{fig:block-averaged-sources}).
+(Fig.~\ref{fig:source_layouts}d).
 This is done by:
@@
 effects in generated grids.
-
-Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
-observation points that simulates a ground survey, and the possible location of
-sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
-averaged sources} and (d) the \emph{grid sources} layouts.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/block-averaged-sources-schematics.pdf}
-    \caption{
-        Block averaged sources.
-        (a)~Given a set of observation points
-        (b)~we divide the survey region on blocks of equal size and compute the
-            median location of the observation points that fall inside each
-            block.
-        (c)~A source point is located beneath each block averaged coordinate.
-            The number of point sources could be less or equal to the number of
-            observation points. No source is located beneath unpopulated
-            blocks.
-    }
-    \label{fig:block-averaged-sources}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
-    \caption{
-        Source layouts.
-        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
-            points that resemble a ground survey.
-        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
-            obtained through the \emph{sources below data} layout.
-        (c) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
-            sources obtained through the \emph{block averaged sources} layout.
-        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
-            obtained through the \emph{grid sources} layout.
-    }
-    \label{fig:source-layouts-schematics}
-\end{figure*}
 

### 2021-01-06 manuscript/manuscript.tex
Add a part about why block averaged sources are good
Add a line about the grey lines in the layouts figure

@@
         sources obtained through the \emph{block-averaged sources} layout.
+        Grey dashed lines represent the spatial blocks within which the median
+        observation location is calculated.
     }
@@
 effects in generated grids.
+We will demonstrate through tests on synthetic that the block-averaged sources
+layout is able to interpolate with comparable accuracy to other layouts while
+using a fraction of the equivalent sources.
 

### 2021-01-06 manuscript/manuscript.tex
Add text to manuscript

--- 2021-01-06 manuscript/manuscript.tex
@@
 \newcommand{\Title}{
-    Gradient-boosted equivalent sources
+    Gradient boosted equivalent sources
 }
@@
 A widely used method for interpolating gravity and magnetic data
-is the equivalent sources technique (also known as equivalent layer, radial
+is the equivalent source technique (also known as equivalent layer, radial
 basis functions, or Green's functions interpolation), first introduced by
@@
 
-Many variants of the equivalent sources technique have been proposed, often
+Many variants of the equivalent source technique have been proposed, often
 attempting to obtain faster or more accurate solutions.
@@
 and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.
-The horizontal and vertical distribution of sources is discussed in section~\ref{sec:source_distribution}.
 
@@
 \subsection{Damped least-squares solution}
-\label{sec:eql_inversion}
+\label{sec:eql-inversion}
 
@@
 $\mathbf{c}$.
-In practice, we find that suitable $\lambda$ values fall between $10^{-8}$ and
-$10^{-1}$, irrespective of the dataset, and that results are mostly sensitive
-to order-of-magnitude changes in $\lambda$.
 
@@
   \item Define a set of $M$ equivalent sources distributed throughout the
-    survey area (see section \ref{sec:source_distribution} for details).
+    survey area (see section \ref{sec:source-distribution} for details).
   \item Define a set of $K$ overlapping windows of equal size that cover the
@@
 
-To improve the convergence of the algorithm, \citet{friedman2002} suggests
+To improve the convergence of the algorithm, \citet{friedman2002} suggests that
 introducing randomness into the fitting process. We achieve this by randomizing
@@
 Therefore, the gradient boosting method allows us to fit
-equivalent source models that would produce Jacobian matrices that are larger
+equivalent sources models that would produce Jacobian matrices that are larger
 than the available computer memory.
@@
 Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
-the final \textit{gradient-boosted equivalent source algorithm}.
+the final \textit{gradient boosted equivalent source algorithm}.
 
@@
   \setstretch{1}
-  \caption{Gradient-boosted equivalent source algorithm.}
+  \caption{ Gradient boosted equivalent source algorithm. }
   \label{alg:gradient_boosting_window}
@@
 
-\subsection{Location of sources}
-\label{sec:source_distribution}
-
-The ideal number of sources and their locations, both horizontally and
-vertically, has been debated since the inception of the equivalent sources
-technique with \citet{dampney1969}.
-The choices made regarding these parameters can play an important role on the
-accuracy of the predictions and the computational resources needed to estimate
-the source coefficients.
-An ideal distribution of sources should simultaneously be able to reproduce the
-measured data on the survey points, make accurate predictions on non-surveyed
-locations, and minimize the required computational resources.
-
-A large number of evenly distributed sources along the survey region are
-capable of reproducing the observed data.
-Nevertheless, the computational load can be prohibitive and such
-underdetermined problems are prone to overfiting the data, leading to poor
-predictive power when interpolating and extrapolating.
-On the other hand, using few sources will reduce the computational requirements
-but the model may be incapable of reproducing the full spectral content of the
-measured data.
-
-Particular survey characteristics also play a role in the choice of equivalent
-source distribution.
-In a ground survey, observations are usually located along irregular paths and
-scattered points.
-The coverage of the survey region is often uneven, leaving large areas without
-any observation.
-On the other hand, observations from airborne surveys are located along almost
-straight and closely spaced flight lines.
-Measurements are usually taken at a high temporal frequency, leading to the
-observation points along the flight lines that are several times closer to each
-other than the flight line spacing.
-This creates a bias in the sampling, which can cause aliasing artifacts in
-gridded products.
-
-\subsubsection{Horizontal source layouts}
-
-The most widely used layouts for distributing equivalent sources horizontally
-are:
+\subsection{Source distributions}
+\label{sec:source-distribution}
+
+How to choose how many sources to use and where to locate them are not
+trivial decisions that play an important role on the accuracy of the
+predictions and the computational resources needed to fit the sources'
+coefficients.
+
+The chosen distribution of sources should simultaneously reproduce the measured
+data on the survey points and be able to make accurate predictions of the
+measured harmonic field on non observed locations.
+
+A high number of sources homogeneously distributed on the survey region are
+capable of reproducing the observed data. Nevertheless, too many sources will
+make the Jacobian matrix too large, what could introduce computational problems
+like the inability of storing the matrix on memory or a high computational time
+needed to fit the sources' coefficients.
+On the other hand, using very few sources will undoubtedly reduce the memory
+needs and lower the computational time when fitting the sources' coefficients.
+Nevertheless, it could be incapable of making accurate predictions or even
+reproducing the measured data if the number of sources is too low.
+
+The choice of the source distribution could also depend on the characteristic
+of the survey and how the observation points are distributed on the region.
+A ground survey usually consists in observation points located along irregular
+paths plus some possible scattered points.
+The survey region is usually heterogeneously covered, leaving areas without any
+observation.
+On the other hand, an airborne survey consists in observation points located
+along almost straight flight lines. The measurements are usually taken at
+a high frequency, so the observation points along the flight lines are very
+close to each other.
+This creates an anisotropy on the observation points: there are much more
+observation points along the flight lines directions.
+
+The most widely used source distributions are: a regular grid of point sources
+and one point source beneath each observation point.
+
+The \emph{regular grid} creates an homogeneous distribution of point sources
+below the surveyed region.
+The distance between sources is controlled by the grid spacing parameter.
+Keeping the boundaries of the grid constant, reducing the spacing increases the
+number of sources.
+
+The \emph{source below data} layout locates one source below each
+observation point, therefore the number of sources will be equal to the number
+of data points.
+
+When working with ground surveys, the \emph{regular grid} needs the grid
+spacing to be sufficiently small so observed values can be accurately
+reproduced by the source distribution.
+This will create too many sources on areas where no observation has been
+carried out.
+In contrast, the \emph{source below data} layout is more likely to accurately
+fit the observed data with much less sources, reducing the computational load
+to fit the equivalent sources' coefficients.
+
+When working with airborne surveys, the \emph{source below data} may
+generate an anisotropic distribution of sources by locating too many sources
+along the flight paths.
+It could lead to unwanted aliases on the predicted values.
+In contrast, the \emph{regular grid} won't generate aliases by homogeneously
+locating sources.
+
+We propose a new source distribution that could simultaneously reduce the
+computational load and remove the drawbacks of the preceding ones: the
+\emph{block averaged sources}.
+It consist in:
 
 \begin{enumerate}
-  \item
-    \emph{Regular grid}: a homogeneous distribution of point sources below the
-    survey region at a constant depth. A padding region is often added to help
-    reduce edge effects. In practice, it often leads to underdetermined problems
-    since a large number of sources is required ($N<M$).
-  \item
-    \emph{Sources below data points}: one equivalent source is placed below each
-    observation point at a given depth (often dependent on the distance to
-    neighboring data points). Therefore, the number of sources is be equal to
-    the number of observations ($N=M$).
+    \item Dividing the region in blocks of equal size. The size of the blocks
+        is controlled by a \emph{spacing} parameter.
+        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
+    \item Computing the median location of the observation points that fall
+        inside each block. Blocks without any observation point are ignored.
+    \item Locating one point source below each block averaged coordinate.
+        (see Fig.~\ref{fig:block-averaged-sources}(c)).
 \end{enumerate}
 
-For ground surveys, the \emph{regular-grid} layout needs a sufficiently
-small grid spacing to be able to fit the observed data.
-This creates an unnecessarily large number of sources in areas where no
-observations exist.
-In contrast, the \emph{sources-below-data} layout is more likely to accurately
-fit the observed data with many fewer sources, reducing the computational load.
-But when applied to airborne surveys, the \emph{source-below-data} layout may
-place an undesirably large number of sources along the flight paths.
-This could lead to aliasing effects on the predicted values, such as the
-stripes parallel to flight lines that are often observed when griding airborne
-magnetic data.
-In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
-distributing sources and using a continuous source layer (e.g.,
-right-rectangular prisms or tesseroids).
-
-We propose a new way of distributing equivalent sources horizontally that could
-simultaneously reduce the computational load and mitigate some of the drawbacks
-of existing layouts.
-In the \emph{block-averaged sources} layout,
-point sources are placed in the average
-position of data points that fall within specified spatial blocks
-(Fig.~\ref{fig:block-averaged-sources}).
-This is done by:
-
-\begin{enumerate}
-    \item Dividing the survey region into rectangular blocks of equal size.
-    \item Computing the median horizontal position of the observation points
-      that fall inside each block. Blocks without any observation point are
-      omitted.
-    \item Assign one point source to the median horizontal position calculated
-      in step 1.
-\end{enumerate}
-
-The number of sources created by this new layout will be less than the number
-of observations if the block size is chosen appropriately (i.e., making sure
-that blocks are large enough to contain more than a single data point).
-The overdetermined problem that arises from this layout has a lower
-computational load and is less prone to overfiting the data since the model
-complexity is lower.
-Moreover, the block averaging process can balance the spacing between sources
-along a flight line and between adjacent lines, helping to reduce aliasing
-effects in generated grids.
-
-Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
-observation points that simulates a ground survey, and the possible location of
-sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
-averaged sources} and (d) the \emph{grid sources} layouts.
+The number of sources created by this new distribution will be less or equal to
+the ones created by the \emph{source below data} and the \emph{regular
+grid} with the same spacing.
+Moreover, the sources are only located beneath populated blocks, so sources
+will be concentrated on regions where data has been gathered and no anisotropic
+distribution of sources will be generated.
 
@@
 
-\section{Performance of gradient-boosted equivalent sources}
+\section{Performance of gradient boosted equivalent sources}
 
@@
 \subsection{Window size}
-\label{sec:window_size}
+\label{sec:window-size}
 
@@
 achieved RMS against the values of the target grid and the time needed to fit
-the sources coefficients.
+the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
 In order to avoid any errors introduced by the way windows are shuffled, the
@@
 
-\subsection{Overlapping}
+We have also registered the computational time needed to fit the
+gradient-boosted equivalent sources for each window size and computed the ratio
+between these times and the computational time needed to fit the non-boosted
+equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against window size.
+        Window sizes are given as a fraction of the dimensions of the synthetic
+        survey area.
+        (a) Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different window sizes. Each RMS
+        error is the mean of the RMS produced by the same set of parameters but
+        with different random seeds.
+        (b) Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+}
+    \label{fig:gradient-boosted-window-size}
+\end{figure}
+
+From the results obtained from the comparison with the synthetic airborne
+survey we can conclude that smaller windows generate less accurate predictions
+than using larger ones and require significantly more computational time to fit
+the sources.
+The reduction of the accuracy might be due to an oversimplification of the
+least-squares problem, and the increase of the computational time might be
+generated by the great number of iterations required to fit the sources.
+As the windows gets larger, the accuracy starts increasing because more data
+points are included into the fitting process of the source coefficients, while
+the fitting process takes less time due to a reduction of the number of
+iterations.
+For very large windows, both accuracy and fitting time are almost constant.
+
+In comparison with the non-boosted equivalent sources, we can see that the
+gradient-boosted ones produce slightly less accurate results due to not being
+able to achieve the global minimum of the least-squares problem, but they
+perform faster.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
+When using gradient-boosted equivalent sources we can conclude that we want to
+maximize the window size as much as possible.
+The only limitation to do so is to generate Jacobian matrices larger than the
+available memory.
+Therefore we recommend using the largest window that generates Jacobian
+matrices that could fit in the available memory.
+
+\subsection{Amount of overlap}
 
@@
 The RMS was obtained as the mean RMS achieved by using different random seeds
-as we did on~\ref{sec:window_size}.
+as we did on~\ref{sec:window-size}.
+
+We have also computed the fitting time ratio for each overlap, in a similar way
+we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against amount of
+        overlap.
+        (a) Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different amount of overlap. Each
+        RMS error is the mean of the RMS produced by the same set of parameters
+        but with different random seeds.
+        (b) Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+    }
+    \label{fig:gradient-boosted-overlap}
+\end{figure}
+
+From the results obtained we can conclude that a lower values of overlap
+generates less accurate results, while a higher overlap increases the
+computational time required for fitting the source coefficients due to the
+significant increment of the number of overlapping windows.
+
+We found that overlaps less than 40\% produce very inaccurate predictions in
+comparison with the non-boosted equivalent sources, while values larger that
+80\% produce predictions with almost the same level of accuracy as the latter.
+Nevertheless, overlap values larger that 70\% takes significantly more
+computational time to fit the source coefficients.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
+We can then conclude that using overlap values between 40\% and 70\% generate
+a balance between predictions accuracy and computational time needed to fit the
+source coefficients.
+This corroborates that our naive choice of 50\% is good enough for producing
+accurate predictions in reasonable times.
 

### 2021-01-07 manuscript/manuscript.tex
Missing "data" word
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

--- 2021-01-06 manuscript/manuscript.tex
@@
 effects in generated grids.
+We will demonstrate through tests on synthetic data that the block-averaged sources
+layout is able to interpolate with comparable accuracy to other layouts while
+using a fraction of the equivalent sources.
 

### 2021-01-07 manuscript/manuscript.tex
Set the year in the header automatically
Remove duplicated "in contrast" at start of sentence

@@
 % ===========================================
-\newcommand{\Title}{
+\newcommand{\Title}{%
     Gradient-boosted equivalent sources
 }
-\newcommand{\Author}{
+\newcommand{\Author}{%
     S.R. Soler,
@@
 }
-\newcommand{\AuthorAffil}{
+\newcommand{\AuthorAffil}{%
     {\large
@@
 }
-\newcommand{\DOI}{
+\newcommand{\DOI}{%
     doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
 }
-\newcommand{\DOILink}{
+\newcommand{\DOILink}{%
     \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
@@
     \fontsize{9pt}{12pt}\selectfont
-    \Author{}, 2019. \DOI{}
+    \Author{} (\the\year{}). \DOI{}
 }
@@
 magnetic data.
-In contrast, the \emph{regular-grid} layout can avoid this effect by evenly
+The \emph{regular-grid} layout can avoid this effect by evenly
 distributing sources and using a continuous source layer (e.g.,

### 2021-01-07 manuscript/manuscript.tex
Rephrase lambda values part as a suggestion

@@
 $\mathbf{c}$.
-In practice, we find that suitable $\lambda$ values fall between $10^{-8}$ and
-$10^{-1}$, irrespective of the dataset, and that results are mostly sensitive
-to order-of-magnitude changes in $\lambda$.
+From experience, we recommend searching for suitable $\lambda$ values between
+$10^{-8}$ and $10^{2}$ varying by order-of-magnitude, irrespective of the
+dataset.
 

### 2021-01-07 manuscript/manuscript.tex
Start review of depths of sources section
Just moved a few things around but still need to revise the actual text.
Will do an enumerate to make it more similar to the horizontal layouts
section.

@@
 
-The depth of the point sources can be chosen following different criteria.
-Deep sources generate low frequencies, while shallow ones generate high
-frequencies (cite).
+It is widely known from potential theory that the depth of a point source
+influences the wavelength of the observed field at the surface.
+This makes the source depth a key parameter affecting the outcome of
+interpolation and other operations done with equivalent sources.
+Several different strategies for assigning the depths of equivalent sources
+have been proposed in the literature.
+
+\begin{enumerate}
+  \item
 The simplest option is to locate all sources at the same depth, which we will
@@
 points.
-
+ \item
 One possible solution is to locate each source below its corresponding
@@
 distance from their corresponding observation (or block averaged) point.
-
+ \item
 In case our survey presents heavily clustered data points on some areas, we may
@@
 (see Fig.~\ref{fig:depth-types}(c)).
+
 So, the depth of the sources can be computed as follows:
@@
 \citet{cordell1992, guspi2004, guspi2009}.
+\end{enumerate}
 
@@
 \end{figure*}
+
+We will test each of these strategies on synthetic data to evaluate their
+effectiveness.
 

### 2021-01-08 manuscript/manuscript.tex
Elaborate on the caption of figure about depths

@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
+    \caption{
+        Examples of different strategies for assigning depths to equivalent
+        sources.
+        Here we assign one source for each
+        observation point, located at the same horizontal coordinates as the
+        data points.
+        Source depths are
+        (a)~a \emph{constant depth} at a chosen vertical coordinate,
+        (b)~a \emph{relative depth} determined by uniformly shifting the
+        vertical coordinate of data points downwards,
+        and
+        (c)~a \emph{variable depth} determined by shifting the vertical
+        coordinates of the observation points by an amount proportional to the
+        average distance to neighbouring sources.
+        The distance between data points and their respective sources (a)
+        depends on observation height, (b) is constant, and (c) is proportional
+        to the horizontal distribution of sources.
+        Notice how the closely spaced sources in the middle of the profile (c)
+        are shallower than their counterparts in (b).
+    }
+    \label{fig:depth_types}
+\end{figure*}
+
 It is widely known from potential theory that the depth of a point source
@@
 have been proposed in the literature.
+Here, we will highlight the following (Fig.~\ref{fig:depth_types}):
 
@@
   \item
-The simplest option is to locate all sources at the same depth, which we will
-call \emph{constant depth} in the future (see Fig.~\ref{fig:depth-types}(a)).
+    \emph{Constant depth}:
+    The simplest option is to locate all sources at the same depth
+    (Fig.~\ref{fig:depth_types}a).
 If the measurement were taken at significantly different altitudes, the
@@
  \item
+    \emph{Relative depth}:
 One possible solution is to locate each source below its corresponding
@@
 observation (or block averaged) point minus a depth parameter that assumes the
-same value for all sources (see Fig.~\ref{fig:depth-types}(b)).
+same value for all sources (see Fig.~\ref{fig:depth_types}(b)).
 The sources won't be all at the same depth, but they will all be at the same
@@
  \item
+    \emph{Variable depth}:
 In case our survey presents heavily clustered data points on some areas, we may
@@
 to the mean distance to its $k$ nearest neighbour sources
-(see Fig.~\ref{fig:depth-types}(c)).
+(see Fig.~\ref{fig:depth_types}(c)).
 
@@
 \end{enumerate}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
-    \caption{
-        Depth types for locating point sources. We put one source beneath each
-        observation point (station) using:
-        (a)~a \emph{constant depth} where all sources are located at the same
-           depth,
-        (b)~a \emph{relative depth} where all sources are located at the same
-           vertical distance from its corresponding observation point, and
-        (c)~a \emph{variable depth} where the depth of the sources is
-           proportional to the average distance to its neighbour sources.
-           Notice how the clustered sources on (c) are relatively shallower
-           than the
-           other ones.
-    }
-    \label{fig:depth-types}
-\end{figure*}
 

### 2021-01-08 manuscript/manuscript.tex
Replace flowchart for an algorithm

--- 2021-01-07 manuscript/manuscript.tex
@@
 % ===========================================
-\newcommand{\Title}{%
-    Gradient-boosted equivalent sources
-}
-\newcommand{\Author}{%
+\newcommand{\Title}{
+    Gradient boosted equivalent sources
+}
+\newcommand{\Author}{
     S.R. Soler,
@@
 }
-\newcommand{\AuthorAffil}{%
+\newcommand{\AuthorAffil}{
     {\large
@@
 }
-\newcommand{\DOI}{%
+\newcommand{\DOI}{
     doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
 }
-\newcommand{\DOILink}{%
+\newcommand{\DOILink}{
     \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
@@
     \fontsize{9pt}{12pt}\selectfont
-    \Author{} (\the\year{}). \DOI{}
+    \Author{}, 2019. \DOI{}
 }
@@
 $\mathbf{c}$.
-From experience, we recommend searching for suitable $\lambda$ values between
-$10^{-8}$ and $10^{2}$ varying by order-of-magnitude, irrespective of the
-dataset.
 
@@
 
-\subsection{Location of sources}
-\label{sec:source_distribution}
-
-The ideal number of sources and their locations, both horizontally and
-vertically, has been debated since the inception of the equivalent sources
-technique with \citet{dampney1969}.
-The choices made regarding these parameters can play an important role on the
-accuracy of the predictions and the computational resources needed to estimate
-the source coefficients.
-An ideal distribution of sources should simultaneously be able to reproduce the
-measured data on the survey points, make accurate predictions on non-surveyed
-locations, and minimize the required computational resources.
-
-A large number of evenly distributed sources along the survey region are
-capable of reproducing the observed data.
-Nevertheless, the computational load can be prohibitive and such
-underdetermined problems are prone to overfiting the data, leading to poor
-predictive power when interpolating and extrapolating.
-On the other hand, using few sources will reduce the computational requirements
-but the model may be incapable of reproducing the full spectral content of the
-measured data.
-
-Particular survey characteristics also play a role in the choice of equivalent
-source distribution.
-In a ground survey, observations are usually located along irregular paths and
-scattered points.
-The coverage of the survey region is often uneven, leaving large areas without
-any observation.
-On the other hand, observations from airborne surveys are located along almost
-straight and closely spaced flight lines.
-Measurements are usually taken at a high temporal frequency, leading to the
-observation points along the flight lines that are several times closer to each
-other than the flight line spacing.
-This creates a bias in the sampling, which can cause aliasing artifacts in
-gridded products.
-
-\subsubsection{Horizontal source layouts}
+\subsection{Source distributions}
+\label{sec:source-distribution}
+
+How to choose how many sources to use and where to locate them are not
+trivial decisions that play an important role on the accuracy of the
+predictions and the computational resources needed to fit the sources'
+coefficients.
+
+The chosen distribution of sources should simultaneously reproduce the measured
+data on the survey points and be able to make accurate predictions of the
+measured harmonic field on non observed locations.
+
+A high number of sources homogeneously distributed on the survey region are
+capable of reproducing the observed data. Nevertheless, too many sources will
+make the Jacobian matrix too large, what could introduce computational problems
+like the inability of storing the matrix on memory or a high computational time
+needed to fit the sources' coefficients.
+On the other hand, using very few sources will undoubtedly reduce the memory
+needs and lower the computational time when fitting the sources' coefficients.
+Nevertheless, it could be incapable of making accurate predictions or even
+reproducing the measured data if the number of sources is too low.
+
+The choice of the source distribution could also depend on the characteristic
+of the survey and how the observation points are distributed on the region.
+A ground survey usually consists in observation points located along irregular
+paths plus some possible scattered points.
+The survey region is usually heterogeneously covered, leaving areas without any
+observation.
+On the other hand, an airborne survey consists in observation points located
+along almost straight flight lines. The measurements are usually taken at
+a high frequency, so the observation points along the flight lines are very
+close to each other.
+This creates an anisotropy on the observation points: there are much more
+observation points along the flight lines directions.
+
+The most widely used source distributions are: a regular grid of point sources
+and one point source beneath each observation point.
+
+The \emph{regular grid} creates an homogeneous distribution of point sources
+below the surveyed region.
+The distance between sources is controlled by the grid spacing parameter.
+Keeping the boundaries of the grid constant, reducing the spacing increases the
+number of sources.
+
+The \emph{source below data} layout locates one source below each
+observation point, therefore the number of sources will be equal to the number
+of data points.
+
+When working with ground surveys, the \emph{regular grid} needs the grid
+spacing to be sufficiently small so observed values can be accurately
+reproduced by the source distribution.
+This will create too many sources on areas where no observation has been
+carried out.
+In contrast, the \emph{source below data} layout is more likely to accurately
+fit the observed data with much less sources, reducing the computational load
+to fit the equivalent sources' coefficients.
+
+When working with airborne surveys, the \emph{source below data} may
+generate an anisotropic distribution of sources by locating too many sources
+along the flight paths.
+It could lead to unwanted aliases on the predicted values.
+In contrast, the \emph{regular grid} won't generate aliases by homogeneously
+locating sources.
+
+We propose a new source distribution that could simultaneously reduce the
+computational load and remove the drawbacks of the preceding ones: the
+\emph{block averaged sources}.
+It consist in:
+
+\begin{enumerate}
+    \item Dividing the region in blocks of equal size. The size of the blocks
+        is controlled by a \emph{spacing} parameter.
+        (see Fig.~\ref{fig:block-averaged-sources}(a)-(b)).
+    \item Computing the median location of the observation points that fall
+        inside each block. Blocks without any observation point are ignored.
+    \item Locating one point source below each block averaged coordinate.
+        (see Fig.~\ref{fig:block-averaged-sources}(c)).
+\end{enumerate}
+
+The number of sources created by this new distribution will be less or equal to
+the ones created by the \emph{source below data} and the \emph{regular
+grid} with the same spacing.
+Moreover, the sources are only located beneath populated blocks, so sources
+will be concentrated on regions where data has been gathered and no anisotropic
+distribution of sources will be generated.
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/block-averaged-sources-schematics.pdf}
+    \caption{
+        Block averaged sources.
+        (a)~Given a set of observation points
+        (b)~we divide the survey region on blocks of equal size and compute the
+            median location of the observation points that fall inside each
+            block.
+        (c)~A source point is located beneath each block averaged coordinate.
+            The number of point sources could be less or equal to the number of
+            observation points. No source is located beneath unpopulated
+            blocks.
+    }
+    \label{fig:block-averaged-sources}
+\end{figure*}
+
+Figure~\ref{fig:source-layouts-schematics} shows (a) an arbitrary set of
+observation points that simulates a ground survey, and the possible location of
+sources generated by (b) the \emph{sources below data}, (c) the new \emph{block
+averaged sources} and (d) the \emph{grid sources} layouts.
 
@@
     \caption{
-        Sketch of different horizontal layouts for equivalent source models.
-        Blue points represent the locations of observations and orange points
-        represent the locations of equivalent sources according to different
-        layout strategies.
-        (a) Set of \SourceLayoutsSchematicsObservations{} observation points
-        that simulate a ground survey.
+        Source layouts.
+        (a) Set of \SourceLayoutsSchematicsObservations{} synthetic observation
+            points that resemble a ground survey.
         (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
-        obtained through the \emph{sources-below-data} layout.
-        (c) Location of the \SourceLayoutsSchematicsGridSources{} sources
-        obtained through the \emph{regular-grid} layout.
-        (d) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
-        sources obtained through the \emph{block-averaged sources} layout.
-        Grey dashed lines represent the spatial blocks within which the median
-        observation location is calculated.
-    }
-    \label{fig:source_layouts}
+            obtained through the \emph{sources below data} layout.
+        (c) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
+            sources obtained through the \emph{block averaged sources} layout.
+        (d) Location of the \SourceLayoutsSchematicsGridSources{} sources
+            obtained through the \emph{grid sources} layout.
+    }
+    \label{fig:source-layouts-schematics}
 \end{figure*}
-
-The most widely used layouts for distributing equivalent sources horizontally
-are:
-
-\begin{enumerate}
-  \item
-    \emph{Sources below data points}: one equivalent source is placed at the
-    horizontal location of each data point (Fig.~\ref{fig:source_layouts}b).
-    Therefore, the number of sources is be equal to the number of observations
-    ($N=M$).
-  \item
-    \emph{Regular grid}: a homogeneous distribution of point sources below the
-    survey region (Fig.~\ref{fig:source_layouts}c). A padding region is often
-    added to help reduce edge effects. In practice, it often leads to
-    underdetermined problems since a large number of sources is required
-    ($N<M$).
-\end{enumerate}
-
-For ground surveys, the \emph{regular-grid} layout needs a sufficiently
-small grid spacing to be able to fit the observed data.
-This creates an unnecessarily large number of sources in areas where no
-observations exist.
-In contrast, the \emph{sources-below-data} layout is more likely to accurately
-fit the observed data with many fewer sources, reducing the computational load.
-But when applied to airborne surveys, the \emph{sources-below-data} layout may
-place an undesirably large number of sources along the flight paths.
-This could lead to aliasing effects on the predicted values, such as the
-stripes parallel to flight lines that are often observed when griding airborne
-magnetic data.
-The \emph{regular-grid} layout can avoid this effect by evenly
-distributing sources and using a continuous source layer (e.g.,
-right-rectangular prisms or tesseroids).
-
-We propose a new way of distributing equivalent sources horizontally that could
-simultaneously reduce the computational load and mitigate some of the drawbacks
-of existing layouts.
-In the \emph{block-averaged sources} layout,
-point sources are placed in the average
-position of data points that fall within specified spatial blocks
-(Fig.~\ref{fig:source_layouts}d).
-This is done by:
-
-\begin{enumerate}
-    \item Dividing the survey region into rectangular blocks of equal size.
-    \item Computing the median horizontal position of the observation points
-      that fall inside each block. Blocks without any observation point are
-      omitted.
-    \item Assign one point source to the median horizontal position calculated
-      in step 1.
-\end{enumerate}
-
-The number of sources created by this new layout will be less than the number
-of observations if the block size is chosen appropriately (i.e., making sure
-that blocks are large enough to contain more than a single data point).
-The overdetermined problem that arises from this layout has a lower
-computational load and is less prone to overfiting the data since the model
-complexity is lower.
-Moreover, the block averaging process can balance the spacing between sources
-along a flight line and between adjacent lines, helping to reduce aliasing
-effects in generated grids.
-We will demonstrate through tests on synthetic data that the block-averaged sources
-layout is able to interpolate with comparable accuracy to other layouts while
-using a fraction of the equivalent sources.
-
-\subsubsection{Depth of sources}
 
@@
 This process is carried out on both ground and airborne synthetic surveys.
-See Figure~\ref{fig:flowchart} for a graphical illustration of it.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/flowchart.pdf}
-    \caption{
-        Flowchart for comparing the performance of the source distributions.
-        For each source distribution we propose different values for its
-        parameters (see Tables~\ref{tab:parameters-ground-survey}
-        and~\ref{tab:parameters-airborne-survey}).
-        These values are then combined to obtain several set of parameters
-        which are iteratively submitted to the process illustrated on this
-        figure.
-        Finally we obtain the best prediction generated by each source
-        distribution as the one that achieves the best score.
-    }
-    \label{fig:flowchart}
-\end{figure}
+See Algorithm~\ref{alg:source_distributions_comparison} for a concise
+representation of it.
+
+\begin{algorithm}[!h]
+  \DontPrintSemicolon
+  \setstretch{1.5}
+
+  combine parameter values
+  \;
+
+  \For{each set of parameters}{
+
+    create the equivalent sources
+    \;
+
+    fit source coefficients
+    \;
+
+    predict field values on target grid points
+    \;
+
+    score the prediction
+    \;
+  }
+
+  determine the best prediction
+  \;
+
+  \BlankLine
+  \setstretch{1}
+  \caption{Algorithm for estimating the best prediction using synthetic data.}
+  \label{alg:source_distributions_comparison}
+\end{algorithm}
 
@@
 The RMS was obtained as the mean RMS achieved by using different random seeds
-as we did on~\ref{sec:window_size}.
+as we did on~\ref{sec:window-size}.
 

### 2021-01-08 manuscript/manuscript.tex
Minor changes
Apply suggestions from code review
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

--- 2021-01-08 manuscript/manuscript.tex
@@
     (Fig.~\ref{fig:depth_types}a).
-If the measurement were taken at significantly different altitudes, the
-elevated computation points will be more distant to the sources than the lower
-ones.
-This may create problems on reproducing high frequencies on the elevated
-points.
+    If the measurements were taken at significantly different altitudes, some
+    measurements will be more distant to the sources than others,
+    which may create problems for reproducing short wavelengths in high
+    altitude points.
  \item
     \emph{Relative depth}:
-One possible solution is to locate each source below its corresponding
-observation (or block averaged) point at a constant \emph{relative depth}
-from it.
-The depth of each source can be computed as the height of its corresponding
-observation (or block averaged) point minus a depth parameter that assumes the
-same value for all sources (see Fig.~\ref{fig:depth_types}(b)).
-The sources won't be all at the same depth, but they will all be at the same
-distance from their corresponding observation (or block averaged) point.
+    The depths of sources are determined by shifting the vertical coordinate of
+    data points downward by a fixed amount (Fig.~\ref{fig:depth_types}b).
+    The sources will not all be at the same vertical coordinate, but they will
+    all be at the same vertical distance from the observation points.
  \item
     \emph{Variable depth}:
-In case our survey presents heavily clustered data points on some areas, we may
-want the sources below that region to be shallower in order to reproduce the
-high frequencies measured by these clustered observation points.
-We can propose a \emph{variable depth} approach: it locates each point source
-according to the \emph{relative depth} and then subtracts a term proportional
-to the mean distance to its $k$ nearest neighbour sources
-(see Fig.~\ref{fig:depth_types}(c)).
-
-So, the depth of the sources can be computed as follows:
+    The depths of sources are proportional to the horizontal distance to the
+    nearest neighbouring data points or sources (Fig.~\ref{fig:depth_types}c).
+    Different variations of this strategy have been proposed before, for
+    example \citet{cordell1992}, \citet{guspi2004}, and \citet{guspi2009}.
+    The rationale for this strategy is that if a survey has data points
+    clustered in some areas, we may
+    want the sources below those areas to be shallower in order to preserve the
+    shorter wavelengths that can be measured.
+\end{enumerate}
+
+Our approach to the \emph{variable depth} strategy will be:
 
 \begin{equation}
-    \begin{split}
-        \textrm{depth} =
-           &\textrm{data point height} - \textrm{relative depth} \\
-           &- \textrm{depth factor} \cdot \textrm{mean distance}
-    \end{split}
+  z = z_{obs} + \Delta z + \alpha h,
 \end{equation}
 
-\noindent where \emph{data point height} is the elevation of the corresponding
-observation (or block averaged) point, \emph{mean distance} is the mean
-distance to the $k$ nearest source neighbours, \emph{depth factor} and
-\emph{relative depth} are parameters.
-The addition of this new term will make clustered sources to be shallower than
-scattered and distant sources.
-
-Similar approaches for setting sources at depths that depend
-on the distance to their nearest neighbours were already proposed by
-\citet{cordell1992, guspi2004, guspi2009}.
-\end{enumerate}
-
-We will test each of these strategies on synthetic data to evaluate their
-effectiveness.
+\noindent
+in which $z$ is the depth of an equivalent source,
+$\Delta z$ is a relative depth shift that is the same for all sources,
+$\alpha$ is an adimensional depth factor,
+$h$ is the median horizontal distance to the $k$ nearest neighbouring sources,
+and
+$z_{obs}$ is a vertical observation coordinate that will depend on the
+horizontal layout strategy.
+For \emph{sources-below-data}, it is the vertical coordinate of the data point
+corresponding to the given source.
+For \emph{regular-grid}, it can be interpolated from the vertical coordinates
+of all data points.
+Finally, for \emph{block-averaged-sources} it will be the average vertical
+coordinate of data within the corresponding block.
+
+In the following sections, we will test the effectiveness and trade-offs of
+each of these strategies on synthetic data.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Comparison of source distributions}
 
@@
 \end{table*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Comparison of source distributions}
 

### 2021-01-08 manuscript/manuscript.tex
Improve first steps of algorithm

@@
 This process is carried out on both ground and airborne synthetic surveys.
-See Figure~\ref{fig:flowchart} for a graphical illustration of it.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/flowchart.pdf}
-    \caption{
-        Flowchart for comparing the performance of the source distributions.
-        For each source distribution we propose different values for its
-        parameters (see Tables~\ref{tab:parameters-ground-survey}
-        and~\ref{tab:parameters-airborne-survey}).
-        These values are then combined to obtain several set of parameters
-        which are iteratively submitted to the process illustrated on this
-        figure.
-        Finally we obtain the best prediction generated by each source
-        distribution as the one that achieves the best score.
-    }
-    \label{fig:flowchart}
-\end{figure}
+See Algorithm~\ref{alg:source_distributions_comparison} for a concise
+representation of it.
+
+\begin{algorithm}[!h]
+  \DontPrintSemicolon
+  \setstretch{1.5}
+
+  define possible values for each parameter
+  \;
+
+  generate each possible combination of parameters values: obtain several
+  \emph{set of parameters}
+  \;
+
+  \For{each set of parameters}{
+
+    select the $M$ locations of the equivalent sources
+    \;
+
+    estimate the source coefficients
+    \;
+
+    predict field values on target grid points
+    \;
+
+    calculate the RMS between the predictions and the target grid
+    \;
+  }
+
+  the best set of parameters produces the smallest RMS
+  \;
+
+  \BlankLine
+  \setstretch{1}
+  \caption{Algorithm for estimating the best prediction using synthetic data.}
+  \label{alg:source_distributions_comparison}
+\end{algorithm}
 

### 2021-01-08 manuscript/manuscript.tex

--- 2021-01-08 manuscript/manuscript.tex
@@
 
+We have also computed the fitting time ratio for each overlap, in a similar way
+we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against amount of
+        overlap.
+        (a) Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different amount of overlap. Each
+        RMS error is the mean of the RMS produced by the same set of parameters
+        but with different random seeds.
+        (b) Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+    }
+    \label{fig:gradient-boosted-overlap}
+\end{figure}
+
+From the results obtained we can conclude that a lower values of overlap
+generates less accurate results, while a higher overlap increases the
+computational time required for fitting the source coefficients due to the
+significant increment of the number of overlapping windows.
+
+We found that overlaps less than 40\% produce very inaccurate predictions in
+comparison with the non-boosted equivalent sources, while values larger that
+80\% produce predictions with almost the same level of accuracy as the latter.
+Nevertheless, overlap values larger that 70\% takes significantly more
+computational time to fit the source coefficients.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
+We can then conclude that using overlap values between 40\% and 70\% generate
+a balance between predictions accuracy and computational time needed to fit the
+source coefficients.
+This corroborates that our naive choice of 50\% is good enough for producing
+accurate predictions in reasonable times.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-08 manuscript/manuscript.tex

--- 2021-01-08 manuscript/manuscript.tex
@@
 interpolating only on regular grids \citep{leao1989},
-or requiring already gridded data (CITE PINGA NEW PAPER),
+or requiring already gridded data \citep{takahashi2020},
 to name a few.

### 2021-01-12 manuscript/manuscript.tex
Put tildes after enumerating subplots on captions

@@
         survey area.
-        (a) Root-mean-squared error between predictions and target grid using
+        (a)~Root-mean-squared error between predictions and target grid using
         non-boosted sources (orange dashed line) and gradient-boosted
@@
         with different random seeds.
-        (b) Ratio between the computational times needed to fit the
+        (b)~Ratio between the computational times needed to fit the
         gradient-boosted and the non-boosted equivalent sources, respectively
@@
         overlap.
-        (a) Root-mean-squared error between predictions and target grid using
+        (a)~Root-mean-squared error between predictions and target grid using
         non-boosted sources (orange dashed line) and gradient-boosted
@@
         but with different random seeds.
-        (b) Ratio between the computational times needed to fit the
+        (b)~Ratio between the computational times needed to fit the
         gradient-boosted and the non-boosted equivalent sources, respectively

### 2021-01-12 manuscript/manuscript.tex
Replace flowchart for an algorithm (#91)
Remove the flowchart image for illustrating the process for estimating the best prediction for synthetic data.
Replace it with an algorithm instead.

--- 2021-01-08 manuscript/manuscript.tex
@@
 This process is carried out on both ground and airborne synthetic surveys.
-See Figure~\ref{fig:flowchart} for a graphical illustration of it.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/flowchart.pdf}
-    \caption{
-        Flowchart for comparing the performance of the source distributions.
-        For each source distribution we propose different values for its
-        parameters (see Tables~\ref{tab:parameters-ground-survey}
-        and~\ref{tab:parameters-airborne-survey}).
-        These values are then combined to obtain several set of parameters
-        which are iteratively submitted to the process illustrated on this
-        figure.
-        Finally we obtain the best prediction generated by each source
-        distribution as the one that achieves the best score.
-    }
-    \label{fig:flowchart}
-\end{figure}
+See Algorithm~\ref{alg:source_distributions_comparison} for a concise
+representation of it.
+
+\begin{algorithm}[!h]
+  \DontPrintSemicolon
+  \setstretch{1.5}
+
+  define possible values for each parameter
+  \;
+
+  generate each possible combination of parameters values: obtain several
+  \emph{sets of parameters}
+  \;
+
+  \For{each set of parameters}{
+
+    select the $M$ locations of the equivalent sources
+    \;
+
+    estimate the source coefficients
+    \;
+
+    predict field values on target grid points
+    \;
+
+    calculate the RMS between the predictions and the target grid
+    \;
+  }
+
+  the best set of parameters produces the smallest RMS
+  \;
+
+  \BlankLine
+  \setstretch{1}
+  \caption{Algorithm for estimating the best prediction using synthetic data.}
+  \label{alg:source_distributions_comparison}
+\end{algorithm}
 

### 2021-01-14 manuscript/manuscript.tex
Reorganize results into a "Synthetic data" section
This will group all results from synthetic data applications. Moved the
discussion subsection to a "Discussion" section where we'll discuss all
of the results from the paper.
Start including Australia gravity into manuscript

@@
 
+Our final goal is to show how gradient-boosted equivalent sources can be used
+to interpolate a very large dataset of gravity data into a regular grid.
+We selected a compilation of gravity surveys over Australia made by
+\citet{wynne2018}.
+It consists in more than 1.7 million data points that cover most part of the
+Australia territory obtained through observations on ground
+(see Fig.~\ref{fig:australia-data}).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/australia-data.pdf}
+    \caption{
+    }
+    \label{fig:australia-data}
+\end{figure}
+
+First we compute the gravity disturbance by removing the normal gravity from
+the observed gravity data (see Fig.~\ref{fig:australia-disturbance}).
+The normal gravity is computed on each observation point through the
+closed-form formula given by \citet{li2001} and using the WGS84 ellipsoid as
+reference.
+Then we obtain plain coordinates of the observation points by applying
+a Mercator projection.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/australia-disturbance.pdf}
+    \caption{
+    }
+    \label{fig:australia-disturbance}
+\end{figure}
+
+We start the interpolation process by defining a set of block-averaged sources
+at a relative depth of \AustraliaRelativeDepth{}.
+The choice of the block spacing must be done taking into account the desired
+resolution of the final grid.
+If the grid will have a much higher resolution than the block spacing, the
+equivalent sources will not be able to reproduce the high frequency components
+of the data.
+Therefore we recommend setting a block spacing that matches the resolution of
+the final grid.
+In this case we will generate a regular grid with a resolution of 1~arc-minute,
+which can be approximated by \SI{1.8}{\kilometer} for the Earth.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-15 notebooks/98-generate_latex_variables.py
Create australia.tex file

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.7.1
+#       jupytext_version: 1.9.1
 #   kernelspec:
 #     display_name: Python [conda env:eql-gradient-boosted]
 #     language: python
@@ -249,6 +249,33 @@ with open(json_file, "r") as f:
     variables = json.loads(f.read())
 
 units["boost_overlapping_window_size"] = "meter"
+# -
+
+latex_variables = [
+    create_latex_variable(key, value, unit=units[key])
+    for key, value in variables.items()
+]
+display(latex_variables)
+
+with open(tex_file, "w") as f:
+    f.write("\n".join(latex_variables))
+
+# ## Australia gravity
+
+# +
+json_file = results_dir / "australia.json"
+tex_file = manuscript_dir / "australia.tex"
+
+with open(json_file, "r") as f:
+    variables = json.loads(f.read())
+
+variables["australia_eql_window_size"] *= 1e-3
+
+units["australia_eql_depth"] = "meter"
+units["australia_eql_damping"] = None
+units["australia_eql_spacing"] = "meter"
+units["australia_eql_window_size"] = "kilometer"
+units["australia_eql_n_sources"] = None
 # -
 
 latex_variables = [

### 2021-01-15 notebooks/98-generate_latex_variables.py
Fix kilo meter unit on australia.tex

@@ -274,7 +274,7 @@ variables["australia_eql_window_size"] *= 1e-3
 units["australia_eql_depth"] = "meter"
 units["australia_eql_damping"] = None
 units["australia_eql_spacing"] = "meter"
-units["australia_eql_window_size"] = "kilometer"
+units["australia_eql_window_size"] = "kilo meter"
 units["australia_eql_n_sources"] = None
 # -
 

### 2021-01-15 manuscript/manuscript.tex
Incorporate australia figures to manuscript

@@
 \input{boost-overlapping.tex}
+\input{australia.tex}
 
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/australia-data.pdf}
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
     \caption{
     }
-    \label{fig:australia-data}
-\end{figure}
+    \label{fig:australia-data-gravity}
+\end{figure*}
 
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/australia-disturbance.pdf}
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
     \caption{
     }
-    \label{fig:australia-disturbance}
-\end{figure}
+    \label{fig:australia-data-disturbance}
+\end{figure*}
 
 We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaRelativeDepth{}.
+at a relative depth of \AustraliaEqlDepth{}.
 The choice of the block spacing must be done taking into account the desired
@@
 In this case we will generate a regular grid with a resolution of 1~arc-minute,
-which can be approximated by \SI{1.8}{\kilometer} for the Earth.
+which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia-grid.png}
+    \caption{
+    }
+    \label{fig:australia-grid}
+\end{figure*}
 

### 2021-01-15 notebooks/99-figures.py

@@ -525,16 +525,19 @@ fig.plot(
     x=australia_data.longitude,
     y=australia_data.latitude,
     color=australia_data.gravity,
-    style="c1p",
+    style="c0.5p",
     cmap=True,
 )
 fig.colorbar(frame='af+l"Observed gravity [mGal]"')
 fig.coast(shorelines=True)
 fig.savefig(figs_dir / "australia-data-gravity.png")
 fig.show()
+# -
 
-# +
-maxabs = vd.maxabs(australia_data.disturbance.values)
+maxabs = vd.maxabs(
+    australia_data.disturbance.values,
+    australia_grid.disturbance.values,
+)
 
 fig = pygmt.Figure()
 fig.basemap(region=region, projection=proj_gmt, frame=["afg"])
@@ -543,16 +546,13 @@ fig.plot(
     x=australia_data.longitude,
     y=australia_data.latitude,
     color=australia_data.disturbance,
-    style="c1p",
+    style="c0.5p",
     cmap=True,
 )
-fig.colorbar(frame='af+l"Gravity Disturbance[mGal]"')
+fig.colorbar(frame='xa50+l"Gravity Disturbance[mGal]"')
 fig.coast(shorelines=True)
 fig.savefig(figs_dir / "australia-data-disturbance.png")
 fig.show()
-
-# +
-maxabs = vd.maxabs(australia_grid.disturbance.values)
 
 fig = pygmt.Figure()
 fig.basemap(region=region, projection=proj_gmt, frame=["afg"])
@@ -560,8 +560,9 @@ pygmt.makecpt(cmap="polar", series=(-maxabs, maxabs))
 fig.grdimage(
     australia_grid.disturbance,
     nan_transparent=True,
+    shading="",
 )
-fig.colorbar(frame='af+l"Gravity Disturbance [mGal]"')
+fig.colorbar(frame='xa50+l"Gravity Disturbance [mGal]"')
 fig.coast(shorelines=True)
 fig.savefig(figs_dir / "australia-grid.png")
 fig.show()

### 2021-01-18 manuscript/manuscript.tex
Advance on manuscript

@@
 Australia territory obtained through observations on ground
-(see Fig.~\ref{fig:australia-data}).
+(see Fig.~\ref{fig:australia-data-gravity}).
 
@@
     \caption{
+        Gravity data for Australia composed by more than 1.7 million
+        observations on ground \citep{wynne2018}. The data is available under
+        the Creative Commons Attribution 4.0 International Licence.
     }
@@
 First we compute the gravity disturbance by removing the normal gravity from
-the observed gravity data (see Fig.~\ref{fig:australia-disturbance}).
+the observed gravity data (see Fig.~\ref{fig:australia-data-disturbance}).
 The normal gravity is computed on each observation point through the
-closed-form formula given by \citet{li2001} and using the WGS84 ellipsoid as
-reference.
+closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
+as reference.
 Then we obtain plain coordinates of the observation points by applying
@@
     \caption{
+        Gravity disturbance of Australia computed as the difference between
+        observed gravity and normal gravity generated by the WGS84 ellipsoid on
+        each observation point.
     }
@@
 We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{}.
+at a relative depth of \AustraliaEqlDepth{} and a block spacing of
+\SI{1.8}{\kilo\meter}.
+These parameters create \AustraliaEqlNSources{}~point sources.
 The choice of the block spacing must be done taking into account the desired
@@
 
+The coefficients of the gradient-boosted equivalent sources are estimated using
+a damping equal to \AustraliaEqlDamping{} and a window size of
+\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
+store the largest Jacobian matrix to 10GB.
+
+Finally, the equivalent sources are used to predict the values of the gravity
+disturbance on a regular grid of
+\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
+\AustraliaEqlGridHeight{} above the ellipsoid
+(see Fig.~\ref{fig:australia-grid}).
+
 \begin{figure*}
@@
     \caption{
+        Interpolated gravity disturbance of Australia on a regular grid at
+        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
+        were obtained through gradient-boosted equivalent sources.
     }

### 2021-01-18 manuscript/manuscript.tex
Start writing software implementation

@@
 \usepackage{setspace}
+
+% Define style for urls
+\urlstyle{same}
 
@@
 
+\section{Software implementation}
+
+We have implemented the methods described in the previous sections though
+a software written in Python language.
+The code for generating the results of this work are available in
+\url{https://doi.org/10.6084/m9.figshare.13604360}.
+The gradient-boosted equivalent sources implementation is based on the
+non-boosted sources available through the Harmonica library
+\citep{harmonica2020}, part of the Fatiando a Terra project
+\citep{fatiando2013}.
+Another Python libraries were used:
+Verde \citep{verde2018} to apply block reductions and managing coordinates,
+Boule \citep{boule2020} for computing normal gravity,
+Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
+multidimensional datasets and numerical
+computations,
+Numba \citep{numba2015} for writing pre-comipled implementations and
+parallelization,
+Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
+the figures.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusions}

### 2021-01-19 manuscript/manuscript.tex
Add github repository url
Start writing the conclusions

--- 2021-01-18 manuscript/manuscript.tex
@@
 
+Equivalent sources that uses the inverse of the distance as the Green's
+functions are well suited for interpolating gravity disturbance data.
+Block-averaged sources reduces the number of point sources, reducing the
+computational load needed to estimate their coefficients, preventing aliasing
+on the interpolated values while maintaining accurate predictions.
+Special attention must be payed when choosing the size of the block spacing:
+as a thumb rule, it must be approximately equal to the resolution of the
+regular grid where the values will be interpolated.
+The three compared strategies for setting the depth of the sources (constant
+depth, relative depth and variable depth) don't significantly affect
+the accuracy of the interpolations.
+Nevertheless, the choice of the parameters for each depth strategy does affects
+the accuracy and the frequency components of the interpolations.
+
+Gradient-boosted equivalent sources heavily reduces the computer memory
+needed to estimate source coefficients, making possible to interpolate even
+very large datasets.
+The interpolations obtained though this new method achieve almost the same
+accuracy than the non-boosted sources, while reducing the computation time
+needed to estimate the source coefficients.
+Because it doesn't involve any assumption on the location of the sources, it
+can be used in conjunction with any horizontal source layout and any strategy
+for setting their depth.
+Moreover, the results equivalent sources can be used not only for interpolating
+on a regular grid, but also on any set of observation points, allowing to
+create profiles or upward continuations.
+In order to maximize the accuracy of the interpolations, the size of the
+rolling windows must be chosen as the maximum value that creates Jacobian
+matrices that fit into our computer memory.
+Therefore its choice is subject to the particular infrastructure where the
+interpolation will be carried out.
+We have shown that an overlap of 50\% between adjacent windows achieves a good
+compromise between accuracy and computation time needed to fit the source
+coefficients.
+
+The gradient-boosted equivalent sources were used to interpolate a compilation
+of more than 1.7 million gravity points from Australia on a regular grid with
+a resolution of 1~arc-minute.
+The whole process was carried out on a modest personal computer, requiring
+a maximum of 10GB of memory.
+This shows how the new gradient-boosted equivalent sources can be applied to
+real-world data.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-21 manuscript/manuscript.tex
Merge the synthetic survey figures into 1
Make a full page figure instead with all the synthetic survey layouts
to simplify the caption and make sure the figures don't end up scattered
throughout the paper.

--- 2021-01-18 manuscript/manuscript.tex
@@
 
-\section{Comparison of source distributions}
+\section{Tests on synthetic data}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
+    \caption{
+        Pseudo-color map of the target grid of synthetic gravity data. The grid
+        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
+        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
+        above the zero height plane.
+    }
+    \label{fig:synthetic-target}
+\end{figure}
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
+    \caption{
+        Maps of the observation locations and gravity values for the synthetic
+        ground and airborne surveys.
+        (a)~Horizontal position and height of the ground survey points.
+        (b)~Synthetic gravity data calculated on the ground survey points with
+        added pseudo-random Gaussian noise.
+        (c)~Horizontal position and height of the airborne survey points.
+        (d)~Synthetic gravity data calculated on the airborne survey points
+        with added pseudo-random Gaussian noise.
+        For (a) and (b), height is given in meters above the zero height plane.
+    }
+    \label{fig:synthetic-layouts}
+\end{figure*}
+
+Start with a description of the model and surveys. This is common for all
+tests.
+
+The synthetic model is made out of \NPrisms{} prisms distributed on a region of
+\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
+height plane.
+Density contrast of prisms range from \ModelMinDensity{} and
+\ModelMaxDensity{}.
+We built deep big and thin shallow prisms for creating gravity anomalies with
+long and short wavelengths, respectively.
+
+The vertical component of the gravity acceleration generated by the synthetic
+model has been computed on a regular grid of
+\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
+\TargetSpacing{} located \TargetHeight{} above the zero height plane
+(Fig.~\ref{fig:synthetic-target}), using \citet{nagy2000} and \citet{nagy2002}.
+We will refer to this grid as the \emph{target} grid in the future.
+
+In order to compare the predictive capabilities of each source distribution
+under on different surveys, we created a ground and an airborne \emph{synthetic
+surveys}.
+For creating the synthetic ground survey we selected a portion of the Southern
+Africa Gravity Data available through the
+\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
+For the airborne survey we used a portion of the Great Britain Aeromagnetic
+Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
+Ltd between 1955 and 1965 and made available by the
+\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
+British Geological Survey (BGS)
+}.
+
+On both cases we selected only a portion of the survey and rescaled it to span
+on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
+The ground survey is composed by \GroundSurveyPoints{} observation points
+distributed at heights ranging between \GroundSurveyMinHeight{} and
+\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-layouts}a).
+While the airborne survey has \AirborneSurveyPoints{} points at heights between
+\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
+(Fig.~\ref{fig:synthetic-layouts}c).
+
+The vertical component of the gravity acceleration generated by the synthetic
+model has been computed on both surveys.
+Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
+to the effect of the synthetic model to simulate acquisition errors
+(Figs.~\ref{fig:synthetic-layouts}b
+and~\ref{fig:synthetic-layouts}d).
+
+\subsection{Comparison of source distribution strategies}
 
@@
 computational load needed to do it.
-
-\subsection{Synthetic Model}
-
-%Describe forward model made out of prisms.
-%Show prisms model?
-
-The synthetic model is made out of \NPrisms{} prisms distributed on a region of
-\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
-height plane.
-Density contrast of prisms range from \ModelMinDensity{} and
-\ModelMaxDensity{}.
-We built deep big and thin shallow prisms for creating gravity anomalies with
-long and short wavelengths, respectively.
-
-The vertical component of the gravity acceleration generated by the synthetic
-model has been computed on a regular grid of
-\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
-\TargetSpacing{} located \TargetHeight{} above the zero height plane
-(Fig.~\ref{fig:target-grid}), using \citet{nagy2000} and \citet{nagy2002}.
-We will refer to this grid as the \emph{target} grid in the future.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
-    \caption{
-        Target grid. Gravitational effect of synthetic model on a regular grid
-        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
-        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
-        zero height plane.
-    }
-    \label{fig:target-grid}
-\end{figure}
-
-\subsection{Synthetic Surveys}
-
-In order to compare the predictive capabilities of each source distribution
-under on different surveys, we created a ground and an airborne \emph{synthetic
-surveys}.
-For creating the synthetic ground survey we selected a portion of the Southern
-Africa Gravity Data available through the
-\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
-For the airborne survey we used a portion of the Great Britain Aeromagnetic
-Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
-Ltd between 1955 and 1965 and made available by the
-\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
-British Geological Survey (BGS)
-}.
-
-On both cases we selected only a portion of the survey and rescaled it to span
-on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
-The ground survey is composed by \GroundSurveyPoints{} observation points
-distributed at heights ranging between \GroundSurveyMinHeight{} and
-\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
-While the airborne survey has \AirborneSurveyPoints{} points at heights between
-\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
-(Fig.~\ref{fig:synthetic-ground-survey}(a)).
-
-The vertical component of the gravity acceleration generated by the synthetic
-model has been computed on both surveys.
-Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
-to the effect of the synthetic model to simulate acquisition errors
-(Figs.~\ref{fig:synthetic-ground-survey}(b)
-and~\ref{fig:synthetic-airborne-survey}(b)).
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
-    \caption{
-        Synthetic ground survey.
-        (a)~Location of observation points. Altitude given in meters above the
-            zero height plane.
-        (b)~Vertical component of gravity acceleration generated by the
-            synthetic model plus Gaussian noise on the ground survey
-            observation points.
-    }
-    \label{fig:synthetic-ground-survey}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/airborne-survey.pdf}
-    \caption{
-        Synthetic airborne survey.
-        (a)~Location of observation points. Altitude given in meters above the
-            zero height plane.
-        (b)~Vertical component of gravity acceleration generated by the
-            synthetic model plus Gaussian noise on the airborne survey
-            observation points.
-        Based upon the Great Britain aeromagnetic data, with the permission of
-        the British Geological Survey.
-    }
-    \label{fig:synthetic-airborne-survey}
-\end{figure}
-
-\subsection{Comparisons}
 
@@
 
-\subsection{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Performance and accuracy of gradient boosting}
+
+Our second goal is to assess the accuracy of the predictions achieved by the
+gradient boosting algorithm while registering its performance by comparison
+with the non-boosted equivalent sources.
+
+\subsubsection{Window size}
+\label{sec:window_size}
+
+One factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the size of the overlapping windows used to create
+each set of equivalent sources.
+The size of the windows controls the size of the Jacobian matrices
+$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
+Thus, using smaller windows will reduce the amount of computer memory needed to
+fit the source coefficients.
+Nevertheless, smaller windows may produce less accurate predictions because
+their inability to achieve the global minimum of the misfit from
+equation~\ref{eq:misfit-unscaled}.
+Besides, the window size might also impact on the computation time needed to
+fit the source coefficients: smaller windows will generate simpler least-square
+problems which are easier to solve, but they will also create more iterations.
+
+We want to assess how the size of the overlapping windows impacts both the
+accuracy of the predictions and the computation time needed to fit the source
+coefficients in comparison with the performance of the non-boosted equivalent
+sources.
+
+We applied the gradient boosted equivalent sources to interpolate the synthetic
+airborne survey on the same points of the target grid.
+We selected several window sizes to assess how accuracy and performance depend
+on that variable.
+For each window size we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
+of 50\%, and with different values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each window size and the damping value used to
+obtain it.
+
+Using the best set of parameters for each window size, we registered the
+achieved RMS against the values of the target grid and the time needed to fit
+the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
+In order to avoid any errors introduced by the way windows are shuffled, the
+RMS for each window size was obtained as the mean RMS achieved by using
+different random seeds.
+
+We have also registered the computational time needed to fit the
+gradient-boosted equivalent sources for each window size and computed the ratio
+between these times and the computational time needed to fit the non-boosted
+equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against window size.
+        Window sizes are given as a fraction of the dimensions of the synthetic
+        survey area.
+        (a)~Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different window sizes. Each RMS
+        error is the mean of the RMS produced by the same set of parameters but
+        with different random seeds.
+        (b)~Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+}
+    \label{fig:gradient-boosted-window-size}
+\end{figure}
+
+From the results obtained from the comparison with the synthetic airborne
+survey we can conclude that smaller windows generate less accurate predictions
+than using larger ones and require significantly more computational time to fit
+the sources.
+The reduction of the accuracy might be due to an oversimplification of the
+least-squares problem, and the increase of the computational time might be
+generated by the great number of iterations required to fit the sources.
+As the windows gets larger, the accuracy starts increasing because more data
+points are included into the fitting process of the source coefficients, while
+the fitting process takes less time due to a reduction of the number of
+iterations.
+For very large windows, both accuracy and fitting time are almost constant.
+
+In comparison with the non-boosted equivalent sources, we can see that the
+gradient-boosted ones produce slightly less accurate results due to not being
+able to achieve the global minimum of the least-squares problem, but they
+perform faster.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
+When using gradient-boosted equivalent sources we can conclude that we want to
+maximize the window size as much as possible.
+The only limitation to do so is to generate Jacobian matrices larger than the
+available memory.
+Therefore we recommend using the largest window that generates Jacobian
+matrices that could fit in the available memory.
+
+\subsubsection{Amount of overlap}
+
+Another factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the amount of overlap between adjacent windows.
+The previous choice of 50\% showed to be sufficiently good to achieve
+acceptable accuracy, although a deeper study should be carried out to assess
+how the amount of overlap impacts both accuracy and fitting time.
+
+We interpolated the synthetic airborne survey using the gradient boosted
+equivalent sources on the same points of the target grid.
+The interpolations were carried out using different amount of overlap, from
+0\% to 0.95\% with a step size of 0.05\%.
+For each overlap we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
+a window size of \BoostOverlappingWindowSize, and with different
+values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each overlap and the damping value used to
+obtain it.
+
+Using the best set of parameters for each overlap, we registered the achieved
+RMS against the values of the target grid and the time needed to fit the
+sources coefficients.
+The RMS was obtained as the mean RMS achieved by using different random seeds
+as we did on~\ref{sec:window_size}.
+
+We have also computed the fitting time ratio for each overlap, in a similar way
+we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against amount of
+        overlap.
+        (a)~Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different amount of overlap. Each
+        RMS error is the mean of the RMS produced by the same set of parameters
+        but with different random seeds.
+        (b)~Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+    }
+    \label{fig:gradient-boosted-overlap}
+\end{figure}
+
+From the results obtained we can conclude that a lower values of overlap
+generates less accurate results, while a higher overlap increases the
+computational time required for fitting the source coefficients due to the
+significant increment of the number of overlapping windows.
+
+We found that overlaps less than 40\% produce very inaccurate predictions in
+comparison with the non-boosted equivalent sources, while values larger that
+80\% produce predictions with almost the same level of accuracy as the latter.
+Nevertheless, overlap values larger that 70\% takes significantly more
+computational time to fit the source coefficients.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
+We can then conclude that using overlap values between 40\% and 70\% generate
+a balance between predictions accuracy and computational time needed to fit the
+source coefficients.
+This corroborates that our naive choice of 50\% is good enough for producing
+accurate predictions in reasonable times.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Gridding Australia gravity data}
+
+Our final goal is to show how gradient-boosted equivalent sources can be used
+to interpolate a very large dataset of gravity data into a regular grid.
+We selected a compilation of gravity surveys over Australia made by
+\citet{wynne2018}.
+It consists in more than 1.7 million data points that cover most part of the
+Australia territory obtained through observations on ground
+(see Fig.~\ref{fig:australia-data-gravity}).
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
+    \caption{
+        Gravity data for Australia composed by more than 1.7 million
+        observations on ground \citep{wynne2018}. The data is available under
+        the Creative Commons Attribution 4.0 International Licence.
+    }
+    \label{fig:australia-data-gravity}
+\end{figure*}
+
+First we compute the gravity disturbance by removing the normal gravity from
+the observed gravity data (see Fig.~\ref{fig:australia-data-disturbance}).
+The normal gravity is computed on each observation point through the
+closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
+as reference.
+Then we obtain plain coordinates of the observation points by applying
+a Mercator projection.
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
+    \caption{
+        Gravity disturbance of Australia computed as the difference between
+        observed gravity and normal gravity generated by the WGS84 ellipsoid on
+        each observation point.
+    }
+    \label{fig:australia-data-disturbance}
+\end{figure*}
+
+We start the interpolation process by defining a set of block-averaged sources
+at a relative depth of \AustraliaEqlDepth{} and a block spacing of
+\SI{1.8}{\kilo\meter}.
+These parameters create \AustraliaEqlNSources{}~point sources.
+The choice of the block spacing must be done taking into account the desired
+resolution of the final grid.
+If the grid will have a much higher resolution than the block spacing, the
+equivalent sources will not be able to reproduce the high frequency components
+of the data.
+Therefore we recommend setting a block spacing that matches the resolution of
+the final grid.
+In this case we will generate a regular grid with a resolution of 1~arc-minute,
+which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
+
+The coefficients of the gradient-boosted equivalent sources are estimated using
+a damping equal to \AustraliaEqlDamping{} and a window size of
+\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
+store the largest Jacobian matrix to 10GB.
+
+Finally, the equivalent sources are used to predict the values of the gravity
+disturbance on a regular grid of
+\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
+\AustraliaEqlGridHeight{} above the ellipsoid
+(see Fig.~\ref{fig:australia-grid}).
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia-grid.png}
+    \caption{
+        Interpolated gravity disturbance of Australia on a regular grid at
+        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
+        were obtained through gradient-boosted equivalent sources.
+    }
+    \label{fig:australia-grid}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}
+
+\subsection{Location of sources}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Performance of gradient-boosted equivalent sources}
-
-Our second goal is to assess the accuracy of the predictions achieved by the
-gradient boosting algorithm while registering its performance by comparison
-with the non-boosted equivalent sources.
-
-\subsection{Window size}
-\label{sec:window_size}
-
-One factor that plays an important role on the performance of the gradient
-boosted equivalent sources is the size of the overlapping windows used to create
-each set of equivalent sources.
-The size of the windows controls the size of the Jacobian matrices
-$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
-Thus, using smaller windows will reduce the amount of computer memory needed to
-fit the source coefficients.
-Nevertheless, smaller windows may produce less accurate predictions because
-their inability to achieve the global minimum of the misfit from
-equation~\ref{eq:misfit-unscaled}.
-Besides, the window size might also impact on the computation time needed to
-fit the source coefficients: smaller windows will generate simpler least-square
-problems which are easier to solve, but they will also create more iterations.
-
-We want to assess how the size of the overlapping windows impacts both the
-accuracy of the predictions and the computation time needed to fit the source
-coefficients in comparison with the performance of the non-boosted equivalent
-sources.
-
-We applied the gradient boosted equivalent sources to interpolate the synthetic
-airborne survey on the same points of the target grid.
-We selected several window sizes to assess how accuracy and performance depend
-on that variable.
-For each window size we gridded the synthetic data using block-averaged sources
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
-a relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
-of 50\%, and with different values of damping.
-Then we compared the resulting interpolations with the target grid in order to
-get the best prediction for each window size and the damping value used to
-obtain it.
-
-Using the best set of parameters for each window size, we registered the
-achieved RMS against the values of the target grid and the time needed to fit
-the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
-In order to avoid any errors introduced by the way windows are shuffled, the
-RMS for each window size was obtained as the mean RMS achieved by using
-different random seeds.
-
-We have also registered the computational time needed to fit the
-gradient-boosted equivalent sources for each window size and computed the ratio
-between these times and the computational time needed to fit the non-boosted
-equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
-    \caption{
-        Gradient-boosted equivalent sources performance against window size.
-        Window sizes are given as a fraction of the dimensions of the synthetic
-        survey area.
-        (a)~Root-mean-squared error between predictions and target grid using
-        non-boosted sources (orange dashed line) and gradient-boosted
-        equivalent sources (blue dots) for different window sizes. Each RMS
-        error is the mean of the RMS produced by the same set of parameters but
-        with different random seeds.
-        (b)~Ratio between the computational times needed to fit the
-        gradient-boosted and the non-boosted equivalent sources, respectively
-        (the fitting time ratio for the non-boosted equivalent sources is
-        therefore equal to one).
-}
-    \label{fig:gradient-boosted-window-size}
-\end{figure}
-
-From the results obtained from the comparison with the synthetic airborne
-survey we can conclude that smaller windows generate less accurate predictions
-than using larger ones and require significantly more computational time to fit
-the sources.
-The reduction of the accuracy might be due to an oversimplification of the
-least-squares problem, and the increase of the computational time might be
-generated by the great number of iterations required to fit the sources.
-As the windows gets larger, the accuracy starts increasing because more data
-points are included into the fitting process of the source coefficients, while
-the fitting process takes less time due to a reduction of the number of
-iterations.
-For very large windows, both accuracy and fitting time are almost constant.
-
-In comparison with the non-boosted equivalent sources, we can see that the
-gradient-boosted ones produce slightly less accurate results due to not being
-able to achieve the global minimum of the least-squares problem, but they
-perform faster.
-
-THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
-
-When using gradient-boosted equivalent sources we can conclude that we want to
-maximize the window size as much as possible.
-The only limitation to do so is to generate Jacobian matrices larger than the
-available memory.
-Therefore we recommend using the largest window that generates Jacobian
-matrices that could fit in the available memory.
-
-\subsection{Amount of overlap}
-
-Another factor that plays an important role on the performance of the gradient
-boosted equivalent sources is the amount of overlap between adjacent windows.
-The previous choice of 50\% showed to be sufficiently good to achieve
-acceptable accuracy, although a deeper study should be carried out to assess
-how the amount of overlap impacts both accuracy and fitting time.
-
-We interpolated the synthetic airborne survey using the gradient boosted
-equivalent sources on the same points of the target grid.
-The interpolations were carried out using different amount of overlap, from
-0\% to 0.95\% with a step size of 0.05\%.
-For each overlap we gridded the synthetic data using block-averaged sources
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
-a relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
-a window size of \BoostOverlappingWindowSize, and with different
-values of damping.
-Then we compared the resulting interpolations with the target grid in order to
-get the best prediction for each overlap and the damping value used to
-obtain it.
-
-Using the best set of parameters for each overlap, we registered the achieved
-RMS against the values of the target grid and the time needed to fit the
-sources coefficients.
-The RMS was obtained as the mean RMS achieved by using different random seeds
-as we did on~\ref{sec:window_size}.
-
-We have also computed the fitting time ratio for each overlap, in a similar way
-we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
-    \caption{
-        Gradient-boosted equivalent sources performance against amount of
-        overlap.
-        (a)~Root-mean-squared error between predictions and target grid using
-        non-boosted sources (orange dashed line) and gradient-boosted
-        equivalent sources (blue dots) for different amount of overlap. Each
-        RMS error is the mean of the RMS produced by the same set of parameters
-        but with different random seeds.
-        (b)~Ratio between the computational times needed to fit the
-        gradient-boosted and the non-boosted equivalent sources, respectively
-        (the fitting time ratio for the non-boosted equivalent sources is
-        therefore equal to one).
-    }
-    \label{fig:gradient-boosted-overlap}
-\end{figure}
-
-From the results obtained we can conclude that a lower values of overlap
-generates less accurate results, while a higher overlap increases the
-computational time required for fitting the source coefficients due to the
-significant increment of the number of overlapping windows.
-
-We found that overlaps less than 40\% produce very inaccurate predictions in
-comparison with the non-boosted equivalent sources, while values larger that
-80\% produce predictions with almost the same level of accuracy as the latter.
-Nevertheless, overlap values larger that 70\% takes significantly more
-computational time to fit the source coefficients.
-
-THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
-
-We can then conclude that using overlap values between 40\% and 70\% generate
-a balance between predictions accuracy and computational time needed to fit the
-source coefficients.
-This corroborates that our naive choice of 50\% is good enough for producing
-accurate predictions in reasonable times.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Gridding Australia gravity data}
-
-Our final goal is to show how gradient-boosted equivalent sources can be used
-to interpolate a very large dataset of gravity data into a regular grid.
-We selected a compilation of gravity surveys over Australia made by
-\citet{wynne2018}.
-It consists in more than 1.7 million data points that cover most part of the
-Australia territory obtained through observations on ground
-(see Fig.~\ref{fig:australia-data-gravity}).
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
-    \caption{
-        Gravity data for Australia composed by more than 1.7 million
-        observations on ground \citep{wynne2018}. The data is available under
-        the Creative Commons Attribution 4.0 International Licence.
-    }
-    \label{fig:australia-data-gravity}
-\end{figure*}
-
-First we compute the gravity disturbance by removing the normal gravity from
-the observed gravity data (see Fig.~\ref{fig:australia-data-disturbance}).
-The normal gravity is computed on each observation point through the
-closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
-as reference.
-Then we obtain plain coordinates of the observation points by applying
-a Mercator projection.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
-    \caption{
-        Gravity disturbance of Australia computed as the difference between
-        observed gravity and normal gravity generated by the WGS84 ellipsoid on
-        each observation point.
-    }
-    \label{fig:australia-data-disturbance}
-\end{figure*}
-
-We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block spacing of
-\SI{1.8}{\kilo\meter}.
-These parameters create \AustraliaEqlNSources{}~point sources.
-The choice of the block spacing must be done taking into account the desired
-resolution of the final grid.
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
-In this case we will generate a regular grid with a resolution of 1~arc-minute,
-which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
-
-The coefficients of the gradient-boosted equivalent sources are estimated using
-a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
-store the largest Jacobian matrix to 10GB.
-
-Finally, the equivalent sources are used to predict the values of the gravity
-disturbance on a regular grid of
-\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid
-(see Fig.~\ref{fig:australia-grid}).
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-grid.png}
-    \caption{
-        Interpolated gravity disturbance of Australia on a regular grid at
-        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
-        were obtained through gradient-boosted equivalent sources.
-    }
-    \label{fig:australia-grid}
-\end{figure*}
+\subsection{Gradient boosting}
 

### 2021-01-21 notebooks/99-figures.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.9.1
+#       jupytext_version: 1.7.1
 #   kernelspec:
 #     display_name: Python [conda env:eql-gradient-boosted]
 #     language: python
@@ -35,143 +35,91 @@ airborne_results_dir = results_dir / "airborne_survey"
 
 figs_dir = Path("..") / "manuscript" / "figs"
 
-# ## Ground survey
+# ## Ground and airborne synthetic surveys
 
-survey = pd.read_csv(ground_results_dir / "survey.csv")
+survey_ground = pd.read_csv(ground_results_dir / "survey.csv")
+survey_airborne = pd.read_csv(airborne_results_dir / "survey.csv")
 
 # +
 # Define useful parameters
-width = 3.33
-figsize = (width, width * 1.7)
-cbar_shrink = 0.95
-cbar_pad = 0.03
-cbar_aspect = 30
-size = 2
-labels = "a b".split()
+figsize = (6.66, 2.9)
+cbar_args = dict(
+    shrink=0.95,
+    pad=0.16,
+    aspect=40,
+    orientation="horizontal",
+)
+size = 0.5
+labels = "a b c d".split()
+coords_scale = 1e-3
 
 # Initialize figure and axes
-fig, (ax1, ax2) = plt.subplots(ncols=1, nrows=2, sharex=True, figsize=figsize)
+fig, (ax1, ax2, ax3, ax4) = plt.subplots(ncols=4, nrows=1, sharey=True, figsize=figsize)
 
-# Plot survey points
 tmp = ax1.scatter(
-    survey.easting, survey.northing, c=survey.height, cmap="cividis", s=size
+    survey_ground.easting * coords_scale, survey_ground.northing * coords_scale, c=survey_ground.height, cmap="cividis", s=size
 )
 clb = plt.colorbar(
     tmp,
     ax=ax1,
-    shrink=cbar_shrink,
-    orientation="vertical",
-    pad=cbar_pad,
-    aspect=cbar_aspect,
+    **cbar_args
 )
-clb.set_label("m", labelpad=-15, y=1.05, rotation=0)
+clb.set_label("meters")
 
-# Plot measured values
-tmp = ax2.scatter(survey.easting, survey.northing, c=survey.g_z, cmap="viridis", s=size)
[…]

### 2021-01-22 manuscript/manuscript.tex
Make a single figure data and grid for Australia
Joining them makes it easier to compare the observations with the
interpolation results. Also added bathymetry as a background and tweaked
the font and frame sizes.

--- 2021-01-18 manuscript/manuscript.tex
@@
 \usepackage{setspace}
-
-% Define style for urls
-\urlstyle{same}
 
@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia.png}
+    \caption{
+      Pseudo-color maps of observed (left) and
+      interpolated (right) gravity disturbance of Australia.
+      Observations are part of a compilation by \citet{wynne2018} of
+      over 1.7 million ground gravity measurements.
+      Interpolated values were obtained through gradient-boosted equivalent
+      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
+      over the WGS84 ellipsoid.
+    }
+    \label{fig:australia}
+\end{figure*}
+
 Our final goal is to show how gradient-boosted equivalent sources can be used
@@
 It consists in more than 1.7 million data points that cover most part of the
-Australia territory obtained through observations on ground
-(see Fig.~\ref{fig:australia-data-gravity}).
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
-    \caption{
-        Gravity data for Australia composed by more than 1.7 million
-        observations on ground \citep{wynne2018}. The data is available under
-        the Creative Commons Attribution 4.0 International Licence.
-    }
-    \label{fig:australia-data-gravity}
-\end{figure*}
-
+Australia territory obtained through observations on ground.
 First we compute the gravity disturbance by removing the normal gravity from
-the observed gravity data (see Fig.~\ref{fig:australia-data-disturbance}).
+the observed gravity data (Fig.~\ref{fig:australia}).
 The normal gravity is computed on each observation point through the
@@
 as reference.
-Then we obtain plain coordinates of the observation points by applying
+Then we obtain planar coordinates of the observation points by applying
 a Mercator projection.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
-    \caption{
-        Gravity disturbance of Australia computed as the difference between
-        observed gravity and normal gravity generated by the WGS84 ellipsoid on
-        each observation point.
-    }
-    \label{fig:australia-data-disturbance}
-\end{figure*}
 
@@
 \AustraliaEqlGridHeight{} above the ellipsoid
-(see Fig.~\ref{fig:australia-grid}).
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-grid.png}
-    \caption{
-        Interpolated gravity disturbance of Australia on a regular grid at
-        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
-        were obtained through gradient-boosted equivalent sources.
-    }
-    \label{fig:australia-grid}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Software implementation}
-
-We have implemented the methods described in the previous sections though
-a software written in Python language.
-The code for generating the results of this work are available in
-\url{https://doi.org/10.6084/m9.figshare.13604360}.
-The gradient-boosted equivalent sources implementation is based on the
-non-boosted sources available through the Harmonica library
-\citep{harmonica2020}, part of the Fatiando a Terra project
-\citep{fatiando2013}.
-Another Python libraries were used:
-Verde \citep{verde2018} to apply block reductions and managing coordinates,
-Boule \citep{boule2020} for computing normal gravity,
-Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
-multidimensional datasets and numerical
-computations,
-Numba \citep{numba2015} for writing pre-comipled implementations and
-parallelization,
-Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
-the figures.
+(Fig.~\ref{fig:australia}).
 

### 2021-01-22 notebooks/99-figures.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.9.1
+#       jupytext_version: 1.7.1
 #   kernelspec:
 #     display_name: Python [conda env:eql-gradient-boosted]
 #     language: python
@@ -507,32 +507,14 @@ australia_data = xr.open_dataset(results_dir / "australia" / "australia-data.nc"
 australia_grid = xr.open_dataset(results_dir / "australia" / "australia-grid.nc")
 
 # +
-region = vd.get_region(
-    (australia_data.longitude.values, australia_data.latitude.values)
+region = vd.pad_region(
+    vd.get_region((australia_data.longitude.values, australia_data.latitude.values)),
+    1,
 )
 lat_ts = australia_data.latitude.mean().values
 lon_ts = australia_data.longitude.mean().values
 
-proj_gmt = "M{:.0f}/{:.0f}/6.66i".format(lon_ts, lat_ts)
-
-# +
-vmin, vmax = australia_data.gravity.values.min(), australia_data.gravity.values.max()
-
-fig = pygmt.Figure()
-pygmt.makecpt(cmap="viridis", series=(vmin, vmax))
-fig.plot(
-    x=australia_data.longitude,
-    y=australia_data.latitude,
-    color=australia_data.gravity,
-    style="c0.5p",
-    cmap=True,
-    projection=proj_gmt,  # needed on the first plot
-)
-fig.coast(shorelines=True)
-fig.basemap(region=region, frame=["afg"])
-fig.colorbar(frame='af+l"Observed gravity [mGal]"')
-fig.savefig(figs_dir / "australia-data-gravity.png")
-fig.show()
+proj_gmt = "M{:.0f}/{:.0f}/5i".format(lon_ts, lat_ts)
 # -
 
 maxabs = vd.maxabs(
@@ -540,11 +522,19 @@ maxabs = vd.maxabs(
     australia_grid.disturbance.values,
 )
 
+# +
 fig = pygmt.Figure()
+
+pygmt.config(
+    FONT_ANNOT="11p,Helvetica,black", 
+    FONT_TITLE="15p,Helvetica,black", 
+    FONT_LABEL="11p,Helvetica,black",
+    MAP_FRAME_WIDTH="2p",
+)
+
[…]

### 2021-01-25 manuscript/manuscript.tex
Review the model and synthetic data description

--- 2021-01-21 manuscript/manuscript.tex
@@
 each of these strategies on synthetic data.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
-    \caption{
-        Pseudo-color map of the target grid of synthetic gravity data. The grid
-        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
-        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
-        above the zero height plane.
-    }
-    \label{fig:synthetic-target}
-\end{figure}
+We have used synthetic gravity datasets to test the interpolation accuracy of
+the difference horizontal and vertical source distribution strategies as well
+as the gradient-boosted equivalent source method.
+To generate the data, we created a model that is made out of \NPrisms{}
+right-rectangular prisms, distributed on a region of
+\ModelEasting{}$\times$\ModelNorthing{} with depths varying between
+\ModelDepth{} and zero.
+The density contrast of prisms ranges from \ModelMinDensity{} to
+\ModelMaxDensity{}.
+The model includes prisms of different shapes, sizes, and depths to create
+gravity disturbances with a variety of wavelengths.
+
+We created two synthetic datasets from the model, one simulating a ground
+survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
+To create the synthetic ground survey, we selected measurement positions from a
+portion of a public domain dataset for Southern Africa, available through the
+NOAA National Centers for Environmental Information (NCEI)\footnote{
+\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}
+(last accessed 25 January 2020)}.
+For the synthetic airborne survey, we used a portion of the Great Britain Aeromagnetic
+Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
+Ltd between 1955 and 1965 and made publicly available by the
+British Geological Survey (BGS)\footnote{
+\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}
+(last accessed 25 January 2020)}.
+In both cases, we rescaled the horizontal coordinates of each survey portion to
+span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
+dimensions.
+The ground survey contains \GroundSurveyPoints{} observations distributed at
+heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
+(Fig.~\ref{fig:synthetic-layouts}a).
+The airborne survey has \AirborneSurveyPoints{} observations at heights between
+\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
+(Fig.~\ref{fig:synthetic-layouts}c).
+
+The vertical component of the gravitational acceleration generated by the
+model was computed  using the method of \citet{nagy2000, nagy2002}
+with recent modifications by \citet{fukushima2020},
+as implemented in the open-source software Harmonica \citep{harmonica}.
+We generated a \emph{target grid} of
+\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
+\TargetSpacing{} and located \TargetHeight{} above the zero height plane
+(Fig.~\ref{fig:synthetic-target}) to serve as a reference when calculating the
+interpolation error.
+We then generated synthetic ground (Fig.~\ref{fig:synthetic-layouts}b) and
+airborne (Fig.~\ref{fig:synthetic-layouts}d) data to which we added
+pseudo-random Gaussian noise with zero mean and \SurveyNoise{} standard
+deviation.
 
@@
         with added pseudo-random Gaussian noise.
-        For (a) and (b), height is given in meters above the zero height plane.
+        Heights are given in meters above the zero height plane.
     }
@@
 
-Start with a description of the model and surveys. This is common for all
-tests.
-
-The synthetic model is made out of \NPrisms{} prisms distributed on a region of
-\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
-height plane.
-Density contrast of prisms range from \ModelMinDensity{} and
-\ModelMaxDensity{}.
-We built deep big and thin shallow prisms for creating gravity anomalies with
-long and short wavelengths, respectively.
-
-The vertical component of the gravity acceleration generated by the synthetic
-model has been computed on a regular grid of
-\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
-\TargetSpacing{} located \TargetHeight{} above the zero height plane
-(Fig.~\ref{fig:synthetic-target}), using \citet{nagy2000} and \citet{nagy2002}.
-We will refer to this grid as the \emph{target} grid in the future.
-
-In order to compare the predictive capabilities of each source distribution
-under on different surveys, we created a ground and an airborne \emph{synthetic
-surveys}.
-For creating the synthetic ground survey we selected a portion of the Southern
-Africa Gravity Data available through the
-\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
-For the airborne survey we used a portion of the Great Britain Aeromagnetic
-Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
-Ltd between 1955 and 1965 and made available by the
-\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
-British Geological Survey (BGS)
-}.
-
-On both cases we selected only a portion of the survey and rescaled it to span
-on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
-The ground survey is composed by \GroundSurveyPoints{} observation points
-distributed at heights ranging between \GroundSurveyMinHeight{} and
-\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-layouts}a).
-While the airborne survey has \AirborneSurveyPoints{} points at heights between
-\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
-(Fig.~\ref{fig:synthetic-layouts}c).
-
-The vertical component of the gravity acceleration generated by the synthetic
-model has been computed on both surveys.
-Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
-to the effect of the synthetic model to simulate acquisition errors
-(Figs.~\ref{fig:synthetic-layouts}b
-and~\ref{fig:synthetic-layouts}d).
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
+    \caption{
+        Pseudo-color map of the target grid of synthetic gravity data. The grid
+        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
+        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
+        above the zero height plane.
+    }
+    \label{fig:synthetic-target}
+\end{figure}
 

### 2021-01-25 manuscript/manuscript.tex
Describe the source layouts so we don't need the table

@@
 
-The combination of the three source layouts with the three strategies to define
-the depth of the sources define seven different source distributions (see
-Table~\ref{tab:source-distributions}).
-The \emph{grid sources} is only compatible with the \emph{constant depth}
-scheme if no further information is provided.
-
-\begin{table*}
-    \centering
-    \caption{
-        Source distributions as combinations of source layouts and depth
-        strategies.
-    }
-    \label{tab:source-distributions}
-    \begin{tabular}{lccc}
-        & Source below data & Block averaged sources & Grid sources \\ \hline
-        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
-        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
-        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
-    \end{tabular}
-\end{table*}
+We investigated the effect of different strategies for distributing the
+equivalent sources horizontally and vertically on interpolation accuracy.
+To do this, we used the damped least-squares solution described in
+Section~\ref{sec:eql_inversion} (without gradient boosting) to interpolate the
+synthetic datasets (Fig.~\ref{fig:synthetic-layouts}) and compared the results
+against the target grid (Fig.~\ref{fig:synthetic-target}).
+This process was repeated for each combination of horizontal layout
+(sources-below-data and block-averaged-sources) and depth type (constant,
+relative, and variable) and for regular-grid sources with a constant depth,
+totalling 7 different combinations.
 

### 2021-01-25 manuscript/manuscript.tex
Review the text about source layout results

@@
 
-Our first goal is to to compare the performance of all source distributions
-from Table~\ref{tab:source-distributions} when predicting harmonic field data
-using the equivalent sources technique.
-To do so we have created a synthetic model made out of prisms of different
-shape and density contrasts.
-The gravitational effect of this synthetic model have been computed on
-a regular grid (\emph{target} grid) at a constant height and on two different
-set of observation points that we will call \emph{synthetic surveys}: a ground
-and an airborne survey.
-The data from each synthetic survey is interpolated on the points of the
-\emph{target} grid and then scored against its values.
-We can then quantitatively compare how accurate is each source distribution at
-predicting unobserved data on each synthetic survey and quantify the
-computational load needed to do it.
-
-Each source distribution from Table~\ref{tab:source-distributions} needs
-certain parameters in order to build the set of point sources.
-The prediction capabilities of the source distribution depends on the choice of
-these parameters.
-For example, locating the sources beneath the data points at constant depth
-needs the definition of the \emph{depth} parameter.
-If the sources are set too close to the data points, the source distribution
-it's very likely to over-fit the data: the measured field will be recovered, but
-the predictions on unobserved locations will be very inaccurate.
-Another parameter that plays an important role on the predictive capabilities
-of the sources is the \emph{damping}.
-
-On real world scenarios, choosing the values of the parameters is a challenging
-task: it's not easy to determine the accuracy of the predictions without
-knowing the true value of the field on unobserved locations.
-This problem can be solved through cross-validation.
-When working with a synthetic model, the situation is different: we can compute
-the true values of harmonic field generated by the synthetic model on any
-point.
-Therefore, interpolating the observed data on the same points of the
-\emph{target} grid and then scoring the prediction against the true values of
-the \emph{target} grid constitutes an objective way to measure the predictive
-accuracy of the source distribution.
-
-In order to compare the predictive capabilities of each source distribution we
-perform a parameter search to obtain the best prediction that can be achieved
-by each one of them.
-For each source distribution we proposed different values for each parameter
-(see Tables~\ref{tab:parameters-ground-survey}
-and~\ref{tab:parameters-airborne-survey}).
-These parameters values are combined obtaining several \emph{set of
-parameters}.
-We use each set of parameters to create the sources, fit their coefficients
-through least-squares and predict the field on the same points of the
-\emph{target} grid.
-We then \emph{score} the prediction by computing the root mean square (RMS)
-between the prediction and the true values of the \emph{target} grid.
-Finally, we obtain the \emph{best prediction} for each source distribution as
-the one that achieves the lowest RMS.
-This process is carried out on both ground and airborne synthetic surveys.
-See Algorithm~\ref{alg:source_distributions_comparison} for a concise
-representation of it.
-
-\begin{algorithm}[!h]
-  \DontPrintSemicolon
-  \setstretch{1.5}
-
-  define possible values for each parameter
-  \;
-
-  generate each possible combination of parameters values: obtain several
-  \emph{sets of parameters}
-  \;
-
-  \For{each set of parameters}{
-
-    select the $M$ locations of the equivalent sources
-    \;
-
-    estimate the source coefficients
-    \;
-
-    predict field values on target grid points
-    \;
-
-    calculate the RMS between the predictions and the target grid
-    \;
-  }
-
-  the best set of parameters produces the smallest RMS
-  \;
-
-  \BlankLine
-  \setstretch{1}
-  \caption{Algorithm for estimating the best prediction using synthetic data.}
-  \label{alg:source_distributions_comparison}
-\end{algorithm}
-
-Tables~\ref{tab:parameters-ground-survey}
-and~\ref{tab:parameters-airborne-survey} also show the parameter combination
-that produces the best prediction for each source distribution and its
-corresponding RMS score, for both ground and airborne synthetic surveys,
-respectively.
+Each source distribution strategy requires certain hyper-parameters to be
+chosen in order to build the set of point sources.
+For example, using a constant depth needs the definition of the depth and using
+block-average-sources requires the definition of the block size.
+The predictive capabilities of the equivalent sources depend on the choice of
+these hyper-parameters.
+To ensure that our comparisons are fair, we perform an exhaustive search over
+combinations of hyper-parameter values (including the damping parameter from
+Eq.~\ref{eq:misfit}) to obtain the best prediction that can be achieved by each
+source distribution strategy.
+Here, the best prediction is defined as the one that minimizes the root
+mean-square error (RMS) between interpolated values and the target grid
+(Fig.~\ref{fig:synthetic-target}).
+The parameter values used in these searches and the one producing the smallest
+RMS error are outlined in Tables~\ref{tab:parameters-ground-survey}
+and~\ref{tab:parameters-airborne-survey}.
+
 Figures~\ref{fig:ground-survey-differences}
 and~\ref{fig:airborne-survey-differences} show the differences between the
-target grid and the best prediction achieved by each source distribution, for
-both ground and airborne synthetic surveys, respectively.
+target grid and the best prediction achieved by each source distribution
+strategy for the ground and airborne synthetic surveys, respectively.
+For the synthetic ground survey, the horizontal layouts produced similar RMS
+values of appropriately 0.8 mGal regardless of the depth type, with the
+exception of the regular-grid layout which produced a larger RMS of
+\BestGroundGridSourcesConstantDepthRms{} mGal.
+The differences between the target grid and the interpolated values are larger
+in regions of poor data coverage.
+Edge effects are present for all strategies but are noticeably smaller for the
+combination of block-averaged-sources with a variable depth based on the
+nearest neighbour distance.
+For the synthetic airborne survey, all strategies (including the regular-grid)
+produced similar RMS errors of approximately 0.3 mGal.
+The maps of the differences between the target grid and interpolation results
+are visually indistinguishable from each other.
 
@@
     \caption{
-        Differences between gravitational effects measured on the target grid
-        and the ones produced by the best prediction made by each source
-        distribution based on the synthetic ground survey.
+        Pseudo-color maps of the differences between the target grid and the
+        interpolated synthetic ground survey data produced by each source
+        distribution strategy.
+        The black dots represent the horizontal location of the synthetic data
+        points. The RMS error and total number of equivalent sources is
+        reported for each strategy at the top of the respective maps.
     }
@@
     \caption{
-        Differences between gravitational effects measured on the target grid
-        and the ones produced by the best prediction made by each source
-        distribution based on the synthetic airborne survey.
+        Pseudo-color maps of the differences between the target grid and the
+        interpolated synthetic airborne survey data produced by each source
+        distribution strategy.
+        The black dots represent the horizontal location of the synthetic data
+        points. The RMS error and total number of equivalent sources is
+        reported for each strategy at the top of the respective maps.
     }
@@
 without which this work would not have been possible.
-
 The synthetic airborne survey was based upon the Great Britain aeromagnetic
 data, reproduced with the permission of the British Geological Survey
-$\textcopyright$UKRI\@.
+\textcopyright{} UKRI.
 All rights reserved.

### 2021-01-25 manuscript/manuscript.tex

--- 2021-01-25 manuscript/manuscript.tex
@@
 each of these strategies on synthetic data.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Tests on synthetic data}
-
-We have used synthetic gravity datasets to test the interpolation accuracy of
-the difference horizontal and vertical source distribution strategies as well
-as the gradient-boosted equivalent source method.
-To generate the data, we created a model that is made out of \NPrisms{}
-right-rectangular prisms, distributed on a region of
-\ModelEasting{}$\times$\ModelNorthing{} with depths varying between
-\ModelDepth{} and zero.
-The density contrast of prisms ranges from \ModelMinDensity{} to
-\ModelMaxDensity{}.
-The model includes prisms of different shapes, sizes, and depths to create
-gravity disturbances with a variety of wavelengths.
-
-We created two synthetic datasets from the model, one simulating a ground
-survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
-To create the synthetic ground survey, we selected measurement positions from a
-portion of a public domain dataset for Southern Africa, available through the
-NOAA National Centers for Environmental Information (NCEI)\footnote{
-\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}
-(last accessed 25 January 2020)}.
-For the synthetic airborne survey, we used a portion of the Great Britain Aeromagnetic
-Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
-Ltd between 1955 and 1965 and made publicly available by the
-British Geological Survey (BGS)\footnote{
-\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}
-(last accessed 25 January 2020)}.
-In both cases, we rescaled the horizontal coordinates of each survey portion to
-span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
-dimensions.
-The ground survey contains \GroundSurveyPoints{} observations distributed at
-heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
-(Fig.~\ref{fig:synthetic-layouts}a).
-The airborne survey has \AirborneSurveyPoints{} observations at heights between
-\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
-(Fig.~\ref{fig:synthetic-layouts}c).
-
-The vertical component of the gravitational acceleration generated by the
-model was computed  using the method of \citet{nagy2000, nagy2002}
-with recent modifications by \citet{fukushima2020},
-as implemented in the open-source software Harmonica \citep{harmonica}.
-We generated a \emph{target grid} of
-\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
-\TargetSpacing{} and located \TargetHeight{} above the zero height plane
-(Fig.~\ref{fig:synthetic-target}) to serve as a reference when calculating the
-interpolation error.
-We then generated synthetic ground (Fig.~\ref{fig:synthetic-layouts}b) and
-airborne (Fig.~\ref{fig:synthetic-layouts}d) data to which we added
-pseudo-random Gaussian noise with zero mean and \SurveyNoise{} standard
-deviation.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
-    \caption{
-        Maps of the observation locations and gravity values for the synthetic
-        ground and airborne surveys.
-        (a)~Horizontal position and height of the ground survey points.
-        (b)~Synthetic gravity data calculated on the ground survey points with
-        added pseudo-random Gaussian noise.
-        (c)~Horizontal position and height of the airborne survey points.
-        (d)~Synthetic gravity data calculated on the airborne survey points
-        with added pseudo-random Gaussian noise.
-        Heights are given in meters above the zero height plane.
-    }
-    \label{fig:synthetic-layouts}
-\end{figure*}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
-    \caption{
-        Pseudo-color map of the target grid of synthetic gravity data. The grid
-        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
-        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
-        above the zero height plane.
-    }
-    \label{fig:synthetic-target}
-\end{figure}
-
-\subsection{Comparison of source distribution strategies}
+\section{Comparison of source distributions}
 
@@
 computational load needed to do it.
+
+\subsection{Synthetic Model}
+
+%Describe forward model made out of prisms.
+%Show prisms model?
+
+The synthetic model is made out of \NPrisms{} prisms distributed on a region of
+\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
+height plane.
+Density contrast of prisms range from \ModelMinDensity{} and
+\ModelMaxDensity{}.
+We built deep big and thin shallow prisms for creating gravity anomalies with
+long and short wavelengths, respectively.
+
+The vertical component of the gravity acceleration generated by the synthetic
+model has been computed on a regular grid of
+\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
+\TargetSpacing{} located \TargetHeight{} above the zero height plane
+(Fig.~\ref{fig:target-grid}), using \citet{nagy2000} and \citet{nagy2002}.
+We will refer to this grid as the \emph{target} grid in the future.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
+    \caption{
+        Target grid. Gravitational effect of synthetic model on a regular grid
+        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
+        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
+        zero height plane.
+    }
+    \label{fig:target-grid}
+\end{figure}
+
+\subsection{Synthetic Surveys}
+
+In order to compare the predictive capabilities of each source distribution
+under on different surveys, we created a ground and an airborne \emph{synthetic
+surveys}.
+For creating the synthetic ground survey we selected a portion of the Southern
+Africa Gravity Data available through the
+\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
+For the airborne survey we used a portion of the Great Britain Aeromagnetic
+Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
+Ltd between 1955 and 1965 and made available by the
+\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
+British Geological Survey (BGS)
+}.
+
+On both cases we selected only a portion of the survey and rescaled it to span
+on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
+The ground survey is composed by \GroundSurveyPoints{} observation points
+distributed at heights ranging between \GroundSurveyMinHeight{} and
+\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
+While the airborne survey has \AirborneSurveyPoints{} points at heights between
+\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
+(Fig.~\ref{fig:synthetic-ground-survey}(a)).
+
+The vertical component of the gravity acceleration generated by the synthetic
+model has been computed on both surveys.
+Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
+to the effect of the synthetic model to simulate acquisition errors
+(Figs.~\ref{fig:synthetic-ground-survey}(b)
+and~\ref{fig:synthetic-airborne-survey}(b)).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
+    \caption{
+        Synthetic ground survey.
+        (a)~Location of observation points. Altitude given in meters above the
+            zero height plane.
+        (b)~Vertical component of gravity acceleration generated by the
+            synthetic model plus Gaussian noise on the ground survey
+            observation points.
+    }
+    \label{fig:synthetic-ground-survey}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/airborne-survey.pdf}
+    \caption{
+        Synthetic airborne survey.
+        (a)~Location of observation points. Altitude given in meters above the
+            zero height plane.
+        (b)~Vertical component of gravity acceleration generated by the
+            synthetic model plus Gaussian noise on the airborne survey
+            observation points.
+        Based upon the Great Britain aeromagnetic data, with the permission of
+        the British Geological Survey.
+    }
+    \label{fig:synthetic-airborne-survey}
+\end{figure}
+
+\subsection{Comparisons}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Performance and accuracy of gradient boosting}
-
-Our second goal is to assess the accuracy of the predictions achieved by the
-gradient boosting algorithm while registering its performance by comparison
-with the non-boosted equivalent sources.
-
-\subsubsection{Window size}
-\label{sec:window_size}
-
-One factor that plays an important role on the performance of the gradient
-boosted equivalent sources is the size of the overlapping windows used to create
-each set of equivalent sources.
-The size of the windows controls the size of the Jacobian matrices
-$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
-Thus, using smaller windows will reduce the amount of computer memory needed to
-fit the source coefficients.
-Nevertheless, smaller windows may produce less accurate predictions because
-their inability to achieve the global minimum of the misfit from
-equation~\ref{eq:misfit-unscaled}.
-Besides, the window size might also impact on the computation time needed to
-fit the source coefficients: smaller windows will generate simpler least-square
-problems which are easier to solve, but they will also create more iterations.
-
-We want to assess how the size of the overlapping windows impacts both the
-accuracy of the predictions and the computation time needed to fit the source
-coefficients in comparison with the performance of the non-boosted equivalent
-sources.
-
-We applied the gradient boosted equivalent sources to interpolate the synthetic
-airborne survey on the same points of the target grid.
-We selected several window sizes to assess how accuracy and performance depend
-on that variable.
-For each window size we gridded the synthetic data using block-averaged sources
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
-a relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
-of 50\%, and with different values of damping.
-Then we compared the resulting interpolations with the target grid in order to
-get the best prediction for each window size and the damping value used to
-obtain it.
-
-Using the best set of parameters for each window size, we registered the
-achieved RMS against the values of the target grid and the time needed to fit
-the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
-In order to avoid any errors introduced by the way windows are shuffled, the
-RMS for each window size was obtained as the mean RMS achieved by using
-different random seeds.
-
-We have also registered the computational time needed to fit the
-gradient-boosted equivalent sources for each window size and computed the ratio
-between these times and the computational time needed to fit the non-boosted
-equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
-    \caption{
-        Gradient-boosted equivalent sources performance against window size.
-        Window sizes are given as a fraction of the dimensions of the synthetic
-        survey area.
-        (a)~Root-mean-squared error between predictions and target grid using
-        non-boosted sources (orange dashed line) and gradient-boosted
-        equivalent sources (blue dots) for different window sizes. Each RMS
-        error is the mean of the RMS produced by the same set of parameters but
-        with different random seeds.
-        (b)~Ratio between the computational times needed to fit the
-        gradient-boosted and the non-boosted equivalent sources, respectively
-        (the fitting time ratio for the non-boosted equivalent sources is
-        therefore equal to one).
-}
-    \label{fig:gradient-boosted-window-size}
-\end{figure}
-
-From the results obtained from the comparison with the synthetic airborne
-survey we can conclude that smaller windows generate less accurate predictions
-than using larger ones and require significantly more computational time to fit
-the sources.
-The reduction of the accuracy might be due to an oversimplification of the
-least-squares problem, and the increase of the computational time might be
-generated by the great number of iterations required to fit the sources.
-As the windows gets larger, the accuracy starts increasing because more data
-points are included into the fitting process of the source coefficients, while
-the fitting process takes less time due to a reduction of the number of
-iterations.
-For very large windows, both accuracy and fitting time are almost constant.
-
-In comparison with the non-boosted equivalent sources, we can see that the
-gradient-boosted ones produce slightly less accurate results due to not being
-able to achieve the global minimum of the least-squares problem, but they
-perform faster.
-
-THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
-
-When using gradient-boosted equivalent sources we can conclude that we want to
-maximize the window size as much as possible.
-The only limitation to do so is to generate Jacobian matrices larger than the
-available memory.
-Therefore we recommend using the largest window that generates Jacobian
-matrices that could fit in the available memory.
-
-\subsubsection{Amount of overlap}
-
-Another factor that plays an important role on the performance of the gradient
-boosted equivalent sources is the amount of overlap between adjacent windows.
-The previous choice of 50\% showed to be sufficiently good to achieve
-acceptable accuracy, although a deeper study should be carried out to assess
-how the amount of overlap impacts both accuracy and fitting time.
-
-We interpolated the synthetic airborne survey using the gradient boosted
-equivalent sources on the same points of the target grid.
-The interpolations were carried out using different amount of overlap, from
-0\% to 0.95\% with a step size of 0.05\%.
-For each overlap we gridded the synthetic data using block-averaged sources
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
-a relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
-a window size of \BoostOverlappingWindowSize, and with different
-values of damping.
-Then we compared the resulting interpolations with the target grid in order to
-get the best prediction for each overlap and the damping value used to
-obtain it.
-
-Using the best set of parameters for each overlap, we registered the achieved
-RMS against the values of the target grid and the time needed to fit the
-sources coefficients.
-The RMS was obtained as the mean RMS achieved by using different random seeds
-as we did on~\ref{sec:window_size}.
-
-We have also computed the fitting time ratio for each overlap, in a similar way
-we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
-    \caption{
-        Gradient-boosted equivalent sources performance against amount of
-        overlap.
-        (a)~Root-mean-squared error between predictions and target grid using
-        non-boosted sources (orange dashed line) and gradient-boosted
-        equivalent sources (blue dots) for different amount of overlap. Each
-        RMS error is the mean of the RMS produced by the same set of parameters
-        but with different random seeds.
-        (b)~Ratio between the computational times needed to fit the
-        gradient-boosted and the non-boosted equivalent sources, respectively
-        (the fitting time ratio for the non-boosted equivalent sources is
-        therefore equal to one).
-    }
-    \label{fig:gradient-boosted-overlap}
-\end{figure}
-
-From the results obtained we can conclude that a lower values of overlap
-generates less accurate results, while a higher overlap increases the
-computational time required for fitting the source coefficients due to the
-significant increment of the number of overlapping windows.
-
-We found that overlaps less than 40\% produce very inaccurate predictions in
-comparison with the non-boosted equivalent sources, while values larger that
-80\% produce predictions with almost the same level of accuracy as the latter.
-Nevertheless, overlap values larger that 70\% takes significantly more
-computational time to fit the source coefficients.
-
-THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
-
-We can then conclude that using overlap values between 40\% and 70\% generate
-a balance between predictions accuracy and computational time needed to fit the
-source coefficients.
-This corroborates that our naive choice of 50\% is good enough for producing
-accurate predictions in reasonable times.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Gridding Australia gravity data}
-
-Our final goal is to show how gradient-boosted equivalent sources can be used
-to interpolate a very large dataset of gravity data into a regular grid.
-We selected a compilation of gravity surveys over Australia made by
-\citet{wynne2018}.
-It consists in more than 1.7 million data points that cover most part of the
-Australia territory obtained through observations on ground
-(see Fig.~\ref{fig:australia-data-gravity}).
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
-    \caption{
-        Gravity data for Australia composed by more than 1.7 million
-        observations on ground \citep{wynne2018}. The data is available under
-        the Creative Commons Attribution 4.0 International Licence.
-    }
-    \label{fig:australia-data-gravity}
-\end{figure*}
-
-First we compute the gravity disturbance by removing the normal gravity from
-the observed gravity data (see Fig.~\ref{fig:australia-data-disturbance}).
-The normal gravity is computed on each observation point through the
-closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
-as reference.
-Then we obtain plain coordinates of the observation points by applying
-a Mercator projection.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
-    \caption{
-        Gravity disturbance of Australia computed as the difference between
-        observed gravity and normal gravity generated by the WGS84 ellipsoid on
-        each observation point.
-    }
-    \label{fig:australia-data-disturbance}
-\end{figure*}
-
-We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block spacing of
-\SI{1.8}{\kilo\meter}.
-These parameters create \AustraliaEqlNSources{}~point sources.
-The choice of the block spacing must be done taking into account the desired
-resolution of the final grid.
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
-In this case we will generate a regular grid with a resolution of 1~arc-minute,
-which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
-
-The coefficients of the gradient-boosted equivalent sources are estimated using
-a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
-store the largest Jacobian matrix to 10GB.
-
-Finally, the equivalent sources are used to predict the values of the gravity
-disturbance on a regular grid of
-\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid
-(see Fig.~\ref{fig:australia-grid}).
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-grid.png}
-    \caption{
-        Interpolated gravity disturbance of Australia on a regular grid at
-        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
-        were obtained through gradient-boosted equivalent sources.
-    }
-    \label{fig:australia-grid}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-
-\subsection{Location of sources}
+\subsection{Discussion}
 
@@
 
-\subsection{Gradient boosting}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Performance of gradient-boosted equivalent sources}
+
+Our second goal is to assess the accuracy of the predictions achieved by the
+gradient boosting algorithm while registering its performance by comparison
+with the non-boosted equivalent sources.
+
+\subsection{Window size}
+\label{sec:window_size}
+
+One factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the size of the overlapping windows used to create
+each set of equivalent sources.
+The size of the windows controls the size of the Jacobian matrices
+$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
+Thus, using smaller windows will reduce the amount of computer memory needed to
+fit the source coefficients.
+Nevertheless, smaller windows may produce less accurate predictions because
+their inability to achieve the global minimum of the misfit from
+equation~\ref{eq:misfit-unscaled}.
+Besides, the window size might also impact on the computation time needed to
+fit the source coefficients: smaller windows will generate simpler least-square
+problems which are easier to solve, but they will also create more iterations.
+
+We want to assess how the size of the overlapping windows impacts both the
+accuracy of the predictions and the computation time needed to fit the source
+coefficients in comparison with the performance of the non-boosted equivalent
+sources.
+
+We applied the gradient boosted equivalent sources to interpolate the synthetic
+airborne survey on the same points of the target grid.
+We selected several window sizes to assess how accuracy and performance depend
+on that variable.
+For each window size we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
+of 50\%, and with different values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each window size and the damping value used to
+obtain it.
+
+Using the best set of parameters for each window size, we registered the
+achieved RMS against the values of the target grid and the time needed to fit
+the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
+In order to avoid any errors introduced by the way windows are shuffled, the
+RMS for each window size was obtained as the mean RMS achieved by using
+different random seeds.
+
+We have also registered the computational time needed to fit the
+gradient-boosted equivalent sources for each window size and computed the ratio
+between these times and the computational time needed to fit the non-boosted
+equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against window size.
+        Window sizes are given as a fraction of the dimensions of the synthetic
+        survey area.
+        (a)~Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different window sizes. Each RMS
+        error is the mean of the RMS produced by the same set of parameters but
+        with different random seeds.
+        (b)~Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+}
+    \label{fig:gradient-boosted-window-size}
+\end{figure}
+
+From the results obtained from the comparison with the synthetic airborne
+survey we can conclude that smaller windows generate less accurate predictions
+than using larger ones and require significantly more computational time to fit
+the sources.
+The reduction of the accuracy might be due to an oversimplification of the
+least-squares problem, and the increase of the computational time might be
+generated by the great number of iterations required to fit the sources.
+As the windows gets larger, the accuracy starts increasing because more data
+points are included into the fitting process of the source coefficients, while
+the fitting process takes less time due to a reduction of the number of
+iterations.
+For very large windows, both accuracy and fitting time are almost constant.
+
+In comparison with the non-boosted equivalent sources, we can see that the
+gradient-boosted ones produce slightly less accurate results due to not being
+able to achieve the global minimum of the least-squares problem, but they
+perform faster.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
+When using gradient-boosted equivalent sources we can conclude that we want to
+maximize the window size as much as possible.
+The only limitation to do so is to generate Jacobian matrices larger than the
+available memory.
+Therefore we recommend using the largest window that generates Jacobian
+matrices that could fit in the available memory.
+
+\subsection{Amount of overlap}
+
+Another factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the amount of overlap between adjacent windows.
+The previous choice of 50\% showed to be sufficiently good to achieve
+acceptable accuracy, although a deeper study should be carried out to assess
+how the amount of overlap impacts both accuracy and fitting time.
+
+We interpolated the synthetic airborne survey using the gradient boosted
+equivalent sources on the same points of the target grid.
+The interpolations were carried out using different amount of overlap, from
+0\% to 0.95\% with a step size of 0.05\%.
+For each overlap we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
+a window size of \BoostOverlappingWindowSize, and with different
+values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each overlap and the damping value used to
+obtain it.
+
+Using the best set of parameters for each overlap, we registered the achieved
+RMS against the values of the target grid and the time needed to fit the
+sources coefficients.
+The RMS was obtained as the mean RMS achieved by using different random seeds
+as we did on~\ref{sec:window_size}.
+
+We have also computed the fitting time ratio for each overlap, in a similar way
+we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against amount of
+        overlap.
+        (a)~Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different amount of overlap. Each
+        RMS error is the mean of the RMS produced by the same set of parameters
+        but with different random seeds.
+        (b)~Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+    }
+    \label{fig:gradient-boosted-overlap}
+\end{figure}
+
+From the results obtained we can conclude that a lower values of overlap
+generates less accurate results, while a higher overlap increases the
+computational time required for fitting the source coefficients due to the
+significant increment of the number of overlapping windows.
+
+We found that overlaps less than 40\% produce very inaccurate predictions in
+comparison with the non-boosted equivalent sources, while values larger that
+80\% produce predictions with almost the same level of accuracy as the latter.
+Nevertheless, overlap values larger that 70\% takes significantly more
+computational time to fit the source coefficients.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
+We can then conclude that using overlap values between 40\% and 70\% generate
+a balance between predictions accuracy and computational time needed to fit the
+source coefficients.
+This corroborates that our naive choice of 50\% is good enough for producing
+accurate predictions in reasonable times.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Gridding Australia gravity data}
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia.png}
+    \caption{
+      Pseudo-color maps of observed (left) and
+      interpolated (right) gravity disturbance of Australia.
+      Observations are part of a compilation by \citet{wynne2018} of
+      over 1.7 million ground gravity measurements.
+      Interpolated values were obtained through gradient-boosted equivalent
+      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
+      over the WGS84 ellipsoid.
+    }
+    \label{fig:australia}
+\end{figure*}
+
+Our final goal is to show how gradient-boosted equivalent sources can be used
+to interpolate a very large dataset of gravity data into a regular grid.
+We selected a compilation of gravity surveys over Australia made by
+\citet{wynne2018}.
+It consists in more than 1.7 million data points that cover most part of the
+Australia territory obtained through observations on ground.
+First we compute the gravity disturbance by removing the normal gravity from
+the observed gravity data (Fig.~\ref{fig:australia}).
+The normal gravity is computed on each observation point through the
+closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
+as reference.
+Then we obtain planar coordinates of the observation points by applying
+a Mercator projection.
+
+We start the interpolation process by defining a set of block-averaged sources
+at a relative depth of \AustraliaEqlDepth{} and a block spacing of
+\SI{1.8}{\kilo\meter}.
+These parameters create \AustraliaEqlNSources{}~point sources.
+The choice of the block spacing must be done taking into account the desired
+resolution of the final grid.
+If the grid will have a much higher resolution than the block spacing, the
+equivalent sources will not be able to reproduce the high frequency components
+of the data.
+Therefore we recommend setting a block spacing that matches the resolution of
+the final grid.
+In this case we will generate a regular grid with a resolution of 1~arc-minute,
+which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
+
+The coefficients of the gradient-boosted equivalent sources are estimated using
+a damping equal to \AustraliaEqlDamping{} and a window size of
+\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
+store the largest Jacobian matrix to 10GB.
+
+Finally, the equivalent sources are used to predict the values of the gravity
+disturbance on a regular grid of
+\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
+\AustraliaEqlGridHeight{} above the ellipsoid
+(Fig.~\ref{fig:australia}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Software implementation}
+
+We have implemented the methods described in the previous sections though
+a software written in Python language.
+The code for generating the results of this work are available in
+\url{https://doi.org/10.6084/m9.figshare.13604360} or
+\url{https//github.com/compgeolab/eql-gradient-boosted}.
+The gradient-boosted equivalent sources implementation is based on the
+non-boosted sources available through the Harmonica library
+\citep{harmonica2020}, part of the Fatiando a Terra project
+\citep{fatiando2013}.
+Another Python libraries were used:
+Verde \citep{verde2018} to apply block reductions and managing coordinates,
+Boule \citep{boule2020} for computing normal gravity,
+Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
+multidimensional datasets and numerical
+computations,
+Numba \citep{numba2015} for writing pre-comipled implementations and
+parallelization,
+Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
+the figures.
 

### 2021-01-25 manuscript/manuscript.tex

@@
 
-\section{Software implementation}
-
-We have implemented the methods described in the previous sections though
-a software written in Python language.
-The code for generating the results of this work are available in
-\url{https://doi.org/10.6084/m9.figshare.13604360} or
-\url{https//github.com/compgeolab/eql-gradient-boosted}.
-The gradient-boosted equivalent sources implementation is based on the
-non-boosted sources available through the Harmonica library
-\citep{harmonica2020}, part of the Fatiando a Terra project
-\citep{fatiando2013}.
-Another Python libraries were used:
-Verde \citep{verde2018} to apply block reductions and managing coordinates,
-Boule \citep{boule2020} for computing normal gravity,
-Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
-multidimensional datasets and numerical
-computations,
-Numba \citep{numba2015} for writing pre-comipled implementations and
-parallelization,
-Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
-the figures.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusions}
+
+Equivalent sources that uses the inverse of the distance as the Green's
+functions are well suited for interpolating gravity disturbance data.
+Block-averaged sources reduces the number of point sources, reducing the
+computational load needed to estimate their coefficients, preventing aliasing
+on the interpolated values while maintaining accurate predictions.
+Special attention must be payed when choosing the size of the block spacing:
+as a thumb rule, it must be approximately equal to the resolution of the
+regular grid where the values will be interpolated.
+The three compared strategies for setting the depth of the sources (constant
+depth, relative depth and variable depth) don't significantly affect
+the accuracy of the interpolations.
+Nevertheless, the choice of the parameters for each depth strategy does affects
+the accuracy and the frequency components of the interpolations.
+
+Gradient-boosted equivalent sources heavily reduces the computer memory
+needed to estimate source coefficients, making possible to interpolate even
+very large datasets.
+The interpolations obtained though this new method achieve almost the same
+accuracy than the non-boosted sources, while reducing the computation time
+needed to estimate the source coefficients.
+Because it doesn't involve any assumption on the location of the sources, it
+can be used in conjunction with any horizontal source layout and any strategy
+for setting their depth.
+Moreover, the results equivalent sources can be used not only for interpolating
+on a regular grid, but also on any set of observation points, allowing to
+create profiles or upward continuations.
+In order to maximize the accuracy of the interpolations, the size of the
+rolling windows must be chosen as the maximum value that creates Jacobian
+matrices that fit into our computer memory.
+Therefore its choice is subject to the particular infrastructure where the
+interpolation will be carried out.
+We have shown that an overlap of 50\% between adjacent windows achieves a good
+compromise between accuracy and computation time needed to fit the source
+coefficients.
+
+The gradient-boosted equivalent sources were used to interpolate a compilation
+of more than 1.7 million gravity points from Australia on a regular grid with
+a resolution of 1~arc-minute.
+The whole process was carried out on a modest personal computer, requiring
+a maximum of 10GB of memory.
+This shows how the new gradient-boosted equivalent sources can be applied to
+real-world data.
 

### 2021-01-26 manuscript/manuscript.tex
Use the siunits package
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

--- 2021-01-25 manuscript/manuscript.tex
@@
 For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of appropriately 0.8 mGal regardless of the depth type, with the
+values of approximately \SI{0.8}{\mgal} regardless of the depth type, with the
 exception of the regular-grid layout which produced a larger RMS of
-\BestGroundGridSourcesConstantDepthRms{} mGal.
+\SI{\BestGroundGridSourcesConstantDepthRms{}}{\mgal}.
 The differences between the target grid and the interpolated values are larger
@@
 For the synthetic airborne survey, all strategies (including the regular-grid)
-produced similar RMS errors of approximately 0.3 mGal.
+produced similar RMS errors of approximately \SI{0.3}{\mgal}.
 The maps of the differences between the target grid and interpolation results

### 2021-01-26 manuscript/manuscript.tex

@@
 \AustraliaEqlGridHeight{} above the ellipsoid
-(see Fig.~\ref{fig:australia-grid}).
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia-grid.png}
-    \caption{
-        Interpolated gravity disturbance of Australia on a regular grid at
-        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
-        were obtained through gradient-boosted equivalent sources.
-    }
-    \label{fig:australia-grid}
-\end{figure*}
+(Fig.~\ref{fig:australia}).
 

### 2021-01-26 manuscript/manuscript.tex
Merge the gradient boosting results into 1 figure
Easier to compare and the figures share x and y axis so this fits
nicely.

@@
 achieved RMS against the values of the target grid and the time needed to fit
-the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
+the sources coefficients (see Fig.~\ref{fig:gradient-boosted-comparison}a).
 In order to avoid any errors introduced by the way windows are shuffled, the
@@
 between these times and the computational time needed to fit the non-boosted
-equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
-    \caption{
-        Gradient-boosted equivalent sources performance against window size.
-        Window sizes are given as a fraction of the dimensions of the synthetic
-        survey area.
-        (a)~Root-mean-squared error between predictions and target grid using
-        non-boosted sources (orange dashed line) and gradient-boosted
-        equivalent sources (blue dots) for different window sizes. Each RMS
-        error is the mean of the RMS produced by the same set of parameters but
-        with different random seeds.
-        (b)~Ratio between the computational times needed to fit the
-        gradient-boosted and the non-boosted equivalent sources, respectively
-        (the fitting time ratio for the non-boosted equivalent sources is
-        therefore equal to one).
-}
-    \label{fig:gradient-boosted-window-size}
-\end{figure}
+equivalent sources (see Fig.~\ref{fig:gradient-boosted-comparison}b).
 
@@
 We have also computed the fitting time ratio for each overlap, in a similar way
-we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
-    \caption{
-        Gradient-boosted equivalent sources performance against amount of
-        overlap.
-        (a)~Root-mean-squared error between predictions and target grid using
-        non-boosted sources (orange dashed line) and gradient-boosted
-        equivalent sources (blue dots) for different amount of overlap. Each
-        RMS error is the mean of the RMS produced by the same set of parameters
-        but with different random seeds.
-        (b)~Ratio between the computational times needed to fit the
-        gradient-boosted and the non-boosted equivalent sources, respectively
-        (the fitting time ratio for the non-boosted equivalent sources is
-        therefore equal to one).
-    }
-    \label{fig:gradient-boosted-overlap}
-\end{figure}
+we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-comparison}d).
 
@@
 accurate predictions in reasonable times.
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
+    \caption{
+        Comparison of the interpolation RMS error and computation time for
+        regular least-squares equivalent sources (orange dashed lines) and
+        gradient-boosted equivalent sources (blue dots and error bars).
+        Both methods used the same source positions (block-averaged sources
+        with a relative depth).
+        Window sizes are given as a fraction of the survey area (e.g., 1
+        represents a window with the same area as the survey) and window
+        overlap is given as a fraction of the window size (e.g., 0.5 equals
+        50\% overlap).
+        Computation time refers to the time required to estimate the source
+        coefficients and is reported as a ratio between the gradient-boosted
+        and the regular equivalent sources.
+        For gradient-boosting, the RMS errors and computation times are the
+        means (error bars represent 1 standard deviation) of results using
+        different seeds for the pseudo-random number generator.
+        (a)~RMS error between the target grid and interpolation results and
+        (b)~computation time as a function of window size.
+        (c)~RMS error between the target grid and interpolation results and
+        (d)~computation time as a function of window overlap.
+}
+    \label{fig:gradient-boosted-comparison}
+\end{figure*}
 
@@
 
+\bibliographystyle{humannat}
+\bibliography{references}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \appendix
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{humannat}
-\bibliography{references}
-
 \end{document}

### 2021-01-26 notebooks/99-figures.py

@@ -17,6 +17,7 @@
 
 from pathlib import Path
 import xarray as xr
+import numpy as np
 import pandas as pd
 import verde as vd
 import pygmt
@@ -127,7 +128,6 @@ plt.tight_layout(w_pad=0, pad=0)
 plt.savefig(
     figs_dir / "synthetic-survey-layouts.pdf",
     bbox_inches="tight",
-    dpi=300,
 )
 # -
 
@@ -155,7 +155,6 @@ plt.tight_layout()
 plt.savefig(
     figs_dir / "target-grid.pdf",
     bbox_inches="tight",
-    dpi=300,
 )
 plt.show()
 # -
@@ -269,7 +268,9 @@ cbl = fig.colorbar(tmp, cax=cbar_ax, orientation="horizontal", label=f"{field_un
 cbl.ax.set_title("Difference between target and interpolated", fontsize="medium")
 
 plt.tight_layout(w_pad=0)
-plt.savefig(figs_dir / "ground_survey_differences.pdf", dpi=300)
+plt.savefig(figs_dir / "ground_survey_differences.pdf",
+    bbox_inches="tight",
+           )
 plt.show()
 # -
 
@@ -382,11 +383,12 @@ cbl = fig.colorbar(tmp, cax=cbar_ax, orientation="horizontal", label=f"{field_un
 cbl.ax.set_title("Difference between target and interpolated", fontsize="medium")
 
 plt.tight_layout(w_pad=0)
-plt.savefig(figs_dir / "airborne_survey_differences.pdf", dpi=300)
+plt.savefig(figs_dir / "airborne_survey_differences.pdf", 
+    bbox_inches="tight",)
 plt.show()
 # -
 
-# # Gradient boosted eqls: window size
+# # Gradient-boosted equivalent sources comparison
 
 # +
 eql_harmonic_results = pd.read_csv(
@@ -404,82 +406,90 @@ boost_window_size = pd.read_csv(
 
 boost_window_size
 
+boost_overlapping = pd.read_csv(
+    results_dir / "gradient-boosted" / "gradient-boosted-overlapping.csv"
+)
+
+boost_overlapping
+
 # +
-width = 3.33
-figsize = (width, width * 0.85 * 1.5)
-fig, (ax1, ax2) = plt.subplots(nrows=2, ncols=1, figsize=figsize, sharex=True)
-ax1.errorbar(
+figsize = (6.66, 3.5)
[…]

### 2021-01-26 manuscript/manuscript.tex
Review the window size results

@@
     \mathbf{d}^o.
+    \label{eq:least_squares_solution}
 \end{equation}
@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
+    \caption{
+        Maps of the observation locations and gravity values for the synthetic
+        ground and airborne surveys.
+        (a)~Horizontal position and height of the ground survey points.
+        (b)~Synthetic gravity data calculated on the ground survey points with
+        added pseudo-random Gaussian noise.
+        (c)~Horizontal position and height of the airborne survey points.
+        (d)~Synthetic gravity data calculated on the airborne survey points
+        with added pseudo-random Gaussian noise.
+        Heights are given in meters above the zero height plane.
+    }
+    \label{fig:synthetic-layouts}
+\end{figure*}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
+    \caption{
+        Pseudo-color map of the target grid of synthetic gravity data. The grid
+        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
+        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
+        above the zero height plane.
+    }
+    \label{fig:synthetic-target}
+\end{figure}
+
 We have used synthetic gravity datasets to test the interpolation accuracy of
@@
 
+\subsection{Source distribution strategies}
+
 \begin{figure*}
-    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
+    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
     \caption{
-        Maps of the observation locations and gravity values for the synthetic
-        ground and airborne surveys.
-        (a)~Horizontal position and height of the ground survey points.
-        (b)~Synthetic gravity data calculated on the ground survey points with
-        added pseudo-random Gaussian noise.
-        (c)~Horizontal position and height of the airborne survey points.
-        (d)~Synthetic gravity data calculated on the airborne survey points
-        with added pseudo-random Gaussian noise.
-        Heights are given in meters above the zero height plane.
-    }
-    \label{fig:synthetic-layouts}
+        Pseudo-color maps of the differences between the target grid and the
+        interpolated synthetic ground survey data produced by each source
+        distribution strategy.
+        The black dots represent the horizontal location of the synthetic data
+        points. The RMS error and total number of equivalent sources is
+        reported for each strategy at the top of the respective maps.
+    }
+    \label{fig:ground-survey-differences}
 \end{figure*}
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
     \caption{
-        Pseudo-color map of the target grid of synthetic gravity data. The grid
-        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
-        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
-        above the zero height plane.
-    }
-    \label{fig:synthetic-target}
-\end{figure}
-
-\subsection{Comparison of source distribution strategies}
+        Pseudo-color maps of the differences between the target grid and the
+        interpolated synthetic airborne survey data produced by each source
+        distribution strategy.
+        The black dots represent the horizontal location of the synthetic data
+        points. The RMS error and total number of equivalent sources is
+        reported for each strategy at the top of the respective maps.
+    }
+    \label{fig:airborne-survey-differences}
+\end{figure*}
 
@@
 
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
-    \caption{
-        Pseudo-color maps of the differences between the target grid and the
-        interpolated synthetic ground survey data produced by each source
-        distribution strategy.
-        The black dots represent the horizontal location of the synthetic data
-        points. The RMS error and total number of equivalent sources is
-        reported for each strategy at the top of the respective maps.
-    }
-    \label{fig:ground-survey-differences}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
-    \caption{
-        Pseudo-color maps of the differences between the target grid and the
-        interpolated synthetic airborne survey data produced by each source
-        distribution strategy.
-        The black dots represent the horizontal location of the synthetic data
-        points. The RMS error and total number of equivalent sources is
-        reported for each strategy at the top of the respective maps.
-    }
-    \label{fig:airborne-survey-differences}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Performance and accuracy of gradient boosting}
-
-Our second goal is to assess the accuracy of the predictions achieved by the
-gradient boosting algorithm while registering its performance by comparison
-with the non-boosted equivalent sources.
+\subsection{Window size and overlap in gradient boosting}
+
+We assessed the trade-offs in interpolation accuracy and computation time of
+the gradient-boosted equivalent sources algorithm as a function of the two key
+controlling factors: the window size and the window overlap.
+The comparisons were performed against a regular least-squares solution
+(Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
+(Fig.~\ref{fig:synthetic-layouts}c-d) .
+To avoid biasing the results, we used the same locations of equivalent sources
+for both the regular and gradient-boosted interpolations, namely
+block-averaged-sources with a block size of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
+relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.
 
@@
 
-One factor that plays an important role on the performance of the gradient
-boosted equivalent sources is the size of the overlapping windows used to create
-each set of equivalent sources.
 The size of the windows controls the size of the Jacobian matrices
-$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
-Thus, using smaller windows will reduce the amount of computer memory needed to
-fit the source coefficients.
-Nevertheless, smaller windows may produce less accurate predictions because
-their inability to achieve the global minimum of the misfit from
-equation~\ref{eq:misfit-unscaled}.
-Besides, the window size might also impact on the computation time needed to
-fit the source coefficients: smaller windows will generate simpler least-square
-problems which are easier to solve, but they will also create more iterations.
-
-We want to assess how the size of the overlapping windows impacts both the
-accuracy of the predictions and the computation time needed to fit the source
-coefficients in comparison with the performance of the non-boosted equivalent
-sources.
-
-We applied the gradient boosted equivalent sources to interpolate the synthetic
-airborne survey on the same points of the target grid.
-We selected several window sizes to assess how accuracy and performance depend
-on that variable.
-For each window size we gridded the synthetic data using block-averaged sources
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
-a relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
-of 50\%, and with different values of damping.
-Then we compared the resulting interpolations with the target grid in order to
-get the best prediction for each window size and the damping value used to
-obtain it.
-
-Using the best set of parameters for each window size, we registered the
-achieved RMS against the values of the target grid and the time needed to fit
-the sources coefficients (see Fig.~\ref{fig:gradient-boosted-comparison}a).
-In order to avoid any errors introduced by the way windows are shuffled, the
-RMS for each window size was obtained as the mean RMS achieved by using
-different random seeds.
-
-We have also registered the computational time needed to fit the
-gradient-boosted equivalent sources for each window size and computed the ratio
-between these times and the computational time needed to fit the non-boosted
-equivalent sources (see Fig.~\ref{fig:gradient-boosted-comparison}b).
-
-From the results obtained from the comparison with the synthetic airborne
-survey we can conclude that smaller windows generate less accurate predictions
-than using larger ones and require significantly more computational time to fit
-the sources.
-The reduction of the accuracy might be due to an oversimplification of the
-least-squares problem, and the increase of the computational time might be
-generated by the great number of iterations required to fit the sources.
-As the windows gets larger, the accuracy starts increasing because more data
-points are included into the fitting process of the source coefficients, while
-the fitting process takes less time due to a reduction of the number of
-iterations.
-For very large windows, both accuracy and fitting time are almost constant.
-
-In comparison with the non-boosted equivalent sources, we can see that the
-gradient-boosted ones produce slightly less accurate results due to not being
-able to achieve the global minimum of the least-squares problem, but they
-perform faster.
-
-THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
-
-When using gradient-boosted equivalent sources we can conclude that we want to
-maximize the window size as much as possible.
-The only limitation to do so is to generate Jacobian matrices larger than the
-available memory.
-Therefore we recommend using the largest window that generates Jacobian
-matrices that could fit in the available memory.
+$\tilde{\mathbf{A}}_k$ by limiting the number of data points and equivalent
+sources used in each step of the gradient-boosting algorithm
+(Alg.~\ref{alg:gradient_boosting_window}).
+Thus, using smaller windows will reduce the total amount of computer memory
+required to estimate the source coefficients.
+Nevertheless, smaller windows may produce less accurate interpolations by
+failing to achieve the global minimum of the goal function in
+Eq.~\ref{eq:misfit}.
+The window size might also impact the computation time in non-intuitive ways
+since smaller windows generate smaller least-squares problems but also require
+more gradient-boosting iterations.
+
+We calculated the interpolation RMS error and computation time for a fixed
+window overlap of 50\% and several window sizes.
+To avoid any biases introduced by the shuffling of windows, the calculations
+were repeated using different seeds for the pseudo-random number generator used
+in the shuffling.
+Figs.~\ref{fig:gradient-boosted-comparison}a and
+\ref{fig:gradient-boosted-comparison}c show the RMS error and computation time
+required for estimating the source coefficients, respectively, as a function of
+the window size.
+
+The results show that the interpolation RMS error for gradient-boosting is
+generally larger than the error for regular equivalent sources.
+The error decreases asymptotically to within $\sim 40\%$ of the regular
+equivalent sources for windows with an area greater than $\sim 35\%$ of the
+survey area.
+The computation time similarly decreases with window size, with the
+gradient-boosting being generally faster than the regular equivalent sources
+for windows with an area greater than $\sim 20\%$ of the survey area.
+As the window size increases, both RMS error and computation time appear to
+stabilize to nearly constant levels.
 
@@
 
+Window size:
+
+In comparison with the non-boosted equivalent sources, we can see that the
+gradient-boosted ones produce slightly less accurate results due to not being
+able to achieve the global minimum of the least-squares problem, but they
+perform faster.
+The reduction of the accuracy might be due to an oversimplification of the
+least-squares problem, and the increase of the computational time might be
+generated by the great number of iterations required to fit the sources.
+As the windows gets larger, the accuracy starts increasing because more data
+points are included into the fitting process of the source coefficients, while
+the fitting process takes less time due to a reduction of the number of
+iterations.
+When using gradient-boosted equivalent sources we can conclude that we want to
+maximize the window size as much as possible.
+The only limitation to do so is to generate Jacobian matrices larger than the
+available memory.
+Therefore we recommend using the largest window that generates Jacobian
+matrices that could fit in the available memory.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-26 notebooks/99-figures.py

@@ -413,7 +413,7 @@ boost_overlapping = pd.read_csv(
 boost_overlapping
 
 # +
-figsize = (6.66, 3.5)
+figsize = (6.66, 4)
 fig, axes = plt.subplots(nrows=2, ncols=2, figsize=figsize, sharex="col", sharey="row")
 
 

### 2021-01-26 manuscript/manuscript.tex
Finish review of the window overlap section

@@
 
-\subsubsection{Amount of overlap}
-
-Another factor that plays an important role on the performance of the gradient
-boosted equivalent sources is the amount of overlap between adjacent windows.
-The previous choice of 50\% showed to be sufficiently good to achieve
-acceptable accuracy, although a deeper study should be carried out to assess
-how the amount of overlap impacts both accuracy and fitting time.
-
-We interpolated the synthetic airborne survey using the gradient boosted
-equivalent sources on the same points of the target grid.
-The interpolations were carried out using different amount of overlap, from
-0\% to 0.95\% with a step size of 0.05\%.
-For each overlap we gridded the synthetic data using block-averaged sources
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
-a relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
-a window size of \BoostOverlappingWindowSize, and with different
-values of damping.
-Then we compared the resulting interpolations with the target grid in order to
-get the best prediction for each overlap and the damping value used to
-obtain it.
-
-Using the best set of parameters for each overlap, we registered the achieved
-RMS against the values of the target grid and the time needed to fit the
-sources coefficients.
-The RMS was obtained as the mean RMS achieved by using different random seeds
-as we did on~\ref{sec:window_size}.
-
-We have also computed the fitting time ratio for each overlap, in a similar way
-we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-comparison}d).
-
-From the results obtained we can conclude that a lower values of overlap
-generates less accurate results, while a higher overlap increases the
-computational time required for fitting the source coefficients due to the
-significant increment of the number of overlapping windows.
-
-We found that overlaps less than 40\% produce very inaccurate predictions in
-comparison with the non-boosted equivalent sources, while values larger that
-80\% produce predictions with almost the same level of accuracy as the latter.
-Nevertheless, overlap values larger that 70\% takes significantly more
-computational time to fit the source coefficients.
-
-THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
-
-We can then conclude that using overlap values between 40\% and 70\% generate
-a balance between predictions accuracy and computational time needed to fit the
-source coefficients.
-This corroborates that our naive choice of 50\% is good enough for producing
-accurate predictions in reasonable times.
+\subsubsection{Window overlap}
+
+The amount of overlap between adjacent windows plays an important role in the
+performance of the gradient-boosted equivalent sources.
+It controls the number of iterations and how often a particular source is used
+in the least-squares fitting process.
+While the experiments in the previous section showed that 50\% overlap was
+sufficient to achieve acceptable interpolation accuracy, we separately studied
+the impacts of the amount of window overlap on both accuracy and computation
+time.
+
+We performed a similar experiment to one in section~\ref{sec:window_size} but
+this time kept the window size fixed to \BoostOverlappingWindowSize{} and
+varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
+All other experimental procedures remained unchanged.
+Figs.~\ref{fig:gradient-boosted-comparison}b and
+\ref{fig:gradient-boosted-comparison}d show the RMS error and computation time
+required for estimating the source coefficients, respectively, as a function of
+the window overlap.
+
+Our results show what the interpolation RMS error decreases with the amount of
+overlap, reaching the same accuracy as the regular equivalent sources at
+approximately 90\% overlap.
+On the other hand, the computation time increases with the amount of overlap,
+becoming larger than that of the regular equivalent sources for overlaps
+greater than 70\%.
+This is expected since increasing the overlap adds iterations to the gradient
+boosting algorithm without decreasing the individual least-squares problem
+sizes to compensate.
 
@@
 
+Overlap:
+
+We can then conclude that using overlap values between 40\% and 70\% generate
+a balance between predictions accuracy and computational time needed to fit the
+source coefficients.
+This corroborates that our naive choice of 50\% is good enough for producing
+accurate predictions in reasonable times.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-26 manuscript/manuscript.tex
Update manuscript/manuscript.tex
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
 the gradient-boosted equivalent sources algorithm as a function of the two key
-controlling factors: the window size and the window overlap.
+controlling factors: the window size and the amount of overlap between adjacent
+windows.
 The comparisons were performed against a regular least-squares solution

### 2021-01-26 manuscript/manuscript.tex
Start reviewing the Australia application

--- 2021-01-26 manuscript/manuscript.tex
@@
     \mathbf{d}^o.
-    \label{eq:least_squares_solution}
 \end{equation}
@@
 each of these strategies on synthetic data.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Tests on synthetic data}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
+\section{Comparison of source distributions}
+
+The combination of the three source layouts with the three strategies to define
+the depth of the sources define seven different source distributions (see
+Table~\ref{tab:source-distributions}).
+The \emph{grid sources} is only compatible with the \emph{constant depth}
+scheme if no further information is provided.
+
+\begin{table*}
+    \centering
     \caption{
-        Maps of the observation locations and gravity values for the synthetic
-        ground and airborne surveys.
-        (a)~Horizontal position and height of the ground survey points.
-        (b)~Synthetic gravity data calculated on the ground survey points with
-        added pseudo-random Gaussian noise.
-        (c)~Horizontal position and height of the airborne survey points.
-        (d)~Synthetic gravity data calculated on the airborne survey points
-        with added pseudo-random Gaussian noise.
-        Heights are given in meters above the zero height plane.
-    }
-    \label{fig:synthetic-layouts}
-\end{figure*}
+        Source distributions as combinations of source layouts and depth
+        strategies.
+    }
+    \label{tab:source-distributions}
+    \begin{tabular}{lccc}
+        & Source below data & Block averaged sources & Grid sources \\ \hline
+        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
+        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
+    \end{tabular}
+\end{table*}
+
+Our first goal is to to compare the performance of all source distributions
+from Table~\ref{tab:source-distributions} when predicting harmonic field data
+using the equivalent sources technique.
+To do so we have created a synthetic model made out of prisms of different
+shape and density contrasts.
+The gravitational effect of this synthetic model have been computed on
+a regular grid (\emph{target} grid) at a constant height and on two different
+set of observation points that we will call \emph{synthetic surveys}: a ground
+and an airborne survey.
+The data from each synthetic survey is interpolated on the points of the
+\emph{target} grid and then scored against its values.
+We can then quantitatively compare how accurate is each source distribution at
+predicting unobserved data on each synthetic survey and quantify the
+computational load needed to do it.
+
+\subsection{Synthetic Model}
+
+%Describe forward model made out of prisms.
+%Show prisms model?
+
+The synthetic model is made out of \NPrisms{} prisms distributed on a region of
+\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
+height plane.
+Density contrast of prisms range from \ModelMinDensity{} and
+\ModelMaxDensity{}.
+We built deep big and thin shallow prisms for creating gravity anomalies with
+long and short wavelengths, respectively.
+
+The vertical component of the gravity acceleration generated by the synthetic
+model has been computed on a regular grid of
+\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
+\TargetSpacing{} located \TargetHeight{} above the zero height plane
+(Fig.~\ref{fig:target-grid}), using \citet{nagy2000} and \citet{nagy2002}.
+We will refer to this grid as the \emph{target} grid in the future.
 
@@
     \caption{
-        Pseudo-color map of the target grid of synthetic gravity data. The grid
-        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
-        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
-        above the zero height plane.
-    }
-    \label{fig:synthetic-target}
+        Target grid. Gravitational effect of synthetic model on a regular grid
+        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
+        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
+        zero height plane.
+    }
+    \label{fig:target-grid}
 \end{figure}
 
-We have used synthetic gravity datasets to test the interpolation accuracy of
-the difference horizontal and vertical source distribution strategies as well
-as the gradient-boosted equivalent source method.
-To generate the data, we created a model that is made out of \NPrisms{}
-right-rectangular prisms, distributed on a region of
-\ModelEasting{}$\times$\ModelNorthing{} with depths varying between
-\ModelDepth{} and zero.
-The density contrast of prisms ranges from \ModelMinDensity{} to
-\ModelMaxDensity{}.
-The model includes prisms of different shapes, sizes, and depths to create
-gravity disturbances with a variety of wavelengths.
-
-We created two synthetic datasets from the model, one simulating a ground
-survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
-To create the synthetic ground survey, we selected measurement positions from a
-portion of a public domain dataset for Southern Africa, available through the
-NOAA National Centers for Environmental Information (NCEI)\footnote{
-\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}
-(last accessed 25 January 2020)}.
-For the synthetic airborne survey, we used a portion of the Great Britain Aeromagnetic
+\subsection{Synthetic Surveys}
+
+In order to compare the predictive capabilities of each source distribution
+under on different surveys, we created a ground and an airborne \emph{synthetic
+surveys}.
+For creating the synthetic ground survey we selected a portion of the Southern
+Africa Gravity Data available through the
+\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
+For the airborne survey we used a portion of the Great Britain Aeromagnetic
 Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
-Ltd between 1955 and 1965 and made publicly available by the
-British Geological Survey (BGS)\footnote{
-\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}
-(last accessed 25 January 2020)}.
-In both cases, we rescaled the horizontal coordinates of each survey portion to
-span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
-dimensions.
-The ground survey contains \GroundSurveyPoints{} observations distributed at
-heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
-(Fig.~\ref{fig:synthetic-layouts}a).
-The airborne survey has \AirborneSurveyPoints{} observations at heights between
+Ltd between 1955 and 1965 and made available by the
+\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
+British Geological Survey (BGS)
+}.
+
+On both cases we selected only a portion of the survey and rescaled it to span
+on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
+The ground survey is composed by \GroundSurveyPoints{} observation points
+distributed at heights ranging between \GroundSurveyMinHeight{} and
+\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
+While the airborne survey has \AirborneSurveyPoints{} points at heights between
 \AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
-(Fig.~\ref{fig:synthetic-layouts}c).
-
-The vertical component of the gravitational acceleration generated by the
-model was computed  using the method of \citet{nagy2000, nagy2002}
-with recent modifications by \citet{fukushima2020},
-as implemented in the open-source software Harmonica \citep{harmonica}.
-We generated a \emph{target grid} of
-\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
-\TargetSpacing{} and located \TargetHeight{} above the zero height plane
-(Fig.~\ref{fig:synthetic-target}) to serve as a reference when calculating the
-interpolation error.
-We then generated synthetic ground (Fig.~\ref{fig:synthetic-layouts}b) and
-airborne (Fig.~\ref{fig:synthetic-layouts}d) data to which we added
-pseudo-random Gaussian noise with zero mean and \SurveyNoise{} standard
-deviation.
-
-\subsection{Source distribution strategies}
+(Fig.~\ref{fig:synthetic-ground-survey}(a)).
+
+The vertical component of the gravity acceleration generated by the synthetic
+model has been computed on both surveys.
+Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
+to the effect of the synthetic model to simulate acquisition errors
+(Figs.~\ref{fig:synthetic-ground-survey}(b)
+and~\ref{fig:synthetic-airborne-survey}(b)).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
+    \caption{
+        Synthetic ground survey.
+        (a)~Location of observation points. Altitude given in meters above the
+            zero height plane.
+        (b)~Vertical component of gravity acceleration generated by the
+            synthetic model plus Gaussian noise on the ground survey
+            observation points.
+    }
+    \label{fig:synthetic-ground-survey}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/airborne-survey.pdf}
+    \caption{
+        Synthetic airborne survey.
+        (a)~Location of observation points. Altitude given in meters above the
+            zero height plane.
+        (b)~Vertical component of gravity acceleration generated by the
+            synthetic model plus Gaussian noise on the airborne survey
+            observation points.
+        Based upon the Great Britain aeromagnetic data, with the permission of
+        the British Geological Survey.
+    }
+    \label{fig:synthetic-airborne-survey}
+\end{figure}
+
+\subsection{Comparisons}
+
+Each source distribution from Table~\ref{tab:source-distributions} needs
+certain parameters in order to build the set of point sources.
+The prediction capabilities of the source distribution depends on the choice of
+these parameters.
+For example, locating the sources beneath the data points at constant depth
+needs the definition of the \emph{depth} parameter.
+If the sources are set too close to the data points, the source distribution
+it's very likely to over-fit the data: the measured field will be recovered, but
+the predictions on unobserved locations will be very inaccurate.
+Another parameter that plays an important role on the predictive capabilities
+of the sources is the \emph{damping}.
+
+On real world scenarios, choosing the values of the parameters is a challenging
+task: it's not easy to determine the accuracy of the predictions without
+knowing the true value of the field on unobserved locations.
+This problem can be solved through cross-validation.
+When working with a synthetic model, the situation is different: we can compute
+the true values of harmonic field generated by the synthetic model on any
+point.
+Therefore, interpolating the observed data on the same points of the
+\emph{target} grid and then scoring the prediction against the true values of
+the \emph{target} grid constitutes an objective way to measure the predictive
+accuracy of the source distribution.
+
+In order to compare the predictive capabilities of each source distribution we
+perform a parameter search to obtain the best prediction that can be achieved
+by each one of them.
+For each source distribution we proposed different values for each parameter
+(see Tables~\ref{tab:parameters-ground-survey}
+and~\ref{tab:parameters-airborne-survey}).
+These parameters values are combined obtaining several \emph{set of
+parameters}.
+We use each set of parameters to create the sources, fit their coefficients
+through least-squares and predict the field on the same points of the
+\emph{target} grid.
+We then \emph{score} the prediction by computing the root mean square (RMS)
+between the prediction and the true values of the \emph{target} grid.
+Finally, we obtain the \emph{best prediction} for each source distribution as
+the one that achieves the lowest RMS.
+This process is carried out on both ground and airborne synthetic surveys.
+See Algorithm~\ref{alg:source_distributions_comparison} for a concise
+representation of it.
+
+\begin{algorithm}[!h]
+  \DontPrintSemicolon
+  \setstretch{1.5}
+
+  define possible values for each parameter
+  \;
+
+  generate each possible combination of parameters values: obtain several
+  \emph{sets of parameters}
+  \;
+
+  \For{each set of parameters}{
+
+    select the $M$ locations of the equivalent sources
+    \;
+
+    estimate the source coefficients
+    \;
+
+    predict field values on target grid points
+    \;
+
+    calculate the RMS between the predictions and the target grid
+    \;
+  }
+
+  the best set of parameters produces the smallest RMS
+  \;
+
+  \BlankLine
+  \setstretch{1}
+  \caption{Algorithm for estimating the best prediction using synthetic data.}
+  \label{alg:source_distributions_comparison}
+\end{algorithm}
+
+Tables~\ref{tab:parameters-ground-survey}
+and~\ref{tab:parameters-airborne-survey} also show the parameter combination
+that produces the best prediction for each source distribution and its
+corresponding RMS score, for both ground and airborne synthetic surveys,
+respectively.
+Figures~\ref{fig:ground-survey-differences}
+and~\ref{fig:airborne-survey-differences} show the differences between the
+target grid and the best prediction achieved by each source distribution, for
+both ground and airborne synthetic surveys, respectively.
 
@@
     \caption{
-        Pseudo-color maps of the differences between the target grid and the
-        interpolated synthetic ground survey data produced by each source
-        distribution strategy.
-        The black dots represent the horizontal location of the synthetic data
-        points. The RMS error and total number of equivalent sources is
-        reported for each strategy at the top of the respective maps.
+        Differences between gravitational effects measured on the target grid
+        and the ones produced by the best prediction made by each source
+        distribution based on the synthetic ground survey.
     }
@@
     \caption{
-        Pseudo-color maps of the differences between the target grid and the
-        interpolated synthetic airborne survey data produced by each source
-        distribution strategy.
-        The black dots represent the horizontal location of the synthetic data
-        points. The RMS error and total number of equivalent sources is
-        reported for each strategy at the top of the respective maps.
+        Differences between gravitational effects measured on the target grid
+        and the ones produced by the best prediction made by each source
+        distribution based on the synthetic airborne survey.
     }
@@
 
-We investigated the effect of different strategies for distributing the
-equivalent sources horizontally and vertically on interpolation accuracy.
-To do this, we used the damped least-squares solution described in
-Section~\ref{sec:eql_inversion} (without gradient boosting) to interpolate the
-synthetic datasets (Fig.~\ref{fig:synthetic-layouts}) and compared the results
-against the target grid (Fig.~\ref{fig:synthetic-target}).
-This process was repeated for each combination of horizontal layout
-(sources-below-data and block-averaged-sources) and depth type (constant,
-relative, and variable) and for regular-grid sources with a constant depth,
-totalling 7 different combinations.
-
-Each source distribution strategy requires certain hyper-parameters to be
-chosen in order to build the set of point sources.
-For example, using a constant depth needs the definition of the depth and using
-block-average-sources requires the definition of the block size.
-The predictive capabilities of the equivalent sources depend on the choice of
-these hyper-parameters.
-To ensure that our comparisons are fair, we perform an exhaustive search over
-combinations of hyper-parameter values (including the damping parameter from
-Eq.~\ref{eq:misfit}) to obtain the best prediction that can be achieved by each
-source distribution strategy.
-Here, the best prediction is defined as the one that minimizes the root
-mean-square error (RMS) between interpolated values and the target grid
-(Fig.~\ref{fig:synthetic-target}).
-The parameter values used in these searches and the one producing the smallest
-RMS error are outlined in Tables~\ref{tab:parameters-ground-survey}
-and~\ref{tab:parameters-airborne-survey}.
-
-Figures~\ref{fig:ground-survey-differences}
-and~\ref{fig:airborne-survey-differences} show the differences between the
-target grid and the best prediction achieved by each source distribution
-strategy for the ground and airborne synthetic surveys, respectively.
-For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of approximately \SI{0.8}{\mgal} regardless of the depth type, with the
-exception of the regular-grid layout which produced a larger RMS of
-\SI{\BestGroundGridSourcesConstantDepthRms{}}{\mgal}.
-The differences between the target grid and the interpolated values are larger
-in regions of poor data coverage.
-Edge effects are present for all strategies but are noticeably smaller for the
-combination of block-averaged-sources with a variable depth based on the
-nearest neighbour distance.
-For the synthetic airborne survey, all strategies (including the regular-grid)
-produced similar RMS errors of approximately \SI{0.3}{\mgal}.
-The maps of the differences between the target grid and interpolation results
-are visually indistinguishable from each other.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Window size and overlap in gradient boosting}
-
-We assessed the trade-offs in interpolation accuracy and computation time of
-the gradient-boosted equivalent sources algorithm as a function of the two key
-controlling factors: the window size and the window overlap.
-The comparisons were performed against a regular least-squares solution
-(Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
-(Fig.~\ref{fig:synthetic-layouts}c-d) .
-To avoid biasing the results, we used the same locations of equivalent sources
-for both the regular and gradient-boosted interpolations, namely
-block-averaged-sources with a block size of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
-relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.
-
-\subsubsection{Window size}
-\label{sec:window_size}
-
-The size of the windows controls the size of the Jacobian matrices
-$\tilde{\mathbf{A}}_k$ by limiting the number of data points and equivalent
-sources used in each step of the gradient-boosting algorithm
-(Alg.~\ref{alg:gradient_boosting_window}).
-Thus, using smaller windows will reduce the total amount of computer memory
-required to estimate the source coefficients.
-Nevertheless, smaller windows may produce less accurate interpolations by
-failing to achieve the global minimum of the goal function in
-Eq.~\ref{eq:misfit}.
-The window size might also impact the computation time in non-intuitive ways
-since smaller windows generate smaller least-squares problems but also require
-more gradient-boosting iterations.
-
-We calculated the interpolation RMS error and computation time for a fixed
-window overlap of 50\% and several window sizes.
-To avoid any biases introduced by the shuffling of windows, the calculations
-were repeated using different seeds for the pseudo-random number generator used
-in the shuffling.
-Figs.~\ref{fig:gradient-boosted-comparison}a and
-\ref{fig:gradient-boosted-comparison}c show the RMS error and computation time
-required for estimating the source coefficients, respectively, as a function of
-the window size.
-
-The results show that the interpolation RMS error for gradient-boosting is
-generally larger than the error for regular equivalent sources.
-The error decreases asymptotically to within $\sim 40\%$ of the regular
-equivalent sources for windows with an area greater than $\sim 35\%$ of the
-survey area.
-The computation time similarly decreases with window size, with the
-gradient-boosting being generally faster than the regular equivalent sources
-for windows with an area greater than $\sim 20\%$ of the survey area.
-As the window size increases, both RMS error and computation time appear to
-stabilize to nearly constant levels.
-
-\subsubsection{Amount of overlap}
-
-Another factor that plays an important role on the performance of the gradient
-boosted equivalent sources is the amount of overlap between adjacent windows.
-The previous choice of 50\% showed to be sufficiently good to achieve
-acceptable accuracy, although a deeper study should be carried out to assess
-how the amount of overlap impacts both accuracy and fitting time.
-
-We interpolated the synthetic airborne survey using the gradient boosted
-equivalent sources on the same points of the target grid.
-The interpolations were carried out using different amount of overlap, from
-0\% to 0.95\% with a step size of 0.05\%.
-For each overlap we gridded the synthetic data using block-averaged sources
-with a spacing of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
-a relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
-a window size of \BoostOverlappingWindowSize, and with different
-values of damping.
-Then we compared the resulting interpolations with the target grid in order to
-get the best prediction for each overlap and the damping value used to
-obtain it.
-
-Using the best set of parameters for each overlap, we registered the achieved
-RMS against the values of the target grid and the time needed to fit the
-sources coefficients.
-The RMS was obtained as the mean RMS achieved by using different random seeds
-as we did on~\ref{sec:window_size}.
-
-We have also computed the fitting time ratio for each overlap, in a similar way
-we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-comparison}d).
-
-From the results obtained we can conclude that a lower values of overlap
-generates less accurate results, while a higher overlap increases the
-computational time required for fitting the source coefficients due to the
-significant increment of the number of overlapping windows.
-
-We found that overlaps less than 40\% produce very inaccurate predictions in
-comparison with the non-boosted equivalent sources, while values larger that
-80\% produce predictions with almost the same level of accuracy as the latter.
-Nevertheless, overlap values larger that 70\% takes significantly more
-computational time to fit the source coefficients.
-
-THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
-
-We can then conclude that using overlap values between 40\% and 70\% generate
-a balance between predictions accuracy and computational time needed to fit the
-source coefficients.
-This corroborates that our naive choice of 50\% is good enough for producing
-accurate predictions in reasonable times.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
-    \caption{
-        Comparison of the interpolation RMS error and computation time for
-        regular least-squares equivalent sources (orange dashed lines) and
-        gradient-boosted equivalent sources (blue dots and error bars).
-        Both methods used the same source positions (block-averaged sources
-        with a relative depth).
-        Window sizes are given as a fraction of the survey area (e.g., 1
-        represents a window with the same area as the survey) and window
-        overlap is given as a fraction of the window size (e.g., 0.5 equals
-        50\% overlap).
-        Computation time refers to the time required to estimate the source
-        coefficients and is reported as a ratio between the gradient-boosted
-        and the regular equivalent sources.
-        For gradient-boosting, the RMS errors and computation times are the
-        means (error bars represent 1 standard deviation) of results using
-        different seeds for the pseudo-random number generator.
-        (a)~RMS error between the target grid and interpolation results and
-        (b)~computation time as a function of window size.
-        (c)~RMS error between the target grid and interpolation results and
-        (d)~computation time as a function of window overlap.
-}
-    \label{fig:gradient-boosted-comparison}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Gridding Australia gravity data}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia.png}
-    \caption{
-      Pseudo-color maps of observed (left) and
-      interpolated (right) gravity disturbance of Australia.
-      Observations are part of a compilation by \citet{wynne2018} of
-      over 1.7 million ground gravity measurements.
-      Interpolated values were obtained through gradient-boosted equivalent
-      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
-      over the WGS84 ellipsoid.
-    }
-    \label{fig:australia}
-\end{figure*}
-
-Our final goal is to show how gradient-boosted equivalent sources can be used
-to interpolate a very large dataset of gravity data into a regular grid.
-We selected a compilation of gravity surveys over Australia made by
-\citet{wynne2018}.
-It consists in more than 1.7 million data points that cover most part of the
-Australia territory obtained through observations on ground.
-First we compute the gravity disturbance by removing the normal gravity from
-the observed gravity data (Fig.~\ref{fig:australia}).
-The normal gravity is computed on each observation point through the
-closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
-as reference.
-Then we obtain planar coordinates of the observation points by applying
-a Mercator projection.
-
-We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block spacing of
-\SI{1.8}{\kilo\meter}.
-These parameters create \AustraliaEqlNSources{}~point sources.
-The choice of the block spacing must be done taking into account the desired
-resolution of the final grid.
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
-In this case we will generate a regular grid with a resolution of 1~arc-minute,
-which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
-
-The coefficients of the gradient-boosted equivalent sources are estimated using
-a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
-store the largest Jacobian matrix to 10GB.
-
-Finally, the equivalent sources are used to predict the values of the gravity
-disturbance on a regular grid of
-\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid
-(Fig.~\ref{fig:australia}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-
-\subsection{Location of sources}
+\subsection{Discussion}
 
@@
 
-\subsection{Gradient boosting}
-
-Window size:
-
-In comparison with the non-boosted equivalent sources, we can see that the
-gradient-boosted ones produce slightly less accurate results due to not being
-able to achieve the global minimum of the least-squares problem, but they
-perform faster.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Performance of gradient-boosted equivalent sources}
+
+Our second goal is to assess the accuracy of the predictions achieved by the
+gradient boosting algorithm while registering its performance by comparison
+with the non-boosted equivalent sources.
+
+\subsection{Window size}
+\label{sec:window_size}
+
+One factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the size of the overlapping windows used to create
+each set of equivalent sources.
+The size of the windows controls the size of the Jacobian matrices
+$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
+Thus, using smaller windows will reduce the amount of computer memory needed to
+fit the source coefficients.
+Nevertheless, smaller windows may produce less accurate predictions because
+their inability to achieve the global minimum of the misfit from
+equation~\ref{eq:misfit-unscaled}.
+Besides, the window size might also impact on the computation time needed to
+fit the source coefficients: smaller windows will generate simpler least-square
+problems which are easier to solve, but they will also create more iterations.
+
+We want to assess how the size of the overlapping windows impacts both the
+accuracy of the predictions and the computation time needed to fit the source
+coefficients in comparison with the performance of the non-boosted equivalent
+sources.
+
+We applied the gradient boosted equivalent sources to interpolate the synthetic
+airborne survey on the same points of the target grid.
+We selected several window sizes to assess how accuracy and performance depend
+on that variable.
+For each window size we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
+of 50\%, and with different values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each window size and the damping value used to
+obtain it.
+
+Using the best set of parameters for each window size, we registered the
+achieved RMS against the values of the target grid and the time needed to fit
+the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
+In order to avoid any errors introduced by the way windows are shuffled, the
+RMS for each window size was obtained as the mean RMS achieved by using
+different random seeds.
+
+We have also registered the computational time needed to fit the
+gradient-boosted equivalent sources for each window size and computed the ratio
+between these times and the computational time needed to fit the non-boosted
+equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against window size.
+        Window sizes are given as a fraction of the dimensions of the synthetic
+        survey area.
+        (a)~Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different window sizes. Each RMS
+        error is the mean of the RMS produced by the same set of parameters but
+        with different random seeds.
+        (b)~Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+}
+    \label{fig:gradient-boosted-window-size}
+\end{figure}
+
+From the results obtained from the comparison with the synthetic airborne
+survey we can conclude that smaller windows generate less accurate predictions
+than using larger ones and require significantly more computational time to fit
+the sources.
 The reduction of the accuracy might be due to an oversimplification of the
@@
 iterations.
+For very large windows, both accuracy and fitting time are almost constant.
+
+In comparison with the non-boosted equivalent sources, we can see that the
+gradient-boosted ones produce slightly less accurate results due to not being
+able to achieve the global minimum of the least-squares problem, but they
+perform faster.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
 When using gradient-boosted equivalent sources we can conclude that we want to
@@
 
+\subsection{Amount of overlap}
+
+Another factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the amount of overlap between adjacent windows.
+The previous choice of 50\% showed to be sufficiently good to achieve
+acceptable accuracy, although a deeper study should be carried out to assess
+how the amount of overlap impacts both accuracy and fitting time.
+
+We interpolated the synthetic airborne survey using the gradient boosted
+equivalent sources on the same points of the target grid.
+The interpolations were carried out using different amount of overlap, from
+0\% to 0.95\% with a step size of 0.05\%.
+For each overlap we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
+a window size of \BoostOverlappingWindowSize, and with different
+values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each overlap and the damping value used to
+obtain it.
+
+Using the best set of parameters for each overlap, we registered the achieved
+RMS against the values of the target grid and the time needed to fit the
+sources coefficients.
+The RMS was obtained as the mean RMS achieved by using different random seeds
+as we did on~\ref{sec:window_size}.
+
+We have also computed the fitting time ratio for each overlap, in a similar way
+we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against amount of
+        overlap.
+        (a)~Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different amount of overlap. Each
+        RMS error is the mean of the RMS produced by the same set of parameters
+        but with different random seeds.
+        (b)~Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+    }
+    \label{fig:gradient-boosted-overlap}
+\end{figure}
+
+From the results obtained we can conclude that a lower values of overlap
+generates less accurate results, while a higher overlap increases the
+computational time required for fitting the source coefficients due to the
+significant increment of the number of overlapping windows.
+
+We found that overlaps less than 40\% produce very inaccurate predictions in
+comparison with the non-boosted equivalent sources, while values larger that
+80\% produce predictions with almost the same level of accuracy as the latter.
+Nevertheless, overlap values larger that 70\% takes significantly more
+computational time to fit the source coefficients.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
+
+We can then conclude that using overlap values between 40\% and 70\% generate
+a balance between predictions accuracy and computational time needed to fit the
+source coefficients.
+This corroborates that our naive choice of 50\% is good enough for producing
+accurate predictions in reasonable times.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Gridding gravity data from Australia}
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia.png}
+    \caption{
+      Pseudo-color maps of observed (left) and
+      interpolated (right) gravity disturbance of Australia.
+      Observations are part of a compilation by \citet{wynne2018} of
+      over 1.7 million ground gravity measurements.
+      Interpolated values were obtained through gradient-boosted equivalent
+      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
+      over the WGS84 ellipsoid.
+    }
+    \label{fig:australia}
+\end{figure*}
+
+This section will demonstrate how gradient-boosted equivalent sources can be
+used to interpolate large datasets of gravity data onto a regular grid at
+uniform height.
+For this purpose, we selected a compilation of ground gravity surveys over
+Australia made by \citet{wynne2018} (TODO: MENTION THE COMPGEOLAB VERSION?).
+It contains over 1.7 million data points and covers most of the Australian
+territory at variable point spacings.
+We computed the gravity disturbance by removing the normal gravity of the WGS84
+ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
+Here, normal gravity was computed at each observation point through the
+closed-form formula of \citet{ligotze2001} (TODO: ADD CITATION TO BOULE).
+Finally, we convert the observations to planar Cartesian coordinates by
+applying a Mercator projection.
+
+We start the interpolation process by defining a set of block-averaged sources
+at a relative depth of \AustraliaEqlDepth{} and a block size of
+\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
+sources.
+The block size was chosen to match the desired
+resolution of the final grid.
+In this case we will generate a regular grid with a resolution of 1~arc-minute,
+which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
+
+The coefficients of the gradient-boosted equivalent sources are estimated using
+a damping equal to \AustraliaEqlDamping{} and a window size of
+\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
+store the largest Jacobian matrix to 10GB.
+
+Finally, the equivalent sources are used to predict the values of the gravity
+disturbance on a regular grid of
+\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
+\AustraliaEqlGridHeight{} above the ellipsoid
+(Fig.~\ref{fig:australia}).
+
+FOR DISCUSSION:
+
+If the grid will have a much higher resolution than the block spacing, the
+equivalent sources will not be able to reproduce the high frequency components
+of the data.
+Therefore we recommend setting a block spacing that matches the resolution of
+the final grid.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 without which this work would not have been possible.
+
 The synthetic airborne survey was based upon the Great Britain aeromagnetic
 data, reproduced with the permission of the British Geological Survey
-\textcopyright{} UKRI.
+$\textcopyright$UKRI\@.
 All rights reserved.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{humannat}
-\bibliography{references}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliographystyle{humannat}
+\bibliography{references}
+
 \end{document}

### 2021-01-26 manuscript/manuscript.tex
Use percentages in the manuscript as well

--- 2021-01-26 manuscript/manuscript.tex
@@
 The error decreases asymptotically to within $\sim 40\%$ of the regular
-equivalent sources for windows with an area greater than $\sim 35\%$ of the
+equivalent sources for windows with an area greater than $\sim 10\%$ of the
 survey area.
@@
 gradient-boosting being generally faster than the regular equivalent sources
-for windows with an area greater than $\sim 20\%$ of the survey area.
+for windows with an area greater than $\sim 5\%$ of the survey area.
 As the window size increases, both RMS error and computation time appear to
@@
         with a relative depth).
-        Window sizes are given as a fraction of the survey area (e.g., 1
+        Window sizes are given as a percentage of the survey area (e.g., 100
         represents a window with the same area as the survey) and window
-        overlap is given as a fraction of the window size (e.g., 0.5 equals
-        50\% overlap).
+        overlap is given as a percentage of the window size.
         Computation time refers to the time required to estimate the source

### 2021-01-26 notebooks/99-figures.py

@@ -432,6 +432,7 @@ boosted = ax1.errorbar(
 nonboosted = ax1.axhline(eql_rms, linestyle="--", color="C1")
 ax1.set_ylabel("Interpolation RMS error [mGal]")
 ax1.set_ylim(0.2, 1.3)
+ax1.set_xticks(np.arange(0, 45, 5))
 
 ax2.errorbar(
     boost_window_size.window_size_ratio ** 2 * 100,

### 2021-01-26 manuscript/manuscript.tex

@@
 with recent modifications by \citet{fukushima2020},
-as implemented in the open-source software Harmonica \citep{harmonica}.
+as implemented in the open-source software Harmonica \citep{harmonica2020}.
 We generated a \emph{target grid} of
@@
 
+\section{Software implementation}
+
+We have implemented the methods described in the previous sections though
+a software written in Python language.
+The code for generating the results of this work are available in
+\url{https://doi.org/10.6084/m9.figshare.13604360} or
+\url{https//github.com/compgeolab/eql-gradient-boosted}.
+The gradient-boosted equivalent sources implementation is based on the
+non-boosted sources available through the Harmonica library
+\citep{harmonica2020}, part of the Fatiando a Terra project
+\citep{fatiando2013}.
+Another Python libraries were used:
+Verde \citep{verde2018} to apply block reductions and managing coordinates,
+Boule \citep{boule2020} for computing normal gravity,
+Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
+multidimensional datasets and numerical
+computations,
+Numba \citep{numba2015} for writing pre-comipled implementations and
+parallelization,
+Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
+the figures.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusions}

### 2021-01-26 manuscript/manuscript.tex
Apply suggestions from code review
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
         with a relative depth).
-        Window sizes are given as a percentage of the survey area (e.g., 100
+        Window sizes are given as a percentage of the survey area (e.g., 100\%
         represents a window with the same area as the survey) and window
-        overlap is given as a percentage of the window size.
+        overlap is given as a percentage of the window size 
+        (an overlap of 50\% means that two adjacent windows
+        share an area half of the size of the entire window).
         Computation time refers to the time required to estimate the source

### 2021-01-26 manuscript/manuscript.tex
Finish text for the Australia application

--- 2021-01-26 manuscript/manuscript.tex
@@
 
-We investigated the effect of different strategies for distributing the
-equivalent sources horizontally and vertically on interpolation accuracy.
-To do this, we used the damped least-squares solution described in
-Section~\ref{sec:eql_inversion} (without gradient boosting) to interpolate the
-synthetic datasets (Fig.~\ref{fig:synthetic-layouts}) and compared the results
-against the target grid (Fig.~\ref{fig:synthetic-target}).
-This process was repeated for each combination of horizontal layout
-(sources-below-data and block-averaged-sources) and depth type (constant,
-relative, and variable) and for regular-grid sources with a constant depth,
-totalling 7 different combinations.
-
-Each source distribution strategy requires certain hyper-parameters to be
-chosen in order to build the set of point sources.
-For example, using a constant depth needs the definition of the depth and using
-block-average-sources requires the definition of the block size.
-The predictive capabilities of the equivalent sources depend on the choice of
-these hyper-parameters.
-To ensure that our comparisons are fair, we perform an exhaustive search over
-combinations of hyper-parameter values (including the damping parameter from
-Eq.~\ref{eq:misfit}) to obtain the best prediction that can be achieved by each
-source distribution strategy.
-Here, the best prediction is defined as the one that minimizes the root
-mean-square error (RMS) between interpolated values and the target grid
-(Fig.~\ref{fig:synthetic-target}).
-The parameter values used in these searches and the one producing the smallest
-RMS error are outlined in Tables~\ref{tab:parameters-ground-survey}
-and~\ref{tab:parameters-airborne-survey}.
-
-Figures~\ref{fig:ground-survey-differences}
-and~\ref{fig:airborne-survey-differences} show the differences between the
-target grid and the best prediction achieved by each source distribution
-strategy for the ground and airborne synthetic surveys, respectively.
-For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of approximately \SI{0.8}{\mgal} regardless of the depth type, with the
-exception of the regular-grid layout which produced a larger RMS of
-\SI{\BestGroundGridSourcesConstantDepthRms{}}{\mgal}.
-The differences between the target grid and the interpolated values are larger
-in regions of poor data coverage.
-Edge effects are present for all strategies but are noticeably smaller for the
-combination of block-averaged-sources with a variable depth based on the
-nearest neighbour distance.
-For the synthetic airborne survey, all strategies (including the regular-grid)
-produced similar RMS errors of approximately \SI{0.3}{\mgal}.
-The maps of the differences between the target grid and interpolation results
-are visually indistinguishable from each other.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Window size and overlap in gradient boosting}
-
-We assessed the trade-offs in interpolation accuracy and computation time of
-the gradient-boosted equivalent sources algorithm as a function of the two key
-controlling factors: the window size and the amount of overlap between adjacent
-windows.
-The comparisons were performed against a regular least-squares solution
-(Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
-(Fig.~\ref{fig:synthetic-layouts}c-d) .
-To avoid biasing the results, we used the same locations of equivalent sources
-for both the regular and gradient-boosted interpolations, namely
-block-averaged-sources with a block size of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
-relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.
-
-\subsubsection{Window size}
-\label{sec:window_size}
-
-The size of the windows controls the size of the Jacobian matrices
-$\tilde{\mathbf{A}}_k$ by limiting the number of data points and equivalent
-sources used in each step of the gradient-boosting algorithm
-(Alg.~\ref{alg:gradient_boosting_window}).
-Thus, using smaller windows will reduce the total amount of computer memory
-required to estimate the source coefficients.
-Nevertheless, smaller windows may produce less accurate interpolations by
-failing to achieve the global minimum of the goal function in
-Eq.~\ref{eq:misfit}.
-The window size might also impact the computation time in non-intuitive ways
-since smaller windows generate smaller least-squares problems but also require
-more gradient-boosting iterations.
-
-We calculated the interpolation RMS error and computation time for a fixed
-window overlap of 50\% and several window sizes.
-To avoid any biases introduced by the shuffling of windows, the calculations
-were repeated using different seeds for the pseudo-random number generator used
-in the shuffling.
-Figs.~\ref{fig:gradient-boosted-comparison}a and
-\ref{fig:gradient-boosted-comparison}c show the RMS error and computation time
-required for estimating the source coefficients, respectively, as a function of
-the window size.
-
-The results show that the interpolation RMS error for gradient-boosting is
-generally larger than the error for regular equivalent sources.
-The error decreases asymptotically to within $\sim 40\%$ of the regular
-equivalent sources for windows with an area greater than $\sim 10\%$ of the
-survey area.
-The computation time similarly decreases with window size, with the
-gradient-boosting being generally faster than the regular equivalent sources
-for windows with an area greater than $\sim 5\%$ of the survey area.
-As the window size increases, both RMS error and computation time appear to
-stabilize to nearly constant levels.
-
-\subsubsection{Window overlap}
-
-The amount of overlap between adjacent windows plays an important role in the
-performance of the gradient-boosted equivalent sources.
-It controls the number of iterations and how often a particular source is used
-in the least-squares fitting process.
-While the experiments in the previous section showed that 50\% overlap was
-sufficient to achieve acceptable interpolation accuracy, we separately studied
-the impacts of the amount of window overlap on both accuracy and computation
-time.
-
-We performed a similar experiment to one in section~\ref{sec:window_size} but
-this time kept the window size fixed to \BoostOverlappingWindowSize{} and
-varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
-All other experimental procedures remained unchanged.
-Figs.~\ref{fig:gradient-boosted-comparison}b and
-\ref{fig:gradient-boosted-comparison}d show the RMS error and computation time
-required for estimating the source coefficients, respectively, as a function of
-the window overlap.
-
-Our results show what the interpolation RMS error decreases with the amount of
-overlap, reaching the same accuracy as the regular equivalent sources at
-approximately 90\% overlap.
-On the other hand, the computation time increases with the amount of overlap,
-becoming larger than that of the regular equivalent sources for overlaps
-greater than 70\%.
-This is expected since increasing the overlap adds iterations to the gradient
-boosting algorithm without decreasing the individual least-squares problem
-sizes to compensate.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
-    \caption{
-        Comparison of the interpolation RMS error and computation time for
-        regular least-squares equivalent sources (orange dashed lines) and
-        gradient-boosted equivalent sources (blue dots and error bars).
-        Both methods used the same source positions (block-averaged sources
-        with a relative depth).
-        Window sizes are given as a percentage of the survey area (e.g., 100
-        represents a window with the same area as the survey) and window
-        overlap is given as a percentage of the window size.
-        Computation time refers to the time required to estimate the source
-        coefficients and is reported as a ratio between the gradient-boosted
-        and the regular equivalent sources.
-        For gradient-boosting, the RMS errors and computation times are the
-        means (error bars represent 1 standard deviation) of results using
-        different seeds for the pseudo-random number generator.
-        (a)~RMS error between the target grid and interpolation results and
-        (b)~computation time as a function of window size.
-        (c)~RMS error between the target grid and interpolation results and
-        (d)~computation time as a function of window overlap.
-}
-    \label{fig:gradient-boosted-comparison}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Gridding Australia gravity data}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia.png}
-    \caption{
-      Pseudo-color maps of observed (left) and
-      interpolated (right) gravity disturbance of Australia.
-      Observations are part of a compilation by \citet{wynne2018} of
-      over 1.7 million ground gravity measurements.
-      Interpolated values were obtained through gradient-boosted equivalent
-      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
-      over the WGS84 ellipsoid.
-    }
-    \label{fig:australia}
-\end{figure*}
-
-Our final goal is to show how gradient-boosted equivalent sources can be used
-to interpolate a very large dataset of gravity data into a regular grid.
-We selected a compilation of gravity surveys over Australia made by
-\citet{wynne2018}.
-It consists in more than 1.7 million data points that cover most part of the
-Australia territory obtained through observations on ground.
-First we compute the gravity disturbance by removing the normal gravity from
-the observed gravity data (Fig.~\ref{fig:australia}).
-The normal gravity is computed on each observation point through the
-closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
-as reference.
-Then we obtain planar coordinates of the observation points by applying
-a Mercator projection.
-
-We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block spacing of
-\SI{1.8}{\kilo\meter}.
-These parameters create \AustraliaEqlNSources{}~point sources.
-The choice of the block spacing must be done taking into account the desired
-resolution of the final grid.
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
-In this case we will generate a regular grid with a resolution of 1~arc-minute,
-which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
-
-The coefficients of the gradient-boosted equivalent sources are estimated using
-a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
-store the largest Jacobian matrix to 10GB.
-
-Finally, the equivalent sources are used to predict the values of the gravity
-disturbance on a regular grid of
-\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid
-(Fig.~\ref{fig:australia}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-
-\subsection{Location of sources}
+\subsection{Discussion}
 
@@
 
-Overlap:
+\subsection{Amount of overlap}
+
+Another factor that plays an important role on the performance of the gradient
+boosted equivalent sources is the amount of overlap between adjacent windows.
+The previous choice of 50\% showed to be sufficiently good to achieve
+acceptable accuracy, although a deeper study should be carried out to assess
+how the amount of overlap impacts both accuracy and fitting time.
+
+We interpolated the synthetic airborne survey using the gradient boosted
+equivalent sources on the same points of the target grid.
+The interpolations were carried out using different amount of overlap, from
+0\% to 0.95\% with a step size of 0.05\%.
+For each overlap we gridded the synthetic data using block-averaged sources
+with a spacing of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
+a relative depth of
+\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
+a window size of \BoostOverlappingWindowSize, and with different
+values of damping.
+Then we compared the resulting interpolations with the target grid in order to
+get the best prediction for each overlap and the damping value used to
+obtain it.
+
+Using the best set of parameters for each overlap, we registered the achieved
+RMS against the values of the target grid and the time needed to fit the
+sources coefficients.
+The RMS was obtained as the mean RMS achieved by using different random seeds
+as we did on~\ref{sec:window_size}.
+
+We have also computed the fitting time ratio for each overlap, in a similar way
+we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
+    \caption{
+        Gradient-boosted equivalent sources performance against amount of
+        overlap.
+        (a)~Root-mean-squared error between predictions and target grid using
+        non-boosted sources (orange dashed line) and gradient-boosted
+        equivalent sources (blue dots) for different amount of overlap. Each
+        RMS error is the mean of the RMS produced by the same set of parameters
+        but with different random seeds.
+        (b)~Ratio between the computational times needed to fit the
+        gradient-boosted and the non-boosted equivalent sources, respectively
+        (the fitting time ratio for the non-boosted equivalent sources is
+        therefore equal to one).
+    }
+    \label{fig:gradient-boosted-overlap}
+\end{figure}
+
+From the results obtained we can conclude that a lower values of overlap
+generates less accurate results, while a higher overlap increases the
+computational time required for fitting the source coefficients due to the
+significant increment of the number of overlapping windows.
+
+We found that overlaps less than 40\% produce very inaccurate predictions in
+comparison with the non-boosted equivalent sources, while values larger that
+80\% produce predictions with almost the same level of accuracy as the latter.
+Nevertheless, overlap values larger that 70\% takes significantly more
+computational time to fit the source coefficients.
+
+THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?
 
@@
 
+\section{Gridding gravity data from Australia}
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia.png}
+    \caption{
+      Pseudo-color maps of observed (left) and
+      interpolated (right) gravity disturbance of Australia.
+      Observations are part of a compilation by \citet{wynne2018} of
+      over 1.7 million ground gravity measurements.
+      Interpolated values were obtained through gradient-boosted equivalent
+      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
+      over the WGS84 ellipsoid.
+    }
+    \label{fig:australia}
+\end{figure*}
+
+This section will demonstrate how gradient-boosted equivalent sources can be
+used to interpolate large datasets of gravity data onto a regular grid at
+uniform height.
+For this purpose, we selected a compilation of ground gravity surveys over
+Australia made by \citet{wynne2018} (TODO: MENTION THE COMPGEOLAB VERSION?).
+It contains over 1.7 million data points and covers most of the Australian
+territory at variable point spacings.
+Our goal is to create a 1 arc-minute resolution grid of gravity disturbances at
+a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
+observations).
+
+We computed the gravity disturbance by removing the normal gravity of
+the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
+Here, normal gravity was computed at each observation point through the
+closed-form formula of \citet{ligotze2001} (TODO: ADD CITATION TO BOULE).
+Finally, we convert the observations to planar Cartesian coordinates by
+applying a Mercator projection.
+
+We start the interpolation process by defining a set of block-averaged sources
+at a relative depth of \AustraliaEqlDepth{} and a block size of
+\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
+sources.
+The block size was chosen to match the desired resolution of the final grid (1
+arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
+The coefficients of the gradient-boosted equivalent sources are estimated using
+a damping equal to \AustraliaEqlDamping{} and a window size of
+\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
+computer memory needed to store the Jacobian matrix to under 10 Gigabytes.
+Finally, we used estimated source coefficients to predict the values of the
+gravity disturbance on a regular grid of
+\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
+\AustraliaEqlGridHeight{} above the ellipsoid.
+Fig.~\ref{fig:australia} shows the original data distribution and the
+interpolated regular grid.
+Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
+point are masked to avoid unrealistic extrapolations.
+
+The resulting grid preserves the high resolution of the original data while
+avoiding aliasing artifacts because to the block averaging.
+Some parts of the grid are smoother and with reduced amplitude (e.g., some
+southwestern parts), which is expected from the upward continuation that was
+performed to have the grid at a constant height.
+On a modest workstation with 16 cores and 16 Gigabytes of RAM,
+estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
+$\sim 1.3$ hours and the forward modelling step took $\sim 18$ minutes.
+
+FOR DISCUSSION:
+
+If the grid will have a much higher resolution than the block spacing, the
+equivalent sources will not be able to reproduce the high frequency components
+of the data.
+Therefore we recommend setting a block spacing that matches the resolution of
+the final grid.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusions}

### 2021-01-26 manuscript/manuscript.tex

--- 2021-01-26 manuscript/manuscript.tex
@@
 
-\section{Gridding Australia gravity data}
+\section{Gridding gravity data from Australia}
 
@@
 
-Our final goal is to show how gradient-boosted equivalent sources can be used
-to interpolate a very large dataset of gravity data into a regular grid.
-We selected a compilation of gravity surveys over Australia made by
-\citet{wynne2018}.
-It consists in more than 1.7 million data points that cover most part of the
-Australia territory obtained through observations on ground.
-First we compute the gravity disturbance by removing the normal gravity from
-the observed gravity data (Fig.~\ref{fig:australia}).
-The normal gravity is computed on each observation point through the
-closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
-as reference.
-Then we obtain planar coordinates of the observation points by applying
-a Mercator projection.
+This section will demonstrate how gradient-boosted equivalent sources can be
+used to interpolate large datasets of gravity data onto a regular grid at
+uniform height.
+For this purpose, we selected a compilation of ground gravity surveys over
+Australia made by \citet{wynne2018} (TODO: MENTION THE COMPGEOLAB VERSION?).
+It contains over 1.7 million data points and covers most of the Australian
+territory at variable point spacings.
+Our goal is to create a 1 arc-minute resolution grid of gravity disturbances at
+a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
+observations).
+
+We computed the gravity disturbance by removing the normal gravity of
+the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
+Here, normal gravity was computed at each observation point through the
+closed-form formula of \citet{ligotze2001} (TODO: ADD CITATION TO BOULE).
+Finally, we convert the observations to planar Cartesian coordinates by
+applying a Mercator projection.
 
 We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block spacing of
-\SI{1.8}{\kilo\meter}.
-These parameters create \AustraliaEqlNSources{}~point sources.
-The choice of the block spacing must be done taking into account the desired
-resolution of the final grid.
+at a relative depth of \AustraliaEqlDepth{} and a block size of
+\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
+sources.
+The block size was chosen to match the desired resolution of the final grid (1
+arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
+The coefficients of the gradient-boosted equivalent sources are estimated using
+a damping equal to \AustraliaEqlDamping{} and a window size of
+\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
+computer memory needed to store the Jacobian matrix to under 10 Gigabytes.
+Finally, we used estimated source coefficients to predict the values of the
+gravity disturbance on a regular grid of
+\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
+\AustraliaEqlGridHeight{} above the ellipsoid.
+Fig.~\ref{fig:australia} shows the original data distribution and the
+interpolated regular grid.
+Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
+point are masked to avoid unrealistic extrapolations.
+
+The resulting grid preserves the high resolution of the original data while
+avoiding aliasing artifacts because to the block averaging.
+Some parts of the grid are smoother and with reduced amplitude (e.g., some
+southwestern parts), which is expected from the upward continuation that was
+performed to have the grid at a constant height.
+On a modest workstation with 16 cores and 16 Gigabytes of RAM,
+estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
+$\sim 1.3$ hours and the forward modelling step took $\sim 18$ minutes.
+
+FOR DISCUSSION:
+
 If the grid will have a much higher resolution than the block spacing, the
@@
 the final grid.
-In this case we will generate a regular grid with a resolution of 1~arc-minute,
-which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
-
-The coefficients of the gradient-boosted equivalent sources are estimated using
-a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
-store the largest Jacobian matrix to 10GB.
-
-Finally, the equivalent sources are used to predict the values of the gravity
-disturbance on a regular grid of
-\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid
-(Fig.~\ref{fig:australia}).
 

### 2021-01-26 manuscript/manuscript.tex
Improvements to conclusions

--- 2021-01-26 manuscript/manuscript.tex
@@
 
-\section{Gridding gravity data from Australia}
+\section{Gridding Australia gravity data}
 
@@
 
-This section will demonstrate how gradient-boosted equivalent sources can be
-used to interpolate large datasets of gravity data onto a regular grid at
-uniform height.
-For this purpose, we selected a compilation of ground gravity surveys over
-Australia made by \citet{wynne2018} (TODO: MENTION THE COMPGEOLAB VERSION?).
-It contains over 1.7 million data points and covers most of the Australian
-territory at variable point spacings.
-Our goal is to create a 1 arc-minute resolution grid of gravity disturbances at
-a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
-observations).
-
-We computed the gravity disturbance by removing the normal gravity of
-the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
-Here, normal gravity was computed at each observation point through the
-closed-form formula of \citet{ligotze2001} (TODO: ADD CITATION TO BOULE).
-Finally, we convert the observations to planar Cartesian coordinates by
-applying a Mercator projection.
+Our final goal is to show how gradient-boosted equivalent sources can be used
+to interpolate a very large dataset of gravity data into a regular grid.
+We selected a compilation of gravity surveys over Australia made by
+\citet{wynne2018}.
+It consists in more than 1.7 million data points that cover most part of the
+Australia territory obtained through observations on ground.
+First we compute the gravity disturbance by removing the normal gravity from
+the observed gravity data (Fig.~\ref{fig:australia}).
+The normal gravity is computed on each observation point through the
+closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
+as reference.
+Then we obtain planar coordinates of the observation points by applying
+a Mercator projection.
 
 We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block size of
-\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
-sources.
-The block size was chosen to match the desired resolution of the final grid (1
-arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
-The coefficients of the gradient-boosted equivalent sources are estimated using
-a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
-computer memory needed to store the Jacobian matrix to under 10 Gigabytes.
-Finally, we used estimated source coefficients to predict the values of the
-gravity disturbance on a regular grid of
-\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid.
-Fig.~\ref{fig:australia} shows the original data distribution and the
-interpolated regular grid.
-Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
-point are masked to avoid unrealistic extrapolations.
-
-The resulting grid preserves the high resolution of the original data while
-avoiding aliasing artifacts because to the block averaging.
-Some parts of the grid are smoother and with reduced amplitude (e.g., some
-southwestern parts), which is expected from the upward continuation that was
-performed to have the grid at a constant height.
-On a modest workstation with 16 cores and 16 Gigabytes of RAM,
-estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
-$\sim 1.3$ hours and the forward modelling step took $\sim 18$ minutes.
-
-FOR DISCUSSION:
-
+at a relative depth of \AustraliaEqlDepth{} and a block spacing of
+\SI{1.8}{\kilo\meter}.
+These parameters create \AustraliaEqlNSources{}~point sources.
+The choice of the block spacing must be done taking into account the desired
+resolution of the final grid.
 If the grid will have a much higher resolution than the block spacing, the
@@
 the final grid.
+In this case we will generate a regular grid with a resolution of 1~arc-minute,
+which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
+
+The coefficients of the gradient-boosted equivalent sources are estimated using
+a damping equal to \AustraliaEqlDamping{} and a window size of
+\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
+store the largest Jacobian matrix to 10GB.
+
+Finally, the equivalent sources are used to predict the values of the gravity
+disturbance on a regular grid of
+\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
+\AustraliaEqlGridHeight{} above the ellipsoid
+(Fig.~\ref{fig:australia}).
 
@@
 \section{Conclusions}
+
+The equivalent source technique has been proven to be a well suited method for
+interpolating any harmonic data such as gravity disturbances and magnetic
+anomalies.
+The two main reasons that make it to stand out over all-purpose 2D
+interpolation methods is the fact that the equivalent sources take into account
+the height of the observations and they always produce harmonic predictions.
+The main inconvenience of using equivalent sources is the computational
+requirements needed to estimate the coefficients of the equivalent sources,
+specially on the computer memory needed to store the Jacobian matrix.
+This forbids the application of the equivalent source technique to very
+large datasets where the computer memory needed to store the whole Jacobian
+matrix greatly exceeds the specifications of modest personal computers now days.
+
+In this work we present two strategies that could be simultaneously applied in
+order to interpolate very large datasets in reasonable times without the need
+to store large matrices into memory:
+the block-averaged sources, which reduce the number of
+equivalent sources needed for the interpolation;
+and the gradient-boosted equivalent sources that simplify the
+problem of estimating the source coefficients into smaller problems
+through sets of equivalent sources defined by overlapping windows.
+
+Both methods were exhaustively tested against a synthetic model and synthetic
+surveys in order to compare accurate they are in comparison to the existing
+techniques and how they perform in terms of computational resources.
+Block-averaged sources were compared to the interpolations obtained with two
+traditional strategies for locating the sources:
+the \emph{source below data} and the \emph{regular grid} of sources.
+The performance of the gradient-boosted equivalent sources was compared against
+the regular non-boosted equivalent sources, along with tests for assessing how
+the choice of the window size and the amount of overlap between adjacent
+windows affect both the accuracy of the interpolations and the computational
+load.
+
+Our results showed that the block-averaged sources reduce the computational
+load needed to estimate their coefficients in comparison to the two traditional
+strategies mentioned before.
+They also showed that this reduction of the number of sources doesn't affect
+the accuracy of the predictions, making block-averaged sources a better
+alternative to the traditional methods.
+Besides, block-averaged sources might also prevent aliasing on the interpolated
+values, specially when the observation points show high anisotropy, i.e. they
+were taken along paths with a high sample frequency.
+From our experimentation with this new strategy we noticed that special
+attention must be payed when choosing the size of the block spacing:
+as a thumb rule, it must be approximately equal to the resolution of the
+regular grid where the values will be interpolated.
+
+We have also carried out similar tests to compare the vertical location of the
+sources.
+Our results showed that any one of the three strategies taken into account
+(\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
+doesn't significantly affects the accuracy of the interpolations.
+Nevertheless, we are more prone to choose either the \emph{constant depth} or
+the \emph{relative depth} for any application because they involve less
+hyper-parameters that would be needed to estimated before the actual
+interpolation.
+
+Regarding the gradient-boosted equivalent sources, our results show that they
+heavily reduce the computer memory needed to estimate source coefficients,
+making possible to interpolate even very large datasets.
+The interpolations obtained though this new method achieve almost the same
+accuracy than the non-boosted sources, while reducing the computation time
+needed to estimate the source coefficients.
+Because it doesn't involve any assumption on the location of the sources, it
+can be used in conjunction with any horizontal source layout and any strategy
+for setting their depth.
+This allows to use both the block-averaged sources and the gradient-boosted
+equivalent sources simultaneously.
+Our results allowed us to develop a rule of thumb in order to maximize the
+accuracy of the interpolations: the size of the overlapping windows must be
+chosen as the maximum value that creates Jacobian matrices that fit into our
+computer memory.
+Therefore its choice is subject to the particular infrastructure where the
+interpolation will be carried out.
+We also show that an overlap of 50\% between adjacent windows achieves a good
+compromise between accuracy and computation time needed to fit the source
+coefficients.
+
+Finally, both proposed methods were used to interpolate a compilation of more
+than 1.7 million gravity points from Australia on a regular grid with
+a resolution of 1~arc-minute.
+The whole process was carried out on a modest personal computer, requiring
+a maximum of 10GB of memory.
+This shows how the new gradient-boosted equivalent sources can be applied to
+real-world data.
 

### 2021-01-26 manuscript/manuscript.tex
Cite Boule in the australia section
Move texts marked for discussions to discussion

--- 2021-01-26 manuscript/manuscript.tex
@@
 
-\textbf{NOTE: This paragraph might be better in the Discussion section.}
-
-Our gradient boosting algorithm for overlapping windows is similar to the
-``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
-fits portions of an equivalent source model to the data residuals.
-The key differences are:
-(1) the sources in the overlapping portions of the windows are fit more than
-once, allowing the algorithm to self-correct for poor solutions to any given
-window;
-(2) using only data points within the window when fitting the data enables the
-use of larger datasets;
-(3) experience shows that the step size parameter improves the convergence of
-the solution, particularly when using only the data inside the windows for
-fitting.
-
 \subsection{Location of sources}
@@
 Here, normal gravity was computed at each observation point through the
-closed-form formula of \citet{ligotze2001} (TODO: ADD CITATION TO BOULE).
+closed-form formula of \citet{ligotze2001} using the Boule software
+\citep{boule2020}.
 Finally, we convert the observations to planar Cartesian coordinates by
@@
 
-FOR DISCUSSION:
-
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Discussion}
+
+Our gradient boosting algorithm for overlapping windows is similar to the
+``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
+fits portions of an equivalent source model to the data residuals.
+The key differences are:
+(1) the sources in the overlapping portions of the windows are fit more than
+once, allowing the algorithm to self-correct for poor solutions to any given
+window;
+(2) using only data points within the window when fitting the data enables the
+use of larger datasets;
+(3) experience shows that the step size parameter improves the convergence of
+the solution, particularly when using only the data inside the windows for
+fitting.
 
@@
 accurate predictions in reasonable times.
+
+If the grid will have a much higher resolution than the block spacing, the
+equivalent sources will not be able to reproduce the high frequency components
+of the data.
+Therefore we recommend setting a block spacing that matches the resolution of
+the final grid.
 

### 2021-01-26 manuscript/manuscript.tex
Cite the compgeolab australia compilation

@@
 uniform height.
-For this purpose, we selected a compilation of ground gravity surveys over
-Australia made by \citet{wynne2018} (TODO: MENTION THE COMPGEOLAB VERSION?).
+For this purpose, we selected an open-access compilation of ground gravity
+surveys over Australia made by \citet{wynne2018} and filtered and referenced to
+the WGS84 ellipsoid by \citet{australia_compilation}.
 It contains over 1.7 million data points and covers most of the Australian

### 2021-01-26 manuscript/manuscript.tex

--- 2021-01-26 manuscript/manuscript.tex
@@
 
+\textbf{NOTE: This paragraph might be better in the Discussion section.}
+
+Our gradient boosting algorithm for overlapping windows is similar to the
+``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
+fits portions of an equivalent source model to the data residuals.
+The key differences are:
+(1) the sources in the overlapping portions of the windows are fit more than
+once, allowing the algorithm to self-correct for poor solutions to any given
+window;
+(2) using only data points within the window when fitting the data enables the
+use of larger datasets;
+(3) experience shows that the step size parameter improves the convergence of
+the solution, particularly when using only the data inside the windows for
+fitting.
+
 \subsection{Location of sources}
@@
 
-This section will demonstrate how gradient-boosted equivalent sources can be
-used to interpolate large datasets of gravity data onto a regular grid at
-uniform height.
-For this purpose, we selected a compilation of ground gravity surveys over
-Australia made by \citet{wynne2018} (TODO: MENTION THE COMPGEOLAB VERSION?).
-It contains over 1.7 million data points and covers most of the Australian
-territory at variable point spacings.
-Our goal is to create a 1 arc-minute resolution grid of gravity disturbances at
-a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
-observations).
-
-We computed the gravity disturbance by removing the normal gravity of
-the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
-Here, normal gravity was computed at each observation point through the
-closed-form formula of \citet{ligotze2001} using the Boule software
-\citep{boule2020}.
-Finally, we convert the observations to planar Cartesian coordinates by
-applying a Mercator projection.
+Our final goal is to show how gradient-boosted equivalent sources can be used
+to interpolate a very large dataset of gravity data into a regular grid.
+We selected a compilation of gravity surveys over Australia made by
+\citet{wynne2018}.
+It consists in more than 1.7 million data points that cover most part of the
+Australia territory obtained through observations on ground.
+First we compute the gravity disturbance by removing the normal gravity from
+the observed gravity data (Fig.~\ref{fig:australia}).
+The normal gravity is computed on each observation point through the
+closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
+as reference.
+Then we obtain planar coordinates of the observation points by applying
+a Mercator projection.
 
 We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block size of
-\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
-sources.
-The block size was chosen to match the desired resolution of the final grid (1
-arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
+at a relative depth of \AustraliaEqlDepth{} and a block spacing of
+\SI{1.8}{\kilo\meter}.
+These parameters create \AustraliaEqlNSources{}~point sources.
+The choice of the block spacing must be done taking into account the desired
+resolution of the final grid.
+If the grid will have a much higher resolution than the block spacing, the
+equivalent sources will not be able to reproduce the high frequency components
+of the data.
+Therefore we recommend setting a block spacing that matches the resolution of
+the final grid.
+In this case we will generate a regular grid with a resolution of 1~arc-minute,
+which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
+
 The coefficients of the gradient-boosted equivalent sources are estimated using
 a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
-computer memory needed to store the Jacobian matrix to under 10 Gigabytes.
-Finally, we used estimated source coefficients to predict the values of the
-gravity disturbance on a regular grid of
+\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
+store the largest Jacobian matrix to 10GB.
+
+Finally, the equivalent sources are used to predict the values of the gravity
+disturbance on a regular grid of
 \AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid.
-Fig.~\ref{fig:australia} shows the original data distribution and the
-interpolated regular grid.
-Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
-point are masked to avoid unrealistic extrapolations.
-
-The resulting grid preserves the high resolution of the original data while
-avoiding aliasing artifacts because to the block averaging.
-Some parts of the grid are smoother and with reduced amplitude (e.g., some
-southwestern parts), which is expected from the upward continuation that was
-performed to have the grid at a constant height.
-On a modest workstation with 16 cores and 16 Gigabytes of RAM,
-estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
-$\sim 1.3$ hours and the forward modelling step took $\sim 18$ minutes.
+\AustraliaEqlGridHeight{} above the ellipsoid
+(Fig.~\ref{fig:australia}).
 
@@
 \section{Discussion}
-
-Our gradient boosting algorithm for overlapping windows is similar to the
-``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
-fits portions of an equivalent source model to the data residuals.
-The key differences are:
-(1) the sources in the overlapping portions of the windows are fit more than
-once, allowing the algorithm to self-correct for poor solutions to any given
-window;
-(2) using only data points within the window when fitting the data enables the
-use of larger datasets;
-(3) experience shows that the step size parameter improves the convergence of
-the solution, particularly when using only the data inside the windows for
-fitting.
 
@@
 accurate predictions in reasonable times.
-
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
 
@@
 
+The equivalent source technique has been proven to be a well suited method for
+interpolating any harmonic data such as gravity disturbances and magnetic
+anomalies.
+The two main reasons that make it to stand out over all-purpose 2D
+interpolation methods is the fact that the equivalent sources take into account
+the height of the observations and they always produce harmonic predictions.
+The main inconvenience of using equivalent sources is the computational
+requirements needed to estimate the coefficients of the equivalent sources,
+specially on the computer memory needed to store the Jacobian matrix.
+This forbids the application of the equivalent source technique to very
+large datasets where the computer memory needed to store the whole Jacobian
+matrix greatly exceeds the specifications of modest personal computers now days.
+
+In this work we present two strategies that could be simultaneously applied in
+order to interpolate very large datasets in reasonable times without the need
+to store large matrices into memory:
+the block-averaged sources, which reduce the number of
+equivalent sources needed for the interpolation;
+and the gradient-boosted equivalent sources that simplify the
+problem of estimating the source coefficients into smaller problems
+through sets of equivalent sources defined by overlapping windows.
+
+Both methods were exhaustively tested against a synthetic model and synthetic
+surveys in order to compare accurate they are in comparison to the existing
+techniques and how they perform in terms of computational resources.
+Block-averaged sources were compared to the interpolations obtained with two
+traditional strategies for locating the sources:
+the \emph{source below data} and the \emph{regular grid} of sources.
+The performance of the gradient-boosted equivalent sources was compared against
+the regular non-boosted equivalent sources, along with tests for assessing how
+the choice of the window size and the amount of overlap between adjacent
+windows affect both the accuracy of the interpolations and the computational
+load.
+
+Our results showed that the block-averaged sources reduce the computational
+load needed to estimate their coefficients in comparison to the two traditional
+strategies mentioned before.
+They also showed that this reduction of the number of sources doesn't affect
+the accuracy of the predictions, making block-averaged sources a better
+alternative to the traditional methods.
+Besides, block-averaged sources might also prevent aliasing on the interpolated
+values, specially when the observation points show high anisotropy, i.e. they
+were taken along paths with a high sample frequency.
+From our experimentation with this new strategy we noticed that special
+attention must be payed when choosing the size of the block spacing:
+as a thumb rule, it must be approximately equal to the resolution of the
+regular grid where the values will be interpolated.
+
+We have also carried out similar tests to compare the vertical location of the
+sources.
+Our results showed that any one of the three strategies taken into account
+(\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
+doesn't significantly affects the accuracy of the interpolations.
+Nevertheless, we are more prone to choose either the \emph{constant depth} or
+the \emph{relative depth} for any application because they involve less
+hyper-parameters that would be needed to estimated before the actual
+interpolation.
+
+Regarding the gradient-boosted equivalent sources, our results show that they
+heavily reduce the computer memory needed to estimate source coefficients,
+making possible to interpolate even very large datasets.
+The interpolations obtained though this new method achieve almost the same
+accuracy than the non-boosted sources, while reducing the computation time
+needed to estimate the source coefficients.
+Because it doesn't involve any assumption on the location of the sources, it
+can be used in conjunction with any horizontal source layout and any strategy
+for setting their depth.
+This allows to use both the block-averaged sources and the gradient-boosted
+equivalent sources simultaneously.
+Our results allowed us to develop a rule of thumb in order to maximize the
+accuracy of the interpolations: the size of the overlapping windows must be
+chosen as the maximum value that creates Jacobian matrices that fit into our
+computer memory.
+Therefore its choice is subject to the particular infrastructure where the
+interpolation will be carried out.
+We also show that an overlap of 50\% between adjacent windows achieves a good
+compromise between accuracy and computation time needed to fit the source
+coefficients.
+
+Finally, both proposed methods were used to interpolate a compilation of more
+than 1.7 million gravity points from Australia on a regular grid with
+a resolution of 1~arc-minute.
+The whole process was carried out on a modest personal computer, requiring
+a maximum of 10GB of memory.
+This shows how the new gradient-boosted equivalent sources can be applied to
+real-world data.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-26 manuscript/manuscript.tex

@@
 
-Our final goal is to show how gradient-boosted equivalent sources can be used
-to interpolate a very large dataset of gravity data into a regular grid.
-We selected a compilation of gravity surveys over Australia made by
-\citet{wynne2018}.
-It consists in more than 1.7 million data points that cover most part of the
-Australia territory obtained through observations on ground.
-First we compute the gravity disturbance by removing the normal gravity from
-the observed gravity data (Fig.~\ref{fig:australia}).
-The normal gravity is computed on each observation point through the
-closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
-as reference.
-Then we obtain planar coordinates of the observation points by applying
-a Mercator projection.
+This section will demonstrate how gradient-boosted equivalent sources can be
+used to interpolate large datasets of gravity data onto a regular grid at
+uniform height.
+For this purpose, we selected an open-access compilation of ground gravity
+surveys over Australia made by \citet{wynne2018} and filtered and referenced to
+the WGS84 ellipsoid by \citet{australia_compilation}.
+It contains over 1.7 million data points and covers most of the Australian
+territory at variable point spacings.
+Our goal is to create a 1 arc-minute resolution grid of gravity disturbances at
+a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
+observations).
+
+We computed the gravity disturbance by removing the normal gravity of
+the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
+Here, normal gravity was computed at each observation point through the
+closed-form formula of \citet{ligotze2001} using the Boule software
+\citep{boule2020}.
+Finally, we convert the observations to planar Cartesian coordinates by
+applying a Mercator projection.
 
 We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block spacing of
-\SI{1.8}{\kilo\meter}.
-These parameters create \AustraliaEqlNSources{}~point sources.
-The choice of the block spacing must be done taking into account the desired
-resolution of the final grid.
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
-In this case we will generate a regular grid with a resolution of 1~arc-minute,
-which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
-
+at a relative depth of \AustraliaEqlDepth{} and a block size of
+\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
+sources.
+The block size was chosen to match the desired resolution of the final grid (1
+arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
 The coefficients of the gradient-boosted equivalent sources are estimated using
 a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
-store the largest Jacobian matrix to 10GB.
-
-Finally, the equivalent sources are used to predict the values of the gravity
-disturbance on a regular grid of
+\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
+computer memory needed to store the Jacobian matrix to under 10 Gigabytes.
+Finally, we used estimated source coefficients to predict the values of the
+gravity disturbance on a regular grid of
 \AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid
-(Fig.~\ref{fig:australia}).
+\AustraliaEqlGridHeight{} above the ellipsoid.
+Fig.~\ref{fig:australia} shows the original data distribution and the
+interpolated regular grid.
+Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
+point are masked to avoid unrealistic extrapolations.
+
+The resulting grid preserves the high resolution of the original data while
+avoiding aliasing artifacts because to the block averaging.
+Some parts of the grid are smoother and with reduced amplitude (e.g., some
+southwestern parts), which is expected from the upward continuation that was
+performed to have the grid at a constant height.
+On a modest workstation with 16 cores and 16 Gigabytes of RAM,
+estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
+$\sim 1.3$ hours and the forward modelling step took $\sim 18$ minutes.
 

### 2021-01-26 manuscript/manuscript.tex
Apply suggestions from code review
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
 territory at variable point spacings.
-Our goal is to create a 1 arc-minute resolution grid of gravity disturbances at
+Our goal is to create a 1~arc-minute resolution grid of gravity disturbances at
 a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
@@
 \citep{boule2020}.
-Finally, we convert the observations to planar Cartesian coordinates by
+Finally, we converted the observations to planar Cartesian coordinates by
 applying a Mercator projection.
@@
 sources.
-The block size was chosen to match the desired resolution of the final grid (1
-arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
+The block size was chosen to match the desired resolution of the final grid
+ (1~arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
 The coefficients of the gradient-boosted equivalent sources are estimated using
@@
 \AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
-computer memory needed to store the Jacobian matrix to under 10 Gigabytes.
-Finally, we used estimated source coefficients to predict the values of the
+computer memory needed to store the Jacobian matrix to under 10~Gigabytes.
+Finally, we used the estimated source coefficients to predict the values of the
 gravity disturbance on a regular grid of
@@
 estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
-$\sim 1.3$ hours and the forward modelling step took $\sim 18$ minutes.
+$\sim 1.3$~hours and the forward modelling step took $\sim 18$~minutes.
 

### 2021-01-26 manuscript/manuscript.tex
Update manuscript/manuscript.tex
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
 performed to have the grid at a constant height.
-On a modest workstation with 16 cores and 16 Gigabytes of RAM,
+On a modest workstation with 16 cores and 16~Gigabytes of RAM,
 estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took

### 2021-01-26 manuscript/manuscript.tex
Improve the discussion section

--- 2021-01-26 manuscript/manuscript.tex
@@
 
-This section will demonstrate how gradient-boosted equivalent sources can be
-used to interpolate large datasets of gravity data onto a regular grid at
-uniform height.
-For this purpose, we selected an open-access compilation of ground gravity
-surveys over Australia made by \citet{wynne2018} and filtered and referenced to
-the WGS84 ellipsoid by \citet{australia_compilation}.
-It contains over 1.7 million data points and covers most of the Australian
-territory at variable point spacings.
-Our goal is to create a 1 arc-minute resolution grid of gravity disturbances at
-a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
-observations).
-
-We computed the gravity disturbance by removing the normal gravity of
-the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
-Here, normal gravity was computed at each observation point through the
-closed-form formula of \citet{ligotze2001} using the Boule software
-\citep{boule2020}.
-Finally, we convert the observations to planar Cartesian coordinates by
-applying a Mercator projection.
+Our final goal is to show how gradient-boosted equivalent sources can be used
+to interpolate a very large dataset of gravity data into a regular grid.
+We selected a compilation of gravity surveys over Australia made by
+\citet{wynne2018}.
+It consists in more than 1.7 million data points that cover most part of the
+Australia territory obtained through observations on ground.
+First we compute the gravity disturbance by removing the normal gravity from
+the observed gravity data (Fig.~\ref{fig:australia}).
+The normal gravity is computed on each observation point through the
+closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
+as reference.
+Then we obtain planar coordinates of the observation points by applying
+a Mercator projection.
 
 We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block size of
-\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
-sources.
-The block size was chosen to match the desired resolution of the final grid (1
-arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
+at a relative depth of \AustraliaEqlDepth{} and a block spacing of
+\SI{1.8}{\kilo\meter}.
+These parameters create \AustraliaEqlNSources{}~point sources.
+The choice of the block spacing must be done taking into account the desired
+resolution of the final grid.
+If the grid will have a much higher resolution than the block spacing, the
+equivalent sources will not be able to reproduce the high frequency components
+of the data.
+Therefore we recommend setting a block spacing that matches the resolution of
+the final grid.
+In this case we will generate a regular grid with a resolution of 1~arc-minute,
+which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.
+
 The coefficients of the gradient-boosted equivalent sources are estimated using
 a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
-computer memory needed to store the Jacobian matrix to under 10 Gigabytes.
-Finally, we used estimated source coefficients to predict the values of the
-gravity disturbance on a regular grid of
+\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
+store the largest Jacobian matrix to 10GB.
+
+Finally, the equivalent sources are used to predict the values of the gravity
+disturbance on a regular grid of
 \AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid.
-Fig.~\ref{fig:australia} shows the original data distribution and the
-interpolated regular grid.
-Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
-point are masked to avoid unrealistic extrapolations.
-
-The resulting grid preserves the high resolution of the original data while
-avoiding aliasing artifacts because to the block averaging.
-Some parts of the grid are smoother and with reduced amplitude (e.g., some
-southwestern parts), which is expected from the upward continuation that was
-performed to have the grid at a constant height.
-On a modest workstation with 16 cores and 16 Gigabytes of RAM,
-estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
-$\sim 1.3$ hours and the forward modelling step took $\sim 18$ minutes.
+\AustraliaEqlGridHeight{} above the ellipsoid
+(Fig.~\ref{fig:australia}).
 
@@
 
-Window size:
-
-In comparison with the non-boosted equivalent sources, we can see that the
-gradient-boosted ones produce slightly less accurate results due to not being
-able to achieve the global minimum of the least-squares problem, but they
-perform faster.
+From figures~\ref{fig:gradient-boosted-comparison}a
+and~\ref{fig:gradient-boosted-comparison}c we can see that the gradient-boosted
+equivalent sources produce slightly less accurate results by failing to achieve
+the global minimum of the least-squares problem, but they perform faster than
+the non-boosted ones.
 The reduction of the accuracy might be due to an oversimplification of the
@@
 generated by the great number of iterations required to fit the sources.
-As the windows gets larger, the accuracy starts increasing because more data
+As the windows get larger, the accuracy starts increasing because more data
 points are included into the fitting process of the source coefficients, while
@@
 iterations.
-When using gradient-boosted equivalent sources we can conclude that we want to
-maximize the window size as much as possible.
+When using gradient-boosted equivalent sources we can conclude that is
+desirable to maximize the window size as much as possible.
 The only limitation to do so is to generate Jacobian matrices larger than the
@@
 
-Overlap:
-
-We can then conclude that using overlap values between 40\% and 70\% generate
-a balance between predictions accuracy and computational time needed to fit the
-source coefficients.
+From the results shown in Figures~\ref{fig:gradient-boosted-comparison}b
+and~\ref{fig:gradient-boosted-comparison}d we can conclude that using
+overlap values between 40\% and 70\% generate a balance between predictions
+accuracy and computational time needed to fit the source coefficients.
 This corroborates that our naive choice of 50\% is good enough for producing
 accurate predictions in reasonable times.
-
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
 

### 2021-01-27 manuscript/manuscript.tex

--- 2021-01-26 manuscript/manuscript.tex
@@
 
+Our gradient boosting algorithm for overlapping windows is similar to the
+``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
+fits portions of an equivalent source model to the data residuals.
+The key differences are:
+(1) the sources in the overlapping portions of the windows are fit more than
+once, allowing the algorithm to self-correct for poor solutions to any given
+window;
+(2) using only data points within the window when fitting the data enables the
+use of larger datasets;
+(3) experience shows that the step size parameter improves the convergence of
+the solution, particularly when using only the data inside the windows for
+fitting.
+
 \subsection{Location of sources}
@@
 
-Our gradient boosting algorithm for overlapping windows is similar to the
-``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
-fits portions of an equivalent source model to the data residuals.
-The key differences are:
-(1) the sources in the overlapping portions of the windows are fit more than
-once, allowing the algorithm to self-correct for poor solutions to any given
-window;
-(2) using only data points within the window when fitting the data enables the
-use of larger datasets;
-(3) experience shows that the step size parameter improves the convergence of
-the solution, particularly when using only the data inside the windows for
-fitting.
-
 \subsection{Location of sources}
@@
 
-Overlap:
-
-We can then conclude that using overlap values between 40\% and 70\% generate
-a balance between predictions accuracy and computational time needed to fit the
-source coefficients.
+From the results shown in Figures~\ref{fig:gradient-boosted-comparison}b
+and~\ref{fig:gradient-boosted-comparison}d we can conclude that using
+overlap values between 40\% and 70\% generate a balance between predictions
+accuracy and computational time needed to fit the source coefficients.
 This corroborates that our naive choice of 50\% is good enough for producing

### 2021-01-27 manuscript/manuscript.tex
Tweaks to discussion of the location of sources

@@
 fits portions of an equivalent source model to the data residuals.
-The key differences are:
-(1) the sources in the overlapping portions of the windows are fit more than
-once, allowing the algorithm to self-correct for poor solutions to any given
-window;
-(2) using only data points within the window when fitting the data enables the
+The key differences are that in our method:
+(1) the sources in the overlapping portions of the windows are
+fit more than once, allowing the algorithm to self-correct for poor solutions
+to any given window;
+(2) we use only data points within the window when fitting the data enables the
 use of larger datasets;
@@
 Nevertheless, the computational load can be prohibitive and such
-underdetermined problems are prone to overfiting the data, leading to poor
+underdetermined problems are prone to overfitting the data, leading to poor
 predictive power when interpolating and extrapolating.
@@
   z = z_{obs} + \Delta z + \alpha h,
+  \label{eq:variable_depth}
 \end{equation}
@@
 Figures~\ref{fig:ground-survey-differences}
-and~\ref{fig:airborne-survey-differences} show that all source distributions
-produce accurate predictions, both for the ground and airborne survey.
-The RMS scores don't show significant difference, so we can only conclude
-that all the source distributions are able to produce comparable predictions.
-Nevertheless, the \emph{block averaged sources} make use of less sources to
-produce this predictions, what would reduce the computational load needed to
-fit the sources coefficients and finally compute the actual prediction.
-
-The RMS doesn't seem to depend on the choice of the depth strategy used to
-locate the equivalent sources.
-At first glance, the choice of a depth strategy doesn't seem to impact the
-computational needs.
-Nevertheless, when trying to find the set of parameters that produce the most
-accurate predictions through a method like cross-validation, we need to fit the
-source coefficients one time per every possible combination of parameters.
-A depth strategy like the \emph{variable depth} needs a higher number of
-parameters (depth, depth factor, K nearest) than \emph{constant depth} or
-\emph{relative depth} (which takes only a depth parameter).
-The addition of these new parameters makes the search of the best set more
-computationally expensive: more parameters means increasing the dimensions of
-the parameters space and thus increasing the number of possible combinations.
-Therefore we would be more prone to choose a \emph{constant depth} or
-a \emph{relative depth} when dealing with very large datasets in order to save
-some computation time.
+and~\ref{fig:airborne-survey-differences} show that there are no significant
+differences between source distribution strategies, both in terms of the
+interpolation RMS errors and from visual inspection of the difference maps.
+Therefore, we argue that all source distribution strategies are able to produce
+comparably accurate interpolations.
+Nevertheless, the \emph{block-averaged-sources} strategy make use of fewer
+sources to when compared with other strategies, which reduces the computational
+load of estimating the sources coefficients and forward modelling.
+
+The choice of source depth strategy does not appear to impact the interpolation
+RMS error.
+At a first glance, the choice of a depth strategy also would not seem to impact
+the computation time.
+However, when searching for the set of hyper-parameters that produce the most
+accurate interpolation (e.g., through cross-validation), one must solve the
+inverse problem once for every possible combination of parameters.
+A depth strategy like the \emph{variable depth} requires a higher number of
+hyper-parameters (depth shift $\Delta z$, depth factor $\alpha$, and the number
+of nearest neighbours $k$ from Eq.~\ref{eq:variable_depth}) than other
+strategies which only require a single parameter.
+Having more parameters means increasing the dimensions of the parameter space
+and thus increasing the number of possible combinations.
+Thus, we recommend using a \emph{constant depth} or a \emph{relative depth}
+when processing large datasets in order to minimize computation time.
 

### 2021-01-27 manuscript/manuscript.tex
Finish

@@
 
-Figures~\ref{fig:ground-survey-differences}
-and~\ref{fig:airborne-survey-differences} show that there are no significant
+The results of our tests on synthetic data
+(Figs~\ref{fig:ground-survey-differences}
+and~\ref{fig:airborne-survey-differences}) show that there are no significant
 differences between source distribution strategies, both in terms of the
@@
 load of estimating the sources coefficients and forward modelling.
+To ensure that the interpolation is able to reproduce the high frequencies in
+the data, the block size used in the averaging should be chosen to match the
+desired grid resolution.
 
@@
 
-From figures~\ref{fig:gradient-boosted-comparison}a
-and~\ref{fig:gradient-boosted-comparison}c we can see that the gradient-boosted
-equivalent sources produce slightly less accurate results by failing to achieve
-the global minimum of the least-squares problem, but they perform faster than
-the non-boosted ones.
-The reduction of the accuracy might be due to an oversimplification of the
-least-squares problem, and the increase of the computational time might be
-generated by the great number of iterations required to fit the sources.
-As the windows get larger, the accuracy starts increasing because more data
-points are included into the fitting process of the source coefficients, while
-the fitting process takes less time due to a reduction of the number of
-iterations.
-When using gradient-boosted equivalent sources we can conclude that is
-desirable to maximize the window size as much as possible.
-The only limitation to do so is to generate Jacobian matrices larger than the
-available memory.
-Therefore we recommend using the largest window that generates Jacobian
-matrices that could fit in the available memory.
-
-From the results shown in Figures~\ref{fig:gradient-boosted-comparison}b
-and~\ref{fig:gradient-boosted-comparison}d we can conclude that using
-overlap values between 40\% and 70\% generate a balance between predictions
-accuracy and computational time needed to fit the source coefficients.
-This corroborates that our naive choice of 50\% is good enough for producing
-accurate predictions in reasonable times.
-
-If the grid will have a much higher resolution than the block spacing, the
-equivalent sources will not be able to reproduce the high frequency components
-of the data.
-Therefore we recommend setting a block spacing that matches the resolution of
-the final grid.
+From Fig.~\ref{fig:gradient-boosted-comparison}a
+and~\ref{fig:gradient-boosted-comparison}c, we can see that the
+gradient-boosted equivalent sources produce slightly less accurate
+interpolation results but are able to achieve smaller computation times than
+regular equivalent sources.
+The reduction of the accuracy might be due to the gradient boosting algorithm
+failing to converge to the global minimum of the goal function.
+As the windows increase in size, interpolation error decreases because more data
+points are included into the least-squares fitting of the source coefficients.
+At the same time, the fitting process becomes faster because of a reduction in
+the number of iterations.
+Our results indicate that it is desirable to maximize the window size up to the
+point that the Jacobian matrices still fit within the available computer
+memory.
+
+The results shown in Figs~\ref{fig:gradient-boosted-comparison}b
+and~\ref{fig:gradient-boosted-comparison}d indicate that using
+window overlap values between 40\% and 70\% strike a balance between
+accuracy and computation time.
+This corroborates our initial choice of 50\% overlap, which is good enough for
+producing accurate predictions in reasonable times.
 

### 2021-01-27 manuscript/manuscript.tex

@@
 Nevertheless, the \emph{block-averaged-sources} strategy make use of fewer
-sources to when compared with other strategies, which reduces the computational
+sources when compared with other strategies, which reduces the computational
 load of estimating the sources coefficients and forward modelling.
@@
 
-The choice of source depth strategy does not appear to impact the interpolation
-RMS error.
-At a first glance, the choice of a depth strategy also would not seem to impact
+The choice of source depth strategy does not appear to significantly impact the
+interpolation RMS error.
+In the particular case of a sparse ground survey with block-averaged-sources,
+the use of a variable depth visibly reduced edge effects and artifacts in areas
+of poor data coverage.
+At a first glance, the choice of a depth strategy would not seem to impact
 the computation time.

### 2021-01-27 manuscript/manuscript.tex
Add data citations and more software citations

@@
 portion of a public domain dataset for Southern Africa, available through the
-NOAA National Centers for Environmental Information (NCEI)\footnote{
-\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}
-(last accessed 25 January 2020)}.
-For the synthetic airborne survey, we used a portion of the Great Britain Aeromagnetic
-Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
-Ltd between 1955 and 1965 and made publicly available by the
-British Geological Survey (BGS)\footnote{
-\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}
-(last accessed 25 January 2020)}.
+NOAA National Centers for Environmental Information (NCEI).
+For the synthetic airborne survey, we used a portion of the Great Britain
+Aeromagnetic Survey acquired by Hunting Geology and Geophysics Ltd and Canadian
+Aeroservices Ltd between 1955 and 1965 and made publicly available by the
+British Geological Survey (BGS).
 In both cases, we rescaled the horizontal coordinates of each survey portion to
@@
 
-\section{Software implementation}
-
-We have implemented the methods described in the previous sections though
-a software written in Python language.
-The code for generating the results of this work are available in
-\url{https://doi.org/10.6084/m9.figshare.13604360} or
-\url{https//github.com/compgeolab/eql-gradient-boosted}.
-The gradient-boosted equivalent sources implementation is based on the
-non-boosted sources available through the Harmonica library
-\citep{harmonica2020}, part of the Fatiando a Terra project
-\citep{fatiando2013}.
-Another Python libraries were used:
-Verde \citep{verde2018} to apply block reductions and managing coordinates,
-Boule \citep{boule2020} for computing normal gravity,
-Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
-multidimensional datasets and numerical
-computations,
-Numba \citep{numba2015} for writing pre-comipled implementations and
-parallelization,
-Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
-the figures.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusions}
@@
 
+\section{Data and code availability}
+
+The Python source code used to produce all results and figures presented here
+is available at
+\url{https://doi.org/10.6084/m9.figshare.13604360} and
+\url{https://github.com/compgeolab/eql-gradient-boosted}
+under the BSD 3-clause open-source license.
+
+The gradient-boosted equivalent sources implementation is based on the
+equivalent source code in the Harmonica library \citep{harmonica2020}.
+Other software used in this study includes:
+Pooch \citep{pooch2020} for downloading and caching datasets,
+Verde \citep{verde2018} for block reductions and coordinate manipulations,
+Boule \citep{boule2020} for normal gravity calculations,
+xarray \citep{xarray2017} and Numpy \citep{numpy2020} for multidimensional
+arrays and numerical computations,
+Numba \citep{numba2015} for just-in-time compilation and parallelization,
+Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
+the figures and maps,
+and the Jupyter notebook programming environment \citep{jupyter2016}.
+Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
+\citep{fatiando2013}.
+
+All datasets used are open-access and publicly available.
+The synthetic surveys were generated using
+a public domain gravity dataset for Southern Africa distributed by the
+NOAA NCEI (\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html})
+and the Great Britain Aeromagnetic
+Survey distributed by the
+British Geological Survey (BGS) under an Open Government License
+(\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}).
+The shaded relief in Fig.~\ref{fig:australia} is the SRTM15+ dataset by
+\citet{tozer2019}.
+The Australian ground gravity
+data is based on a compilation distributed by Geoscience Australia under a
+Creative Commons Attribution 4.0 International Licence \citep{wynne2018}  which
+was filtered and referenced to the WGS84 ellipsoid by
+\citet{australia_compilation} and is distributed under the same license
+(\url{https://doi.org/10.6084/m9.figshare.13643837}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Acknowledgements}
@@
 without which this work would not have been possible.
-The synthetic airborne survey was based upon the Great Britain aeromagnetic
-data, reproduced with the permission of the British Geological Survey
-\textcopyright{} UKRI.
-All rights reserved.
+Contains British Geological Survey materials © UKRI.
 

### 2021-01-27 manuscript/manuscript.tex
Review the conclusions section
Trimmed it a little bit and added a final part on future research.

--- 2021-01-27 manuscript/manuscript.tex
@@
 
-The equivalent source technique has been proven to be a well suited method for
-interpolating any harmonic data such as gravity disturbances and magnetic
-anomalies.
-The two main reasons that make it to stand out over all-purpose 2D
-interpolation methods is the fact that the equivalent sources take into account
-the height of the observations and they always produce harmonic predictions.
-The main inconvenience of using equivalent sources is the computational
-requirements needed to estimate the coefficients of the equivalent sources,
+The equivalent source technique has been proven to be well suited for
+interpolating gravity disturbances and magnetic anomalies.
+The two main reasons that make it to stand out from other 2D interpolation
+methods is the fact that the equivalent sources take into account the height of
+the observations and that the interpolated values will always be harmonic
+functions.
+The main challenge to using equivalent sources in practice is the high
+computational load of estimating the coefficients of the equivalent sources,
 specially on the computer memory needed to store the Jacobian matrix.
-This forbids the application of the equivalent source technique to very
-large datasets where the computer memory needed to store the whole Jacobian
-matrix greatly exceeds the specifications of modest personal computers now days.
-
 In this work we present two strategies that could be simultaneously applied in
-order to interpolate very large datasets in reasonable times without the need
-to store large matrices into memory:
-the block-averaged sources, which reduce the number of
-equivalent sources needed for the interpolation;
-and the gradient-boosted equivalent sources that simplify the
-problem of estimating the source coefficients into smaller problems
-through sets of equivalent sources defined by overlapping windows.
-
-Both methods were exhaustively tested against a synthetic model and synthetic
-surveys in order to compare accurate they are in comparison to the existing
-techniques and how they perform in terms of computational resources.
-Block-averaged sources were compared to the interpolations obtained with two
-traditional strategies for locating the sources:
-the \emph{source below data} and the \emph{regular grid} of sources.
-The performance of the gradient-boosted equivalent sources was compared against
-the regular non-boosted equivalent sources, along with tests for assessing how
-the choice of the window size and the amount of overlap between adjacent
-windows affect both the accuracy of the interpolations and the computational
-load.
-
-Our results showed that the block-averaged sources reduce the computational
-load needed to estimate their coefficients in comparison to the two traditional
-strategies mentioned before.
-They also showed that this reduction of the number of sources doesn't affect
-the accuracy of the predictions, making block-averaged sources a better
-alternative to the traditional methods.
-Besides, block-averaged sources might also prevent aliasing on the interpolated
-values, specially when the observation points show high anisotropy, i.e. they
-were taken along paths with a high sample frequency.
-From our experimentation with this new strategy we noticed that special
-attention must be payed when choosing the size of the block spacing:
-as a thumb rule, it must be approximately equal to the resolution of the
-regular grid where the values will be interpolated.
-
-We have also carried out similar tests to compare the vertical location of the
-sources.
-Our results showed that any one of the three strategies taken into account
+order to interpolate very large datasets (millions of points) in reasonable
+computation times on modest hardware:
+block-averaging source locations, which reduce the number of equivalent sources
+needed for the interpolation,
+and the gradient-boosted equivalent source algorithm, which breaks down the
+inverse problem into smaller  sets of equivalent sources defined by overlapping
+windows.
+Both methods were tested against synthetic datasets in order to compare their
+accuracy and how they perform in terms of computational resources.
+
+Our results show that the block-averaged sources reduce the computational
+load needed to estimate source coefficients in comparison to the two traditional
+strategies of placing sources below data points or on regular grids.
+We also showed that this reduction of the number of sources does not affect
+the accuracy of the predictions.
+The use of block-averaged sources may also prevent aliasing of the interpolated
+values, specially when the observations are unevenly sampled (e.g., airborne
+and shipborne surveys).
+Special attention must be payed when choosing the size of the blocks for
+averaging: as a thumb rule, we recommend choosing a size approximately equal to
+the resolution of the regular grid where the values will be interpolated.
+
+Tests that compared strategies for the vertical location of the
+sources showed that any one of the three strategies tested
 (\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
-doesn't significantly affects the accuracy of the interpolations.
-Nevertheless, we are more prone to choose either the \emph{constant depth} or
-the \emph{relative depth} for any application because they involve less
-hyper-parameters that would be needed to estimated before the actual
+produces comparable accuracy of interpolation.
+Nevertheless, we are more prone to recommending either the \emph{constant
+depth} or the \emph{relative depth} for most applications because they involve
+less hyper-parameters that would be needed to configured before the actual
 interpolation.
 
-Regarding the gradient-boosted equivalent sources, our results show that they
-heavily reduce the computer memory needed to estimate source coefficients,
-making possible to interpolate even very large datasets.
-The interpolations obtained though this new method achieve almost the same
-accuracy than the non-boosted sources, while reducing the computation time
-needed to estimate the source coefficients.
-Because it doesn't involve any assumption on the location of the sources, it
-can be used in conjunction with any horizontal source layout and any strategy
-for setting their depth.
-This allows to use both the block-averaged sources and the gradient-boosted
-equivalent sources simultaneously.
-Our results allowed us to develop a rule of thumb in order to maximize the
-accuracy of the interpolations: the size of the overlapping windows must be
-chosen as the maximum value that creates Jacobian matrices that fit into our
-computer memory.
-Therefore its choice is subject to the particular infrastructure where the
-interpolation will be carried out.
+Gradient-boosted equivalent sources were shown to heavily reduce the computer
+memory needed to estimate source coefficients, making it possible to
+interpolate large datasets with millions of points that would otherwise produce
+Jacobian matrices larger than the available memory.
+The interpolations obtained though this new method achieve close to the same
+accuracy than the regular equivalent sources (within approximately 40\%), while
+reducing the computation time needed to estimate the source coefficients by
+approximately three times.
 We also show that an overlap of 50\% between adjacent windows achieves a good
-compromise between accuracy and computation time needed to fit the source
-coefficients.
-
-Finally, both proposed methods were used to interpolate a compilation of more
-than 1.7 million gravity points from Australia on a regular grid with
-a resolution of 1~arc-minute.
-The whole process was carried out on a modest personal computer, requiring
-a maximum of 10GB of memory.
-This shows how the new gradient-boosted equivalent sources can be applied to
-real-world data.
+compromise between accuracy and computation time.
+The size of the overlapping windows should be chosen as the maximum value
+possible that creates Jacobian matrices that still fit into computer memory.
+
+The gradient-boosting method developed here can be used in conjunction with any
+horizontal source layout, depth strategy, or source type (e.g., point sources,
+prisms, tesseroids) because it does not rely on assumptions about the sources.
+Future research should investigate the application of gradient boosting to
+other equivalent source methods, as well as alternatives to overlapping windows
+for converting the equivalent source model into an additive model.
 

### 2021-01-27 manuscript/manuscript.tex
Add an author contributions statement
A few sentences explaining who did what.
Standardize the use of Eq. and Fig.
We were using a mix of "Eq." and "equation" and "Fig" and "Figure" for
referencing. Use just the abbreviated version which is in line with the
GJI guide.

--- 2021-01-27 manuscript/manuscript.tex
@@
 we can find a least-squares solution to
-equation~\ref{eq:linear-problem} and obtain the values of
+Eq.~\ref{eq:linear-problem} and obtain the values of
 $\mathbf{c}$ that best fit the observations.
@@
 at any other point outside of the sources by evaluating
-equation~\ref{eq:eql-forward}.
+Eq.~\ref{eq:eql-forward}.
 Gridding and upward continuation can thus be achieved by predicting values on
@@
 $\mathbf{A}$.
-We then write the forward problem in equation~\ref{eq:linear-problem} as
+We then write the forward problem in Eq.~\ref{eq:linear-problem} as
 
@@
 
-The goal function defined in equation~\ref{eq:misfit-unscaled} can be
+The goal function defined in Eq.~\ref{eq:misfit-unscaled} can be
 rewritten as
@@
 We can transform our equivalent source problem in
-equation~\ref{eq:linear-problem} into an additive model by following these
+Eq.~\ref{eq:linear-problem} into an additive model by following these
 steps:
@@
 solutions for the $K$ parameters vectors $\mathbf{c}_k$ and step sizes
-$\alpha_k$ in equation~\ref{eq:gb-linear-model} is presented in
+$\alpha_k$ in Eq.~\ref{eq:gb-linear-model} is presented in
 Algorithm~\ref{alg:gradient_boosting}.
@@
 The forward modeling operation performed in step \ref{alg:predicted} can be
-done by a summation (equation~\ref{eq:forward-sum})
+done by a summation (Eq.~\ref{eq:forward-sum})
 instead of a matrix-vector product, which allows us to avoid computing and
@@
 
-Figures~\ref{fig:ground-survey-differences}
+Fig~\ref{fig:ground-survey-differences}
 and~\ref{fig:airborne-survey-differences} show the differences between the

### 2021-01-27 manuscript/manuscript.tex
Add an abstract and keywords
Based on Santiago's EGU abstract and keywords chosen from the official
GJI list.

@@
 
+\noindent
+\textbf{Keywords:}
+Gravity anomalies and Earth structure;
+Magnetic anomalies: modelling and interpretation;
+Geopotential theory;
+Inverse theory;
+Statistical methods;
+Australia;
+
 \begin{abstract}
-    My abstract
-    \\[0.5cm]
-    \textbf{Keywords:}
-    My keywords
+  The equivalent source technique is a powerful and widely used method for
+  processing gravity and magnetic data.  Nevertheless, it has the major
+  drawback of having a large computational cost in terms of processing time and
+  computer memory.
+  We present two techniques for reducing the computational cost of equivalent
+  source processing: block-averaging source locations and the
+  gradient-boosted equivalent source algorithm.
+  By using block-averaging, we reduce the number of source coefficients that
+  must be estimated while retaining the minimum desired resolution in the final
+  processed data.
+  With the gradient boosting method, we estimate the layer coefficients in
+  small batches along overlapping windows, allowing us to reduce the computer
+  memory requirements arbitrarily to conform to the constraints of the
+  available hardware.
+  We show that the combination of block-averaging and gradient-boosted
+  equivalent sources are capable of producing accurate interpolations through
+  tests against synthetic data.
+  Moreover, we demonstrate the feasibility of our method by gridding a gravity
+  dataset covering Australia with over 1.7 million observations using a modest
+  personal computer in under two hours of total processing time.
 \end{abstract}
@@
 we can find a least-squares solution to
-Eq.~\ref{eq:linear-problem} and obtain the values of
+equation~\ref{eq:linear-problem} and obtain the values of
 $\mathbf{c}$ that best fit the observations.
@@
 at any other point outside of the sources by evaluating
-Eq.~\ref{eq:eql-forward}.
+equation~\ref{eq:eql-forward}.
 Gridding and upward continuation can thus be achieved by predicting values on
@@
 $\mathbf{A}$.
-We then write the forward problem in Eq.~\ref{eq:linear-problem} as
+We then write the forward problem in equation~\ref{eq:linear-problem} as
 
@@
 
-The goal function defined in Eq.~\ref{eq:misfit-unscaled} can be
+The goal function defined in equation~\ref{eq:misfit-unscaled} can be
 rewritten as
@@
 We can transform our equivalent source problem in
-Eq.~\ref{eq:linear-problem} into an additive model by following these
+equation~\ref{eq:linear-problem} into an additive model by following these
 steps:
@@
 solutions for the $K$ parameters vectors $\mathbf{c}_k$ and step sizes
-$\alpha_k$ in Eq.~\ref{eq:gb-linear-model} is presented in
+$\alpha_k$ in equation~\ref{eq:gb-linear-model} is presented in
 Algorithm~\ref{alg:gradient_boosting}.
@@
 The forward modeling operation performed in step \ref{alg:predicted} can be
-done by a summation (Eq.~\ref{eq:forward-sum})
+done by a summation (equation~\ref{eq:forward-sum})
 instead of a matrix-vector product, which allows us to avoid computing and
@@
 
-Fig~\ref{fig:ground-survey-differences}
+Figures~\ref{fig:ground-survey-differences}
 and~\ref{fig:airborne-survey-differences} show the differences between the

### 2021-01-27 manuscript/manuscript.tex
Add some text to the appendix with the tables

@@
 
-\noindent
+\begin{abstract}
+    My abstract
+    \\[0.5cm]
     \textbf{Keywords:}
-Gravity anomalies and Earth structure;
-Magnetic anomalies: modelling and interpretation;
-Geopotential theory;
-Inverse theory;
-Statistical methods;
-Australia;
-
-\begin{abstract}
-  The equivalent source technique is a powerful and widely used method for
-  processing gravity and magnetic data.  Nevertheless, it has the major
-  drawback of having a large computational cost in terms of processing time and
-  computer memory.
-  We present two techniques for reducing the computational cost of equivalent
-  source processing: block-averaging source locations and the
-  gradient-boosted equivalent source algorithm.
-  By using block-averaging, we reduce the number of source coefficients that
-  must be estimated while retaining the minimum desired resolution in the final
-  processed data.
-  With the gradient boosting method, we estimate the layer coefficients in
-  small batches along overlapping windows, allowing us to reduce the computer
-  memory requirements arbitrarily to conform to the constraints of the
-  available hardware.
-  We show that the combination of block-averaging and gradient-boosted
-  equivalent sources are capable of producing accurate interpolations through
-  tests against synthetic data.
-  Moreover, we demonstrate the feasibility of our method by gridding a gravity
-  dataset covering Australia with over 1.7 million observations using a modest
-  personal computer in under two hours of total processing time.
+    My keywords
 \end{abstract}
@@
 \subsection{Source distribution strategies}
+\label{sec:synthetic_distributions}
 
@@
 
-\section{Source distributions parameters}
+\section{Source position parameters used for the tests on synthetic data}
+
+Tables~\ref{tab:parameters-ground-survey}
+and~\ref{tab:parameters-airborne-survey} show the parameter values tested and
+their optimal values for creating the equivalent source distributions tested in
+Section~\ref{sec:synthetic_distributions}.
+The optimal values were used to produce the results in
+Figs~\ref{fig:ground-survey-differences}
+and~\ref{fig:airborne-survey-differences}.
 
@@
     \caption{
-        Parameters used with each source distribution when gridding the
-        synthetic ground survey. The table also contains the set of parameters
-        that generates the best prediction for each source distribution and its
-        corresponding RMS score (in mGal).
+        Parameters used to produce each source distribution for interpolating
+        the synthetic ground survey data. Also contains the set of parameters
+        that generates the smallest RMS error for each source distribution and
+        their corresponding RMS.
     }
@@
             &
-                & K nearest
+                & $k$ neighbours
                 & \GroundSourceBelowDataVariableDepthKNearest
@@
             &
-                & Spacing (m)
+                & Block size (m)
                 & \GroundBlockAveragedSourcesConstantDepthSpacing
@@
             &
-                & Spacing (m)
+                & Block size (m)
                 & \GroundBlockAveragedSourcesRelativeDepthSpacing
@@
             &
-                & K nearest
+                & $k$ neighbours
                 & \GroundBlockAveragedSourcesVariableDepthKNearest
@@
             &
-                & Spacing (m)
+                & Block size (m)
                 & \GroundBlockAveragedSourcesVariableDepthSpacing
@@
             &
-                & Spacing (m)
+                & Grid spacing (m)
                 & \GroundGridSourcesConstantDepthSpacing
@@
     \caption{
-        Parameters used with each source distribution when gridding the
-        synthetic airborne survey. The table also contains the set of
-        parameters that generates the best prediction for each source
-        distribution and its corresponding RMS score (in mGal).
+        Parameters used to produce each source distribution for interpolating
+        the synthetic airborne survey data. Also contains the set of parameters
+        that generates the smallest RMS error for each source distribution and
+        their corresponding RMS.
     }
@@
             &
-                & K nearest
+                & $k$ neighbours
                 & \AirborneSourceBelowDataVariableDepthKNearest
@@
             &
-                & Spacing (m)
+                & Block size (m)
                 & \AirborneBlockAveragedSourcesConstantDepthSpacing
@@
             &
-                & Spacing (m)
+                & Block size (m)
                 & \AirborneBlockAveragedSourcesRelativeDepthSpacing
@@
             &
-                & K nearest
+                & $k$ neighbours
                 & \AirborneBlockAveragedSourcesVariableDepthKNearest
@@
             &
-                & Spacing (m)
+                & Block size (m)
                 & \AirborneBlockAveragedSourcesVariableDepthSpacing
@@
             &
-                & Spacing (m)
+                & Grid spacing (m)
                 & \AirborneGridSourcesConstantDepthSpacing

### 2021-01-27 manuscript/manuscript.tex

--- 2021-01-27 manuscript/manuscript.tex
@@
 
-\section{Software implementation}
-
-We have implemented the methods described in the previous sections though
-a software written in Python language.
-The code for generating the results of this work are available in
-\url{https://doi.org/10.6084/m9.figshare.13604360} or
-\url{https//github.com/compgeolab/eql-gradient-boosted}.
+\section{Conclusions}
+
+The equivalent source technique has been proven to be well suited for
+interpolating gravity disturbances and magnetic anomalies.
+The two main reasons that make it to stand out from other 2D interpolation
+methods is the fact that the equivalent sources take into account the height of
+the observations and that the interpolated values will always be harmonic
+functions.
+The main challenge to using equivalent sources in practice is the high
+computational load of estimating the coefficients of the equivalent sources,
+specially on the computer memory needed to store the Jacobian matrix.
+In this work we present two strategies that could be simultaneously applied in
+order to interpolate very large datasets (millions of points) in reasonable
+computation times on modest hardware:
+block-averaging source locations, which reduce the number of equivalent sources
+needed for the interpolation,
+and the gradient-boosted equivalent source algorithm, which breaks down the
+inverse problem into smaller  sets of equivalent sources defined by overlapping
+windows.
+Both methods were tested against synthetic datasets in order to compare their
+accuracy and how they perform in terms of computational resources.
+
+Our results show that the block-averaged sources reduce the computational
+load needed to estimate source coefficients in comparison to the two traditional
+strategies of placing sources below data points or on regular grids.
+We also showed that this reduction of the number of sources does not affect
+the accuracy of the predictions.
+The use of block-averaged sources may also prevent aliasing of the interpolated
+values, specially when the observations are unevenly sampled (e.g., airborne
+and shipborne surveys).
+Special attention must be payed when choosing the size of the blocks for
+averaging: as a thumb rule, we recommend choosing a size approximately equal to
+the resolution of the regular grid where the values will be interpolated.
+
+Tests that compared strategies for the vertical location of the
+sources showed that any one of the three strategies tested
+(\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
+produces comparable accuracy of interpolation.
+Nevertheless, we are more prone to recommending either the \emph{constant
+depth} or the \emph{relative depth} for most applications because they involve
+less hyper-parameters that would be needed to configured before the actual
+interpolation.
+
+Gradient-boosted equivalent sources were shown to heavily reduce the computer
+memory needed to estimate source coefficients, making it possible to
+interpolate large datasets with millions of points that would otherwise produce
+Jacobian matrices larger than the available memory.
+The interpolations obtained though this new method achieve close to the same
+accuracy than the regular equivalent sources (within approximately 40\%), while
+reducing the computation time needed to estimate the source coefficients by
+approximately three times.
+We also show that an overlap of 50\% between adjacent windows achieves a good
+compromise between accuracy and computation time.
+The size of the overlapping windows should be chosen as the maximum value
+possible that creates Jacobian matrices that still fit into computer memory.
+
+The gradient-boosting method developed here can be used in conjunction with any
+horizontal source layout, depth strategy, or source type (e.g., point sources,
+prisms, tesseroids) because it does not rely on assumptions about the sources.
+Future research should investigate the application of gradient boosting to
+other equivalent source methods, as well as alternatives to overlapping windows
+for converting the equivalent source model into an additive model.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Data and code availability}
+
+The Python source code used to produce all results and figures presented here
+is available at
+\url{https://doi.org/10.6084/m9.figshare.13604360} and
+\url{https://github.com/compgeolab/eql-gradient-boosted}
+under the BSD 3-clause open-source license.
+
 The gradient-boosted equivalent sources implementation is based on the
-non-boosted sources available through the Harmonica library
-\citep{harmonica2020}, part of the Fatiando a Terra project
+equivalent source code in the Harmonica library \citep{harmonica2020}.
+Other software used in this study includes:
+Pooch \citep{pooch2020} for downloading and caching datasets,
+Verde \citep{verde2018} for block reductions and coordinate manipulations,
+Boule \citep{boule2020} for normal gravity calculations,
+xarray \citep{xarray2017} and Numpy \citep{numpy2020} for multidimensional
+arrays and numerical computations,
+Numba \citep{numba2015} for just-in-time compilation and parallelization,
+Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
+the figures and maps,
+and the Jupyter notebook programming environment \citep{jupyter2016}.
+Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
 \citep{fatiando2013}.
-Another Python libraries were used:
-Verde \citep{verde2018} to apply block reductions and managing coordinates,
-Boule \citep{boule2020} for computing normal gravity,
-Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
-multidimensional datasets and numerical
-computations,
-Numba \citep{numba2015} for writing pre-comipled implementations and
-parallelization,
-Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
-the figures.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusions}
-
-The equivalent source technique has been proven to be a well suited method for
-interpolating any harmonic data such as gravity disturbances and magnetic
-anomalies.
-The two main reasons that make it to stand out over all-purpose 2D
-interpolation methods is the fact that the equivalent sources take into account
-the height of the observations and they always produce harmonic predictions.
-The main inconvenience of using equivalent sources is the computational
-requirements needed to estimate the coefficients of the equivalent sources,
-specially on the computer memory needed to store the Jacobian matrix.
-This forbids the application of the equivalent source technique to very
-large datasets where the computer memory needed to store the whole Jacobian
-matrix greatly exceeds the specifications of modest personal computers now days.
-
-In this work we present two strategies that could be simultaneously applied in
-order to interpolate very large datasets in reasonable times without the need
-to store large matrices into memory:
-the block-averaged sources, which reduce the number of
-equivalent sources needed for the interpolation;
-and the gradient-boosted equivalent sources that simplify the
-problem of estimating the source coefficients into smaller problems
-through sets of equivalent sources defined by overlapping windows.
-
-Both methods were exhaustively tested against a synthetic model and synthetic
-surveys in order to compare accurate they are in comparison to the existing
-techniques and how they perform in terms of computational resources.
-Block-averaged sources were compared to the interpolations obtained with two
-traditional strategies for locating the sources:
-the \emph{source below data} and the \emph{regular grid} of sources.
-The performance of the gradient-boosted equivalent sources was compared against
-the regular non-boosted equivalent sources, along with tests for assessing how
-the choice of the window size and the amount of overlap between adjacent
-windows affect both the accuracy of the interpolations and the computational
-load.
-
-Our results showed that the block-averaged sources reduce the computational
-load needed to estimate their coefficients in comparison to the two traditional
-strategies mentioned before.
-They also showed that this reduction of the number of sources doesn't affect
-the accuracy of the predictions, making block-averaged sources a better
-alternative to the traditional methods.
-Besides, block-averaged sources might also prevent aliasing on the interpolated
-values, specially when the observation points show high anisotropy, i.e. they
-were taken along paths with a high sample frequency.
-From our experimentation with this new strategy we noticed that special
-attention must be payed when choosing the size of the block spacing:
-as a thumb rule, it must be approximately equal to the resolution of the
-regular grid where the values will be interpolated.
-
-We have also carried out similar tests to compare the vertical location of the
-sources.
-Our results showed that any one of the three strategies taken into account
-(\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
-doesn't significantly affects the accuracy of the interpolations.
-Nevertheless, we are more prone to choose either the \emph{constant depth} or
-the \emph{relative depth} for any application because they involve less
-hyper-parameters that would be needed to estimated before the actual
-interpolation.
-
-Regarding the gradient-boosted equivalent sources, our results show that they
-heavily reduce the computer memory needed to estimate source coefficients,
-making possible to interpolate even very large datasets.
-The interpolations obtained though this new method achieve almost the same
-accuracy than the non-boosted sources, while reducing the computation time
-needed to estimate the source coefficients.
-Because it doesn't involve any assumption on the location of the sources, it
-can be used in conjunction with any horizontal source layout and any strategy
-for setting their depth.
-This allows to use both the block-averaged sources and the gradient-boosted
-equivalent sources simultaneously.
-Our results allowed us to develop a rule of thumb in order to maximize the
-accuracy of the interpolations: the size of the overlapping windows must be
-chosen as the maximum value that creates Jacobian matrices that fit into our
-computer memory.
-Therefore its choice is subject to the particular infrastructure where the
-interpolation will be carried out.
-We also show that an overlap of 50\% between adjacent windows achieves a good
-compromise between accuracy and computation time needed to fit the source
-coefficients.
-
-Finally, both proposed methods were used to interpolate a compilation of more
-than 1.7 million gravity points from Australia on a regular grid with
-a resolution of 1~arc-minute.
-The whole process was carried out on a modest personal computer, requiring
-a maximum of 10GB of memory.
-This shows how the new gradient-boosted equivalent sources can be applied to
-real-world data.
+
+All datasets used are open-access and publicly available.
+The synthetic surveys were generated using
+a public domain gravity dataset for Southern Africa distributed by the
+NOAA NCEI (\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html})
+and the Great Britain Aeromagnetic
+Survey distributed by the
+British Geological Survey (BGS) under an Open Government License
+(\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}).
+The shaded relief in Fig.~\ref{fig:australia} is the SRTM15+ dataset by
+\citet{tozer2019}.
+The Australian ground gravity
+data is based on a compilation distributed by Geoscience Australia under a
+Creative Commons Attribution 4.0 International Licence \citep{wynne2018}  which
+was filtered and referenced to the WGS84 ellipsoid by
+\citet{australia_compilation} and is distributed under the same license
+(\url{https://doi.org/10.6084/m9.figshare.13643837}).
 

### 2021-01-27 manuscript/manuscript.tex
Apply suggestions from code review
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
 functions.
-The main challenge to using equivalent sources in practice is the high
+The main challenge of using equivalent sources in practice is the high
 computational load of estimating the coefficients of the equivalent sources,
@@
 depth} or the \emph{relative depth} for most applications because they involve
-less hyper-parameters that would be needed to configured before the actual
+less hyper-parameters that would need to be configured before the actual
 interpolation.

### 2021-01-27 manuscript/manuscript.tex
Remove part about additive modesl from conclusion

@@
 Future research should investigate the application of gradient boosting to
-other equivalent source methods, as well as alternatives to overlapping windows
-for converting the equivalent source model into an additive model.
+other equivalent source methods.
 

### 2021-01-27 manuscript/manuscript.tex
Standardize the use of Eq. and Fig. (#106)
We were using a mix of "Eq." and "equation" and "Fig" and "Figure" for
referencing. Use just the abbreviated version which is in line with the
GJI guide.

Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

@@
 
-The equivalent source technique has been proven to be well suited for
-interpolating gravity disturbances and magnetic anomalies.
-The two main reasons that make it to stand out from other 2D interpolation
-methods is the fact that the equivalent sources take into account the height of
-the observations and that the interpolated values will always be harmonic
-functions.
-The main challenge of using equivalent sources in practice is the high
-computational load of estimating the coefficients of the equivalent sources,
+The equivalent source technique has been proven to be a well suited method for
+interpolating any harmonic data such as gravity disturbances and magnetic
+anomalies.
+The two main reasons that make it to stand out over all-purpose 2D
+interpolation methods is the fact that the equivalent sources take into account
+the height of the observations and they always produce harmonic predictions.
+The main inconvenience of using equivalent sources is the computational
+requirements needed to estimate the coefficients of the equivalent sources,
 specially on the computer memory needed to store the Jacobian matrix.
+This forbids the application of the equivalent source technique to very
+large datasets where the computer memory needed to store the whole Jacobian
+matrix greatly exceeds the specifications of modest personal computers now days.
+
 In this work we present two strategies that could be simultaneously applied in
-order to interpolate very large datasets (millions of points) in reasonable
-computation times on modest hardware:
-block-averaging source locations, which reduce the number of equivalent sources
-needed for the interpolation,
-and the gradient-boosted equivalent source algorithm, which breaks down the
-inverse problem into smaller sets of equivalent sources defined by overlapping
-windows.
-Both methods were tested against synthetic datasets in order to compare their
-accuracy and how they perform in terms of computational resources.
-
-Our results show that the block-averaged sources reduce the computational
-load needed to estimate source coefficients in comparison to the two traditional
-strategies of placing sources below data points or on regular grids.
-We also showed that this reduction of the number of sources does not affect
-the accuracy of the predictions.
-The use of block-averaged sources may also prevent aliasing of the interpolated
-values, specially when the observations are unevenly sampled (e.g., airborne
-and shipborne surveys).
-Special attention must be payed when choosing the size of the blocks for
-averaging: as a thumb rule, we recommend choosing a size approximately equal to
-the resolution of the regular grid where the values will be interpolated.
-
-Tests that compared strategies for the vertical location of the
-sources showed that any one of the three strategies tested
+order to interpolate very large datasets in reasonable times without the need
+to store large matrices into memory:
+the block-averaged sources, which reduce the number of
+equivalent sources needed for the interpolation;
+and the gradient-boosted equivalent sources that simplify the
+problem of estimating the source coefficients into smaller problems
+through sets of equivalent sources defined by overlapping windows.
+
+Both methods were exhaustively tested against a synthetic model and synthetic
+surveys in order to compare accurate they are in comparison to the existing
+techniques and how they perform in terms of computational resources.
+Block-averaged sources were compared to the interpolations obtained with two
+traditional strategies for locating the sources:
+the \emph{source below data} and the \emph{regular grid} of sources.
+The performance of the gradient-boosted equivalent sources was compared against
+the regular non-boosted equivalent sources, along with tests for assessing how
+the choice of the window size and the amount of overlap between adjacent
+windows affect both the accuracy of the interpolations and the computational
+load.
+
+Our results showed that the block-averaged sources reduce the computational
+load needed to estimate their coefficients in comparison to the two traditional
+strategies mentioned before.
+They also showed that this reduction of the number of sources doesn't affect
+the accuracy of the predictions, making block-averaged sources a better
+alternative to the traditional methods.
+Besides, block-averaged sources might also prevent aliasing on the interpolated
+values, specially when the observation points show high anisotropy, i.e. they
+were taken along paths with a high sample frequency.
+From our experimentation with this new strategy we noticed that special
+attention must be payed when choosing the size of the block spacing:
+as a thumb rule, it must be approximately equal to the resolution of the
+regular grid where the values will be interpolated.
+
+We have also carried out similar tests to compare the vertical location of the
+sources.
+Our results showed that any one of the three strategies taken into account
 (\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
-produces comparable accuracy of interpolation.
-Nevertheless, we are more prone to recommending either the \emph{constant
-depth} or the \emph{relative depth} for most applications because they involve
-less hyper-parameters that would need to be configured before the actual
+doesn't significantly affects the accuracy of the interpolations.
+Nevertheless, we are more prone to choose either the \emph{constant depth} or
+the \emph{relative depth} for any application because they involve less
+hyper-parameters that would be needed to estimated before the actual
 interpolation.
 
-Gradient-boosted equivalent sources were shown to heavily reduce the computer
-memory needed to estimate source coefficients, making it possible to
-interpolate large datasets with millions of points that would otherwise produce
-Jacobian matrices larger than the available memory.
-The interpolations obtained though this new method achieve close to the same
-accuracy than the regular equivalent sources (within approximately 40\%), while
-reducing the computation time needed to estimate the source coefficients by
-approximately three times.
+Regarding the gradient-boosted equivalent sources, our results show that they
+heavily reduce the computer memory needed to estimate source coefficients,
+making possible to interpolate even very large datasets.
+The interpolations obtained though this new method achieve almost the same
+accuracy than the non-boosted sources, while reducing the computation time
+needed to estimate the source coefficients.
+Because it doesn't involve any assumption on the location of the sources, it
+can be used in conjunction with any horizontal source layout and any strategy
+for setting their depth.
+This allows to use both the block-averaged sources and the gradient-boosted
+equivalent sources simultaneously.
+Our results allowed us to develop a rule of thumb in order to maximize the
+accuracy of the interpolations: the size of the overlapping windows must be
+chosen as the maximum value that creates Jacobian matrices that fit into our
+computer memory.
+Therefore its choice is subject to the particular infrastructure where the
+interpolation will be carried out.
 We also show that an overlap of 50\% between adjacent windows achieves a good
-compromise between accuracy and computation time.
-The size of the overlapping windows should be chosen as the maximum value
-possible that creates Jacobian matrices that still fit into computer memory.
-
-The gradient-boosting method developed here can be used in conjunction with any
-horizontal source layout, depth strategy, or source type (e.g., point sources,
-prisms, tesseroids) because it does not rely on assumptions about the sources.
-Future research should investigate the application of gradient boosting to
-other equivalent source methods.
+compromise between accuracy and computation time needed to fit the source
+coefficients.
+
+Finally, both proposed methods were used to interpolate a compilation of more
+than 1.7 million gravity points from Australia on a regular grid with
+a resolution of 1~arc-minute.
+The whole process was carried out on a modest personal computer, requiring
+a maximum of 10GB of memory.
+This shows how the new gradient-boosted equivalent sources can be applied to
+real-world data.
 

### 2021-01-27 manuscript/manuscript.tex
Apply suggestions from code review
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

--- 2021-01-27 manuscript/manuscript.tex
@@
 
+\noindent
+\textbf{Keywords:}
+Gravity anomalies and Earth structure;
+Magnetic anomalies: modelling and interpretation;
+Geopotential theory;
+Inverse theory;
+Statistical methods;
+Australia;
+
 \begin{abstract}
-    My abstract
-    \\[0.5cm]
-    \textbf{Keywords:}
-    My keywords
+  The equivalent source technique is a powerful and widely used method for
+  processing gravity and magnetic data.  Nevertheless, its major
+  drawback is the large computational cost in terms of processing time and
+  computer memory.
+  We present two techniques for reducing the computational cost of equivalent
+  source processing: block-averaging source locations and the
+  gradient-boosted equivalent source algorithm.
+  By using block-averaging, we reduce the number of source coefficients that
+  must be estimated while retaining the minimum desired resolution in the final
+  processed data.
+  With the gradient boosting method, we estimate the layer coefficients in
+  small batches along overlapping windows, allowing us to reduce the computer
+  memory requirements arbitrarily to conform to the constraints of the
+  available hardware.
+  We show that the combination of block-averaging and gradient-boosted
+  equivalent sources are capable of producing accurate interpolations through
+  tests against synthetic data.
+  Moreover, we demonstrate the feasibility of our method by gridding a gravity
+  dataset covering Australia with over 1.7 million observations using a modest
+  personal computer in under two hours of total processing time.
 \end{abstract}
@@
 portion of a public domain dataset for Southern Africa, available through the
-NOAA National Centers for Environmental Information (NCEI).
-For the synthetic airborne survey, we used a portion of the Great Britain
-Aeromagnetic Survey acquired by Hunting Geology and Geophysics Ltd and Canadian
-Aeroservices Ltd between 1955 and 1965 and made publicly available by the
-British Geological Survey (BGS).
+NOAA National Centers for Environmental Information (NCEI)\footnote{
+\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}
+(last accessed 25 January 2020)}.
+For the synthetic airborne survey, we used a portion of the Great Britain Aeromagnetic
+Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
+Ltd between 1955 and 1965 and made publicly available by the
+British Geological Survey (BGS)\footnote{
+\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}
+(last accessed 25 January 2020)}.
 In both cases, we rescaled the horizontal coordinates of each survey portion to
@@
 
-\section{Data and code availability}
-
-The Python source code used to produce all results and figures presented here
-is available at
-\url{https://doi.org/10.6084/m9.figshare.13604360} and
-\url{https://github.com/compgeolab/eql-gradient-boosted}
-under the BSD 3-clause open-source license.
-
-The gradient-boosted equivalent sources implementation is based on the
-equivalent source code in the Harmonica library \citep{harmonica2020}.
-Other software used in this study includes:
-Pooch \citep{pooch2020} for downloading and caching datasets,
-Verde \citep{verde2018} for block reductions and coordinate manipulations,
-Boule \citep{boule2020} for normal gravity calculations,
-xarray \citep{xarray2017} and Numpy \citep{numpy2020} for multidimensional
-arrays and numerical computations,
-Numba \citep{numba2015} for just-in-time compilation and parallelization,
-Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
-the figures and maps,
-and the Jupyter notebook programming environment \citep{jupyter2016}.
-Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
-\citep{fatiando2013}.
-
-All datasets used are open-access and publicly available.
-The synthetic surveys were generated using
-a public domain gravity dataset for Southern Africa distributed by the
-NOAA NCEI (\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html})
-and the Great Britain Aeromagnetic
-Survey distributed by the
-British Geological Survey (BGS) under an Open Government License
-(\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}).
-The shaded relief in Fig.~\ref{fig:australia} is the SRTM15+ dataset by
-\citet{tozer2019}.
-The Australian ground gravity
-data is based on a compilation distributed by Geoscience Australia under a
-Creative Commons Attribution 4.0 International Licence \citep{wynne2018}  which
-was filtered and referenced to the WGS84 ellipsoid by
-\citet{australia_compilation} and is distributed under the same license
-(\url{https://doi.org/10.6084/m9.figshare.13643837}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Acknowledgements}
@@
 without which this work would not have been possible.
-Contains British Geological Survey materials © UKRI.
+The synthetic airborne survey was based upon the Great Britain aeromagnetic
+data, reproduced with the permission of the British Geological Survey
+\textcopyright{} UKRI.
+All rights reserved.
 

### 2021-01-27 manuscript/manuscript.tex
Update manuscript/manuscript.tex

@@
   dataset covering Australia with over 1.7 million observations using a modest
-  personal computer in under two hours of total processing time.
+  personal computer.
 \end{abstract}

### 2021-01-27 manuscript/manuscript.tex

--- 2021-01-27 manuscript/manuscript.tex
@@
 
+\noindent
+\textbf{Keywords:}
+Gravity anomalies and Earth structure;
+Magnetic anomalies: modelling and interpretation;
+Geopotential theory;
+Inverse theory;
+Statistical methods;
+Australia;
+
 \begin{abstract}
-    My abstract
-    \\[0.5cm]
-    \textbf{Keywords:}
-    My keywords
+  The equivalent source technique is a powerful and widely used method for
+  processing gravity and magnetic data.  Nevertheless, its major
+  drawback is the large computational cost in terms of processing time and
+  computer memory.
+  We present two techniques for reducing the computational cost of equivalent
+  source processing: block-averaging source locations and the
+  gradient-boosted equivalent source algorithm.
+  By using block-averaging, we reduce the number of source coefficients that
+  must be estimated while retaining the minimum desired resolution in the final
+  processed data.
+  With the gradient boosting method, we estimate the layer coefficients in
+  small batches along overlapping windows, allowing us to reduce the computer
+  memory requirements arbitrarily to conform to the constraints of the
+  available hardware.
+  We show that the combination of block-averaging and gradient-boosted
+  equivalent sources are capable of producing accurate interpolations through
+  tests against synthetic data.
+  Moreover, we demonstrate the feasibility of our method by gridding a gravity
+  dataset covering Australia with over 1.7 million observations using a modest
+  personal computer.
 \end{abstract}
@@
 without which this work would not have been possible.
+S.R. Soler is supported by a scholarship from CONICET, Argentina.
 Contains British Geological Survey materials © UKRI.
+
+S.R. Soler and L. Uieda jointly developed the initial idea, analysed the
+results, and wrote the paper. S.R. Soler produced all results and developed the
+software implementation with minor revisions by L. Uieda.
 

### 2021-01-27 manuscript/manuscript.tex

@@
 
-The equivalent source technique has been proven to be a well suited method for
-interpolating any harmonic data such as gravity disturbances and magnetic
-anomalies.
-The two main reasons that make it to stand out over all-purpose 2D
-interpolation methods is the fact that the equivalent sources take into account
-the height of the observations and they always produce harmonic predictions.
-The main inconvenience of using equivalent sources is the computational
-requirements needed to estimate the coefficients of the equivalent sources,
+The equivalent source technique has been proven to be well suited for
+interpolating gravity disturbances and magnetic anomalies.
+The two main reasons that make it to stand out from other 2D interpolation
+methods is the fact that the equivalent sources take into account the height of
+the observations and that the interpolated values will always be harmonic
+functions.
+The main challenge of using equivalent sources in practice is the high
+computational load of estimating the coefficients of the equivalent sources,
 specially on the computer memory needed to store the Jacobian matrix.
-This forbids the application of the equivalent source technique to very
-large datasets where the computer memory needed to store the whole Jacobian
-matrix greatly exceeds the specifications of modest personal computers now days.
-
 In this work we present two strategies that could be simultaneously applied in
-order to interpolate very large datasets in reasonable times without the need
-to store large matrices into memory:
-the block-averaged sources, which reduce the number of
-equivalent sources needed for the interpolation;
-and the gradient-boosted equivalent sources that simplify the
-problem of estimating the source coefficients into smaller problems
-through sets of equivalent sources defined by overlapping windows.
-
-Both methods were exhaustively tested against a synthetic model and synthetic
-surveys in order to compare accurate they are in comparison to the existing
-techniques and how they perform in terms of computational resources.
-Block-averaged sources were compared to the interpolations obtained with two
-traditional strategies for locating the sources:
-the \emph{source below data} and the \emph{regular grid} of sources.
-The performance of the gradient-boosted equivalent sources was compared against
-the regular non-boosted equivalent sources, along with tests for assessing how
-the choice of the window size and the amount of overlap between adjacent
-windows affect both the accuracy of the interpolations and the computational
-load.
-
-Our results showed that the block-averaged sources reduce the computational
-load needed to estimate their coefficients in comparison to the two traditional
-strategies mentioned before.
-They also showed that this reduction of the number of sources doesn't affect
-the accuracy of the predictions, making block-averaged sources a better
-alternative to the traditional methods.
-Besides, block-averaged sources might also prevent aliasing on the interpolated
-values, specially when the observation points show high anisotropy, i.e. they
-were taken along paths with a high sample frequency.
-From our experimentation with this new strategy we noticed that special
-attention must be payed when choosing the size of the block spacing:
-as a thumb rule, it must be approximately equal to the resolution of the
-regular grid where the values will be interpolated.
-
-We have also carried out similar tests to compare the vertical location of the
-sources.
-Our results showed that any one of the three strategies taken into account
+order to interpolate very large datasets (millions of points) in reasonable
+computation times on modest hardware:
+block-averaging source locations, which reduce the number of equivalent sources
+needed for the interpolation,
+and the gradient-boosted equivalent source algorithm, which breaks down the
+inverse problem into smaller sets of equivalent sources defined by overlapping
+windows.
+Both methods were tested against synthetic datasets in order to compare their
+accuracy and how they perform in terms of computational resources.
+
+Our results show that the block-averaged sources reduce the computational
+load needed to estimate source coefficients in comparison to the two traditional
+strategies of placing sources below data points or on regular grids.
+We also showed that this reduction of the number of sources does not affect
+the accuracy of the predictions.
+The use of block-averaged sources may also prevent aliasing of the interpolated
+values, specially when the observations are unevenly sampled (e.g., airborne
+and shipborne surveys).
+Special attention must be payed when choosing the size of the blocks for
+averaging: as a thumb rule, we recommend choosing a size approximately equal to
+the resolution of the regular grid where the values will be interpolated.
+
+Tests that compared strategies for the vertical location of the
+sources showed that any one of the three strategies tested
 (\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
-doesn't significantly affects the accuracy of the interpolations.
-Nevertheless, we are more prone to choose either the \emph{constant depth} or
-the \emph{relative depth} for any application because they involve less
-hyper-parameters that would be needed to estimated before the actual
+produces comparable accuracy of interpolation.
+Nevertheless, we are more prone to recommending either the \emph{constant
+depth} or the \emph{relative depth} for most applications because they involve
+less hyper-parameters that would need to be configured before the actual
 interpolation.
 
-Regarding the gradient-boosted equivalent sources, our results show that they
-heavily reduce the computer memory needed to estimate source coefficients,
-making possible to interpolate even very large datasets.
-The interpolations obtained though this new method achieve almost the same
-accuracy than the non-boosted sources, while reducing the computation time
-needed to estimate the source coefficients.
-Because it doesn't involve any assumption on the location of the sources, it
-can be used in conjunction with any horizontal source layout and any strategy
-for setting their depth.
-This allows to use both the block-averaged sources and the gradient-boosted
-equivalent sources simultaneously.
-Our results allowed us to develop a rule of thumb in order to maximize the
-accuracy of the interpolations: the size of the overlapping windows must be
-chosen as the maximum value that creates Jacobian matrices that fit into our
-computer memory.
-Therefore its choice is subject to the particular infrastructure where the
-interpolation will be carried out.
+Gradient-boosted equivalent sources were shown to heavily reduce the computer
+memory needed to estimate source coefficients, making it possible to
+interpolate large datasets with millions of points that would otherwise produce
+Jacobian matrices larger than the available memory.
+The interpolations obtained though this new method achieve close to the same
+accuracy than the regular equivalent sources (within approximately 40\%), while
+reducing the computation time needed to estimate the source coefficients by
+approximately three times.
 We also show that an overlap of 50\% between adjacent windows achieves a good
-compromise between accuracy and computation time needed to fit the source
-coefficients.
-
-Finally, both proposed methods were used to interpolate a compilation of more
-than 1.7 million gravity points from Australia on a regular grid with
-a resolution of 1~arc-minute.
-The whole process was carried out on a modest personal computer, requiring
-a maximum of 10GB of memory.
-This shows how the new gradient-boosted equivalent sources can be applied to
-real-world data.
+compromise between accuracy and computation time.
+The size of the overlapping windows should be chosen as the maximum value
+possible that creates Jacobian matrices that still fit into computer memory.
+
+The gradient-boosting method developed here can be used in conjunction with any
+horizontal source layout, depth strategy, or source type (e.g., point sources,
+prisms, tesseroids) because it does not rely on assumptions about the sources.
+Future research should investigate the application of gradient boosting to
+other equivalent source methods.
 

### 2021-01-27 manuscript/manuscript.tex
Remove the difference between RMS errors from conclusions

@@
 The interpolations obtained though this new method achieve close to the same
-accuracy than the regular equivalent sources (within approximately 40\%), while
-reducing the computation time needed to estimate the source coefficients by
-approximately three times.
+accuracy than the regular equivalent sources, while reducing the computation
+time needed to estimate the source coefficients by approximately three times.
 We also show that an overlap of 50\% between adjacent windows achieves a good

### 2021-01-28 manuscript/manuscript.tex
Small fix on writing

@@
 to any given window;
-(2) we use only data points within the window when fitting the data enables the
+(2) we use only data points within the window when fitting, what enables the
 use of larger datasets;

### 2021-01-28 manuscript/manuscript.tex
Start editing manuscript to work with GJI style

@@
-\documentclass[twocolumn]{article}
-%\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
-\setlength{\columnsep}{2\columnsep}
+\documentclass[extra]{gji}
 \usepackage[utf8]{inputenc}
+\usepackage{timet}
 \usepackage{amssymb}
@@
 \usepackage{siunitx}
-\usepackage[round,authoryear,sort]{natbib}
 \usepackage{url}
 \usepackage[pdftex,colorlinks=true]{hyperref}
-\usepackage{fancyhdr}
 \usepackage{multirow}
@@
 \DeclareSIUnit\mgal{\milli Gal}
+\newcommand{\Gal}{Gal}
 
@@
 % Import files with parameter values generated by notebooks
-\newcommand{\Gal}{Gal}
 \input{synthetic-surveys.tex}
@@
 
-% Define title, authors, affiliations and DOI
-% ===========================================
-\newcommand{\Title}{%
+% Define title, authors and affiliations
+% ======================================
+\title{
     Gradient-boosted equivalent sources
 }
-\newcommand{\Author}{%
-    S.R. Soler,
-    L. Uieda
+\author[S.R. Soler and L. Uieda]{
+    Santiago R. Soler$^{1,2}$ and Leonardo Uieda$^3$ \\
+    $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com) \\
+    $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina \\
+    $^{3}$Department of Earth, Ocean and Ecological Sciences, School of
+    Environmental Sciences, University of Liverpool, UK
 }
-\newcommand{\AuthorAffil}{%
-    {\large
-        Santiago R. Soler$^{1,2}$,
-        Leonardo Uieda$^{3}$
-    }
-    \\[0.4cm]
-    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
-    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
-    {\small $^{3}$Department of Earth, Ocean and Ecological Sciences, School of Environmental Sciences, University of Liverpool, UK} \\
-}
-\newcommand{\DOI}{%
-    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
-}
-\newcommand{\DOILink}{%
-    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
-}
-
-% Configure header and hypersetup
-% ===============================
-\pagestyle{fancy}
-\fancyhf{}
-\lhead{
-    \fontsize{9pt}{12pt}\selectfont
-    \Author{} (\the\year{}). \DOI{}
-}
-\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
-\renewcommand{\headrulewidth}{0pt}
-\hypersetup{
-    allcolors=blue,
-    pdftitle={\Title},
-    pdfauthor={\Author},
-}
 
@@
 
-\title{\Title}
-\author{\AuthorAffil}
-\date{
-    \normalsize
-    \today
-}
 \maketitle
 
-\noindent
-\textbf{Keywords:}
-Gravity anomalies and Earth structure;
-Magnetic anomalies: modelling and interpretation;
-Geopotential theory;
-Inverse theory;
-Statistical methods;
-Australia;
-
-\begin{abstract}
+\begin{summary}
   The equivalent source technique is a powerful and widely used method for
@@
   personal computer.
-\end{abstract}
+\end{summary}
+
+\begin{keywords}
+Gravity anomalies and Earth structure,
+Magnetic anomalies: modelling and interpretation,
+Geopotential theory,
+Inverse theory,
+Statistical methods,
+Australia,
+\end{keywords}
 
@@
 
-\bibliographystyle{humannat}
+\bibliographystyle{gji}
 \bibliography{references}

### 2021-01-29 manuscript/manuscript.tex
Apply one possible solution for the issue between gji and siunitx
Rerun notebook and remove siunitx from manuscript

--- 2021-01-28 manuscript/manuscript.tex
@@
 \usepackage{graphicx}
-\usepackage{siunitx}
 \usepackage[round,authoryear,sort]{natbib}
@@
 
-% Define special units
-\DeclareSIUnit\mgal{\milli Gal}
-
 % Define inverse symbol with shorter minus
@@
 For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of approximately \SI{0.8}{\mgal} regardless of the depth type, with the
+values of approximately 0.8~mGal regardless of the depth type, with the
 exception of the regular-grid layout which produced a larger RMS of
-\SI{\BestGroundGridSourcesConstantDepthRms{}}{\mgal}.
+\BestGroundGridSourcesConstantDepthRms{}~mGal.
 The differences between the target grid and the interpolated values are larger
@@
 For the synthetic airborne survey, all strategies (including the regular-grid)
-produced similar RMS errors of approximately \SI{0.3}{\mgal}.
+produced similar RMS errors of approximately 0.3~mGal.
 The maps of the differences between the target grid and interpolation results
@@
 block-averaged-sources with a block size of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
+\BestAirborneBlockAveragedSourcesRelativeDepthSpacing~m and a
 relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.
+\BestAirborneBlockAveragedSourcesRelativeDepthDepth~m.
 
@@
 at a relative depth of \AustraliaEqlDepth{} and a block size of
-\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
+1.8~km, resulting in a total of \AustraliaEqlNSources{}~point
 sources.
 The block size was chosen to match the desired resolution of the final grid
- (1~arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
+ (1~arc-minute is approximately 1.8~km at the equator).
 The coefficients of the gradient-boosted equivalent sources are estimated using
@@
 interpolated regular grid.
-Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
+Grid points that are further than 50~km from the nearest data
 point are masked to avoid unrealistic extrapolations.

### 2021-02-02 manuscript/content.tex
Refactor manuscript
Split the manuscript into several files: keywords.tex, abstract.tex,
content.tex, appendix.tex, variables.tex.
Move all .tex files generated by the notebooks results into their own
directory: manuscript/results/

--- 2021-01-28 manuscript/manuscript.tex
@@
-\documentclass[extra]{gji}
-\usepackage[utf8]{inputenc}
-\usepackage{timet}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage[longend,linesnumbered,ruled]{algorithm2e}
-\usepackage{graphicx}
-\usepackage{siunitx}
-\usepackage{url}
-\usepackage[pdftex,colorlinks=true]{hyperref}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{setspace}
-
-% Define style for urls
-\urlstyle{same}
-
-% Define special units
-\DeclareSIUnit\mgal{\milli Gal}
-\newcommand{\Gal}{Gal}
-
-% Define inverse symbol with shorter minus
-\newcommand{\inv}{^{\text{-}1}}
-\newcommand{\trans}{^{\text{T}}}
-
-% Import files with parameter values generated by notebooks
-\input{synthetic-surveys.tex}
-\input{parameters-ground-survey.tex}
-\input{parameters-airborne-survey.tex}
-\input{best-parameters-ground-survey.tex}
-\input{best-parameters-airborne-survey.tex}
-\input{source-layouts-schematics.tex}
-\input{boost-overlapping.tex}
-\input{australia.tex}
-
-% Define title, authors and affiliations
-% ======================================
-\title{
-    Gradient-boosted equivalent sources
-}
-\author[S.R. Soler and L. Uieda]{
-    Santiago R. Soler$^{1,2}$ and Leonardo Uieda$^3$ \\
-    $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com) \\
-    $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina \\
-    $^{3}$Department of Earth, Ocean and Ecological Sciences, School of
-    Environmental Sciences, University of Liverpool, UK
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\maketitle
-
-\begin{summary}
-  The equivalent source technique is a powerful and widely used method for
-  processing gravity and magnetic data.  Nevertheless, its major
-  drawback is the large computational cost in terms of processing time and
-  computer memory.
-  We present two techniques for reducing the computational cost of equivalent
-  source processing: block-averaging source locations and the
-  gradient-boosted equivalent source algorithm.
-  By using block-averaging, we reduce the number of source coefficients that
-  must be estimated while retaining the minimum desired resolution in the final
-  processed data.
-  With the gradient boosting method, we estimate the layer coefficients in
-  small batches along overlapping windows, allowing us to reduce the computer
-  memory requirements arbitrarily to conform to the constraints of the
-  available hardware.
-  We show that the combination of block-averaging and gradient-boosted
-  equivalent sources are capable of producing accurate interpolations through
-  tests against synthetic data.
-  Moreover, we demonstrate the feasibility of our method by gridding a gravity
-  dataset covering Australia with over 1.7 million observations using a modest
-  personal computer.
-\end{summary}
-
-\begin{keywords}
-Gravity anomalies and Earth structure,
-Magnetic anomalies: modelling and interpretation,
-Geopotential theory,
-Inverse theory,
-Statistical methods,
-Australia,
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
@@
 For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of approximately \SI{0.8}{\mgal} regardless of the depth type, with the
+values of approximately 0.8\mGal regardless of the depth type, with the
 exception of the regular-grid layout which produced a larger RMS of
-\SI{\BestGroundGridSourcesConstantDepthRms{}}{\mgal}.
+\BestGroundGridSourcesConstantDepthRms{}\mGal.
 The differences between the target grid and the interpolated values are larger
@@
 For the synthetic airborne survey, all strategies (including the regular-grid)
-produced similar RMS errors of approximately \SI{0.3}{\mgal}.
+produced similar RMS errors of approximately 0.3\mGal.
 The maps of the differences between the target grid and interpolation results
@@
 block-averaged-sources with a block size of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
+\BestAirborneBlockAveragedSourcesRelativeDepthSpacing\m and a
 relative depth of
-\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.
+\BestAirborneBlockAveragedSourcesRelativeDepthDepth\m.
 
@@
 at a relative depth of \AustraliaEqlDepth{} and a block size of
-\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
+1.8\km, resulting in a total of \AustraliaEqlNSources{}~point
 sources.
 The block size was chosen to match the desired resolution of the final grid
- (1~arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
+ (1~arc-minute is approximately 1.8\km at the equator).
 The coefficients of the gradient-boosted equivalent sources are estimated using
@@
 interpolated regular grid.
-Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
+Grid points that are further than 50\km from the nearest data
 point are masked to avoid unrealistic extrapolations.
@@
 software implementation with minor revisions by L. Uieda.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{gji}
-\bibliography{references}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Source position parameters used for the tests on synthetic data}
-
-Tables~\ref{tab:parameters-ground-survey}
-and~\ref{tab:parameters-airborne-survey} show the parameter values tested and
-their optimal values for creating the equivalent source distributions tested in
-Section~\ref{sec:synthetic_distributions}.
-The optimal values were used to produce the results in
-Figs~\ref{fig:ground-survey-differences}
-and~\ref{fig:airborne-survey-differences}.
-
-\begin{table*}
-    \centering
-    \caption{
-        Parameters used to produce each source distribution for interpolating
-        the synthetic ground survey data. Also contains the set of parameters
-        that generates the smallest RMS error for each source distribution and
-        their corresponding RMS.
-    }
-    \label{tab:parameters-ground-survey}
-    \begin{tabular}{c c l c c c}
-        \textbf{Source layout}
-            & \textbf{Depth type}
-            & \multicolumn{1}{c}{\textbf{Parameters}}
-            & \textbf{Values}
-            & \textbf{Best}
-            & \textbf{RMS} \\
-        \toprule
-
-        \multirow{8}{*}{Source Below Data}
-            & \multirow{2}{*}{Constant}
-                & Depth (m)
-                & \GroundSourceBelowDataConstantDepthDepth
-                & \BestGroundSourceBelowDataConstantDepthDepth
-                & \multirow{2}{*}{
-                    \BestGroundSourceBelowDataConstantDepthRms
-                  } \\
-            &
-                & Damping
-                & \GroundSourceBelowDataConstantDepthDamping
-                & \BestGroundSourceBelowDataConstantDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{2}{*}{Relative}
-                & Depth (m)
-                & \GroundSourceBelowDataRelativeDepthDepth
-                & \BestGroundSourceBelowDataRelativeDepthDepth
-                & \multirow{2}{*}{
-                    \BestGroundSourceBelowDataRelativeDepthRms
-                  } \\
-            &
-                & Damping
-                & \GroundSourceBelowDataRelativeDepthDamping
-                & \BestGroundSourceBelowDataRelativeDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{4}{*}{Variable}
-                & Depth (m)
-                & \GroundSourceBelowDataVariableDepthDepth
-                & \BestGroundSourceBelowDataVariableDepthDepth
-                & \multirow{4}{*}{
-                    \BestGroundSourceBelowDataVariableDepthRms
-                  } \\
-            &
-                & Depth factor
-                & \GroundSourceBelowDataVariableDepthDepthFactor
-                & \BestGroundSourceBelowDataVariableDepthDepthFactor
-                & \\
-            &
-                & $k$ neighbours
-                & \GroundSourceBelowDataVariableDepthKNearest
-                & \BestGroundSourceBelowDataVariableDepthKNearest
-                & \\
-            &
-                & Damping
-                & \GroundSourceBelowDataVariableDepthDamping
-                & \BestGroundSourceBelowDataVariableDepthDamping
-                & \\
-        \midrule
-
-        \multirow{11}{*}{Block Averaged Sources}
-            & \multirow{3}{*}{Constant}
-                & Depth (m)
-                & \GroundBlockAveragedSourcesConstantDepthDepth
-                & \BestGroundBlockAveragedSourcesConstantDepthDepth
-                & \multirow{3}{*}{
-                    \BestGroundBlockAveragedSourcesConstantDepthRms
-                  } \\
-            &
-                & Block size (m)
-                & \GroundBlockAveragedSourcesConstantDepthSpacing
-                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockAveragedSourcesConstantDepthDamping
-                & \BestGroundBlockAveragedSourcesConstantDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{3}{*}{Relative}
-                & Depth (m)
-                & \GroundBlockAveragedSourcesRelativeDepthDepth
-                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
-                & \multirow{3}{*}{
-                    \BestGroundBlockAveragedSourcesRelativeDepthRms
-                  } \\
-            &
-                & Block size (m)
-                & \GroundBlockAveragedSourcesRelativeDepthSpacing
-                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockAveragedSourcesRelativeDepthDamping
-                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{5}{*}{Variable}
-                & Depth (m)
-                & \GroundBlockAveragedSourcesVariableDepthDepth
-                & \BestGroundBlockAveragedSourcesVariableDepthDepth
-                & \multirow{5}{*}{
-                    \BestGroundBlockAveragedSourcesVariableDepthRms
-                  } \\
-            &
-                & Depth factor
-                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
-                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
-                & \\
-            &
-                & $k$ neighbours
-                & \GroundBlockAveragedSourcesVariableDepthKNearest
-                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
-                & \\
-            &
-                & Block size (m)
-                & \GroundBlockAveragedSourcesVariableDepthSpacing
-                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockAveragedSourcesVariableDepthDamping
-                & \BestGroundBlockAveragedSourcesVariableDepthDamping
-                & \\
-        \midrule
-
-        \multirow{4}{*}{Grid Sources}
-            & \multirow{4}{*}{Constant}
-                & Depth (m)
-                & \GroundGridSourcesConstantDepthDepth
-                & \BestGroundGridSourcesConstantDepthDepth
-                & \multirow{4}{*}{
-                    \BestGroundGridSourcesConstantDepthRms
-                  } \\
-            &
-                & Grid spacing (m)
-                & \GroundGridSourcesConstantDepthSpacing
-                & \BestGroundGridSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundGridSourcesConstantDepthDamping
-                & \BestGroundGridSourcesConstantDepthDamping
-                & \\
-    \end{tabular}
-\end{table*}
-
-\begin{table*}
-    \centering
-    \caption{
-        Parameters used to produce each source distribution for interpolating
-        the synthetic airborne survey data. Also contains the set of parameters
-        that generates the smallest RMS error for each source distribution and
-        their corresponding RMS.
-    }
-    \label{tab:parameters-airborne-survey}
-    \begin{tabular}{c c l c c c}
-        \textbf{Source layout}
-            & \textbf{Depth type}
-            & \multicolumn{1}{c}{\textbf{Parameters}}
-            & \textbf{Values}
-            & \textbf{Best}
-            & \textbf{RMS} \\
-        \toprule
-
-        \multirow{8}{*}{Source Below Data}
-            & \multirow{2}{*}{Constant}
-                & Depth (m)
-                & \AirborneSourceBelowDataConstantDepthDepth
-                & \BestAirborneSourceBelowDataConstantDepthDepth
-                & \multirow{2}{*}{
-                    \BestAirborneSourceBelowDataConstantDepthRms
-                  } \\
-            &
-                & Damping
-                & \AirborneSourceBelowDataConstantDepthDamping
-                & \BestAirborneSourceBelowDataConstantDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{2}{*}{Relative}
-                & Depth (m)
-                & \AirborneSourceBelowDataRelativeDepthDepth
-                & \BestAirborneSourceBelowDataRelativeDepthDepth
-                & \multirow{2}{*}{
-                    \BestAirborneSourceBelowDataRelativeDepthRms
-                  } \\
-            &
-                & Damping
-                & \AirborneSourceBelowDataRelativeDepthDamping
-                & \BestAirborneSourceBelowDataRelativeDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{4}{*}{Variable}
-                & Depth (m)
-                & \AirborneSourceBelowDataVariableDepthDepth
-                & \BestAirborneSourceBelowDataVariableDepthDepth
-                & \multirow{4}{*}{
-                    \BestAirborneSourceBelowDataVariableDepthRms
-                  } \\
-            &
-                & Depth factor
-                & \AirborneSourceBelowDataVariableDepthDepthFactor
-                & \BestAirborneSourceBelowDataVariableDepthDepthFactor
-                & \\
-            &
-                & $k$ neighbours
-                & \AirborneSourceBelowDataVariableDepthKNearest
-                & \BestAirborneSourceBelowDataVariableDepthKNearest
-                & \\
-            &
-                & Damping
-                & \AirborneSourceBelowDataVariableDepthDamping
-                & \BestAirborneSourceBelowDataVariableDepthDamping
-                & \\
-        \midrule
-
-        \multirow{11}{*}{Block Averaged Sources}
-            & \multirow{3}{*}{Constant}
-                & Depth (m)
-                & \AirborneBlockAveragedSourcesConstantDepthDepth
-                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
-                & \multirow{3}{*}{
-                    \BestAirborneBlockAveragedSourcesConstantDepthRms
-                  } \\
-            &
-                & Block size (m)
-                & \AirborneBlockAveragedSourcesConstantDepthSpacing
-                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockAveragedSourcesConstantDepthDamping
-                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{3}{*}{Relative}
-                & Depth (m)
-                & \AirborneBlockAveragedSourcesRelativeDepthDepth
-                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
-                & \multirow{3}{*}{
-                    \BestAirborneBlockAveragedSourcesRelativeDepthRms
-                  } \\
-            &
-                & Block size (m)
-                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
-                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockAveragedSourcesRelativeDepthDamping
-                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{5}{*}{Variable}
-                & Depth (m)
-                & \AirborneBlockAveragedSourcesVariableDepthDepth
-                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
-                & \multirow{5}{*}{
-                    \BestAirborneBlockAveragedSourcesVariableDepthRms
-                  } \\
-            &
-                & Depth factor
-                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
-                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
-                & \\
-            &
-                & $k$ neighbours
-                & \AirborneBlockAveragedSourcesVariableDepthKNearest
-                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
-                & \\
-            &
-                & Block size (m)
-                & \AirborneBlockAveragedSourcesVariableDepthSpacing
-                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockAveragedSourcesVariableDepthDamping
-                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
-                & \\
-        \midrule
-
-        \multirow{4}{*}{Grid Sources}
-            & \multirow{4}{*}{Constant}
-                & Depth (m)
-                & \AirborneGridSourcesConstantDepthDepth
-                & \BestAirborneGridSourcesConstantDepthDepth
-                & \multirow{4}{*}{
-                    \BestAirborneGridSourcesConstantDepthRms
-                  } \\
-            &
-                & Grid spacing (m)
-                & \AirborneGridSourcesConstantDepthSpacing
-                & \BestAirborneGridSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneGridSourcesConstantDepthDamping
-                & \BestAirborneGridSourcesConstantDepthDamping
-                & \\
-    \end{tabular}
-\end{table*}
-
-\end{document}

### 2021-02-02 manuscript/manuscript.tex
Refactor manuscript
Split the manuscript into several files: keywords.tex, abstract.tex,
content.tex, appendix.tex, variables.tex.
Move all .tex files generated by the notebooks results into their own
directory: manuscript/results/

@@
 \documentclass[twocolumn]{article}
-%\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
 \setlength{\columnsep}{2\columnsep}
@@
 
-% Define inverse symbol with shorter minus
-\newcommand{\inv}{^{\text{-}1}}
-\newcommand{\trans}{^{\text{T}}}
-
-% Import files with parameter values generated by notebooks
-\input{synthetic-surveys.tex}
-\input{parameters-ground-survey.tex}
-\input{parameters-airborne-survey.tex}
-\input{best-parameters-ground-survey.tex}
-\input{best-parameters-airborne-survey.tex}
-\input{source-layouts-schematics.tex}
-\input{boost-overlapping.tex}
-\input{australia.tex}
+% Import variables
+\input{variables.tex}
 
@@
 % ===========================================
-\newcommand{\Title}{%
-    Gradient-boosted equivalent sources
-}
 \newcommand{\Author}{%
-    S.R. Soler,
-    L. Uieda
+    \AuthorAShort,
+    \AuthorBShort
 }
@@
     {\large
-        Santiago R. Soler$^{1,2}$,
-        Leonardo Uieda$^{3}$
+        \AuthorA$^{1,2}$
+        and
+        \AuthorB$^{3}$
     }
     \\[0.4cm]
-    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
-    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
-    {\small $^{3}$Department of Earth, Ocean and Ecological Sciences, School of Environmental Sciences, University of Liverpool, UK} \\
-}
-\newcommand{\DOI}{%
-    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
-}
-\newcommand{\DOILink}{%
-    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
+    {\small $^{1}$\AffiliationA} \\
+    {\small $^{2}$\AffiliationB} \\
+    {\small $^{3}$\AffiliationC} \\
 }
@@
 \textbf{Keywords:}
-Gravity anomalies and Earth structure;
-Magnetic anomalies: modelling and interpretation;
-Geopotential theory;
-Inverse theory;
-Statistical methods;
-Australia;
+\input{keywords.tex}
 
 \begin{abstract}
-  The equivalent source technique is a powerful and widely used method for
-  processing gravity and magnetic data.  Nevertheless, its major
-  drawback is the large computational cost in terms of processing time and
-  computer memory.
-  We present two techniques for reducing the computational cost of equivalent
-  source processing: block-averaging source locations and the
-  gradient-boosted equivalent source algorithm.
-  By using block-averaging, we reduce the number of source coefficients that
-  must be estimated while retaining the minimum desired resolution in the final
-  processed data.
-  With the gradient boosting method, we estimate the layer coefficients in
-  small batches along overlapping windows, allowing us to reduce the computer
-  memory requirements arbitrarily to conform to the constraints of the
-  available hardware.
-  We show that the combination of block-averaging and gradient-boosted
-  equivalent sources are capable of producing accurate interpolations through
-  tests against synthetic data.
-  Moreover, we demonstrate the feasibility of our method by gridding a gravity
-  dataset covering Australia with over 1.7 million observations using a modest
-  personal computer.
+    \input{abstract}
 \end{abstract}
@@
 
-\section{Introduction}
-
-Measurements of anomalies in potential fields, like gravity disturbances and
-total-field magnetic anomalies, are widely used in geophysical exploration for
-their relatively low cost of acquisition.
-These data can be surveyed using ground, airborne, shipborne, or satellite
-systems.
-In ground surveys, the data are often gathered following irregular paths or
-networks along the surface of the terrain, leading to highly variable
-elevations in mountainous regions.
-On airborne surveys, the data are gathered along flight lines, producing a
-large number of measurements concentrated along almost straight lines.
-Measurement height can also change because of the vertical movement of the
-aircraft.
-Processing of the data often involves interpolation onto a regular grid at
-constant height, both to improve visualization for interpretation purposes as
-well as to prepare the data for further processing and modelling (e.g.,
-reduction-to-the-pole, derivative calculations, upward continuation, Euler
-deconvolution).
-
-Several methods exist in the literature for interpolation in two dimensions,
-for example continuous curvature splines in tension \citep{smith1990},
-bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
-These general-purpose methods have limitations when it comes to interpolating
-potential field data:
-(i) they are not able to take into account the variable height of the
-observation points and
-(ii) the interpolating functions are not necessarily harmonic functions, which
-is the underlying assumption behind many processing techniques
-(e.g., upward continuation and vertical derivatives).
-
-A widely used method for interpolating gravity and magnetic data
-is the equivalent sources technique (also known as equivalent layer, radial
-basis functions, or Green's functions interpolation), first introduced by
-\citet{dampney1969}.
-It consists in fitting a model of elementary sources to the data and using this
-model to predict new data values.
-Besides interpolation, equivalent sources have been used for
-reduction-to-the-pole of magnetic data
-\citep{silva1986, nakatsuka2006, guspi2009}, upward
-continuation \citep{emilia1973, li2010}, joint processing of gravity gradient
-data \citep{barnes2011}, modelling the lithospheric magnetic field
-\citep{kother2015}, recovering the magnetic induction vector from
-total-field magnetic anomalies \citep{li2020}, and more.
-
-Many variants of the equivalent sources technique have been proposed, often
-attempting to obtain faster or more accurate solutions.
-The key factors that vary between them are: (i) the type of source, (ii)
-the location of the sources, and (iii) the solution strategy.
-The type of source is most commonly a point mass for gravity or dipole for
-magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
-However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
-li2020} and tesseroids \citep{bouman2016} have also been used successfully.
-In fact, even point sources with a simple inverse distance function, instead of
-actual gravity or magnetic fields, can be used as
-equivalent sources \citep{cordell1992}.
-The sources are often distributed on a regular grid at a constant depth
-\citep[e.g.,~][]{leao1989, barnes2011, oliveira2013}
-or placed beneath each data point \citep[e.g.,~][]{cordell1992, siqueira2017}.
-The model is usually estimated through damped least-squares, which imposes a
-heavy computational load when the number of data points is large (e.g.,
-airborne and satellite surveys).
-To reduce the computational load, \citet{mendonca1994} built the solution
-iteratively by incorporating one data point at a time using the ``equivalent
-data concept''.
-\citet{leao1989} processed the input data using a moving window, only fitting the
-data inside the window and predicting observations at the center of the window.
-\citet{li2010} and \citet{barnes2011} apply different operations to generate a
-sparse representation of the sensitive matrix (respectively, wavelet
-compression and quadtree discretization), which significantly improves the
-speed of the least-squares solution.
-\citet{oliveira2013} parametrized the equivalent layer as a piecewise bivariate
-polynomial function, reducing the number of parameters in the solution.
-\citet{siqueira2017} developed an iterative solution in which the sensitivity
-matrix is transformed into a diagonal matrix with constant terms through the
-``excess mass criterion''.
-\citet{jirigalatu2019} applied the Gauss-FFT method to speed up the forward
-modelling operations and solved the least-squares problem using steepest
-descent to avoid calculating the Hessian matrix and solving linear systems.
-
-Many of the existing methods solve under-determined problems, requiring a much
-larger number of equivalent sources than the number of data points.
-Some achieve greater efficiency by restricting their applications
-specific data types \citep{siqueira2017},
-interpolating only on regular grids \citep{leao1989},
-or requiring already gridded data \citep{takahashi2020},
-to name a few.
-Furthermore, many of the optimizations proposed are also complex to implement
-in a computer program, limiting their wider adoption.
-
-In the present study,
-we propose a two strategies for reducing the computational load of
-the equivalent sources technique:
-
-\begin{enumerate}
-    \item Reduce the number of equivalent sources for oversampled surveys
-      through a \emph{block-averaging} strategy while maintaining the quality
-      of the solution.
-    \item Fit the equivalent source model iteratively along overlapping windows
-      using a \emph{gradient boosting} algorithm \citep{friedman2001}.
-\end{enumerate}
-
-The first strategy consists in dividing the survey area into horizontal blocks
-and assign one source to each block, located at the median horizontal location
-of the data points. For airborne, shipborne, and satellite surveys, which are
-oversampled along tracks, this can greatly reduce the size of the inverse
-problem while retaining the same quality of interpolation.
-
-The gradient boosting algorithm allows us to fit the equivalent source model
-iteratively by operating on individual overlapping windows.
-Thus, our method solves several much smaller least-squares problems instead of
-a large one.
-This has some similarities with the strategy used by \citet{leao1989} but
-without the requirement for sources and predictions to be on regular grids.
-
-Through tests on synthetic data, we show that: (i) the \emph{block-averaged}
-sources are able to achieve the same accuracy as other traditional equivalent
-source layouts while using a fraction of the number of sources, and (ii) the
-\emph{gradient boosting} algorithm greatly reduces the computational memory
-required to fit very large datasets without sacrificing prediction accuracy.
-Finally, a combination of both strategies are used to process a collection of
-around 1.7 million ground gravity data measurements from Australia.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-\subsection{The equivalent sources technique}
-
-Here, we will follow the ``generalized equivalent sources'' of
-\citet{cordell1992} and assume that any harmonic function $d(\mathbf{p})$ can
-be approximated by a sum of $M$ discrete point source effects
-
-\begin{equation}
-    d(\mathbf{p})
-    =
-    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p} - \mathbf{q}_j
-    \right\rVert} \ ,
-    \label{eq:eql-forward}
-\end{equation}
-
-\noindent in which
-$\mathbf{p}$ and $\mathbf{q}_j$ are position vectors in a 3D Cartesian space,
-$c_j$ is a scalar coefficient related to the point source located at
-$\mathbf{q}_j$,
-and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.
-The horizontal and vertical distribution of sources is discussed in section~\ref{sec:source_distribution}.
-
-In case we have measured the value of the harmonic field on $N$ points
-$\{\mathbf{p}_1\ \mathbf{p}_2\ \ldots\ \mathbf{p}_N\}$,
-we can write a set of $N$ equations of the form
-
-\begin{equation}
-    d_i
-    =
-    \sum\limits_{j=1}^{M} \frac{c_j}{\left\lVert \mathbf{p}_i - \mathbf{q}_j
-    \right\rVert}
-    \quad \forall i=1,2,\ldots,N
-    \ ,
-    \label{eq:forward-sum}
-\end{equation}
-
-\noindent where $d_i$ is the value of the potential field at the observation point $\mathbf{p}_i$.
-These equations can also be expressed as
-
-\begin{equation}
-    \mathbf{d} = \mathbf{A} \mathbf{c} \ ,
-    \label{eq:linear-problem}
-\end{equation}
-
-\noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
-values of the observed field at the observation points,
-$\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,
-and $\mathbf{A}$ is the $N \times M$ Jacobian matrix,
-whose elements are
-
-\begin{equation}
-    a_{ij} = \frac{1}{\left\lVert\mathbf{p}_i - \mathbf{q}_j\right\rVert}
-\end{equation}
-
-For a given set of $N$ observed field values $\mathbf{d}^o$,
-we can find a least-squares solution to
-Eq.~\ref{eq:linear-problem} and obtain the values of
-$\mathbf{c}$ that best fit the observations.
-These values can, in turn, be used to predict the value of the harmonic field
-at any other point outside of the sources by evaluating
-Eq.~\ref{eq:eql-forward}.
-Gridding and upward continuation can thus be achieved by predicting values on
-points that fall on a regular grid or at different heights.
-
-\subsection{Damped least-squares solution}
-\label{sec:eql_inversion}
-
-We can obtain the values of the source coefficients $\mathbf{c}$ that best
-fit the observed field values $\mathbf{d}^o$ by minimizing the goal function
-
-\begin{equation}
-    \phi(\mathbf{c}) =
-    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]\trans
-    \mathbf{W}
-    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]
-    + \lambda_d\ \mathbf{c}\trans\mathbf{c}
-    \ ,
-    \label{eq:misfit-unscaled}
-\end{equation}
-
-\noindent where
-$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
-$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
-Jacobian matrix elements.
-The second term on the right-hand side of the equation is a zeroth-order
-Tikhonov regularization \citep{tikhonov1977} (also known as a damping
-regularization or ridge regression) that is used to stabilize the solution.
-
-The range of acceptable values for the damping parameter $\lambda_d$ will
-depend on the values of the Jacobian matrix $\mathbf{A}$ and the coefficients.
-Consequently, this range will vary (often dramatically) between datasets,
-making it difficult to choose an appropriate value for $\lambda_d$ in practice.
-
-To solve this issue, we first scale the Jacobian matrix so that its elements
-are unitless and each column has unit variance.
-We define a diagonal matrix $\mathbf{S}$
-
-\begin{equation}
-    \mathbf{S} =
-    \begin{bmatrix}
-      \sigma_1 & 0 & \cdots &0 \\
-      0 & \sigma_2 & \cdots &0 \\
-      \vdots & \vdots & \ddots & \vdots \\
-      0  & 0 & \cdots & \sigma_M
-    \end{bmatrix}_{M \times M}
-    ,
-\end{equation}
-
-\noindent in which $\sigma_j$ is the standard deviation of the $j$-th column of
-$\mathbf{A}$.
-We then write the forward problem in Eq.~\ref{eq:linear-problem} as
-
-\begin{equation}
-    \mathbf{d}
-    =
-    \mathbf{A} \mathbf{S}\inv \mathbf{S} \mathbf{c}
-    =
-    \left[
-        \mathbf{A} \mathbf{S}\inv
-    \right]
-    \left[
-        \mathbf{S} \mathbf{c}
-    \right]
-    =
-    \mathbf{B} \mathbf{m}
-\end{equation}
-
-\noindent where $\mathbf{B}$ is the scaled and unitless Jacobian matrix and
-$\mathbf{m}$ is a vector containing scaled coefficients with the same units as
-the data.
-
-The goal function defined in Eq.~\ref{eq:misfit-unscaled} can be
-rewritten as
-
-\begin{equation}
-    \phi(\mathbf{m}) =
-    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]\trans
-    \mathbf{W}
-    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]
-    + \lambda\ \mathbf{m}\trans\mathbf{m}
-    \ ,
-    \label{eq:misfit}
-\end{equation}
-
-\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
-regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
-$\mathbf{c}$.
-From experience, we recommend searching for suitable $\lambda$ values between
-$10^{-8}$ and $10^{2}$ varying by order-of-magnitude, irrespective of the
-dataset.
-
-The vector of scaled coefficients $\hat{\mathbf{m}}$ that minimizes the goal
-function can be found by solving the \emph{normal equation system}
-\citep{menke1989}
-
-\begin{equation}
-    \left[
-      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
-    \right]
-    \hat{\mathbf{m}} =
-    \mathbf{B}\trans\mathbf{W}
-    \mathbf{d}^o.
-    \label{eq:least_squares_solution}
-\end{equation}
-
-Once the scaled coefficients are obtained, the estimated unscaled coefficients
-$\hat{\mathbf{c}}$ can be calculated by removing the scaling factor
-
-\begin{equation}
-    \hat{\mathbf{c}} = \mathbf{S}\inv \hat{\mathbf{m}} \ .
-\end{equation}
-
-\noindent The forward modeling operations used to perform predictions
-(e.g., for interpolation and upward continuation) are left unchanged by
-using vector $\hat{\mathbf{c}}$ instead of $\hat{\mathbf{m}}$.
-
-\subsection{Gradient boosting}
-
-Gradient boosting was first introduced by \citet{friedman2001, friedman2002} as
-a method for fitting additive parametric models of the form
-
-\begin{equation}
-  d = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
-\end{equation}
-
-\noindent where $\alpha_k$ is a scalar coefficient called the \emph{step-size}
-and $f$ is a function of the parameter vector $\mathbf{c}_k$.
-For linear regression problems, these additive models can be written as the
-matrix equation
-
-\begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k \ .
-    \label{eq:gb-linear-model}
-\end{equation}
-
-We can transform our equivalent source problem in
-Eq.~\ref{eq:linear-problem} into an additive model by following these
-steps:
-
-\begin{enumerate}
-  \item Define a set of $M$ equivalent sources distributed throughout the
-    survey area (see section \ref{sec:source_distribution} for details).
-  \item Define a set of $K$ overlapping windows of equal size that cover the
-    survey area.
-  \item Create $K$ separate sets of equivalent sources, one for each window.
-    Each set will be formed by the portion of the original $M$ sources that fall inside
-    the respective window.
-    Since the windows overlap, the total number of sources
-    from all sets will be greater than $M$.
-  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
-    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
-    matrix between those sources and every data point of the survey.
-  \item Model the predicted data as a superposition of the effects of the $K$
-    separate sets of equivalent sources.
-\end{enumerate}
-
-The gradient boosting algorithm works by fitting each component of the
-additive model, one at a time, to the residuals of the previous component.
-\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
-optimization in the so-called ``function space'', with $\alpha_k$ corresponding
-to step sizes in steepest descent.
-The adaptation of the gradient boosting method to find the damped least-squares
-solutions for the $K$ parameters vectors $\mathbf{c}_k$ and step sizes
-$\alpha_k$ in Eq.~\ref{eq:gb-linear-model} is presented in
-Algorithm~\ref{alg:gradient_boosting}.
-
-\begin{algorithm}[!h]
-  \DontPrintSemicolon
-  \setstretch{1.5}
-  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
-  \For{ $k = 1$ \KwTo $K$ }{
-
-    calculate $N \times M_k$ Jacobian matrix $\mathbf{A}_k$
-    \;
-
-    $\mathbf{B}_k = \mathbf{A}_k \mathbf{S}_k\inv$
-    \nllabel{alg:scale}
-    \;
-
-    $
-     \hat{\mathbf{m}}_k = \left[\mathbf{B}_k\trans \mathbf{W}_k \mathbf{B}_k +
-     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \mathbf{W}_k
-     \mathbf{r}_{k-1}
-    $
-    \nllabel{alg:fit}
-    \;
-
-    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$
-    \nllabel{alg:unscale}
-    \;
-
-    $\mathbf{d}_k = \mathbf{A}_k \hat{\mathbf{c}}_k$
-    \nllabel{alg:predicted}
-    \;
-
-    $
-      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
-      \left(
-        \left\lVert
-          \mathbf{r}_{k - 1} - \alpha \mathbf{d}_k
-        \right\rVert ^ 2
-      \right)
-      = \dfrac{
-        \mathbf{r}_{k-1}\trans \mathbf{d}_k
-      }{
-        \mathbf{d}_k\trans \mathbf{d}_k
-      }
-    $
-    \nllabel{alg:stepsize}
-    \;
-
-    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
-    \nllabel{alg:residual}
-    \;
-  }
-  \BlankLine
-  \setstretch{1}
-  \caption{Gradient boosting solution for damped least-squares regression.}
-  \label{alg:gradient_boosting}
-\end{algorithm}
-
-After all $\alpha_k$ step sizes and $\mathbf{c}_k$ coefficients vectors
-are estimated, we can predict the effect of the additive equivalent source
-model on any point through the summation
-
-\begin{equation}
-    d(\mathbf{p}) =
-    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
-    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
-    \ ,
-\end{equation}
-
-\noindent where ${c_k}_j$ is the $j$-th element of the $\mathbf{c}_k$ vector.
-
-To improve the convergence of the algorithm, \citet{friedman2002} suggests
-introducing randomness into the fitting process. We achieve this by randomizing
-the order in which the $K$ windows are used in the gradient boosting algorithm.
-
-The $\mathbf{A}_k$ matrices have only $N \times M_k$ elements
-(where $M_k$ is the number sources on the $k-$th window), which can be
-considerably smaller than the $N \times M$ elements of $\mathbf{A}$.
-Therefore, the gradient boosting method allows us to fit
-equivalent source models that would produce Jacobian matrices that are larger
-than the available computer memory.
-Furthermore, we can increase or decrease the size of the overlapping windows as
-needed depending on the number of sources in the model and the available
-computer memory.
-
-We can improve the efficiency of the algorithm further by using only the $N_k$ data
-points that fall within the $k$-th window for fitting the sources
-(steps \ref{alg:scale} and \ref{alg:fit} of
-algorithm~\ref{alg:gradient_boosting}),
-while using all available data when calculating the step size and residuals
-(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}
-of algorithm~\ref{alg:gradient_boosting}).
-By doing so, we can reduce the size of the Jacobian matrix further to $N_k
-\times M_k$ elements.
-The forward modeling operation performed in step \ref{alg:predicted} can be
-done by a summation (Eq.~\ref{eq:forward-sum})
-instead of a matrix-vector product, which allows us to avoid computing and
-storing the larger $N \times M_k$ Jacobian at any point.
-Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
-the final \textit{gradient-boosted equivalent source algorithm}.
-
-\begin{algorithm}[!h]
-  \DontPrintSemicolon
-  \setstretch{1.5}
-  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
-  \For{ $k = 1$ \KwTo $K$ }{
-
-    select weights $\tilde{\mathbf{W}}_k$ and residuals
-    $\tilde{\mathbf{r}}_{k - 1}$ for data points inside the $k$-th window only
-    \;
-
-    calculate $N_k \times M_k$ Jacobian matrix $\tilde{\mathbf{A}}_k$
-    with data points and sources inside the $k$-th window only
-    \;
-
-    $\mathbf{B}_k = \tilde{\mathbf{A}}_k \mathbf{S}_k\inv$
-    \;
-
-    $
-     \hat{\mathbf{m}}_k = \left[
-     \mathbf{B}_k\trans \tilde{\mathbf{W}}_k \mathbf{B}_k +
-     \lambda \mathbf{I} \right]\inv \mathbf{B}_k\trans \tilde{\mathbf{W}}_k
-     \tilde{\mathbf{r}}_{k-1}
-    $
-    \;
-
-    $\hat{\mathbf{c}}_k = \mathbf{S}_k\inv \hat{\mathbf{m}}_k$
-    \;
-
-    $
-    \mathbf{d}_k \Rightarrow
-    {d_k}_i
-    =
-    \sum\limits_{j=1}^{M_k} \dfrac{{c_k}_j}{\left\lVert \mathbf{p}_i -
-        {\mathbf{q}_k}_j
-    \right\rVert}
-    \ \forall i=1\ \text{to}\ N
-    $
-    \;
-
-    $
-      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
-      \left(
-        \left\lVert
-          \mathbf{r}_{k - 1} - \alpha \mathbf{d}_k
-        \right\rVert ^ 2
-      \right)
-      = \dfrac{
-        \mathbf{r}_{k-1}\trans \mathbf{d}_k
-      }{
-        \mathbf{d}_k\trans \mathbf{d}_k
-      }
-    $
-    \;
-
-    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
-    \;
-  }
-  \BlankLine
-  \setstretch{1}
-  \caption{Gradient-boosted equivalent source algorithm.}
-  \label{alg:gradient_boosting_window}
-\end{algorithm}
-
-The influence of distance sources on the solution is maintained by using the
-entire set of data points when calculating
-the step size $\alpha_k$ and updating the residuals vector.
-In this case, the step size prevents the algorithm from worsening the fit to
-data points that fall outside of the current window.
-As such, it improves the convergence of the solution and ensures that the
-overall misfit decreases with iteration.
-
-Our gradient boosting algorithm for overlapping windows is similar to the
-``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
-fits portions of an equivalent source model to the data residuals.
-The key differences are that in our method:
-(1) the sources in the overlapping portions of the windows are
-fit more than once, allowing the algorithm to self-correct for poor solutions
-to any given window;
-(2) we use only data points within the window when fitting, what enables the
-use of larger datasets;
-(3) experience shows that the step size parameter improves the convergence of
-the solution, particularly when using only the data inside the windows for
-fitting.
-
-\subsection{Location of sources}
-\label{sec:source_distribution}
-
-The ideal number of sources and their locations, both horizontally and
-vertically, has been debated since the inception of the equivalent sources
-technique with \citet{dampney1969}.
-The choices made regarding these parameters can play an important role on the
-accuracy of the predictions and the computational resources needed to estimate
-the source coefficients.
-An ideal distribution of sources should simultaneously be able to reproduce the
-measured data on the survey points, make accurate predictions on non-surveyed
-locations, and minimize the required computational resources.
-
-A large number of evenly distributed sources along the survey region are
-capable of reproducing the observed data.
-Nevertheless, the computational load can be prohibitive and such
-underdetermined problems are prone to overfitting the data, leading to poor
-predictive power when interpolating and extrapolating.
-On the other hand, using few sources will reduce the computational requirements
-but the model may be incapable of reproducing the full spectral content of the
-measured data.
-
-Particular survey characteristics also play a role in the choice of equivalent
-source distribution.
-In a ground survey, observations are usually located along irregular paths and
-scattered points.
-The coverage of the survey region is often uneven, leaving large areas without
-any observation.
-On the other hand, observations from airborne surveys are located along almost
-straight and closely spaced flight lines.
-Measurements are usually taken at a high temporal frequency, leading to the
-observation points along the flight lines that are several times closer to each
-other than the flight line spacing.
-This creates a bias in the sampling, which can cause aliasing artifacts in
-gridded products.
-
-\subsubsection{Horizontal source layouts}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
-    \caption{
-        Sketch of different horizontal layouts for equivalent source models.
-        Blue points represent the locations of observations and orange points
-        represent the locations of equivalent sources according to different
-        layout strategies.
-        (a) Set of \SourceLayoutsSchematicsObservations{} observation points
-        that simulate a ground survey.
-        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
-        obtained through the \emph{sources-below-data} layout.
-        (c) Location of the \SourceLayoutsSchematicsGridSources{} sources
-        obtained through the \emph{regular-grid} layout.
-        (d) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
-        sources obtained through the \emph{block-averaged sources} layout.
-        Grey dashed lines represent the spatial blocks within which the median
-        observation location is calculated.
-    }
-    \label{fig:source_layouts}
-\end{figure*}
-
-The most widely used layouts for distributing equivalent sources horizontally
-are:
-
-\begin{enumerate}
-  \item
-    \emph{Sources below data points}: one equivalent source is placed at the
-    horizontal location of each data point (Fig.~\ref{fig:source_layouts}b).
-    Therefore, the number of sources is be equal to the number of observations
-    ($N=M$).
-  \item
-    \emph{Regular grid}: a homogeneous distribution of point sources below the
-    survey region (Fig.~\ref{fig:source_layouts}c). A padding region is often
-    added to help reduce edge effects. In practice, it often leads to
-    underdetermined problems since a large number of sources is required
-    ($N<M$).
-\end{enumerate}
-
-For ground surveys, the \emph{regular-grid} layout needs a sufficiently
-small grid spacing to be able to fit the observed data.
-This creates an unnecessarily large number of sources in areas where no
-observations exist.
-In contrast, the \emph{sources-below-data} layout is more likely to accurately
-fit the observed data with many fewer sources, reducing the computational load.
-But when applied to airborne surveys, the \emph{sources-below-data} layout may
-place an undesirably large number of sources along the flight paths.
-This could lead to aliasing effects on the predicted values, such as the
-stripes parallel to flight lines that are often observed when griding airborne
-magnetic data.
-The \emph{regular-grid} layout can avoid this effect by evenly
-distributing sources and using a continuous source layer (e.g.,
-right-rectangular prisms or tesseroids).
-
-We propose a new way of distributing equivalent sources horizontally that could
-simultaneously reduce the computational load and mitigate some of the drawbacks
-of existing layouts.
-In the \emph{block-averaged sources} layout,
-point sources are placed in the average
-position of data points that fall within specified spatial blocks
-(Fig.~\ref{fig:source_layouts}d).
-This is done by:
-
-\begin{enumerate}
-    \item Dividing the survey region into rectangular blocks of equal size.
-    \item Computing the median horizontal position of the observation points
-      that fall inside each block. Blocks without any observation point are
-      omitted.
-    \item Assign one point source to the median horizontal position calculated
-      in step 1.
-\end{enumerate}
-
-The number of sources created by this new layout will be less than the number
-of observations if the block size is chosen appropriately (i.e., making sure
-that blocks are large enough to contain more than a single data point).
-The overdetermined problem that arises from this layout has a lower
-computational load and is less prone to overfiting the data since the model
-complexity is lower.
-Moreover, the block averaging process can balance the spacing between sources
-along a flight line and between adjacent lines, helping to reduce aliasing
-effects in generated grids.
-We will demonstrate through tests on synthetic data that the block-averaged sources
-layout is able to interpolate with comparable accuracy to other layouts while
-using a fraction of the equivalent sources.
-
-\subsubsection{Depth of sources}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
-    \caption{
-        Examples of different strategies for assigning depths to equivalent
-        sources.
-        Here we assign one source for each
-        observation point, located at the same horizontal coordinates as the
-        data points.
-        Source depths are
-        (a)~a \emph{constant depth} at a chosen vertical coordinate,
-        (b)~a \emph{relative depth} determined by uniformly shifting the
-        vertical coordinate of data points downwards,
-        and
-        (c)~a \emph{variable depth} determined by shifting the vertical
-        coordinates of the observation points by an amount proportional to the
-        average distance to neighbouring sources.
-        The distance between data points and their respective sources (a)
-        depends on observation height, (b) is constant, and (c) is proportional
-        to the horizontal distribution of sources.
-        Notice how the closely spaced sources in the middle of the profile (c)
-        are shallower than their counterparts in (b).
-    }
-    \label{fig:depth_types}
-\end{figure*}
-
-It is widely known from potential theory that the depth of a point source
-influences the wavelength of the observed field at the surface.
-This makes the source depth a key parameter affecting the outcome of
-interpolation and other operations done with equivalent sources.
-Several different strategies for assigning the depths of equivalent sources
-have been proposed in the literature.
-Here, we will highlight the following (Fig.~\ref{fig:depth_types}):
-
-\begin{enumerate}
-  \item
-    \emph{Constant depth}:
-    The simplest option is to locate all sources at the same depth
-    (Fig.~\ref{fig:depth_types}a).
-    If the measurements were taken at significantly different altitudes, some
-    measurements will be more distant to the sources than others,
-    which may create problems for reproducing short wavelengths in high
-    altitude points.
- \item
-    \emph{Relative depth}:
-    The depths of sources are determined by shifting the vertical coordinate of
-    data points downward by a fixed amount (Fig.~\ref{fig:depth_types}b).
-    The sources will not all be at the same vertical coordinate, but they will
-    all be at the same vertical distance from the observation points.
- \item
-    \emph{Variable depth}:
-    The depths of sources are proportional to the horizontal distance to the
-    nearest neighbouring data points or sources (Fig.~\ref{fig:depth_types}c).
-    Different variations of this strategy have been proposed before, for
-    example \citet{cordell1992}, \citet{guspi2004}, and \citet{guspi2009}.
-    The rationale for this strategy is that if a survey has data points
-    clustered in some areas, we may
-    want the sources below those areas to be shallower in order to preserve the
-    shorter wavelengths that can be measured.
-\end{enumerate}
-
-Our approach to the \emph{variable depth} strategy will be:
-
-\begin{equation}
-  z = z_{obs} + \Delta z + \alpha h,
-  \label{eq:variable_depth}
-\end{equation}
-
-\noindent
-in which $z$ is the depth of an equivalent source,
-$\Delta z$ is a relative depth shift that is the same for all sources,
-$\alpha$ is an adimensional depth factor,
-$h$ is the median horizontal distance to the $k$ nearest neighbouring sources,
-and
-$z_{obs}$ is a vertical observation coordinate that will depend on the
-horizontal layout strategy.
-For \emph{sources-below-data}, it is the vertical coordinate of the data point
-corresponding to the given source.
-For \emph{regular-grid}, it can be interpolated from the vertical coordinates
-of all data points.
-Finally, for \emph{block-averaged-sources} it will be the average vertical
-coordinate of data within the corresponding block.
-
-In the following sections, we will test the effectiveness and trade-offs of
-each of these strategies on synthetic data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Tests on synthetic data}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
-    \caption{
-        Maps of the observation locations and gravity values for the synthetic
-        ground and airborne surveys.
-        (a)~Horizontal position and height of the ground survey points.
-        (b)~Synthetic gravity data calculated on the ground survey points with
-        added pseudo-random Gaussian noise.
-        (c)~Horizontal position and height of the airborne survey points.
-        (d)~Synthetic gravity data calculated on the airborne survey points
-        with added pseudo-random Gaussian noise.
-        Heights are given in meters above the zero height plane.
-    }
-    \label{fig:synthetic-layouts}
-\end{figure*}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
-    \caption{
-        Pseudo-color map of the target grid of synthetic gravity data. The grid
-        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
-        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
-        above the zero height plane.
-    }
-    \label{fig:synthetic-target}
-\end{figure}
-
-We have used synthetic gravity datasets to test the interpolation accuracy of
-the difference horizontal and vertical source distribution strategies as well
-as the gradient-boosted equivalent source method.
-To generate the data, we created a model that is made out of \NPrisms{}
-right-rectangular prisms, distributed on a region of
-\ModelEasting{}$\times$\ModelNorthing{} with depths varying between
-\ModelDepth{} and zero.
-The density contrast of prisms ranges from \ModelMinDensity{} to
-\ModelMaxDensity{}.
-The model includes prisms of different shapes, sizes, and depths to create
-gravity disturbances with a variety of wavelengths.
-
-We created two synthetic datasets from the model, one simulating a ground
-survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
-To create the synthetic ground survey, we selected measurement positions from a
-portion of a public domain dataset for Southern Africa, available through the
-NOAA National Centers for Environmental Information (NCEI).
-For the synthetic airborne survey, we used a portion of the Great Britain
-Aeromagnetic Survey acquired by Hunting Geology and Geophysics Ltd and Canadian
-Aeroservices Ltd between 1955 and 1965 and made publicly available by the
-British Geological Survey (BGS).
-In both cases, we rescaled the horizontal coordinates of each survey portion to
-span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
-dimensions.
-The ground survey contains \GroundSurveyPoints{} observations distributed at
-heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
-(Fig.~\ref{fig:synthetic-layouts}a).
-The airborne survey has \AirborneSurveyPoints{} observations at heights between
-\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
-(Fig.~\ref{fig:synthetic-layouts}c).
-
-The vertical component of the gravitational acceleration generated by the
-model was computed  using the method of \citet{nagy2000, nagy2002}
-with recent modifications by \citet{fukushima2020},
-as implemented in the open-source software Harmonica \citep{harmonica2020}.
-We generated a \emph{target grid} of
-\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
-\TargetSpacing{} and located \TargetHeight{} above the zero height plane
-(Fig.~\ref{fig:synthetic-target}) to serve as a reference when calculating the
-interpolation error.
-We then generated synthetic ground (Fig.~\ref{fig:synthetic-layouts}b) and
-airborne (Fig.~\ref{fig:synthetic-layouts}d) data to which we added
-pseudo-random Gaussian noise with zero mean and \SurveyNoise{} standard
-deviation.
-
-\subsection{Source distribution strategies}
-\label{sec:synthetic_distributions}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
-    \caption{
-        Pseudo-color maps of the differences between the target grid and the
-        interpolated synthetic ground survey data produced by each source
-        distribution strategy.
-        The black dots represent the horizontal location of the synthetic data
-        points. The RMS error and total number of equivalent sources is
-        reported for each strategy at the top of the respective maps.
-    }
-    \label{fig:ground-survey-differences}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
-    \caption{
-        Pseudo-color maps of the differences between the target grid and the
-        interpolated synthetic airborne survey data produced by each source
-        distribution strategy.
-        The black dots represent the horizontal location of the synthetic data
-        points. The RMS error and total number of equivalent sources is
-        reported for each strategy at the top of the respective maps.
-    }
-    \label{fig:airborne-survey-differences}
-\end{figure*}
-
-We investigated the effect of different strategies for distributing the
-equivalent sources horizontally and vertically on interpolation accuracy.
-To do this, we used the damped least-squares solution described in
-Section~\ref{sec:eql_inversion} (without gradient boosting) to interpolate the
-synthetic datasets (Fig.~\ref{fig:synthetic-layouts}) and compared the results
-against the target grid (Fig.~\ref{fig:synthetic-target}).
-This process was repeated for each combination of horizontal layout
-(sources-below-data and block-averaged-sources) and depth type (constant,
-relative, and variable) and for regular-grid sources with a constant depth,
-totalling 7 different combinations.
-
-Each source distribution strategy requires certain hyper-parameters to be
-chosen in order to build the set of point sources.
-For example, using a constant depth needs the definition of the depth and using
-block-average-sources requires the definition of the block size.
-The predictive capabilities of the equivalent sources depend on the choice of
-these hyper-parameters.
-To ensure that our comparisons are fair, we perform an exhaustive search over
-combinations of hyper-parameter values (including the damping parameter from
-Eq.~\ref{eq:misfit}) to obtain the best prediction that can be achieved by each
-source distribution strategy.
-Here, the best prediction is defined as the one that minimizes the root
-mean-square error (RMS) between interpolated values and the target grid
-(Fig.~\ref{fig:synthetic-target}).
-The parameter values used in these searches and the one producing the smallest
-RMS error are outlined in Tables~\ref{tab:parameters-ground-survey}
-and~\ref{tab:parameters-airborne-survey}.
-
-Fig~\ref{fig:ground-survey-differences}
-and~\ref{fig:airborne-survey-differences} show the differences between the
-target grid and the best prediction achieved by each source distribution
-strategy for the ground and airborne synthetic surveys, respectively.
-For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of approximately 0.8~mGal regardless of the depth type, with the
-exception of the regular-grid layout which produced a larger RMS of
-\BestGroundGridSourcesConstantDepthRms{}~mGal.
-The differences between the target grid and the interpolated values are larger
-in regions of poor data coverage.
-Edge effects are present for all strategies but are noticeably smaller for the
-combination of block-averaged-sources with a variable depth based on the
-nearest neighbour distance.
-For the synthetic airborne survey, all strategies (including the regular-grid)
-produced similar RMS errors of approximately 0.3~mGal.
-The maps of the differences between the target grid and interpolation results
-are visually indistinguishable from each other.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Window size and overlap in gradient boosting}
-
-We assessed the trade-offs in interpolation accuracy and computation time of
-the gradient-boosted equivalent sources algorithm as a function of the two key
-controlling factors: the window size and the amount of overlap between adjacent
-windows.
-The comparisons were performed against a regular least-squares solution
-(Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
-(Fig.~\ref{fig:synthetic-layouts}c-d) .
-To avoid biasing the results, we used the same locations of equivalent sources
-for both the regular and gradient-boosted interpolations, namely
-block-averaged-sources with a block size of
-\BestAirborneBlockAveragedSourcesRelativeDepthSpacing~m and a
-relative depth of
-\BestAirborneBlockAveragedSourcesRelativeDepthDepth~m.
-
-\subsubsection{Window size}
-\label{sec:window_size}
-
-The size of the windows controls the size of the Jacobian matrices
-$\tilde{\mathbf{A}}_k$ by limiting the number of data points and equivalent
-sources used in each step of the gradient-boosting algorithm
-(Alg.~\ref{alg:gradient_boosting_window}).
-Thus, using smaller windows will reduce the total amount of computer memory
-required to estimate the source coefficients.
-Nevertheless, smaller windows may produce less accurate interpolations by
-failing to achieve the global minimum of the goal function in
-Eq.~\ref{eq:misfit}.
-The window size might also impact the computation time in non-intuitive ways
-since smaller windows generate smaller least-squares problems but also require
-more gradient-boosting iterations.
-
-We calculated the interpolation RMS error and computation time for a fixed
-window overlap of 50\% and several window sizes.
-To avoid any biases introduced by the shuffling of windows, the calculations
-were repeated using different seeds for the pseudo-random number generator used
-in the shuffling.
-Figs.~\ref{fig:gradient-boosted-comparison}a and
-\ref{fig:gradient-boosted-comparison}c show the RMS error and computation time
-required for estimating the source coefficients, respectively, as a function of
-the window size.
-
-The results show that the interpolation RMS error for gradient-boosting is
-generally larger than the error for regular equivalent sources.
-The error decreases asymptotically to within $\sim 40\%$ of the regular
-equivalent sources for windows with an area greater than $\sim 10\%$ of the
-survey area.
-The computation time similarly decreases with window size, with the
-gradient-boosting being generally faster than the regular equivalent sources
-for windows with an area greater than $\sim 5\%$ of the survey area.
-As the window size increases, both RMS error and computation time appear to
-stabilize to nearly constant levels.
-
-\subsubsection{Window overlap}
-
-The amount of overlap between adjacent windows plays an important role in the
-performance of the gradient-boosted equivalent sources.
-It controls the number of iterations and how often a particular source is used
-in the least-squares fitting process.
-While the experiments in the previous section showed that 50\% overlap was
-sufficient to achieve acceptable interpolation accuracy, we separately studied
-the impacts of the amount of window overlap on both accuracy and computation
-time.
-
-We performed a similar experiment to one in section~\ref{sec:window_size} but
-this time kept the window size fixed to \BoostOverlappingWindowSize{} and
-varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
-All other experimental procedures remained unchanged.
-Figs.~\ref{fig:gradient-boosted-comparison}b and
-\ref{fig:gradient-boosted-comparison}d show the RMS error and computation time
-required for estimating the source coefficients, respectively, as a function of
-the window overlap.
-
-Our results show what the interpolation RMS error decreases with the amount of
-overlap, reaching the same accuracy as the regular equivalent sources at
-approximately 90\% overlap.
-On the other hand, the computation time increases with the amount of overlap,
-becoming larger than that of the regular equivalent sources for overlaps
-greater than 70\%.
-This is expected since increasing the overlap adds iterations to the gradient
-boosting algorithm without decreasing the individual least-squares problem
-sizes to compensate.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
-    \caption{
-        Comparison of the interpolation RMS error and computation time for
-        regular least-squares equivalent sources (orange dashed lines) and
-        gradient-boosted equivalent sources (blue dots and error bars).
-        Both methods used the same source positions (block-averaged sources
-        with a relative depth).
-        Window sizes are given as a percentage of the survey area (e.g., 100\%
-        represents a window with the same area as the survey) and window
-        overlap is given as a percentage of the window size
-        (an overlap of 50\% means that two adjacent windows
-        share an area half of the size of the entire window).
-        Computation time refers to the time required to estimate the source
-        coefficients and is reported as a ratio between the gradient-boosted
-        and the regular equivalent sources.
-        For gradient-boosting, the RMS errors and computation times are the
-        means (error bars represent 1 standard deviation) of results using
-        different seeds for the pseudo-random number generator.
-        (a)~RMS error between the target grid and interpolation results and
-        (b)~computation time as a function of window size.
-        (c)~RMS error between the target grid and interpolation results and
-        (d)~computation time as a function of window overlap.
-}
-    \label{fig:gradient-boosted-comparison}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Gridding gravity data from Australia}
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/australia.png}
-    \caption{
-      Pseudo-color maps of observed (left) and
-      interpolated (right) gravity disturbance of Australia.
-      Observations are part of a compilation by \citet{wynne2018} of
-      over 1.7 million ground gravity measurements.
-      Interpolated values were obtained through gradient-boosted equivalent
-      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
-      over the WGS84 ellipsoid.
-    }
-    \label{fig:australia}
-\end{figure*}
-
-This section will demonstrate how gradient-boosted equivalent sources can be
-used to interpolate large datasets of gravity data onto a regular grid at
-uniform height.
-For this purpose, we selected an open-access compilation of ground gravity
-surveys over Australia made by \citet{wynne2018} and filtered and referenced to
-the WGS84 ellipsoid by \citet{australia_compilation}.
-It contains over 1.7 million data points and covers most of the Australian
-territory at variable point spacings.
-Our goal is to create a 1~arc-minute resolution grid of gravity disturbances at
-a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
-observations).
-
-We computed the gravity disturbance by removing the normal gravity of
-the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
-Here, normal gravity was computed at each observation point through the
-closed-form formula of \citet{ligotze2001} using the Boule software
-\citep{boule2020}.
-Finally, we converted the observations to planar Cartesian coordinates by
-applying a Mercator projection.
-
-We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block size of
-1.8~km, resulting in a total of \AustraliaEqlNSources{}~point
-sources.
-The block size was chosen to match the desired resolution of the final grid
- (1~arc-minute is approximately 1.8~km at the equator).
-The coefficients of the gradient-boosted equivalent sources are estimated using
-a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
-computer memory needed to store the Jacobian matrix to under 10~Gigabytes.
-Finally, we used the estimated source coefficients to predict the values of the
-gravity disturbance on a regular grid of
-\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
-\AustraliaEqlGridHeight{} above the ellipsoid.
-Fig.~\ref{fig:australia} shows the original data distribution and the
-interpolated regular grid.
-Grid points that are further than 50~km from the nearest data
-point are masked to avoid unrealistic extrapolations.
-
-The resulting grid preserves the high resolution of the original data while
-avoiding aliasing artifacts because to the block averaging.
-Some parts of the grid are smoother and with reduced amplitude (e.g., some
-southwestern parts), which is expected from the upward continuation that was
-performed to have the grid at a constant height.
-On a modest workstation with 16 cores and 16~Gigabytes of RAM,
-estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
-$\sim 1.3$~hours and the forward modelling step took $\sim 18$~minutes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-
-\subsection{Location of sources}
-
-The results of our tests on synthetic data
-(Figs~\ref{fig:ground-survey-differences}
-and~\ref{fig:airborne-survey-differences}) show that there are no significant
-differences between source distribution strategies, both in terms of the
-interpolation RMS errors and from visual inspection of the difference maps.
-Therefore, we argue that all source distribution strategies are able to produce
-comparably accurate interpolations.
-Nevertheless, the \emph{block-averaged-sources} strategy make use of fewer
-sources when compared with other strategies, which reduces the computational
-load of estimating the sources coefficients and forward modelling.
-To ensure that the interpolation is able to reproduce the high frequencies in
-the data, the block size used in the averaging should be chosen to match the
-desired grid resolution.
-
-The choice of source depth strategy does not appear to significantly impact the
-interpolation RMS error.
-In the particular case of a sparse ground survey with block-averaged-sources,
-the use of a variable depth visibly reduced edge effects and artifacts in areas
-of poor data coverage.
-At a first glance, the choice of a depth strategy would not seem to impact
-the computation time.
-However, when searching for the set of hyper-parameters that produce the most
-accurate interpolation (e.g., through cross-validation), one must solve the
-inverse problem once for every possible combination of parameters.
-A depth strategy like the \emph{variable depth} requires a higher number of
-hyper-parameters (depth shift $\Delta z$, depth factor $\alpha$, and the number
-of nearest neighbours $k$ from Eq.~\ref{eq:variable_depth}) than other
-strategies which only require a single parameter.
-Having more parameters means increasing the dimensions of the parameter space
-and thus increasing the number of possible combinations.
-Thus, we recommend using a \emph{constant depth} or a \emph{relative depth}
-when processing large datasets in order to minimize computation time.
-
-\subsection{Gradient boosting}
-
-From Fig.~\ref{fig:gradient-boosted-comparison}a
-and~\ref{fig:gradient-boosted-comparison}c, we can see that the
-gradient-boosted equivalent sources produce slightly less accurate
-interpolation results but are able to achieve smaller computation times than
-regular equivalent sources.
-The reduction of the accuracy might be due to the gradient boosting algorithm
-failing to converge to the global minimum of the goal function.
-As the windows increase in size, interpolation error decreases because more data
-points are included into the least-squares fitting of the source coefficients.
-At the same time, the fitting process becomes faster because of a reduction in
-the number of iterations.
-Our results indicate that it is desirable to maximize the window size up to the
-point that the Jacobian matrices still fit within the available computer
-memory.
-
-The results shown in Figs~\ref{fig:gradient-boosted-comparison}b
-and~\ref{fig:gradient-boosted-comparison}d indicate that using
-window overlap values between 40\% and 70\% strike a balance between
-accuracy and computation time.
-This corroborates our initial choice of 50\% overlap, which is good enough for
-producing accurate predictions in reasonable times.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusions}
-
-The equivalent source technique has been proven to be well suited for
-interpolating gravity disturbances and magnetic anomalies.
-The two main reasons that make it to stand out from other 2D interpolation
-methods is the fact that the equivalent sources take into account the height of
-the observations and that the interpolated values will always be harmonic
-functions.
-The main challenge of using equivalent sources in practice is the high
-computational load of estimating the coefficients of the equivalent sources,
-specially on the computer memory needed to store the Jacobian matrix.
-In this work we present two strategies that could be simultaneously applied in
-order to interpolate very large datasets (millions of points) in reasonable
-computation times on modest hardware:
-block-averaging source locations, which reduce the number of equivalent sources
-needed for the interpolation,
-and the gradient-boosted equivalent source algorithm, which breaks down the
-inverse problem into smaller sets of equivalent sources defined by overlapping
-windows.
-Both methods were tested against synthetic datasets in order to compare their
-accuracy and how they perform in terms of computational resources.
-
-Our results show that the block-averaged sources reduce the computational
-load needed to estimate source coefficients in comparison to the two traditional
-strategies of placing sources below data points or on regular grids.
-We also showed that this reduction of the number of sources does not affect
-the accuracy of the predictions.
-The use of block-averaged sources may also prevent aliasing of the interpolated
-values, specially when the observations are unevenly sampled (e.g., airborne
-and shipborne surveys).
-Special attention must be payed when choosing the size of the blocks for
-averaging: as a thumb rule, we recommend choosing a size approximately equal to
-the resolution of the regular grid where the values will be interpolated.
-
-Tests that compared strategies for the vertical location of the
-sources showed that any one of the three strategies tested
-(\emph{constant depth}, \emph{relative depth} and \emph{variable depth})
-produces comparable accuracy of interpolation.
-Nevertheless, we are more prone to recommending either the \emph{constant
-depth} or the \emph{relative depth} for most applications because they involve
-less hyper-parameters that would need to be configured before the actual
-interpolation.
-
-Gradient-boosted equivalent sources were shown to heavily reduce the computer
-memory needed to estimate source coefficients, making it possible to
-interpolate large datasets with millions of points that would otherwise produce
-Jacobian matrices larger than the available memory.
-The interpolations obtained though this new method achieve close to the same
-accuracy than the regular equivalent sources, while reducing the computation
-time needed to estimate the source coefficients by approximately three times.
-We also show that an overlap of 50\% between adjacent windows achieves a good
-compromise between accuracy and computation time.
-The size of the overlapping windows should be chosen as the maximum value
-possible that creates Jacobian matrices that still fit into computer memory.
-
-The gradient-boosting method developed here can be used in conjunction with any
-horizontal source layout, depth strategy, or source type (e.g., point sources,
-prisms, tesseroids) because it does not rely on assumptions about the sources.
-Future research should investigate the application of gradient boosting to
-other equivalent source methods.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Data and code availability}
-
-The Python source code used to produce all results and figures presented here
-is available at
-\url{https://doi.org/10.6084/m9.figshare.13604360} and
-\url{https://github.com/compgeolab/eql-gradient-boosted}
-under the BSD 3-clause open-source license.
-
-The gradient-boosted equivalent sources implementation is based on the
-equivalent source code in the Harmonica library \citep{harmonica2020}.
-Other software used in this study includes:
-Pooch \citep{pooch2020} for downloading and caching datasets,
-Verde \citep{verde2018} for block reductions and coordinate manipulations,
-Boule \citep{boule2020} for normal gravity calculations,
-xarray \citep{xarray2017} and Numpy \citep{numpy2020} for multidimensional
-arrays and numerical computations,
-Numba \citep{numba2015} for just-in-time compilation and parallelization,
-Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
-the figures and maps,
-and the Jupyter notebook programming environment \citep{jupyter2016}.
-Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
-\citep{fatiando2013}.
-
-All datasets used are open-access and publicly available.
-The synthetic surveys were generated using
-a public domain gravity dataset for Southern Africa distributed by the
-NOAA NCEI (\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html})
-and the Great Britain Aeromagnetic
-Survey distributed by the
-British Geological Survey (BGS) under an Open Government License
-(\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}).
-The shaded relief in Fig.~\ref{fig:australia} is the SRTM15+ dataset by
-\citet{tozer2019}.
-The Australian ground gravity
-data is based on a compilation distributed by Geoscience Australia under a
-Creative Commons Attribution 4.0 International Licence \citep{wynne2018}  which
-was filtered and referenced to the WGS84 ellipsoid by
-\citet{australia_compilation} and is distributed under the same license
-(\url{https://doi.org/10.6084/m9.figshare.13643837}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Acknowledgements}
-
-We are indebted to the developers and maintainers of the open-source software
-without which this work would not have been possible.
-S.R. Soler is supported by a scholarship from CONICET, Argentina.
-Contains British Geological Survey materials © UKRI.
-
-S.R. Soler and L. Uieda jointly developed the initial idea, analysed the
-results, and wrote the paper. S.R. Soler produced all results and developed the
-software implementation with minor revisions by L. Uieda.
+\input{content.tex}
 
@@
 
-\appendix
-
-\section{Source position parameters used for the tests on synthetic data}
-
-Tables~\ref{tab:parameters-ground-survey}
-and~\ref{tab:parameters-airborne-survey} show the parameter values tested and
-their optimal values for creating the equivalent source distributions tested in
-Section~\ref{sec:synthetic_distributions}.
-The optimal values were used to produce the results in
-Figs~\ref{fig:ground-survey-differences}
-and~\ref{fig:airborne-survey-differences}.
-
-\begin{table*}
-    \centering
-    \caption{
-        Parameters used to produce each source distribution for interpolating
-        the synthetic ground survey data. Also contains the set of parameters
-        that generates the smallest RMS error for each source distribution and
-        their corresponding RMS.
-    }
-    \label{tab:parameters-ground-survey}
-    \begin{tabular}{c c l c c c}
-        \textbf{Source layout}
-            & \textbf{Depth type}
-            & \multicolumn{1}{c}{\textbf{Parameters}}
-            & \textbf{Values}
-            & \textbf{Best}
-            & \textbf{RMS} \\
-        \toprule
-
-        \multirow{8}{*}{Source Below Data}
-            & \multirow{2}{*}{Constant}
-                & Depth (m)
-                & \GroundSourceBelowDataConstantDepthDepth
-                & \BestGroundSourceBelowDataConstantDepthDepth
-                & \multirow{2}{*}{
-                    \BestGroundSourceBelowDataConstantDepthRms
-                  } \\
-            &
-                & Damping
-                & \GroundSourceBelowDataConstantDepthDamping
-                & \BestGroundSourceBelowDataConstantDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{2}{*}{Relative}
-                & Depth (m)
-                & \GroundSourceBelowDataRelativeDepthDepth
-                & \BestGroundSourceBelowDataRelativeDepthDepth
-                & \multirow{2}{*}{
-                    \BestGroundSourceBelowDataRelativeDepthRms
-                  } \\
-            &
-                & Damping
-                & \GroundSourceBelowDataRelativeDepthDamping
-                & \BestGroundSourceBelowDataRelativeDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{4}{*}{Variable}
-                & Depth (m)
-                & \GroundSourceBelowDataVariableDepthDepth
-                & \BestGroundSourceBelowDataVariableDepthDepth
-                & \multirow{4}{*}{
-                    \BestGroundSourceBelowDataVariableDepthRms
-                  } \\
-            &
-                & Depth factor
-                & \GroundSourceBelowDataVariableDepthDepthFactor
-                & \BestGroundSourceBelowDataVariableDepthDepthFactor
-                & \\
-            &
-                & $k$ neighbours
-                & \GroundSourceBelowDataVariableDepthKNearest
-                & \BestGroundSourceBelowDataVariableDepthKNearest
-                & \\
-            &
-                & Damping
-                & \GroundSourceBelowDataVariableDepthDamping
-                & \BestGroundSourceBelowDataVariableDepthDamping
-                & \\
-        \midrule
-
-        \multirow{11}{*}{Block Averaged Sources}
-            & \multirow{3}{*}{Constant}
-                & Depth (m)
-                & \GroundBlockAveragedSourcesConstantDepthDepth
-                & \BestGroundBlockAveragedSourcesConstantDepthDepth
-                & \multirow{3}{*}{
-                    \BestGroundBlockAveragedSourcesConstantDepthRms
-                  } \\
-            &
-                & Block size (m)
-                & \GroundBlockAveragedSourcesConstantDepthSpacing
-                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockAveragedSourcesConstantDepthDamping
-                & \BestGroundBlockAveragedSourcesConstantDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{3}{*}{Relative}
-                & Depth (m)
-                & \GroundBlockAveragedSourcesRelativeDepthDepth
-                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
-                & \multirow{3}{*}{
-                    \BestGroundBlockAveragedSourcesRelativeDepthRms
-                  } \\
-            &
-                & Block size (m)
-                & \GroundBlockAveragedSourcesRelativeDepthSpacing
-                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockAveragedSourcesRelativeDepthDamping
-                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{5}{*}{Variable}
-                & Depth (m)
-                & \GroundBlockAveragedSourcesVariableDepthDepth
-                & \BestGroundBlockAveragedSourcesVariableDepthDepth
-                & \multirow{5}{*}{
-                    \BestGroundBlockAveragedSourcesVariableDepthRms
-                  } \\
-            &
-                & Depth factor
-                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
-                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
-                & \\
-            &
-                & $k$ neighbours
-                & \GroundBlockAveragedSourcesVariableDepthKNearest
-                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
-                & \\
-            &
-                & Block size (m)
-                & \GroundBlockAveragedSourcesVariableDepthSpacing
-                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundBlockAveragedSourcesVariableDepthDamping
-                & \BestGroundBlockAveragedSourcesVariableDepthDamping
-                & \\
-        \midrule
-
-        \multirow{4}{*}{Grid Sources}
-            & \multirow{4}{*}{Constant}
-                & Depth (m)
-                & \GroundGridSourcesConstantDepthDepth
-                & \BestGroundGridSourcesConstantDepthDepth
-                & \multirow{4}{*}{
-                    \BestGroundGridSourcesConstantDepthRms
-                  } \\
-            &
-                & Grid spacing (m)
-                & \GroundGridSourcesConstantDepthSpacing
-                & \BestGroundGridSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \GroundGridSourcesConstantDepthDamping
-                & \BestGroundGridSourcesConstantDepthDamping
-                & \\
-    \end{tabular}
-\end{table*}
-
-\begin{table*}
-    \centering
-    \caption{
-        Parameters used to produce each source distribution for interpolating
-        the synthetic airborne survey data. Also contains the set of parameters
-        that generates the smallest RMS error for each source distribution and
-        their corresponding RMS.
-    }
-    \label{tab:parameters-airborne-survey}
-    \begin{tabular}{c c l c c c}
-        \textbf{Source layout}
-            & \textbf{Depth type}
-            & \multicolumn{1}{c}{\textbf{Parameters}}
-            & \textbf{Values}
-            & \textbf{Best}
-            & \textbf{RMS} \\
-        \toprule
-
-        \multirow{8}{*}{Source Below Data}
-            & \multirow{2}{*}{Constant}
-                & Depth (m)
-                & \AirborneSourceBelowDataConstantDepthDepth
-                & \BestAirborneSourceBelowDataConstantDepthDepth
-                & \multirow{2}{*}{
-                    \BestAirborneSourceBelowDataConstantDepthRms
-                  } \\
-            &
-                & Damping
-                & \AirborneSourceBelowDataConstantDepthDamping
-                & \BestAirborneSourceBelowDataConstantDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{2}{*}{Relative}
-                & Depth (m)
-                & \AirborneSourceBelowDataRelativeDepthDepth
-                & \BestAirborneSourceBelowDataRelativeDepthDepth
-                & \multirow{2}{*}{
-                    \BestAirborneSourceBelowDataRelativeDepthRms
-                  } \\
-            &
-                & Damping
-                & \AirborneSourceBelowDataRelativeDepthDamping
-                & \BestAirborneSourceBelowDataRelativeDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{4}{*}{Variable}
-                & Depth (m)
-                & \AirborneSourceBelowDataVariableDepthDepth
-                & \BestAirborneSourceBelowDataVariableDepthDepth
-                & \multirow{4}{*}{
-                    \BestAirborneSourceBelowDataVariableDepthRms
-                  } \\
-            &
-                & Depth factor
-                & \AirborneSourceBelowDataVariableDepthDepthFactor
-                & \BestAirborneSourceBelowDataVariableDepthDepthFactor
-                & \\
-            &
-                & $k$ neighbours
-                & \AirborneSourceBelowDataVariableDepthKNearest
-                & \BestAirborneSourceBelowDataVariableDepthKNearest
-                & \\
-            &
-                & Damping
-                & \AirborneSourceBelowDataVariableDepthDamping
-                & \BestAirborneSourceBelowDataVariableDepthDamping
-                & \\
-        \midrule
-
-        \multirow{11}{*}{Block Averaged Sources}
-            & \multirow{3}{*}{Constant}
-                & Depth (m)
-                & \AirborneBlockAveragedSourcesConstantDepthDepth
-                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
-                & \multirow{3}{*}{
-                    \BestAirborneBlockAveragedSourcesConstantDepthRms
-                  } \\
-            &
-                & Block size (m)
-                & \AirborneBlockAveragedSourcesConstantDepthSpacing
-                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockAveragedSourcesConstantDepthDamping
-                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{3}{*}{Relative}
-                & Depth (m)
-                & \AirborneBlockAveragedSourcesRelativeDepthDepth
-                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
-                & \multirow{3}{*}{
-                    \BestAirborneBlockAveragedSourcesRelativeDepthRms
-                  } \\
-            &
-                & Block size (m)
-                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
-                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockAveragedSourcesRelativeDepthDamping
-                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
-                & \\
-            \cmidrule{2-6}
-            & \multirow{5}{*}{Variable}
-                & Depth (m)
-                & \AirborneBlockAveragedSourcesVariableDepthDepth
-                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
-                & \multirow{5}{*}{
-                    \BestAirborneBlockAveragedSourcesVariableDepthRms
-                  } \\
-            &
-                & Depth factor
-                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
-                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
-                & \\
-            &
-                & $k$ neighbours
-                & \AirborneBlockAveragedSourcesVariableDepthKNearest
-                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
-                & \\
-            &
-                & Block size (m)
-                & \AirborneBlockAveragedSourcesVariableDepthSpacing
-                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneBlockAveragedSourcesVariableDepthDamping
-                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
-                & \\
-        \midrule
-
-        \multirow{4}{*}{Grid Sources}
-            & \multirow{4}{*}{Constant}
-                & Depth (m)
-                & \AirborneGridSourcesConstantDepthDepth
-                & \BestAirborneGridSourcesConstantDepthDepth
-                & \multirow{4}{*}{
-                    \BestAirborneGridSourcesConstantDepthRms
-                  } \\
-            &
-                & Grid spacing (m)
-                & \AirborneGridSourcesConstantDepthSpacing
-                & \BestAirborneGridSourcesConstantDepthSpacing
-                & \\
-            &
-                & Damping
-                & \AirborneGridSourcesConstantDepthDamping
-                & \BestAirborneGridSourcesConstantDepthDamping
-                & \\
-    \end{tabular}
-\end{table*}
+\input{appendix.tex}
 

### 2021-02-02 notebooks/98-generate_latex_variables.py

@@ -103,7 +103,7 @@ def best_parameters_to_latex(parameters, survey):
 # ## Define results and manuscript directories
 
 results_dir = Path("..") / "results"
-manuscript_dir = Path("..") / "manuscript"
+manuscript_dir = Path("..") / "manuscript" / "results"
 ground_results_dir = results_dir / "ground_survey"
 airborne_results_dir = results_dir / "airborne_survey"
 

### 2021-02-02 manuscript/manuscript.tex
Ditch siunitx (#114)
After the problems faced on #113 related to incompatibilities between siunitx and gji, I'm considering ditching siunitx by defining the values and units through Python instead of leaving the process to the macros in siunitx.

--- 2021-01-29 manuscript/manuscript.tex
@@
 \newcommand{\trans}{^{\text{T}}}
+
+% Define some units
+\newcommand{\m}{$\,$m}
+\newcommand{\km}{$\,$km}
+\newcommand{\mGal}{$\,$mGal}
 
@@
 For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of approximately 0.8~mGal regardless of the depth type, with the
+values of approximately 0.8\mGal regardless of the depth type, with the
 exception of the regular-grid layout which produced a larger RMS of
-\BestGroundGridSourcesConstantDepthRms{}~mGal.
+\BestGroundGridSourcesConstantDepthRms{}\mGal.
 The differences between the target grid and the interpolated values are larger
@@
 For the synthetic airborne survey, all strategies (including the regular-grid)
-produced similar RMS errors of approximately 0.3~mGal.
+produced similar RMS errors of approximately 0.3\mGal.
 The maps of the differences between the target grid and interpolation results
@@
 block-averaged-sources with a block size of
-\BestAirborneBlockAveragedSourcesRelativeDepthSpacing~m and a
+\BestAirborneBlockAveragedSourcesRelativeDepthSpacing\m and a
 relative depth of
-\BestAirborneBlockAveragedSourcesRelativeDepthDepth~m.
+\BestAirborneBlockAveragedSourcesRelativeDepthDepth\m.
 
@@
 at a relative depth of \AustraliaEqlDepth{} and a block size of
-1.8~km, resulting in a total of \AustraliaEqlNSources{}~point
+1.8\km, resulting in a total of \AustraliaEqlNSources{}~point
 sources.
 The block size was chosen to match the desired resolution of the final grid
- (1~arc-minute is approximately 1.8~km at the equator).
+ (1~arc-minute is approximately 1.8\km at the equator).
 The coefficients of the gradient-boosted equivalent sources are estimated using
@@
 interpolated regular grid.
-Grid points that are further than 50~km from the nearest data
+Grid points that are further than 50\km from the nearest data
 point are masked to avoid unrealistic extrapolations.

### 2021-02-02 notebooks/boost_and_layouts/__init__.py

@@ -8,6 +8,7 @@ from .latex_variables import (
     create_loglist,
     list_to_latex,
     format_variable_name,
+    format_power_of_ten,
 )
 from .utils import (
     save_to_json,

### 2021-02-02 notebooks/boost_and_layouts/latex_variables.py

@@ -1,6 +1,7 @@
 """
 Function to define LaTeX variables
 """
+import re
 import numpy as np
 
 
@@ -13,10 +14,8 @@ def create_latex_variable(variable_name, value, unit=None, fmt="5g"):
         value = value_to_string(value, fmt)
     if unit:
         unit = format_unit(unit)
-        tex_string = (
-            r"\newcommand{{\{variable_name}}}{{\SI{{{value}}}{{{unit}}}}}".format(
-                variable_name=variable_name, value=value, unit=unit
-            )
+        tex_string = r"\newcommand{{\{variable_name}}}{{${value} \, {unit}$}}".format(
+            variable_name=variable_name, value=value, unit=unit
         )
     else:
         tex_string = r"\newcommand{{\{variable_name}}}{{{value}}}".format(
@@ -43,9 +42,28 @@ def format_variable_name(name):
 
 def format_unit(unit):
     """
-    Format unit string to work well with SIunits LaTeX packcage
+    Format unit string to LaTeX
     """
-    return " ".join(["\\" + u for u in unit.strip().split()])
+    # Define regex pattern for units as alphabetic characters followed by
+    # a positive or negative int.
+    unit_pattern = r"^[a-zA-Z]+-?(\d+)?$"
+    # Get each unit from the passed string
+    splits = unit.strip().split()
+    # Generate the LaTeX units
+    units = []
+    for split in splits:
+        # Check if the passed unit has the valid format
+        if not re.match(unit_pattern, split):
+            raise ValueError("Invalid unit '{}'.".format(split))
+        # Take the alphabetic characters of the unit and its power (if exists)
+        alpha = re.findall("[a-zA-Z]+", split)[0]
+        power = re.findall(r"-?\d+", split)
+        # Build LaTeX unit
+        unit_tex = r"\text{{{}}}".format(alpha)
+        if power:
+            unit_tex += "^{{{}}}".format(power[0])
+        units.append(unit_tex)
+    return r" \, ".join(units)
 
 
 def list_to_latex(values, max_list_items=4, fmt="5g"):
@@ -64,6 +82,16 @@ def list_to_latex(values, max_list_items=4, fmt="5g"):
         return create_numlist(values, fmt)
 
 
+def create_numlist(values, fmt):
+    """
+    Create a numlist out of a list of values
+
+    Intended to represent a list of random values.
+    """
+    values = [value_to_string(v, fmt) for v in values]
[…]

### 2021-02-02 notebooks/boost_and_layouts/test_latex_variables.py

@@ -1,0 +1,120 @@
+"""
+Test functions to create LaTeX variables
+"""
+import pytest
+from .latex_variables import (
+    format_power_of_ten,
+    create_latex_variable,
+    list_to_latex,
+    create_loglist,
+    format_unit,
+)
+
+
+def test_power_of_ten():
+    """
+    Test format_power_of_ten
+    """
+    assert format_power_of_ten(1e2) == "10$^{2}$"
+    assert format_power_of_ten(1e-5) == "10$^{-5}$"
+    assert format_power_of_ten(1e10) == "10$^{10}$"
+    assert format_power_of_ten(1e-10) == "10$^{-10}$"
+    assert format_power_of_ten(1e0) == "1"
+    with pytest.raises(ValueError):
+        format_power_of_ten(3.14)
+
+
+def test_latex_variable():
+    """
+    Test create_latex_variable
+    """
+    assert (
+        create_latex_variable("my_variable", 3.1416, unit=None)
+        == r"\newcommand{\MyVariable}{3.1416}"
+    )
+    assert (
+        create_latex_variable("my_other_variable", 3.141592653589793, unit=None)
+        == r"\newcommand{\MyOtherVariable}{3.14159}"
+    )
+    assert (
+        create_latex_variable("my_length", 5400, unit="m")
+        == r"\newcommand{\MyLength}{$5400 \, \text{m}$}"
+    )
+    assert (
+        create_latex_variable("my_area", 200, unit="m2")
+        == r"\newcommand{\MyArea}{$200 \, \text{m}^{2}$}"
+    )
+    assert (
+        create_latex_variable("my_density", 2670, unit="kg m-3")
+        == r"\newcommand{\MyDensity}{$2670 \, \text{kg} \, \text{m}^{-3}$}"
+    )
+
+
+def test_list_to_latex():
+    """
+    Test list_to_latex
+    """
+    # Check if passing a equidistant list works as expected
+    values = [1, 2, 3, 4]  # a short list
+    assert list_to_latex(values) == "1, 2, 3 and 4"
+    values = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10]  # a long list
+    assert list_to_latex(values) == "1 to 10, step size 1"
+    # Check if passing a random list works as expected
+    values = [1, 3, 8, 12]
[…]

### 2021-02-02 manuscript/abstract.tex
Apply GJI style to manuscript and refactor it (#115)
Refactor manuscript by splitting it into several files. Create
a manuscript-gji.tex file that creates a version of the manuscript following
the GJI style. Both manuscript.tex and manuscript-gji.tex don't contain
actual content, just compiles the content of the other files. Move every .tex
file created by the notebooks to manuscript/results/. Comment out the
definition of \nl command on gji_extra.sty: it's already being defined by
algorithm2e. Update the Makefile to the latest changes, add targets for
building the GJI version of the manuscrip

--- 2021-02-02 manuscript/manuscript.tex
@@
-\documentclass[twocolumn]{article}
-\setlength{\columnsep}{2\columnsep}
-\usepackage[utf8]{inputenc}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage[longend,linesnumbered,ruled]{algorithm2e}
-\usepackage{graphicx}
-\usepackage[round,authoryear,sort]{natbib}
-\usepackage{url}
-\usepackage[pdftex,colorlinks=true]{hyperref}
-\usepackage{fancyhdr}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{setspace}
-
-% Define style for urls
-\urlstyle{same}
-
-% Import variables
-\input{variables.tex}
-
-% Define title, authors, affiliations and DOI
-% ===========================================
-\newcommand{\Author}{%
-    \AuthorAShort,
-    \AuthorBShort
-}
-\newcommand{\AuthorAffil}{%
-    {\large
-        \AuthorA$^{1,2}$
-        and
-        \AuthorB$^{3}$
-    }
-    \\[0.4cm]
-    {\small $^{1}$\AffiliationA} \\
-    {\small $^{2}$\AffiliationB} \\
-    {\small $^{3}$\AffiliationC} \\
-}
-
-% Configure header and hypersetup
-% ===============================
-\pagestyle{fancy}
-\fancyhf{}
-\lhead{
-    \fontsize{9pt}{12pt}\selectfont
-    \Author{} (\the\year{}). \DOI{}
-}
-\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
-\renewcommand{\headrulewidth}{0pt}
-\hypersetup{
-    allcolors=blue,
-    pdftitle={\Title},
-    pdfauthor={\Author},
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\title{\Title}
-\author{\AuthorAffil}
-\date{
-    \normalsize
-    \today
-}
-\maketitle
-
-\noindent
-\textbf{Keywords:}
-\input{keywords.tex}
-
-\begin{abstract}
-    \input{abstract}
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{content.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{humannat}
-\bibliography{references}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{appendix.tex}
-
-\end{document}
+The equivalent source technique is a powerful and widely used method for
+processing gravity and magnetic data.  Nevertheless, its major
+drawback is the large computational cost in terms of processing time and
+computer memory.
+We present two techniques for reducing the computational cost of equivalent
+source processing: block-averaging source locations and the
+gradient-boosted equivalent source algorithm.
+By using block-averaging, we reduce the number of source coefficients that
+must be estimated while retaining the minimum desired resolution in the final
+processed data.
+With the gradient boosting method, we estimate the layer coefficients in
+small batches along overlapping windows, allowing us to reduce the computer
+memory requirements arbitrarily to conform to the constraints of the
+available hardware.
+We show that the combination of block-averaging and gradient-boosted
+equivalent sources are capable of producing accurate interpolations through
+tests against synthetic data.
+Moreover, we demonstrate the feasibility of our method by gridding a gravity
+dataset covering Australia with over 1.7 million observations using a modest
+personal computer.

### 2021-02-04 manuscript/abstract.tex
Edits to abstract

@@
 gradient-boosted equivalent source algorithm.
-By using block-averaging, we reduce the number of source coefficients that
+Though block-averaging, we reduce the number of source coefficients that
 must be estimated while retaining the minimum desired resolution in the final
 processed data.
-With the gradient boosting method, we estimate the layer coefficients in
+With the gradient boosting method, we estimate the sources coefficients in
 small batches along overlapping windows, allowing us to reduce the computer
@@
 We show that the combination of block-averaging and gradient-boosted
-equivalent sources are capable of producing accurate interpolations through
+equivalent sources is capable of producing accurate interpolations through
 tests against synthetic data.

### 2021-02-04 manuscript/content.tex
Edits to introduction

@@
 potential field data:
-(i) they are not able to take into account the variable height of the
+(i)~they are not able to take into account the variable height of the
 observation points and
-(ii) the interpolating functions are not necessarily harmonic functions, which
+(ii)~the interpolating functions are not necessarily harmonic, which
 is the underlying assumption behind many processing techniques
@@
 \citet{dampney1969}.
-It consists in fitting a model of elementary sources to the data and using this
-model to predict new data values.
+It consists in fitting a model of finite elementary sources to the data and
+using this model to predict new data values.
 Besides interpolation, equivalent sources have been used for
@@
 \citet{leao1989} processed the input data using a moving window, only fitting the
-data inside the window and predicting observations at the center of the window.
+data inside the window and predicting observations at its center.
 \citet{li2010} and \citet{barnes2011} apply different operations to generate a
@@
 Some achieve greater efficiency by restricting their applications
-specific data types \citep{siqueira2017},
+to specific data types \citep{siqueira2017},
 interpolating only on regular grids \citep{leao1989},
@@
 
-Through tests on synthetic data, we show that: (i) the \emph{block-averaged}
-sources are able to achieve the same accuracy as other traditional equivalent
-source layouts while using a fraction of the number of sources, and (ii) the
-\emph{gradient boosting} algorithm greatly reduces the computational memory
-required to fit very large datasets without sacrificing prediction accuracy.
-Finally, a combination of both strategies are used to process a collection of
+Through tests on synthetic data, we show that:
+(i)~the \emph{block-averaged} sources are able to achieve the same accuracy as
+other traditional equivalent source layouts while using a fraction of the
+number of sources, and
+(ii)~the \emph{gradient boosting} algorithm greatly reduces the computational
+memory required to fit very large datasets without sacrificing prediction
+accuracy.
+Finally, a combination of both strategies is used to process a collection of
 around 1.7 million ground gravity data measurements from Australia.

### 2021-02-04 manuscript/content.tex
Edits to methodology

@@
 \begin{equation}
-  d = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
+    \mathbf{d} = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
 \end{equation}
@@
 
+    calculate $ \mathbf{d}_k $, where
     $
-    \mathbf{d}_k \Rightarrow
     {d_k}_i
@@
 the step size $\alpha_k$ and updating the residuals vector.
-In this case, the step size prevents the algorithm from worsening the fit to
+In this case, the step size prevents the algorithm from worsening the fit over
 data points that fall outside of the current window.
@@
 The key differences are that in our method:
-(1) the sources in the overlapping portions of the windows are
-fit more than once, allowing the algorithm to self-correct for poor solutions
-to any given window;
-(2) we use only data points within the window when fitting, what enables the
+(i)~the sources in the overlapping portions of the windows are fitted more than
+once, allowing the algorithm to self-correct for poor solutions to any given
+window;
+(ii)~we use only data points within the window when fitting, what enables the
 use of larger datasets;
-(3) experience shows that the step size parameter improves the convergence of
+(iii)~experience shows that the step size parameter improves the convergence of
 the solution, particularly when using only the data inside the windows for
@@
 straight and closely spaced flight lines.
-Measurements are usually taken at a high temporal frequency, leading to the
+Measurements are usually taken at a high temporal frequency, leading to
 observation points along the flight lines that are several times closer to each
@@
     \item Dividing the survey region into rectangular blocks of equal size.
-    \item Computing the median horizontal position of the observation points
-      that fall inside each block. Blocks without any observation point are
-      omitted.
+    \item \label{item:median-position} Computing the median horizontal position
+        of the observation points that fall inside each block. Blocks without
+        any observation point are omitted.
     \item Assign one point source to the median horizontal position calculated
-      in step 1.
+        in step \ref{item:median-position}.
 \end{enumerate}
@@
 The overdetermined problem that arises from this layout has a lower
-computational load and is less prone to overfiting the data since the model
+computational load and is less prone to overfitting the data since the model
 complexity is lower.
@@
         (a)~a \emph{constant depth} at a chosen vertical coordinate,
-        (b)~a \emph{relative depth} determined by uniformly shifting the
-        vertical coordinate of data points downwards,
+        (b)~a \emph{relative depth} determined by uniformly downward shifting
+        the vertical coordinate of data points,
         and

### 2021-02-04 manuscript/content.tex
Remove dashes from source layouts and uniform their name

@@
         (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
-        obtained through the \emph{sources-below-data} layout.
+        obtained through the \emph{sources below data} layout.
         (c) Location of the \SourceLayoutsSchematicsGridSources{} sources
-        obtained through the \emph{regular-grid} layout.
+        obtained through the \emph{regular grid} layout.
         (d) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
@@
 
-For ground surveys, the \emph{regular-grid} layout needs a sufficiently
+For ground surveys, the \emph{regular grid} layout needs a sufficiently
 small grid spacing to be able to fit the observed data.
@@
 observations exist.
-In contrast, the \emph{sources-below-data} layout is more likely to accurately
+In contrast, the \emph{sources below data} layout is more likely to accurately
 fit the observed data with many fewer sources, reducing the computational load.
-But when applied to airborne surveys, the \emph{sources-below-data} layout may
+But when applied to airborne surveys, the \emph{sources below data} layout may
 place an undesirably large number of sources along the flight paths.
@@
 magnetic data.
-The \emph{regular-grid} layout can avoid this effect by evenly
+The \emph{regular grid} layout can avoid this effect by evenly
 distributing sources and using a continuous source layer (e.g.,
@@
 horizontal layout strategy.
-For \emph{sources-below-data}, it is the vertical coordinate of the data point
+For \emph{sources below data}, it is the vertical coordinate of the data point
 corresponding to the given source.
-For \emph{regular-grid}, it can be interpolated from the vertical coordinates
+For \emph{regular grid}, it can be interpolated from the vertical coordinates
 of all data points.
-Finally, for \emph{block-averaged-sources} it will be the average vertical
+Finally, for \emph{block-averaged sources} it will be the average vertical
 coordinate of data within the corresponding block.
@@
 This process was repeated for each combination of horizontal layout
-(sources-below-data and block-averaged-sources) and depth type (constant,
-relative, and variable) and for regular-grid sources with a constant depth,
-totalling 7 different combinations.
+(\emph{sources below data} and \emph{block-averaged sources}) and depth type
+(\emph{constant}, \emph{relative}, and \emph{variable}) and for regular grid
+sources with a constant depth, totalling 7 different combinations.
 
@@
 For example, using a constant depth needs the definition of the depth and using
-block-average-sources requires the definition of the block size.
+block-averaged sources requires the definition of the block size.
 The predictive capabilities of the equivalent sources depend on the choice of
@@
 values of approximately 0.8\mGal regardless of the depth type, with the
-exception of the regular-grid layout which produced a larger RMS of
+exception of the regular grid layout which produced a larger RMS of
 \BestGroundGridSourcesConstantDepthRms{}\mGal.
@@
 Edge effects are present for all strategies but are noticeably smaller for the
-combination of block-averaged-sources with a variable depth based on the
+combination of block-averaged sources with a variable depth based on the
 nearest neighbour distance.
-For the synthetic airborne survey, all strategies (including the regular-grid)
+For the synthetic airborne survey, all strategies (including the regular grid)
 produced similar RMS errors of approximately 0.3\mGal.
@@
 for both the regular and gradient-boosted interpolations, namely
-block-averaged-sources with a block size of
+block-averaged sources with a block size of
 \BestAirborneBlockAveragedSourcesRelativeDepthSpacing\m and a
@@
 comparably accurate interpolations.
-Nevertheless, the \emph{block-averaged-sources} strategy make use of fewer
+Nevertheless, the \emph{block-averaged sources} strategy make use of fewer
 sources when compared with other strategies, which reduces the computational
@@
 interpolation RMS error.
-In the particular case of a sparse ground survey with block-averaged-sources,
+In the particular case of a sparse ground survey with block-averaged sources,
 the use of a variable depth visibly reduced edge effects and artifacts in areas

### 2021-02-04 manuscript/content.tex
Add curly brackets after every unit

@@
 The airborne survey has \AirborneSurveyPoints{} observations at heights between
-\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
+\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}
 (Fig.~\ref{fig:synthetic-layouts}c).
@@
 For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of approximately 0.8\mGal regardless of the depth type, with the
+values of approximately 0.8\mGal{} regardless of the depth type, with the
 exception of the regular grid layout which produced a larger RMS of
-\BestGroundGridSourcesConstantDepthRms{}\mGal.
+\BestGroundGridSourcesConstantDepthRms{}\mGal{}.
 The differences between the target grid and the interpolated values are larger
@@
 For the synthetic airborne survey, all strategies (including the regular grid)
-produced similar RMS errors of approximately 0.3\mGal.
+produced similar RMS errors of approximately 0.3\mGal{}.
 The maps of the differences between the target grid and interpolation results
@@
 block-averaged sources with a block size of
-\BestAirborneBlockAveragedSourcesRelativeDepthSpacing\m and a
+\BestAirborneBlockAveragedSourcesRelativeDepthSpacing\m{} and a
 relative depth of
-\BestAirborneBlockAveragedSourcesRelativeDepthDepth\m.
+\BestAirborneBlockAveragedSourcesRelativeDepthDepth\m{}.
 
@@
 at a relative depth of \AustraliaEqlDepth{} and a block size of
-1.8\km, resulting in a total of \AustraliaEqlNSources{}~point
+1.8\km{}, resulting in a total of \AustraliaEqlNSources{}~point
 sources.
 The block size was chosen to match the desired resolution of the final grid
- (1~arc-minute is approximately 1.8\km at the equator).
+ (1~arc-minute is approximately 1.8\km{} at the equator).
 The coefficients of the gradient-boosted equivalent sources are estimated using
@@
 interpolated regular grid.
-Grid points that are further than 50\km from the nearest data
+Grid points that are further than 50\km{} from the nearest data
 point are masked to avoid unrealistic extrapolations.

### 2021-02-04 manuscript/content.tex
Edits to results

@@
 
-The results show that the interpolation RMS error for gradient-boosting is
+The results show that the interpolation error for gradient-boosting is
 generally larger than the error for regular equivalent sources.
@@
 
-Our results show what the interpolation RMS error decreases with the amount of
+Our results show that the interpolation RMS error decreases with the amount of
 overlap, reaching the same accuracy as the regular equivalent sources at
@@
 The resulting grid preserves the high resolution of the original data while
-avoiding aliasing artifacts because to the block averaging.
+avoiding aliasing artifacts due to the block averaging.
 Some parts of the grid are smoother and with reduced amplitude (e.g., some

### 2021-02-04 manuscript/content.tex
Fix caption of figure
Swap the description of two subfigs that were wrong.

@@
         (a)~RMS error between the target grid and interpolation results and
-        (b)~computation time as a function of window size.
-        (c)~RMS error between the target grid and interpolation results and
+        (b)~RMS error between the target grid and interpolation results and
+        (c)~computation time as a function of window size.
         (d)~computation time as a function of window overlap.

### 2021-02-04 manuscript/content.tex
Edits to data availability and acknowledgments

@@
 Boule \citep{boule2020} for normal gravity calculations,
-xarray \citep{xarray2017} and Numpy \citep{numpy2020} for multidimensional
-arrays and numerical computations,
+xarray \citep{xarray2017} and Numpy \citep{numpy2020} for handling
+multidimensional arrays and numerical computations,
 Numba \citep{numba2015} for just-in-time compilation and parallelization,
@@
 S.R. Soler is supported by a scholarship from CONICET, Argentina.
-Contains British Geological Survey materials © UKRI.
+This work contains British Geological Survey materials © UKRI.
 

### 2021-02-04 manuscript/abstract.tex
Fix typo

@@
 gradient-boosted equivalent source algorithm.
-Though block-averaging, we reduce the number of source coefficients that
+Through block-averaging, we reduce the number of source coefficients that
 must be estimated while retaining the minimum desired resolution in the final

### 2021-02-04 manuscript/content.tex
Add tildes after items in figure caption

@@
         layout strategies.
-        (a) Set of \SourceLayoutsSchematicsObservations{} observation points
+        (a)~Set of \SourceLayoutsSchematicsObservations{} observation points
         that simulate a ground survey.
-        (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
+        (b)~Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
         obtained through the \emph{sources below data} layout.
-        (c) Location of the \SourceLayoutsSchematicsGridSources{} sources
+        (c)~Location of the \SourceLayoutsSchematicsGridSources{} sources
         obtained through the \emph{regular grid} layout.
-        (d) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
+        (d)~Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
         sources obtained through the \emph{block-averaged sources} layout.

### 2021-02-04 notebooks/07-grid-airborne-data.py
Change range of damping on airborne survey

@@ -67,7 +67,7 @@ depths = np.arange(1e3, 18e3, 2e3)
 #    spacing, depth and damping
 grid_sources_spacings = [1e3, 2e3, 3e3]
 grid_sources_depths = np.arange(1e3, 11e3, 2e3)
-grid_sources_dampings = np.logspace(1, 4, 4)
+grid_sources_dampings = np.logspace(-3, 2, 6)
 # Define parameters for variable relative depth layouts:
 #    depth factor, depth shift and k_values
 depth_factors = [1, 2, 3, 4, 5, 6]

### 2021-02-05 manuscript/content.tex
Add highlight figures for Australia results
Included a zoom in highlight of a part in the Northwest that had some
interesting mix of gaps and spacings.

--- 2021-02-04 manuscript/content.tex
@@
 potential field data:
-(i)~they are not able to take into account the variable height of the
+(i) they are not able to take into account the variable height of the
 observation points and
-(ii)~the interpolating functions are not necessarily harmonic, which
+(ii) the interpolating functions are not necessarily harmonic functions, which
 is the underlying assumption behind many processing techniques
@@
 \citet{dampney1969}.
-It consists in fitting a model of finite elementary sources to the data and
-using this model to predict new data values.
+It consists in fitting a model of elementary sources to the data and using this
+model to predict new data values.
 Besides interpolation, equivalent sources have been used for
@@
 \citet{leao1989} processed the input data using a moving window, only fitting the
-data inside the window and predicting observations at its center.
+data inside the window and predicting observations at the center of the window.
 \citet{li2010} and \citet{barnes2011} apply different operations to generate a
@@
 Some achieve greater efficiency by restricting their applications
-to specific data types \citep{siqueira2017},
+specific data types \citep{siqueira2017},
 interpolating only on regular grids \citep{leao1989},
@@
 
-Through tests on synthetic data, we show that:
-(i)~the \emph{block-averaged} sources are able to achieve the same accuracy as
-other traditional equivalent source layouts while using a fraction of the
-number of sources, and
-(ii)~the \emph{gradient boosting} algorithm greatly reduces the computational
-memory required to fit very large datasets without sacrificing prediction
-accuracy.
-Finally, a combination of both strategies is used to process a collection of
+Through tests on synthetic data, we show that: (i) the \emph{block-averaged}
+sources are able to achieve the same accuracy as other traditional equivalent
+source layouts while using a fraction of the number of sources, and (ii) the
+\emph{gradient boosting} algorithm greatly reduces the computational memory
+required to fit very large datasets without sacrificing prediction accuracy.
+Finally, a combination of both strategies are used to process a collection of
 around 1.7 million ground gravity data measurements from Australia.
@@
 \begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
+  d = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
 \end{equation}
@@
 
-    calculate $ \mathbf{d}_k $, where
     $
+    \mathbf{d}_k \Rightarrow
     {d_k}_i
@@
 the step size $\alpha_k$ and updating the residuals vector.
-In this case, the step size prevents the algorithm from worsening the fit over
+In this case, the step size prevents the algorithm from worsening the fit to
 data points that fall outside of the current window.
@@
 The key differences are that in our method:
-(i)~the sources in the overlapping portions of the windows are fitted more than
-once, allowing the algorithm to self-correct for poor solutions to any given
-window;
-(ii)~we use only data points within the window when fitting, what enables the
+(1) the sources in the overlapping portions of the windows are
+fit more than once, allowing the algorithm to self-correct for poor solutions
+to any given window;
+(2) we use only data points within the window when fitting, what enables the
 use of larger datasets;
-(iii)~experience shows that the step size parameter improves the convergence of
+(3) experience shows that the step size parameter improves the convergence of
 the solution, particularly when using only the data inside the windows for
@@
 straight and closely spaced flight lines.
-Measurements are usually taken at a high temporal frequency, leading to
+Measurements are usually taken at a high temporal frequency, leading to the
 observation points along the flight lines that are several times closer to each
@@
         (b) Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
-        obtained through the \emph{sources below data} layout.
+        obtained through the \emph{sources-below-data} layout.
         (c) Location of the \SourceLayoutsSchematicsGridSources{} sources
-        obtained through the \emph{regular grid} layout.
+        obtained through the \emph{regular-grid} layout.
         (d) Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
@@
 
-For ground surveys, the \emph{regular grid} layout needs a sufficiently
+For ground surveys, the \emph{regular-grid} layout needs a sufficiently
 small grid spacing to be able to fit the observed data.
@@
 observations exist.
-In contrast, the \emph{sources below data} layout is more likely to accurately
+In contrast, the \emph{sources-below-data} layout is more likely to accurately
 fit the observed data with many fewer sources, reducing the computational load.
-But when applied to airborne surveys, the \emph{sources below data} layout may
+But when applied to airborne surveys, the \emph{sources-below-data} layout may
 place an undesirably large number of sources along the flight paths.
@@
 magnetic data.
-The \emph{regular grid} layout can avoid this effect by evenly
+The \emph{regular-grid} layout can avoid this effect by evenly
 distributing sources and using a continuous source layer (e.g.,
@@
     \item Dividing the survey region into rectangular blocks of equal size.
-    \item \label{item:median-position} Computing the median horizontal position
-        of the observation points that fall inside each block. Blocks without
-        any observation point are omitted.
+    \item Computing the median horizontal position of the observation points
+      that fall inside each block. Blocks without any observation point are
+      omitted.
     \item Assign one point source to the median horizontal position calculated
-        in step \ref{item:median-position}.
+      in step 1.
 \end{enumerate}
@@
 The overdetermined problem that arises from this layout has a lower
-computational load and is less prone to overfitting the data since the model
+computational load and is less prone to overfiting the data since the model
 complexity is lower.
@@
         (a)~a \emph{constant depth} at a chosen vertical coordinate,
-        (b)~a \emph{relative depth} determined by uniformly downward shifting
-        the vertical coordinate of data points,
+        (b)~a \emph{relative depth} determined by uniformly shifting the
+        vertical coordinate of data points downwards,
         and
@@
 horizontal layout strategy.
-For \emph{sources below data}, it is the vertical coordinate of the data point
+For \emph{sources-below-data}, it is the vertical coordinate of the data point
 corresponding to the given source.
-For \emph{regular grid}, it can be interpolated from the vertical coordinates
+For \emph{regular-grid}, it can be interpolated from the vertical coordinates
 of all data points.
-Finally, for \emph{block-averaged sources} it will be the average vertical
+Finally, for \emph{block-averaged-sources} it will be the average vertical
 coordinate of data within the corresponding block.
@@
 The airborne survey has \AirborneSurveyPoints{} observations at heights between
-\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}
+\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
 (Fig.~\ref{fig:synthetic-layouts}c).
@@
 This process was repeated for each combination of horizontal layout
-(\emph{sources below data} and \emph{block-averaged sources}) and depth type
-(\emph{constant}, \emph{relative}, and \emph{variable}) and for regular grid
-sources with a constant depth, totalling 7 different combinations.
+(sources-below-data and block-averaged-sources) and depth type (constant,
+relative, and variable) and for regular-grid sources with a constant depth,
+totalling 7 different combinations.
 
@@
 For example, using a constant depth needs the definition of the depth and using
-block-averaged sources requires the definition of the block size.
+block-average-sources requires the definition of the block size.
 The predictive capabilities of the equivalent sources depend on the choice of
@@
 For the synthetic ground survey, the horizontal layouts produced similar RMS
-values of approximately 0.8\mGal{} regardless of the depth type, with the
-exception of the regular grid layout which produced a larger RMS of
-\BestGroundGridSourcesConstantDepthRms{}\mGal{}.
+values of approximately 0.8\mGal regardless of the depth type, with the
+exception of the regular-grid layout which produced a larger RMS of
+\BestGroundGridSourcesConstantDepthRms{}\mGal.
 The differences between the target grid and the interpolated values are larger
@@
 Edge effects are present for all strategies but are noticeably smaller for the
-combination of block-averaged sources with a variable depth based on the
+combination of block-averaged-sources with a variable depth based on the
 nearest neighbour distance.
-For the synthetic airborne survey, all strategies (including the regular grid)
-produced similar RMS errors of approximately 0.3\mGal{}.
+For the synthetic airborne survey, all strategies (including the regular-grid)
+produced similar RMS errors of approximately 0.3\mGal.
 The maps of the differences between the target grid and interpolation results
@@
 for both the regular and gradient-boosted interpolations, namely
-block-averaged sources with a block size of
-\BestAirborneBlockAveragedSourcesRelativeDepthSpacing\m{} and a
+block-averaged-sources with a block size of
+\BestAirborneBlockAveragedSourcesRelativeDepthSpacing\m and a
 relative depth of
-\BestAirborneBlockAveragedSourcesRelativeDepthDepth\m{}.
+\BestAirborneBlockAveragedSourcesRelativeDepthDepth\m.
 
@@
 
-The results show that the interpolation error for gradient-boosting is
+The results show that the interpolation RMS error for gradient-boosting is
 generally larger than the error for regular equivalent sources.
@@
 
-Our results show that the interpolation RMS error decreases with the amount of
+Our results show what the interpolation RMS error decreases with the amount of
 overlap, reaching the same accuracy as the regular equivalent sources at
@@
         (a)~RMS error between the target grid and interpolation results and
-        (b)~RMS error between the target grid and interpolation results and
-        (c)~computation time as a function of window size.
+        (b)~computation time as a function of window size.
+        (c)~RMS error between the target grid and interpolation results and
         (d)~computation time as a function of window overlap.
@@
     \caption{
-      Pseudo-color maps of observed (left) and
-      interpolated (right) gravity disturbance of Australia.
+      Pseudo-color maps of observed (a and c) and
+      interpolated (b and d) gravity disturbance of Australia.
+      The observed values in a and c are plotted as colored circles.
+      The red rectangle marks the boundaries of the highlight maps in c
+      and d.
       Observations are part of a compilation by \citet{wynne2018} of
@@
 at a relative depth of \AustraliaEqlDepth{} and a block size of
-1.8\km{}, resulting in a total of \AustraliaEqlNSources{}~point
+1.8\km, resulting in a total of \AustraliaEqlNSources{}~point
 sources.
 The block size was chosen to match the desired resolution of the final grid
- (1~arc-minute is approximately 1.8\km{} at the equator).
+ (1~arc-minute is approximately 1.8\km at the equator).
 The coefficients of the gradient-boosted equivalent sources are estimated using
@@
 interpolated regular grid.
-Grid points that are further than 50\km{} from the nearest data
+Grid points that are further than 50\km from the nearest data
 point are masked to avoid unrealistic extrapolations.
@@
 The resulting grid preserves the high resolution of the original data while
-avoiding aliasing artifacts due to the block averaging.
+avoiding aliasing artifacts because to the block averaging.
 Some parts of the grid are smoother and with reduced amplitude (e.g., some
@@
 comparably accurate interpolations.
-Nevertheless, the \emph{block-averaged sources} strategy make use of fewer
+Nevertheless, the \emph{block-averaged-sources} strategy make use of fewer
 sources when compared with other strategies, which reduces the computational
@@
 interpolation RMS error.
-In the particular case of a sparse ground survey with block-averaged sources,
+In the particular case of a sparse ground survey with block-averaged-sources,
 the use of a variable depth visibly reduced edge effects and artifacts in areas

### 2021-02-05 notebooks/99-figures.py

@@ -509,6 +509,7 @@ region = vd.pad_region(
     vd.get_region((australia_data.longitude.values, australia_data.latitude.values)),
     1,
 )
+subregion = [121, 133, -22, -14]
 lat_ts = australia_data.latitude.mean().values
 lon_ts = australia_data.longitude.mean().values
 
@@ -525,10 +526,13 @@ fig = pygmt.Figure()
 
 pygmt.config(
     FONT_ANNOT="11p,Helvetica,black",
-    FONT_TITLE="15p,Helvetica,black",
+    FONT_TITLE="13p,Helvetica,black",
     FONT_LABEL="11p,Helvetica,black",
+    MAP_TITLE_OFFSET="0p",
     MAP_FRAME_WIDTH="2p",
 )
+
+fig.shift_origin(0, "5.1i")
 
 fig.grdimage(
     "@earth_relief_01m",
@@ -549,7 +553,12 @@ fig.plot(
     cmap=True,
 )
 fig.coast(shorelines=True)
-fig.basemap(frame=["af", 'WeSN+t"Gravity disturbance observations"'])
+fig.plot(
+    x=[subregion[0], subregion[1], subregion[1], subregion[0], subregion[0]],
+    y=[subregion[3], subregion[3], subregion[2], subregion[2], subregion[3]],
+    pen="2p,orangered1,-",
+)
+fig.basemap(frame=["af", 'WeSn+t"a) Gravity disturbance observations"'])
 with pygmt.config(FONT_ANNOT="9p,Helvetica,black"):
     fig.colorbar(
         box="+gwhite+c-0.1c/0.2c+r0.1c",
@@ -575,7 +584,50 @@ fig.grdimage(
     nan_transparent=True,
 )
 fig.coast(shorelines=True)
-fig.basemap(frame=["af", 'wESN+t"Interpolated grid of gravity disturbances"'])
+fig.basemap(frame=["af", 'wESn+t"b) Interpolated grid of gravity disturbances"'])
+
+fig.shift_origin("-5.1i", "-4.3i")
+
+fig.grdimage(
+    "@earth_relief_01m",
+    region=subregion,
+    projection=proj_gmt,
+    shading="+a45+nt0.7",
+    cmap="gray",
+)
+fig.coast(
+    land="#333333",
+)
+pygmt.makecpt(cmap="polar", series=(-maxabs, maxabs))
+fig.plot(
+    x=australia_data.longitude,
+    y=australia_data.latitude,
[…]

### 2021-02-05 manuscript/content.tex
Set d as a scalar on first equation of gradient-boosting
Replace over for on

--- 2021-02-04 manuscript/content.tex
@@
 \begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
+    d = \sum_{k=1}^K \alpha_k f(\mathbf{c}_k),
 \end{equation}
@@
 the step size $\alpha_k$ and updating the residuals vector.
-In this case, the step size prevents the algorithm from worsening the fit over
+In this case, the step size prevents the algorithm from worsening the fit on
 data points that fall outside of the current window.

### 2021-02-05 notebooks/98-generate_latex_variables.py
Change range of damping on airborne survey (#120)
Change range of damping because the lowest RMS was achieved with the lower boundary value of the damping.

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.9.1
+#       jupytext_version: 1.7.1
 #   kernelspec:
 #     display_name: Python [conda env:eql-gradient-boosted]
 #     language: python

### 2021-02-09 notebooks/02-source-layouts-schematics.py
Start adding gradient boosting schematics figure

@@ -6,12 +6,14 @@
 #       extension: .py
 #       format_name: light
 #       format_version: '1.5'
-#       jupytext_version: 1.7.1
+#       jupytext_version: 1.9.1
 #   kernelspec:
 #     display_name: Python [conda env:eql-gradient-boosted]
 #     language: python
 #     name: conda-env-eql-gradient-boosted-py
 # ---
+
+# # Source layouts schematics
 
 # +
 from IPython.display import display  # noqa: F401  # ignore used but not imported
@@ -169,3 +171,67 @@ for layout in layouts:
 
 json_file = results_dir / "source-layouts-schematics.json"
 save_to_json(variables, json_file)
+# -
+
+# # Gradient boosting schematics
+
+sources = source_distributions["source_below_data"]
+region = vd.get_region(sources)
+
+# +
+overlapping = 0.5
+window_size = 18e3
+spacing = window_size * (1 - overlapping)
+
+centers, indices = vd.rolling_window(sources, size=window_size, spacing=spacing)
+spacing_easting = centers[0][0, 1] - centers[0][0, 0]
+spacing_northing = centers[1][1, 0] - centers[1][0, 0]
+
+print("Desired spacing:", spacing)
+print("Actual spacing:", (spacing_easting, spacing_northing))
+
+# +
+indices = [i[0] for i in indices.ravel()]
+centers = [i.ravel() for i in centers]
+n_windows = centers[0].size
+
+print("Number of windows:", n_windows)
+
+# +
+from matplotlib.patches import Rectangle
+
+ncols = 3
+nrows = int(np.ceil(n_windows / ncols))
+# figsize = (6.66, 2 * nrows)
+figsize = (3.33, 1 * nrows)
+size = 2
+
+
+fig, axes = plt.subplots(
+    ncols=ncols, nrows=nrows, figsize=figsize, sharex=True, sharey=True
+)
+axes = axes.ravel()
+
+for i in range(n_windows):
+    ax = axes[i]
+    window = indices[i]
+    easting, northing = centers[0][i], centers[1][i]
+    not_window = [i for i in np.arange(sources[0].size) if i not in window]
+    ax.scatter(sources[0][window], sources[1][window], c="C3", s=size)
+    ax.scatter(sources[0][not_window], sources[1][not_window], c="C7", s=size)
+    rectangle = Rectangle(
+        xy=(easting - window_size / 2, northing - window_size / 2),
[…]

### 2021-02-09 manuscript/content.tex
Start adding gradient boosting schematics figure
Add observation points, sources and caption to figure

@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
+    \caption{
+        Sketch of the gradient-boosting process.
+        (a)~Set of observation points that simulate a ground survey.
+        (b)~Location of the sources obtained by putting one source below each
+        observation point.
+        (c)~Sets of equivalent sources obtained through gradient-boosting by
+        selecting only the ones that fall inside each overlapping window.
+        Blue and orange dots represent the horizontal location of the
+        observation points and the original sources, respectively.
+        The dashed line squares represent the boundaries of each overlapping
+        window, while its corresponding sources are symbolized through red
+        dots.
+        Grey dots represent the other sources that aren't included in that
+        particular set.
+    }
+    \label{fig:gradient-boosting-schematics}
+\end{figure*}
+
 The gradient boosting algorithm works by fitting each component of the
@@
 S.R. Soler is supported by a scholarship from CONICET, Argentina.
-This work contains British Geological Survey materials © UKRI.
+This work contains British Geological Survey materials ©~UKRI.
 

### 2021-02-09 notebooks/02-source-layouts-schematics.py

@@ -22,6 +22,7 @@ import numpy as np
 import pandas as pd
 import verde as vd
 import matplotlib.pyplot as plt
+from matplotlib.patches import Rectangle
 
 import boost_and_layouts
 from boost_and_layouts import save_to_json
@@ -198,11 +199,8 @@ n_windows = centers[0].size
 print("Number of windows:", n_windows)
 
 # +
-from matplotlib.patches import Rectangle
-
 ncols = 3
 nrows = int(np.ceil(n_windows / ncols))
-# figsize = (6.66, 2 * nrows)
 figsize = (3.33, 1 * nrows)
 size = 2
 
@@ -232,6 +230,7 @@ for i in range(n_windows):
     ax.axis("off")
 
 plt.tight_layout()
-plt.savefig(Path("..") / "manuscript" / "figs" / "gradient-boosting-schematics.pdf")
+plt.savefig(
+    Path("..") / "manuscript" / "figs" / "svg" / "gradient-boosting-windows.svg"
+)
 plt.show()
-# -

### 2021-02-09 manuscript/content.tex
Add reference to the figure on text

@@
   \item Define a set of $M$ equivalent sources distributed throughout the
-    survey area (see section \ref{sec:source_distribution} for details).
+    survey area (Fig.~\ref{fig:gradient-boosting-schematics}b).
   \item Define a set of $K$ overlapping windows of equal size that cover the
@@
     the respective window.
-    Since the windows overlap, the total number of sources
-    from all sets will be greater than $M$.
+    Since the windows overlap, the total number of sources from all sets will
+    be greater than $M$ (Fig.~\ref{fig:gradient-boosting-schematics}c).
   \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent

### 2021-02-10 manuscript/content.tex
Interpret GB as refitting source coefficients

--- 2021-02-05 manuscript/content.tex
@@
 
+Worth noting that two sets of equivalent sources obtained through two adjacent
+overlapping windows have some portion of the sources on the same locations,
+specifically the ones that fall on the intersection between the two windows.
+We can interpret this as as the gradient-boosting algorithm fitting the source
+coefficients multiple times: one time for every window that covers each source.
+This fact can be exploited in order to save some computational memory.
+Instead of allocating the multiple $\mathbf{c}_k$ vectors
+(Eq.~\ref{eq:gb-linear-model}), we can initialize a single $\mathbf{c}$ vector
+full of zeros, where each element represents the coefficient of each one of the
+original $M$ sources.
+After each iteration of the gradient-boosting algorithm, we add the product of
+the resulting coefficients $\hat{\mathbf{c}}_k$ and the step-size coefficient
+$\alpha_k$  to the $\mathbf{c}$ vector, respecting the order of its elements.
+Because the relation between the source coefficients and the effect they
+generate is linear, we can safely compute the resulting field through
+Equation~\ref{eq:eql-forward}.
+This way the memory needed to store the entire set of estimated coefficients is
+limited to a single vector of $M$ elements.
+
 Our gradient boosting algorithm for overlapping windows is similar to the

### 2021-02-15 manuscript/content.tex
Reduce width of figure and center it
Minor styling improvement
Remove duplicated "as"
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

@@
 specifically the ones that fall on the intersection between the two windows.
-We can interpret this as as the gradient-boosting algorithm fitting the source
+We can interpret this as the gradient-boosting algorithm fitting the source
 coefficients multiple times: one time for every window that covers each source.

### 2021-02-15 manuscript/content.tex
Replace allocating for storing
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

@@
 This fact can be exploited in order to save some computational memory.
-Instead of allocating the multiple $\mathbf{c}_k$ vectors
+Instead of storing all of the multiple $\mathbf{c}_k$ vectors
 (Eq.~\ref{eq:gb-linear-model}), we can initialize a single $\mathbf{c}$ vector

### 2021-02-15 manuscript/content.tex
Replace "full of" for "with"
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

--- 2021-02-15 manuscript/content.tex
@@
 This fact can be exploited in order to save some computational memory.
-Instead of allocating the multiple $\mathbf{c}_k$ vectors
+Instead of storing all of the multiple $\mathbf{c}_k$ vectors
 (Eq.~\ref{eq:gb-linear-model}), we can initialize a single $\mathbf{c}$ vector
-full of zeros, where each element represents the coefficient of each one of the
+with zeros, where each element represents the coefficient of each one of the
 original $M$ sources.

### 2021-02-15 manuscript/content.tex
Replace "product" for "multiplication"
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

@@
 original $M$ sources.
-After each iteration of the gradient-boosting algorithm, we add the product of
+After each iteration of the gradient-boosting algorithm, we add the multiplication of
 the resulting coefficients $\hat{\mathbf{c}}_k$ and the step-size coefficient

### 2021-02-15 manuscript/content.tex
Replace "resulting" for "estimated"
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

--- 2021-02-15 manuscript/content.tex
@@
 original $M$ sources.
-After each iteration of the gradient-boosting algorithm, we add the product of
-the resulting coefficients $\hat{\mathbf{c}}_k$ and the step-size coefficient
+After each iteration of the gradient-boosting algorithm, we add the multiplication of
+the estimated coefficients $\hat{\mathbf{c}}_k$ and the step-size
 $\alpha_k$  to the $\mathbf{c}$ vector, respecting the order of its elements.

### 2021-02-15 manuscript/content.tex
Minor rephrasing
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

@@
 the estimated coefficients $\hat{\mathbf{c}}_k$ and the step-size
-$\alpha_k$  to the $\mathbf{c}$ vector, respecting the order of its elements.
+$\alpha_k$ to the corresponding elements of vector $\mathbf{c}$.
 Because the relation between the source coefficients and the effect they

### 2021-02-15 manuscript/content.tex
Add missing comma
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>
Add "It is worth"

@@
 
-Worth noting that two sets of equivalent sources obtained through two adjacent
-overlapping windows have some portion of the sources on the same locations,
-specifically the ones that fall on the intersection between the two windows.
+It is worth noting that two sets of equivalent sources obtained through two
+adjacent overlapping windows have some portion of the sources on the same
+locations, specifically the ones that fall on the intersection between the two
+windows.
 We can interpret this as the gradient-boosting algorithm fitting the source
@@
 Equation~\ref{eq:eql-forward}.
-This way the memory needed to store the entire set of estimated coefficients is
+This way, the memory needed to store the entire set of estimated coefficients is
 limited to a single vector of $M$ elements.

### 2021-02-16 manuscript/content.tex
Wrap long lines

@@
   \item Create $K$ separate sets of equivalent sources, one for each window.
-    Each set will be formed by the portion of the original $M$ sources that fall inside
-    the respective window.
-    Since the windows overlap, the total number of sources
-    from all sets will be greater than $M$.
+    Each set will be formed by the portion of the original $M$ sources that
+    fall inside the respective window.
+    Since the windows overlap, the total number of sources from all sets will
+    be greater than $M$ (Fig.~\ref{fig:gradient-boosting-schematics}c).
   \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
@@
 \end{enumerate}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.8\linewidth]{figs/gradient-boosting-schematics.pdf}
+    \caption{
+        Sketch of the gradient-boosting process.
+        (a)~Set of observation points that simulate a ground survey.
+        (b)~Location of the sources obtained by putting one source below each
+        observation point.
+        (c)~Sets of equivalent sources obtained through gradient-boosting by
+        selecting only the ones that fall inside each overlapping window.
+        Blue and orange dots represent the horizontal location of the
+        observation points and the original sources, respectively.
+        The dashed line squares represent the boundaries of each overlapping
+        window, while its corresponding sources are symbolized through red
+        dots.
+        Grey dots represent the other sources that aren't included in that
+        particular set.
+    }
+    \label{fig:gradient-boosting-schematics}
+\end{figure*}
 
@@
 original $M$ sources.
-After each iteration of the gradient-boosting algorithm, we add the multiplication of
-the estimated coefficients $\hat{\mathbf{c}}_k$ and the step-size
-$\alpha_k$ to the corresponding elements of vector $\mathbf{c}$.
+After each iteration of the gradient-boosting algorithm, we add the
+multiplication of the estimated coefficients $\hat{\mathbf{c}}_k$ and the
+step-size $\alpha_k$ to the corresponding elements of vector $\mathbf{c}$.
 Because the relation between the source coefficients and the effect they
@@
 Equation~\ref{eq:eql-forward}.
-This way, the memory needed to store the entire set of estimated coefficients is
-limited to a single vector of $M$ elements.
+This way, the memory needed to store the entire set of estimated coefficients
+is limited to a single vector of $M$ elements.
 

### 2021-02-16 manuscript/content.tex
Improve gradient-boosting schematic figure
Follow the design discussed on last meeting.
Update the caption of the figure.
Use triangle markers for observation points on every schematic figure.

--- 2021-02-15 manuscript/content.tex
@@
 \end{enumerate}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
+    \caption{
+        Sketch of the gradient-boosting algorithm.
+        Given a set of data points (blue upwards triangles), define a set of
+        equivalent sources (orange dots).
+        Start the gradient-boosting algorithm by selecting the data points and
+        the sources that fall under one of the overlapping windows, and
+        estimate their coefficients by fitting against this portion of the
+        data.
+        Then predict the effect of this set of sources on every observation
+        point and calculate the residuals.
+        Use another window to select residual points and sources that fall
+        under it, and estimate their coefficients by fitting them against the
+        selected residual points.
+        Predict the effect of this set of sources on every observation point
+        and update the residue.
+        Repeat this step for every remaining window.
+        The order in which the windows are covered is randomized to improve
+        convergence of the algorithm.
+    }
+    \label{fig:gradient-boosting-schematics}
+\end{figure*}
 

### 2021-02-16 notebooks/02-schematics-figures.py

@@ -133,7 +133,7 @@ for ax, label in zip(axes, labels):
 
 # Plot observation points
 ax = axes[0]
-ax.scatter(survey.easting, survey.northing, s=size, c="C0")
+ax.scatter(survey.easting, survey.northing, s=size, c="C0", marker="^")
 ax.set_title("Observation points")
 
 # Plot location of sources for each source layout
@@ -199,38 +199,109 @@ n_windows = centers[0].size
 print("Number of windows:", n_windows)
 
 # +
-ncols = 3
-nrows = int(np.ceil(n_windows / ncols))
-figsize = (3.33, 1 * nrows)
-size = 2
+ncols = 10
+figsize = (1.7 * ncols, 1.7)
+size = 3
 
+fig, axes = plt.subplots(ncols=ncols, nrows=1, figsize=figsize, dpi=300, sharex=True, sharey=True)
 
-fig, axes = plt.subplots(
-    ncols=ncols, nrows=nrows, figsize=figsize, sharex=True, sharey=True
-)
-axes = axes.ravel()
-
-for i in range(n_windows):
-    ax = axes[i]
-    window = indices[i]
-    easting, northing = centers[0][i], centers[1][i]
-    not_window = [i for i in np.arange(sources[0].size) if i not in window]
-    ax.scatter(sources[0][window], sources[1][window], c="C3", s=size)
-    ax.scatter(sources[0][not_window], sources[1][not_window], c="C7", s=size)
-    rectangle = Rectangle(
-        xy=(easting - window_size / 2, northing - window_size / 2),
-        width=window_size,
-        height=window_size,
-        fill=False,
-        linewidth=0.5,
-        linestyle="--",
-    )
-    ax.add_patch(rectangle)
+for ax in axes:
     ax.set_aspect("equal")
     ax.axis("off")
 
-plt.tight_layout()
+# Observation points
+axes[0].scatter(survey.easting, survey.northing, s=size, c="C0", marker="^")
+
+# Sources
+axes[1].scatter(*sources[:2], s=size, c="C1")
+
+# First fit
+# ---------
+window_i = 0
+window = indices[window_i]
+not_window = [i for i in np.arange(sources[0].size) if i not in window]
+w_center_easting, w_center_northing = centers[0][window_i], centers[1][window_i]
+rectangle_kwargs = dict(
+    xy=(w_center_easting - window_size / 2, w_center_northing - window_size / 2),
+    width=window_size,
[…]

### 2021-02-16 manuscript/content.tex
Specify symbol of residuals on caption
Change location of figure and adequate text to it

@@
   \item Define a set of $M$ equivalent sources distributed throughout the
-    survey area (Fig.~\ref{fig:gradient-boosting-schematics}b).
+    survey area.
   \item Define a set of $K$ overlapping windows of equal size that cover the
@@
     Since the windows overlap, the total number of sources from all sets will
-    be greater than $M$ (Fig.~\ref{fig:gradient-boosting-schematics}c).
+    be greater than $M$.
   \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
@@
 \end{enumerate}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
-    \caption{
-        Sketch of the gradient-boosting algorithm.
-        Given a set of data points (blue upwards triangles), define a set of
-        equivalent sources (orange dots).
-        Start the gradient-boosting algorithm by selecting the data points and
-        the sources that fall under one of the overlapping windows, and
-        estimate their coefficients by fitting against this portion of the
-        data.
-        Then predict the effect of this set of sources on every observation
-        point and calculate the residuals.
-        Use another window to select residual points and sources that fall
-        under it, and estimate their coefficients by fitting them against the
-        selected residual points.
-        Predict the effect of this set of sources on every observation point
-        and update the residue.
-        Repeat this step for every remaining window.
-        The order in which the windows are covered is randomized to improve
-        convergence of the algorithm.
-    }
-    \label{fig:gradient-boosting-schematics}
-\end{figure*}
 
@@
 the final \textit{gradient-boosted equivalent source algorithm}.
+Figure~\ref{fig:gradient-boosting-schematics} shows a sketch of the
+gradient-boosted equivalent source algorithm with a set of observation points
+that simulate a ground survey and locating one source below each data point.
 
@@
 \end{algorithm}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
+    \caption{
+        Sketch of the gradient-boosted equivalent source algorithm.
+        Given a set of data points (blue upwards triangles), define a set of
+        equivalent sources (orange dots) by locating one source below each
+        observation point.
+        Start the gradient-boosting algorithm by selecting the data points and
+        the sources that fall under one of the overlapping windows, and
+        estimate their coefficients by fitting against this portion of the
+        data.
+        Then predict the effect of this set of sources on every observation
+        point and calculate the residuals (red downward triangles).
+        Use another window to select residual points and sources that fall
+        under it, and estimate their coefficients by fitting them against the
+        selected residual points.
+        Predict the effect of this set of sources on every observation point
+        and update the residuals.
+        Repeat this step for every remaining window.
+        The order in which the windows are covered is randomized to improve
+        convergence of the algorithm.
+    }
+    \label{fig:gradient-boosting-schematics}
+\end{figure*}
 

### 2021-02-18 manuscript/content.tex
Restore text from one of the items

@@
   \item Define a set of $M$ equivalent sources distributed throughout the
-    survey area.
+    survey area (see section \ref{sec:source_distribution} for details).
   \item Define a set of $K$ overlapping windows of equal size that cover the
@@
         Sketch of the gradient-boosted equivalent source algorithm.        
-        Given a set of data points (blue upwards triangles), define a set of
-        equivalent sources (orange dots) by locating one source below each
-        observation point.
-        Start the gradient-boosting algorithm by selecting the data points and
-        the sources that fall under one of the overlapping windows, and
-        estimate their coefficients by fitting against this portion of the
-        data.
-        Then predict the effect of this set of sources on every observation
-        point and calculate the residuals (red downward triangles).
-        Use another window to select residual points and sources that fall
-        under it, and estimate their coefficients by fitting them against the
-        selected residual points.
-        Predict the effect of this set of sources on every observation point
-        and update the residuals.
-        Repeat this step for every remaining window.
-        The order in which the windows are covered is randomized to improve
-        convergence of the algorithm.
+        Data points are represented by blue upwards-facing triangles,
+        equivalent sources by orange dots, data residuals by red downwards-facing 
+        triangles, and the current window by black dashed lines.
+        The algorithm starts by selecting the data and sources 
+        inside the first window and estimating the source coefficients 
+        using the selected data points.
+        Then, the effect of the estimated sources is predicted on all data
+        points and used to calculate the residuals.
+        Another window is used to select residuals and sources and 
+        estimate the coefficients using the selected residuals instead of the 
+        original data.
+        Again, the effect of the estimated sources is predicted on all data points
+        and the residuals are updated.
+        These steps are repeated for every window in a randomized order.
     }

### 2021-05-28 manuscript/content.tex
Add more content to Australia section in manuscript

@@
 We start the interpolation process by defining a set of block-averaged sources
-at a relative depth of \AustraliaEqlDepth{} and a block size of
-1.8\km{}, resulting in a total of \AustraliaEqlNSources{}~point
-sources.
+using a block size of 1.8\km{}, resulting in a total of
+\AustraliaEqlNSources{}~point sources which depths remain unknown for now.
 The block size was chosen to match the desired resolution of the final grid
  (1~arc-minute is approximately 1.8\km{} at the equator).
-The coefficients of the gradient-boosted equivalent sources are estimated using
-a damping equal to \AustraliaEqlDamping{} and a window size of
-\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
-computer memory needed to store the Jacobian matrix to under 10~Gigabytes.
-Finally, we used the estimated source coefficients to predict the values of the
+Then we need to determine the size of the windows that will be used for
+estimating the coefficients of the gradient-boosted equivalent sources.
+We computed the amount of computer memory needed in order to store the largest
+Jacobian matrix for different values of window size
+(Fig.~\ref{fig:australia-memory-cv-error}a).
+We have chosen a window size of \AustraliaEqlWindowSize{} in order to limit the
+amount of memory needed to under 16~Gigabytes.
+
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
+    \caption{
+        (a) Amount of computer memory needed to store the largest Jacobian
+        matrix vs different window sizes. Each memory requirement corresponds
+        to the ammount of memory needed to store the elements of the largest
+        Jacobian matrix during the process of estimating the gradient-boosted
+        equivalent sources coefficients, using a double precision floating
+        point for each (64 bits).
+        (b) Root-mean square errors obtained after the K-Fold cross-validation
+        for each pair of damping and depth parameters. The orange
+        square highlights the minimum RMS value.
+        (c) Root-mean square error of the residue after each iteration of the
+        coefficients estimation process.
+    }
+    \label{fig:australia-memory-cv-error}
+\end{figure*}
+
+Secondly, we need to determine the depth of the sources and the value for the
+damping parameter. Based on the results obtained in
+Section~\ref{sec:synthetic_distributions}, we have chosen to locate them using
+the \emph{relative depth} strategy.
+In order to determine the values for the \emph{depth} and \emph{damping}
+parameters, we have applied a K-Fold cross-validation method through the
+scikit-learn implementation \citep{sklearn2011}.
+It consists in randomly dividing the original data into $k$ small sets (or
+folds), estimate the source coefficients using only $k - 1$ of the folds
+(training data) and validate the model by comparing its predictions with the
+remaining fold (testing data). This process is carried out once for each one of
+the $k$ folds.
+With the goal of speeding up the computations, we selected a portion of the
+Australia gravity disturbances to run the cross-validation: an area of
+\AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
+containing \AustraliaSmallAreaNPoints points.
+We run the cross-validation with a combination of \emph{depth} ranging from
+\AustraliaDepthMin{} to \AustraliaDepthMax{},
+and \emph{damping} from
+\AustraliaDampingMin{} to \AustraliaDampingMax{} in steps of one order of
+magnitude.
+We have used the root-mean square error as the validation function between the
+testing data and the predictions on each k-fold and computed the mean of all
+the RMS for each combination of the \emph{depth} and \emph{damping} parameters.
+Figure \ref{fig:australia-memory-cv-error}b shows the resulting scores of the
+cross-validation and highlights the minimum value achieved:
+\AustraliaEqlRmsScore{} corresponding to a relative depth of \AustraliaEqlDepth{} and
+a damping equal to \AustraliaEqlDamping{}.
+
+Finally, we proceed to estimate the coefficients of the whole set of
+gradient-boosted equivalent sources using the parameters previously determined.
+Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
+residue after each iteration of the gradient-boosting algorithm, exposing how
+to algorithm converges at a minimum difference between the gravity disturbance
+data and the predicted values by the equivalent sources.
+We then used the estimated source coefficients to predict the values of the
 gravity disturbance on a regular grid of
@@
 point are masked to avoid unrealistic extrapolations.
+
+Fig.~\ref{fig:australia-residuals} shows the residuals on each observation
+point: the difference between the gravity disturbance data and the predicted
+values by the equivalent sources on the same points.
+The inset figure shows a histogram of the residual values, depicting that the
+residuals are normally distributed around zero.
 
@@
 $\sim 1.3$~hours and the forward modelling step took $\sim 18$~minutes.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/australia-residuals.png}
+    \caption{
+        Residuals. Differences between the gravity disturbance data from
+        Australia and the predicted values by the estimated equivalent sources
+        on the same observation points. The color map has been truncated to
+        improve the visualization around the largest portion of residual
+        values. The inset plot shows a histogram of the residuals.
+    }
+    \label{fig:australia-residuals}
+\end{figure}
 
@@
 Numba \citep{numba2015} for just-in-time compilation and parallelization,
+scikit-learn \citep{sklearn2011} for cross-validation,
 Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating

### 2021-05-28 manuscript/content.tex
Replace residue for residuals on manuscript

@@
         square highlights the minimum RMS value.
-        (c) Root-mean square error of the residue after each iteration of the
+        (c) Root-mean square error of the residuals after each iteration of the
         coefficients estimation process.
@@
 Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
-residue after each iteration of the gradient-boosting algorithm, exposing how
+residuals after each iteration of the gradient-boosting algorithm, exposing how
 to algorithm converges at a minimum difference between the gravity disturbance

### 2021-06-02 manuscript/content.tex
Extend Australia section (#154)
Redo cross-validation using K-Fold and RMS as score. Generate more plots for
the manuscript: window size vs memory needed, RMS scores of cross-validation,
RMS vs iterations, map of the residuals with histogram inset. Add a few more
latex variables for the manuscript.

@@
 \AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
-containing \AustraliaSmallAreaNPoints points.
+containing \AustraliaSmallAreaNPoints{} points.
 We run the cross-validation with a combination of \emph{depth} ranging from
@@
 residuals after each iteration of the gradient-boosting algorithm, exposing how
-to algorithm converges at a minimum difference between the gravity disturbance
+the algorithm converges at a minimum difference between the gravity disturbance
 data and the predicted values by the equivalent sources.

### 2021-06-03 manuscript/content.tex
Add results of eql-boost on airborne survey to manuscript

@@
 \subsection{Window size and overlap in gradient boosting}
+\label{sec:window_size_and_overlap}
 
@@
 \end{figure*}
+
+\subsection{
+    Interpolating synthetic survey with gradient boosting
+}
+
+Finally we used gradient-boosted equivalent sources to interpolate the
+synthetic airborne survey. We started by locating a set of block-averaged
+equivalent sources using a block size of \EqlBoostAirborneSpacing{} and, based
+on the results presented on section \ref{sec:window_size_and_overlap}, we
+decided to use an overlap of 50\% and a window size of
+\EqlBoostAirborneWindowSize{} in order to define a considerable amount of
+windows.
+
+We estimated the \emph{depth} and \emph{damping} parameters by comparing the
+predictions against the values of the target grid, exploring \emph{depth}
+values between \EqlBoostAirborneMinDepth{} and \EqlBoostAirborneMaxDepth{} and
+\emph{damping} values between \EqlBoostAirborneMinDamping{} and
+\EqlBoostAirborneMaxDamping{} by steps of one order of magnitude.
+The most accurate predictions achieved a RMS error of
+\EqlBoostAirborneRmsScore{} with a depth of \EqlBoostAirborneDepth{} and
+a damping of \EqlBoostAirborneDamping{}.
+
+Figure \ref{fig:eql-boost-airborne}a shows the difference between the target
+grid and the predictions made by the gradient-boosted equivalent sources.
+Figure \ref{fig:eql-boost-airborne}b shows the RMS error of the
+residuals after each iteration, exposing how the gradient-boosting algorithm
+converges to a minimum fitting error.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
+    \caption{
+        Results of interpolating the airborne synthetic survey with
+        gradient-boosted equivalent sources.
+        a)~Pseudo-color maps of the differences between the target grid and the
+        interpolated synthetic airborne survey data produced gradient-boosted
+        equivalent sources.
+        b)~Root-mean squared error of the residuals after each iteration of the
+        gradient-boosting algorithm.
+}
+\label{fig:eql-boost-airborne}
+\end{figure}
 

### 2021-06-04 manuscript/content.tex
Remove step-size coefficient from manuscript

@@
 \begin{equation}
-    \mathbf{d} = \sum_{k=1}^K \alpha_k \mathbf{A}_k \mathbf{c}_k \ .
+    \mathbf{d} = \sum_{k=1}^K \mathbf{A}_k \mathbf{c}_k \ .
     \label{eq:gb-linear-model}
 \end{equation}
+
+\noindent Because of the linearity of the problem, the step-size parameters
+can be included into the parameter vector $\mathbf{c}_k$.
 
@@
 \citet{friedman2001} demonstrates that this corresponds to a steepest-descent
-optimization in the so-called ``function space'', with $\alpha_k$ corresponding
-to step sizes in steepest descent.
+optimization in the so-called ``function space''.
 The adaptation of the gradient boosting method to find the damped least-squares
-solutions for the $K$ parameters vectors $\mathbf{c}_k$ and step sizes
-$\alpha_k$ in Eq.~\ref{eq:gb-linear-model} is presented in
+solutions for the $K$ parameters vectors $\mathbf{c}_k$ in
+Eq.~\ref{eq:gb-linear-model} is presented in
 Algorithm~\ref{alg:gradient_boosting}.
@@
 
-    $
-      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
-      \left(
-        \left\lVert
-          \mathbf{r}_{k - 1} - \alpha \mathbf{d}_k
-        \right\rVert ^ 2
-      \right)
-      = \dfrac{
-        \mathbf{r}_{k-1}\trans \mathbf{d}_k
-      }{
-        \mathbf{d}_k\trans \mathbf{d}_k
-      }
-    $
-    \nllabel{alg:stepsize}
-    \;
-
-    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
+    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \mathbf{d}_k$
     \nllabel{alg:residual}
@@
 
-After all $\alpha_k$ step sizes and $\mathbf{c}_k$ coefficients vectors
-are estimated, we can predict the effect of the additive equivalent source
-model on any point through the summation
+After all $\mathbf{c}_k$ coefficients vectors are estimated, we can predict the
+effect of the additive equivalent source model on any point through the
+summation
 
@@
     \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
-    \alpha_k \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
+    \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
     \ ,
@@
 while using all available data when calculating the step size and residuals
-(steps \ref{alg:predicted}, \ref{alg:stepsize}, and \ref{alg:residual}
+(steps \ref{alg:predicted} and \ref{alg:residual}
 of algorithm~\ref{alg:gradient_boosting}).
@@
 
-    $
-      \alpha_k = \underset{\alpha}{\mathrm{argmin}}
-      \left(
-        \left\lVert
-          \mathbf{r}_{k - 1} - \alpha \mathbf{d}_k
-        \right\rVert ^ 2
-      \right)
-      = \dfrac{
-        \mathbf{r}_{k-1}\trans \mathbf{d}_k
-      }{
-        \mathbf{d}_k\trans \mathbf{d}_k
-      }
-    $
-    \;
-
-    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \alpha_k\mathbf{d}_k$
+    $\mathbf{r}_k = \mathbf{r}_{k - 1} - \mathbf{d}_k$
     \;
@@
 
-The influence of distance sources on the solution is maintained by using the
-entire set of data points when calculating
-the step size $\alpha_k$ and updating the residuals vector.
-In this case, the step size prevents the algorithm from worsening the fit on
-data points that fall outside of the current window.
-As such, it improves the convergence of the solution and ensures that the
-overall misfit decreases with iteration.
-
 It is worth noting that two sets of equivalent sources obtained through two
@@
 original $M$ sources.
-After each iteration of the gradient-boosting algorithm, we add the
-multiplication of the estimated coefficients $\hat{\mathbf{c}}_k$ and the
-step-size $\alpha_k$ to the corresponding elements of vector $\mathbf{c}$.
+After each iteration of the gradient-boosting algorithm, we add the estimated
+coefficients $\hat{\mathbf{c}}_k$ to the corresponding elements of vector
+$\mathbf{c}$.
 Because the relation between the source coefficients and the effect they
@@
 (ii)~we use only data points within the window when fitting, what enables the
-use of larger datasets;
-(iii)~experience shows that the step size parameter improves the convergence of
-the solution, particularly when using only the data inside the windows for
-fitting.
+use of larger datasets.
 

### 2021-06-04 manuscript/content.tex
Small changes to manuscript, improve format of RMS scores

@@
 
-Figure \ref{fig:eql-boost-airborne}a shows the difference between the target
+Figure \ref{fig:eql-boost-airborne}a shows the differences between the target
 grid and the predictions made by the gradient-boosted equivalent sources.
@@
 converges to a minimum fitting error.
+
+Worth noting that the RMS error achieved by the gradient-boosted equivalent
+sources is comparable to the values obtained by the regular equivalent sources
+in Section \ref{sec:synthetic_distributions}.
 

### 2021-06-04 notebooks/boost_and_layouts/eql_boost.py
Drop line search and the step size coefficient (#155)
Remove the line search option from the codebase. Move the notebook for
eql-boost the airborne survey after the ones that determine window size and
ammount of overlap. Update the results. Run Australia notebook without
line-search Add a new subsection to manuscript with the results of gridding the
airborne survey with gradient-boosting. Remove step-size coefficient from
manuscript: remove it from the equations, text and algorithms. Add two more
tests on the eql-boost-synthetic notebook: one that grids the airborne
synthetic survey without sh

@@ -61,14 +61,6 @@ class EQLHarmonicBoost(EQLHarmonic):
         number generator. If None, the random number generator is the
         ``RandomState`` instance used by `np.random`. Ignored if ``shuffle`` is
         False. Default None.
-    line_search : bool
-        If True, the gradient boosting method fits the step-size parameter on
-        each iteration in order to minimize the misfit between the effect of
-        the fitted coefficients on that iteration on every observation point
-        and the previous residue. This helps to stabilize the convergence and
-        to take into account, to some extent, the effect of the fitted
-        coefficients on observation points outside the current window. If
-        False, only the source coefficients are fitted. Default to True.
 
     Attributes
     ----------
@@ -95,14 +87,12 @@ class EQLHarmonicBoost(EQLHarmonic):
         warm_start=False,
         shuffle=True,
         random_state=None,
-        line_search=True,
     ):
         super().__init__(damping=damping, points=points, relative_depth=relative_depth)
         self.window_size = window_size
         self.warm_start = warm_start
         self.shuffle = shuffle
         self.random_state = random_state
-        self.line_search = line_search
 
     def fit(self, coordinates, data, weights=None):
         """
@@ -205,6 +195,7 @@ class EQLHarmonicBoost(EQLHarmonic):
                 self.damping,
                 copy_jacobian=True,
             )
+            # Predict field of the sources in the window on every data point
             predicted[:] = 0
             predict_numba_parallel(
                 coordinates,
@@ -213,12 +204,11 @@ class EQLHarmonicBoost(EQLHarmonic):
                 predicted,
                 greens_func_cartesian,
             )
-            if self.line_search:
-                step = np.sum(residue * predicted) / np.sum(predicted ** 2)
-                predicted *= step
-                coeffs_chunk *= step
+            # Update the residue
             residue -= predicted
+            # Add RMS of the residue
             errors.append(np.sqrt(np.mean(residue ** 2)))
+            # Update source coefficients
             self.coefs_[point_window] += coeffs_chunk
         self.errors_ = np.array(errors)
 

### 2021-06-07 manuscript/content.tex
Extend comments on damping parameter

@@
 To solve this issue, we first scale the Jacobian matrix so that its elements
-are unitless and each column has unit variance.
+are dimensionless and each column has unit variance.
 We define a diagonal matrix $\mathbf{S}$
@@
 
-\noindent where $\mathbf{B}$ is the scaled and unitless Jacobian matrix and
-$\mathbf{m}$ is a vector containing scaled coefficients with the same units as
-the data.
+\noindent where $\mathbf{B}$ is the scaled and dimensionless Jacobian matrix
+and $\mathbf{m}$ is a vector containing scaled coefficients with the same units
+as the data.
 
@@
 $\mathbf{c}$.
+Using a dimensionless damping parameter allows us to narrow the range of values
+of $\lambda$ that would generate the most accurate predictions, irrespective
+of the dataset and its units.
+The damping parameter controls the amount of regularization that is be applied:
+a large damping value would generate smooth solutions that fail to reproduce
+the high frequency components, while a small value would overfit the data,
+failing to produce accurate predictions.
 From experience, we recommend searching for suitable $\lambda$ values between
-$10^{-8}$ and $10^{2}$ varying by order-of-magnitude, irrespective of the
+$10^{-6}$ and $10^{4}$ varying by order-of-magnitude, irrespective of the
 dataset.
+The choice of the damping and any other hyper-parameter could be done through
+validation methods, such as cross-validation algorithms.
 

### 2021-06-08 manuscript/content.tex
Update manuscript/content.tex
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

@@
 the high frequency components, while a small value would overfit the data,
-failing to produce accurate predictions.
+failing to produce realistic interpolation results.
 From experience, we recommend searching for suitable $\lambda$ values between

### 2021-06-08 manuscript/content.tex
Update manuscript/content.tex
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>
Extend comments on damping parameter (#157)
Add results of eql boost without shuffling

@@
 dataset.
-The choice of the damping and any other hyper-parameter could be done through
-validation methods, such as cross-validation algorithms.
+The choice of the damping and other hyper-parameters like the source depth could be done through
+well-established statistical methods, such as cross-validation.
 
@@
 
-Fig~\ref{fig:ground-survey-differences}
+Fig.~\ref{fig:ground-survey-differences}
 and~\ref{fig:airborne-survey-differences} show the differences between the
@@
 
-Figure \ref{fig:eql-boost-airborne}a shows the differences between the target
+Figure~\ref{fig:eql-boost-airborne}a shows the differences between the target
 grid and the predictions made by the gradient-boosted equivalent sources.
-Figure \ref{fig:eql-boost-airborne}b shows the RMS error of the
+Figure~\ref{fig:eql-boost-airborne}b shows the RMS error of the
 residuals after each iteration, exposing how the gradient-boosting algorithm
@@
 
-\begin{figure}
+\begin{figure*}
     \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
@@
         Results of interpolating the airborne synthetic survey with
-        gradient-boosted equivalent sources.
-        a)~Pseudo-color maps of the differences between the target grid and the
-        interpolated synthetic airborne survey data produced gradient-boosted
-        equivalent sources.
-        b)~Root-mean squared error of the residuals after each iteration of the
-        gradient-boosting algorithm.
+        gradient-boosted equivalent sources with overlapping windows being
+        iterated in random order (a and b), and with overlapping windows being
+        iterated in sequential order (c and d).
+        (a and c)~Pseudo-color maps of the differences between the target grid
+        and the interpolated synthetic airborne survey data produced
+        gradient-boosted.
+        (b and d)~Root-mean squared error of the residuals after each iteration
+        of the gradient-boosting algorithm.
 }
 \label{fig:eql-boost-airborne}
-\end{figure}
+\end{figure*}
+
+With the goal of highlighting the importance of randomizing the order in which
+the overlapping windows are iterated, we interpolated the airborne synthetic
+survey using the same estimated values for the \emph{damping} and
+\emph{depth} but disabling the random shuffling of the windows, iterating over
+them in sequential order.
+Fig.~\ref{fig:eql-boost-airborne}c shows the differences between the target
+grid and the predictions made by the gradient-boosted equivalent sources
+without random shuffling the windows.
+Fig.~\ref{fig:eql-boost-airborne}d shows the RMS error of the
+residuals after each iteration.
+These results show how the gradient-boosted equivalent sources outperform by
+iterating over the overlapping windows in sequential order: they fail to
+produce realistic and accurate predictions while the speed in which the
+algorithm converges is considerable smaller.
 
@@
 The results of our tests on synthetic data
-(Figs~\ref{fig:ground-survey-differences}
+(Figs.~\ref{fig:ground-survey-differences}
 and~\ref{fig:airborne-survey-differences}) show that there are no significant
@@
 
-The results shown in Figs~\ref{fig:gradient-boosted-comparison}b
+The results shown in Figs.~\ref{fig:gradient-boosted-comparison}b
 and~\ref{fig:gradient-boosted-comparison}d indicate that using
@@
 producing accurate predictions in reasonable times.
+
+Finally, the results in Fig.~\ref{fig:eql-boost-airborne} highlight the
+importance of randomize the order in which the overlapping windows are
+iterated.
+Running the gradient boosting process by sequentially iterating over the
+overlapping windows produce predictions of considerable lower quality with
+a much smaller convergence rate than the ones obtained by a previous random
+shuffling of the windows.
 
@@
 possible that creates Jacobian matrices that still fit into computer memory.
+Moreover, randomizing the order in which the overlapping windows are iterated
+is highly recommended to improve the quality of the predictions and increasing
+the convergence rate of the algorithm.
 

### 2021-06-09 manuscript/content.tex
Replace outperform for underperform

@@
 residuals after each iteration.
-These results show how the gradient-boosted equivalent sources outperform by
+These results show how the gradient-boosted equivalent sources underperform by
 iterating over the overlapping windows in sequential order: they fail to

### 2021-06-15 manuscript/content.tex
Move damping text and add Martinez and Li (2016)
Fix typo and move explanation about damping to where it's first
introduced.

--- 2021-06-08 manuscript/content.tex
@@
 regularization or ridge regression) that is used to stabilize the solution.
+The damping parameter controls the amount of regularization that will be applied:
+a large damping value would generate smooth solutions that fail to reproduce
+the high frequency components, while a small value would overfit the data,
+failing to produce realistic interpolation results \citep{martinez2016}.
 
@@
 of the dataset and its units.
-The damping parameter controls the amount of regularization that is be applied:
-a large damping value would generate smooth solutions that fail to reproduce
-the high frequency components, while a small value would overfit the data,
-failing to produce realistic interpolation results.
 From experience, we recommend searching for suitable $\lambda$ values between
-$10^{-6}$ and $10^{4}$ varying by order-of-magnitude, irrespective of the
-dataset.
-The choice of the damping and any other hyper-parameter could be done through
-validation methods, such as cross-validation algorithms.
+$10^{-6}$ and $10^{4}$ varying by order-of-magnitude.
+The choice of the damping and other hyper-parameters like the source depth
+could be done through well-established statistical methods, such as
+cross-validation.
 

### 2021-06-25 manuscript/content.tex
Minor corrections to the text
Clarify that we mean "overly large and small" values. Remove the colon and 
start a new sentence.

@@
 regularization or ridge regression) that is used to stabilize the solution.
-The damping parameter controls the amount of regularization that will be applied:
-a large damping value would generate smooth solutions that fail to reproduce
-the high frequency components, while a small value would overfit the data,
-failing to produce realistic interpolation results \citep{martinez2016}.
+The damping parameter controls the amount of regularization that will be applied.
+An overly large value would generate a smooth solution that fails to reproduce
+the high frequency components of the data, while an overly small value would 
+result in over-fitting, thus failing to produce realistic interpolation results 
+\citep{martinez2016}.
 

### 2021-06-25 manuscript/content.tex

--- 2021-06-09 manuscript/content.tex
@@
 produce realistic and accurate predictions while the speed in which the
-algorithm converges is considerable smaller.
+algorithm converges is smaller.
 
@@
 Finally, the results in Fig.~\ref{fig:eql-boost-airborne} highlight the
-importance of randomize the order in which the overlapping windows are
+importance of randomizing the order in which the overlapping windows are
 iterated.
-Running the gradient boosting process by sequentially iterating over the
-overlapping windows produce predictions of considerable lower quality with
-a much smaller convergence rate than the ones obtained by a previous random
-shuffling of the windows.
+Running the gradient boosting algorithm sequentially produces less accurate 
+predictions and decreases the convergence rate.
 
@@
 Moreover, randomizing the order in which the overlapping windows are iterated
-is highly recommended to improve the quality of the predictions and increasing
+is essential to improve the quality of the predictions and increase
 the convergence rate of the algorithm.

### 2021-06-25 manuscript/content.tex

@@
 regularization or ridge regression) that is used to stabilize the solution.
+The damping parameter controls the amount of regularization that will be applied.
+An overly large value would generate a smooth solution that fails to reproduce
+the high frequency components of the data, while an overly small value would 
+result in over-fitting, thus failing to produce realistic interpolation results 
+\citep{martinez2016}.
 
@@
 of the dataset and its units.
-The damping parameter controls the amount of regularization that is be applied:
-a large damping value would generate smooth solutions that fail to reproduce
-the high frequency components, while a small value would overfit the data,
-failing to produce realistic interpolation results.
 From experience, we recommend searching for suitable $\lambda$ values between
-$10^{-6}$ and $10^{4}$ varying by order-of-magnitude, irrespective of the
-dataset.
-The choice of the damping and other hyper-parameters like the source depth could be done through
-well-established statistical methods, such as cross-validation.
+$10^{-6}$ and $10^{4}$ varying by order-of-magnitude.
+The choice of the damping and other hyper-parameters like the source depth
+could be done through well-established statistical methods, such as
+cross-validation.
 

### 2021-06-25 manuscript/content.tex
Add a section on collocation
Included a paragraph on collocation explaining what it's use for and
that it suffers from the same computational limitations of EQL. Also
broke apart the paragraph where we compare all the different EQL papers.
It was huge and a bit difficult to follow. Had to add some text to the
location strategies part otherwise it would be a single sentence.

@@
 
+It also worth mentioning the least-squares collocation method
+(LSC), which is widely used in geodesy
+\citep[][and references therein]{tscherning2015}.
+LCS is often applied to combine and interpolate different linear functionals of
+the disturbing gravity potential (gravity anomalies, gravity disturbances,
+deflections of the vertical, geoid height, et cetera).
+Like equivalent sources, collocation also requires the solution of a large
+linear system of the order of the number of observed data.
+As such, it's practical application suffers from the same computational
+challenges.
+
 Many variants of the equivalent sources technique have been proposed, often
@@
 the location of the sources, and (iii) the solution strategy.
+
 The type of source is most commonly a point mass for gravity or dipole for
@@
 equivalent sources \citep{cordell1992}.
-The sources are often distributed on a regular grid at a constant depth
-\citep[e.g.,~][]{leao1989, barnes2011, oliveira2013}
-or placed beneath each data point \citep[e.g.,~][]{cordell1992, siqueira2017}.
-The model is usually estimated through damped least-squares, which imposes a
-heavy computational load when the number of data points is large (e.g.,
-airborne and satellite surveys).
+
+The location of sources often follows one of two strategies.
+The most common approach is to distribute sources on a regular grid at a
+constant depth \citep[e.g.,~][]{leao1989, barnes2011, oliveira2013}.
+Alternatively, sources can be placed beneath each data point
+\citep[e.g.,~][]{cordell1992, siqueira2017}.
+Some recent work by \citet{li2020} places the sources in two overlapping layers
+at different depths.
+
+The coefficients of the equivalent source model are often estimated through
+damped least-squares.
+This imposes a heavy computational load when the number of data points is
+large (e.g., airborne and satellite surveys).
 To reduce the computational load, \citet{mendonca1994} built the solution

### 2021-06-25 manuscript/content.tex
Review the first part of the introduction
Some small wording changes.

@@
 total-field magnetic anomalies, are widely used in geophysical exploration for
-their relatively low cost of acquisition.
+their low cost of acquisition.
 These data can be surveyed using ground, airborne, shipborne, or satellite
 systems.
-In ground surveys, the data are often gathered following irregular paths or
+During ground surveys, the data are often gathered following irregular paths or
 networks along the surface of the terrain, leading to highly variable
 elevations in mountainous regions.
-On airborne surveys, the data are gathered along flight lines, producing a
-large number of measurements concentrated along almost straight lines.
+Airborne and satellite surveys gather data along flight lines, producing
+closely spaced measurements along almost straight lines but with larger spacing
+between adjacent lines.
 Measurement height can also change because of the vertical movement of the
@@
 for example continuous curvature splines in tension \citep{smith1990},
-bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
+bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging
+\citep{hansen1993}.
 These general-purpose methods have limitations when it comes to interpolating
-potential field data:
+potential field data, namely
 (i)~they are not able to take into account the variable height of the
@@
 is the equivalent sources technique (also known as equivalent layer, radial
-basis functions, or Green's functions interpolation), first introduced by
-\citet{dampney1969}.
-It consists in fitting a model of finite elementary sources to the data and
-using this model to predict new data values.
+basis functions, or Green's functions interpolation).
+First introduced by \citet{dampney1969}, the method consists in fitting a model
+of finite elementary sources to the data and using this model to predict new
+data values.
 Besides interpolation, equivalent sources have been used for
@@
 
-It also worth mentioning the least-squares collocation method
+It is also worth mentioning the least-squares collocation method
 (LSC), which is widely used in geodesy

### 2021-06-25 manuscript/content.tex
Review the end of the introduction

@@
 In the present study,
-we propose a two strategies for reducing the computational load of
+we propose two strategies for reducing the computational load of
 the equivalent sources technique:
@@
 The first strategy consists in dividing the survey area into horizontal blocks
-and assign one source to each block, located at the median horizontal location
-of the data points. For airborne, shipborne, and satellite surveys, which are
-oversampled along tracks, this can greatly reduce the size of the inverse
-problem while retaining the same quality of interpolation.
+and assigning a single source to each block, located at the median horizontal
+location of the data points.
+For airborne, shipborne, and satellite surveys, which are oversampled along
+tracks, this can greatly reduce the size of the inverse problem while retaining
+the same quality of interpolation.
 
@@
 iteratively by operating on individual overlapping windows.
-Thus, our method solves several much smaller least-squares problems instead of
-a large one.
+As a result, our method solves several much smaller least-squares problems
+instead of a large one.
 This has some similarities with the strategy used by \citet{leao1989} but
@@
 Finally, a combination of both strategies is used to process a collection of
-around 1.7 million ground gravity data measurements from Australia.
+approximately 1.7 million ground gravity data measurements from Australia.
 

### 2021-06-25 manuscript/content.tex
Review the start of the methods

@@
 
-Here, we will follow the ``generalized equivalent sources'' of
-\citet{cordell1992} and assume that any harmonic function $d(\mathbf{p})$ can
-be approximated by a sum of $M$ discrete point source effects
+We will follow the ``generalized equivalent sources'' of \citet{cordell1992}
+and assume that any harmonic function $d(\mathbf{p})$ can be approximated by a
+sum of $M$ discrete point source effects
 
@@
 \noindent in which
-$\mathbf{p}$ and $\mathbf{q}_j$ are position vectors in a 3D Cartesian space,
+$\mathbf{p}$ and $\mathbf{q}_j$ are, respectively, the position vectors in a 3D
+Cartesian space of data and sources,
 $c_j$ is a scalar coefficient related to the point source located at
@@
 and $\lVert \cdot \rVert$ represents the $\text{L}_2$ norm.
-The horizontal and vertical distribution of sources is discussed in section~\ref{sec:source_distribution}.
-
-In case we have measured the value of the harmonic field on $N$ points
+The horizontal and vertical distribution of sources is discussed in
+section~\ref{sec:source_distribution}.
+
+In case we have values of the harmonic function at $N$ discrete points
 $\{\mathbf{p}_1\ \mathbf{p}_2\ \ldots\ \mathbf{p}_N\}$,
@@
 
-\noindent where $d_i$ is the value of the potential field at the observation point $\mathbf{p}_i$.
-These equations can also be expressed as
+\noindent where $d_i$ is the calculated value at point $\mathbf{p}_i$.
+These equations can also be expressed in matrix form as
 
@@
 \noindent where $\mathbf{d}$ is a column vector containing the $N$ predicted
-values of the observed field at the observation points,
+values at the observation points,
 $\mathbf{c}$ is a column vector containing the $M$ coefficients $c_j$,
@@
 
-For a given set of $N$ observed field values $\mathbf{d}^o$,
+For a given set of $N$ observed data $\mathbf{d}^o$,
 we can find a least-squares solution to
@@
 $\mathbf{c}$ that best fit the observations.
-These values can, in turn, be used to predict the value of the harmonic field
-at any other point outside of the sources by evaluating
+These coefficients can, in turn, be used to predict the value of the harmonic
+function at any other point outside of the sources by evaluating
 Eq.~\ref{eq:eql-forward}.
 Gridding and upward continuation can thus be achieved by predicting values on
-points that fall on a regular grid or at different heights.
+points that fall on a regular grid or at different heights, respectively.
 

### 2021-06-25 manuscript/content.tex
Review the least-squares part

@@
 Jacobian matrix elements.
-The second term on the right-hand side of the equation is a zeroth-order
-Tikhonov regularization \citep{tikhonov1977} (also known as a damping
-regularization or ridge regression) that is used to stabilize the solution.
-The damping parameter controls the amount of regularization that will be applied.
+The second term on the right-hand side of Eq.~\ref{eq:misfit-unscaled} is the
+zeroth-order Tikhonov regularization \citep{tikhonov1977}, also known as a
+damping regularization, that is used to stabilize the solution.
+
+The damping parameter controls the amount of regularization that will be
+applied.
 An overly large value would generate a smooth solution that fails to reproduce
@@
 \citep{martinez2016}.
-
 The range of acceptable values for the damping parameter $\lambda_d$ will
@@
 Consequently, this range will vary (often dramatically) between datasets,
-making it difficult to choose an appropriate value for $\lambda_d$ in practice.
+making it difficult to choose an appropriate value in practice.
 
@@
 
-\noindent where $\mathbf{B}$ is the scaled and dimensionless Jacobian matrix
-and $\mathbf{m}$ is a vector containing scaled coefficients with the same units
-as the data.
+\noindent where $\mathbf{B} = \mathbf{A} \mathbf{S}\inv$ is the scaled and
+dimensionless Jacobian matrix
+and $\mathbf{m} = \mathbf{S} \mathbf{c}$ is a vector containing scaled
+coefficients with the same units as the data.
 
@@
 $10^{-6}$ and $10^{4}$ varying by order-of-magnitude.
-The choice of the damping and other hyper-parameters like the source depth
+The choice of the damping and other hyper-parameters, like the source depth,
 could be done through well-established statistical methods, such as

### 2021-06-25 manuscript/content.tex
Add a section on collocation (#160)
Included a paragraph on collocation explaining what it's use for and
that it suffers from the same computational limitations of EQL. Also
broke apart the paragraph where we compare all the different EQL papers.
It was huge and a bit difficult to follow. Had to add some text to the
location strategies part otherwise it would be a single sentence.

--- 2021-06-25 manuscript/content.tex
@@
 total-field magnetic anomalies, are widely used in geophysical exploration for
-their low cost of acquisition.
+their relatively low cost of acquisition.
 These data can be surveyed using ground, airborne, shipborne, or satellite
 systems.
-During ground surveys, the data are often gathered following irregular paths or
+In ground surveys, the data are often gathered following irregular paths or
 networks along the surface of the terrain, leading to highly variable
 elevations in mountainous regions.
-Airborne and satellite surveys gather data along flight lines, producing
-closely spaced measurements along almost straight lines but with larger spacing
-between adjacent lines.
+On airborne surveys, the data are gathered along flight lines, producing a
+large number of measurements concentrated along almost straight lines.
 Measurement height can also change because of the vertical movement of the
@@
 for example continuous curvature splines in tension \citep{smith1990},
-bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging
-\citep{hansen1993}.
+bi-harmonic (thin-plate) splines \citep{sandwell1987}, and kriging \citep{hansen1993}.
 These general-purpose methods have limitations when it comes to interpolating
-potential field data, namely
+potential field data:
 (i)~they are not able to take into account the variable height of the
@@
 is the equivalent sources technique (also known as equivalent layer, radial
-basis functions, or Green's functions interpolation).
-First introduced by \citet{dampney1969}, the method consists in fitting a model
-of finite elementary sources to the data and using this model to predict new
-data values.
+basis functions, or Green's functions interpolation), first introduced by
+\citet{dampney1969}.
+It consists in fitting a model of finite elementary sources to the data and
+using this model to predict new data values.
 Besides interpolation, equivalent sources have been used for
@@
 In the present study,
-we propose two strategies for reducing the computational load of
+we propose a two strategies for reducing the computational load of
 the equivalent sources technique:
@@
 The first strategy consists in dividing the survey area into horizontal blocks
-and assigning a single source to each block, located at the median horizontal
-location of the data points.
-For airborne, shipborne, and satellite surveys, which are oversampled along
-tracks, this can greatly reduce the size of the inverse problem while retaining
-the same quality of interpolation.
+and assign one source to each block, located at the median horizontal location
+of the data points. For airborne, shipborne, and satellite surveys, which are
+oversampled along tracks, this can greatly reduce the size of the inverse
+problem while retaining the same quality of interpolation.
 
@@
 iteratively by operating on individual overlapping windows.
-As a result, our method solves several much smaller least-squares problems
-instead of a large one.
+Thus, our method solves several much smaller least-squares problems instead of
+a large one.
 This has some similarities with the strategy used by \citet{leao1989} but
@@
 Finally, a combination of both strategies is used to process a collection of
-approximately 1.7 million ground gravity data measurements from Australia.
+around 1.7 million ground gravity data measurements from Australia.
 

### 2021-06-28 manuscript/content.tex
Clarify the part about the A_k Jacobian matrices
Break apart the item that describes them to highlight the definition.

--- 2021-06-25 manuscript/content.tex
@@
 and $f$ is a function of the parameter vector $\mathbf{c}_k$.
-For linear regression problems, these additive models can be written as the
-matrix equation
+For linear problems, these additive models can be written as the matrix
+equation
 
@@
 
-\noindent Because of the linearity of the problem, the step-size parameters
-can be included into the parameter vector $\mathbf{c}_k$.
+\noindent Because of the linearity of the $f(\mathbf{c}_k)$ functions, the
+$\alpha_k$ step-size parameters can be incorporated into the parameter vector
+$\mathbf{c}_k$.
 
@@
     be greater than $M$.
-  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
-    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
-    matrix between those sources and every data point of the survey.
+  \item Define vector $\mathbf{c}_k$ as the coefficients of the equivalent
+    sources of the $k$-th window.
+  \item Define matrix $\mathbf{A}_k$ as the Jacobian matrix between the sources
+    in the $k$-th window and all $N$ data points of the survey.
   \item Model the predicted data as a superposition of the effects of the $K$
-    separate sets of equivalent sources.
+    separate sets of equivalent sources (i.e., Eq.~\ref{eq:gb-linear-model}).
 \end{enumerate}

### 2021-06-28 manuscript/content.tex
Clarify the part about the A_k Jacobian matrices
Break apart the item that describes them to highlight the definition.

@@
     be greater than $M$.
-  \item Define vector $\mathbf{c}_k$ as the coefficients of the equivalent
-    sources of the $k$-th window.
-  \item Define matrix $\mathbf{A}_k$ as the Jacobian matrix between the sources
-    in the $k$-th window and all $N$ data points of the survey.
+  \item Define vector $\mathbf{c}_k$ as the $M_k$ coefficients of the
+    equivalent sources of the $k$-th window.
+  \item Define matrix $\mathbf{A}_k$ as the $N \times M_k$ Jacobian matrix
+    between the sources in the $k$-th window and all $N$ data points of the
+    survey.
   \item Model the predicted data as a superposition of the effects of the $K$
@@
 The adaptation of the gradient boosting method to find the damped least-squares
-solutions for the $K$ parameters vectors $\mathbf{c}_k$ in
+solutions for the $K$ parameter vectors $\mathbf{c}_k$ in
 Eq.~\ref{eq:gb-linear-model} is presented in
@@
   \setstretch{1.5}
-  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
+  Define the residual vector $\mathbf{r}_{0} = \mathbf{d}^o$ \;
   \For{ $k = 1$ \KwTo $K$ }{
 
-    calculate $N \times M_k$ Jacobian matrix $\mathbf{A}_k$
+    Calculate the $N \times M_k$ Jacobian matrix $\mathbf{A}_k$
     \;
@@
     \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
-    \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
+    \frac{{c_k}_j}{\left\lVert \mathbf{p} - {\mathbf{q}_k}_j \right\rVert}
     \ ,
+    \label{eq:eql-forward-gb}
 \end{equation}
 
-\noindent where ${c_k}_j$ is the $j$-th element of the $\mathbf{c}_k$ vector.
+\noindent
+in which ${c_k}_j$ is the $j$-th element of the $\mathbf{c}_k$ vector and the
+${\mathbf{q}_k}_j$ is the position vector of the $j$-th source of the $k$-th
+window.
 
@@
 the order in which the $K$ windows are used in the gradient boosting algorithm.
+Section~\ref{sec:gb_interpolation} explores the effect of randomization in the
+convergence rate of the algorithm and the accuracy of the interpolation.
 
@@
 
-We can improve the efficiency of the algorithm further by using only the $N_k$ data
-points that fall within the $k$-th window for fitting the sources
-(steps \ref{alg:scale} and \ref{alg:fit} of
-algorithm~\ref{alg:gradient_boosting}),
-while using all available data when calculating the step size and residuals
-(steps \ref{alg:predicted} and \ref{alg:residual}
-of algorithm~\ref{alg:gradient_boosting}).
-By doing so, we can reduce the size of the Jacobian matrix further to $N_k
-\times M_k$ elements.
-The forward modeling operation performed in step \ref{alg:predicted} can be
-done by a summation (Eq.~\ref{eq:forward-sum})
-instead of a matrix-vector product, which allows us to avoid computing and
-storing the larger $N \times M_k$ Jacobian at any point.
-Algorithm~\ref{alg:gradient_boosting_window} incorporates these changes and is
-the final \textit{gradient-boosted equivalent source algorithm}.
-Figure~\ref{fig:gradient-boosting-schematics} shows a sketch of the
-gradient-boosted equivalent source algorithm with a set of observation points
-that simulate a ground survey and locating one source below each data point.
+We can improve the efficiency of the algorithm further by:
+
+\begin{enumerate}
+  \item Using only the $N_k$ data points that fall within the $k$-th window for
+    fitting the sources (steps \ref{alg:scale} and \ref{alg:fit} of
+    algorithm~\ref{alg:gradient_boosting}).
+    By doing so, we can replace the $N \times M_k$ Jacobian matrix $\mathbf{A}_k$
+    with the smaller $N_k \times M_k$ matrix $\tilde{\mathbf{A}}_k$.
+    We still use all $N$ data points when calculating the predicted data and
+    residuals (steps \ref{alg:predicted} and \ref{alg:residual} of
+    algorithm~\ref{alg:gradient_boosting}).
+  \item The forward modeling operation performed in step \ref{alg:predicted}
+    can be done by a summation (Eq.~\ref{eq:forward-sum}) instead of a
+    matrix-vector product, which allows us to avoid computing and storing the
+    larger $N \times M_k$ matrix $\mathbf{A}_k$ at any point.
+\end{enumerate}
+
+Algorithm~\ref{alg:gradient_boosting_window} is the final
+\textit{gradient-boosted equivalent sources algorithm} which incorporates these
+changes.
+Figure~\ref{fig:gradient-boosting-schematics} shows a sketch of the algorithm
+steps applied a set of observation points that simulate a ground survey and
+locating one source below each data point.
 
@@
   \setstretch{1.5}
-  define the residual vector: $\mathbf{r}_{0} = \mathbf{d}^o$ \;
+  Define the residual vector $\mathbf{r}_{0} = \mathbf{d}^o$ \;
   \For{ $k = 1$ \KwTo $K$ }{
 
-    select weights $\tilde{\mathbf{W}}_k$ and residuals
-    $\tilde{\mathbf{r}}_{k - 1}$ for data points inside the $k$-th window only
+    Select weights $\tilde{\mathbf{W}}_k$ and residuals
+    $\tilde{\mathbf{r}}_{k - 1}$ for data points inside the $k$-th window
     \;
 
-    calculate $N_k \times M_k$ Jacobian matrix $\tilde{\mathbf{A}}_k$
-    with data points and sources inside the $k$-th window only
+    Calculate Jacobian matrix $\tilde{\mathbf{A}}_k$ with data points and
+    sources inside the $k$-th window
     \;
@@
 
-    calculate $ \mathbf{d}_k $, where
+    Calculate $ \mathbf{d}_k $, where
     $
@@
     \right\rVert}
-    \ \forall i=1\ \text{to}\ N
+    \quad \forall\ i=1\ \text{to}\ N
     $
@@
   \setstretch{1}
-  \caption{Gradient-boosted equivalent source algorithm.}
+  \caption{Gradient-boosted equivalent sources algorithm.}
   \label{alg:gradient_boosting_window}
@@
 coefficients multiple times: one time for every window that covers each source.
-This fact can be exploited in order to save some computational memory.
-Instead of storing all of the multiple $\mathbf{c}_k$ vectors
+This fact can be exploited in order to save computer memory.
+Instead of storing all of the $\mathbf{c}_k$ vectors
 (Eq.~\ref{eq:gb-linear-model}), we can initialize a single $\mathbf{c}$ vector
@@
 $\mathbf{c}$.
-Because the relation between the source coefficients and the effect they
-generate is linear, we can safely compute the resulting field through
-Equation~\ref{eq:eql-forward}.
+Because the forward modelling function is linear, we can safely compute the
+resulting field through Eq.~\ref{eq:eql-forward} instead of
+Eq.~\ref{eq:eql-forward-gb}.
 This way, the memory needed to store the entire set of estimated coefficients
@@
     horizontal location of each data point (Fig.~\ref{fig:source_layouts}b).
-    Therefore, the number of sources is be equal to the number of observations
-    ($N=M$).
+    Therefore, the number of sources is equal to the number of observations
+    ($M=N$).
   \item
@@
     underdetermined problems since a large number of sources is required
-    ($N<M$).
+    ($M>N$).
 \end{enumerate}
@@
         any observation point are omitted.
-    \item Assign one point source to the median horizontal position calculated
-        in step \ref{item:median-position}.
+    \item Assign one point source to each of the median horizontal positions
+      calculated in step \ref{item:median-position}.
 \end{enumerate}
@@
 along a flight line and between adjacent lines, helping to reduce aliasing
-effects in generated grids.
-We will demonstrate through tests on synthetic data that the block-averaged sources
-layout is able to interpolate with comparable accuracy to other layouts while
-using a fraction of the equivalent sources.
+effects in the generated grids.
+In Section~\ref{sec:synthetic_distributions}, we demonstrate through tests on
+synthetic data that the block-averaged sources layout is able to interpolate
+with comparable accuracy to other layouts while using a fraction of the
+equivalent sources.
 
@@
         (a)~a \emph{constant depth} at a chosen vertical coordinate,
-        (b)~a \emph{relative depth} determined by uniformly downward shifting
+        (b)~a \emph{relative depth} determined by uniformly shifting downward
         the vertical coordinate of data points,
@@
 \noindent
-in which $z$ is the depth of an equivalent source,
+in which $z$ is the vertical coordinate (positive downwards) of an equivalent
+source,
 $\Delta z$ is a relative depth shift that is the same for all sources,
@@
 of all data points.
-Finally, for \emph{block-averaged sources} it will be the average vertical
-coordinate of data within the corresponding block.
-
-In the following sections, we will test the effectiveness and trade-offs of
-each of these strategies on synthetic data.
+Finally, for \emph{block-averaged sources} it will be the median vertical
+coordinate of the data within the corresponding block.
+
+In Section~\ref{sec:synthetic_distributions}, we test the effectiveness each of
+these strategies on synthetic data.
 
@@
 }
+\label{sec:gb_interpolation}
 

### 2021-06-28 manuscript/content.tex
Define M_k and fix summation equation
The position vector is not q_j but q_k_j.

--- 2021-06-28 manuscript/content.tex
@@
     \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
-    \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
+    \frac{{c_k}_j}{\left\lVert \mathbf{p} - {\mathbf{q}_k}_j \right\rVert}
     \ ,
@@
 
-\noindent where ${c_k}_j$ is the $j$-th element of the $\mathbf{c}_k$ vector.
+\noindent
+in which ${c_k}_j$ is the $j$-th element of the $\mathbf{c}_k$ vector and the
+${\mathbf{q}_k}_j$ is the position vector of the $j$-th source of the $k$-th
+window.
 

### 2021-06-28 manuscript/content.tex
Refer to new gb interpolation section in methods
Point to it when we talk about randomizing windows.
Break up the optimization used in EQL GB
Using only data inside the window and forward modelling by summation
were locked inside a large paragraph. Use an enumerate to make it clear
that there are two optimizations and make them jump out in the text a
bit more.

--- 2021-06-28 manuscript/content.tex
@@
     horizontal location of each data point (Fig.~\ref{fig:source_layouts}b).
-    Therefore, the number of sources is equal to the number of observations
-    ($M=N$).
+    Therefore, the number of sources is be equal to the number of observations
+    ($N=M$).
   \item
@@
     underdetermined problems since a large number of sources is required
-    ($M>N$).
+    ($N<M$).
 \end{enumerate}
@@
         any observation point are omitted.
-    \item Assign one point source to each of the median horizontal positions
-      calculated in step \ref{item:median-position}.
+    \item Assign one point source to the median horizontal position calculated
+        in step \ref{item:median-position}.
 \end{enumerate}
@@
 along a flight line and between adjacent lines, helping to reduce aliasing
-effects in the generated grids.
-In Section~\ref{sec:synthetic_distributions}, we demonstrate through tests on
-synthetic data that the block-averaged sources layout is able to interpolate
-with comparable accuracy to other layouts while using a fraction of the
-equivalent sources.
+effects in generated grids.
+We will demonstrate through tests on synthetic data that the block-averaged sources
+layout is able to interpolate with comparable accuracy to other layouts while
+using a fraction of the equivalent sources.
 
@@
         (a)~a \emph{constant depth} at a chosen vertical coordinate,
-        (b)~a \emph{relative depth} determined by uniformly shifting downward
+        (b)~a \emph{relative depth} determined by uniformly downward shifting
         the vertical coordinate of data points,
@@
 \noindent
-in which $z$ is the vertical coordinate (positive downwards) of an equivalent
-source,
+in which $z$ is the depth of an equivalent source,
 $\Delta z$ is a relative depth shift that is the same for all sources,
@@
 of all data points.
-Finally, for \emph{block-averaged sources} it will be the median vertical
-coordinate of the data within the corresponding block.
-
-In Section~\ref{sec:synthetic_distributions}, we test the effectiveness each of
-these strategies on synthetic data.
+Finally, for \emph{block-averaged sources} it will be the average vertical
+coordinate of data within the corresponding block.
+
+In the following sections, we will test the effectiveness and trade-offs of
+each of these strategies on synthetic data.
 

### 2021-06-28 manuscript/content.tex
Review source layouts section of the methods
Nothing major, just some wording
Review the source layouts results section

--- 2021-06-28 manuscript/content.tex
@@
 the difference horizontal and vertical source distribution strategies as well
-as the gradient-boosted equivalent source method.
-To generate the data, we created a model that is made out of \NPrisms{}
-right-rectangular prisms, distributed on a region of
-\ModelEasting{}$\times$\ModelNorthing{} with depths varying between
-\ModelDepth{} and zero.
+as the gradient-boosted equivalent sources method.
+To generate the data, we created a model of \NPrisms{} right-rectangular
+prisms,
+distributed in a \ModelEasting{}$\times$\ModelNorthing{} area with depths
+varying between \ModelDepth{} and zero.
 The density contrast of prisms ranges from \ModelMinDensity{} to
@@
 To create the synthetic ground survey, we selected measurement positions from a
-portion of a public domain dataset for Southern Africa, available through the
-NOAA National Centers for Environmental Information (NCEI).
+portion of a public domain gravity dataset for Southern Africa, available
+through the NOAA National Centers for Environmental Information (NCEI).
 For the synthetic airborne survey, we used a portion of the Great Britain
@@
 
-We investigated the effect of different strategies for distributing the
-equivalent sources horizontally and vertically on interpolation accuracy.
+We investigated the effect on interpolation accuracy of different strategies
+for distributing the equivalent sources horizontally and vertically.
 To do this, we used the damped least-squares solution described in

### 2021-07-01 manuscript/content.tex
Slight tweaks to window size results

@@
 (Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
-(Fig.~\ref{fig:synthetic-layouts}c-d) .
+(Fig.~\ref{fig:synthetic-layouts}c-d).
 To avoid biasing the results, we used the same locations of equivalent sources
@@
 
-We calculated the interpolation RMS error and computation time for a fixed
-window overlap of 50\% and several window sizes.
+We calculated the interpolation RMS error (between the interpolated grid and
+the target grid in Fig.~\ref{fig:synthetic-target}) and computation time for a
+fixed window overlap of 50\% and several window sizes.
 To avoid any biases introduced by the shuffling of windows, the calculations
@@
 in the shuffling.
-Figs.~\ref{fig:gradient-boosted-comparison}a and
-\ref{fig:gradient-boosted-comparison}c show the RMS error and computation time
-required for estimating the source coefficients, respectively, as a function of
+Fig.~\ref{fig:gradient-boosted-comparison}a shows the RMS error and
+Fig.~\ref{fig:gradient-boosted-comparison}c shows the computation time
+required for estimating the source coefficients, both as functions of
 the window size.
 
-The results show that the interpolation error for gradient-boosting is
+These results show that the interpolation error for gradient-boosting is
 generally larger than the error for regular equivalent sources.

### 2021-07-01 manuscript/content.tex
Slight tweaks to caption and section for window overlap

@@
 
+\begin{figure*}
+    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
+    \caption{
+        Interpolation RMS error (a-b) and relative computation time (c-d) for
+        regular least-squares equivalent sources (orange dashed lines) and
+        gradient-boosted equivalent sources (blue dots and error bars).
+        Window overlap is given as a percentage of the window size (an overlap
+        of 50\% means that two adjacent windows share an area half of the size
+        of the entire window).
+        For gradient-boosting, the RMS errors and computation times are the
+        means (error bars are 1 standard deviation) of results using different
+        seeds for the pseudo-random number generator.
+        Computation time is the ratio between the time required to estimate the
+        source coefficients for the gradient-boosted and the regular equivalent
+        sources.
+}
+    \label{fig:gradient-boosted-comparison}
+\end{figure*}
+
 These results show that the interpolation error for gradient-boosting is
@@
 performance of the gradient-boosted equivalent sources.
-It controls the number of iterations and how often a particular source is used
-in the least-squares fitting process.
-While the experiments in the previous section showed that 50\% overlap was
-sufficient to achieve acceptable interpolation accuracy, we separately studied
-the impacts of the amount of window overlap on both accuracy and computation
-time.
+It controls the number of iterations and how many times a particular source is
+used in the least-squares fitting process.
+The experiments in the previous section showed that 50\% overlap was
+sufficient to achieve acceptable interpolation accuracy.
+However, we studied separately the impacts of the amount of window overlap on
+both accuracy and computation time.
 
@@
 All other experimental procedures remained unchanged.
-Figs.~\ref{fig:gradient-boosted-comparison}b and
-\ref{fig:gradient-boosted-comparison}d show the RMS error and computation time
-required for estimating the source coefficients, respectively, as a function of
+Fig.~\ref{fig:gradient-boosted-comparison}b shows the RMS error and
+Fig.~\ref{fig:gradient-boosted-comparison}d shows the computation time
+required for estimating the source coefficients, both as functions of
 the window overlap.
@@
 sizes to compensate.
-
-\begin{figure*}
-    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
-    \caption{
-        Comparison of the interpolation RMS error and computation time for
-        regular least-squares equivalent sources (orange dashed lines) and
-        gradient-boosted equivalent sources (blue dots and error bars).
-        Both methods used the same source positions (block-averaged sources
-        with a relative depth).
-        Window sizes are given as a percentage of the survey area (e.g., 100\%
-        represents a window with the same area as the survey) and window
-        overlap is given as a percentage of the window size
-        (an overlap of 50\% means that two adjacent windows
-        share an area half of the size of the entire window).
-        Computation time refers to the time required to estimate the source
-        coefficients and is reported as a ratio between the gradient-boosted
-        and the regular equivalent sources.
-        For gradient-boosting, the RMS errors and computation times are the
-        means (error bars represent 1 standard deviation) of results using
-        different seeds for the pseudo-random number generator.
-        (a)~RMS error between the target grid and interpolation results and
-        (b)~RMS error between the target grid and interpolation results and
-        (c)~computation time as a function of window size.
-        (d)~computation time as a function of window overlap.
-}
-    \label{fig:gradient-boosted-comparison}
-\end{figure*}
 

### 2021-07-01 manuscript/content.tex
Simplify caption of the synthetic data

@@
     \caption{
-        Maps of the observation locations and gravity values for the synthetic
-        ground and airborne surveys.
-        (a)~Horizontal position and height of the ground survey points.
-        (b)~Synthetic gravity data calculated on the ground survey points with
-        added pseudo-random Gaussian noise.
-        (c)~Horizontal position and height of the airborne survey points.
-        (d)~Synthetic gravity data calculated on the airborne survey points
-        with added pseudo-random Gaussian noise.
+        Observation heights and gravity values for the synthetic ground (a-b)
+        and airborne (c-d) surveys.
         Heights are given in meters above the zero height plane.
+        The synthetic gravity data are contaminated with pseudo-random Gaussian
+        noise with zero mean and \SurveyNoise{} standard deviation.
     }

### 2021-07-01 manuscript/content.tex
Tweaks to figures
Use RbBy for synthetic data since it's diverging (and seismic is a bit
too saturated at the ends). Make the random/sequential comparison single
column by plotting convergence on the same plot. Add xlabel to the
histogram in australia residuals.

@@
 
-\begin{figure*}
+\begin{figure}
     \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
     \caption{
-        Results of interpolating the airborne synthetic survey with
-        gradient-boosted equivalent sources with overlapping windows being
-        iterated in random order (a and b), and with overlapping windows being
-        iterated in sequential order (c and d).
-        (a and c)~Pseudo-color maps of the differences between the target grid
-        and the interpolated synthetic airborne survey data produced
-        gradient-boosted.
-        (b and d)~Root-mean squared error of the residuals after each iteration
-        of the gradient-boosting algorithm.
+        Interpolation error for gradient-boosted equivalent sources using
+        randomized (a) and sequential (b) window order.
+        (a and b)~Pseudo-color maps of the differences between the target grid
+        and the interpolated synthetic airborne survey data.
+        (c)~Root-mean squared error after each iteration of the
+        gradient-boosting algorithm.
 }
 \label{fig:eql-boost-airborne}
-\end{figure*}
+\end{figure}
 

### 2021-07-01 manuscript/content.tex
Revise the new gb random/sequential section

@@
 \subsection{
-    Interpolating synthetic survey with gradient boosting
+    Interpolation with gradient boosting
 }
@@
 
-Finally we used gradient-boosted equivalent sources to interpolate the
-synthetic airborne survey. We started by locating a set of block-averaged
-equivalent sources using a block size of \EqlBoostAirborneSpacing{} and, based
-on the results presented on section \ref{sec:window_size_and_overlap}, we
-decided to use an overlap of 50\% and a window size of
-\EqlBoostAirborneWindowSize{} in order to define a considerable amount of
-windows.
-
-We estimated the \emph{depth} and \emph{damping} parameters by comparing the
-predictions against the values of the target grid, exploring \emph{depth}
-values between \EqlBoostAirborneMinDepth{} and \EqlBoostAirborneMaxDepth{} and
-\emph{damping} values between \EqlBoostAirborneMinDamping{} and
-\EqlBoostAirborneMaxDamping{} by steps of one order of magnitude.
+Finally, we applied the gradient-boosted equivalent sources to interpolate the
+synthetic airborne survey (Fig.~\ref{fig:synthetic-layouts}).
+As previously, we used the block-averaged sources layout with a block size of
+\EqlBoostAirborneSpacing{}.
+Based on the results from section \ref{sec:window_size_and_overlap}, we adopted
+a window overlap of 50\% and a window size of \EqlBoostAirborneWindowSize{}.
+
+We estimated the relative depth of the sources and the damping parameter by
+comparing the predictions against the values of the target grid.
+The search explored \emph{depth} values between \EqlBoostAirborneMinDepth{} and
+\EqlBoostAirborneMaxDepth{} and \emph{damping} values between
+\EqlBoostAirborneMinDamping{} and \EqlBoostAirborneMaxDamping{} by steps of one
+order of magnitude.
 The most accurate predictions achieved a RMS error of
@@
 a damping of \EqlBoostAirborneDamping{}.
-
-Figure~\ref{fig:eql-boost-airborne}a shows the differences between the target
-grid and the predictions made by the gradient-boosted equivalent sources.
-Figure~\ref{fig:eql-boost-airborne}b shows the RMS error of the
-residuals after each iteration, exposing how the gradient-boosting algorithm
-converges to a minimum fitting error.
-
-Worth noting that the RMS error achieved by the gradient-boosted equivalent
-sources is comparable to the values obtained by the regular equivalent sources
-in Section \ref{sec:synthetic_distributions}.
+It is worth noting that the RMS error achieved by the gradient-boosted
+equivalent sources is comparable to the ones obtained by the regular equivalent
+sources in Section \ref{sec:synthetic_distributions}.
+To highlight the importance of randomizing the order of windows in the
+gradient-boosting iterations, we preformed the interpolation once more using
+the same values of \emph{damping} and \emph{depth} but this time iterating over
+windows in sequential order (South to North, West to East).
+
+Figs.~\ref{fig:eql-boost-airborne}a-b show the differences between the target
+grid and the interpolation results for windows in randomized and sequential
+order, respectively.
+The differences for randomized windows resemble those for regular least-squares
+equivalent sources seen in Figs.~\ref{fig:ground-survey-differences} and
+\ref{fig:airborne-survey-differences}.
+On the other hand, the differences for sequential windows show a clear
+trend of large negative differences in the South decreasing towards the North.
+This trend is correlated with the order in which windows are executed, with
+differences decreasing in absolute value towards the end of the algorithm.
+Fig.~\ref{fig:eql-boost-airborne}c shows the RMS error of the fitting process
+after each iteration for both window orders, clearly indicating that
+a randomized window order leads to faster convergence of the algorithm.
 
@@
 \end{figure}
-
-With the goal of highlighting the importance of randomizing the order in which
-the overlapping windows are iterated, we interpolated the airborne synthetic
-survey using the same estimated values for the \emph{damping} and
-\emph{depth} but disabling the random shuffling of the windows, iterating over
-them in sequential order.
-Fig.~\ref{fig:eql-boost-airborne}c shows the differences between the target
-grid and the predictions made by the gradient-boosted equivalent sources
-without random shuffling the windows.
-Fig.~\ref{fig:eql-boost-airborne}d shows the RMS error of the
-residuals after each iteration.
-These results show how the gradient-boosted equivalent sources underperform by
-iterating over the overlapping windows in sequential order: they fail to
-produce realistic and accurate predictions while the speed in which the
-algorithm converges is smaller.
 

### 2021-07-01 manuscript/content.tex
Revise the australia results

@@
 This section will demonstrate how gradient-boosted equivalent sources can be
-used to interpolate large datasets of gravity data onto a regular grid at
-uniform height.
+used to interpolate large datasets onto regular grids at uniform height.
 For this purpose, we selected an open-access compilation of ground gravity
@@
 using a block size of 1.8\km{}, resulting in a total of
-\AustraliaEqlNSources{}~point sources which depths remain unknown for now.
+\AustraliaEqlNSources{}~point sources.
 The block size was chosen to match the desired resolution of the final grid
 (1~arc-minute is approximately 1.8\km{} at the equator).
-Then we need to determine the size of the windows that will be used for
-estimating the coefficients of the gradient-boosted equivalent sources.
-We computed the amount of computer memory needed in order to store the largest
-Jacobian matrix for different values of window size
+Based on the results obtained in Section~\ref{sec:synthetic_distributions}, we
+have chosen to use the \emph{relative depth} strategy.
+The window overlap was once again fixed at 50\%.
+To determine the size of the windows, we computed the amount of computer memory
+needed to store the largest Jacobian matrix for different values of window size
 (Fig.~\ref{fig:australia-memory-cv-error}a).
-We have chosen a window size of \AustraliaEqlWindowSize{} in order to limit the
+We have chosen a size of \AustraliaEqlWindowSize{} in order to limit the
 amount of memory needed to under 16~Gigabytes.
@@
         (a) Amount of computer memory needed to store the largest Jacobian
-        matrix vs different window sizes. Each memory requirement corresponds
-        to the ammount of memory needed to store the elements of the largest
-        Jacobian matrix during the process of estimating the gradient-boosted
-        equivalent sources coefficients, using a double precision floating
-        point for each (64 bits).
-        (b) Root-mean square errors obtained after the K-Fold cross-validation
+        matrix for different window sizes. Our implementation uses double
+        precision floating point numbers (64 bits) for the Jacobian.
+        (b) K-Fold cross-validation root-mean square errors obtained after the
         for each pair of damping and depth parameters. The orange
-        square highlights the minimum RMS value.
-        (c) Root-mean square error of the residuals after each iteration of the
-        coefficients estimation process.
+        square highlights the minimum.
+        (c) Root-mean square error against the observed data after each
+        iteration of the gradient-boosting algorithm.
     }
@@
 
-Secondly, we need to determine the depth of the sources and the value for the
-damping parameter. Based on the results obtained in
-Section~\ref{sec:synthetic_distributions}, we have chosen to locate them using
-the \emph{relative depth} strategy.
-In order to determine the values for the \emph{depth} and \emph{damping}
-parameters, we have applied a K-Fold cross-validation method through the
-scikit-learn implementation \citep{sklearn2011}.
-It consists in randomly dividing the original data into $k$ small sets (or
-folds), estimate the source coefficients using only $k - 1$ of the folds
-(training data) and validate the model by comparing its predictions with the
-remaining fold (testing data). This process is carried out once for each one of
-the $k$ folds.
-With the goal of speeding up the computations, we selected a portion of the
-Australia gravity disturbances to run the cross-validation: an area of
+We determined the depth of the sources and the damping parameter by applying
+K-Fold cross-validation through the scikit-learn library \citep{sklearn2011}.
+The method randomly divides the original data into $k$ sets (folds), fits the
+model using only data from $k - 1$ folds, and validates the model by comparing
+its predictions against the one remaining fold.
+This process is carried out once for each one of the $k$ folds, leading to
+an estimated mean cross-validation RMS error for the model.
+To speed up the computation, we only performed the cross-validation on a subset
+of the data corresponding to an area of
 \AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
 containing \AustraliaSmallAreaNPoints{} points.
-We run the cross-validation with a combination of \emph{depth} ranging from
-\AustraliaDepthMin{} to \AustraliaDepthMax{},
-and \emph{damping} from
-\AustraliaDampingMin{} to \AustraliaDampingMax{} in steps of one order of
-magnitude.
-We have used the root-mean square error as the validation function between the
-testing data and the predictions on each k-fold and computed the mean of all
-the RMS for each combination of the \emph{depth} and \emph{damping} parameters.
-Figure \ref{fig:australia-memory-cv-error}b shows the resulting scores of the
-cross-validation and highlights the minimum value achieved:
-\AustraliaEqlRmsScore{} corresponding to a relative depth of \AustraliaEqlDepth{} and
-a damping equal to \AustraliaEqlDamping{}.
-
-Finally, we proceed to estimate the coefficients of the whole set of
-gradient-boosted equivalent sources using the parameters previously determined.
-Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
-residuals after each iteration of the gradient-boosting algorithm, exposing how
-the algorithm converges at a minimum difference between the gravity disturbance
-data and the predicted values by the equivalent sources.
-We then used the estimated source coefficients to predict the values of the
+We ran the cross-validation repeatedly for combinations of \emph{depth},
+ranging from \AustraliaDepthMin{} to \AustraliaDepthMax{},
+and \emph{damping}, from \AustraliaDampingMin{} to \AustraliaDampingMax{} in
+steps of one order of magnitude.
+Figure \ref{fig:australia-memory-cv-error}b shows the resulting
+cross-validation RMS errors and highlights the minimum value of
+\AustraliaEqlRmsScore{}, which corresponds to a relative depth of
+\AustraliaEqlDepth{} and a damping equal to \AustraliaEqlDamping{}.
+
+Finally, we proceeded to estimate the source coefficients using the entire
+dataset and the parameters previously determined.
+Fig.~\ref{fig:australia-memory-cv-error}c shows the RMS error against the
+observed data after each iteration of the algorithm.
+The estimated source coefficients were then used to predict the values of the
 gravity disturbance on a regular grid of
@@
 Fig.~\ref{fig:australia} shows the original data distribution and the
-interpolated regular grid.
-Grid points that are further than 50\km{} from the nearest data
-point are masked to avoid unrealistic extrapolations.
-
-Fig.~\ref{fig:australia-residuals} shows the residuals on each observation
-point: the difference between the gravity disturbance data and the predicted
-values by the equivalent sources on the same points.
-The inset figure shows a histogram of the residual values, depicting that the
-residuals are normally distributed around zero.
+interpolated grid.
+Grid points that are further than 50\km{} from the nearest data point are
+masked to avoid unrealistic extrapolations.
 
@@
 $\sim 1.3$~hours and the forward modelling step took $\sim 18$~minutes.
+
+Fig.~\ref{fig:australia-residuals} shows the difference between the observed
+and predicted gravity disturbances.
+The inset figure shows a histogram of these residuals, which are approximately
+normally distributed around zero.
+The largest residuals are located in regions with high-amplitude
+short-wavelength features in the observed data.
 

### 2021-07-14 manuscript/content.tex
Revise discussion of source location and gradient boosting

@@
         and the interpolated synthetic airborne survey data.
+        The color scale has been cropped to the same range as
+        Fig.~\ref{fig:airborne-survey-differences}.
         (c)~Root-mean squared error after each iteration of the
@@
 
-\begin{figure*}
+\begin{figure}
     \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
@@
         precision floating point numbers (64 bits) for the Jacobian.
-        (b) K-Fold cross-validation root-mean square errors obtained after the
-        for each pair of damping and depth parameters. The orange
-        square highlights the minimum.
-        (c) Root-mean square error against the observed data after each
+        (b) Root-mean square error against the observed data after each
         iteration of the gradient-boosting algorithm.
+        (c) K-Fold cross-validation root-mean square errors obtained for each
+        pair of damping and depth parameters. The orange star highlights the
+        minimum.
     }
     \label{fig:australia-memory-cv-error}
-\end{figure*}
+\end{figure}
 
@@
 and~\ref{fig:airborne-survey-differences}) show that there are no significant
-differences between source distribution strategies, both in terms of the
-interpolation RMS errors and from visual inspection of the difference maps.
-Therefore, we argue that all source distribution strategies are able to produce
-comparably accurate interpolations.
-Nevertheless, the \emph{block-averaged sources} strategy make use of fewer
+differences in interpolation accuracy between source distribution strategies,
+both in terms of the interpolation RMS errors and from visual inspection of the
+difference maps.
+Therefore, we conclude that all source distribution strategies are able to
+produce comparable interpolations.
+Nevertheless, the \emph{block-averaged sources} strategy makes use of fewer
 sources when compared with other strategies, which reduces the computational
@@
 the number of iterations.
-Our results indicate that it is desirable to maximize the window size up to the
-point that the Jacobian matrices still fit within the available computer
-memory.
+Our results indicate that it is desirable to maximize the window size,
+which can be done up to the point that the Jacobian matrices still fit within
+the available computer memory.
 
@@
 Running the gradient boosting algorithm sequentially produces less accurate
-predictions and decreases the convergence rate.
+predictions and decreases the convergence rate of the method.
 

### 2021-07-14 manuscript/content.tex
Add a discussion section for the australia results
Move some of the text from the end of the results section here.

@@
 dataset and the parameters previously determined.
-Fig.~\ref{fig:australia-memory-cv-error}c shows the RMS error against the
-observed data after each iteration of the algorithm.
 The estimated source coefficients were then used to predict the values of the
@@
 \AustraliaEqlGridHeight{} above the ellipsoid.
+On a modest workstation with 16 cores and 16~Gigabytes of RAM,
+estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
+$\sim 1.3$~hours and the prediction step took $\sim 18$~minutes.
+
 Fig.~\ref{fig:australia} shows the original data distribution and the
@@
 masked to avoid unrealistic extrapolations.
-
-The resulting grid preserves the high resolution of the original data while
-avoiding aliasing artifacts due to the block averaging.
-Some parts of the grid are smoother and with reduced amplitude (e.g., some
-southwestern parts), which is expected from the upward continuation that was
-performed to have the grid at a constant height.
-On a modest workstation with 16 cores and 16~Gigabytes of RAM,
-estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
-$\sim 1.3$~hours and the forward modelling step took $\sim 18$~minutes.
-
+Fig.~\ref{fig:australia-memory-cv-error}c shows the RMS error against the
+observed data after each iteration of the algorithm.
 Fig.~\ref{fig:australia-residuals} shows the difference between the observed
@@
 normally distributed around zero.
-The largest residuals are located in regions with high-amplitude
-short-wavelength features in the observed data.
 
@@
 predictions and decreases the convergence rate of the method.
+
+\subsection{Australia gravity data}
+
+The application of the gradient-boosted equivalent sources to the Australian
+gravity dataset demonstrates that the method is able to interpolate and
+upward-continue large datasets in a reasonable amount of time using only modest
+computational resources.
+The resulting grid (Fig.~\ref{fig:australia}) preserves the high resolution of
+the original data while avoiding aliasing artifacts due to the block averaging
+of the source locations.
+Some parts of the grid are smoother and have lower amplitudes than the original
+data (e.g., some southwestern parts), which is expected from the upward
+continuation that was performed to have the grid at a constant height.
+
+The largest residuals in Fig.~\ref{fig:australia-residuals} are located in
+regions with high-amplitude short-wavelength features in the observed data.
+This is expected since the method involves some degree of smoothing because of
+the use of damping and the source depths.
+There are also low-amplitude long-wavelength residual signals that seem to
+coincide with some of the windows of the gradient-boosting method.
+A possible cause of these features is inability of the equivalent-sources
+within a window to adequately fit the long-wavelength components of the data.
+We note, however, that all of these long-wavelength residuals are smaller than
+1 mGal in amplitude and do not represent a significant source of errors.
 

### 2021-07-14 manuscript/content.tex
Add something about the CV results

--- 2021-07-14 manuscript/content.tex
@@
 steps of one order of magnitude.
-Figure \ref{fig:australia-memory-cv-error}b shows the resulting
+Figure \ref{fig:australia-memory-cv-error}c shows the resulting
 cross-validation RMS errors and highlights the minimum value of
@@
 masked to avoid unrealistic extrapolations.
-Fig.~\ref{fig:australia-memory-cv-error}c shows the RMS error against the
+Fig.~\ref{fig:australia-memory-cv-error}b shows the RMS error against the
 observed data after each iteration of the algorithm.
@@
 1 mGal in amplitude and do not represent a significant source of errors.
+
+The elongated valley around the minimum of the cross-validation RMS errors
+(Fig.~\ref{fig:australia-memory-cv-error}c) shows that there is ambiguity in
+the choice of damping and source depths.
+One could choose a large damping with a small depth or a small damping with a
+large depth to achieve roughly the same interpolation result.
+This is expected since both parameters control the smoothness of the
+interpolation.
 

### 2021-07-14 manuscript/content.tex
Minor changes to the conclusions

@@
 computational load of estimating the coefficients of the equivalent sources,
-specially on the computer memory needed to store the Jacobian matrix.
-In this work we present two strategies that could be simultaneously applied in
-order to interpolate very large datasets (millions of points) in reasonable
-computation times on modest hardware:
-block-averaging source locations, which reduce the number of equivalent sources
-needed for the interpolation,
+specially the computer memory needed to store the Jacobian matrix.
+
+We present two strategies that could be simultaneously applied to interpolate
+datasets with millions of points on modest hardware:
+block-averaging source locations, which reduces the number of equivalent
+sources needed for the interpolation,
 and the gradient-boosted equivalent source algorithm, which breaks down the
@@
 Both methods were tested against synthetic datasets in order to compare their
-accuracy and how they perform in terms of computational resources.
+accuracy and how they perform in terms of computational efficiency.
 
 Our results show that the block-averaged sources reduce the computational
-load needed to estimate source coefficients in comparison to the two traditional
-strategies of placing sources below data points or on regular grids.
-We also showed that this reduction of the number of sources does not affect
+load needed to estimate source coefficients in comparison to two traditional
+strategies (placing sources below data points or on regular grids).
+We also show that this reduction of the number of sources does not affect
 the accuracy of the predictions.
@@
 Special attention must be payed when choosing the size of the blocks for
-averaging: as a thumb rule, we recommend choosing a size approximately equal to
+averaging.
+As a thumb rule, we recommend choosing a size approximately equal to
 the resolution of the regular grid where the values will be interpolated.
@@
 accuracy than the regular equivalent sources, while reducing the computation
-time needed to estimate the source coefficients by approximately three times.
+time by approximately a factor of three.
 We also show that an overlap of 50\% between adjacent windows achieves a good
@@
 possible that creates Jacobian matrices that still fit into computer memory.
-Moreover, randomizing the order in which the overlapping windows are iterated
-is essential to improve the quality of the predictions and increase
-the convergence rate of the algorithm.
-
-The gradient-boosting method developed here can be used in conjunction with any
-horizontal source layout, depth strategy, or source type (e.g., point sources,
-prisms, tesseroids) because it does not rely on assumptions about the sources.
+Moreover, randomizing the order in which the windows are iterated increases the
+convergence rate of the algorithm and is essential to producing accurate
+predictions.
+
+The gradient-boosting method can be used in conjunction with any horizontal
+source layout, depth strategy, or source type (e.g., point sources, prisms,
+tesseroids) because it does not rely on assumptions about the sources.
 Future research should investigate the application of gradient boosting to

### 2021-07-15 manuscript/content.tex
Add a sentence about the interpolation error from CV
Review discussion once more (#163)
Going over the discussion and conclusions. Added some text about the Australia data application (some moved from the results).

@@
 continuation that was performed to have the grid at a constant height.
+From the cross-validation analysis on a subset of the data, we estimate that
+the interpolation error is approximately \AustraliaEqlRmsScore{}.
 
@@
 without which this work would not have been possible.
+We would also like to thank Editor Frederik Simons, Assistant Editor Fern
+Storey, and two anonymous reviewers for their constructive comments.
 S.R. Soler is supported by a scholarship from CONICET, Argentina.
 This work contains British Geological Survey materials ©~UKRI.
-
 S.R. Soler and L. Uieda jointly developed the initial idea, analysed the
 results, and wrote the paper. S.R. Soler produced all results and developed the
-software implementation with minor revisions by L. Uieda.
+software implementation with the assistance of L. Uieda.

### 2021-07-15 manuscript/content.tex
Fix small typos on manuscript

@@
 This could lead to aliasing effects on the predicted values, such as the
-stripes parallel to flight lines that are often observed when griding airborne
+stripes parallel to flight lines that are often observed when gridding airborne
 magnetic data.
@@
 $\Delta z$ is a relative depth shift that is the same for all sources,
-$\alpha$ is an adimensional depth factor,
+$\alpha$ is an dimensionless depth factor,
 $h$ is the median horizontal distance to the $k$ nearest neighbouring sources,

### 2021-07-16 manuscript/content.tex
Make small edits (#164)

@@
 
-The type of source is most commonly a point mass for gravity or dipole for
-magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994, siqueira2017}.
+The most commonly used type of source is a point mass for gravity or dipole for
+magnetics \citep[e.g.,~][]{vonfrese1981, silva1986, mendonca1994,
+siqueira2017}.
 However, right-rectangular prisms \citep[e.g.,][]{barnes2011, jirigalatu2019,
@@
 
-We performed a similar experiment to one in section~\ref{sec:window_size} but
-this time kept the window size fixed to \BoostOverlappingWindowSize{} and
+We performed a similar experiment to the one in section~\ref{sec:window_size}
+but this time kept the window size fixed to \BoostOverlappingWindowSize{} and
 varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
@@
 The window overlap was once again fixed at 50\%.
-To determine the size of the windows, we computed the amount of computer memory
+To determine the size of the windows, we calculated the amount of computer memory
 needed to store the largest Jacobian matrix for different values of window size

### 2021-08-24 manuscript/content.tex
Shrink figure on preprint due to onecolumn
Some tweaks to the preprint styling (#167)
* Some tweaks to the preprint styling

Decreased margins (to save space), increase column separation (better
readability), tweak figure placement, and remove the footer (the header
has the citation info, which is what's important).

* Increase margins to 1.5cm

Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>
Use the mGal variable in manuscript

@@
 
-\begin{figure*}
+\begin{figure*}[tb]
     \centering
@@
 
-\begin{figure*}
+\begin{figure*}[tb]
     \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
@@
 
-\begin{figure*}
+\begin{figure*}[tb]
     \includegraphics[width=\linewidth]{figs/depth_types.pdf}
@@
 
-\begin{figure*}
+\begin{figure*}[tb]
     \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
@@
 
-\begin{figure}
+\begin{figure}[tb]
     \includegraphics[width=\linewidth]{figs/target-grid.pdf}
@@
 
-\begin{figure*}
+\begin{figure*}[p]
     \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
@@
 
-\begin{figure*}
+\begin{figure*}[p]
     \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
@@
 
-\begin{figure*}
+\begin{figure*}[tb]
     \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
@@
 
+\begin{figure}[tb]
+    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
+    \caption{
+        Interpolation error for gradient-boosted equivalent sources using
+        randomized (a) and sequential (b) window order.
+        (a and b)~Pseudo-color maps of the differences between the target grid
+        and the interpolated synthetic airborne survey data.
+        The color scale has been cropped to the same range as
+        Fig.~\ref{fig:airborne-survey-differences}.
+        (c)~Root-mean squared error after each iteration of the
+        gradient-boosting algorithm.
+}
+\label{fig:eql-boost-airborne}
+\end{figure}
+
 Figs.~\ref{fig:eql-boost-airborne}a-b show the differences between the target
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
-    \caption{
-        Interpolation error for gradient-boosted equivalent sources using
-        randomized (a) and sequential (b) window order.
-        (a and b)~Pseudo-color maps of the differences between the target grid
-        and the interpolated synthetic airborne survey data.
-        The color scale has been cropped to the same range as
-        Fig.~\ref{fig:airborne-survey-differences}.
-        (c)~Root-mean squared error after each iteration of the
-        gradient-boosting algorithm.
-}
-\label{fig:eql-boost-airborne}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure*}
+\begin{figure*}[p]
     \includegraphics[width=\linewidth]{figs/australia.png}
@@
 
-\begin{figure}
+\begin{figure}[tbh!]
+    \makeatletter%
+    \if@twocolumn%
         \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
+    \else% \@twocolumnfalse
+        \centering
+        \includegraphics[width=0.6\linewidth]{figs/australia-memory-cv-error.pdf}
+    \fi
+    \makeatother
     \caption{
@@
 
-\begin{figure}
+\begin{figure}[tb]
     \includegraphics[width=\linewidth]{figs/australia-residuals.png}
@@
 We note, however, that all of these long-wavelength residuals are smaller than
-1 mGal in amplitude and do not represent a significant source of errors.
+1\mGal{} in amplitude and do not represent a significant source of errors.
 
